### 2017-08-29 docs/main.tex
latex files

\documentclass[a4paper, 11pt, twoside, onecolumn, openany]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel} % English please
\usepackage{subfiles}
\usepackage{standalone}
\usepackage[a4paper, tmargin=2cm, rmargin = 2cm]{geometry}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{multirow}

\usepackage[final]{microtype} % Less badboxes
\usepackage{color}
\usepackage{standalone}

\usepackage{amsmath,amssymb,mathtools,amsthm} % Math
\mathtoolsset{centercolon} %to make the colon and the equal sign in := on the same line
\title{Packing Boxes with Score Constraints}
\author{Asyl L. Hawa}
\date{\today}

\begin{document}
\maketitle
% example, n = 9, + extra box = 10
% add one more box with dominating vertices, i.e. score widths 70mm
% use indices, not actual score widths 
% sort scores in increasing order
% assign random mates, except dom vertices, they must be on the same box, assign them as mates to each other
% assign box widths except dominating box, doesn't need a width (doesn't get used)
% talk about MTGMA matchList vector
% talk about MIS - mateInduced vector - length of MIS
% talk about T-cycles FCA
% patch together - fullT vs split T
% final cycle, final path

\section{Example}
\subsection{Creating problem instance}
In this example, we will attempt to find a feasible alignment of nine boxes, with score widths ranging between 1mm and 70mm. The minimum score separation constraint, or ``threshold'', will be set at 70mm, the industry standard.

Initially, we create 18 random values between 1 and 70, which will be our score widths. We also need to add an extra box with two score of widths 70mm, which will be our ``dominating scores'', giving us a total of 10 boxes and 20 scores. These dominating scores will eventually be discarded.

We then sort the scores in non-decreasing order, and place them in a vector. The scores will now be addressed by their indices throughout the rest of the algorithm (see Table \ref{table:allScores}).

\begin{table}[htb]
\centering
\begin{tabular}{|l*{20}{|c}|}
	\hline
	Index & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 \\ \hline
	Scores & 3 & 4 & 12 & 22 & 25 & 35 & 36 & 37 & 38 & 45 & 49 & 54 & 54 & 55 & 55 & 64 & 65 & 66 & 70 & 70 \\
	\hline	
\end{tabular}
\caption{allScores vector.}
\label{table:allScores}
\end{table}

Since every box consists of two scores, each score is randomly assigned a ``mate'', so that one score (the smaller score) represents the left-hand side of the box, and the other score represents the right-hand side of the box. The only exceptions to the random allocation of mates are the dominating scores - they must be assigned to one another. We can then assign measurements to each pair of mates to represent the width of each individual box. %except dominating box, score not needed

\begin{table}[htb]
	\centering
	\begin{tabular}{|c|c|c|}
	\hline
	\multicolumn{2}{|c|}{Mates} & Box Width \\ \hline
	0 & 6 & 314 \\ \hline
	1 & 10 & 372 \\ \hline
	2 & 16 & 297 \\ \hline
	3 & 11 & 220 \\ \hline
	4 & 17 & 959 \\ \hline
	5 & 9 & 738 \\ \hline
	7 & 12 & 622 \\ \hline
	8 & 15 & 635 \\ \hline
	13 & 14 & 859 \\ \hline
	18 & 19 & 0 \\
	\hline
	\end{tabular}
	\caption{Mates.}
\end{table}

Next, we create an adjaceny matrix. This adjaceny matrix contains information regarding threshold constraint. If the sum of two scores is greater than or equal to the threshold, the adjaceny matrix contains ``1'' in the relevant cell. If two scores are mates, the adjaceny matrix contains ``2''. Else, the adjaceny matrix contains ``0''. %change this, also explain that the adjMatrix is of size numScore x numScore, square matrix

% Modified matching

\begin{table}[htb]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		\multicolumn{2}{|c|}{Match}\\ \hline
		0 & 19 \\ \hline
		1 & 18 \\ \hline
		2 & 17 \\ \hline
		3 & 16 \\ \hline
		4 & 15 \\ \hline
		5 & 14 \\ \hline
		6 & 13 \\ \hline
		7 & 11 \\ \hline
		8 & 12 \\ \hline
		9 & 10 \\
		\hline
	\end{tabular}
	\caption{Match List.}
\end{table}

\begin{table}[htb]
	\centering
	\begin{tabular}{|l*{10}{|c}|}
		\hline
		Cycle 0 & 0 & 6 & 13 & 14 & 15 & 9 & 10 & 1 & 18 & 19 \\ \hline
		Cycle 1 & 2 & 16 & 3 & 11 & 7 & 12 & 8 & 15 & 4 & 17 \\
		\hline
	\end{tabular}
	\caption{Mate-Induced Cycles.}	
\end{table}

\begin{table}[htb]
	\centering
	\begin{tabular}{c|c|c|}
		\cline{2-3}
		& \multicolumn{2}{|c|}{Edges} \\ \hline
		\multicolumn{1}{|c|}{cycle 1} & 1 & 2 \\ \hline
		\multicolumn{1}{|c|}{cycle 2} & 4 & 5 \\ \hline
		\multicolumn{1}{|c|}{cycle 3} & 6 & 8 \\
		\hline
	\end{tabular}
	\caption{T-Matrix.}
\end{table}

\begin{figure}
	\centering
	\includestandalone[width=0.9\textwidth]{patch}
	\caption{Patching MIS blue = mates, red = matching, explain dotted lines.}	
\end{figure}

\end{document}

### 2017-08-29 docs/main.tex
updated MGTMA

@@
 Initially, we create 18 random values between 1 and 70, which will be our score widths.
-We also need to add an extra box with two score of widths 70mm, which will be our ``dominating scores'', giving us a total of 10 boxes and 20 scores.
+We also need to add an extra box with two score of widths 70mm, which will be our ``dominating scores'', giving us a total of $n$ = 10 boxes and 20 scores.
 These dominating scores will eventually be discarded.
@@
 
-% Modified matching
+\subsection{Matching scores}
+Once we have created the problem instance, we then have to attempt to match the scores together.
+If two scores can be matched, it means that the boxes can be placed next to each other, and the total width of the two scores from the boxes is equal to or exceeds the threshold, and can therefore be scored using the knives in the scoring machine.
+
+The matching is performed as follows: starting from the smallest score (0), we attempt to match it with the largest possible score it is adjacent to ( = 1 in the adjaceny matrix), and that has not yet been matched (in this case, 19).
+We continue until all scores have been matched.
+If a score cannot be matched due to the largest score being its mate, we match the score with the second largest score available.
+As we can see in Table \ref{table:match}, score 7 was unable to be matched with the largest possible score, 12, as they are mates.
+Instead, 7 was matched with the next largest score, 11.
+
+Once the matching algorithm is complete, we then examine the size of the matching list.
+For the instance to be feasible, all of the scores must be matched.
+If not all of the scores are matched, i.e.
+there are less than $n$ matchings in the matching list, then there are not enough matching edges to create a path, and the instance is infeasible.
 
@@
 	\caption{Match List.}
+	\label{table:match}
 \end{table}
+
+\subsection{Mate-Induced Structure}
 

### 2017-08-30 docs/main.tex
updated MIS

@@
 \subsection{Mate-Induced Structure}
+Now that we have a list of matched scores, we can now attempt to create an \textit{alternating cycle} which consists of an edge between scores that are mates, followed by an edge between scores that are matched.
+Therefore each score will either be preceded by a mate and followed by a match, or vice versa.
+The cycles are easily formed using the mate list and match list.
+
+If the mate-induced structure consists of only one cycle, then the instance is instantly feasible.
+In this example we have two cycles, and so we must find a way to connect, or ``patch'', these two cycles together to create a single cycle.
 
@@
 \end{table}
+
+\subsection{FCA}%change this title
 

### 2017-09-02 docs/main.tex
updated

@@
 \usepackage{multirow}
+\usepackage{verbatim}
+\definecolor{light-gray}{gray}{0.95} 
+\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}
 
@@
 		\hline
-		Cycle 0 & 0 & 6 & 13 & 14 & 15 & 9 & 10 & 1 & 18 & 19 \\ \hline
-		Cycle 1 & 2 & 16 & 3 & 11 & 7 & 12 & 8 & 15 & 4 & 17 \\
+		Cycle 1 & 0 & 6 & 13 & 14 & 15 & 9 & 10 & 1 & 18 & 19 \\ \hline
+		Cycle 2 & 2 & 16 & 3 & 11 & 7 & 12 & 8 & 15 & 4 & 17 \\
 		\hline
 	\end{tabular}
-	\caption{Mate-Induced Cycles.}	
+	\caption{Mate-induced structure consisting of two cycles.}	
 \end{table}
@@
 \subsection{FCA}%change this title
+In order to join these two cycles together to create a single cycle, we must find scores from different cycles that are able to be matched, i.e the sum of the scores are greater than or equal to the threshold.
+If we are able to find such scores, then we simply remove the old matches, and add the new ones.
+In this case, there are three possible sets of scores that can be used to connect the cycles together.
+For simplicity and speed, we choose the first set of scores found.
+This is depicted in FIGURE.
 
+\begin{table}[htb]
+	\centering
+	\begin{tabular}{c|c|}
+		\cline{2-2}
+		& Scores \\ \hline
+		\multicolumn{1}{|c|}{Cycle 1} & 1 - 18 - 2 - 17 \\ \hline
+		\multicolumn{1}{|c|}{Cycle 2} & 4 - 15 - 5 - 14 \\ \hline
+		\multicolumn{1}{|c|}{Cycle 3} & 6 - 13 - 8 - 12 \\
+		\hline
+	\end{tabular}
+	\caption{T-Matrix.}
+\end{table}
+
+\begin{figure}[htb]
+	\centering
+	\includestandalone[width=0.9\textwidth]{patch}
+	\caption{Patching MIS blue = mates, red = matching, explain dotted lines.}	
+\end{figure}
+
+Now that the cycle has been formed, we simply remove the dominating scores, and obtain a single path.\\
+\\
+\code{Complete Path: 0 6 13 14 5 9 10 1 17 4 15 8 12 7 11 3 16 2}\\
+\code{Order of Boxes: 1 9 6 -2 -5 -8 -7 -4 -3}\\
+\code{Total Length of Path: 5043 millimeters.}
+
+\begin{figure}[htb]
+	\centering
+	\includestandalone[width=0.6\textwidth]{boxes}
+	\caption{Individual boxes.}	
+\end{figure}
+
+\begin{figure}[htb]
+	\centering
+	\includestandalone[width=\textwidth]{path}
+	\caption{Final feasible alignment of boxes.}	
+\end{figure}
+
+\begin{comment}
+\begin{table}[htb]
+\centering
+\begin{tabular}{c|c|c|c|c|}
+\cline{2-5}
+& \multicolumn{4}{|c|}{Scores} \\ \hline
+\multicolumn{1}{|c|}{cycle 1} & 1 & 18 & 2 & 17 \\ \hline
+\multicolumn{1}{|c|}{cycle 2} & 4 & 15 & 5 & 14 \\ \hline
+\multicolumn{1}{|c|}{cycle 3} & 6 & 13 & 8 & 12 \\
+\hline
+\end{tabular}
+\caption{T-Matrix.}
+\end{table}	
+\end{comment}
+
+\begin{comment}
 \begin{table}[htb]
@@
 \end{table}	
-
-\begin{figure}
-	\centering
-	\includestandalone[width=0.9\textwidth]{patch}
-	\caption{Patching MIS blue = mates, red = matching, explain dotted lines.}	
-\end{figure}
+\end{comment}
 

### 2017-09-03 docs/main.tex
updated

@@
 \usepackage{amsmath,amssymb,mathtools,amsthm} % Math
-\mathtoolsset{centercolon} %to make the colon and the equal sign in := on the same line
+\mathtoolsset{centercolon} % to make the colon and the equal sign in := on the same line
+
 \title{Packing Boxes with Score Constraints}
@@
 	\caption{Mates.}
+	\label{table:mates}
 \end{table}
@@
 	\caption{Mate-induced structure consisting of two cycles.}	
+	\label{table:mis}
 \end{table}
@@
 	\caption{T-Matrix.}
+	\label{table:tcycles}
 \end{table}
@@
 	\caption{Patching MIS blue = mates, red = matching, explain dotted lines.}
+	\label{fig:patch}	
 \end{figure}
@@
 	\caption{Individual boxes.}	
+	\label{fig:boxes}
 \end{figure}
@@
 	\caption{Final feasible alignment of boxes.}	
+	\label{fig:path}
 \end{figure}
 
-\begin{comment}
-\begin{table}[htb]
-\centering
-\begin{tabular}{c|c|c|c|c|}
-\cline{2-5}
-& \multicolumn{4}{|c|}{Scores} \\ \hline
-\multicolumn{1}{|c|}{cycle 1} & 1 & 18 & 2 & 17 \\ \hline
-\multicolumn{1}{|c|}{cycle 2} & 4 & 15 & 5 & 14 \\ \hline
-\multicolumn{1}{|c|}{cycle 3} & 6 & 13 & 8 & 12 \\
-\hline
-\end{tabular}
-\caption{T-Matrix.}
-\end{table}	
-\end{comment}
+\section{Improvements}
+\begin{itemize}
+	\item Becker used arrays and set a specific size for each one - wastes memory and is inefficient. Instead I used vectors that could be expanded as required.
+	\item Becker's code only evaluates whether a specific instance is feasible or infeasible. My code now outputs a solution to an instance in full, including the following:
+	\begin{itemize}
+		\item Outputs final solution with score indices in order.
+		\item Outputs final solution with score widths in millimeters in order.
+		\item Outputs box widths in millimeters in order.
+		\item Outputs box number in order: if the number is positive, then the box's orientation is ``regular'' (the smallest score width is on the left-hand side), and if the number is negative, then the box's orientation is ``rotated'' (the smallest score is on the right-hand side).
+		\item Outputs the total length of the boxes in millimeters.
+	\end{itemize}
+	\item All methods in the algorithm are now in separate functions, which makes the code easier to read and edit.
+	\item The code determines whether only one T-cycle is required to connect all the cycles together, or whether multiple T-cycles are required. 
+	\item Box widths have now been added - each box has a width in millimeters.
+	\item User input - users can create a simple text file containing score width, mates and box widths to use with the program.
 
-\begin{comment}
-\begin{table}[htb]
-\centering
-\begin{tabular}{c|c|c|}
-\cline{2-3}
-& \multicolumn{2}{|c|}{Edges} \\ \hline
-\multicolumn{1}{|c|}{cycle 1} & 1 & 2 \\ \hline
-\multicolumn{1}{|c|}{cycle 2} & 4 & 5 \\ \hline
-\multicolumn{1}{|c|}{cycle 3} & 6 & 8 \\
-\hline
-\end{tabular}
-\caption{T-Matrix.}
-\end{table}	
-\end{comment}
+\end{itemize}
+
+\section{Things to find out/do}
+\begin{itemize}
+	\item What are the industry standard strip lengths?
+	\item Goulimis $n$ = 10, is this true? Are there cases where more boxes are needed?
+	\item Current speed of scoring in industry
+	\item What happens before/after scoring in industry?
+	\item Output to csv file?
+	\item Calculate complexity
+	\item Martello and Toth (1990b) MTP algorithm, adapt with additional constraints
+	\item Exemptions on threshold, what if the instance in infeasible due to one box, can that box be held back and attempt to use in the next instance? Or can it still be used, but scoring run slower?
+	\item How many scoring knives are used?
+	\begin{itemize}
+		\item If only one set of scoring knives is used, then are the boxes placed on a conveyor belt? Does this affect the time?
+		\item If there are a specific number of scoring knives used, should we look at how many boxes are on each strip?
+I.e.
+if there are 4 scoring knives, then there should be only 4 scores on the strip, even if there is space available left on the strip?
+
+	\end{itemize}
+
+\end{itemize}
 

### 2017-09-06 docs/main.tex
updated

@@
 \maketitle
-% example, n = 9, + extra box = 10
-% add one more box with dominating vertices, i.e. score widths 70mm
-% use indices, not actual score widths 
-% sort scores in increasing order
-% assign random mates, except dom vertices, they must be on the same box, assign them as mates to each other
-% assign box widths except dominating box, doesn't need a width (doesn't get used)
-% talk about MTGMA matchList vector
-% talk about MIS - mateInduced vector - length of MIS
-% talk about T-cycles FCA
-% patch together - fullT vs split T
-% final cycle, final path
 
@@
 In this example, we will attempt to find a feasible alignment of nine boxes, with score widths ranging between 1mm and 70mm.
-The minimum score separation constraint, or ``threshold'', will be set at 70mm, the industry standard.
+The minimum score separation constraint, or ``threshold'', is the minimum distance allowed between two scores from different boxes, and will be set at 70mm, the industry standard.
 
 Initially, we create 18 random values between 1 and 70, which will be our score widths.
-We also need to add an extra box with two score of widths 70mm, which will be our ``dominating scores'', giving us a total of $n$ = 10 boxes and 20 scores.
+We also need to add an extra ``dominating box'' with two scores of widths 70mm, which will be our ``dominating scores'', giving us a total of $n$ = 10 boxes and 20 scores.
 These dominating scores will eventually be discarded.
@@
 
-\begin{table}[htb]
+\begin{table}[!htb]
 \centering
@@
 Since every box consists of two scores, each score is randomly assigned a ``mate'', so that one score (the smaller score) represents the left-hand side of the box, and the other score represents the right-hand side of the box.
+Therefore, each pair of mates represents a box.
 The only exceptions to the random allocation of mates are the dominating scores - they must be assigned to one another.
 We can then assign measurements to each pair of mates to represent the width of each individual box.
-%except dominating box, score not needed
+Note that we do not assign a box width to the dominating box, as it will not be used in the final solution.
 
-\begin{table}[htb]
+\begin{table}[!htb]
 	\centering
-	\begin{tabular}{|c|c|c|}
+	\begin{tabular}{|c|c|c|c|}
 	\hline
-	\multicolumn{2}{|c|}{Mates} & Box Width \\ \hline
-	0 & 6 & 314 \\ \hline
-	1 & 10 & 372 \\ \hline
-	2 & 16 & 297 \\ \hline
-	3 & 11 & 220 \\ \hline
-	4 & 17 & 959 \\ \hline
-	5 & 9 & 738 \\ \hline
-	7 & 12 & 622 \\ \hline
-	8 & 15 & 635 \\ \hline
-	13 & 14 & 859 \\ \hline
-	18 & 19 & 0 \\
+	Box & \multicolumn{2}{|c|}{Scores} & Box Width \\ \hline
+	1 & 0 & 6 & 314 \\ \hline
+	2 & 1 & 10 & 372 \\ \hline
+	3 & 2 & 16 & 297 \\ \hline
+	4 & 3 & 11 & 220 \\ \hline
+	5 & 4 & 17 & 959 \\ \hline
+	6 & 5 & 9 & 738 \\ \hline
+	7 & 7 & 12 & 622 \\ \hline
+	8 & 8 & 15 & 635 \\ \hline
+	9 & 13 & 14 & 859 \\ \hline
+	10 & 18 & 19 & 0 \\
 	\hline
@@
 
-Next, we create an adjaceny matrix.
-This adjaceny matrix contains information regarding threshold constraint.
-If the sum of two scores is greater than or equal to the threshold, the adjaceny matrix contains ``1'' in the relevant cell.
-If two scores are mates, the adjaceny matrix contains ``2''.
-Else, the adjaceny matrix contains ``0''.
-%change this, also explain that the adjMatrix is of size numScore x numScore, square matrix
+Figure \ref{fig:boxes} shows the individual boxes with their respective score widths and box number.
+The box number will be used in the final solution to show the order in which the boxes should be placed.
+
+\begin{figure}[!htb]	
+	\centering
+	\includestandalone[width=0.6\textwidth]{boxes}
+	\caption{Individual boxes.}	
+	\label{fig:boxes}
+\end{figure}
+
+We then create an adjacency matrix, which contains information regarding which pairs of scores meet the minimum score separation constraint, as well as which pairs of scores are mates.
+
+We can also depict this problem graphically (Figure \ref{fig:threshold}) by representing each score as a vertex with an assigned value corresponding to the score width.
+A red edge between two vertices shows that the scores meet the minimum score separation constraint, and can be feasibly matched, and a blue edge between two vertices shows that the corresponding scores are mates, and therefore represent a box.
+
+\begin{figure}[!htb]
+	\centering
+	\includestandalone[width=0.5\textwidth]{thresholdgraph}
+	\caption{Threshold graph.}
+	\label{fig:threshold}	
+\end{figure}
 
@@
 
-The matching is performed as follows: starting from the smallest score (0), we attempt to match it with the largest possible score it is adjacent to ( = 1 in the adjaceny matrix), and that has not yet been matched (in this case, 19).
-We continue until all scores have been matched.
-If a score cannot be matched due to the largest score being its mate, we match the score with the second largest score available.
+We already have a list of all the scores that any one score is adjacent to.
+For each score $u$, we now have to choose just one score $v$ that score $u$ will be matched with.
+Starting from the smallest score, we use the adjacent matrix to match each score to the largest possible score available.
+If a score $u$ cannot be matched with the largest possible score $v$, due to $v$ being $u$'s mate, we instead match $u$ with the second largest score available.
 As we can see in Table \ref{table:match}, score 7 was unable to be matched with the largest possible score, 12, as they are mates.
@@
 
-Once the matching algorithm is complete, we then examine the size of the matching list.
-For the instance to be feasible, all of the scores must be matched.
-If not all of the scores are matched, i.e.
-there are less than $n$ matchings in the matching list, then there are not enough matching edges to create a path, and the instance is infeasible.
-
-\begin{table}[htb]
+\begin{table}[!htb]
 	\centering
-	\begin{tabular}{|c|c|}
+	\begin{tabular}{|l*{20}{|c}|}
 		\hline
-		\multicolumn{2}{|c|}{Match}\\ \hline
-		0 & 19 \\ \hline
-		1 & 18 \\ \hline
-		2 & 17 \\ \hline
-		3 & 16 \\ \hline
-		4 & 15 \\ \hline
-		5 & 14 \\ \hline
-		6 & 13 \\ \hline
-		7 & 11 \\ \hline
-		8 & 12 \\ \hline
-		9 & 10 \\
+		Score & 0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 \\ \hline
+		Match & 19 & 18 & 17 & 16 & 15 & 14 & 13 & 11 & 12 & 10 & 9 & 7 & 8 & 6 & 5 & 4 & 3 & 2 & 1 & 0 \\
 		\hline	
 	\end{tabular}
-	\caption{Match List.}
+	\caption{Match list.}
 	\label{table:match}
@@
 
+Once the matching algorithm is complete, each score should be associated with exactly two other scores: its mate, and its match.
+For the instance to be feasible, all of the scores must be matched.
+If there are one or more scores that are unmatched, the instance is immediately infeasible.
+
+Graphically, as depicted in Figure \ref{fig:match}, if the instance is feasible, each vertex will be adjacent to two other vertices via two edges of different colours, one red edge, and one blue edge.
+The resulting graph is a 2-regular graph.
+
+\begin{figure}[!htb]
+	\centering
+	\includestandalone[width=0.45\textwidth]{matchgraph}
+	\caption{Match graph.}
+	\label{fig:match}	
+\end{figure}
+
 \subsection{Mate-Induced Structure}
-Now that we have a list of matched scores, we can now attempt to create an \textit{alternating cycle} which consists of an edge between scores that are mates, followed by an edge between scores that are matched.
-Therefore each score will either be preceded by a mate and followed by a match, or vice versa.
-The cycles are easily formed using the mate list and match list.
+Now that we have a list of matched scores, we can now attempt to create an \textit{alternating cycle}, which is a cycle consisting of edges of alternating colours.
+In other words, the cycle will consist of an edge between scores that are mates, followed by an edge between scores that are matched.
+Therefore, each score will either be preceded by a mate and followed by a match, or vice versa.
+The cycles are easily formed using the mate list and match list, and are collectively called the mate-induced structure.
 
-If the mate-induced structure consists of only one cycle, then the instance is instantly feasible.
-In this example we have two cycles, and so we must find a way to connect, or ``patch'', these two cycles together to create a single cycle.
-
-\begin{table}[htb]
+\begin{table}[!htb]
 	\centering
@@
 
-\subsection{FCA}%change this title
-In order to join these two cycles together to create a single cycle, we must find scores from different cycles that are able to be matched, i.e the sum of the scores are greater than or equal to the threshold.
-If we are able to find such scores, then we simply remove the old matches, and add the new ones.
-In this case, there are three possible sets of scores that can be used to connect the cycles together.
-For simplicity and speed, we choose the first set of scores found.
-This is depicted in FIGURE.
+If the mate-induced structure consists of only one cycle, then the instance is instantly feasible.
+We simply remove the dominating vertices and obtain a feasible alignment of the boxes.
+In this example we have two cycles, and so we must find a way to connect, or ``patch'', these two cycles together to create a single cycle.
 
-\begin{table}[htb]
+\begin{figure}[!htb]
 	\centering
-	\begin{tabular}{c|c|}
-		\cline{2-2}
-		& Scores \\ \hline
-		\multicolumn{1}{|c|}{Cycle 1} & 1 - 18 - 2 - 17 \\ \hline
-		\multicolumn{1}{|c|}{Cycle 2} & 4 - 15 - 5 - 14 \\ \hline
-		\multicolumn{1}{|c|}{Cycle 3} & 6 - 13 - 8 - 12 \\
-		\hline
-	\end{tabular}
-	\caption{T-Matrix.}
-	\label{table:tcycles}
-\end{table}
+	\includestandalone[width=0.9\textwidth]{mis}
+	\caption{MIS.}
+	\label{fig:mis}	
+\end{figure}
 
-\begin{figure}[htb]
+\subsection{Connecting cycles}%change this title
+In order to join these two cycles together to create a single cycle, we must find scores from different cycles that are able to be matched.
+If we are able to find such scores, then we simply remove the old matching edges, and add the new ones.
+In this case, we can use the edges $\{1,18\}$ and $\{2,17\}$, which are from different cycles.
+Score 1 can be feasibly matched with score 17, and score 2 can be feasibly matched with score 18.
+Therefore, we remove the original edges $\{1,18\}$, $\{2,17\}$, and create two new edges, $\{1,17\}$ and $\{2,18\}$.
+The two cycles have now been connect to create a single cycle, as shown in Figure \ref{fig:patch}.
+
+\begin{figure}[!htb]
 	\centering
@@
 
-Now that the cycle has been formed, we simply remove the dominating scores, and obtain a single path.\\
-\\
-\code{Complete Path: 0 6 13 14 5 9 10 1 17 4 15 8 12 7 11 3 16 2}\\
-\code{Order of Boxes: 1 9 6 -2 -5 -8 -7 -4 -3}\\
-\code{Total Length of Path: 5043 millimeters.}
+Now that we have a single alternating cycle containing all of the scores, we can remove the dominating scores, and obtain a feasible solution to the problem.
+The final feasible alignment of the boxes is shown in Figure \ref{fig:path}.
 
-\begin{figure}[htb]	
-	\centering
-	\includestandalone[width=0.6\textwidth]{boxes}
-	\caption{Individual boxes.}	
-	\label{fig:boxes}
-\end{figure}
-
-\begin{figure}[htb]
+\begin{figure}[!htb]
 	\centering
@@
 \end{figure}
+
+\section{Output}
+Becker's original algorithm was designed to output a statement of feasibility or infeasibility for a large number of instances.
+This is useful to test the efficiency of the algorithm, but it does not allow a user to obtain an explicit solution for any given instance.
+In Becker's algorithm, he determines whether the cycles of the mate-induced structure can be connected, and if so, outputs a statement of feasibility - his program does not actually proceed to connect the cycles together.
+I have extended the program, and created functions that connect the cycles together, removes the dominating scores, and outputs the scores and box numbers in the order that will produce a feasible alignment of the boxes.
+The output corresponding to the above example is as follows:\\
+\\
+\code{Complete Path: 0 6 13 14 5 9 10 1 17 4 15 8 12 7 11 3 16 2}\\
+\code{Order of Boxes: 1 9 6 -2 -5 -8 -7 -4 -3}\\
+\code{Total Length of Path: 5043 millimeters.}\\
+
+If the box is aligned in its original form, i.e.
+with the smallest score on the left-hand side, the box number in the \texttt{Order of Boxes} output is positive.
+If the box needs to be rotated in the alignment, i.e.
+with the smallest score on the right-hand side, the box number is negative.
+This immediately provides the user with the information required to form a feasible alignment of the boxes.
 
@@
 
+\begin{comment}
+\begin{table}[!htb]
+\centering
+\begin{tabular}{|c|c|}
+\hline
+\multicolumn{2}{|c|}{Match}\\ \hline
+0 & 19 \\ \hline
+1 & 18 \\ \hline
+2 & 17 \\ \hline
+3 & 16 \\ \hline
+4 & 15 \\ \hline
+5 & 14 \\ \hline
+6 & 13 \\ \hline
+7 & 11 \\ \hline
+8 & 12 \\ \hline
+9 & 10 \\
+\hline
+\end{tabular}
+\caption{Match List.}
+%\label{table:match}
+\end{table}	
+\end{comment}
+
+\begin{comment}
+\begin{table}[!htb]
+\centering
+\begin{tabular}{c|c|}
+\cline{2-2}
+& Scores \\ \hline
+\multicolumn{1}{|c|}{Cycle 1} & 1 - 18 - 2 - 17 \\ \hline
+\multicolumn{1}{|c|}{Cycle 2} & 4 - 15 - 5 - 14 \\ \hline
+\multicolumn{1}{|c|}{Cycle 3} & 6 - 13 - 8 - 12 \\
+\hline
+\end{tabular}
+\caption{T-Matrix.}
+\label{table:tcycles}
+\end{table}	
+\end{comment}
+
 \end{document}

### 2017-09-14 main.cpp
removed packStripsSmallest original function, renamed packStripsSmallestSearch to packStripsSmallest

@@ -159,11 +159,11 @@ int main(int argc, char **argv){
 
         //continue;
 
-        //packStripsSmallest(numScores, numBox, maxStripWidth, mates, adjMatrix, boxWidths);
-        //continue; //do not do MTGMA/MIS/FCA/PATCH
 
-        packStripsSmallestSearch(numScores, numBox, maxStripWidth, mates, adjMatrix, boxWidths);
-        continue;
+
+        packStripsSmallest(numScores, numBox, maxStripWidth, mates, adjMatrix, boxWidths);
+        continue; //do not do MTGMA/MIS/FCA/PATCH
+
         //endregion
 
         //region MTGMA

### 2017-09-14 packing.cpp

@@ -7,109 +7,6 @@ packing.cpp
 #include "packing.h"
 using namespace std;
 
-void packStripsSmallest(int numScores, int numBox, int maxStripWidth, vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths){
-//REDO THIS ALGORITHM
-    // USE WITH NUMSCORES - 2
-    int i, j, x, k;
-    vector<int> stripSum(numBox, 0);
-    vector<vector<int> > strip(numBox);
-    int numStrips = 0;
-    vector<int> checked(numScores - 2, 0);
-
-    strip[0].push_back(0);
-    strip[0].push_back(mates[0]);
-    stripSum[0] += boxWidths[0][mates[0]];
-    /*for(k = 0; k < adjMatrix.size(); ++k){
-        adjMatrix[k][0] = 0;
-        adjMatrix[k][mates[0]] = 0;
-    }*/
-    checked[0] = 1;
-    checked[mates[0]] = 1;
-    x = 0;
-
-    //cout << "NS: " << numScores << endl;
-
-    for(j = 0; j < numScores - 2; ++j){
-        if (checked[j] == 1) {
-            continue;
-        }
-        for(i = 0; i < strip.size(); ++i){
-            if(!strip[i].empty()){
-                if(adjMatrix[strip[i].back()][j] == 1){
-                    if(stripSum[i] + boxWidths[j][mates[j]] <= maxStripWidth){
-                        strip[i].push_back(j);
-                        strip[i].push_back(mates[j]);
-                        stripSum[i] += boxWidths[j][mates[j]];
-                        checked[j] = 1;
-                        checked[mates[j]] = 1;
-                        x = 1;
-                        break;
-                    }
-                }
-                else {
-                    break;
-                }
-            }
-            else if (strip[i].empty()){
-                strip[i].push_back(j);
-                strip[i].push_back(mates[j]);
-                stripSum[i] += boxWidths[j][mates[j]];
-                checked[j] = 1;
-                checked[mates[j]] = 1;
-                x = 1;
-                break;
-            }
-
-        }
-        if(x == 1) {
-            x = 0;
-            j = -1;
-        }
-    }
-
-    cout << "Strips:\n";
-    for(i = 0; i < strip.size(); ++i){
-        if(!strip[i].empty()){
[…]

### 2017-09-14 packing.h

@@ -10,8 +10,6 @@ packing.h
 #include <vector>
 using namespace std;
 
-void packStripsSmallest(int numScores, int numBox, int maxStripWidth, vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths);
-
 void packStripsMIS(int numBox, int maxStripWidth, vector<vector<int> > &adjMatrix, vector<vector<int> > &mateInduced, vector<vector<int> > &boxWidths);
 
 void weakMatchPath(int vacant, int numScores, vector<int> &matchList, vector<int> &mates);
@@ -40,6 +38,6 @@ void packStripsNFDScores(int vacant, int numBox, int maxStripWidth, vector<vecto
 
 void packStripsNFIScores(int vacant, int numBox, int maxStripWidth, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths);
 
-void packStripsSmallestSearch(int numScores, int numBox, int maxStripWidth, vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths);
+void packStripsSmallest(int numScores, int numBox, int maxStripWidth, vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths);
 
 #endif

### 2017-09-15 main.cpp
no change

@@ -161,8 +161,8 @@ int main(int argc, char **argv){
 
 
 
-        packStripsSmallest(numScores, numBox, maxStripWidth, mates, adjMatrix, boxWidths);
-        continue; //do not do MTGMA/MIS/FCA/PATCH
+        //packStripsSmallest(numScores, numBox, maxStripWidth, mates, adjMatrix, boxWidths);
+        //continue; //do not do MTGMA/MIS/FCA/PATCH
 
         //endregion
 

### 2017-09-29 docs/main.tex
added packing section
rough draft - need to proof read and edit

@@
 	Box & \multicolumn{2}{|c|}{Scores} & Box Width \\ \hline
-	1 & 0 & 6 & 314 \\ \hline
+	1 & 0 & 6 & 341 \\ \hline
 	2 & 1 & 10 & 372 \\ \hline
@@
 
+\section{Packing}
+
+One of the algorithms currently implemented into the program packs the boxes into strips by aligning each score next to the smallest possible score avaialable.
+Each strip is packed in turn, and the box with the smallest score that has not yet been packed is the first to be placed at the beginning of the strip.
+We then search through the list of remaining scores in non-decreasing order to find the smallest score that can be feasibly placed next to the score at the end of the first strip, and whose corresponding box width fits onto the strip.
+If such a box is found, we add it to the strip, and repeat.
+Once the first strip is fully packed, either because there are no scores that meet the minimum score separation constraint, or because the remaining box widths cannot fit onto the strip, we move onto the next strip.
+This continues until all of the boxes have been packed.
+
+There are also functions that perform best-fit, first-fit, or next-fit algorithms on box widths sorted in both increasing and decreasing order of widths.
+
 \section{Improvements}
@@
 	\item User input - users can create a simple text file containing score width, mates and box widths to use with the program.
-
-\end{itemize}
-
-\section{Things to find out/do}
-\begin{itemize}
-	\item What are the industry standard strip lengths?
-	\item Goulimis $n$ = 10, is this true? Are there cases where more boxes are needed?
-	\item Current speed of scoring in industry
-	\item What happens before/after scoring in industry?
-	\item Output to csv file?
-	\item Calculate complexity
-	\item Martello and Toth (1990b) MTP algorithm, adapt with additional constraints
-	\item Exemptions on threshold, what if the instance in infeasible due to one box, can that box be held back and attempt to use in the next instance? Or can it still be used, but scoring run slower?
-	\item How many scoring knives are used?
-	\begin{itemize}
-		\item If only one set of scoring knives is used, then are the boxes placed on a conveyor belt? Does this affect the time?
-		\item If there are a specific number of scoring knives used, should we look at how many boxes are on each strip?
-I.e.
-if there are 4 scoring knives, then there should be only 4 scores on the strip, even if there is space available left on the strip?
-
-	\end{itemize}
 

### 2017-09-29 mbahra.cpp
changed box width output in createInstance and createInstanceUser functions

@@ -48,6 +48,7 @@ void createInstance(int threshold, int minWidth, int maxWidth, int minBoxWidth, 
 
     int i, j, k;
     vector<int> randOrder;
+    vector<int> checkBox(numScores, 0);
 
     //Create random values to be used as score widths, put in allScores vector (except last two elements)
     for (i = 0; i < numScores - 2; ++i) {
@@ -95,14 +96,14 @@ void createInstance(int threshold, int minWidth, int maxWidth, int minBoxWidth, 
         adjMatrix[randOrder[2 * i + 1]][randOrder[2 * i]] = 2;
     }
 
-    cout << "AdjMatrix:\n";
+    /*cout << "AdjMatrix:\n";
     for(i = 0; i < numScores; ++i){
         for(j = 0; j < numScores; ++j){
             cout << adjMatrix[i][j] << " ";
         }
         cout << endl;
     }
-    cout << endl << endl;
+    cout << endl << endl;*/
 
 
 
@@ -136,12 +137,13 @@ void createInstance(int threshold, int minWidth, int maxWidth, int minBoxWidth, 
 
     cout << "Box Widths:\n";
     for(i = 0; i < numScores; ++i){
-        for(j = 0; j < numScores; ++j){
-            cout << boxWidths[i][j] << "  ";
+        if(checkBox[i] == 1){
+            continue;
         }
-        cout << endl;
+        cout << i << "-" << mates[i] << ": " << boxWidths[i][mates[i]] << endl;
+        checkBox[i] = 1;
+        checkBox[mates[i]] = 1;
     }
-    cout << endl;
 
     k = 1;
     for(i = 0; i < numScores; ++i){
@@ -170,6 +172,7 @@ void createInstance(int threshold, int minWidth, int maxWidth, int minBoxWidth, 
 void createInstanceUser(int threshold, int numScores, vector<int> &allScores, vector<vector<int> > &userInput, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes){
 
     int i, j, m1, m2, k;
+    vector<int> checkBox(numScores, 0);
 
     for(i = 0; i < userInput.size(); ++i){
         for(j = 0; j < userInput[i].size() - 1; ++j){
@@ -226,12 +229,13 @@ void createInstanceUser(int threshold, int numScores, vector<int> &allScores, ve
 
     cout << "BoxWidths:\n";
[…]

### 2017-12-06 main.cpp
added new vector<vector<int> > populationSum, updated function statement

@@ -54,6 +54,7 @@ int main(int argc, char **argv){
     //vector<int> stripSum(numBox, 0);
     //vector<vector<int> > strip(numBox);
     vector<vector<vector<int> > > population;
+    vector<vector<int> > populationSum;
     int swapType;
     int feasible; //bool?
     int moveType;
@@ -71,7 +72,7 @@ int main(int argc, char **argv){
 
     createInstance(threshold, minWidth, maxWidth, minBoxWidth, maxBoxWidth, numScores, numBox, totalBoxWidth, allScores, adjMatrix, mates, boxWidths, allBoxes);
 
-    createInitialPopulation(numScores, numBox, maxBoxWidth, maxStripWidth, allScores, adjMatrix, mates, boxWidths, population);
+    createInitialPopulation(numScores, numBox, maxBoxWidth, maxStripWidth, allScores, mates, adjMatrix, boxWidths, populationSum, population);
 
 
     endTime = clock();

### 2017-12-06 packing.cpp
added new functions mutation, local search, partialFFD, createInitialPopulation, FFD, MBAHRA

@@ -23,16 +23,17 @@ int lowerBound(double totalBoxWidth, int maxStripWidth){
     return lBound;
 }
 
-void FFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip){
+void FFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<int> &mates,
+         vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip){
 
     int i, j, mini, k, l;
     int min = 0;
     int max = maxBoxWidth;
-    vector<int> boxDecrease;
+    vector<int> boxOrder;
     vector<int> checked(numScores, 0);
 
 
-    while(boxDecrease.size() < numBox) {
+    while(boxOrder.size() < numBox) {
         for (i = 0; i < numScores; ++i) {
             if(checked[i] == 1){
                 continue;
@@ -42,46 +43,47 @@ void FFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<v
                 mini = i;
             }
         }
-        boxDecrease.push_back(mini);
+        boxOrder.push_back(mini);
         checked[mini] = 1;
         checked[mates[mini]] = 1;
         max = min;
         min = 0;
     }
 
+
     cout << "Box decrease:\n";
-    for(i = 0; i < boxDecrease.size(); ++i){
-        cout << boxDecrease[i] << " ";
+    for(i = 0; i < boxOrder.size(); ++i){
+        cout << boxOrder[i] << " ";
     }
     cout << endl << endl;
 
-    strip[0].push_back(boxDecrease[0]);
-    strip[0].push_back(mates[boxDecrease[0]]);
-    stripSum[0] += boxWidths[boxDecrease[0]][mates[boxDecrease[0]]];
+    strip[0].push_back(boxOrder[0]);
+    strip[0].push_back(mates[boxOrder[0]]);
+    stripSum[0] += boxWidths[boxOrder[0]][mates[boxOrder[0]]];
 
 
-    for(j = 1; j < boxDecrease.size(); ++j){
+    for(j = 1; j < boxOrder.size(); ++j){
         for(i = 0; i < strip.size(); ++i){
             if(!strip[i].empty()){
[…]

### 2017-12-06 packing.h

@@ -15,14 +15,25 @@ void swap(int &a, int &b);
 
 int lowerBound(double totalBoxWidth, int maxStripWidth);
 
-void FFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void FFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<int> &mates,
+         vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
-void createInitialPopulation(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<vector<int> > > &population);
+void partialFFD(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &mates, vector<vector<int> > &adjMatrix,
+                vector<vector<int> > &boxWidths, vector<int> &partialBoxes, vector<int> &partialSum, vector<vector<int> > &partialSol);
 
-void mutation(int maxBoxWidth, int maxStripWidth, vector<int> &allScores, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void createInitialPopulation(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<int> &allScores,
+                             vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths,
+                             vector<vector<int> > &populationSum, vector<vector<vector<int> > > &population);
 
-void localSearch(int maxBoxWidth, int maxStripWidth, vector<int> &allScores, vector<vector<int> > &boxWidths, vector<int> &stripSumX, vector<vector<int> > &stripX, vector<int> &stripSumY, vector<vector<int> > &stripY);
 
-void MBAHRA(int swapType, int moveType, int &feasible, int i1, int a1, int b1, int j1, int c1, int d1, vector<int> &allScores, vector<vector<int> > &boxWidths, vector<vector<int> > &stripX, vector<vector<int> > &stripY, vector<int> &stripSumX, vector<int> &stripSumY);
[…]

### 2017-12-06 packing.cpp
nochange

@@ -245,7 +245,7 @@ void createInitialPopulation(int numScores, int numBox, int maxBoxWidth, int max
 
     population.push_back(strip);
     populationSum.push_back(stripSum);
-    
+
 }
 
 void mutation(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &allScores, vector<int> &mates,

### 2017-12-07 paper/paper.tex
paper for IWOCA

\documentclass{article}

% Algorithms
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\IndStatex}[1][1]{\Statex\hspace{6mm}}
\newcommand{\IndIndStatex}[1][1]{\Statex\hspace{12mm}}
\newcommand{\IndIndIndStatex}[1][1]{\Statex\hspace{18mm}}

% Contains advanced math extensions
\usepackage{amsmath}

% Introduces the *proof* environment and the \theoremstyle command
\usepackage{amsthm}

% Adds new symbols to be used in math mode, e.g. \mathbb
\usepackage{amssymb}

% To declare multiple authors
\usepackage{authblk}

% Provides extra comands as well as optimisation for producing tables
\usepackage{booktabs}

% Allows customisation of appearance and placements for figures/tables etc.
\usepackage{caption}

% Adds support for arbitrarily-deep nested lists
\usepackage{enumitem}

% Improves the interface for defining floating objects such as figures/tables
\usepackage{float}

\usepackage{fullpage}

% For easy management of document margins and the document page size
%\usepackage{geometry}

% Allows insertion of graphic files within a document
\usepackage{graphicx}

% Manage links within the document or to any URL when you compile in PDF
\usepackage{hyperref}

% Successor of amsmath
\usepackage{mathtools}

% No indentation, space between paragraphs
\usepackage{parskip}

%Include standalone .tex files
\usepackage{standalone}

% Define multiple floats (figures/tables) within one environment with individual captions 1a, 1b etc
\usepackage{subcaption}

\usepackage{tikz}

\usepackage{wrapfig}

%Theorem style
\theoremstyle{plain}% default
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]

\theoremstyle{definition}
\newtheorem{defn}{Definition}[section]
\newtheorem{proposition}{Proposition}[defn]
\newtheorem{exmp}{Example}[section]

\title{Paper for IWOCA}
\author{Asyl L. Hawa}
\affil{\small{\textit{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, CF24 4AG}}}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}

\end{document}
\grid

### 2017-12-07 packing.cpp
added FFRandom function

@@ -23,15 +23,12 @@ int lowerBound(double totalBoxWidth, int maxStripWidth){
     return lBound;
 }
 
-void FFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<int> &mates,
-         vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip){
+void FFDecreasing(int numScores, int numBox, int maxBoxWidth, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &boxOrder){
 
-    int i, j, mini, k, l;
+    int i, mini;
     int min = 0;
     int max = maxBoxWidth;
-    vector<int> boxOrder;
     vector<int> checked(numScores, 0);
-
 
     while(boxOrder.size() < numBox) {
         for (i = 0; i < numScores; ++i) {
@@ -51,11 +48,52 @@ void FFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<i
     }
 
 
-    cout << "Box decrease:\n";
+}
+
+void FFRandom(int numScores, int numBox, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &boxOrder){
+
+    int i, r;
+    vector<int> checked(numScores, 0);
+
+    while(boxOrder.size() < numBox){
+        r = rand() % numScores;
+        if(checked[r] == 1){
+            continue;
+        }
+        if(r < mates[r]){
+            boxOrder.push_back(r);
+            checked[r] = 1;
+            checked[mates[r]] = 1;
+        }
+        else{
+            boxOrder.push_back(mates[r]);
+            checked[r] = 1;
+            checked[mates[r]] = 1;
+        }
+    }
+
+
+
+}
+
+void FFShell(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<int> &mates,
+         vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip, bool decrease){
+
+    int i, j, k, l;
+    vector<int> boxOrder;
+
+    if(decrease){
+        FFDecreasing(numScores, numBox, maxBoxWidth, mates, boxWidths, boxOrder);
+    }
+    else{
+        FFRandom(numScores, numBox, mates, boxWidths, boxOrder);
+    }
+
+    /*cout << "Box Order:\n";
     for(i = 0; i < boxOrder.size(); ++i){
[…]

### 2017-12-07 packing.h

@@ -15,11 +15,17 @@ void swap(int &a, int &b);
 
 int lowerBound(double totalBoxWidth, int maxStripWidth);
 
-void FFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<int> &mates,
-         vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void FFDecreasing(int numScores, int numBox, int maxBoxWidth, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &boxOrder);
+
+void FFRandom(int numScores, int numBox, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &boxOrder);
+
+void FFShell(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<int> &mates,
+         vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip, bool decrease);
+
 
 void partialFFD(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &mates, vector<vector<int> > &adjMatrix,
                 vector<vector<int> > &boxWidths, vector<int> &partialBoxes, vector<int> &partialSum, vector<vector<int> > &partialSol);
+
 
 void createInitialPopulation(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vector<int> &allScores,
                              vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths,

### 2017-12-08 base.cpp
changed order of parameters in createInstance function

@@ -9,9 +9,11 @@ Evolutionary Algorithm with Local Search
 #include "base.h"
 using namespace std;
 
-void createInstance(int threshold, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, int numScores, int numBox, double &totalBoxWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes){
+void createInstance(int numScores, int numBox, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, double &totalBoxWidth,
+                    vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes){
 
     int i, j, k;
+    int threshold = 70;
     int count = 1;
     vector<int> randOrder;
     vector<int> checkBox(numScores, 0);

### 2017-12-08 base.h

@@ -12,9 +12,7 @@ Evolutionary Algorithm with Local Search
 #include <vector>
 using namespace std;
 
-void createInstance(int threshold, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, int numScores, int numBox, double &totalBoxWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes);
-
-
-
+void createInstance(int numScores, int numBox, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, double &totalBoxWidth,
+                    vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes);
 
 #endif

### 2017-12-08 main.cpp
removed unnecessary variables, added EA function

@@ -40,11 +40,10 @@ int main(int argc, char **argv){
     int maxStripWidth = atoi(argv[6]);
     int randomSeed = atoi(argv[7]); //random seed
 
-    int i, j, k, q, n;
+    int i, j, q, n;
     int instance; //counter for instances loop
     int numScores = numBox * 2; //number of scores, 2 per box (1 either side), last two scores are dominating vertices
-    int threshold = 70; //adjacency threshold of scores, minimum knife distance
-    int vacant = 999;
+    //int threshold = 70; //adjacency threshold of scores, minimum knife distance
     vector<int> allScores;
     vector<vector<int> > adjMatrix(numScores, vector<int>(numScores, 0)); //adjaceny matrix (createInstance, MTGMA, MIS, FCA)
     vector<int> mates(numScores, 0); //contains vertex index for mates, e.g if vertex 0 is mates with vertex 4, then mates[0] = 4 (createInstance, MIS)
@@ -55,9 +54,6 @@ int main(int argc, char **argv){
     //vector<vector<int> > strip(numBox);
     vector<vector<vector<int> > > population;
     vector<vector<int> > populationSum;
-    int swapType;
-    int feasible; //bool?
-    int moveType;
     //endregion
 
 
@@ -70,9 +66,11 @@ int main(int argc, char **argv){
     time_t startTime, endTime; //start clock
     startTime = clock();
 
-    createInstance(threshold, minWidth, maxWidth, minBoxWidth, maxBoxWidth, numScores, numBox, totalBoxWidth, allScores, adjMatrix, mates, boxWidths, allBoxes);
+    createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths, allBoxes);
 
     createInitialPopulation(numScores, numBox, maxBoxWidth, maxStripWidth, allScores, mates, adjMatrix, boxWidths, populationSum, population);
+
+    EA(numScores, maxBoxWidth, maxStripWidth, allScores, mates, adjMatrix, boxWidths, populationSum, population);
 
 
     endTime = clock();

### 2017-12-08 packing.cpp
added EA and GGA functions

@@ -154,9 +154,9 @@ void FFShell(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, vect
         }
         cout << endl;
     }
-    cout << endl;
+    cout << endl;*/
 
-    cout << "Strip" << setw(8) << "Width" << setw(12) << "Residual\n";
+    /*cout << "Strip" << setw(8) << "Width" << setw(12) << "Residual\n";
     for(i = 0; i < stripSum.size(); ++i){
         if(stripSum[i] !=0) {
             cout << i << setw(9) << stripSum[i] << setw(9) << maxStripWidth - stripSum[i] << endl;
@@ -251,7 +251,7 @@ void partialFFD(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &
     //cout << "After REPAIR FFD: " << partialSol.size() << " strips\n";
 
 
-    /*cout << "REPAIR Strips FFD (scores):\n";
+    cout << "REPAIR Strips FFD (scores):\n";
     for(i = 0; i < partialSol.size(); ++i){
         cout << "Strip " << i << ": ";
         for(j = 0; j < partialSol[i].size(); ++j){
@@ -265,7 +265,7 @@ void partialFFD(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &
     for(i = 0; i < partialSum.size(); ++i){
         cout << partialSum[i] << " ";
     }
-    cout << endl << endl;*/
+    cout << endl << endl;
 
 }
 
@@ -273,7 +273,7 @@ void createInitialPopulation(int numScores, int numBox, int maxBoxWidth, int max
                              vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths,
                              vector<vector<int> > &populationSum, vector<vector<vector<int> > > &population){
 
-    int i, j, k;
+    int i, j, k, l;
     vector<vector<int> > strip(numBox);
     vector<int> stripSum(numBox, 0);
 
@@ -301,17 +301,21 @@ void createInitialPopulation(int numScores, int numBox, int maxBoxWidth, int max
 
     }
 
-    for(k = 0; k < population.size(); ++k){
-        cout << "set:\n";
+    /*for(k = 0; k < population.size(); ++k){
+        cout << "Population " << k << ":\n";
         for(i = 0; i < population[k].size(); ++i){
             for(j = 0; j < population[k][i].size(); ++j){
                 cout << population[k][i][j] << " ";
             }
[…]

### 2017-12-08 packing.h

@@ -41,5 +41,11 @@ void localSearch(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> 
 
 void MBAHRA(int swapType, int moveType, int &feasible, int i1, int a1, int b1, int j1, int c1, int d1, vector<int> &allScores,
             vector<vector<int> > &boxWidths, vector<int> &stripSumX, vector<vector<int> > &stripX, vector<int> &stripSumY, vector<vector<int> > &stripY);
+
+void EA(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
+        vector<vector<int> > &boxWidths, vector<vector<int> > &populationSum, vector<vector<vector<int> > > &population);
+
+void GGA(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
+         vector<vector<int> > &boxWidths, vector<int> &stripSumX, vector<vector<int> > &stripX, vector<int> &stripSumY, vector<vector<int> > &stripY);
 #endif
 

### 2017-12-11 paper/ffdexact/baseexact.cpp
code for ffd using mbahra algorithm

@@ -1,0 +1,294 @@
+/*--------------/
+ALH
+base.cpp
+12/10/17
+/--------------*/
+#include <algorithm>
+#include <iomanip>
+#include "baseexact.h"
+using namespace std;
+
+void resetVectors(int numScores, int numBox, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes, vector<int> &stripSum, vector<vector<int> > &strip){
+
+    int i, j;
+
+    for(i = 0; i < numScores; ++i){
+        mates[i] = 0;
+        for(j = 0; j < numScores; ++j){
+            adjMatrix[i][j] = 0;
+            boxWidths[i][j] = 0;
+            allBoxes[i][j] = 0;
+        }
+    }
+
+    while(!strip.empty()){
+        strip.pop_back();
+    }
+
+    while(!stripSum.empty()){
+        stripSum.pop_back();
+    }
+
+    vector<int> temp;
+    for(i = 0; i < numBox; ++i){
+        strip.push_back(temp);
+        stripSum.push_back(0);
+    }
+
+
+
+}
+
+void clearVectors(vector<int> &allScores, vector<int> &stripNumBoxes, vector<int> &stripSumX, vector<int> &stripSumY, vector<vector<int> > &stripX, vector<vector<int> > &stripY){
+
+    allScores.clear();
+    stripNumBoxes.clear();
+    stripSumX.clear();
+    stripSumY.clear();
+    stripX.clear();
+    stripY.clear();
+}
+
+void createInstance(int threshold, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, int numScores, int numBox, double &totalBoxWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes){
+
+    int i, j, k;
+    int count = 1;
+    vector<int> randOrder;
+    vector<int> checkBox(numScores, 0);
+    totalBoxWidth = 0.0;
+
+    //Create random values to be used as score widths, put in allScores vector (except last two elements)
+    for (i = 0; i < numScores; ++i) {
+        allScores.push_back(rand() % (maxWidth - minWidth + 1) + minWidth);
+    }
+
+
+    //Sort all of the scores in the allScores vector in ascending order
[…]

### 2017-12-11 paper/ffdexact/baseexact.h

@@ -1,0 +1,24 @@
+/*--------------/
+ALH
+base.h
+12/10/17
+/--------------*/
+
+#ifndef BASE_H
+#define BASE_H
+
+#include <iostream>
+#include <vector>
+using namespace std;
+
+void resetVectors(int numScores, int numBox, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes, vector<int> &stripSum, vector<vector<int> > &strip);
+
+void clearVectors(vector<int> &allScores, vector<int> &stripNumBoxes, vector<int> &stripSumX, vector<int> &stripSumY, vector<vector<int> > &stripX, vector<vector<int> > &stripY);
+
+void createInstance(int threshold, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, int numScores, int numBox, double &totalBoxWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes);
+
+void createInstanceUser(int threshold, int numScores, double &totalBoxWidth, vector<int> &allScores, vector<vector<int> > &userInput, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes);
+
+
+
+#endif

### 2017-12-11 paper/ffdexact/mainexact.cpp

@@ -1,0 +1,153 @@
+/*--------------/
+ALH
+mainexact.cpp
+11/12/2017
+/--------------*/
+#include <iostream>
+#include <fstream>
+#include <ctime>
+using namespace std;
+
+#include "baseexact.h"
+#include "packingexact.h"
+
+int main(int argc, char **argv){
+    //region USAGE - ARGUMENTS REQUIRED
+    if(argc < 8){
+        cout << "Minimum Score Separation Problem: MBAHRA.\n";
+        cout << "Arguments are the following:\n";
+        cout << "- Number of instances (integer)\n";
+        cout << "- Number of boxes (integer)\n";
+        cout << "- Minimum width of scores (millimeters, min = 1)\n";
+        cout << "- Maximum width of scores (millimeters, max = 70)\n";
+        cout << "- Minimum width of boxes (millimeters, min = 140)\n";
+        cout << "- Maximum width of boxes (millimeters, max = 1000)\n";
+        cout << "- Maximum width of strips (millimeters)\n";
+        cout << "- Random Seed (integer)\n";
+        cout << "- Name of input file (must have .txt extension)\n";
+        exit(1);
+    }
+    //endregion
+
+    //region VARIABLES
+    //int numInstances = atoi(argv[1]); //number of instances of mssp, use in main for loop
+    int numBox = atoi(argv[1]); //number of boxes in mssp plus 1 extra box (scores on either side of extra box will be dominating vertices, score widths = 71)
+    int minWidth = atoi(argv[2]); //minimum width of scores (millimeters)
+    int maxWidth = atoi(argv[3]); //maximum width of scores (millimeters)
+    int minBoxWidth = atoi(argv[4]); //min box width (mm)
+    int maxBoxWidth = atoi(argv[5]); //max box width (mm)
+    int maxStripWidth = atoi(argv[6]);
+    int randomSeed = atoi(argv[7]); //random seed
+
+    int i, j, k, q, n;
+    int instance; //counter for instances loop
+    int numScores = numBox * 2; //number of scores, 2 per box (1 either side), last two scores are dominating vertices
+    int threshold = 70; //adjacency threshold of scores, minimum knife distance
+    int vacant = 999;
+    vector<int> allScores;
[…]

### 2017-12-11 paper/ffdexact/packingexact.cpp

@@ -1,0 +1,1337 @@
+/*--------------/
+ALH
+packing.cpp
+12/10/17
+/--------------*/
+#include <algorithm>
+#include <cmath>
+#include <iomanip>
+#include "packingexact.h"
+using namespace std;
+
+void swap(int &a, int &b){
+    int temp = a;
+    a = b;
+    b = temp;
+}
+
+int lowerBound(double totalBoxWidth, int maxStripWidth){
+    int lBound;
+
+    lBound = ceil(totalBoxWidth/maxStripWidth);
+    return lBound;
+}
+
+int initCost(int &totalCost, int maxStripWidth, vector<int> &stripSum){
+
+    int i;
+    totalCost = 0;
+
+    for(i = 0; i < stripSum.size(); ++i){
+        totalCost += pow((maxStripWidth - stripSum[i]), 2);
+    }
+
+    return totalCost;
+
+}
+
+void packStripsFFD(int numScores, int numBox, int &totalCost, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<int> &stripNumBoxes, vector<vector<int> > &strip){
+
+    int i, j, mini, k, l;
+    int min = 0;
+    int max = maxBoxWidth;
+    int numStrips = 0;
+    int feasible;
+    vector<int> boxDecrease;
+    vector<int> checked(numScores, 0);
+
+
+    while(boxDecrease.size() < numBox) {
+        for (i = 0; i < numScores; ++i) {
+            if(checked[i] == 1){
+                continue;
+            }
+            if (boxWidths[i][mates[i]] > min && boxWidths[i][mates[i]] <= max) {
+                min = boxWidths[i][mates[i]];
+                mini = i;
+            }
+        }
+        boxDecrease.push_back(mini);
+        checked[mini] = 1;
+        checked[mates[mini]] = 1;
+        max = min;
+        min = 0;
+    }
+
+    cout << "Box decrease:\n";
+    for(i = 0; i < boxDecrease.size(); ++i){
+        cout << boxDecrease[i] << " ";
+    }
+    cout << endl << endl;
+
+    strip[0].push_back(boxDecrease[0]);
+    strip[0].push_back(mates[boxDecrease[0]]);
[…]

### 2017-12-11 paper/ffdexact/packingexact.h

@@ -1,0 +1,25 @@
+/*--------------/
+ALH
+packing.h
+12/10/17
+/--------------*/
+#ifndef PACKING_H
+#define PACKING_H
+
+#include <iostream>
+#include <vector>
+using namespace std;
+
+void swap(int &a, int &b);
+
+int lowerBound(double totalBoxWidth, int maxStripWidth);
+
+int initCost(int &totalCost, int maxStripWidth, vector<int> &stripSum);
+
+void packStripsFFD(int numScores, int numBox, int &totalCost, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<int> &stripNumBoxes, vector<vector<int> > &strip);
+
+void MBAHRA(int i1, int j1, int &feasible, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
+            vector<vector<int> > &boxWidths, vector<int> &boxDecrease, vector<int> &stripSum, vector<vector<int> > &strip);
+
+#endif
+

### 2017-12-11 paper/paper.tex
updated templates
changed from documentclass{article} to {llncs}
added alternating Hamiltonian defn, started layout

@@
-\documentclass{article}
+\documentclass{llncs}
 
-% Algorithms
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
-\newcommand{\IndStatex}[1][1]{\Statex\hspace{6mm}}
-\newcommand{\IndIndStatex}[1][1]{\Statex\hspace{12mm}}
-\newcommand{\IndIndIndStatex}[1][1]{\Statex\hspace{18mm}}
-
-% Contains advanced math extensions
-\usepackage{amsmath}
-
-% Introduces the *proof* environment and the \theoremstyle command
-\usepackage{amsthm}
-
-% Adds new symbols to be used in math mode, e.g. \mathbb
-\usepackage{amssymb}
-
-% To declare multiple authors
-\usepackage{authblk}
-
-% Provides extra comands as well as optimisation for producing tables
-\usepackage{booktabs}
-
-% Allows customisation of appearance and placements for figures/tables etc.
-\usepackage{caption}
-
-% Adds support for arbitrarily-deep nested lists
-\usepackage{enumitem}
-
-% Improves the interface for defining floating objects such as figures/tables
-\usepackage{float}
-
-\usepackage{fullpage}
-
-% For easy management of document margins and the document page size
-%\usepackage{geometry}
-
-% Allows insertion of graphic files within a document
-\usepackage{graphicx}
-
-% Manage links within the document or to any URL when you compile in PDF
-\usepackage{hyperref}
-
-% Successor of amsmath
-\usepackage{mathtools}
-
-% No indentation, space between paragraphs
-\usepackage{parskip}
-
-%Include standalone .tex files
-\usepackage{standalone}
-
-% Define multiple floats (figures/tables) within one environment with individual captions 1a, 1b etc
-\usepackage{subcaption}
-
-\usepackage{tikz}
-
-\usepackage{wrapfig}
-
-%Theorem style
-\theoremstyle{plain}% default
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[theorem]
-
-\theoremstyle{definition}
-\newtheorem{defn}{Definition}[section]
-\newtheorem{proposition}{Proposition}[defn]
-\newtheorem{exmp}{Example}[section]
+\input{includes/preamble.tex}
 
 \title{Paper for IWOCA}
-\author{Asyl L. Hawa}
-\affil{\small{\textit{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, CF24 4AG}}}
+\author{Asyl L. Hawa \and Rhyd Lewis \and Jonathan Thompson}
+\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
 \date{\today}
@@
 \begin{document}
-
 \maketitle
@@
 \section{Introduction}
+\begin{itemize}
+	\item complexity
+\end{itemize}
+
+\begin{itemize}
+	\item discuss problem with score constraints
+	\item Goulimis
+	\item packing
+\end{itemize}
+
+\section{FFD with approximate heuristic}
+
+\section{FFD with exact algorithm}
+\begin{definition}
+	Let $G(V,P\cup E)$ be an undirected graph, where $P \cap E = \emptyset$.
+Then $G$ has an alternating Hamiltonian path (or cycle) if there exists a Hamiltonian path (or cycle) on $G$ such that the successive edges are members of different edge sets, *i.e.
+if vertex $v_k$ is adjacent to vertex $v_{k-1}$ via an edge from $P$, then $v_k$ must be adjacent to vertex $v_{k+1}$ via an edge from $E$, or vice versa.
+$G$ is said to be alternating Hamiltonian if and only if there exists an alternating Hamiltonian cycle on $G$.
+(OR *i.e.
+if $\{v_{k-1}, v_k\} \in P$, then $\{v_k, v_{k+1}\} \in E$, or vice versa.)
+\end{definition}
+
+\subsection{Intro}
+\begin{itemize}
+	\item $n$ boxes, each box has two score lines, one on each side (mates)
+	\item Score width - distance between edge of box and score line
+	\item scores come in pairs
+	\item let each box be represented by two vertices, one vertex for each score
+	\item vertex weight equivalent to score width (mm)
+	\item if two scores are part of the same box, join corresponding vertices together with an edge
+	\item call this set of edges $P$, where $|P| = n$.
+	\item edges in $P$ are weighted, equivalent to box width
+	\item threshold graph: if sum of two vertices $\geq$ threshold, and vertices are not connected via an edge from $P$, i.e. $\{u, v\} \notin P$, then join vertices together via an edge
+	\item call this set of edges $T$
+	\item two sets of edges, $P$ and $T$
+	\item add dominating vertices
+	\item we want to find an alternating hamiltonian path, edges alternating between set $P$ and set $T$.
+\end{itemize}
+
+Let each box be represented by two vertices on a graph $G$, one vertex for each side of the box.
+Each vertex is assigned a value corresponding to the width of the score it represents.
+We refer to two vertices that represent either side of the same box as ``mates''.
+The boxes cannot be altered in anyway, and so vertices that are mates must be adjacent to one another.
+Thus, we have a set of edges $P$ that consists of edges between mates.
+
+As described in the introduction, let $\tau \in \mathbb{R}_{+}$ be the minimum scoring distance.
+If the sum of the values of two vertices $\{u, v\}$ is greater than or equal to $\tau$, and $\{u,v\} \notin P$, then we can connect these two vertices with an edge.
+Hence we have another set of edges $T$ consisting of edges between vertices that could ?
+
+\subsection{MTGMA}
+\begin{itemize}
+	\item need a suitable matching $M\subset E$ s.t. $|M| = n-1$ CHECK THIS NOW WE HAVE DOMINATING VERTICES
+	\item maximum cardinality matching algorithm for threshold graphs (Mahadev and Peled 1994)
+	\item modify algorithm so that duplicate edges from mates are deleted, only consider edges from matching
+	\item explain swap of mates??
+\end{itemize}
+Due to the structure of threshold graphs, there is a simple maximum cardinality matching algorithm (Mahadev and Peled, 1994) that produced a matching ?? containing suitable edges from $T$.
+
+Initially, the vertices are sorted in order of non-decreasing weights, with ties broken arbitrarily.
+Starting from the vertex with the smallest weight, attempt to match it with any vertex in its neighbourhood that has not yet been matched.
+If such a vertex is available, add the current vertex and its match to a set $I$ that keeps track of the matched vertices.
+Succesively proceed to the next largest vertex until all vertices have been assessed.
+
+\subsection{MIS}
+\begin{itemize}
+	\item either have one alternating cycle, or more than one
+	\item if one, remove extra vertices, final solution
+	\item if more than one cycle, need to find a way to join them together
+	\item need to find one edge in each cycle such that the current matches can be broken, and new matches can be made between them, creating one cycle
+\end{itemize}
+
+\subsection{FCA}
+\begin{itemize}
+	\item pair of edges from different cycles
+\end{itemize}
+
+\section{Experiments/Comparison}
+
+\section{Conclusion}
 
 \end{document}
-\grid

### 2017-12-13 main.cpp
added fitness function and variables

@@ -54,11 +54,14 @@ int main(int argc, char **argv){
     //vector<vector<int> > strip(numBox);
     vector<vector<vector<int> > > population;
     vector<vector<int> > populationSum;
+    double parent1cost;
+    double parent2cost;
     //endregion
 
 
 
-    cout << "MSSP - MBAHRA\n-------------\n";
+    cout << "local search\n-------------\n";
+
     //srand(unsigned(time(NULL))); //seed
     srand(randomSeed);
 
@@ -70,7 +73,7 @@ int main(int argc, char **argv){
 
     createInitialPopulation(numScores, numBox, maxBoxWidth, maxStripWidth, allScores, mates, adjMatrix, boxWidths, populationSum, population);
 
-    EA(numScores, maxBoxWidth, maxStripWidth, allScores, mates, adjMatrix, boxWidths, populationSum, population);
+    EA(numScores, maxBoxWidth, maxStripWidth, parent1cost, parent2cost, allScores, mates, adjMatrix, boxWidths, populationSum, population);
 
 
     endTime = clock();

### 2017-12-13 packing.cpp

@@ -23,6 +23,23 @@ int lowerBound(double totalBoxWidth, int maxStripWidth){
     return lBound;
 }
 
+double fitness (int maxStripWidth, vector<int> &stripSum, vector<vector<int> > &strip){
+
+    int i;
+    double total = 0.0;
+    double final;
+
+    for(i = 0; i < strip.size(); ++i){
+        double a = static_cast<double>(stripSum[i]) / static_cast<double>(maxStripWidth);
+        total += pow(a, 2);
+    }
+
+    final = total / static_cast<double>(strip.size());
+
+    return final;
+
+}
+
 void FFDecreasing(int numScores, int numBox, int maxBoxWidth, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &boxOrder){
 
     int i, mini;
@@ -251,7 +268,7 @@ void partialFFD(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &
     //cout << "After REPAIR FFD: " << partialSol.size() << " strips\n";
 
 
-    cout << "REPAIR Strips FFD (scores):\n";
+    /*cout << "REPAIR Strips FFD (scores):\n";
     for(i = 0; i < partialSol.size(); ++i){
         cout << "Strip " << i << ": ";
         for(j = 0; j < partialSol[i].size(); ++j){
@@ -265,7 +282,7 @@ void partialFFD(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &
     for(i = 0; i < partialSum.size(); ++i){
         cout << partialSum[i] << " ";
     }
-    cout << endl << endl;
+    cout << endl << endl;*/
 
 }
 
@@ -597,9 +614,9 @@ void localSearch(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> 
     //endregion
 
     End:
-    cout << "Local Search complete\n-------------------\n";
+    //cout << "Local Search complete\n-------------------\n";
     if(feasible == 2){
-        cout << "stripY emptied\n\n";
+        /*cout << "stripY emptied\n\n";
         cout << "stripX:\n";
         for(i = 0; i < stripX.size(); ++i){
             for(j = 0; j < stripX[i].size(); ++j){
@@ -611,7 +628,7 @@ void localSearch(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> 
         for(i = 0; i < stripSumX.size(); ++i){
             cout << stripSumX[i] << " ";
         }
[…]

### 2017-12-13 packing.h

@@ -15,6 +15,8 @@ void swap(int &a, int &b);
 
 int lowerBound(double totalBoxWidth, int maxStripWidth);
 
+double fitness (int maxStripWidth, vector<int> &stripSum, vector<vector<int> > &strip);
+
 void FFDecreasing(int numScores, int numBox, int maxBoxWidth, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &boxOrder);
 
 void FFRandom(int numScores, int numBox, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &boxOrder);
@@ -42,7 +44,7 @@ void localSearch(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> 
 void MBAHRA(int swapType, int moveType, int &feasible, int i1, int a1, int b1, int j1, int c1, int d1, vector<int> &allScores,
             vector<vector<int> > &boxWidths, vector<int> &stripSumX, vector<vector<int> > &stripX, vector<int> &stripSumY, vector<vector<int> > &stripY);
 
-void EA(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
+void EA(int numScores, int maxBoxWidth, int maxStripWidth, double &parent1cost, double &parent2cost, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
         vector<vector<int> > &boxWidths, vector<vector<int> > &populationSum, vector<vector<vector<int> > > &population);
 
 void GGA(int numScores, int maxBoxWidth, int maxStripWidth, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,

### 2017-12-13 paper/paper.tex
updated sections

@@
 
+\begin{abstract}
+	Abstract
+\end{abstract}
+
 \section{Introduction}
-\begin{itemize}
-	\item complexity
-\end{itemize}
-
-\begin{itemize}
-	\item discuss problem with score constraints
-	\item Goulimis
-	\item packing
-\end{itemize}
+\begin{enumerate}
+	\item Goulimis (2004)
+	\item boxes are scored in specfici places to make folding easier 
+	\item only consider outermost scores, although box may have many 
+	\item machine explanation, scoring knives cannot be placed too close together
+	\item therefore we have a score constraint/minimum knife distance
+	\item strips of material of a fixed length
+	\item minimise waste whilst adhering to the score constraints
+	\item feasible arrangement of boxes
+	\item boxes have same heights, different widths
+	\item therefore have a strip packing/bpp with an additional constraint
+	\item explain rest of paper
+\end{enumerate}
 
 \section{FFD with approximate heuristic}
+\begin{enumerate}
+	\item background on FF/FFD
+	\item explain how FFD operates without score constraints (simple)
+	\item complexity/lower bound
+	\item explain FFD with score constraint (algorithm)
+	\item pros and cons: speed, however there may be a solution that exists that cannot be found due to boxes being fixed in place
+\end{enumerate}
 
 \section{FFD with exact algorithm}
+\begin{enumerate}
+	\item extension of the above, however we include an algorithm that can find a feasible alignment of boxes with score constraints if one exists
+	\item if a box can fit onto a strip, instead of attempting to place on the end, we apply this algorithm
+	\item therefore unlike the heuristic above, boxes are not fixed in place, all boxes can be reordered
+	\item then go on to explain mbahra + output of solution
+	\item pros and cons? polynomial time, however it means that it cannot be done continuously
+	\item i.e. the heuristic can be applied during scoring, but with the exact alg, a full solution must be found before any scoring can occur, as boxes can be moved around
+\end{enumerate}
+
 \begin{definition}
+	% Alternating Hamiltonian Path/cycle
 	Let $G(V,P\cup E)$ be an undirected graph, where $P \cap E = \emptyset$.
@@
 \subsection{Intro}
+\begin{enumerate}
+	\item Notation
+	\item Creating two sets of edges
+	\item Alternating Hamiltonian Path/cycle
+\end{enumerate}
 \begin{itemize}
@@
 	\item we want to find an alternating hamiltonian path, edges alternating between set $P$ and set $T$.
+	\item -----------------------
+	\item each box has same height, varying width (introduction?)
+	\item vertices have values corresponding to the score width
+	\item two vertices that represent either side of the same box are called ``mates''
+	\item add dominating vertices that are mates with value = mkd, removed at the end
+	\item so graph has $2n + 2$ vertices
+	\item mates must be adjacent to one another, so we have a set of edges $P$ that consists of edges between mates
+	\item each of these edges are weighted, value corresponds to boxwidth
+	\item seconds set of edges $T$: if the sum of two score widths from different boxes is greater than or equal to the mkd, the corresponding vertices will be connected with an edge 
+	\item called these matched
+	\item or if the sum of two vertices that are not adjacent via an edge from $P$ is $\geq$ mkd, connect via an edge
+	\item picture threshold graph colours or dots?	
 \end{itemize}
 
+--------------------------------\\
 Let each box be represented by two vertices on a graph $G$, one vertex for each side of the box.
@@
 \subsection{MTGMA}
+\begin{enumerate}
+	\item explain max cardinality matching algorithm excluding edges from $P$
+	\item swap of mates
+	\item if $|M| = n$, continue, else fail, no feasible arrangement of the boxes exists
+\end{enumerate}
 \begin{itemize}
@@
 \end{itemize}
-Due to the structure of threshold graphs, there is a simple maximum cardinality matching algorithm (Mahadev and Peled, 1994) that produced a matching ?? containing suitable edges from $T$.
+
+There is a simple maximum cardinality matching algorithm (Mahadev and Peled, 1994) that produced a matching ?? containing suitable edges from $T$.
 
@@
 \subsection{MIS}
-\begin{itemize}
-	\item either have one alternating cycle, or more than one
-	\item if one, remove extra vertices, final solution
-	\item if more than one cycle, need to find a way to join them together
-	\item need to find one edge in each cycle such that the current matches can be broken, and new matches can be made between them, creating one cycle
-\end{itemize}
+\begin{enumerate}
+	\item new graph, each vertex has degree 2 (connected to one vertex via edge from $P$ and one vertex via edge from $M$)
+	\item either one cycle, remove dominating vertices
+	\item 2+ cycles, need to connect all cycles together
+\end{enumerate}
 
 \subsection{FCA}
-\begin{itemize}
-	\item pair of edges from different cycles
-\end{itemize}
+\begin{enumerate}
+	\item find pairs of vertices in each cycle connected via a matching edge that can be broken and rematched
+	\item lower vertex adj to higher vertex of other cycle's edge
+	\item connect cycles together, remove dominating vertices
+	\item if cycles cannot be connected, then no feasible arrangement of all boxes exists
+\end{enumerate}
+
+\subsection{Other}
+\begin{enumerate}
+	\item benefits of this alg wrt FFD/BPP?
+\end{enumerate}
 
@@
 
+\section{Other}
+\begin{itemize}
+	\item complexity
+\end{itemize}
+
 \end{document}

### 2017-12-13 paper/ffdexact/baseexact.cpp
commented out cout statements, rearrangement of parameters in functions

@@ -8,7 +8,8 @@ base.cpp
 #include "baseexact.h"
 using namespace std;
 
-void resetVectors(int numScores, int numBox, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes, vector<int> &stripSum, vector<vector<int> > &strip){
+void resetVectors(int numScores, int numBox, vector<int> &allScores, vector<int> &mates,
+                  vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip){
 
     int i, j;
 
@@ -17,7 +18,6 @@ void resetVectors(int numScores, int numBox, vector<vector<int> > &adjMatrix, ve
         for(j = 0; j < numScores; ++j){
             adjMatrix[i][j] = 0;
             boxWidths[i][j] = 0;
-            allBoxes[i][j] = 0;
         }
     }
 
@@ -35,23 +35,18 @@ void resetVectors(int numScores, int numBox, vector<vector<int> > &adjMatrix, ve
         stripSum.push_back(0);
     }
 
-
-
-}
-
-void clearVectors(vector<int> &allScores, vector<int> &stripNumBoxes, vector<int> &stripSumX, vector<int> &stripSumY, vector<vector<int> > &stripX, vector<vector<int> > &stripY){
-
     allScores.clear();
-    stripNumBoxes.clear();
-    stripSumX.clear();
-    stripSumY.clear();
-    stripX.clear();
-    stripY.clear();
+
+
+
 }
 
-void createInstance(int threshold, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, int numScores, int numBox, double &totalBoxWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes){
 
-    int i, j, k;
+void createInstance(int numScores, int numBox, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, double &totalBoxWidth,
+                    vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths){
+
+    int i, j;
+    int threshold = 70;
     int count = 1;
     vector<int> randOrder;
     vector<int> checkBox(numScores, 0);
[…]

### 2017-12-13 paper/ffdexact/baseexact.h

@@ -11,11 +11,11 @@ base.h
 #include <vector>
 using namespace std;
 
-void resetVectors(int numScores, int numBox, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes, vector<int> &stripSum, vector<vector<int> > &strip);
+void resetVectors(int numScores, int numBox, vector<int> &allScores, vector<int> &mates,
+                  vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
-void clearVectors(vector<int> &allScores, vector<int> &stripNumBoxes, vector<int> &stripSumX, vector<int> &stripSumY, vector<vector<int> > &stripX, vector<vector<int> > &stripY);
-
-void createInstance(int threshold, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, int numScores, int numBox, double &totalBoxWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes);
+void createInstance(int numScores, int numBox, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, double &totalBoxWidth,
+                    vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths);
 
 void createInstanceUser(int threshold, int numScores, double &totalBoxWidth, vector<int> &allScores, vector<vector<int> > &userInput, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<vector<int> > &allBoxes);
 

### 2017-12-13 paper/ffdexact/mainexact.cpp

@@ -39,16 +39,13 @@ int main(int argc, char **argv){
     int maxStripWidth = atoi(argv[6]);
     int randomSeed = atoi(argv[7]); //random seed
 
-    int i, j, k, q, n;
+    int i, j;
     int instance; //counter for instances loop
     int numScores = numBox * 2; //number of scores, 2 per box (1 either side), last two scores are dominating vertices
-    int threshold = 70; //adjacency threshold of scores, minimum knife distance
-    int vacant = 999;
     vector<int> allScores;
     vector<vector<int> > adjMatrix(numScores, vector<int>(numScores, 0)); //adjaceny matrix (createInstance, MTGMA, MIS, FCA)
     vector<int> mates(numScores, 0); //contains vertex index for mates, e.g if vertex 0 is mates with vertex 4, then mates[0] = 4 (createInstance, MIS)
     vector<vector<int> > boxWidths(numScores, vector<int>(numScores, 0)); // holds widths in mm for the widths of boxes
-    vector<vector<int> > allBoxes(numScores, vector<int>(numScores, 0)); //contains values from 1 to numBox to denote which box the scores belong to
     //srand(unsigned(time(NULL))); //seed
     srand(randomSeed);
     vector<vector<int> > userInput;
@@ -57,17 +54,6 @@ int main(int argc, char **argv){
     double totalBoxWidth = 0.0;
     vector<int> stripSum(numBox, 0);
     vector<vector<int> > strip(numBox);
-    vector<int> stripSum2(numBox, 0);
-    vector<vector<int> > strip2(numBox);
-    vector<int> stripNumBoxes;
-    vector<int> stripNumBoxes2;
-    int totalCost;
-    int moved;
-    vector<vector<int> > stripX;
-    vector<vector<int> > stripY;
-    vector<int> stripSumX;
-    vector<int> stripSumY;
-
     //endregion
 
 
@@ -123,17 +109,19 @@ int main(int argc, char **argv){
 
         //endregion
 
-    //cout << "Instance: " << instance << endl;
+    for(i = 0; i < 10; ++i) {
+        cout << "Instance: " << i << endl;
 
-    createInstance(threshold, minWidth, maxWidth, minBoxWidth, maxBoxWidth, numScores, numBox, totalBoxWidth, allScores, adjMatrix, mates, boxWidths, allBoxes);
[…]

### 2017-12-13 paper/ffdexact/packingexact.cpp

@@ -15,32 +15,19 @@ void swap(int &a, int &b){
     b = temp;
 }
 
-int lowerBound(double totalBoxWidth, int maxStripWidth){
+int lowerBound(int maxStripWidth, double totalBoxWidth){
     int lBound;
 
     lBound = ceil(totalBoxWidth/maxStripWidth);
     return lBound;
 }
 
-int initCost(int &totalCost, int maxStripWidth, vector<int> &stripSum){
-
-    int i;
-    totalCost = 0;
-
-    for(i = 0; i < stripSum.size(); ++i){
-        totalCost += pow((maxStripWidth - stripSum[i]), 2);
-    }
-
-    return totalCost;
-
-}
-
-void packStripsFFD(int numScores, int numBox, int &totalCost, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<int> &stripNumBoxes, vector<vector<int> > &strip){
+void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
+                   vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip){
 
     int i, j, mini, k, l;
     int min = 0;
     int max = maxBoxWidth;
-    int numStrips = 0;
     int feasible;
     vector<int> boxDecrease;
     vector<int> checked(numScores, 0);
@@ -63,11 +50,11 @@ void packStripsFFD(int numScores, int numBox, int &totalCost, int maxBoxWidth, i
         min = 0;
     }
 
-    cout << "Box decrease:\n";
+    /*cout << "Box decrease:\n";
     for(i = 0; i < boxDecrease.size(); ++i){
         cout << boxDecrease[i] << " ";
     }
-    cout << endl << endl;
+    cout << endl << endl;*/
 
     strip[0].push_back(boxDecrease[0]);
     strip[0].push_back(mates[boxDecrease[0]]);
@@ -119,19 +106,12 @@ void packStripsFFD(int numScores, int numBox, int &totalCost, int maxBoxWidth, i
         stripSum.pop_back();
         --l;
     }
[…]

### 2017-12-13 paper/ffdexact/packingexact.h

@@ -12,11 +12,10 @@ using namespace std;
 
 void swap(int &a, int &b);
 
-int lowerBound(double totalBoxWidth, int maxStripWidth);
+int lowerBound(int maxStripWidth, double totalBoxWidth);
 
-int initCost(int &totalCost, int maxStripWidth, vector<int> &stripSum);
-
-void packStripsFFD(int numScores, int numBox, int &totalCost, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<vector<int> > &adjMatrix, vector<int> &mates, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<int> &stripNumBoxes, vector<vector<int> > &strip);
+void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
+                   vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 void MBAHRA(int i1, int j1, int &feasible, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
             vector<vector<int> > &boxWidths, vector<int> &boxDecrease, vector<int> &stripSum, vector<vector<int> > &strip);

### 2018-01-02 paper/paper.tex
Initial introduction

--- 2017-12-07 paper/paper.tex
@@
-\documentclass{article}
+\documentclass{llncs}
 
-% Algorithms
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
-\newcommand{\IndStatex}[1][1]{\Statex\hspace{6mm}}
-\newcommand{\IndIndStatex}[1][1]{\Statex\hspace{12mm}}
-\newcommand{\IndIndIndStatex}[1][1]{\Statex\hspace{18mm}}
+\input{includes/preamble.tex}
 
-% Contains advanced math extensions
-\usepackage{amsmath}
-
-% Introduces the *proof* environment and the \theoremstyle command
-\usepackage{amsthm}
-
-% Adds new symbols to be used in math mode, e.g. \mathbb
-\usepackage{amssymb}
-
-% To declare multiple authors
-\usepackage{authblk}
-
-% Provides extra comands as well as optimisation for producing tables
-\usepackage{booktabs}
-
-% Allows customisation of appearance and placements for figures/tables etc.
-\usepackage{caption}
-
-% Adds support for arbitrarily-deep nested lists
-\usepackage{enumitem}
-
-% Improves the interface for defining floating objects such as figures/tables
-\usepackage{float}
-
-\usepackage{fullpage}
-
-% For easy management of document margins and the document page size
-%\usepackage{geometry}
-
-% Allows insertion of graphic files within a document
-\usepackage{graphicx}
-
-% Manage links within the document or to any URL when you compile in PDF
-\usepackage{hyperref}
-
-% Successor of amsmath
-\usepackage{mathtools}
-
-% No indentation, space between paragraphs
-\usepackage{parskip}
-
-%Include standalone .tex files
-\usepackage{standalone}
-
-% Define multiple floats (figures/tables) within one environment with individual captions 1a, 1b etc
-\usepackage{subcaption}
-
-\usepackage{tikz}
-
-\usepackage{wrapfig}
-
-%Theorem style
-\theoremstyle{plain}% default
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{corollary}{Corollary}[theorem]
-
-\theoremstyle{definition}
-\newtheorem{defn}{Definition}[section]
-\newtheorem{proposition}{Proposition}[defn]
-\newtheorem{exmp}{Example}[section]
-
-\title{Paper for IWOCA}
-\author{Asyl L. Hawa}
-\affil{\small{\textit{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, CF24 4AG}}}
+\title{IWOCA Paper}
+\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
+\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
 \date{\today}
@@
 \begin{document}
+\maketitle
 
-\maketitle
+\begin{abstract}
+	Abstract
+\end{abstract}
 
@@
 
+The bin packing problem is a widely researched problem\\
+BPP can be stated as follows:
+
+\begin{itemize}
+	\item \textcolor{red}{original BPP}
+	\item Definition of problem: packing items of different sizes into a finite number of bins/containers that have a fixed size such that the number of bins/containers required is minimised.
+	\item Combinatorial NP-hard problem (computational complexity)
+	\item NP-Complete (decision problem)
+	\item Heuristics
+	\item FF and FFD
+	\item FF can produce a feasible solution quickly, but the solution may not be optimal O(nln n), n is the number of items that need to be packed.
+	\item ``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki)
+	\item ``bound for FFD is tight'' (wiki)
+	\item 2015 Hoberg and Rothvoss proposed and proofed a new complexity for the algorithm FF (wiki)
+	\item Exact algorithms, Martello and Toth (MTP), Bin Completion algorithm Korf 2002, Schreiber and Korf (2013) (wiki)
+
+	\item \textcolor{red}{Score constraints}	
+	\item Goulimis 2004, score constraints for packing and folding
+	\item Explain knives for scoring
+	\item Picture of box with score widths, score lines
+	\item All boxes have same height, different widths, different score widths
+	\item ``Threshold'' ``minimum knife distance'' ``minimum score separation constraint'' ``minimum score line distance'', ``minimum score line constraint'' 70mm industry
+	\item Becker alg exact, P, but without packing, all boxes on one strip
+	\item \textcolor{red}{Multiple strips}
+	\item Material may not come in long sizes, instead short sizes of fixed length
+	\item find optimal arrangement of boxes on strips while mimimising waste and number of strips required
+
+	\item Formal statement of BPP with score constraint
+
+	\item layout of paper
+\end{itemize}
+
 \end{document}
-\grid

### 2018-01-03 paper/paper.tex
added bibliography

@@
-\documentclass{llncs}
+\documentclass[oribibl]{llncs}
 
@@
 
-The bin packing problem is a widely researched problem\\
-BPP can be stated as follows:
+The one-dimensional bin packing problem (BPP) is a widely researched problem \\
+The problem is as follows: given a set of $n$ weighted items  and a finite number of bins with equal capacity $c$, find the minimum number of bins required to contain all of the items.
+NP-Hard \cite{garey1979}, \cite{coffman1984}, \cite{lewis2017}, \cite{becker2015}, \cite{becker2010}, \cite{goulimis2004}, \cite{karp1972}, \cite{mahadev1995}.
 
@@
 	\item Definition of problem: packing items of different sizes into a finite number of bins/containers that have a fixed size such that the number of bins/containers required is minimised.
-	\item Combinatorial NP-hard problem (computational complexity)
+	\item Combinatorial NP-hard problem (computational complexity) Gary and Johnson 1979
 	\item NP-Complete (decision problem)
@@
 
+\bibliographystyle{dcu}
+\bibliography{includes/bibliography}
+
+%\input{includes/bibliography.tex}
+
 \end{document}

### 2018-01-04 paper/paper.tex
continued introduction and references

--- 2018-01-02 paper/paper.tex
@@
 
-\title{IWOCA Paper}
+\title{Heuristics for the Score Constrained Bin-Packing Problem}
 \author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
@@
 \section{Introduction}
+\label{sec:intro}
 
-The bin packing problem is a widely researched problem\\
-BPP can be stated as follows:
+The one-dimensional bin packing problem (BPP) is a combinatorial optimisation problem that has been widely researched and discussed due to its ability to model a variety of real-life sitations.
+The BPP can be described as follows: given a set of $n$ items of varying sizes $w$, and a finite number of bins with equal capacity $c$, find the minimum number of bins required to contain all of the items.
+As shown by \cite{garey1979}, this problem is NP-hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP.
+Instead, heursitics can be used to find a near-optimal solution in a shorter amount of time.
+One example is the greedy heuristic known as first-fit, an online algorithm that places each item (in some arbitrary order) into the lowest-indexed bin.
+If there are no bins that can feasibly accommodate the item, the algorithm places the item into a new bin.
+A modified version of first-fit yields the well-known first-fit decreasing (FFD) algorithm (\cite{eilon1971}), which initially sorts the items into non-decreasing order of size before allocating them into bins.
+As proven by \cite{dosa2007}, the worst case for FFD is $\frac{11}{9}k + 4$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ (\cite{korf2002}).
+
+In 2004, Goulimis brought to light an open-combinatorial problem related to the bin-packing problem.
+Corrugated boxes are formed in two stages: firstly, they are produced flat, then a device consistsing of knives mounted on a bar creates ``scores'' along fold lines on the flat boxes.
+These scores allow the boxes to be folded in predetermined places.
+The first stage of this process involves finding a feasible pattern of the flat boxes that minimises the amount of waste, and has been researched extensively.
+It is classically solved by delayed column-generation \citep{gilmore1961, gilmore1963}.
+However, the second step of this process requires an additional constraint.
+
+The scoring knives, by design, cannot be placed too close together (around 70mm in industry), and as such have a ``minimum knife distance''.
+The problem then becomes a bin-packing problem with an additional constraint: find a feasible arrangement of boxes such that the sum of two adjacent score widths from different boxes is greater than or equal to the minimum knife distance.
+We will call this constraint the minimum total width constraint.
+
+\textcolor{red}{INSERT FIGURE TWO BOXES ANNOTATED AND KNIVES ON BAR FOLD LINES SCORE WIDTH}
+
+There exists a polynomial time algorithm that is able to recognise whether a particular instance of the problem is feasible or infeasible (\cite{becker2010}) (i.e.
+whether all boxes can be arranged in one line).
+However, the algorithm does not consider the lengths of each individual box, or the total length of the final arrangement of boxes.
+In industry, strips of materials are provided in fixed lengths, so, given a large number of boxes to pack, it may not be feasible to pack all of the boxes onto one strip.
+
+This leads us to our main problem: given a collection of boxes with varying widths and score widths on either side, and strips of a fixed length, find the minimum number of strips required to accommodate all of the boxes, such that the minimum total width constraint is met between all boxes on all strips.
+
+The remainder of this report will firstly, in Section \ref{sec:ffdapprox}, introduce the first-fit decreasing approximate algorithm and describe the modifications made to consider the minimum score width constraint.
+In Section \ref{sec:ffdexact}, we will present a new algorithm which consists of the modified first-fit decreasing algorithm detailed in the previous section combined with a polynomial-time algorithm which will be used to find feasible sub-solutions.
+A comparison of the two algorithms and an analysis of the results will be provided in Section \ref{sec:compresult}, and finally Section \ref{sec:conclusion} concludes the paper and proposes some potential directions for furture work.
 
@@
 	\item FF can produce a feasible solution quickly, but the solution may not be optimal O(nln n), n is the number of items that need to be packed.
-	\item ``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki)
+	\item ``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki) Rhyd Lewis 2009
 	\item ``bound for FFD is tight'' (wiki)
@@
 	\item Exact algorithms, Martello and Toth (MTP), Bin Completion algorithm Korf 2002, Schreiber and Korf (2013) (wiki)
+	\item \textcolor{blue}{Although there are exact solutions available for the BPP} (martello knapsack MTP 1989 (1990b) ``is based on a first-fit decreasing'' branching strategy and is the best existing algorithm for optimal packing (KOrf2002)'', hung and brown 1978 ``a branch-and-bound algorithm'' paper title:``an algorithm for a class of loading problems'', eilon christofides 1971 ``a depth-first numerative algorithm'' paper title: ``the loadings problem'', schreiber and korf 2002 bin completion algorithm) \textcolor{blue}{they are only able to find solutions to problems that have a small input size.}
+	\item ``Hence, exact solution techniques are bound to work well for small to medium sized problem instances only, and real world sized problems including up to thousands of items have to be solved heuristically.''
 
@@
 	\item All boxes have same height, different widths, different score widths
-	\item ``Threshold'' ``minimum knife distance'' ``minimum score separation constraint'' ``minimum score line distance'', ``minimum score line constraint'' 70mm industry
+	\item ``Threshold'' ``minimum knife distance'' ``minimum score separation constraint'' ``minimum score line distance'', ``minimum score line constraint'' ``minimum total width constraint'' 70mm industry
 	\item Becker alg exact, P, but without packing, all boxes on one strip
@@
 
+\section{FFD Using Approximate Algorithm}
+\label{sec:ffdapprox}
+
+\section{FFD Using Exact Algorithm}
+\label{sec:ffdexact}
+
+\section{Comparison and Results}
+\label{sec:compresult}
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+\section{References}
+\cite{becker2010}: Twin Constrainted Hamiltonain Paths on Threshold Graphs
+
+\cite{becker2015}: A Heuristics for the MSSP
+
+\cite{coffman1978}: An Application of Bin-Packing to Multiprocessor Scheduling
+
+\cite{coffman1984}: Approximation Algorithms for Bin-Packing - An Updated Survey.
+\begin{itemize}
+	\item ``first fit and first fit decreasing algorithms have equivalent worst-case time complexities of O(n ln n) (cite coffman1984)''
+	\item ``we refer the interested reader to the excellent survery by (cite coffman1984), which includes a bibliography of more than one hundred titles''
+	\item ``A comprehensive review of various heuristic algorithms is provided in a recent survery by (cite coffman1984)''
+	\item ``(cite coffman1984) did an excellent survey on this problem, particularly on approximation algorithms and their asymptotic performance ratios''
+\end{itemize}
+\cite{dosa2007}: The tight bound of first fit decreasing bin packing algorithm
+
+\cite{eilon1971}: The loading problem. 
+\begin{itemize}
+	\item ``(cite eilon1971) presented a depth-first enumerative algorithm''
+	\item ``(cite eilon1971) discuss its(the BPP) application to the loading of vehicles (or other containers) with consignment'' 
+	\item ``the most well-known heuristics are the FFD and the BFD (cite eilon1971)''
+\end{itemize}
+\cite{garey1979}: Computers and Intractibility - A Guide to the Theory of NP-Completeness. 
+\begin{itemize}
+	\item ``(cite garey1979) cite simple heuristics which can be shown to be no
+	worse(but also no better) than a rather small multiplying factor above the optimal number of bins.''
+	\item ``the bpp problem is NP-Hard''
+\end{itemize}
+
+\cite{gilmore1961}: A LP Approach to the CSP Part 1
+
+\cite{gilmore1963}: A LP Approach to the CSP Part 2
+
+\cite{goulimis2004}: Minimum Score Separation
+
+\cite{johnson1974}: Worst case performance bounds for simple one-dimensional packing algorithms
+\begin{itemize}
+	\item ``(cite johnson1974) discuss three practical applications in computer science, which are table formatting, prepaging, and file allocation''
+\end{itemize}
+
+\cite{karp1972}: Reducibility among combinatorial problems
+
+\cite{korf2002}: A new algorithm for optimal bin packing.
+``If the number of bins in a solution is equivalent to the expression (sum of all weights/ capacity) then that solution is an optimal solution to the problem instance (cite Korf2002)''
+
+\cite{lewis2009}: A general-purpose hill-climbing method for order independent minimum grouping problems
+
+\cite{lewis2017}: How to pack trapezoids
+
+\cite{lewis2011}: An investigation into two bpp with ordering and orientation implications
+
+\cite{mahadev1995}: Threshold graphs and related topics
+
+\cite{martello1990}: Knapsack problems. ``(cite martello1990) proposed a branch-and-bound based exact algorithm MTP for the BPP.''
+
+\bibliographystyle{dcu}
+\bibliography{includes/bibliography}
+
+%\input{includes/bibliography.tex}
+
 \end{document}

### 2018-01-05 paper/notespaper.tex
notes and ideas for IWOCA paper
continued introduction and ffd approx

--- 2017-12-13 paper/paper.tex
@@
 
-\title{Paper for IWOCA}
-\author{Asyl L. Hawa \and Rhyd Lewis \and Jonathan Thompson}
-\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
-\date{\today}
+\title{Notes for IWOCA Paper}
+\author{Asyl L. Hawa}
 
@@
 \section{Introduction}
+
+\begin{itemize}
+	\item \textcolor{red}{original BPP}
+	\item Definition of problem: packing items of different sizes into a finite number of bins/containers that have a fixed size such that the number of bins/containers required is minimised.
+	\item Combinatorial NP-hard problem (computational complexity) Gary and Johnson 1979
+	\item NP-Complete (decision problem)
+	\item Heuristics
+	\item FF and FFD
+	\item FF can produce a feasible solution quickly, but the solution may not be optimal O(nln n), n is the number of items that need to be packed.
+	\item ``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki) Rhyd Lewis 2009
+	\item ``bound for FFD is tight'' (wiki)
+	\item 2015 Hoberg and Rothvoss proposed and proofed a new complexity for the algorithm FF (wiki)
+	\item Exact algorithms, Martello and Toth (MTP), Bin Completion algorithm Korf 2002, Schreiber and Korf (2013) (wiki)
+	\item \textcolor{blue}{Although there are exact solutions available for the BPP} (martello knapsack MTP 1989 (1990b) ``is based on a first-fit decreasing'' branching strategy and is the best existing algorithm for optimal packing (KOrf2002)'', hung and brown 1978 ``a branch-and-bound algorithm'' paper title:``an algorithm for a class of loading problems'', eilon christofides 1971 ``a depth-first numerative algorithm'' paper title: ``the loadings problem'', schreiber and korf 2002 bin completion algorithm) \textcolor{blue}{they are only able to find solutions to problems that have a small input size.}
+	\item ``Hence, exact solution techniques are bound to work well for small to medium sized problem instances only, and real world sized problems including up to thousands of items have to be solved heuristically.''
+
+	\item \textcolor{red}{Score constraints}	
+	\item Goulimis 2004, score constraints for packing and folding
+	\item Explain knives for scoring
+	\item Picture of box with score widths, score lines
+	\item All boxes have same height, different widths, different score widths
+	\item ``Threshold'' ``minimum knife distance'' ``minimum score separation constraint'' ``minimum score line distance'', ``minimum score line constraint'' ``minimum total width constraint'' 70mm industry
+	\item Becker alg exact, P, but without packing, all boxes on one strip
+	\item \textcolor{red}{Multiple strips}
+	\item Material may not come in long sizes, instead short sizes of fixed length
+	\item find optimal arrangement of boxes on strips while mimimising waste and number of strips required
+
+	\item Formal statement of BPP with score constraint called the Score Constrained Bin packing problem: given ...
+
+	\item layout of paper
+\end{itemize}
+
 \begin{enumerate}
@@
 	\item then go on to explain mbahra + output of solution
-	\item pros and cons? polynomial time, however it means that it cannot be done continuously
-	\item i.e. the heuristic can be applied during scoring, but with the exact alg, a full solution must be found before any scoring can occur, as boxes can be moved around
+	\item pros and cons?
+polynomial time, however it means that it cannot be done continuously, i.e.
+the heuristic can be applied during scoring, but with the exact alg, a full solution must be found before any scoring can occur, as boxes can be moved around
 \end{enumerate}

### 2018-01-05 paper/paper.tex
continued introduction and ffd approx

@@
 
-\title{Heuristics for the Score Constrained Bin-Packing Problem}
+\title{Heuristics for the Score-Constrained Bin-Packing Problem}
 \author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
@@
 If there are no bins that can feasibly accommodate the item, the algorithm places the item into a new bin.
-A modified version of first-fit yields the well-known first-fit decreasing (FFD) algorithm (\cite{eilon1971}), which initially sorts the items into non-decreasing order of size before allocating them into bins.
-As proven by \cite{dosa2007}, the worst case for FFD is $\frac{11}{9}k + 4$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ (\cite{korf2002}).
+A modified version of first-fit yields the well-known first-fit decreasing (FFD) algorithm (\citealp{eilon1971}), which initially sorts the items into non-decreasing order of size before allocating them into bins.
+As proven by \cite{dosa2007}, the worst case for FFD is $\frac{11}{9}k + 4$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ (..if the solution has this many bins then it is optimal, (\citealp{korf2002})).
 
 In 2004, Goulimis brought to light an open-combinatorial problem related to the bin-packing problem.
-Corrugated boxes are formed in two stages: firstly, they are produced flat, then a device consistsing of knives mounted on a bar creates ``scores'' along fold lines on the flat boxes.
+Corrugated boxes are formed in two stages: firstly, they are produced flat, then a device consistsing of knives mounted on a bar creates ``scores'' along specific lines on the flat boxes.
 These scores allow the boxes to be folded in predetermined places.
 The first stage of this process involves finding a feasible pattern of the flat boxes that minimises the amount of waste, and has been researched extensively.
-It is classically solved by delayed column-generation \citep{gilmore1961, gilmore1963}.
+It is classically solved by delayed column-generation (\citealp{gilmore1961, gilmore1963}).
 However, the second step of this process requires an additional constraint.
@@
 
-There exists a polynomial time algorithm that is able to recognise whether a particular instance of the problem is feasible or infeasible (\cite{becker2010}) (i.e.
+\textcolor{blue}{Figure showing two boxes with score widths and the scoring knives mounted on a bar.
+Since the sum of the two adjacent score widths from different boxes is greater than or equal to 70mm, the minimum total width constraint has been met - this is a feasible alignment of these two boxes}
+
+There exists a polynomial time algorithm that is able to recognise whether a particular instance of the problem is feasible or infeasible (\citealp{becker2010}) (i.e.
 whether all boxes can be arranged in one line).
@@
 \begin{itemize}
-	\item \textcolor{red}{original BPP}
-	\item Definition of problem: packing items of different sizes into a finite number of bins/containers that have a fixed size such that the number of bins/containers required is minimised.
-	\item Combinatorial NP-hard problem (computational complexity) Gary and Johnson 1979
-	\item NP-Complete (decision problem)
-	\item Heuristics
-	\item FF and FFD
-	\item FF can produce a feasible solution quickly, but the solution may not be optimal O(nln n), n is the number of items that need to be packed.
-	\item ``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki) Rhyd Lewis 2009
-	\item ``bound for FFD is tight'' (wiki)
-	\item 2015 Hoberg and Rothvoss proposed and proofed a new complexity for the algorithm FF (wiki)
+	\item FF if online, FFD is offline
+	\item FF and FFD can produce a feasible solution quickly, but the solution may not be optimal O(nln n), where n is the number of items that need to be packed
 	\item Exact algorithms, Martello and Toth (MTP), Bin Completion algorithm Korf 2002, Schreiber and Korf (2013) (wiki)
@@
 	\item ``Hence, exact solution techniques are bound to work well for small to medium sized problem instances only, and real world sized problems including up to thousands of items have to be solved heuristically.''
-
-	\item \textcolor{red}{Score constraints}	
-	\item Goulimis 2004, score constraints for packing and folding
-	\item Explain knives for scoring
+	\item ``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki) Rhyd Lewis 2009
 	\item Picture of box with score widths, score lines
 	\item All boxes have same height, different widths, different score widths
-	\item ``Threshold'' ``minimum knife distance'' ``minimum score separation constraint'' ``minimum score line distance'', ``minimum score line constraint'' ``minimum total width constraint'' 70mm industry
-	\item Becker alg exact, P, but without packing, all boxes on one strip
-	\item \textcolor{red}{Multiple strips}
-	\item Material may not come in long sizes, instead short sizes of fixed length
-	\item find optimal arrangement of boxes on strips while mimimising waste and number of strips required
+	\item Recognition algorithm Becker
+	\item Formal statement of BPP with score constraint called the Score Constrained Bin packing problem (SCBPP): given
+	\item dicuss other paper/articles with this problem, i.e. rhyd 2017
 
-	\item Formal statement of BPP with score constraint
-
-	\item layout of paper
 \end{itemize}
@@
 \label{sec:ffdapprox}
+
+\begin{itemize}
+	\item discuss heuristics
+	\item ``Heuristics are approximate solution techniques that typically provide solutions in the least amount of time to the detriment of the solutions quality''
+	\item ``Exact methods find a best possible packing, but are slow and may be unable to provide solutions to large or reastically sized problem instances within reasonable time''
+	\item ``Consider a set of $n$ items.
+In the context of bin packing problems, heuristics consider these items one-by-one and attempt to pack them into a bin so as to achieve a near-optimal solution without the guarantee that a solution is optimal.''
+	\item ``Exact packing methods are often called deterministic methods and are guarantees to find an optimal solution to a problem (given sufficient time and a feasible region) while heuristics attempt to find optimal solutions, but are not guaranteed to do so.''
+	\item ``Exact methods may often be too slow to solve large problem instances, but may typically be used to solve smaller ones.''
+	\item ``Packing heuristics follow a fixed set of rules to pack items in such a manner as to find good, feasible (but not necessarily optimal) solutions to the bin packing problem within as short a time span as possible.''
+	\item offline algorithm, whole problem data is provided/required at the start.
+	\item online, doesn't consider future events/items, data is processed in the order that it is input into the algorithm, entire input is not required to be available from the start
+	\item ``first-fit decreasing (FFD) algorithm for one-dimensional bin packing by johnson et al (1974, worst-case performance bounds for simple one-dimensional packing algorithms)''
+	\item FF is online, FFD is offline
+	\item FF and FFD can produce a feasible solution quickly, but the solution may not be optimal, O(nln n), where n is the number of items that need to be packed
+	\item who stated that ffd is O(nlog n)?
+	\item Coffman et al 1984 heuristics survey
+	\item \textcolor{blue}{Describe how the ffdapprox algorithm works}
+	\item \textcolor{red}{figure of packed boxes on strips}
+	\item previously placed boxes are fixed, cannot be rearranged
+	\item complexity of modified FFD for SCBPP
+	\item background information on FFD
+	\item works in the same way as FFD, but with an additional step - each box must meet the minimum total score width constraint, so if a box fits onto a strip, we start by checking if the smallest of the two score widths on the box, and the free score width on the end of the current strip, meet the mtswc.
+If not, then we rotate the box $180^{\circ}$ and check again if the mtswc is met.
+If neither score width on the box meets the mtswc with the free score width, then we move onto the next strip and try again.
+	\item start from bottom of strip/end of strip, pack from left to right
+	\item Karp complexity
+	\item \textcolor{red}{figure of one packed strip indicating free score end $e$}
+	\item pros and cons: speed, however there may be a solution that exists that cannot be found due to boxes being fixed in place
+	\item In this algorithm, the boxes are sorted by non-increasing widths prior to packing.
+	\item If a box does not fit onto any existing strips, a new strip is initialised.
+	\item Initially, pack the largest (widest/box with the largest width/first box in the sorted list of boxes) box into the first strip.
+
+\end{itemize}
+
+\begin{algorithm}[H]
+	\caption{First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}
+	\label{alg:ffdapprox}
+	\begin{algorithmic}[1]
+		\Require $n$ boxes with widths $w_i$, each box has two score widths $u_{i1} \text{ and } u_{i2}$, where $u_{i1}$ is the smaller of the two score widths, n strips of fixed lengths $l \text { and residual length } r_j \text { which is initially set to } l$.
+$j = 1,2, ..$ strips.
+$e_j$ is the score width at the end of strip $j$, i.e a score width of the most recent box packed into that strip, free end, etc.
+$t$ is the minimum total score width that must be met in order for the boxes to be packed.
+Assume no box has a width that is larger than the strip length, i.e.
+$w_i \leq l \forall i $.
+Could do strips set $S$ with $\{u_{i1}, u_{i2}\}$ representing box on strip $S_j$ with smallest score width first, and $\{u_{i2}, u_{i1}\}$ representing box with larger score width first.
+need to put $i = 1, 2, ..., n$ and $j = 1, 2, ...$.
+		\State Sort boxes in non-increasing order of widths, breaking ties arbitrarily
+		\ForAll{boxes $i = 1, 2, ..., n$}
+			\ForAll{strips $j = 1,2,...$}
+				\If{$r_j < l \land w_i \leq r_j $}
+					\If{$e_j + s_{i1} \geq t$}
+						\IndIndIndStatex $S_j \gets S_j + \{\{u_{i1}, u_{i2}\}\}$
+						\IndIndIndStatex $r_j \gets r_j - w_i$
+						\IndIndIndStatex break
+					\ElsIf{$e_j + s_{i2} \geq t$}
+						\IndIndIndStatex $S_j \gets S_j + \{\{u_{i2}, u_{i1}\}\}$
+						\IndIndIndStatex $r_j \gets r_j - w_i$
+						\IndIndIndStatex break
+					\EndIf
+				\ElsIf{$r_j = l$}
+					\IndIndStatex $S_j \gets S_j + \{\{u_{i1}, u_{i2}\}\}$
+					\IndIndStatex $r_j \gets r_j - w_i$
+					\IndIndStatex break
+				\EndIf
+			\EndFor
+		\EndFor
+		\Ensure all boxes packed onto strips while meeting minimum total width constraint. Set $S$ is all strips with boxes in correct rotation to meet minimum total score width constraint.
+
+	\end{algorithmic}	
+\end{algorithm}
 
@@
 \label{sec:compresult}
+
+\begin{itemize}
+	\item ``Dowsland and Dowsland (1992, ``Packing Problems'') comment that while average or worst-case performance bounds are useful guidelines, it is best to determine an algorithm's usefuless by testing it on data sets typical to the intended problem.
+Repositories are available on the internet where benchamrk data sets for packing problems are stored for the purpose of evaluating algorithms.''
+\end{itemize}
 
@@
 
-\cite{martello1990}: Knapsack problems. ``(cite martello1990) proposed a branch-and-bound based exact algorithm MTP for the BPP.''
+\cite{martello1990b}: Knapsack problems. ``(cite martello1990) proposed a branch-and-bound based exact algorithm MTP for the BPP.''
 

### 2018-01-07 paper/paper.tex
changed break statements in algorithm ffdapprox
edited ffdapprox, started ffdexact

@@
 A modified version of first-fit yields the well-known first-fit decreasing (FFD) algorithm (\citealp{eilon1971}), which initially sorts the items into non-decreasing order of size before allocating them into bins.
-As proven by \cite{dosa2007}, the worst case for FFD is $\frac{11}{9}k + 4$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ (..if the solution has this many bins then it is optimal, (\citealp{korf2002})).
+As proven by \cite{dosa2007} (tight bound), the worst case for FFD is $\frac{11}{9}k + \frac{6}{9}$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ (..if the solution has this many bins then it is optimal, (\citealp{korf2002})).
 
@@
 
-This leads us to our main problem: given a collection of boxes with varying widths and score widths on either side, and strips of a fixed length, find the minimum number of strips required to accommodate all of the boxes, such that the minimum total width constraint is met between all boxes on all strips.
+This leads us to our main problem, the score-constrained bin-packing problem: given a collection of boxes with varying widths and score widths on either side, and strips of a fixed length, find the minimum number of strips required to accommodate all of the boxes, such that the minimum total width constraint is met between all boxes on all strips.
 
@@
 	\item dicuss other paper/articles with this problem, i.e. rhyd 2017	
+\end{itemize}
 
-\end{itemize}
+\section{Formulating the problem}
+We are given $n$ boxes that need to be packed onto strips.
+Each of these boxes have a positive width, and two score widths, one on either side of the box.
+Since these score widths are not necessarily equal, the boxes can be aligned in two ways: either in a ``regular'' alignment, where the smaller of the two score widths is on the left hand side of the box, or in a ``rotated'' alignment, where the box has been rotated by $180^{\circ}$ so that the larger score width is on the left-hand side of the box.
+Strips are packed left to right.
+We also have a finite number of strips of equal fixed lengths.
+Once a box has been placed onto a strip, the rightmost score on the strip is referred to as the ``free'' score.
+A box can only be placed onto a strip if it can fit onto the strip, i.e.
+the addition of the box to the strip doesn't exceed the length of the strip, and if the free score and one of the scores on the box meet the minimum total score width constraint, i.e.
+the sum of the free score width and one of the scores on the box is greater than or equal to the minimum total score width.
+Assume that no box has a width that is greater than the fixed length of the strips.
+
+Definition: Score-Constrained Bin-Packing Problem.
+Find the minimum number of strips required to feasibly pack all the boxes such that the minimum total score width constraint is met between every pair of adjacent score widths from different boxes on every strip.
+Then the SCBPP consists of finding a feasible alignment of all of the boxes onto the strips such that every pair of adjacent score widths from different boxes meets the minimum total score width constraint, and that the least number of strips is used.
 
@@
 \label{sec:ffdapprox}
-
 \begin{itemize}
@@
 If neither score width on the box meets the mtswc with the free score width, then we move onto the next strip and try again.
-	\item start from bottom of strip/end of strip, pack from left to right
+	\item pack from left to right
+	\item boxes can be aligned in two ways, with smaller score on LHS, or rotated $180^{\circ}$ so the smaller score is on the LHS
 	\item Karp complexity
@@
 	\item Initially, pack the largest (widest/box with the largest width/first box in the sorted list of boxes) box into the first strip.
-
+	\item ``Simchi-Levi (1994, ``New worst-case results for the bpp'') has shown that the FFD and the BFD heuristics have an absolute performance ratio of 1.5, and that this value is the best possible for the BPP, unles $P = NP$.''
 \end{itemize}
@@
 	\begin{algorithmic}[1]
-		\Require $n$ boxes with widths $w_i$, each box has two score widths $u_{i1} \text{ and } u_{i2}$, where $u_{i1}$ is the smaller of the two score widths, n strips of fixed lengths $l \text { and residual length } r_j \text { which is initially set to } l$.
-$j = 1,2, ..$ strips.
-$e_j$ is the score width at the end of strip $j$, i.e a score width of the most recent box packed into that strip, free end, etc.
-$t$ is the minimum total score width that must be met in order for the boxes to be packed.
-Assume no box has a width that is larger than the strip length, i.e.
-$w_i \leq l \forall i $.
-Could do strips set $S$ with $\{u_{i1}, u_{i2}\}$ representing box on strip $S_j$ with smallest score width first, and $\{u_{i2}, u_{i1}\}$ representing box with larger score width first.
-need to put $i = 1, 2, ..., n$ and $j = 1, 2, ...$.
+	\Require $n$ boxes with widths $w(i)$ for $i = 1,2,...,n$, each box $i$ has two scores $i_1$ (smaller score width) and $i_2$ (larger score width), where $w(i_1) \leq w(i_2)$.
+Let $\{i_1, i_2\}$ represent box $i$ aligned such that the smaller score is on the LHS, and let $\{i_2, i_2\}$ represent box $i$ rotated by $180^{\circ}$ such that the larger score is on the LHS.
+Strips are packed from left to right.
+Finite number of strips $S_j, j = 1, 2, ...$ that all have equal fixed length $l > 0$, and a residual length $r(j)$, where initially $r(j) = l \forall j = 1, 2, ...$.
+Initially $S_j = \emptyset \forall j = 1, 2,...$.
+Let $w(f_j)$ denote the width of the free score for strip $j$.
 	\State Sort boxes in non-increasing order of widths, breaking ties arbitrarily
-		\ForAll{boxes $i = 1, 2, ..., n$}
-			\ForAll{strips $j = 1,2,...$}
-				\If{$r_j < l \land w_i \leq r_j $}
-					\If{$e_j + s_{i1} \geq t$}
-						\IndIndIndStatex $S_j \gets S_j + \{\{u_{i1}, u_{i2}\}\}$
-						\IndIndIndStatex $r_j \gets r_j - w_i$
-						\IndIndIndStatex break
-					\ElsIf{$e_j + s_{i2} \geq t$}
-						\IndIndIndStatex $S_j \gets S_j + \{\{u_{i2}, u_{i1}\}\}$
-						\IndIndIndStatex $r_j \gets r_j - w_i$
-						\IndIndIndStatex break
+	\State $i \gets 1, j \gets 1$
+	\State $S_j \gets S_j + \{\{i_1, i_2\}\}$
+	\State $r(j) \gets r(j) - w(i)$
+	\For{$i \gets 2$ \textbf{to} $n$}
+		\For{$j \gets 1$ \textbf{to} $n$}
+			\If{$S_j \neq \emptyset \land w(i) \leq r(j)$}
+				\If{$w(f_j) + w(i_1) \geq t$}
+					\IndIndIndStatex $S_j \gets S_j \cup \{i_1, i_2\}$
+					\IndIndIndStatex $r(j) \gets r(j) - w(i)$
+					\IndIndIndStatex \Break
+				\ElsIf{$w(f_j) + w(i_2) \geq t$}
+					\IndIndIndStatex $S_j \gets S_j \cup \{i_2, i_1\}$
+					\IndIndIndStatex $r(j) \gets r(j) - w(i)$
+					\IndIndIndStatex \Break					
 				\EndIf
-				\ElsIf{$r_j = l$}
-					\IndIndStatex $S_j \gets S_j + \{\{u_{i1}, u_{i2}\}\}$
-					\IndIndStatex $r_j \gets r_j - w_i$
-					\IndIndStatex break
+			\ElsIf{$S_j = \emptyset$}
+				\IndIndStatex $S_j \gets S_j \cup \{i_1, i_2\}$
+				\IndIndStatex $r(j) \gets r(j) - w(i)$
+				\IndIndStatex \Break
 			\EndIf
@@
 	\Ensure all boxes packed onto strips while meeting minimum total width constraint. Set $S$ is all strips with boxes in correct rotation to meet minimum total score width constraint.	
-
 	\end{algorithmic}	
@@
 
+DESCRIPTION OF FFDAPPROX 
+\begin{itemize}
+	\item start by sorting all boxes into non-increasing order of widths, breaking ties arbitrarily
+	\item starting with the first box in the list (i.e with the box that has the largest width), put it onto the first strip, with the box rotated such that the side of the box with the smaller score width is placed at the beginning of the strip
+	\item for each box, find the lowest indexed strip that the box can fit into
+	\item if the box can fit onto a strip, check if the free score width on that strip and the smaller of the two score widths on the box meet the minimum total score width requirement.
+If so, place the box onto that strip such that the smaller of the two score widths is placed next to the free score width.
+Move onto the next box in the list
+	\item else, check if the larger of the two score widths on the box and the free score width meet the minimum total score width constraint.
+If so, place the box onto that strip such that the larger of the two score widths is placed next to the free score width.
+Move onto the next box.
+	\item else, if neither of the two score widths and the free score meet the minimum total score width constraint, move onto the next used strip and repeat
+	\item if there are no used strips that can accommodate the current box, place the box into a new unused strip, with the smaller score at the beginning of the strip (on the LHS).
+move onto the next box.
+	\item we then obtain ...
+\end{itemize}
+
 \section{FFD Using Exact Algorithm}
 \label{sec:ffdexact}
+Introduction
+\begin{itemize}
+	\item This alg will be combining a well known heuristic with an exact algorithm to find a feasible solution to the SCBPP
+	\item Becker 2010 recognicity algorithm in polynomial time
+	\item doesn't take into account individual widths of boxes
+	\item only one strip/align all boxes into one row
+	\item in industry, strips have a finite length
+	\item algorithm also doesn't output a full solution, only whether there exists a feasible solution or not
+	\item ffd but including an algorithm that can find a feasible aligment of boxes with score constraints if one exists
+	\item unlike ffd, where boxes are placed onto the end of each strip, the boxes are not fixed in place, all boxes can be reordered.
+	\item try to find a hamiltonian path 
+\end{itemize}
+
+Explanation: Initialise
+\begin{itemize}
+	\item initialise
+\end{itemize}
+
+Let each box be represented by two vertices on a graph $G$, one vertex for each side of the box.
+Each vertex has a value corresponding to the score width it represent.
+We will refer to two vertices that represent either side of the same box as ``mates''.
+The boxes cannot be altered in any way, and so the pairs of vertices must be adjacent to one another on the graph.
+
+------------------
+
+MTGMA/MIS
+\begin{itemize}
+	\item mtgma/mis
+\end{itemize}
+
+FIS/Patch
+\begin{itemize}
+	\item fis/patch
+\end{itemize}
 
@@
 
+%%Additional Comments
+\begin{comment}
+- all citations have been changed to \cite{}, so that the citation shows up in green in latex.
+some of these citations need to be changed to (\citealp{}) (or \citep{}, same outcome) as the citations need to be in brackets but without the year in brackets.
+- 1. "As proven by \cite{dosa2007}, ..." -> "As proven by Dosa (2007), ..."
+- 2.
+"...
+FFD algorithm (\cite{eilon1971}), which ..." -> "...
+FFD algorithm (Eilon and Christofides (1971)), which .." NOTE THE YEAR IS IN BRACKETS INSIDE THE CITATION BRACKETS, THIS IS ONLY WHILE WRITING, THIS NEEDS TO BE CHANGED BEFORE SUBMISSION
+- 3. "... FFD algorithm (\citealp{eilon1971}), which ..." -> "... FFD algorithm (Eilon and Christofides, 1971), which .." THIS IS HOW IT NEEDS TO BE WHEN SUBMITTING
+\end{comment}
+
 \end{document}

### 2018-01-08 paper/paper.tex
continued ffdexact, filled in bullet sections of algorithm, pseudocode for ffdexact, bullet description of ffd exact

@@
 The problem then becomes a bin-packing problem with an additional constraint: find a feasible arrangement of boxes such that the sum of two adjacent score widths from different boxes is greater than or equal to the minimum knife distance.
-We will call this constraint the minimum total width constraint.
+We will call this constraint the minimum total score width constraint.
 
@@
 \begin{algorithm}[H]
-\caption{First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}
+	\caption{\textcolor{red}{First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
 	\label{alg:ffdapprox}
@@
 	\State $i \gets 1, j \gets 1$
-	\State $S_j \gets S_j + \{\{i_1, i_2\}\}$
+	\State $S_j \gets S_j \cup \{i_1, i_2\}$
 	\State $r(j) \gets r(j) - w(i)$
@@
 				\If{$w(f_j) + w(i_1) \geq t$}
-					\IndIndIndStatex $S_j \gets S_j \cup \{i_1, i_2\}$
-					\IndIndIndStatex $r(j) \gets r(j) - w(i)$
-					\IndIndIndStatex \Break
+					\State $S_j \gets S_j \cup \{i_1, i_2\}$
+					\State $r(j) \gets r(j) - w(i)$
+					\State \Break
 				\ElsIf{$w(f_j) + w(i_2) \geq t$}
-					\IndIndIndStatex $S_j \gets S_j \cup \{i_2, i_1\}$
-					\IndIndIndStatex $r(j) \gets r(j) - w(i)$
-					\IndIndIndStatex \Break					
+					\State $S_j \gets S_j \cup \{i_2, i_1\}$
+					\State $r(j) \gets r(j) - w(i)$
+					\State \Break					
 				\EndIf
 			\ElsIf{$S_j = \emptyset$}
-				\IndIndStatex $S_j \gets S_j \cup \{i_1, i_2\}$
-				\IndIndStatex $r(j) \gets r(j) - w(i)$
-				\IndIndStatex \Break
+				\State $S_j \gets S_j \cup \{i_1, i_2\}$
+				\State $r(j) \gets r(j) - w(i)$
+				\State \Break
 			\EndIf
@@
 	\item unlike ffd, where boxes are placed onto the end of each strip, the boxes are not fixed in place, all boxes can be reordered.
+	\item Can find a solution for a set of boxes on a strip when it may not have been possible to find one in ffdapprox due to only the last box being checked.
 	\item try to find a hamiltonian path 
+	\item complexity $O(n^2), O(n)$ to construct a solution
+	\item if the algorithm cannot find a feasible alignment of the boxes including the current box, move onto next strip and try again.
 \end{itemize}
@@
 \begin{itemize}
-	\item initialise
+	\item Let each box be represented by two vertices on a graph $G$, one vertex for each side of the box.
+Each vertex has a value corresponding to the score width it represent.
+We will refer to two vertices that represent either side of the same box as ``partners''.
+The boxes cannot be altered in any way, and so the pairs of vertices must be adjacent to one another on the graph.
+	\item Add extra dominating box with dominating score widths equal to the minimum total score width, the dominating box will be removed at the end.
+	\item Therefore we connect pair of vertices that are partners via an edge on the graph $G$.
+	\item Call this set of edges $P$.
+	\item Edges of P are also weighted, value equivalent to the corresponding box width.
+	\item For every pair of vertices on $G$, if the sum of their values/score widths is greater than or equal to the minimum total score width, and the two vertices are not partners/not connected via an edge from $P$, connect the vertices with an edge - call this set of edges $Q$ (These edges are not weighted).
+	\item Call a pair of vertices connected via an edge from $Q$ ``matched''.
+	\item We want to find an alternating Hamiltonian cycle, where successive edges alternate from sets $P$ and $Q$.
 \end{itemize}
-
-Let each box be represented by two vertices on a graph $G$, one vertex for each side of the box.
-Each vertex has a value corresponding to the score width it represent.
-We will refer to two vertices that represent either side of the same box as ``mates''.
-The boxes cannot be altered in any way, and so the pairs of vertices must be adjacent to one another on the graph.
-
-------------------
 
@@
 \begin{itemize}
-	\item mtgma/mis
+	\item \cite{mahadev1994} Maximum cardinality matching algorithm.
+	\item From the set of edges $Q$, we need to obtain a set of edges $M \subset Q$ of cardinality $n$ such that the edges from sets $M$ and $P$ form an alternating Hamiltonian cycle.
+	\item We use a simple maximum cardinality matching algorithm to obtain the set of edges $M$ (the matching).
+	\item Explain algorithm.
+	\item Swap of partners?
+	\item Explain matching on a graph.
+	\item If $|M| < n$, then infeasible, there is no feasible arrangement of the boxes such that the minimum total score width constraint is met, exit.
+	\item If $|M| = n$, then we should have at least one alternating Hamiltonian cycle.
+	\item If there is only one cycle, remove the dominating vertices, obtain final solution of boxes in order they should be packed, exit.
+	\item Else, if there is more than one cycle, we need to find a way to combine these cycles into one alternating Hamiltonian cycle.
 \end{itemize}
 
-FIS/Patch
+FCA/Patch
 \begin{itemize}
-	\item fis/patch
+	\item Find pairs of vertices in each cycle connected via a matching edge/ edge from $M$ that can be broken and rematched.
+	\item Break/remove matching edges between vertices and create/add new matching edges such that the cycles are combined/connected.
+	\item If there are no vertices that can be rematched from different cycles, then the cycles cannot be joined together, and therefore there is no feasible solution.
+	\item Else, if we are able to join the cycles together to create one alternating Hamiltonian cycle, we then simply have to remove the dominating vertices to obtain a final solution/feasible alignment of the boxes.
+	\item Sort edges, successive edges, see if edges are from different cycles and if the smaller vertex of the lower indexed edge is adjacent to the larger vertex of the higher indexed edge.
+\end{itemize}
+
+\begin{algorithm}[H]
+	\caption{\textcolor{blue}{First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
+	\label{alg:ffdexact}
+	\begin{algorithmic}[1]
+	\Require fill in.   
+	\State Sort boxes in non-increasing order of widths, breaking ties arbitrarily
+	\State $i \gets 1, j \gets 1$
+	\State $S_j \gets S_j \cup \{i_1, i_2\}$
+	\State $r(j) \gets r(j) - w(i)$
+	\For{$i \gets 2$ \textbf{to} $n$}
+		\For{$j \gets 1$ \textbf{to} $n$}
+			\If{$S_j \neq \emptyset \land w(i) \leq r(j)$}
+				\State Perform \textcolor{red}{algorithm} on boxes in $S_j$ and box $i$
+				\If{feasible alignment of boxes found}
+					\State Replace alignment of boxes in $S_j$ with new box alignment including box $i$
+					\State $r(j) \gets r(j) - w(i)$
+					\State \Break
+				\EndIf
+			\ElsIf{$S_j = \emptyset$}
+				\State $S_j \gets S_j \cup \{i_1, i_2\}$
+				\State $r(j) \gets r(j) - w(i)$
+				\State \Break
+			\EndIf
+		\EndFor
+	\EndFor		
+	\Ensure all boxes packed onto strips while meeting minimum total width constraint. Set $S$ is all strips with boxes in correct rotation to meet minimum total score width constraint.	
+	\end{algorithmic}	
+\end{algorithm}
+
+DESCRIPTION FFD EXACT
+\begin{itemize}
+	\item Start with boxes sorted in order of non-increasing widths, breaking ties arbitrarily.
+	\item Place the first box onto the first strip, such that the smaller of the two score widths is on the leftmost side of the strip.
+	\item Attempt to fit each box $i, i = 2,..., n$ onto the lowest-indexed strip possible that already contains a box, i.e. the strip is not empty.
+	\item If a box is able to feasibly fit onto a strip, apply the \textcolor{red}{algorithm} on all of the boxes on the strip plus the current box $i$.
+	\item If a feasible alignment of the boxes has been found, replace the current alignment of boxes on the strip with the new alignment, which includes box $i$ (and move onto the next box).
+	\item If no feasible alignment of the boxes is found, we move onto the next lowest-indexed strip and repeat.
+	\item If a box cannot fit into any of the used strips, i.e.
+any of the strips that already contain a box/any of the open strips, we then place the box onto a new, unused strip, such that the smaller of the two score widths on the box is on the leftmost side of the strip, then move onto the next box.
+	\item Continue untill all boxes have been placed onto a strip/until all boxes have been packed.
 \end{itemize}
@@
 
+\cite{mahadev1994}: Longest cycle in threshold graphs
+
 \cite{mahadev1995}: Threshold graphs and related topics

### 2018-01-09 paper/paper.tex
wrote draft Initialize section for ffdexact

@@
 	\item ``Simchi-Levi (1994, ``New worst-case results for the bpp'') has shown that the FFD and the BFD heuristics have an absolute performance ratio of 1.5, and that this value is the best possible for the BPP, unles $P = NP$.''
+	\item We use $\{i_1, i_2\}$ or $\{i_2, i_1\}$ to represent the box, rather than just $i$, because the feasibility of the alignment of boxes on the strip depends on which way the box is placed, regularly or rotated.
 \end{itemize}
@@
 Explanation: Initialise
-\begin{itemize}
-	\item Let each box be represented by two vertices on a graph $G$, one vertex for each side of the box.
-Each vertex has a value corresponding to the score width it represent.
-We will refer to two vertices that represent either side of the same box as ``partners''.
-The boxes cannot be altered in any way, and so the pairs of vertices must be adjacent to one another on the graph.
-	\item Add extra dominating box with dominating score widths equal to the minimum total score width, the dominating box will be removed at the end.
-	\item Therefore we connect pair of vertices that are partners via an edge on the graph $G$.
-	\item Call this set of edges $P$.
-	\item Edges of P are also weighted, value equivalent to the corresponding box width.
-	\item For every pair of vertices on $G$, if the sum of their values/score widths is greater than or equal to the minimum total score width, and the two vertices are not partners/not connected via an edge from $P$, connect the vertices with an edge - call this set of edges $Q$ (These edges are not weighted).
-	\item Call a pair of vertices connected via an edge from $Q$ ``matched''.
-	\item We want to find an alternating Hamiltonian cycle, where successive edges alternate from sets $P$ and $Q$.
-\end{itemize}
+
+Let each box be represented by two vertices on a graph $G$, one vertex for each side of the box.
+We also introduce a ``dummy'' box that has two ``dominating scores'' with widths equal to the minimum total score width, $t$.
+This dummy box will be discarded at the end of the algorithm, and will not be included in the final feasible alignment.
+We now have $n$ boxes including the dummy box, and so $G$ will have $2n$ vertices.
+
+We will refer two two vertices that represent either side of the same box as ``partners''.
+The boxes cannot be altered in any way, and so partners must be adjacent to one another.
+We therefore create a set of edges, $P$, consisting of edges between partners on $G$.
+\textcolor{red}{weighted edges $P$}.
+
+Each vertex $v_i$ for $i = 1, 2, ..., 2n$ has a positive value $w(v)$ corresponding to the score width it represents.
+There is an edge between two vertices $u$ and $v$ on $G$ if and only if the vertices fulfil the \textit{minimum total score width constraint},
+
+\begin{equation*}
+w(u) + w(v) \geq t,
+\end{equation*}
+
+and $u$ and $v$ are not partners, i.e.
+$\{u, v\} \notin P$.
+The vertices $u$ and $v$ are referred to as ``matched'', and so their corresponding score widths can be feasibly aligned next to one another.
+We now have another set of edges, $Q$, consisting of edges between matched vertices.
+
+In order to find a feasible alignment of the boxes, we must find an alternating Hamiltonian cycle on $G$. \textcolor{red}{turns into path when we remove dummy box.}
+
+\begin{definition}
+	Let $G(V, P\cup Q)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $Q$.
+$G$ has an \textit{alternating Hamiltonian cycle} if there exists a Hamiltonian cycle on $G$ such that the successive edges alternate between sets $P$ and $Q$.
+For example, if vertex $v_k$ in the Hamiltonian cycle is adjacent to vertex $v_{k-1}$ via an edge from $P$, then $v_k$ must be adjacent to vertex $v_{k+1}$ via an edge from $Q$, or vice versa.
+\end{definition}
+
+\textcolor{red}{Figure of graph $G$ with boxes, figure of aligned boxes with alternating Hamiltonian path underneath.}
 

### 2018-01-10 paper/paper.tex
wrote up MTGMA/MIS section ffdexact

@@
 $\{u, v\} \notin P$.
-The vertices $u$ and $v$ are referred to as ``matched'', and so their corresponding score widths can be feasibly aligned next to one another.
-We now have another set of edges, $Q$, consisting of edges between matched vertices.
+The vertices $u$ and $v$ are referred to as \textcolor{red}{``matched''}, and so their corresponding score widths can be feasibly aligned next to one another.
+We now have another set of edges, $Q$, consisting of edges between \textcolor{red}{``matched''} vertices.
 
@@
 \begin{definition}
+	\label{defn:althamcycle}
 	Let $G(V, P\cup Q)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $Q$.
@@
 
+\textcolor{red}{we now need to find a way of producing the alternating hamiltonian cycle on the graph $G$, if one exists.}
+
 MTGMA/MIS
-\begin{itemize}
-	\item \cite{mahadev1994} Maximum cardinality matching algorithm.
-	\item From the set of edges $Q$, we need to obtain a set of edges $M \subset Q$ of cardinality $n$ such that the edges from sets $M$ and $P$ form an alternating Hamiltonian cycle.
-	\item We use a simple maximum cardinality matching algorithm to obtain the set of edges $M$ (the matching).
-	\item Explain algorithm.
-	\item Swap of partners?
-	\item Explain matching on a graph.
-	\item If $|M| < n$, then infeasible, there is no feasible arrangement of the boxes such that the minimum total score width constraint is met, exit.
-	\item If $|M| = n$, then we should have at least one alternating Hamiltonian cycle.
-	\item If there is only one cycle, remove the dominating vertices, obtain final solution of boxes in order they should be packed, exit.
-	\item Else, if there is more than one cycle, we need to find a way to combine these cycles into one alternating Hamiltonian cycle.
-\end{itemize}
+
+We need to obtain a set of matching edges $M \subset Q$ of cardinality $n$, such that the matching edges from $M$ and the edges from $P$ form an alternating Hamiltonain cycle as described in Definition \ref{defn:althamcycle}.
+We use a modified matching algorithm (\citealp{mahadev1994, becker2010}) that produces a suitable set of matching edges $M$.
+
+Initially, the vertices are sorted in order of non-decreasing values, and ties are broken arbitrarily.
+Starting from the smallest vertex, find the largest adjacent vertex (under $Q$?
+in the set $Q$?
+)that is not the current vertex's partner, and that has not yet been matched.
+Add this pair of vertices to the set $M$ that keeps a record of the matching edges, and proceed to the next vertex in the list.
+Continue until all vertices have been assessed.
+
+If a vertex $v_i$ is not adjacent to any other vertex except its partner, we can rematch previous vertices to provide $v_i$ with a feasible match, provided $v_i$ is not the first vertex in the sorted list, the previous vertex $v_{i-1}$ has a match (i.e.
+$v_{i-1} \in M$), and $v_{i-1}$ is adajcent to $v_i$'s partner.
+We then simply match $v_{i-1}$ with $v_i$'s partner, and match $v_i$ with $v_{i-1}$'s previous match.
+\textcolor{red}{max cardinality.}
+
+If $|M| < n$, then there are not enough matching edges to form an alternating Hamiltonian cycle with the edges in $P$, and therefore there is no feasible arrangement of the boxes such that the minimum total score width constraint is not violated.
+However, if $|M| = n$, then the graph $G(V, P \cup M)$ is a 2-regular graph, where each vertex is adjacent to one vertex via an edge in $P$, (i.e.
+its partner), and another vertex via an edge in $M$ (i.e.
+its match).
+If $G$ consists of one alternating Hamiltonian cycle, then we simply remove the dominating vertices to obtain a feasible alignment of the boxes/feasible solution.
+If there are more than two cycles on $G$, we need to combine them into one alternating Hamiltonian cycle.
 

### 2018-01-11 paper/paper.tex
changed ffdexact pseudocode, added FCA section, added colours

@@
 A modified version of first-fit yields the well-known first-fit decreasing (FFD) algorithm (\citealp{eilon1971}), which initially sorts the items into non-decreasing order of size before allocating them into bins.
-As proven by \cite{dosa2007} (tight bound), the worst case for FFD is $\frac{11}{9}k + \frac{6}{9}$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ (..if the solution has this many bins then it is optimal, (\citealp{korf2002})).
+As proven by \cite{dosa2007} \textcolor{RoyalBlue}{(tight bound)}, the worst case for FFD is $\frac{11}{9}k + \frac{6}{9}$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ \textcolor{RoyalBlue}{(..if the solution has this many bins then it is optimal,} (\citealp{korf2002})).
 
@@
 The problem then becomes a bin-packing problem with an additional constraint: find a feasible arrangement of boxes such that the sum of two adjacent score widths from different boxes is greater than or equal to the minimum knife distance.
-We will call this constraint the minimum total score width constraint.
+\textcolor{RoyalBlue}{We will call this constraint the minimum total score width constraint.}
 
-\textcolor{red}{INSERT FIGURE TWO BOXES ANNOTATED AND KNIVES ON BAR FOLD LINES SCORE WIDTH}
+\textcolor{OrangeRed}{Insert figure, two boxes annotated with score widths, score lines, box widths, knives mounted on bar showing minimum total score width constraint}
 
-\textcolor{blue}{Figure showing two boxes with score widths and the scoring knives mounted on a bar.
+\textcolor{RoyalBlue}{Figure showing two boxes with score widths and the scoring knives mounted on a bar.
 Since the sum of the two adjacent score widths from different boxes is greater than or equal to 70mm, the minimum total width constraint has been met - this is a feasible alignment of these two boxes}
 
-There exists a polynomial time algorithm that is able to recognise whether a particular instance of the problem is feasible or infeasible (\citealp{becker2010}) (i.e.
-whether all boxes can be arranged in one line).
+There exists a polynomial time algorithm that is able to recognise whether a particular instance of the problem is feasible or infeasible (\citealp{becker2010}) \textcolor{RoyalBlue}{(i.e.
+whether all boxes can be arranged in one line)}.
 However, the algorithm does not consider the lengths of each individual box, or the total length of the final arrangement of boxes.
@@
 	\item Exact algorithms, Martello and Toth (MTP), Bin Completion algorithm Korf 2002, Schreiber and Korf (2013) (wiki)
-	\item \textcolor{blue}{Although there are exact solutions available for the BPP} (martello knapsack MTP 1989 (1990b) ``is based on a first-fit decreasing'' branching strategy and is the best existing algorithm for optimal packing (KOrf2002)'', hung and brown 1978 ``a branch-and-bound algorithm'' paper title:``an algorithm for a class of loading problems'', eilon christofides 1971 ``a depth-first numerative algorithm'' paper title: ``the loadings problem'', schreiber and korf 2002 bin completion algorithm) \textcolor{blue}{they are only able to find solutions to problems that have a small input size.}
-	\item ``Hence, exact solution techniques are bound to work well for small to medium sized problem instances only, and real world sized problems including up to thousands of items have to be solved heuristically.''
-	\item ``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki) Rhyd Lewis 2009
-	\item Picture of box with score widths, score lines
+	\item \textcolor{RoyalBlue}{Although there are exact solutions available for the BPP} (martello knapsack MTP 1989 (1990b) \textcolor{Plum}{``is based on a first-fit decreasing'' branching strategy and is the best existing algorithm for optimal packing (Korf2002)'', hung and brown 1978 ``a branch-and-bound algorithm'' paper title:``an algorithm for a class of loading problems'', eilon christofides 1971 ``a depth-first numerative algorithm'' paper title: ``the loadings problem'', schreiber and korf 2002 bin completion algorithm)} \textcolor{RoyalBlue}{they are only able to find solutions to problems that have a small input size.}
+	\item \textcolor{Plum}{``Hence, exact solution techniques are bound to work well for small to medium sized problem instances only, and real world sized problems including up to thousands of items have to be solved heuristically.''}
+	\item \textcolor{Plum}{``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki) Rhyd Lewis 2009}
 	\item All boxes have same height, different widths, different score widths
 	\item Recognition algorithm Becker
-	\item Formal statement of BPP with score constraint called the Score Constrained Bin packing problem (SCBPP): given
+	\item \textcolor{RoyalBlue}{Formal statement of BPP with score constraint called the Score Constrained Bin packing problem (SCBPP): given}
 	\item dicuss other paper/articles with this problem, i.e. rhyd 2017	
@@
 
-Definition: Score-Constrained Bin-Packing Problem.
+\textcolor{RoyalBlue}{Definition: Score-Constrained Bin-Packing Problem.
 Find the minimum number of strips required to feasibly pack all the boxes such that the minimum total score width constraint is met between every pair of adjacent score widths from different boxes on every strip.
-Then the SCBPP consists of finding a feasible alignment of all of the boxes onto the strips such that every pair of adjacent score widths from different boxes meets the minimum total score width constraint, and that the least number of strips is used.
+Then the SCBPP consists of finding a feasible alignment of all of the boxes onto the strips such that every pair of adjacent score widths from different boxes meets the minimum total score width constraint, and that the least number of strips is used.}
+
+Notation
+\begin{itemize}
+	\item $n$ boxes, $i = 1, 2, ..., n$.
+	\item Each box $i$ has a total width $w(i)$.
+	\item Each box $i$ has two scores, $i_1$ (the smaller score), and $i_2$ (the larger score), and widths $w(i_1), w(i_2)$, such that $w(i_1) \leq w(i_2)$.
+	\item $\{i_1, i_2\}$ represents ``regular'' box $i$: $i_1$ on LHS of box.
+	\item $\{i_2, i_1\}$ represents ``rotated'' box $i$: $i_2$ on LHS of box (box rotated by $180^{\circ}$).
+	\item All box widths $w(i) > 0$ and all score widths $w(i_1), w(i_2) > 0$ $\forall$ $i = 1, 2, ..., n$.
+	\item Finite number of strips $S_j$, $j = 1, 2, ...$.
+	\item All strips $S_j$ have equal fixed length $l > 0$ $\forall$ $j = 1, 2, ...$.
+	\item All strips $S_j$ have a residual length $r(j)$, initially $r(j) = l$ $\forall$ $j = 1,2, ...$, which reduces as boxes are added to each strip.
+	\item Assumption: all box widths $w(i) \leq l, i = 1, 2, ..., n$
+	\item Initially, $S_j = \emptyset$ $\forall$ $j = 1, 2, ...$.
+	\item For all strips $S_j \neq \emptyset$, the score on the right hand side of the last box in the strip is called the ``free score'', denoted $f_j$, with width $w(f_j)$.
+	\item The \textit{minimum total score width} is denoted by $t, t > 0$ \textcolor{RoyalBlue}{usually 70mm in industry}.
+\textcolor{RoyalBlue}{The \textit{minimum total score width constraint} is $w(u_p) + w(v_q) \geq t$, $u \neq v, p, q = 1 or 2$.}
+
+	\item -------------------------
+
+	\item Notation for Exact algorithm
+	\item $n$ boxes including dummy box.
+	\item $2n$ vertices including dominating vertices.
+	\item Graph $G$ is an undirected graph with $2n$ vertices $v_i, i = 1, 2, ...,2n$.
+	\item Vertices are weighted, $w(v_i)$.
+	\item Vertices that represent either side of same box referred to as ``partners''
+	\item $P$ contains the set of edges between partners, fixed, $|P| = n$.
+	\item Edges in $P$ are weighted, corresponding to box width.
+	\item $Q$ contains the set of edges between vertices that meet the minimum total score width constraint, excluding partners (these edges are not weighted).
+	\item $G(V, P \cup Q)$ - each edge on $G$ is either in $P$ or $Q$, not both.
+	\item $t$ still represents the minimum total score width.
+	\item $M$ is the set of matching edges, $M \subset Q$, edges chosen using the matching algorithm (need $|M| = n$).
+	\item number of cycles on $G$ after MTGMA =  ?
+	\item $C_k$: sets of edges for connecting cycles.
+
+\end{itemize}
 
@@
 	\item discuss heuristics
-	\item ``Heuristics are approximate solution techniques that typically provide solutions in the least amount of time to the detriment of the solutions quality''
-	\item ``Exact methods find a best possible packing, but are slow and may be unable to provide solutions to large or reastically sized problem instances within reasonable time''
-	\item ``Consider a set of $n$ items.
-In the context of bin packing problems, heuristics consider these items one-by-one and attempt to pack them into a bin so as to achieve a near-optimal solution without the guarantee that a solution is optimal.''
-	\item ``Exact packing methods are often called deterministic methods and are guarantees to find an optimal solution to a problem (given sufficient time and a feasible region) while heuristics attempt to find optimal solutions, but are not guaranteed to do so.''
-	\item ``Exact methods may often be too slow to solve large problem instances, but may typically be used to solve smaller ones.''
-	\item ``Packing heuristics follow a fixed set of rules to pack items in such a manner as to find good, feasible (but not necessarily optimal) solutions to the bin packing problem within as short a time span as possible.''
+	\item \textcolor{Plum}{``Heuristics are approximate solution techniques that typically provide solutions in the least amount of time to the detriment of the solutions quality''}
+	\item \textcolor{Plum}{``Exact methods find a best possible packing, but are slow and may be unable to provide solutions to large or reastically sized problem instances within reasonable time''}
+	\item \textcolor{Plum}{``Consider a set of $n$ items.
+In the context of bin packing problems, heuristics consider these items one-by-one and attempt to pack them into a bin so as to achieve a near-optimal solution without the guarantee that a solution is optimal.''}
+	\item \textcolor{Plum}{``Exact packing methods are often called deterministic methods and are guarantees to find an optimal solution to a problem (given sufficient time and a feasible region) while heuristics attempt to find optimal solutions, but are not guaranteed to do so.''}
+	\item \textcolor{Plum}{``Exact methods may often be too slow to solve large problem instances, but may typically be used to solve smaller ones.''}
+	\item \textcolor{Plum}{``Packing heuristics follow a fixed set of rules to pack items in such a manner as to find good, feasible (but not necessarily optimal) solutions to the bin packing problem within as short a time span as possible.''}
 	\item offline algorithm, whole problem data is provided/required at the start.
 	\item online, doesn't consider future events/items, data is processed in the order that it is input into the algorithm, entire input is not required to be available from the start
-	\item ``first-fit decreasing (FFD) algorithm for one-dimensional bin packing by johnson et al (1974, worst-case performance bounds for simple one-dimensional packing algorithms)''
+	\item \textcolor{Plum}{``first-fit decreasing (FFD) algorithm for one-dimensional bin packing by johnson et al (1974, worst-case performance bounds for simple one-dimensional packing algorithms)''}
 	\item FF is online, FFD is offline
 	\item FF and FFD can produce a feasible solution quickly, but the solution may not be optimal, O(nln n), where n is the number of items that need to be packed
-	\item who stated that ffd is O(nlog n)?
-	\item Coffman et al 1984 heuristics survey
-	\item \textcolor{blue}{Describe how the ffdapprox algorithm works}
-	\item \textcolor{red}{figure of packed boxes on strips}
+	\item \textcolor{Plum}{who stated that ffd is O(nlog n)?}
+	\item \textcolor{Plum}{Coffman et al 1984 heuristics survey}
+	\item \textcolor{RoyalBlue}{Describe how the ffdapprox algorithm works}
+	\item \textcolor{OrangeRed}{figure of packed boxes on strips}
 	\item previously placed boxes are fixed, cannot be rearranged
@@
 	\item Karp complexity
-	\item \textcolor{red}{figure of one packed strip indicating free score end $e$}
+	\item \textcolor{OrangeRed}{figure of one packed strip indicating free score end $e$}
 	\item pros and cons: speed, however there may be a solution that exists that cannot be found due to boxes being fixed in place
@@
 	\item Initially, pack the largest (widest/box with the largest width/first box in the sorted list of boxes) box into the first strip.
-	\item ``Simchi-Levi (1994, ``New worst-case results for the bpp'') has shown that the FFD and the BFD heuristics have an absolute performance ratio of 1.5, and that this value is the best possible for the BPP, unles $P = NP$.''
+	\item \textcolor{Plum}{``Simchi-Levi (1994, ``New worst-case results for the bpp'') has shown that the FFD and the BFD heuristics have an absolute performance ratio of 1.5, and that this value is the best possible for the BPP, unless $P = NP$.''}
 	\item We use $\{i_1, i_2\}$ or $\{i_2, i_1\}$ to represent the box, rather than just $i$, because the feasibility of the alignment of boxes on the strip depends on which way the box is placed, regularly or rotated.
@@
 \begin{algorithm}[H]
-	\caption{\textcolor{red}{First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
+	\caption{\textcolor{OliveGreen}{First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
 	\label{alg:ffdapprox}
 	\begin{algorithmic}[1]
-	\Require $n$ boxes with widths $w(i)$ for $i = 1,2,...,n$, each box $i$ has two scores $i_1$ (smaller score width) and $i_2$ (larger score width), where $w(i_1) \leq w(i_2)$.
+	\Require \textcolor{RoyalBlue}{$n$ boxes with widths $w(i)$ for $i = 1,2,...,n$, each box $i$ has two scores $i_1$ (smaller score width) and $i_2$ (larger score width), where $w(i_1) \leq w(i_2)$.
 Let $\{i_1, i_2\}$ represent box $i$ aligned such that the smaller score is on the LHS, and let $\{i_2, i_2\}$ represent box $i$ rotated by $180^{\circ}$ such that the larger score is on the LHS.
@@
 Initially $S_j = \emptyset \forall j = 1, 2,...$.
-Let $w(f_j)$ denote the width of the free score for strip $j$.
+Let $w(f_j)$ denote the width of the free score for strip $j$.}
 	\State Sort boxes in non-increasing order of widths, breaking ties arbitrarily
@@
 	\EndFor		
-	\Ensure all boxes packed onto strips while meeting minimum total width constraint. Set $S$ is all strips with boxes in correct rotation to meet minimum total score width constraint.	
+	\Ensure \textcolor{RoyalBlue}{all boxes packed onto strips while meeting minimum total width constraint.
+Set $S$ is all strips with boxes in correct rotation to meet minimum total score width constraint.}
 	\end{algorithmic}	
@@
 We therefore create a set of edges, $P$, consisting of edges between partners on $G$.
-\textcolor{red}{weighted edges $P$}.
+\textcolor{RoyalBlue}{weighted edges $P$}.
 
@@
 $\{u, v\} \notin P$.
-The vertices $u$ and $v$ are referred to as \textcolor{red}{``matched''}, and so their corresponding score widths can be feasibly aligned next to one another.
-We now have another set of edges, $Q$, consisting of edges between \textcolor{red}{``matched''} vertices.
+The vertices $u$ and $v$ are referred to as \textcolor{OliveGreen}{``matched''}, and so their corresponding score widths can be feasibly aligned next to one another.
+We now have another set of edges, $Q$, consisting of edges between \textcolor{OliveGreen}{``matched''} vertices.
 
-In order to find a feasible alignment of the boxes, we must find an alternating Hamiltonian cycle on $G$. \textcolor{red}{turns into path when we remove dummy box.}
+In order to find a feasible alignment of the boxes, we must find an alternating Hamiltonian cycle on $G$. \textcolor{RoyalBlue}{turns into path when we remove dummy box.}
 
@@
 
-\textcolor{red}{Figure of graph $G$ with boxes, figure of aligned boxes with alternating Hamiltonian path underneath.}
+\textcolor{OrangeRed}{Figure of graph $G$ with boxes, figure of aligned boxes with alternating Hamiltonian path underneath.}
 
-\textcolor{red}{we now need to find a way of producing the alternating hamiltonian cycle on the graph $G$, if one exists.}
+\textcolor{RoyalBlue}{we now need to find a way of producing the alternating hamiltonian cycle on the graph $G$, if one exists.}
 
@@
 We then simply match $v_{i-1}$ with $v_i$'s partner, and match $v_i$ with $v_{i-1}$'s previous match.
-\textcolor{red}{max cardinality.}
+\textcolor{RoyalBlue}{max cardinality.}
 
@@
 If there are more than two cycles on $G$, we need to combine them into one alternating Hamiltonian cycle.
+\textcolor{RoyalBlue}{notation number of cycles.}
+
+\textcolor{OrangeRed}{figure of graph $G$ showing edges between partners ($P$), edges in the set $M$, and faint lines to represent the rest of the edges $Q$.}
 
 FCA/Patch
-\begin{itemize}
-	\item Find pairs of vertices in each cycle connected via a matching edge/ edge from $M$ that can be broken and rematched.
-	\item Break/remove matching edges between vertices and create/add new matching edges such that the cycles are combined/connected.
-	\item If there are no vertices that can be rematched from different cycles, then the cycles cannot be joined together, and therefore there is no feasible solution.
-	\item Else, if we are able to join the cycles together to create one alternating Hamiltonian cycle, we then simply have to remove the dominating vertices to obtain a final solution/feasible alignment of the boxes.
-	\item Sort edges, successive edges, see if edges are from different cycles and if the smaller vertex of the lower indexed edge is adjacent to the larger vertex of the higher indexed edge.
-\end{itemize}
+
+In order to combine multiple cycles into one, we need to replace some matching edges with feasible edges from the set $Q$ that connect vertices from different cycles.
+\textcolor{RoyalBlue}{The following algorithm is used to find these feasible edges}.
+
+The algorithm initially creates a list of all matching edges in $M$, sorted in order of non-decreasing vertex values \textcolor{RoyalBlue}{(i.e.
+the edge which connects the smallest vertex to its match is first in the list) (do not include edges from partner swap)}.
+Starting from the first edge in the list, the algorithm searches through the list of edges until it finds an edge whose smaller vertex is adjacent via an edge in $Q$ to the larger vertex of the succeeding edge in the list, such that both edges are from different cycles on the graph $G$.
+If such a pair of edges has been found, the algorithm adds the first edge of the pair to a set $C_k$.
+The algorithm then continues to add all succeeding edges to $C_k$, provided that the smaller vertex of the current edge is adjacent to the larger vertex of the succeeding edge via an edge in $Q$, the succeeding edge does not belong to a cycle that is already represented by an edge in $C_k$, and the algorithm has not reached the final edge in the list.
+Once there are no more valid edges to add to $C_k$, the algorithm proceeds to the next edge in the list, and checked whether this edge is suitable for beginning a new set $C_{k+1}$.
+If the algorithm has already reached the penultimate or final edge in the list, the algorithm terminates.
+
+If the algorithm does not produce a single set $C$, there are no edges available to connect the cycles together, and therefore no feasible alignment of the boxes in this problem instance exists.
+\textcolor{RoyalBlue}{also if the set $C$ doesn't include an edge from every cycle, or multiple sets $C$ that don't cover all cycles, infeasible.}
+
+If there exists a set $C_k$ such that $|C_k| = \textcolor{OliveGreen}{number of cycles}$, then the cycles can be connected as follows: starting from the first edge in $C_k$, connect the smaller vertex to the larger vertex of the second edge in the set.
+Then, connect the smaller vertex of the second edge to the larger vertex of the third edge.
+Continue in this manner until the last edge in $C_k$ is reached, and connect the lower vertex of this final edge to the larger vertex of the first edge.
+These new matching edges will join the distinct cycles together to form one alternating Hamiltonian cycle.
+The edges in the set $C_k$ can be removed from the graph $G$
+
+\textcolor{RoyalBlue}{Multiple $C_k$ cycles required.}
 
 \begin{algorithm}[H]
-	\caption{\textcolor{blue}{First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
+	\caption{\textcolor{OliveGreen}{First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
 	\label{alg:ffdexact}
 	\begin{algorithmic}[1]
-	\Require fill in.   
-	\State Sort boxes in non-increasing order of widths, breaking ties arbitrarily
-	\State $i \gets 1, j \gets 1$
-	\State $S_j \gets S_j \cup \{i_1, i_2\}$
+	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, $\mathcal{S} = \emptyset$.
+	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.
+	\State Sort the boxes in order of non-increasing widths
+	\For{$i \gets 1$ \textbf{to} $n$}
+		\For{$j \gets 1$ \textbf{to} $n$}
+			\If{$S_j = \emptyset$}
+				\State $S_j \gets \{i_1, i_2\}$
 				\State $r(j) \gets r(j) - w(i)$
-	\For{$i \gets 2$ \textbf{to} $n$}
-		\For{$j \gets 1$ \textbf{to} $n$}
-			\If{$S_j \neq \emptyset \land w(i) \leq r(j)$}
-				\State Perform \textcolor{red}{algorithm} on boxes in $S_j$ and box $i$
-				\If{feasible alignment of boxes found}
-					\State Replace alignment of boxes in $S_j$ with new box alignment including box $i$
+				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
+				\State \Break
+			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
+				\State \textcolor{RoyalBlue}{Run} \textcolor{OrangeRed}{``MBAHRA''} \textcolor{RoyalBlue}{on boxes in $S_j$ and box $i$}
+				\If{feasible alignment found}
+					\State $S_j \gets$ \textcolor{RoyalBlue}{new alignment found by} \textcolor{OrangeRed}{``MBAHRA''}
 					\State $r(j) \gets r(j) - w(i)$
@@
 				\EndIf
-			\ElsIf{$S_j = \emptyset$}
-				\State $S_j \gets S_j \cup \{i_1, i_2\}$
-				\State $r(j) \gets r(j) - w(i)$
-				\State \Break
 			\EndIf
@@
 	\EndFor
-	\Ensure all boxes packed onto strips while meeting minimum total width constraint. Set $S$ is all strips with boxes in correct rotation to meet minimum total score width constraint.	
 	\end{algorithmic}	
@@
 \begin{itemize}
-	\item Start with boxes sorted in order of non-increasing widths, breaking ties arbitrarily.
+	\item Start with boxes sorted in order of non-increasing widths, breaking ties by choosing the box with the smallest score width.
 	\item Place the first box onto the first strip, such that the smaller of the two score widths is on the leftmost side of the strip.
 	\item Attempt to fit each box $i, i = 2,..., n$ onto the lowest-indexed strip possible that already contains a box, i.e. the strip is not empty.
-	\item If a box is able to feasibly fit onto a strip, apply the \textcolor{red}{algorithm} on all of the boxes on the strip plus the current box $i$.
+	\item If a box is able to feasibly fit onto a strip, apply the \textcolor{OliveGreen}{algorithm} on all of the boxes on the strip plus the current box $i$.
 	\item If a feasible alignment of the boxes has been found, replace the current alignment of boxes on the strip with the new alignment, which includes box $i$ (and move onto the next box).
@@
 \begin{itemize}
-	\item ``Dowsland and Dowsland (1992, ``Packing Problems'') comment that while average or worst-case performance bounds are useful guidelines, it is best to determine an algorithm's usefuless by testing it on data sets typical to the intended problem.
-Repositories are available on the internet where benchamrk data sets for packing problems are stored for the purpose of evaluating algorithms.''
+	\item \textcolor{Plum}{``Dowsland and Dowsland (1992, ``Packing Problems'') comment that while average or worst-case performance bounds are useful guidelines, it is best to determine an algorithm's usefuless by testing it on data sets typical to the intended problem.
+Repositories are available on the internet where benchamrk data sets for packing problems are stored for the purpose of evaluating algorithms.''}
 \end{itemize}
@@
 \begin{itemize}
-	\item ``first fit and first fit decreasing algorithms have equivalent worst-case time complexities of O(n ln n) (cite coffman1984)''
-	\item ``we refer the interested reader to the excellent survery by (cite coffman1984), which includes a bibliography of more than one hundred titles''
-	\item ``A comprehensive review of various heuristic algorithms is provided in a recent survery by (cite coffman1984)''
-	\item ``(cite coffman1984) did an excellent survey on this problem, particularly on approximation algorithms and their asymptotic performance ratios''
+	\item \textcolor{Plum}{``first fit and first fit decreasing algorithms have equivalent worst-case time complexities of O(n ln n) (cite coffman1984)''}
+	\item \textcolor{Plum}{``we refer the interested reader to the excellent survery by (cite coffman1984), which includes a bibliography of more than one hundred titles''}
+	\item \textcolor{Plum}{``A comprehensive review of various heuristic algorithms is provided in a recent survery by (cite coffman1984)''}
+	\item \textcolor{Plum}{``(cite coffman1984) did an excellent survey on this problem, particularly on approximation algorithms and their asymptotic performance ratios''}
 \end{itemize}
+
 \cite{dosa2007}: The tight bound of first fit decreasing bin packing algorithm
@@
 \begin{itemize}
-	\item ``(cite eilon1971) presented a depth-first enumerative algorithm''
-	\item ``(cite eilon1971) discuss its(the BPP) application to the loading of vehicles (or other containers) with consignment'' 
-	\item ``the most well-known heuristics are the FFD and the BFD (cite eilon1971)''
+	\item \textcolor{Plum}{``(cite eilon1971) presented a depth-first enumerative algorithm''}
+	\item \textcolor{Plum}{``(cite eilon1971) discuss its(the BPP) application to the loading of vehicles (or other containers) with consignment''}
+	\item \textcolor{Plum}{``the most well-known heuristics are the FFD and the BFD (cite eilon1971)''}
 \end{itemize}
+
 \cite{garey1979}: Computers and Intractibility - A Guide to the Theory of NP-Completeness. 
 \begin{itemize}
-	\item ``(cite garey1979) cite simple heuristics which can be shown to be no
-	worse(but also no better) than a rather small multiplying factor above the optimal number of bins.''
-	\item ``the bpp problem is NP-Hard''
+	\item \textcolor{Plum}{``(cite garey1979) cite simple heuristics which can be shown to be noworse(but also no better) than a rather small multiplying factor above the optimal number of bins.''}
+	\item \textcolor{Plum}{``the bpp problem is NP-Hard''}
 \end{itemize}
@@
 \begin{itemize}
-	\item ``(cite johnson1974) discuss three practical applications in computer science, which are table formatting, prepaging, and file allocation''
+	\item \textcolor{Plum}{ ``(cite johnson1974) discuss three practical applications in computer science, which are table formatting, prepaging, and file allocation''}
 \end{itemize}
@@
 \cite{korf2002}: A new algorithm for optimal bin packing.
-``If the number of bins in a solution is equivalent to the expression (sum of all weights/ capacity) then that solution is an optimal solution to the problem instance (cite Korf2002)''
+\textcolor{Plum}{``If the number of bins in a solution is equivalent to the expression (sum of all weights/ capacity) then that solution is an optimal solution to the problem instance (cite Korf2002)''}
 
@@
 
-\cite{martello1990b}: Knapsack problems. ``(cite martello1990) proposed a branch-and-bound based exact algorithm MTP for the BPP.''
+\cite{martello1990b}: Knapsack problems.\textcolor{Plum}{ ``(cite martello1990) proposed a branch-and-bound based exact algorithm MTP for the BPP.''}
 
@@
 
-%\input{includes/bibliography.tex}
-
-%%Additional Comments
-\begin{comment}
-- all citations have been changed to \cite{}, so that the citation shows up in green in latex.
-some of these citations need to be changed to (\citealp{}) (or \citep{}, same outcome) as the citations need to be in brackets but without the year in brackets.
-- 1. "As proven by \cite{dosa2007}, ..." -> "As proven by Dosa (2007), ..."
-- 2.
-"...
-FFD algorithm (\cite{eilon1971}), which ..." -> "...
-FFD algorithm (Eilon and Christofides (1971)), which .." NOTE THE YEAR IS IN BRACKETS INSIDE THE CITATION BRACKETS, THIS IS ONLY WHILE WRITING, THIS NEEDS TO BE CHANGED BEFORE SUBMISSION
-- 3. "... FFD algorithm (\citealp{eilon1971}), which ..." -> "... FFD algorithm (Eilon and Christofides, 1971), which .." THIS IS HOW IT NEEDS TO BE WHEN SUBMITTING
-\end{comment}
-
 \end{document}

### 2018-01-12 paper/paper.tex
added descriptions for ffdapprox and ffdexact, changed pseudocode for ffdapprox and ffd exact, wrote formal definition for SCBPP

@@
 \label{sec:intro}
-
 The one-dimensional bin packing problem (BPP) is a combinatorial optimisation problem that has been widely researched and discussed due to its ability to model a variety of real-life sitations.
@@
 The first stage of this process involves finding a feasible pattern of the flat boxes that minimises the amount of waste, and has been researched extensively.
-It is classically solved by delayed column-generation (\citealp{gilmore1961, gilmore1963}).
+\textcolor{Plum}{It is classically solved by delayed column-generation} (\citealp{gilmore1961, gilmore1963}).
 However, the second step of this process requires an additional constraint.
@@
 Assume that no box has a width that is greater than the fixed length of the strips.
+\textcolor{RoyalBlue}{need to explain minimum total score width constraint with equation and example, used in the definition for SCBPP below.}
 
-\textcolor{RoyalBlue}{Definition: Score-Constrained Bin-Packing Problem.
-Find the minimum number of strips required to feasibly pack all the boxes such that the minimum total score width constraint is met between every pair of adjacent score widths from different boxes on every strip.
-Then the SCBPP consists of finding a feasible alignment of all of the boxes onto the strips such that every pair of adjacent score widths from different boxes meets the minimum total score width constraint, and that the least number of strips is used.}
+\begin{itemize}
+	\item $n$ boxes need to be packed, all have same height but different widths $w(i)$.
+	\item Each box $i$ has two scores $i_1, i_2$, one on either side of the box.
+	\item Each of these scores has a width $w(i_1) \leq w(i_2)$.
+	\item Score widths not necessarily equal, therefore box has two different positions.
+	\item Regular position, smaller score on LHS, denoted $\{i_1, i_2\}$.
+	\item Rotated position, smaller score on RHS, denoted $\{i_2, i_1\}$ (rotated $180^{\circ}$).
+	\item Boxes will be placed side by side.
+	\item The sum of two adjacent score widths must fulfil the minimum total score width constraint ... $t$ is the minimum total score width.
+	\item The minimum total score width constraint must be fulfilled in order for the scoring knives to be able to score the boxes correctly.
+	\item There are a finite number of strips $S_j$, with equal fixed lengths $l$.
+	\item Need to pack the boxes onto the strips so mtswc is met and least number of strips used.
+	\item $l > 0, w(i) > 0, w(i) \leq l$
+\end{itemize}
+
+\begin{definition} 
+	\label{defn:scbpp}
+	Given $n$ boxes of varying widths $w(i)$ and score widths $w(i_1), w(i_2)$, and a finite number of strips $S_j$ with equal fixed lengths $l$, the Score-Constrained Bin-Packing Problem (SCBPP) consists of finding the minimum number of strips required to pack all of the boxes such that the minimum total score width constraint is met between every pair of boxes.
+\textcolor{RoyalBlue}{or: such that for every pair of boxes the sum of the adjacent score widths is greater than or equal to some fixed value $t$.}
+\end{definition}
 
@@
 \textcolor{RoyalBlue}{The \textit{minimum total score width constraint} is $w(u_p) + w(v_q) \geq t$, $u \neq v, p, q = 1 or 2$.}
+	\item Strips packed from left to right.
 
@@
 	\item Karp complexity
-	\item \textcolor{OrangeRed}{figure of one packed strip indicating free score end $e$}
+	\item \textcolor{OrangeRed}{figure of one packed strip indicating free score end $f_j$}
 	\item pros and cons: speed, however there may be a solution that exists that cannot be found due to boxes being fixed in place
@@
 \begin{algorithm}[H]
-	\caption{\textcolor{OliveGreen}{First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
+	\caption{\textcolor{OliveGreen}{Approximate First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
 	\label{alg:ffdapprox}
 	\begin{algorithmic}[1]
-	\Require \textcolor{RoyalBlue}{$n$ boxes with widths $w(i)$ for $i = 1,2,...,n$, each box $i$ has two scores $i_1$ (smaller score width) and $i_2$ (larger score width), where $w(i_1) \leq w(i_2)$.
-Let $\{i_1, i_2\}$ represent box $i$ aligned such that the smaller score is on the LHS, and let $\{i_2, i_2\}$ represent box $i$ rotated by $180^{\circ}$ such that the larger score is on the LHS.
-Strips are packed from left to right.
-Finite number of strips $S_j, j = 1, 2, ...$ that all have equal fixed length $l > 0$, and a residual length $r(j)$, where initially $r(j) = l \forall j = 1, 2, ...$.
-Initially $S_j = \emptyset \forall j = 1, 2,...$.
-Let $w(f_j)$ denote the width of the free score for strip $j$.}
-	\State Sort boxes in non-increasing order of widths, breaking ties arbitrarily
-	\State $i \gets 1, j \gets 1$
-	\State $S_j \gets S_j \cup \{i_1, i_2\}$
+	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, minimum total score width $t$, and a set $\mathcal{S} = \emptyset$.
+	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.
+	\State Sort the boxes in order of non-increasing widths.
+	\For{$i \gets 1 \To n$}
+		\For{$j \gets 1 \To n$}
+			\If{$S_j = \emptyset$}
+				\State $S_j \gets \{i_1, i_2\}$
 				\State $r(j) \gets r(j) - w(i)$
-	\For{$i \gets 2$ \textbf{to} $n$}
-		\For{$j \gets 1$ \textbf{to} $n$}
-			\If{$S_j \neq \emptyset \land w(i) \leq r(j)$}
+				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
+				\Break
+			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
 				\If{$w(f_j) + w(i_1) \geq t$}
@@
 					\State $r(j) \gets r(j) - w(i)$
-					\State \Break
+					\Break
 				\ElsIf{$w(f_j) + w(i_2) \geq t$}
@@
 					\State $r(j) \gets r(j) - w(i)$
-					\State \Break					
+					\Break
 				\EndIf
-			\ElsIf{$S_j = \emptyset$}
-				\State $S_j \gets S_j \cup \{i_1, i_2\}$
-				\State $r(j) \gets r(j) - w(i)$
-				\State \Break
 			\EndIf
@@
 	\EndFor
-	\Ensure \textcolor{RoyalBlue}{all boxes packed onto strips while meeting minimum total width constraint.
-Set $S$ is all strips with boxes in correct rotation to meet minimum total score width constraint.}
+	\Return $\mathcal{S}$
 	\end{algorithmic}	
@@
 
-DESCRIPTION OF FFDAPPROX 
-\begin{itemize}
-	\item start by sorting all boxes into non-increasing order of widths, breaking ties arbitrarily
-	\item starting with the first box in the list (i.e with the box that has the largest width), put it onto the first strip, with the box rotated such that the side of the box with the smaller score width is placed at the beginning of the strip
-	\item for each box, find the lowest indexed strip that the box can fit into
-	\item if the box can fit onto a strip, check if the free score width on that strip and the smaller of the two score widths on the box meet the minimum total score width requirement.
-If so, place the box onto that strip such that the smaller of the two score widths is placed next to the free score width.
-Move onto the next box in the list
-	\item else, check if the larger of the two score widths on the box and the free score width meet the minimum total score width constraint.
-If so, place the box onto that strip such that the larger of the two score widths is placed next to the free score width.
-Move onto the next box.
-	\item else, if neither of the two score widths and the free score meet the minimum total score width constraint, move onto the next used strip and repeat
-	\item if there are no used strips that can accommodate the current box, place the box into a new unused strip, with the smaller score at the beginning of the strip (on the LHS).
-move onto the next box.
-	\item we then obtain ...
-\end{itemize}
+\textbf{\textcolor{Rhodamine}{DESCRIPTION OF FFDAPPROX}}
+
+Initially, the algorithm arranges the boxes in non-increasing order of widths, breaking ties by choosing the box with the smallest score width.
+For each box $i$ in the sorted list, the algorithm find the lowest-indexed strip $S_j$ that is able to feasibly accommodate $i$.
+If $S_j$ is empty, $i$ is placed in a regular position onto $S_j$, which is then added to a set $\mathcal{S}$ that maintains a record of strips that are being packed.
+However, if $S_j$ is not empty, the algorithm checks the minimum total score width constraint with $i$ firstly in a regular position, then in a rotated position.
+If the constraint is met in either case, $i$ is placed accordingly onto $S_j$.
+If neither positions are able to fulfil the constraint, the algorithm moves onto the next strip $S_{j+1}$ and the process of attempting to pack $i$ is repeated.
+Once a box $i$ has been placed onto a strip, the algorithm moves onto the next box $i+1$, until all of the boxes have been packed.
 
@@
 \begin{equation*}
+	\label{eqn:mtswcg}
 	w(u) + w(v) \geq t,
@@
 \begin{algorithm}[H]
-	\caption{\textcolor{OliveGreen}{First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
+	\caption{\textcolor{OliveGreen}{Exact First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
 	\label{alg:ffdexact}
 	\begin{algorithmic}[1]
-	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, $\mathcal{S} = \emptyset$.
+	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, and a set $\mathcal{S} = \emptyset$.
 	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.
 	\State Sort the boxes in order of non-increasing widths
-	\For{$i \gets 1$ \textbf{to} $n$}
-		\For{$j \gets 1$ \textbf{to} $n$}
+	\For{$i \gets 1 \To n$}
+		\For{$j \gets 1 \To n$}
 			\If{$S_j = \emptyset$}
@@
 				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
-				\State \Break
+				\Break
 			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
 				\State \textcolor{RoyalBlue}{Run} \textcolor{OrangeRed}{``MBAHRA''} \textcolor{RoyalBlue}{on boxes in $S_j$ and box $i$}
+				%\Return \textcolor{OrangeRed}{found}
 				\If{feasible alignment found}
+				%\If{found}
 					\State $S_j \gets$ \textcolor{RoyalBlue}{new alignment found by} \textcolor{OrangeRed}{``MBAHRA''}
 					\State $r(j) \gets r(j) - w(i)$
-					\State \Break
+					\Break
 				\EndIf
@@
 	\EndFor
+	\Return $\mathcal{S}$
 	\end{algorithmic}	
@@
 
-DESCRIPTION FFD EXACT
-\begin{itemize}
-	\item Start with boxes sorted in order of non-increasing widths, breaking ties by choosing the box with the smallest score width.
-	\item Place the first box onto the first strip, such that the smaller of the two score widths is on the leftmost side of the strip.
-	\item Attempt to fit each box $i, i = 2,..., n$ onto the lowest-indexed strip possible that already contains a box, i.e. the strip is not empty.
-	\item If a box is able to feasibly fit onto a strip, apply the \textcolor{OliveGreen}{algorithm} on all of the boxes on the strip plus the current box $i$.
-	\item If a feasible alignment of the boxes has been found, replace the current alignment of boxes on the strip with the new alignment, which includes box $i$ (and move onto the next box).
-	\item If no feasible alignment of the boxes is found, we move onto the next lowest-indexed strip and repeat.
-	\item If a box cannot fit into any of the used strips, i.e.
-any of the strips that already contain a box/any of the open strips, we then place the box onto a new, unused strip, such that the smaller of the two score widths on the box is on the leftmost side of the strip, then move onto the next box.
-	\item Continue untill all boxes have been placed onto a strip/until all boxes have been packed.
-\end{itemize}
+\textbf{\textcolor{ProcessBlue}{DESCRIPTION OF FFDEXACT}}
+
+\textcolor{RoyalBlue}{In a similar fashion/manner to ``FFD approx'' (rename)} The algorithm starts by sorting the boxes in order of non-increasing widths, with ties broken by choosing the box with the smallest score width.
+Starting with the first box, the algorithm finds the lowest-indexed strip $S_j$ that can feasibly accommodate the current box $i$.
+If $S_j$ is empty, box $i$ is placed onto $S_j$ in a ``regular'' position \textcolor{RoyalBlue}{(i.e.
+smallest score width on the LHS of the box)}.
+This strip is added to the set $\mathcal{S}$ that keeps track of the strips being used to form a solution, and the algorithm proceeds onto the next box $i+1$ in the sorted list.
+
+If $S_j$ is not empty \textcolor{RoyalBlue}{(i.e contains at least one box, $|S_j| > 0$)}, then \textcolor{OrangeRed}{MBAHRA} is performed on all of the boxes in $S_j$ and the current box $i$.
+If a feasible alignment of the boxes has been found, the current boxes on $S_j$ are replaced with the new alignment, and the algorithm proceeds onto the next box $i+1$.
+If \textcolor{OrangeRed}{MBAHRA} is unable to find a feasible alignment of the boxes, the algorithm moves onto the next strip $S_{j+1}$ and the process is repeated.
+The algorithm continues until all of the boxes have been packed.
+\textcolor{RoyalBlue}{Complexity}
 

### 2018-01-12 paper/notespaper.tex
added extra bullets from paper.tex that may come in use later

@@
 
+DESCRIPTION OF FFD EXACT
+\begin{itemize}
+	\item Start with boxes sorted in order of non-increasing widths, breaking ties by choosing the box with the smallest score width.
+	\item Place the first box onto the first strip, such that the smaller of the two score widths is on the leftmost side of the strip.
+	\item Attempt to fit each box $i, i = 2,..., n$ onto the lowest-indexed strip possible that already contains a box, i.e. the strip is not empty.
+	\item If a box is able to feasibly fit onto a strip, apply the \textcolor{OliveGreen}{algorithm} on all of the boxes on the strip plus the current box $i$.
+	\item If a feasible alignment of the boxes has been found, replace the current alignment of boxes on the strip with the new alignment, which includes box $i$ (and move onto the next box).
+	\item If no feasible alignment of the boxes is found, we move onto the next lowest-indexed strip and repeat.
+	\item If a box cannot fit into any of the used strips, i.e.
+any of the strips that already contain a box/any of the open strips, we then place the box onto a new, unused strip, such that the smaller of the two score widths on the box is on the leftmost side of the strip, then move onto the next box.
+	\item Continue untill all boxes have been placed onto a strip/until all boxes have been packed.
+\end{itemize}
+
 \section{Experiments/Comparison}

### 2018-01-13 paper/paper.tex
added overview of layout, removed bullet lists

@@
 A modified version of first-fit yields the well-known first-fit decreasing (FFD) algorithm (\citealp{eilon1971}), which initially sorts the items into non-decreasing order of size before allocating them into bins.
-As proven by \cite{dosa2007} \textcolor{RoyalBlue}{(tight bound)}, the worst case for FFD is $\frac{11}{9}k + \frac{6}{9}$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ \textcolor{RoyalBlue}{(..if the solution has this many bins then it is optimal,} (\citealp{korf2002})).
+As proven by \cite{dosa2007} \textcolor{RoyalBlue}{(proved bound is tight)}, the worst case for FFD is $\frac{11}{9}k + \frac{6}{9}$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ \textcolor{RoyalBlue}{(..if the solution has this many bins then it is optimal,} (\citealp{korf2002})).
 
@@
 
-\begin{itemize}
-	\item FF if online, FFD is offline
-	\item FF and FFD can produce a feasible solution quickly, but the solution may not be optimal O(nln n), where n is the number of items that need to be packed
-	\item Exact algorithms, Martello and Toth (MTP), Bin Completion algorithm Korf 2002, Schreiber and Korf (2013) (wiki)
-	\item \textcolor{RoyalBlue}{Although there are exact solutions available for the BPP} (martello knapsack MTP 1989 (1990b) \textcolor{Plum}{``is based on a first-fit decreasing'' branching strategy and is the best existing algorithm for optimal packing (Korf2002)'', hung and brown 1978 ``a branch-and-bound algorithm'' paper title:``an algorithm for a class of loading problems'', eilon christofides 1971 ``a depth-first numerative algorithm'' paper title: ``the loadings problem'', schreiber and korf 2002 bin completion algorithm)} \textcolor{RoyalBlue}{they are only able to find solutions to problems that have a small input size.}
-	\item \textcolor{Plum}{``Hence, exact solution techniques are bound to work well for small to medium sized problem instances only, and real world sized problems including up to thousands of items have to be solved heuristically.''}
-	\item \textcolor{Plum}{``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki) Rhyd Lewis 2009}
-	\item All boxes have same height, different widths, different score widths
-	\item Recognition algorithm Becker
-	\item \textcolor{RoyalBlue}{Formal statement of BPP with score constraint called the Score Constrained Bin packing problem (SCBPP): given}
-	\item dicuss other paper/articles with this problem, i.e. rhyd 2017	
-\end{itemize}
-
 \section{Formulating the problem}
@@
 
-\begin{itemize}
-	\item $n$ boxes need to be packed, all have same height but different widths $w(i)$.
-	\item Each box $i$ has two scores $i_1, i_2$, one on either side of the box.
-	\item Each of these scores has a width $w(i_1) \leq w(i_2)$.
-	\item Score widths not necessarily equal, therefore box has two different positions.
-	\item Regular position, smaller score on LHS, denoted $\{i_1, i_2\}$.
-	\item Rotated position, smaller score on RHS, denoted $\{i_2, i_1\}$ (rotated $180^{\circ}$).
-	\item Boxes will be placed side by side.
-	\item The sum of two adjacent score widths must fulfil the minimum total score width constraint ... $t$ is the minimum total score width.
-	\item The minimum total score width constraint must be fulfilled in order for the scoring knives to be able to score the boxes correctly.
-	\item There are a finite number of strips $S_j$, with equal fixed lengths $l$.
-	\item Need to pack the boxes onto the strips so mtswc is met and least number of strips used.
-	\item $l > 0, w(i) > 0, w(i) \leq l$
-\end{itemize}
-
 \begin{definition} 
@@
 
-Notation
-\begin{itemize}
-	\item $n$ boxes, $i = 1, 2, ..., n$.
-	\item Each box $i$ has a total width $w(i)$.
-	\item Each box $i$ has two scores, $i_1$ (the smaller score), and $i_2$ (the larger score), and widths $w(i_1), w(i_2)$, such that $w(i_1) \leq w(i_2)$.
-	\item $\{i_1, i_2\}$ represents ``regular'' box $i$: $i_1$ on LHS of box.
-	\item $\{i_2, i_1\}$ represents ``rotated'' box $i$: $i_2$ on LHS of box (box rotated by $180^{\circ}$).
-	\item All box widths $w(i) > 0$ and all score widths $w(i_1), w(i_2) > 0$ $\forall$ $i = 1, 2, ..., n$.
-	\item Finite number of strips $S_j$, $j = 1, 2, ...$.
-	\item All strips $S_j$ have equal fixed length $l > 0$ $\forall$ $j = 1, 2, ...$.
-	\item All strips $S_j$ have a residual length $r(j)$, initially $r(j) = l$ $\forall$ $j = 1,2, ...$, which reduces as boxes are added to each strip.
-	\item Assumption: all box widths $w(i) \leq l, i = 1, 2, ..., n$
-	\item Initially, $S_j = \emptyset$ $\forall$ $j = 1, 2, ...$.
-	\item For all strips $S_j \neq \emptyset$, the score on the right hand side of the last box in the strip is called the ``free score'', denoted $f_j$, with width $w(f_j)$.
-	\item The \textit{minimum total score width} is denoted by $t, t > 0$ \textcolor{RoyalBlue}{usually 70mm in industry}.
-\textcolor{RoyalBlue}{The \textit{minimum total score width constraint} is $w(u_p) + w(v_q) \geq t$, $u \neq v, p, q = 1 or 2$.}
-	\item Strips packed from left to right.
-
-	\item -------------------------
-
-	\item Notation for Exact algorithm
-	\item $n$ boxes including dummy box.
-	\item $2n$ vertices including dominating vertices.
-	\item Graph $G$ is an undirected graph with $2n$ vertices $v_i, i = 1, 2, ...,2n$.
-	\item Vertices are weighted, $w(v_i)$.
-	\item Vertices that represent either side of same box referred to as ``partners''
-	\item $P$ contains the set of edges between partners, fixed, $|P| = n$.
-	\item Edges in $P$ are weighted, corresponding to box width.
-	\item $Q$ contains the set of edges between vertices that meet the minimum total score width constraint, excluding partners (these edges are not weighted).
-	\item $G(V, P \cup Q)$ - each edge on $G$ is either in $P$ or $Q$, not both.
-	\item $t$ still represents the minimum total score width.
-	\item $M$ is the set of matching edges, $M \subset Q$, edges chosen using the matching algorithm (need $|M| = n$).
-	\item number of cycles on $G$ after MTGMA =  ?
-	\item $C_k$: sets of edges for connecting cycles.
-
-\end{itemize}
-
 \section{FFD Using Approximate Algorithm}
 \label{sec:ffdapprox}
-\begin{itemize}
-	\item discuss heuristics
-	\item \textcolor{Plum}{``Heuristics are approximate solution techniques that typically provide solutions in the least amount of time to the detriment of the solutions quality''}
-	\item \textcolor{Plum}{``Exact methods find a best possible packing, but are slow and may be unable to provide solutions to large or reastically sized problem instances within reasonable time''}
-	\item \textcolor{Plum}{``Consider a set of $n$ items.
-In the context of bin packing problems, heuristics consider these items one-by-one and attempt to pack them into a bin so as to achieve a near-optimal solution without the guarantee that a solution is optimal.''}
-	\item \textcolor{Plum}{``Exact packing methods are often called deterministic methods and are guarantees to find an optimal solution to a problem (given sufficient time and a feasible region) while heuristics attempt to find optimal solutions, but are not guaranteed to do so.''}
-	\item \textcolor{Plum}{``Exact methods may often be too slow to solve large problem instances, but may typically be used to solve smaller ones.''}
-	\item \textcolor{Plum}{``Packing heuristics follow a fixed set of rules to pack items in such a manner as to find good, feasible (but not necessarily optimal) solutions to the bin packing problem within as short a time span as possible.''}
-	\item offline algorithm, whole problem data is provided/required at the start.
-	\item online, doesn't consider future events/items, data is processed in the order that it is input into the algorithm, entire input is not required to be available from the start
-	\item \textcolor{Plum}{``first-fit decreasing (FFD) algorithm for one-dimensional bin packing by johnson et al (1974, worst-case performance bounds for simple one-dimensional packing algorithms)''}
-	\item FF is online, FFD is offline
-	\item FF and FFD can produce a feasible solution quickly, but the solution may not be optimal, O(nln n), where n is the number of items that need to be packed
-	\item \textcolor{Plum}{who stated that ffd is O(nlog n)?}
-	\item \textcolor{Plum}{Coffman et al 1984 heuristics survey}
-	\item \textcolor{RoyalBlue}{Describe how the ffdapprox algorithm works}
-	\item \textcolor{OrangeRed}{figure of packed boxes on strips}
-	\item previously placed boxes are fixed, cannot be rearranged
-	\item complexity of modified FFD for SCBPP
-	\item background information on FFD
-	\item works in the same way as FFD, but with an additional step - each box must meet the minimum total score width constraint, so if a box fits onto a strip, we start by checking if the smallest of the two score widths on the box, and the free score width on the end of the current strip, meet the mtswc.
-If not, then we rotate the box $180^{\circ}$ and check again if the mtswc is met.
-If neither score width on the box meets the mtswc with the free score width, then we move onto the next strip and try again.
-	\item pack from left to right
-	\item boxes can be aligned in two ways, with smaller score on LHS, or rotated $180^{\circ}$ so the smaller score is on the LHS
-	\item Karp complexity
-	\item \textcolor{OrangeRed}{figure of one packed strip indicating free score end $f_j$}
-	\item pros and cons: speed, however there may be a solution that exists that cannot be found due to boxes being fixed in place
-	\item In this algorithm, the boxes are sorted by non-increasing widths prior to packing.
-	\item If a box does not fit onto any existing strips, a new strip is initialised.
-	\item Initially, pack the largest (widest/box with the largest width/first box in the sorted list of boxes) box into the first strip.
-	\item \textcolor{Plum}{``Simchi-Levi (1994, ``New worst-case results for the bpp'') has shown that the FFD and the BFD heuristics have an absolute performance ratio of 1.5, and that this value is the best possible for the BPP, unless $P = NP$.''}
-	\item We use $\{i_1, i_2\}$ or $\{i_2, i_1\}$ to represent the box, rather than just $i$, because the feasibility of the alignment of boxes on the strip depends on which way the box is placed, regularly or rotated.
-\end{itemize}
 
@@
 Introduction
-\begin{itemize}
-	\item This alg will be combining a well known heuristic with an exact algorithm to find a feasible solution to the SCBPP
-	\item Becker 2010 recognicity algorithm in polynomial time
-	\item doesn't take into account individual widths of boxes
-	\item only one strip/align all boxes into one row
-	\item in industry, strips have a finite length
-	\item algorithm also doesn't output a full solution, only whether there exists a feasible solution or not
-	\item ffd but including an algorithm that can find a feasible aligment of boxes with score constraints if one exists
-	\item unlike ffd, where boxes are placed onto the end of each strip, the boxes are not fixed in place, all boxes can be reordered.
-	\item Can find a solution for a set of boxes on a strip when it may not have been possible to find one in ffdapprox due to only the last box being checked.
-	\item try to find a hamiltonian path 
-	\item complexity $O(n^2), O(n)$ to construct a solution
-	\item if the algorithm cannot find a feasible alignment of the boxes including the current box, move onto next strip and try again.
-\end{itemize}
 
@@
 
-\begin{itemize}
-	\item \textcolor{Plum}{``Dowsland and Dowsland (1992, ``Packing Problems'') comment that while average or worst-case performance bounds are useful guidelines, it is best to determine an algorithm's usefuless by testing it on data sets typical to the intended problem.
-Repositories are available on the internet where benchamrk data sets for packing problems are stored for the purpose of evaluating algorithms.''}
-\end{itemize}
-
 \section{Conclusion}
@@
 \section{References}
-\cite{becker2010}: Twin Constrainted Hamiltonain Paths on Threshold Graphs
+\cite{becker2010}, \cite{becker2015}, \cite{coffman1978}, \cite{dosa2007}, \cite{eilon1971}, \cite{garey1979}, \cite{gilmore1961}, \cite{gilmore1963}, \cite{goulimis2004}, \cite{johnson1974}, \cite{karp1972}, \cite{korf2002}, \cite{lewis2009}, \cite{lewis2017}, \cite{lewis2011}, \cite{mahadev1994}, \cite{mahadev1995}, \cite{martello1990a}, \cite{martello1990b}
 
-\cite{becker2015}: A Heuristics for the MSSP
-
-\cite{coffman1978}: An Application of Bin-Packing to Multiprocessor Scheduling
-
-\cite{coffman1984}: Approximation Algorithms for Bin-Packing - An Updated Survey.
+\section{Layout}
+Introduction:
 \begin{itemize}
-	\item \textcolor{Plum}{``first fit and first fit decreasing algorithms have equivalent worst-case time complexities of O(n ln n) (cite coffman1984)''}
-	\item \textcolor{Plum}{``we refer the interested reader to the excellent survery by (cite coffman1984), which includes a bibliography of more than one hundred titles''}
-	\item \textcolor{Plum}{``A comprehensive review of various heuristic algorithms is provided in a recent survery by (cite coffman1984)''}
-	\item \textcolor{Plum}{``(cite coffman1984) did an excellent survey on this problem, particularly on approximation algorithms and their asymptotic performance ratios''}
+	\item One-dimensional BPP, NP-Hard.
+	\item Goulimis packing boxes onto \textit{one} strip, where boxes have score constraints.
+	\item Describe boxes, scores, score widths, minimum total score width constraint, scoring knives on bar etc. (include figure(s)).
+	\item Becker has created a polynomial time algorithm for this problem (again, only on \textit{one} strip).
+	\item How we adapt this problem: we take into account the width of each individual box (added widths to the boxes, not included by Becker), multiple strips, fixed lengths, if there was an instance with many boxes it's unlikely they would all fit onto one strip, strips come in fixed lengths that cannot be changed.
+	\item Our problem: pack the boxes onto multiple strips of fixed lengths while meeting the minimum total score width constraint, not exceeding the capacity of the strips, and trying to minimise the number of strips used (perhaps mention minimising waste per strip?).
+	\item Are there any similar problems? Who has researched this problem/similar problem, and using what methods? \cite{lewis2017} trapezoids paper. 
+	\item Explain \textit{why this problem is important} (see above, strips come in fixed lengths, becker's algorithm is rendered useless if the total width of all boxes exceeds the length of one strip).
+	\item Outline rest of paper.	
 \end{itemize}
 
-\cite{dosa2007}: The tight bound of first fit decreasing bin packing algorithm
-
-\cite{eilon1971}: The loading problem. 
+Lit Review
 \begin{itemize}
-	\item \textcolor{Plum}{``(cite eilon1971) presented a depth-first enumerative algorithm''}
-	\item \textcolor{Plum}{``(cite eilon1971) discuss its(the BPP) application to the loading of vehicles (or other containers) with consignment''}
-	\item \textcolor{Plum}{``the most well-known heuristics are the FFD and the BFD (cite eilon1971)''}
+	\item Solving the one-dimensional bpp using exact methods and heuristics.
+	\item Exact methods - \cite{martello1990a} branch and bound based exact algorithm MTP, Carvalho 1999 column generation and branch-and-bound, \cite{eilon1971} depth-first search enumerative algorithm, only solve small size problem instances.
+	\item \cite{garey1979} \textcolor{RoyalBlue}{NP-Hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP.}
+	\item \textcolor{RoyalBlue}{Instead, heuristics can be used to find a near optimal solution in a shorter amount of time}.
+	\item discuss heuristics.
+	\item Explain FF and FFD, online/offline \cite{eilon1971}, \cite{dosa2007} tight bound, optimal number of bins $k$ \cite{korf2002}, complexity $O(n \log n)$ \cite{coffman1984} (where n is the number of items to be packed).
+	\item quickly produce a feasible solution, but may not be optimal.
+	\item Use heuristics in this paper to find feasible solutions for the problem, why?
 \end{itemize}
 
-\cite{garey1979}: Computers and Intractibility - A Guide to the Theory of NP-Completeness. 
+Notation and Formulating the problem
 \begin{itemize}
-	\item \textcolor{Plum}{``(cite garey1979) cite simple heuristics which can be shown to be noworse(but also no better) than a rather small multiplying factor above the optimal number of bins.''}
-	\item \textcolor{Plum}{``the bpp problem is NP-Hard''}
+	\item $n$ boxes, $i = 1, 2, ..., n$, same height, different widths.
+	\item Each box $i$ has a total width $w(i)$.
+	\item Each box $i$ has two scores, $i_1$ (the smaller score), and $i_2$ (the larger score), and widths $w(i_1), w(i_2)$, such that $w(i_1) \leq w(i_2)$.
+	\item Score widths not necessarily equal, therefore box has two different positions.
+	\item $\{i_1, i_2\}$ represents ``regular'' box $i$: $i_1$ on LHS of box.
+	\item $\{i_2, i_1\}$ represents ``rotated'' box $i$: $i_2$ on LHS of box (box rotated by $180^{\circ}$).
+	\item Boxes will be placed side by side.
+	\item All box widths $w(i) > 0$ and all score widths $w(i_1), w(i_2) > 0$ $\forall$ $i = 1, 2, ..., n$.
+	\item Finite number of strips $S_j$, $j = 1, 2, ...$.
+	\item All strips $S_j$ have equal fixed length $l > 0$ $\forall$ $j = 1, 2, ...$.
+	\item All strips $S_j$ have a residual length $r(j)$, initially $r(j) = l$ $\forall$ $j = 1,2, ...$, which reduces as boxes are added to each strip.
+	\item Assumption: all box widths $w(i) \leq l, i = 1, 2, ..., n$
+	\item Initially, $S_j = \emptyset$ $\forall$ $j = 1, 2, ...$.
+	\item For all strips $S_j \neq \emptyset$, the score on the right hand side of the last box in the strip is called the ``free score'', denoted $f_j$, with width $w(f_j)$.
+	\item The sum of two adjacent score widths must fulfil the minimum total score width constraint ... $t$ is the minimum total score width.
+	\item The minimum total score width constraint must be fulfilled in order for the scoring knives to be able to score the boxes correctly.
+	\item The \textit{minimum total score width} is denoted by $t, t > 0$ \textcolor{RoyalBlue}{usually 70mm in industry}.
+\textcolor{RoyalBlue}{The \textit{minimum total score width constraint} is $w(u_p) + w(v_q) \geq t$, $u \neq v, p, q = 1 or 2$.}
+	\item Strips packed from left to right.
+	\item $l > 0, w(i) > 0, w(i) \leq l$
+	\item Need to pack the boxes onto the strips so mtswc is met and least number of strips used.
+	\item Formal definition of Score-Constrained Bin Packing Problem
 \end{itemize}
 
-\cite{gilmore1961}: A LP Approach to the CSP Part 1
-
-\cite{gilmore1963}: A LP Approach to the CSP Part 2
-
-\cite{goulimis2004}: Minimum Score Separation
-
-\cite{johnson1974}: Worst case performance bounds for simple one-dimensional packing algorithms
+FFD Approx
 \begin{itemize}
-	\item \textcolor{Plum}{ ``(cite johnson1974) discuss three practical applications in computer science, which are table formatting, prepaging, and file allocation''}
+	\item Explain FFD modified for scored boxes (basic).
+	\item Free score $f_j$, residual length $r(j)$.
+	\item Figure: partially packed strip showing first box in regular position, free score, minimum total score width constraint met between boxes, residual length.
+	\item Pseudocode
+	\item Description of algorithm
+	\item Complexity, discuss how algorithm only checks if current box meets constraint with free score on final box, boxes are not able to be rearranged, even though there may be another arrangement of the boxes that is feasible (lead on to next algorithm FFD using exact algorithm).
 \end{itemize}
 
-\cite{karp1972}: Reducibility among combinatorial problems
+FFD Using Exact Algorithm
+\begin{itemize}
+	\item Combine FFD with exact algorithm to find a feasible solution to the SCBPP
+	\item Unlike FFD approx, where attempts are made to place each box at the end of a strip, this algorithm is able to rearrange the order of the boxes in a strip to find a feasible arrangement.
+	\item Can find a solution for a set of boxes on a strip when it may not have possible to find one in ffdapprox
+	\item Describe Becker algorithm, using graph theory, Hamiltonian path/cycle
+	\item Notation for Exact algorithm:
+	\item $n$ boxes including dummy box.
+	\item $2n$ vertices including dominating vertices.
+	\item Graph $G$ is an undirected graph with $2n$ vertices $v_i, i = 1, 2, ...,2n$.
+	\item Vertices are weighted, $w(v_i)$.
+	\item Vertices that represent either side of same box referred to as ``partners''
+	\item $P$ contains the set of edges between partners, fixed, $|P| = n$.
+	\item Edges in $P$ are weighted, corresponding to box width.
+	\item $Q$ contains the set of edges between vertices that meet the minimum total score width constraint, excluding partners (these edges are not weighted).
+	\item $G(V, P \cup Q)$ - each edge on $G$ is either in $P$ or $Q$, not both.
+	\item $t$ still represents the minimum total score width.
+	\item $M$ is the set of matching edges, $M \subset Q$, edges chosen using the matching algorithm (need $|M| = n$).
+	\item number of cycles on $G$ after MTGMA =  ?
+	\item $C_k$: sets of edges for connecting cycles.
+	\item Section: Becker algorithm
+	\item Combine alg with ffd
+	\item Pseudocode
+	\item Description of algorithm
+	\item Complexity
+\end{itemize}
 
-\cite{korf2002}: A new algorithm for optimal bin packing.
-\textcolor{Plum}{``If the number of bins in a solution is equivalent to the expression (sum of all weights/ capacity) then that solution is an optimal solution to the problem instance (cite Korf2002)''}
+Comparison/Results
 
-\cite{lewis2009}: A general-purpose hill-climbing method for order independent minimum grouping problems
-
-\cite{lewis2017}: How to pack trapezoids
-
-\cite{lewis2011}: An investigation into two bpp with ordering and orientation implications
-
-\cite{mahadev1994}: Longest cycle in threshold graphs
-
-\cite{mahadev1995}: Threshold graphs and related topics
-
-\cite{martello1990b}: Knapsack problems.\textcolor{Plum}{ ``(cite martello1990) proposed a branch-and-bound based exact algorithm MTP for the BPP.''}
+Conclusion
 

### 2018-01-14 paper/main.tex
main paper

\documentclass[oribibl]{llncs}

\input{includes/preamble.tex}

\title{Heuristics for the Score-Constrained Bin-Packing Problem}
\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
	This version started: 14/01/2018
\end{abstract}

\section{Introduction}
\label{sec:intro}

The one-dimensional bin-packing problem (BPP) is a combinatorial optimisation problem that has been widely researched and discussed due to its ability to model a variety of real-life situations. The BPP can be described as follows: given a set of $n$ items of varying sizes $w$, and a finite number of bins with equal capacity $c$, find the minimum number of bins required to contain all of the items. In 2004, \citeauthor{goulimis2004} brought to light an open-combinatorial problem related to the bin-packing problem. Corrugated boxes are formed in two stages: firstly, they are produced flat, then a device consisting of knives mounted of a bar creates scores along specific lines on the flat boxes. These scores allow the boxes to be folded in predetermined locations. The first stage of this process is a cutting stock problem, and involves finding a feasible pattern of the flat boxes that minimises the amount of waste. This problem has been researched extensively, and can be solved using delayed column-generation (\citealp{gilmore1961, gilmore1963}). However, the second strip of this process requires an additional constraint.

The scoring knives are arranged in pairs, and cut along score lines from two adjacent boxes simultaneously. By design, the knives cannot be placed too close to one another, and so the distance between the scoring knives must exceed a fixed minimum value $\tau \in \mathbb{R}^{+}$ (around 70mm in industry). The problem therefore consists of finding a feasible arrangement of boxes such that the distance between two score lines is greater than or equal to $t$.

There exists a polynomial-time algorithm that is able to recognise whether a particular instance of this problem is feasible (\citealp{becker2010}). However, this algorithm does not consider the widths of each individual box, and only attempts to place the boxes onto a single strip. In industry, strips of material are provided in fixed lengths, and so given a large problem instance multiple strips may be required to feasibly accommodate all of the boxes without exceeding the capacity of the strips.

This leads us to our main problem: given a collection of boxes of varying widths and a finite number of strips of fixed lengths, find the minimum number of strips required to feasibly pack all of the boxes such that the distance between two adjacent score lines on every pair of boxes is greater than or equal to some fixed value $\tau$ on all strips.

The remainder of this article will firstly, in Section \ref{sec:scbpp}, state the notation that will be used throughout, and formally define the problem. Section \ref{sec:ffdapprox} will introduce a modified first-fit decreasing heuristic and describe the changes made to consider the new constraint. In Section \ref{sec:ffdexact}, we will present a new algorithm which consists of the modified heuristic detailed in the previous section combine with a polynomial-time algorithm which will be used to find feasible sub-solutions. A comparison of the two heuristics and an analysis of the results will be provided in Section \ref{sec:comparison}, and finally Section \ref{sec:conclusion} concludes the paper and proposes some potential directions for future work.

\section{Formulating the Score-Constrained Bin-Packing Problem}
\label{sec:scbpp}
Insert lit review here.

Let each box $i$ of a set of $n$ boxes have a positive width $w(i)$. A ``score width'' is the distance between a score line and the nearest edge of the box. Each box $i$ has two score lines, $i_1, i_2$, with score widths $w(i_1), w(i_2)$ such that $w(i_1) \leq w(i_2)$. Since these score widths are not necessarily equal, each box can be algined in two distinct ways: in a ``regular'' position, where the smaller score width $w(i_1)$ is on the left-hand side of the box, or in a ``rotated'' position, with the smaller score width on the right-hand side of the box. The boxes can be expressed using their score lines, where $\{i_1, i_2\}$ represents a regular position, and $\{i_2, i_1\}$ a rotated position.

Given the minimum fixed value $\tau$, two boxes can only be placed next to one another if the adjacent score lines $\alpha$ and $\beta$ fulfil the \textit{minimum total score width constraint},

\begin{equation*}
	\label{eqn:mtswc}
	w(\alpha) + w(\beta) \geq \tau,
\end{equation*}

that is, the sum of the adjacent score widths must exceed the \textit{minimum total score width} $\tau$.

There are a finite number of strips $S_j, j = 1, 2, ...$, with equal fixed lengths $l > 0$, that are to be packed from left to right. Assume that, for all boxes $i = 1, 2, ..., n$, $w(i) \leq l$, and $0 < w(i_1) \leq w(i_2) \leq \tau$. We are now able to present a formal definition of the problem.

\begin{definition}
	Given $n$ boxes of varying widths $w(i)$ and score widths $w(i_1), w(i_2)$, $i = 1, 2, ..., n$, a finite number of strips $S_j$ with equal fixed lengths $l$, and a minimum total score width $\tau$, the Score-Constrained Bin-Packing Problem (SCBPP) consists of finding the minimum number of strips required to pack the boxes such that the minimum total score width constraint is met between every pair of adjacent boxes. 
\end{definition}

\section{FFD Approx}
\label{sec:ffdapprox}

\section{FFD Exact}
\label{sec:ffdexact}

\section{Comparison and results}
\label{sec:comparison}

\section{Conclusion}
\label{sec:conclusion}

\bibliographystyle{dcu}
\bibliography{includes/bibliography}

\end{document}

### 2018-01-15 paper/main.tex
updated main paper

@@
 Each box $i$ has two score lines, $i_1, i_2$, with score widths $w(i_1), w(i_2)$ such that $w(i_1) \leq w(i_2)$.
-Since these score widths are not necessarily equal, each box can be algined in two distinct ways: in a ``regular'' position, where the smaller score width $w(i_1)$ is on the left-hand side of the box, or in a ``rotated'' position, with the smaller score width on the right-hand side of the box.
+Since these score widths are not necessarily equal, each box can be aligned in two distinct ways: in a ``regular'' position, where the smaller score width $w(i_1)$ is on the left-hand side of the box, or in a ``rotated'' position, with the smaller score width on the right-hand side of the box.
 The boxes can be expressed using their score lines, where $\{i_1, i_2\}$ represents a regular position, and $\{i_2, i_1\}$ a rotated position.
@@
 
+\begin{algorithm}[H]
+	\caption{\textcolor{OliveGreen}{Approximate First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
+	\label{alg:ffdapprox}
+	\begin{algorithmic}[1]
+	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, minimum total score width $\tau$, and a set $\mathcal{S} = \emptyset$.
+	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.
+	\State Sort the boxes in order of non-increasing widths.
+	\For{$i \gets 1 \To n$}
+		\For{$j \gets 1 \To n$}
+			\If{$S_j = \emptyset$}
+				\State $S_j \gets \{i_1, i_2\}$
+				\State $r(j) \gets r(j) - w(i)$
+				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
+				\Break
+			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
+				\If{$w(f_j) + w(i_1) \geq \tau$}
+					\State $S_j \gets S_j \cup \{i_1, i_2\}$
+					\State $r(j) \gets r(j) - w(i)$
+					\Break
+				\ElsIf{$w(f_j) + w(i_2) \geq \tau$}
+					\State $S_j \gets S_j \cup \{i_2, i_1\}$
+					\State $r(j) \gets r(j) - w(i)$
+					\Break
+				\EndIf
+			\EndIf
+		\EndFor
+	\EndFor
+	\Return $\mathcal{S}$
+	\end{algorithmic}	
+\end{algorithm}
+
+Initially, the algorithm arranges the boxes in non-increasing order of widths, breaking ties by choosing the box with the smallest score width.
+For each box $i$ in the sorted list, the algorithm find the lowest-indexed strip $S_j$ that is able to feasibly accommodate $i$.
+If $S_j$ is empty, $i$ is placed in a regular position onto $S_j$, which is then added to a set $\mathcal{S}$ that maintains a record of strips that are being packed.
+However, if $S_j$ is not empty, the algorithm checks the minimum total score width constraint with $i$ firstly in a regular position, then in a rotated position.
+If the constraint is met in either case, $i$ is placed accordingly onto $S_j$.
+If neither positions are able to fulfil the constraint, the algorithm moves onto the next strip $S_{j+1}$ and the process of attempting to pack $i$ is repeated.
+Once a box $i$ has been placed onto a strip, the algorithm moves onto the next box $i+1$, until all of the boxes have been packed.
+
 \section{FFD Exact}
 \label{sec:ffdexact}
+
+Let each box be represented by two vertices on a graph $G$, one vertex for each side of a box.
+A ``dummy'' box is introduced, with two ``dominating'' score widths equal to the minimum total score width $\tau$.
+This dummy box will be discarded at the end of the algorihtm, and will not be included in the final solution.
+Thus, there are $n$ boxes, including the dummy box, and so $G$ will consist of $2n$ vertices.
+
+Two vertices $v_i, v_j$ $(i \neq j)$ that represent either side of the same box are referred to as ``partners''.
+The boxes cannot be altered in any way, and so partners must always be adjacent to one another.
+Therefore, a set $P$ is created, consisting of edges between partners on $G$.
+These edges are weighted, with values corresponding to the width of the box that the partners are associated with.
+
+Each vertex $v_i, i = 1, 2, ..., 2n$ has a postive value $w(v_i)$ corresponding to the score width it represents.
+There is an edge between two vertices $v_i, v_j$ $(i \neq j)$ on $G$ if and only if the vertices fulfil the minimum total score width constraint,
+
+\begin{equation*}
+	w(v_i) + w(v_j) \geq \tau,
+\end{equation*}
+
+and $v_i, v_j$ are not partners, i.e.
+$\{v_i, v_j\} \notin P$.
+The vertices $v_i, v_j$ are then referred to as ``matched'', and so their corresponding score widths can be feasibly placed next to one another.
+Hence there is another set of edges $Q$, which contains edges between matched vertices.
+
+Thus, $G(V, P\cup Q)$ is an undirected graph with vertex set $V = \{v_1, v_2, ..., v_{2n}\}$, and two edge sets $P$ and $Q$, with $P \cap Q = \emptyset$.
+In order to find a feasible alignment of the boxes, $G$ must contain an alternating Hamiltonian cycle.
+
+\begin{definition}
+	\label{defn:althamcycle}
+	Let $G(V, P\cup Q)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $Q$.
+$G$ has an \textit{alternating Hamiltonian cycle} if there exists a Hamiltonian cycle on $G$ such that the successive edges alternate between sets $P$ and $Q$.
+For example, if vertex $v_i$ in the Hamiltonian cycle is adjacent to vertex $v_{i-1}$ via an edge from $P$, then $v_i$ must be adjacent to vertex $v_{i+1}$ via an edge from $Q$, or vice versa.
+\end{definition}
+
+If $G$ does contain an alternating Hamiltonian cycle, the algorithm simply removes the dominating vertices and any associated edges to obtain an alternating Hamiltonian path, which portrays the order of the score widths that gives rise to a feasible alignment of the boxes.
+Thus, the aim of the algorithm is to find an alternating Hamiltonian cycle on $G$, if one exists.
+
+The next step of the algorithm attemps to obtain a set of matching edges $M \subset Q$ of cardinality $n$, such that the edges from $M$ and $P$ form an alternating Hamiltonain cycle as described in Definition \ref{defn:althamcycle}.
+There is a modified matching algorithm (\citealp{mahadev1994, becker2010}) that is able to choose a suitable set of edges for $M$.
+
+Initially, the vertices are sorted in order of non-decreasing values $w(v_i), i = 1,2, .., 2n$, with ties broken arbitrarily.
+For each vertex in the list, find the largest adjacent vertex in $Q$ that has not yet been added to the matching set $M$.
+This pair of vertices is then added to $M$, and the algorithm proceeds on to the next vertex in the sorted list.
+This process continues until all of the vertices have been assessed.
+
+If a vertex $v_i$ is not adjacent to any other vertex except its partner, the previous vertex can be rematched, provided $v_i$ is not the first vertex in the sorted list, the previous vertex $v_{i-1}$ is matched under $M$ (i.e.
+$v_{i-1} \in M$), and $v_{i-1}$ is adajcent to $v_i$'s partner.
+Then, $v_{i-1}$ is matched with $v_i$'s partner, and $v_i$ is matched with $v_{i-1}$'s previous match under $M$.
+It is guaranteed that this algorithm will produce a maximum cardinality matching $M \subset Q$ (\citealp{becker2010}).
+
+If $|M| < n$, there are not enough matching edges to form an alternating Hamiltonian cycle with the edges in $P$, and therefore there is no feasible arrangement of the boxes such that the minimum total score width constraint is not violated.
+However, if $|M| = n$, then the graph $G(V, P \cup M)$ is a 2-regular graph where each vertex is adjacent to one vertex (its partner) via an edge in $P$, and another vertex (its match) via an edge in $M$.
+If $G$ consists of one alternating Hamiltonian cycle, the dominating vertices are removed to obtain a feasible alignment of the boxes.
+If there are two or more cycles on $G(V, P \cup M)$, a solution to the problem has not yet been found.
+These cycles need to be combined into one single alternating Hamiltonian cycle.
+
+To merge the multiple cycles on $G$, we need to connect vertices from different cycles by removing some matching edges and adding new edges from $Q$.
+The following algorithm finds the matching edges on the graph $G(V, P \cup M)$ that allow the cycles to be combined.
+
+The algorithm initially creates a list of all matching edges in $M$, sorted in order of non-decreasing vertex values.
+Starting from the first edge, the algorithm searches through the list of edges until it finds an edge whose smaller vertex is adjacent via an edge in $Q$ to the larger vertex of the succeeding edge in the list, such that both edges are from different cycles on the graph $G$.
+If such a pair of edges is found, the first edge of the pair is added to a set $C_k$.
+The algorithm then continues to add all succeeding edges to $C_k$, provided that the smaller vertex of the current edge is adjacent to the larger vertex of the succeeding edge via an edge in $Q$, the succeeding edge does not belong to a cycle that is already represented by an edge in $C_k$, and the algorithm has not reached the final edge in the list.
+Once there are no more valid edges to add to $C_k$, the algorithm proceeds to the next edge in the list, and checks whether this edge is suitable for beginning a new set $C_{k+1}$.
+If the penultimate or final edge in the list is reached, the algorithm terminates.
+
+If the algorithm does not produce a single set $C$, there are no edges available to connect the cycles together, and therefore no feasible alignment of the boxes in this problem instance exists.
+\textcolor{RoyalBlue}{also if the set $C$ doesn't include an edge from every cycle, or multiple sets $C$ that don't cover all cycles, infeasible.}
+
+If there exists a set $C_k$ such that $|C_k| = \textcolor{OliveGreen}{number of cycles}$, then the cycles can be connected as follows: starting from the first edge in $C_k$, connect the smaller vertex to the larger vertex of the second edge in the set.
+Then, connect the smaller vertex of the second edge to the larger vertex of the third edge.
+Continue in this manner until the last edge in $C_k$ is reached, and connect the lower vertex of this final edge to the larger vertex of the first edge.
+These new matching edges will join the distinct cycles together to form one alternating Hamiltonian cycle.
+The edges in the set $C_k$ can be removed from the graph $G$
+
+\textcolor{RoyalBlue}{Multiple $C_k$ cycles required.}
+
+\begin{algorithm}[H]
+	\caption{\textcolor{OliveGreen}{Exact First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
+	\label{alg:ffdexact}
+	\begin{algorithmic}[1]
+	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, and a set $\mathcal{S} = \emptyset$.
+	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.	
+	\State Sort the boxes in order of non-increasing widths
+	\For{$i \gets 1 \To n$}
+		\For{$j \gets 1 \To n$}
+			\If{$S_j = \emptyset$}
+				\State $S_j \gets \{i_1, i_2\}$
+				\State $r(j) \gets r(j) - w(i)$
+				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
+				\Break
+			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
+				\State \textcolor{RoyalBlue}{Run} \textcolor{OrangeRed}{``MBAHRA''} \textcolor{RoyalBlue}{on boxes in $S_j$ and box $i$}
+				\If{feasible alignment found}
+					\State $S_j \gets$ \textcolor{RoyalBlue}{new alignment found by} \textcolor{OrangeRed}{``MBAHRA''}
+					\State $r(j) \gets r(j) - w(i)$
+					\Break
+				\EndIf
+			\EndIf
+		\EndFor
+	\EndFor
+	\Return $\mathcal{S}$
+	\end{algorithmic}	
+\end{algorithm}
+
+\textcolor{RoyalBlue}{In a similar fashion/manner to ``FFD approx'' (rename)} The algorithm starts by sorting the boxes in order of non-increasing widths, with ties broken by choosing the box with the smallest score width.
+Starting with the first box, the algorithm finds the lowest-indexed strip $S_j$ that can feasibly accommodate the current box $i$.
+If $S_j$ is empty, box $i$ is placed onto $S_j$ in a ``regular'' position \textcolor{RoyalBlue}{(i.e.
+smallest score width on the LHS of the box)}.
+This strip is added to the set $\mathcal{S}$ that keeps track of the strips being used to form a solution, and the algorithm proceeds onto the next box $i+1$ in the sorted list.
+
+If $S_j$ is not empty \textcolor{RoyalBlue}{(i.e contains at least one box, $|S_j| > 0$)}, then \textcolor{OrangeRed}{MBAHRA} is performed on all of the boxes in $S_j$ and the current box $i$.
+If a feasible alignment of the boxes has been found, the current boxes on $S_j$ are replaced with the new alignment, and the algorithm proceeds onto the next box $i+1$.
+If \textcolor{OrangeRed}{MBAHRA} is unable to find a feasible alignment of the boxes, the algorithm moves onto the next strip $S_{j+1}$ and the process is repeated.
+The algorithm continues until all of the boxes have been packed.
+\textcolor{RoyalBlue}{Complexity}
 

### 2018-01-15 paper/paper.tex
using as draft, added date
changed spelling error

@@
 
-\title{Heuristics for the Score-Constrained Bin-Packing Problem}
+\title{DRAFT}
 \author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
@@
 \begin{abstract}
-	Abstract
+	This version finished: 13/01/2018
 \end{abstract}
@@
 
-In 2004, Goulimis brought to light an open-combinatorial problem related to the bin-packing problem.
+In 2004, \citeauthor{goulimis2004} brought to light an open-combinatorial problem related to the bin-packing problem.
 Corrugated boxes are formed in two stages: firstly, they are produced flat, then a device consistsing of knives mounted on a bar creates ``scores'' along specific lines on the flat boxes.
@@
 The algorithm then continues to add all succeeding edges to $C_k$, provided that the smaller vertex of the current edge is adjacent to the larger vertex of the succeeding edge via an edge in $Q$, the succeeding edge does not belong to a cycle that is already represented by an edge in $C_k$, and the algorithm has not reached the final edge in the list.
-Once there are no more valid edges to add to $C_k$, the algorithm proceeds to the next edge in the list, and checked whether this edge is suitable for beginning a new set $C_{k+1}$.
+Once there are no more valid edges to add to $C_k$, the algorithm proceeds to the next edge in the list, and checks whether this edge is suitable for beginning a new set $C_{k+1}$.
 If the algorithm has already reached the penultimate or final edge in the list, the algorithm terminates.

### 2018-01-15 paper/main.tex
updated main.tex

@@
 \label{sec:ffdapprox}
+
+The first heuristic to be dicussed is a first-fit decreasing heuristic, modified to account for the minimum total score width constraint.
+The strips are initially empty, thus we define a residual length $r(j)$ for each strip $S_j, j = 1, 2, ...$.
+The residual lengths are set equal to the strip lengths $l$, and reduce as boxes are added to the strips.
+Each strip $S_j$ that is packed with at least one
 

### 2018-01-16 paper/main.tex
added citations

@@
 \begin{abstract}
-	This version started: 14/01/2018
+
 \end{abstract}
@@
 By design, the knives cannot be placed too close to one another, and so the distance between the scoring knives must exceed a fixed minimum value $\tau \in \mathbb{R}^{+}$ (around 70mm in industry).
-The problem therefore consists of finding a feasible arrangement of boxes such that the distance between two score lines is greater than or equal to $t$.
+The problem therefore consists of finding a feasible arrangement of boxes such that the distance between two score lines is greater than or equal to $\tau$.
 
@@
 \begin{definition}
+	\label{defn:scbpp}
 	Given $n$ boxes of varying widths $w(i)$ and score widths $w(i_1), w(i_2)$, $i = 1, 2, ..., n$, a finite number of strips $S_j$ with equal fixed lengths $l$, and a minimum total score width $\tau$, the Score-Constrained Bin-Packing Problem (SCBPP) consists of finding the minimum number of strips required to pack the boxes such that the minimum total score width constraint is met between every pair of adjacent boxes.
@@
 The residual lengths are set equal to the strip lengths $l$, and reduce as boxes are added to the strips.
-Each strip $S_j$ that is packed with at least one
+Each strip $S_j$ that is packed with at least one box has a ``free'' score $f_j$, the score on the right-hand side of the last box on the strip.
+A box can only be placed onto $S_j$ if the box can feasibly fit onto the strip, i.e.
+the width of th box is less than or equal to the residual length of the strip, and if $f_j$ and the left-hand socre of the box meet the minimum total score width constraint.
+Since each box has two position, regular and rotated, the heuristic checks if the constraint is met in both positions, favouring the regular position.
+If a box is only able to fit onto a strip that is empty, then the box is placed onto the strip in a regular position.
 
@@
 
+Insert introduction to FFD Exact.
+
 Let each box be represented by two vertices on a graph $G$, one vertex for each side of a box.
@@
 \begin{equation*}
+	\label{eqn:mtswcg}
 	w(v_i) + w(v_j) \geq \tau,
@@
 
-\textcolor{RoyalBlue}{Multiple $C_k$ cycles required.}
+-Multiple $C_k$ cycles required.
 
@@
 
+\section{Layout}
+Introduction:
+\begin{itemize}
+	\item One-dimensional BPP, NP-Hard.
+	\item Goulimis packing boxes onto \textit{one} strip, where boxes have score constraints.
+	\item Describe boxes, scores, score widths, minimum total score width constraint, scoring knives on bar etc. (include figure(s)).
+	\item Becker has created a polynomial time algorithm for this problem (again, only on \textit{one} strip).
+	\item How we adapt this problem: we take into account the width of each individual box (added widths to the boxes, not included by Becker), multiple strips, fixed lengths, if there was an instance with many boxes it's unlikely they would all fit onto one strip, strips come in fixed lengths that cannot be changed.
+	\item Our problem: pack the boxes onto multiple strips of fixed lengths while meeting the minimum total score width constraint, not exceeding the capacity of the strips, and trying to minimise the number of strips used (perhaps mention minimising waste per strip?).
+	\item Are there any similar problems? Who has researched this problem/similar problem, and using what methods? \cite{lewis2017} trapezoids paper. 
+	\item Explain \textit{why this problem is important} (see above, strips come in fixed lengths, becker's algorithm is rendered useless if the total width of all boxes exceeds the length of one strip).
+	\item Outline rest of paper.	
+\end{itemize}
+
+Lit Review
+\begin{itemize}
+	\item Solving the one-dimensional bpp using exact methods and heuristics.
+	\item Exact methods - \cite{martello1990a} branch and bound based exact algorithm MTP, Carvalho 1999 column generation and branch-and-bound, \cite{eilon1971} depth-first search enumerative algorithm, only solve small size problem instances.
+	\item \cite{garey1979} NP-Hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP.
+	\item Instead, heuristics can be used to find a near optimal solution in a shorter amount of time.
+	\item discuss heuristics.
+	\item Explain FF and FFD, online/offline \cite{eilon1971}, \cite{dosa2007} tight bound, optimal number of bins $k$ \cite{korf2002}, complexity $O(n \log n)$ \cite{coffman1984} (where n is the number of items to be packed).
+	\item quickly produce a feasible solution, but may not be optimal.
+	\item Use heuristics in this paper to find feasible solutions for the problem, why?
+\end{itemize}
+
+Notation and Formulating the problem
+\begin{itemize}
+	\item $n$ boxes, $i = 1, 2, ..., n$, same height, different widths.
+	\item Each box $i$ has a total width $w(i)$.
+	\item Each box $i$ has two scores, $i_1$ (the smaller score), and $i_2$ (the larger score), and widths $w(i_1), w(i_2)$, such that $w(i_1) \leq w(i_2)$.
+	\item Score widths not necessarily equal, therefore box has two different positions.
+	\item $\{i_1, i_2\}$ represents ``regular'' box $i$: $i_1$ on LHS of box.
+	\item $\{i_2, i_1\}$ represents ``rotated'' box $i$: $i_2$ on LHS of box (box rotated by $180^{\circ}$).
+	\item Boxes will be placed side by side.
+	\item All box widths $w(i) > 0$ and all score widths $w(i_1), w(i_2) > 0$ $\forall$ $i = 1, 2, ..., n$.
+	\item Finite number of strips $S_j$, $j = 1, 2, ...$.
+	\item All strips $S_j$ have equal fixed length $l > 0$ $\forall$ $j = 1, 2, ...$.
+	\item All strips $S_j$ have a residual length $r(j)$, initially $r(j) = l$ $\forall$ $j = 1,2, ...$, which reduces as boxes are added to each strip.
+	\item Assumption: all box widths $w(i) \leq l, i = 1, 2, ..., n$
+	\item Initially, $S_j = \emptyset$ $\forall$ $j = 1, 2, ...$.
+	\item For all strips $S_j \neq \emptyset$, the score on the right hand side of the last box in the strip is called the ``free score'', denoted $f_j$, with width $w(f_j)$.
+	\item The sum of two adjacent score widths must fulfil the minimum total score width constraint ... $t$ is the minimum total score width.
+	\item The minimum total score width constraint must be fulfilled in order for the scoring knives to be able to score the boxes correctly.
+	\item The \textit{minimum total score width} is denoted by $\tau, \tau > 0$ (usually 70mm in industry).
+	\item Strips packed from left to right.
+	\item $l > 0, w(i) > 0, w(i) \leq l$
+	\item Need to pack the boxes onto the strips so mtswc is met and least number of strips used.
+	\item Formal definition of Score-Constrained Bin Packing Problem
+\end{itemize}
+
+FFD Approx
+\begin{itemize}
+	\item Explain FFD modified for scored boxes (basic).
+	\item Free score $f_j$, residual length $r(j)$.
+	\item Figure: partially packed strip showing first box in regular position, free score, minimum total score width constraint met between boxes, residual length.
+	\item Pseudocode
+	\item Description of algorithm
+	\item Complexity, discuss how algorithm only checks if current box meets constraint with free score on final box, boxes are not able to be rearranged, even though there may be another arrangement of the boxes that is feasible (lead on to next algorithm FFD using exact algorithm).
+\end{itemize}
+
+FFD Using Exact Algorithm
+\begin{itemize}
+	\item Combine FFD with exact algorithm to find a feasible solution to the SCBPP
+	\item Unlike FFD approx, where attempts are made to place each box at the end of a strip, this algorithm is able to rearrange the order of the boxes in a strip to find a feasible arrangement.
+	\item Can find a solution for a set of boxes on a strip when it may not have possible to find one in ffdapprox
+	\item Describe Becker algorithm, using graph theory, Hamiltonian path/cycle
+	\item Notation for Exact algorithm:
+	\item $n$ boxes including dummy box.
+	\item $2n$ vertices including dominating vertices.
+	\item Graph $G$ is an undirected graph with $2n$ vertices $v_i, i = 1, 2, ...,2n$.
+	\item Vertices are weighted, $w(v_i)$.
+	\item Vertices that represent either side of same box referred to as ``partners''
+	\item $P$ contains the set of edges between partners, fixed, $|P| = n$.
+	\item Edges in $P$ are weighted, corresponding to box width.
+	\item $Q$ contains the set of edges between vertices that meet the minimum total score width constraint, excluding partners (these edges are not weighted).
+	\item $G(V, P \cup Q)$ - each edge on $G$ is either in $P$ or $Q$, not both.
+	\item $t$ still represents the minimum total score width.
+	\item $M$ is the set of matching edges, $M \subset Q$, edges chosen using the matching algorithm (need $|M| = n$).
+	\item number of cycles on $G$ after MTGMA =  ?
+	\item $C_k$: sets of edges for connecting cycles.
+	\item Section: Becker algorithm
+	\item Combine alg with ffd
+	\item Pseudocode
+	\item Description of algorithm
+	\item Complexity
+\end{itemize}
+
+\section{References}
+\cite{becker2010}, \cite{becker2015}, \cite{coffman1978}, \cite{dosa2007}, \cite{eilon1971}, \cite{garey1979}, \cite{gilmore1961}, \cite{gilmore1963}, \cite{goulimis2004}, \cite{johnson1974worst}, \cite{johnson1974fast}, \cite{hung1978}, \cite{garey1972}, \cite{johnson1973}, \cite{karp1972}, \cite{korf2002}, \cite{lewis2009}, \cite{lewis2017}, \cite{lewis2011}, \cite{mahadev1994}, \cite{mahadev1995}, \cite{martello1990a}, \cite{martello1990b}
+
 \bibliographystyle{dcu}

### 2018-01-17 paper/main.tex
started lit review

@@
 \label{sec:scbpp}
-Insert lit review here.
+
+Despite the simplicity of the bin-packing problem statement, it has in fact been shown to be an NP-hard optimisation problem (\citealp{garey1979}).
+Thus, under the assumption that $P \neq NP$, there is no known algorithm that is able to find an optimal solution for every instance of the BPP in polynomial time.
+Instead, heuristics can be used to find near-optimal solutions within a shorter amount of time.
+One example is the greedy heuristic known as first-fit (FF), an online algorithm that places each item (in some arbitrary order) into the lowest-indexed bin such that the bin capacity is not exceeded.
+It has been seen that by arranging the items in decreasing order of sizes, a bin-packing heuristic will produce a solution that is closer to the optimal than if the items are arranged in any other order (\citealp{johnson1974fast}).
+Applying FF onto items sorted in this manner yields the well-known first-fit decreasing (FFD) heuristic.
+
+An optimal solution to an instance of the BPP is a solution that consists of the fewest number of bins, $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
+
+\begin{equation*}
+	k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{c}}
+\end{equation*}
+
+where $n$ is the number of items to be packed, $w_i$ the size of each item $i$, and $c$ the maximum capacity of the bins (\citealp{martello1990b}).
+In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ bins.
+More recently, \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight.
+Due to the initial sorting of the $n$ items in non-increasing order of sizes, FFD can be implemented in $O(n\log n)$ time.
+
+---------------------------------
 

### 2018-01-17 paper/main.tex
changed parts of sentences in lit review, changed w_i to w(i)

@@
 Thus, under the assumption that $P \neq NP$, there is no known algorithm that is able to find an optimal solution for every instance of the BPP in polynomial time.
-Instead, heuristics can be used to find near-optimal solutions within a shorter amount of time.
+Instead, heuristics can be used to find near-optimal solutions in a shorter amount of time.
 One example is the greedy heuristic known as first-fit (FF), an online algorithm that places each item (in some arbitrary order) into the lowest-indexed bin such that the bin capacity is not exceeded.
-It has been seen that by arranging the items in decreasing order of sizes, a bin-packing heuristic will produce a solution that is closer to the optimal than if the items are arranged in any other order (\citealp{johnson1974fast}).
+It has been shown that by arranging the items in decreasing order of size, a bin-packing heuristic will produce a solution that is closer to the optimal than if the items are arranged in any other order (\citealp{johnson1974fast}).
 Applying FF onto items sorted in this manner yields the well-known first-fit decreasing (FFD) heuristic.
 
-An optimal solution to an instance of the BPP is a solution that consists of the fewest number of bins, $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
+An optimal solution of an instance of the BPP is a solution that consists of the fewest number of bins, $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
 
 \begin{equation*}
-	k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{c}}
+	k \geq \ceil*{\frac{\sum_{i=1}^{n}w(i)}{c}}
 \end{equation*}
 
-where $n$ is the number of items to be packed, $w_i$ the size of each item $i$, and $c$ the maximum capacity of the bins (\citealp{martello1990b}).
+where $n$ is the number of items to be packed, $w(i)$ the size of each item $i$, and $c$ the maximum capacity of the bins (\citealp{martello1990b}).
 In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ bins.
 More recently, \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight.
-Due to the initial sorting of the $n$ items in non-increasing order of sizes, FFD can be implemented in $O(n\log n)$ time.
+Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time compelexity of FFD is $O(n\log n)$.
 

### 2018-01-18 paper/main.tex
new main.tex for updated version cutting stock problem

--- 2018-01-16 paper/main.tex
@@
 
-The one-dimensional bin-packing problem (BPP) is a combinatorial optimisation problem that has been widely researched and discussed due to its ability to model a variety of real-life situations.
-The BPP can be described as follows: given a set of $n$ items of varying sizes $w$, and a finite number of bins with equal capacity $c$, find the minimum number of bins required to contain all of the items.
-In 2004, \citeauthor{goulimis2004} brought to light an open-combinatorial problem related to the bin-packing problem.
-Corrugated boxes are formed in two stages: firstly, they are produced flat, then a device consisting of knives mounted of a bar creates scores along specific lines on the flat boxes.
-These scores allow the boxes to be folded in predetermined locations.
-The first stage of this process is a cutting stock problem, and involves finding a feasible pattern of the flat boxes that minimises the amount of waste.
-This problem has been researched extensively, and can be solved using delayed column-generation (\citealp{gilmore1961, gilmore1963}).
-However, the second strip of this process requires an additional constraint.
-
-The scoring knives are arranged in pairs, and cut along score lines from two adjacent boxes simultaneously.
-By design, the knives cannot be placed too close to one another, and so the distance between the scoring knives must exceed a fixed minimum value $\tau \in \mathbb{R}^{+}$ (around 70mm in industry).
-The problem therefore consists of finding a feasible arrangement of boxes such that the distance between two score lines is greater than or equal to $\tau$.
-
-There exists a polynomial-time algorithm that is able to recognise whether a particular instance of this problem is feasible (\citealp{becker2010}).
-However, this algorithm does not consider the widths of each individual box, and only attempts to place the boxes onto a single strip.
-In industry, strips of material are provided in fixed lengths, and so given a large problem instance multiple strips may be required to feasibly accommodate all of the boxes without exceeding the capacity of the strips.
-
-This leads us to our main problem: given a collection of boxes of varying widths and a finite number of strips of fixed lengths, find the minimum number of strips required to feasibly pack all of the boxes such that the distance between two adjacent score lines on every pair of boxes is greater than or equal to some fixed value $\tau$ on all strips.
-
-The remainder of this article will firstly, in Section \ref{sec:scbpp}, state the notation that will be used throughout, and formally define the problem.
-Section \ref{sec:ffdapprox} will introduce a modified first-fit decreasing heuristic and describe the changes made to consider the new constraint.
-In Section \ref{sec:ffdexact}, we will present a new algorithm which consists of the modified heuristic detailed in the previous section combine with a polynomial-time algorithm which will be used to find feasible sub-solutions.
-A comparison of the two heuristics and an analysis of the results will be provided in Section \ref{sec:comparison}, and finally Section \ref{sec:conclusion} concludes the paper and proposes some potential directions for future work.
-
-\section{Formulating the Score-Constrained Bin-Packing Problem}
-\label{sec:scbpp}
-Insert lit review here.
-
-Let each box $i$ of a set of $n$ boxes have a positive width $w(i)$.
-A ``score width'' is the distance between a score line and the nearest edge of the box.
-Each box $i$ has two score lines, $i_1, i_2$, with score widths $w(i_1), w(i_2)$ such that $w(i_1) \leq w(i_2)$.
-Since these score widths are not necessarily equal, each box can be aligned in two distinct ways: in a ``regular'' position, where the smaller score width $w(i_1)$ is on the left-hand side of the box, or in a ``rotated'' position, with the smaller score width on the right-hand side of the box.
-The boxes can be expressed using their score lines, where $\{i_1, i_2\}$ represents a regular position, and $\{i_2, i_1\}$ a rotated position.
-
-Given the minimum fixed value $\tau$, two boxes can only be placed next to one another if the adjacent score lines $\alpha$ and $\beta$ fulfil the \textit{minimum total score width constraint},
-
-\begin{equation*}
-	\label{eqn:mtswc}
-	w(\alpha) + w(\beta) \geq \tau,
-\end{equation*}
-
-that is, the sum of the adjacent score widths must exceed the \textit{minimum total score width} $\tau$.
-
-There are a finite number of strips $S_j, j = 1, 2, ...$, with equal fixed lengths $l > 0$, that are to be packed from left to right.
-Assume that, for all boxes $i = 1, 2, ..., n$, $w(i) \leq l$, and $0 < w(i_1) \leq w(i_2) \leq \tau$.
-We are now able to present a formal definition of the problem.
+Modification/adaption of the Pair Sequencing Problem (PSP) as seen in \cite{lewis2017}:
 
 \begin{definition}
-	\label{defn:scbpp}
-	Given $n$ boxes of varying widths $w(i)$ and score widths $w(i_1), w(i_2)$, $i = 1, 2, ..., n$, a finite number of strips $S_j$ with equal fixed lengths $l$, and a minimum total score width $\tau$, the Score-Constrained Bin-Packing Problem (SCBPP) consists of finding the minimum number of strips required to pack the boxes such that the minimum total score width constraint is met between every pair of adjacent boxes.
+	\label{defn:psp}
+	Let $\mathcal{P}$ be a multiset of unordered pairs $\mathcal{P} = \{\{x_1, y_1\}, \{x_2,y_2\},...,\{x_n,y_n\}\}$, $x_i, y_i \in \mathbb{Z}^{+}$ for $i \in \{1,2,...,n\}$, and let $\mathcal{X}$ be an ordering of the elements on $\mathcal{P}$ in which each element is also expressed as an ordered pair.
+The \textcolor{RoyalBlue}{constrained} PSP involves finding a solution $\mathcal{X}$ such that
+	\begin{equation*}
+		\textup{rhs}(i) + \textup{lhs}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\}
+	\end{equation*}
+	where \textup{lhs($i$)} and \textup{rhs($i$)} denote the values on the left- and right-hand sides of the $i$th ordered pair in $\mathcal{X}$, and $\tau \in \mathbb{R}^{+}$ is a fixed value.	
 \end{definition}
 
-\section{FFD Approx}
-\label{sec:ffdapprox}
+Adaptations from original PSP:
 
-The first heuristic to be dicussed is a first-fit decreasing heuristic, modified to account for the minimum total score width constraint.
-The strips are initially empty, thus we define a residual length $r(j)$ for each strip $S_j, j = 1, 2, ...$.
-The residual lengths are set equal to the strip lengths $l$, and reduce as boxes are added to the strips.
-Each strip $S_j$ that is packed with at least one box has a ``free'' score $f_j$, the score on the right-hand side of the last box on the strip.
-A box can only be placed onto $S_j$ if the box can feasibly fit onto the strip, i.e.
-the width of th box is less than or equal to the residual length of the strip, and if $f_j$ and the left-hand socre of the box meet the minimum total score width constraint.
-Since each box has two position, regular and rotated, the heuristic checks if the constraint is met in both positions, favouring the regular position.
-If a box is only able to fit onto a strip that is empty, then the box is placed onto the strip in a regular position.
-
-\begin{algorithm}[H]
-	\caption{\textcolor{OliveGreen}{Approximate First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
-	\label{alg:ffdapprox}
-	\begin{algorithmic}[1]
-	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, minimum total score width $\tau$, and a set $\mathcal{S} = \emptyset$.
-	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.
-	\State Sort the boxes in order of non-increasing widths.
-	\For{$i \gets 1 \To n$}
-		\For{$j \gets 1 \To n$}
-			\If{$S_j = \emptyset$}
-				\State $S_j \gets \{i_1, i_2\}$
-				\State $r(j) \gets r(j) - w(i)$
-				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
-				\Break
-			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
-				\If{$w(f_j) + w(i_1) \geq \tau$}
-					\State $S_j \gets S_j \cup \{i_1, i_2\}$
-					\State $r(j) \gets r(j) - w(i)$
-					\Break
-				\ElsIf{$w(f_j) + w(i_2) \geq \tau$}
-					\State $S_j \gets S_j \cup \{i_2, i_1\}$
-					\State $r(j) \gets r(j) - w(i)$
-					\Break
-				\EndIf
-			\EndIf
-		\EndFor
-	\EndFor
-	\Return $\mathcal{S}$
-	\end{algorithmic}	
-\end{algorithm}
-
-Initially, the algorithm arranges the boxes in non-increasing order of widths, breaking ties by choosing the box with the smallest score width.
-For each box $i$ in the sorted list, the algorithm find the lowest-indexed strip $S_j$ that is able to feasibly accommodate $i$.
-If $S_j$ is empty, $i$ is placed in a regular position onto $S_j$, which is then added to a set $\mathcal{S}$ that maintains a record of strips that are being packed.
-However, if $S_j$ is not empty, the algorithm checks the minimum total score width constraint with $i$ firstly in a regular position, then in a rotated position.
-If the constraint is met in either case, $i$ is placed accordingly onto $S_j$.
-If neither positions are able to fulfil the constraint, the algorithm moves onto the next strip $S_{j+1}$ and the process of attempting to pack $i$ is repeated.
-Once a box $i$ has been placed onto a strip, the algorithm moves onto the next box $i+1$, until all of the boxes have been packed.
-
-\section{FFD Exact}
-\label{sec:ffdexact}
-
-Insert introduction to FFD Exact.
-
-Let each box be represented by two vertices on a graph $G$, one vertex for each side of a box.
-A ``dummy'' box is introduced, with two ``dominating'' score widths equal to the minimum total score width $\tau$.
-This dummy box will be discarded at the end of the algorihtm, and will not be included in the final solution.
-Thus, there are $n$ boxes, including the dummy box, and so $G$ will consist of $2n$ vertices.
-
-Two vertices $v_i, v_j$ $(i \neq j)$ that represent either side of the same box are referred to as ``partners''.
-The boxes cannot be altered in any way, and so partners must always be adjacent to one another.
-Therefore, a set $P$ is created, consisting of edges between partners on $G$.
-These edges are weighted, with values corresponding to the width of the box that the partners are associated with.
-
-Each vertex $v_i, i = 1, 2, ..., 2n$ has a postive value $w(v_i)$ corresponding to the score width it represents.
-There is an edge between two vertices $v_i, v_j$ $(i \neq j)$ on $G$ if and only if the vertices fulfil the minimum total score width constraint,
-
-\begin{equation*}
-	\label{eqn:mtswcg}
-	w(v_i) + w(v_j) \geq \tau,
-\end{equation*}
-
-and $v_i, v_j$ are not partners, i.e.
-$\{v_i, v_j\} \notin P$.
-The vertices $v_i, v_j$ are then referred to as ``matched'', and so their corresponding score widths can be feasibly placed next to one another.
-Hence there is another set of edges $Q$, which contains edges between matched vertices.
-
-Thus, $G(V, P\cup Q)$ is an undirected graph with vertex set $V = \{v_1, v_2, ..., v_{2n}\}$, and two edge sets $P$ and $Q$, with $P \cap Q = \emptyset$.
-In order to find a feasible alignment of the boxes, $G$ must contain an alternating Hamiltonian cycle.
-
-\begin{definition}
-	\label{defn:althamcycle}
-	Let $G(V, P\cup Q)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $Q$.
-$G$ has an \textit{alternating Hamiltonian cycle} if there exists a Hamiltonian cycle on $G$ such that the successive edges alternate between sets $P$ and $Q$.
-For example, if vertex $v_i$ in the Hamiltonian cycle is adjacent to vertex $v_{i-1}$ via an edge from $P$, then $v_i$ must be adjacent to vertex $v_{i+1}$ via an edge from $Q$, or vice versa.
-\end{definition}
-
-If $G$ does contain an alternating Hamiltonian cycle, the algorithm simply removes the dominating vertices and any associated edges to obtain an alternating Hamiltonian path, which portrays the order of the score widths that gives rise to a feasible alignment of the boxes.
-Thus, the aim of the algorithm is to find an alternating Hamiltonian cycle on $G$, if one exists.
-
-The next step of the algorithm attemps to obtain a set of matching edges $M \subset Q$ of cardinality $n$, such that the edges from $M$ and $P$ form an alternating Hamiltonain cycle as described in Definition \ref{defn:althamcycle}.
-There is a modified matching algorithm (\citealp{mahadev1994, becker2010}) that is able to choose a suitable set of edges for $M$.
-
-Initially, the vertices are sorted in order of non-decreasing values $w(v_i), i = 1,2, .., 2n$, with ties broken arbitrarily.
-For each vertex in the list, find the largest adjacent vertex in $Q$ that has not yet been added to the matching set $M$.
-This pair of vertices is then added to $M$, and the algorithm proceeds on to the next vertex in the sorted list.
-This process continues until all of the vertices have been assessed.
-
-If a vertex $v_i$ is not adjacent to any other vertex except its partner, the previous vertex can be rematched, provided $v_i$ is not the first vertex in the sorted list, the previous vertex $v_{i-1}$ is matched under $M$ (i.e.
-$v_{i-1} \in M$), and $v_{i-1}$ is adajcent to $v_i$'s partner.
-Then, $v_{i-1}$ is matched with $v_i$'s partner, and $v_i$ is matched with $v_{i-1}$'s previous match under $M$.
-It is guaranteed that this algorithm will produce a maximum cardinality matching $M \subset Q$ (\citealp{becker2010}).
-
-If $|M| < n$, there are not enough matching edges to form an alternating Hamiltonian cycle with the edges in $P$, and therefore there is no feasible arrangement of the boxes such that the minimum total score width constraint is not violated.
-However, if $|M| = n$, then the graph $G(V, P \cup M)$ is a 2-regular graph where each vertex is adjacent to one vertex (its partner) via an edge in $P$, and another vertex (its match) via an edge in $M$.
-If $G$ consists of one alternating Hamiltonian cycle, the dominating vertices are removed to obtain a feasible alignment of the boxes.
-If there are two or more cycles on $G(V, P \cup M)$, a solution to the problem has not yet been found.
-These cycles need to be combined into one single alternating Hamiltonian cycle.
-
-To merge the multiple cycles on $G$, we need to connect vertices from different cycles by removing some matching edges and adding new edges from $Q$.
-The following algorithm finds the matching edges on the graph $G(V, P \cup M)$ that allow the cycles to be combined.
-
-The algorithm initially creates a list of all matching edges in $M$, sorted in order of non-decreasing vertex values.
-Starting from the first edge, the algorithm searches through the list of edges until it finds an edge whose smaller vertex is adjacent via an edge in $Q$ to the larger vertex of the succeeding edge in the list, such that both edges are from different cycles on the graph $G$.
-If such a pair of edges is found, the first edge of the pair is added to a set $C_k$.
-The algorithm then continues to add all succeeding edges to $C_k$, provided that the smaller vertex of the current edge is adjacent to the larger vertex of the succeeding edge via an edge in $Q$, the succeeding edge does not belong to a cycle that is already represented by an edge in $C_k$, and the algorithm has not reached the final edge in the list.
-Once there are no more valid edges to add to $C_k$, the algorithm proceeds to the next edge in the list, and checks whether this edge is suitable for beginning a new set $C_{k+1}$.
-If the penultimate or final edge in the list is reached, the algorithm terminates.
-
-If the algorithm does not produce a single set $C$, there are no edges available to connect the cycles together, and therefore no feasible alignment of the boxes in this problem instance exists.
-\textcolor{RoyalBlue}{also if the set $C$ doesn't include an edge from every cycle, or multiple sets $C$ that don't cover all cycles, infeasible.}
-
-If there exists a set $C_k$ such that $|C_k| = \textcolor{OliveGreen}{number of cycles}$, then the cycles can be connected as follows: starting from the first edge in $C_k$, connect the smaller vertex to the larger vertex of the second edge in the set.
-Then, connect the smaller vertex of the second edge to the larger vertex of the third edge.
-Continue in this manner until the last edge in $C_k$ is reached, and connect the lower vertex of this final edge to the larger vertex of the first edge.
-These new matching edges will join the distinct cycles together to form one alternating Hamiltonian cycle.
-The edges in the set $C_k$ can be removed from the graph $G$
-
--Multiple $C_k$ cycles required.
-
-\begin{algorithm}[H]
-	\caption{\textcolor{OliveGreen}{Exact First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
-	\label{alg:ffdexact}
-	\begin{algorithmic}[1]
-	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, and a set $\mathcal{S} = \emptyset$.
-	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.	
-	\State Sort the boxes in order of non-increasing widths
-	\For{$i \gets 1 \To n$}
-		\For{$j \gets 1 \To n$}
-			\If{$S_j = \emptyset$}
-				\State $S_j \gets \{i_1, i_2\}$
-				\State $r(j) \gets r(j) - w(i)$
-				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
-				\Break
-			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
-				\State \textcolor{RoyalBlue}{Run} \textcolor{OrangeRed}{``MBAHRA''} \textcolor{RoyalBlue}{on boxes in $S_j$ and box $i$}
-				\If{feasible alignment found}
-					\State $S_j \gets$ \textcolor{RoyalBlue}{new alignment found by} \textcolor{OrangeRed}{``MBAHRA''}
-					\State $r(j) \gets r(j) - w(i)$
-					\Break
-				\EndIf
-			\EndIf
-		\EndFor
-	\EndFor
-	\Return $\mathcal{S}$
-	\end{algorithmic}	
-\end{algorithm}
-
-\textcolor{RoyalBlue}{In a similar fashion/manner to ``FFD approx'' (rename)} The algorithm starts by sorting the boxes in order of non-increasing widths, with ties broken by choosing the box with the smallest score width.
-Starting with the first box, the algorithm finds the lowest-indexed strip $S_j$ that can feasibly accommodate the current box $i$.
-If $S_j$ is empty, box $i$ is placed onto $S_j$ in a ``regular'' position \textcolor{RoyalBlue}{(i.e.
-smallest score width on the LHS of the box)}.
-This strip is added to the set $\mathcal{S}$ that keeps track of the strips being used to form a solution, and the algorithm proceeds onto the next box $i+1$ in the sorted list.
-
-If $S_j$ is not empty \textcolor{RoyalBlue}{(i.e contains at least one box, $|S_j| > 0$)}, then \textcolor{OrangeRed}{MBAHRA} is performed on all of the boxes in $S_j$ and the current box $i$.
-If a feasible alignment of the boxes has been found, the current boxes on $S_j$ are replaced with the new alignment, and the algorithm proceeds onto the next box $i+1$.
-If \textcolor{OrangeRed}{MBAHRA} is unable to find a feasible alignment of the boxes, the algorithm moves onto the next strip $S_{j+1}$ and the process is repeated.
-The algorithm continues until all of the boxes have been packed.
-\textcolor{RoyalBlue}{Complexity}
-
-\section{Comparison and results}
-\label{sec:comparison}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-\section{Layout}
-Introduction:
 \begin{itemize}
-	\item One-dimensional BPP, NP-Hard.
-	\item Goulimis packing boxes onto \textit{one} strip, where boxes have score constraints.
-	\item Describe boxes, scores, score widths, minimum total score width constraint, scoring knives on bar etc. (include figure(s)).
-	\item Becker has created a polynomial time algorithm for this problem (again, only on \textit{one} strip).
-	\item How we adapt this problem: we take into account the width of each individual box (added widths to the boxes, not included by Becker), multiple strips, fixed lengths, if there was an instance with many boxes it's unlikely they would all fit onto one strip, strips come in fixed lengths that cannot be changed.
-	\item Our problem: pack the boxes onto multiple strips of fixed lengths while meeting the minimum total score width constraint, not exceeding the capacity of the strips, and trying to minimise the number of strips used (perhaps mention minimising waste per strip?).
-	\item Are there any similar problems? Who has researched this problem/similar problem, and using what methods? \cite{lewis2017} trapezoids paper. 
-	\item Explain \textit{why this problem is important} (see above, strips come in fixed lengths, becker's algorithm is rendered useless if the total width of all boxes exceeds the length of one strip).
-	\item Outline rest of paper.	
-\end{itemize}
-
-Lit Review
-\begin{itemize}
-	\item Solving the one-dimensional bpp using exact methods and heuristics.
-	\item Exact methods - \cite{martello1990a} branch and bound based exact algorithm MTP, Carvalho 1999 column generation and branch-and-bound, \cite{eilon1971} depth-first search enumerative algorithm, only solve small size problem instances.
-	\item \cite{garey1979} NP-Hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP.
-	\item Instead, heuristics can be used to find a near optimal solution in a shorter amount of time.
-	\item discuss heuristics.
-	\item Explain FF and FFD, online/offline \cite{eilon1971}, \cite{dosa2007} tight bound, optimal number of bins $k$ \cite{korf2002}, complexity $O(n \log n)$ \cite{coffman1984} (where n is the number of items to be packed).
-	\item quickly produce a feasible solution, but may not be optimal.
-	\item Use heuristics in this paper to find feasible solutions for the problem, why?
-\end{itemize}
-
-Notation and Formulating the problem
-\begin{itemize}
-	\item $n$ boxes, $i = 1, 2, ..., n$, same height, different widths.
-	\item Each box $i$ has a total width $w(i)$.
-	\item Each box $i$ has two scores, $i_1$ (the smaller score), and $i_2$ (the larger score), and widths $w(i_1), w(i_2)$, such that $w(i_1) \leq w(i_2)$.
-	\item Score widths not necessarily equal, therefore box has two different positions.
-	\item $\{i_1, i_2\}$ represents ``regular'' box $i$: $i_1$ on LHS of box.
-	\item $\{i_2, i_1\}$ represents ``rotated'' box $i$: $i_2$ on LHS of box (box rotated by $180^{\circ}$).
-	\item Boxes will be placed side by side.
-	\item All box widths $w(i) > 0$ and all score widths $w(i_1), w(i_2) > 0$ $\forall$ $i = 1, 2, ..., n$.
-	\item Finite number of strips $S_j$, $j = 1, 2, ...$.
-	\item All strips $S_j$ have equal fixed length $l > 0$ $\forall$ $j = 1, 2, ...$.
-	\item All strips $S_j$ have a residual length $r(j)$, initially $r(j) = l$ $\forall$ $j = 1,2, ...$, which reduces as boxes are added to each strip.
-	\item Assumption: all box widths $w(i) \leq l, i = 1, 2, ..., n$
-	\item Initially, $S_j = \emptyset$ $\forall$ $j = 1, 2, ...$.
-	\item For all strips $S_j \neq \emptyset$, the score on the right hand side of the last box in the strip is called the ``free score'', denoted $f_j$, with width $w(f_j)$.
-	\item The sum of two adjacent score widths must fulfil the minimum total score width constraint ... $t$ is the minimum total score width.
-	\item The minimum total score width constraint must be fulfilled in order for the scoring knives to be able to score the boxes correctly.
-	\item The \textit{minimum total score width} is denoted by $\tau, \tau > 0$ (usually 70mm in industry).
-	\item Strips packed from left to right.
-	\item $l > 0, w(i) > 0, w(i) \leq l$
-	\item Need to pack the boxes onto the strips so mtswc is met and least number of strips used.
-	\item Formal definition of Score-Constrained Bin Packing Problem
-\end{itemize}
-
-FFD Approx
-\begin{itemize}
-	\item Explain FFD modified for scored boxes (basic).
-	\item Free score $f_j$, residual length $r(j)$.
-	\item Figure: partially packed strip showing first box in regular position, free score, minimum total score width constraint met between boxes, residual length.
-	\item Pseudocode
-	\item Description of algorithm
-	\item Complexity, discuss how algorithm only checks if current box meets constraint with free score on final box, boxes are not able to be rearranged, even though there may be another arrangement of the boxes that is feasible (lead on to next algorithm FFD using exact algorithm).
-\end{itemize}
-
-FFD Using Exact Algorithm
-\begin{itemize}
-	\item Combine FFD with exact algorithm to find a feasible solution to the SCBPP
-	\item Unlike FFD approx, where attempts are made to place each box at the end of a strip, this algorithm is able to rearrange the order of the boxes in a strip to find a feasible arrangement.
-	\item Can find a solution for a set of boxes on a strip when it may not have possible to find one in ffdapprox
-	\item Describe Becker algorithm, using graph theory, Hamiltonian path/cycle
-	\item Notation for Exact algorithm:
-	\item $n$ boxes including dummy box.
-	\item $2n$ vertices including dominating vertices.
-	\item Graph $G$ is an undirected graph with $2n$ vertices $v_i, i = 1, 2, ...,2n$.
-	\item Vertices are weighted, $w(v_i)$.
-	\item Vertices that represent either side of same box referred to as ``partners''
-	\item $P$ contains the set of edges between partners, fixed, $|P| = n$.
-	\item Edges in $P$ are weighted, corresponding to box width.
-	\item $Q$ contains the set of edges between vertices that meet the minimum total score width constraint, excluding partners (these edges are not weighted).
-	\item $G(V, P \cup Q)$ - each edge on $G$ is either in $P$ or $Q$, not both.
-	\item $t$ still represents the minimum total score width.
-	\item $M$ is the set of matching edges, $M \subset Q$, edges chosen using the matching algorithm (need $|M| = n$).
-	\item number of cycles on $G$ after MTGMA =  ?
-	\item $C_k$: sets of edges for connecting cycles.
-	\item Section: Becker algorithm
-	\item Combine alg with ffd
-	\item Pseudocode
-	\item Description of algorithm
-	\item Complexity
+	\item Instead of minimising an objective function, the aim is to find a single solution/determine whether a solution exists such that the constraint is met.
+	\item In this case, there may not be a solution, whereas original case will have a solution.
+	\item introduction of $\tau \in \mathbb{R}^{+}$.
+	\item $x_i, y_i \in \mathbb{Z}^{+}$, original PSP was $\mathbb{N}_{0}$.
+Changed since if $x_i = 0$ or $y_i = 0$ for any $i \in\{1, 2, ..., n\}$, then a score width would not exist.
+Ensure that all items (boxes) have two score widths, one on either side.
+	\item Original PSP checks distance between rhs($n$) and lhs(1).
+Not required in this case, as the first and last score widths will be ``free'', not adjacent to any other score widths, strip does not wrap around.
 \end{itemize}

### 2018-01-19 paper/main.tex
added example for PSP

@@
 	\begin{equation*}
-		\textup{rhs}(i) + \textup{lhs}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\}
+		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\}
 	\end{equation*}
-	where \textup{lhs($i$)} and \textup{rhs($i$)} denote the values on the left- and right-hand sides of the $i$th ordered pair in $\mathcal{X}$, and $\tau \in \mathbb{R}^{+}$ is a fixed value.	
+	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the values on the left- and right-hand sides of the $i$th ordered pair in $\mathcal{X}$, and $\tau \in \mathbb{R}^{+}$ is a fixed value.
 \end{definition}
 
-Adaptations from original PSP:
-
-\begin{itemize}
-	\item Instead of minimising an objective function, the aim is to find a single solution/determine whether a solution exists such that the constraint is met.
-	\item In this case, there may not be a solution, whereas original case will have a solution.
-	\item introduction of $\tau \in \mathbb{R}^{+}$.
-	\item $x_i, y_i \in \mathbb{Z}^{+}$, original PSP was $\mathbb{N}_{0}$.
-Changed since if $x_i = 0$ or $y_i = 0$ for any $i \in\{1, 2, ..., n\}$, then a score width would not exist.
-Ensure that all items (boxes) have two score widths, one on either side.
-	\item Original PSP checks distance between rhs($n$) and lhs(1).
-Not required in this case, as the first and last score widths will be ``free'', not adjacent to any other score widths, strip does not wrap around.
-\end{itemize}
-
-\section{References}
-\cite{becker2010}, \cite{becker2015}, \cite{coffman1978}, \cite{dosa2007}, \cite{eilon1971}, \cite{garey1979}, \cite{gilmore1961}, \cite{gilmore1963}, \cite{goulimis2004}, \cite{johnson1974worst}, \cite{johnson1974fast}, \cite{hung1978}, \cite{garey1972}, \cite{johnson1973}, \cite{karp1972}, \cite{korf2002}, \cite{lewis2009}, \cite{lewis2017}, \cite{lewis2011}, \cite{mahadev1994}, \cite{mahadev1995}, \cite{martello1990a}, \cite{martello1990b}
+For example, if $\mathcal{P} = \{\{1,2\}, \{1,5\}, \{2,4\}, \{3,4\}, \{4,5\}\}$ and $\tau = 7$, a solution is $\mathcal{X} = \langle(1,2), (5,4), (3,4), (4,2), (5,1) \rangle$.
 

### 2018-01-22 paper/main.tex
changed paper again, includes constrained pair ordering problem

@@
 
-Modification/adaption of the Pair Sequencing Problem (PSP) as seen in \cite{lewis2017}:
+\begin{definition}
+	\label{defn:cpop}
+	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple.
+The Constrained Pair Ordering Problem consists of finding a solution $\mathcal{T}$ such that
+	\begin{equation*}
+		\label{eqn:cpop}
+		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
+	\end{equation*}
+	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple, and $\tau \in \mathbb{R}^{+}$ is a fixed value.	
+\end{definition}
+
+For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,5\}, \{2,4\}, \{3,4\}, \{4,5\}\}$ and $\tau = 7$, a feasible solution is $\mathcal{T} = \langle(1,2), (5,4), (3,4), (4,2), (5,1) \rangle$.
+
+\textcolor{OrangeRed}{Model the problem using a graph.}
+
+Let $\mathcal{M}$ be a multiset as described in Definition \ref{defn:cpop}, with an additional unordered pair consisting of ``dominating'' values equal to $\tau$.
+Two values that make up a pair in $\mathcal{M}$ are referred to as ``partners''.
+Then, $G(V, P \cup Q)$ is an undirected graph defined by a vertex set $V = \{v_1, v_2, ...v_{2n+2}\}$, where each vertex is assigned a value from $\mathcal{M}$ such that $v_1 \leq v_2 \leq ...
+\leq v_{2n+2}$.
+$G$ comprises two distinct edge sets: $P$, which contains edges between vertices that are partners, and $Q$, which consists of edges between vertices that fulfil the \textit{joint sum constraint}.
+That is, for two distinct vertices $v_i, v_j$,
+
+\begin{equation*}
+	\label{eqn:jointsum}
+	v_i + v_j \geq \tau,
+\end{equation*}
+
+provided $\{v_i, v_j\} \notin P$. Observe that $P$ is in fact a perfect matching, with $|P| = |\mathcal{M}| = n+1$, and that $P \cap Q = \emptyset$.
+
+If $G(V, P\cup Q)$ features an alternating Hamiltonian cycle, then a feasible solution $\mathcal{T}$ exists.
 
 \begin{definition}
-	\label{defn:psp}
-	Let $\mathcal{P}$ be a multiset of unordered pairs $\mathcal{P} = \{\{x_1, y_1\}, \{x_2,y_2\},...,\{x_n,y_n\}\}$, $x_i, y_i \in \mathbb{Z}^{+}$ for $i \in \{1,2,...,n\}$, and let $\mathcal{X}$ be an ordering of the elements on $\mathcal{P}$ in which each element is also expressed as an ordered pair.
-The \textcolor{RoyalBlue}{constrained} PSP involves finding a solution $\mathcal{X}$ such that
-	\begin{equation*}
-		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\}
-	\end{equation*}
-	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the values on the left- and right-hand sides of the $i$th ordered pair in $\mathcal{X}$, and $\tau \in \mathbb{R}^{+}$ is a fixed value.
+	\label{defn:althamcycle}
+	Let $G(V, P\cup Q)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $Q$.
+$G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such successive edges alternate between sets $P$ and $Q$.
+For example, if $\{v_{i-1}, v_i\} \in P$, then $\{v_i, v_{i+1}\} \in Q$, or vice versa.
 \end{definition}
 
-For example, if $\mathcal{P} = \{\{1,2\}, \{1,5\}, \{2,4\}, \{3,4\}, \{4,5\}\}$ and $\tau = 7$, a solution is $\mathcal{X} = \langle(1,2), (5,4), (3,4), (4,2), (5,1) \rangle$.
+compulsory edges $P$ values pairs cannot be altered.
+
+%========================================================================%
+
+\begin{comment}
+The PSP can be seen in a problem related to the cutting-stock problem, first described by \cite{goulimis2004}.
+Let $\mathcal{I}$ be a set of rectangular items of equal heights, made from corrugated cardboard.
+Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$ and possess two vertical score lines.
+A pair of knives mounted on a bar will cut along these score lines to allow the items to be folded with ease.
+The distances between each edge of an item and the nearest score line are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$.
+As illustrated in Figure \ref{fig:boxesknife}, the knives cut along score lines from two adjacent items simultaneously.
+By design, the knives cannot be placed too close to one another - the distance between the knives must exceed a fixed minimum $\tau \in \mathbb{R}^{+}$ (around 70mm in industry).
+In order for the knives to be able to cut the items in the correct locations, two adajcent score widths, for example $a_i$ and $b_{i+1}$, must fulfil the \textit{minimum total score width constraint}
+
+\begin{equation*}
+a_i + b_{i+1} \geq \tau.
+\end{equation*}
+
+That is, the sum of two adjacent score widths must exceed the \textit{minimum total score width} $\tau$.
+Therefore, the problem involves finding a feasible arrangement of the items such that between each pair of items the minimum total score width constraint is met.
+
+\begin{figure}[H]	
+\centering
+\includestandalone[width=0.4\textwidth]{figures/boxesknifeannotate}
+\caption{\textcolor{red}{Individual boxes.}}	
+\label{fig:boxesknife}
+\end{figure}
+
+Since the score widths on each item $i \in \mathcal{I}$ are not necessarily equal, they can be aligned in two distinct orientations: ``regular'', denoted by $(a_i, b_i)$, and ``rotated'', denoted by $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right-hand side of the item respectively.
+
+This can be seen as a PSP, where the values $x_i$ and $y_i$ are the score widths, and a feasible solution $\mathcal{X}$ consists of an arrangement of items in some order such that $\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \forall  i \in \{1,2,..., |\mathcal{I}|-1\}$.
+
+There exists a polynomial-time algorithm that is able to recognise whether a particular instance of this problem is feasible (\citealp{becker2010}).
+
+\end{comment}
 

### 2018-01-25 paper/main.tex
changed equation* to equation, added theorem

@@
 	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple.
-The Constrained Pair Ordering Problem consists of finding a solution $\mathcal{T}$ such that
-	\begin{equation*}
+The Constrained Pair Ordering Problem (CPOP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{R}^{+},$
+	\begin{equation}
 		\label{eqn:cpop}
 		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
-	\end{equation*}
-	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple, and $\tau \in \mathbb{R}^{+}$ is a fixed value.	
+	\end{equation}
+	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple.	
 \end{definition}
 
-For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,5\}, \{2,4\}, \{3,4\}, \{4,5\}\}$ and $\tau = 7$, a feasible solution is $\mathcal{T} = \langle(1,2), (5,4), (3,4), (4,2), (5,1) \rangle$.
+For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,5\}, \{2,4\}, \{3,4\}, \{4,5\}\}$ and $\tau = 7$, one possible feasible solution is $\mathcal{T} = \langle(1,2), (5,4), (3,4), (4,2), (5,1) \rangle$.
 
@@
 Two values that make up a pair in $\mathcal{M}$ are referred to as ``partners''.
-Then, $G(V, P \cup Q)$ is an undirected graph defined by a vertex set $V = \{v_1, v_2, ...v_{2n+2}\}$, where each vertex is assigned a value from $\mathcal{M}$ such that $v_1 \leq v_2 \leq ...
+Then, $G(V, P \cup E)$ is an undirected graph defined by a vertex set $V = \{v_1, v_2, ...v_{2n+2}\}$, where each vertex is assigned a value from $\mathcal{M}$ such that $v_1 \leq v_2 \leq ...
 \leq v_{2n+2}$.
-$G$ comprises two distinct edge sets: $P$, which contains edges between vertices that are partners, and $Q$, which consists of edges between vertices that fulfil the \textit{joint sum constraint}.
+$G$ comprises two distinct edge sets: $P$, which contains edges between vertices that are partners, and $E$, which consists of edges between vertices that fulfil the \textit{joint sum constraint}.
 That is, for two distinct vertices $v_i, v_j$,
 
-\begin{equation*}
+\begin{equation}
 	\label{eqn:jointsum}
 	v_i + v_j \geq \tau,
-\end{equation*}
+\end{equation}
 
-provided $\{v_i, v_j\} \notin P$. Observe that $P$ is in fact a perfect matching, with $|P| = |\mathcal{M}| = n+1$, and that $P \cap Q = \emptyset$.
+provided $\{v_i, v_j\} \notin P$. Observe that $P$ is in fact a perfect matching, with $|P| = |\mathcal{M}| = n+1$, and that $P \cap E = \emptyset$.
 
-If $G(V, P\cup Q)$ features an alternating Hamiltonian cycle, then a feasible solution $\mathcal{T}$ exists.
+If $G(V, P\cup E)$ features an alternating Hamiltonian cycle, then a feasible solution $\mathcal{T}$ exists.
 
@@
 	\label{defn:althamcycle}
-	Let $G(V, P\cup Q)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $Q$.
-$G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such successive edges alternate between sets $P$ and $Q$.
-For example, if $\{v_{i-1}, v_i\} \in P$, then $\{v_i, v_{i+1}\} \in Q$, or vice versa.
+	Let $G(V, P\cup E)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $E$.
+$G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such successive edges alternate between sets $P$ and $E$.
+For example, if $\{v_{i-1}, v_i\} \in P$, then $\{v_i, v_{i+1}\} \in E$, or vice versa.
 \end{definition}
 
-compulsory edges $P$ values pairs cannot be altered.
+\begin{theorem}
+	\label{thm:cpopsolnalt}
+	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the CPOP if and only if its corresponding graph $G(V, P\cup E)$ contains an alternating Hamiltonian cycle.
+\end{theorem}
+\begin{proof}
+	To be completed. \qed
+\end{proof}
 

### 2018-01-29 paper/main.tex
added Becker algorithm for CPOP

@@
 
+The values in each unordered pair in $\mathcal{M}$ cannot be altered, and so every edge in $P$ must be present in the alternating Hamiltonian cycle.
+Thus, the task involves finding a matching $Q \subset E$ of cardinality $n+1$, such that the edge sets $P$ and $Q$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.
+If no suitable matching $Q$ can be found, then, in accordance with Theorem \ref{thm:cpopsolnalt}, no feasible solution exists for the given instance $\mathcal{M}$.
+
+To find a matching $Q \subset E$, the following modified maximum cardinality matching algorithm is executed (\citealp{mahadev1994, becker2010}): for each vertex $v_i, i = 1, 2,...,2n+2$, find the largest vertex in $v_i$'s neighbourhood, excluding partners, that is not incident to any edge in $Q$.
+Add the edge connecting these two vertices to $Q$, and proceed to the next vertex until all vertices have been assessed.
+The pair of vertices incident to each edge in $Q$ are referred to as being ``matched'', and are connected by a ``matching'' edge.
+
+During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner, the preceeding vertex $v_{i-1}$ can be rematched, provided that $v_i$ is not the first vertex (i.e $i \neq 1$), $v_{i-1}$ is incident to an edge in $Q$, (i.e.
+$v_{i-1}$ has been matched) and $v_{i-1}$ is adjacne to $v_i$'s partner via an edge in $E$.
+Thenm, $v_{i-1}$ is matched with $v_i$'s partner, and $v_i$ is matched with $v_{i-1}$'s previous match.
+It is guaranteed that this algorithm will produce a maximum cardinality matching $Q \subset E$ (\citealp{becker2010}).
+
+If $|Q| < n+1$, clearly there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $P$, and hence there is no feasible solution to this particular instance of the CPOP.
+However, if $|Q| = n+1$, then the spanning subgraph $G'(V, P \cup Q)$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $P$, and its match via an edge in $Q$.
+$G'$ thus consists of a collection of alternating Hamiltonian cycles $A_1, A_2, ..., A_{\lambda}$.
+If there is only one alternating Hamiltonian cycle on $G'$, i.e.
+$\lambda = 1$, then a feasible solution has been found \textcolor{OrangeRed}{remove dominating vertices}.
+If $\lambda > 1$, then the components of $G'$ need to be combined into one single alternating Hamiltonian cycle, by removing some matching edges from $Q$, and adding new edges from $E$.
+The following algorithm finds edges that are able to merge the components of $G'$ together.
+
+For each edge $(v_i, v_j) \in Q$, with $i < j$, $v_i$ is referred to as the ``smaller'' vertex, and $v_j$ as the ``larger'' vertex, since the value associated with $v_i$ is less than or equal to the value associated with $v_j$.
+Initially, the edges in $Q$ are sorted in a list such that the smaller vertices of the edges are in lexicographical order, and therefore in non-decreasing order of values.
+\textcolor{OrangeRed}{remove edges from list that are a result of rematching}.
+Starting from the first edge, search through the list to find an edge that meets the following conditions:
+\begin{enumerate}
+	\item The smaller vertex of the current edge is adjacent to the larger vertex of the succeeding edge in the list via an edge in $E$,
+	\item The current edge and the succeeding edge are members of different alternating Hamiltonian cycles on $G$.
+\end{enumerate}
+
+If such an edge is found, add it to a set $C_i$, and continue to add all succeeding edges in the list to $C_i$, provided that for each edge conditions 1 and 2 hold, and the succeeding edge does not belong to a component on $G$ that is already represented by an edge in $C_i$.
+Once there are no more valid edges to add to $C_i$, continue to search through the remaining edges in the list to find an edge that meets conditions 1 and 2, and can therefore start a new set $C_{i+1}$.
+If the final edge in the list has been reached, the process is terminated.
+
+The sets $C_i, i = 1, ..., k$ that have been created during this process are then analysed.
+In the case where not a single set $C$ has been produced, then the cycles $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
+If there exists a set $C_i$ such that $|C_i| = \lambda$, then all components on $G'$ can be combined as follows:
+
+Starting from the first edge in $C_i$, add the edge from $E$ connecting the smaller vertex of each edge to the larger vertex of the succeeding edge to the matching $Q$.
+For the final edge in $C_i$, add the edge from $E$ that connects its smaller vertex to the larger vertex of the first edge in $C_i$ to $Q$.
+Then, edges that appear in both $C_i$ and $Q$ are removed from $Q$, such that $C_i \cap Q = \emptyset$.
+\textcolor{OrangeRed}{Then components have been merged, remove dominating vertices etc}.
+
+If there is no set $C_i$ such that $|C_i| = \lambda$, and $k > 1$ (i.e.
+there are multiple sets $C_i, i = 1,..., k$), it may be that multiple sets are required to combine the components of $G'$.
+Let $\mathcal{C}$ be a set that will contain all the sets $C_i$ needed to merge all components of $G'$ together, and let $\Lambda$ be a set that records the components covered by the sets in $\mathcal{C}$.
+For the set $C_1$, append the componnents $A_i$ that each edge in $C_1$ is a member of to $\Lambda$, and then add $C_1$ to $\mathcal{C}$.
+At this stage, $|\Lambda| = |\mathcal{C}|$.
+Proceeding throug the sets $C_i, i = 2, ..., k$, find a set $C_i$ that contains at least one edge that is a member of a component recorded in $\Lambda$, and at least one edge that is a member of a component not yet recorded in $\Lambda$.
+Append the component that each edge in this set $C_i$ is a member of to $\Lambda$, provided the component is not already a member of $\Lambda$, and add $C_i$ to $\mathcal{C}$.
+Continue in this manner until the final set $C_k$ has been assessed.
+If $|\Lambda| = \lambda$, then the sets in $\mathcal{C}$ are able to merge the components of $G'$ together.
+This is done by repeating the connecting process for a single set $C_i$ on every set in $\mathcal{C}$.
+
+\textcolor{OrangeRed}{Complexity of the CPOP algorithm, ability to find a solution, complete recognition.}
+
 %========================================================================%

### 2018-01-30 paper/main.tex
added mssp and related it to cpop

@@
 
+One prominent application of the CPOP is in a cutting stock problem \textcolor{OrangeRed}{(or strip packing problem)} brought to light as an open-combinatorial problem by \cite{goulimis2004} in 2004.
+A set $\mathcal{I}$ of rectangular items of equal height $h$ made from cardboard are to be packed onto  strip from left to right.
+Each item $i \in \mathcal{I}$ has a width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined placed.
+A pair of knives mounted on a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure ref{}).
+However, by desgn, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry).
+Thus, the distance between two score lines on adjacent items must be greater than or equal to the minimum scoring distance in order for the knives to be able to cut the items correctly.
+The distance between a score line and the nearest edge on an item is called a score width.
+Each item $i \in \mathcal{I}$ thus has two score widths, $a_i, b_i \in \mathbb{Z}^{+}$, with $a_i \leq b_i$.
+Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, where the smaller score $a_i$ is on the left-hand side of the item, or ``rotated'', denoted $(b_i, a_i)$, where the item has been rotated by $180^{\circ}$ so that the smaller score $a_i$ is on the right-hand side of the item.
+Then, for two items to be feasibly placed alongside one another, the sum of the adjacent score widths must be greater than or equal to the minimum scoring distance.
+Thus, the problem consists of finding a suitable ordering and orientation of the items on a strip $\mathcal{S}$ that fulfils the \textit{minimum total score width constraint},
+
+\begin{equation}
+\label{eqn:mtswc}
+\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., |\mathcal{S}|-1\},
+\end{equation}
+
+where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th item on the strip $\mathcal{S}$, and $\tau \in \mathbb{R}^{+}$ is the minimum scoring distance.
+
+It can be seen that this problem is analogous to the CPOP, where the pairs of score widths on each item are expressed as an unordered pair in a multiset $\mathcal{M}$, and therefore the problem can be solved in the same manner.
+
+In the problem detailed by Goulimis, the aim is to align all of the items onto a single strip.
+So, when an instance of this problem is expressed as an instance of the CPOP, the widths of the individual items are not taken into account.
+In reality, strips of material are provided in fixed lengths.
+Given a large problem instance, multiple strips may be required to feasibly accommodate all of the items.
+For this reasons, we define a new problem to be investigated.
+
+\begin{definition}
+	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ with equal fixed length $l$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the minimum total score width constraint is met between every pair of adjacent items on every strip.
+\end{definition}
+
+Indeed, the SCSPP is a generalisation of the classical one-dimensional bin-packing problem (BPP), where in the latter problem, the minimum scoring distance $\tau$ can be said to be equal to zero.
+It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}).
+Thus, we will be using heuristics..
+
 %========================================================================%

### 2018-01-31 paper/main.tex
added section about ffd

@@
 Indeed, the SCSPP is a generalisation of the classical one-dimensional bin-packing problem (BPP), where in the latter problem, the minimum scoring distance $\tau$ can be said to be equal to zero.
-It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}).
-Thus, we will be using heuristics..
+It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}), and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.
+Instead, heuristics can be used to find near-optimal solutions in a shorter amount of time.
+One example is the greedy heuristic known as first-fit (FF), an online algorithm that places each item (in some arbitrary order) onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
+It has been shown that by arranging the items in decreasing order of size, a packing heuristic will produce a solution that is closer to the optimal than if the items are arranged in any other order (\citealp{johnson1974fast}).
+Applying FF onto items sorted in this manner yields the well-known first-fit decreasing (FFD) heuristic.
+
+An optimal solution of an instance of the SCSPP is a solution that consists of the fewest number of strips, $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
+
+\begin{equation}
+	k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{l}}
+\end{equation}
+
+where $n$ is the number of items in the set $\mathcal{I}$, $w_i$ the width of each item $i \in \mathcal{I}$, and $l$ is the length of the strips (\citealp{martello1990b}).
+In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ strips.
+More recently, \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight.
+Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$.
 

### 2018-01-31 paper/ffdexact/mainexact.cpp
changed instance loop from 10 to 2

@@ -109,7 +109,7 @@ int main(int argc, char **argv){
 
         //endregion
 
-    for(i = 0; i < 10; ++i) {
+    for(i = 0; i < 2; ++i) {
         cout << "Instance: " << i << endl;
 
         createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates,

### 2018-01-31 paper/ffdexact/packingexact.cpp
split packing ffd into two, one ffdexact, one ffd approx

@@ -61,6 +61,27 @@ void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth
     stripSum[0] += boxWidths[boxDecrease[0]][mates[boxDecrease[0]]];
 
 
+    /*for(j = 1; j < boxDecrease.size(); ++j){
+        for(i = 0; i < strip.size(); ++i){
+            if(!strip[i].empty()){
+                if(stripSum[i] + boxWidths[boxDecrease[j]][mates[boxDecrease[j]]] <= maxStripWidth){
+                    feasible = 0;
+                    MBAHRA(i, j, feasible, allScores, mates, adjMatrix, boxWidths, boxDecrease, stripSum, strip);
+                    if(feasible == 1){
+                        break;
+                    }
+                }
+            }
+            else if (strip[i].empty()){
+                strip[i].push_back(boxDecrease[j]);
+                strip[i].push_back(mates[boxDecrease[j]]);
+                stripSum[i] += boxWidths[boxDecrease[j]][mates[boxDecrease[j]]];
+                break;
+            }
+        }
+    }*/
+
+
     for(j = 1; j < boxDecrease.size(); ++j){
         for(i = 0; i < strip.size(); ++i){
             if(!strip[i].empty()){
@@ -77,13 +98,13 @@ void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth
                         stripSum[i] += boxWidths[boxDecrease[j]][mates[boxDecrease[j]]];
                         break;
                     }
-                    else{
+                    /*else{
                         feasible = 0;
                         MBAHRA(i, j, feasible, allScores, mates, adjMatrix, boxWidths, boxDecrease, stripSum, strip);
                         if(feasible == 1){
                             break;
                         }
-                    }
+                    }*/
                 }
             }
             else if (strip[i].empty()){

### 2018-01-31 paper/ffdexact/mainexact.cpp
changed instance loop from 2 to 1

@@ -109,7 +109,7 @@ int main(int argc, char **argv){
 
         //endregion
 
-    for(i = 0; i < 2; ++i) {
+    for(i = 0; i < 1; ++i) {
         cout << "Instance: " << i << endl;
 
         createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates,

### 2018-02-02 paper/main.tex
moved description of MSSP to introduction, added explanation to link MSSP to CPOP in introduction

@@
 
-\title{Heuristics for the Score-Constrained Bin-Packing Problem}
+\title{Heuristics for the Score-Constrained Strip-Packing Problem}
 \author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
@@
 
+Firstly, let us introduce the Constrained Pair-Ordering Problem:
+
 \begin{definition}
@@
 	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple.
-The Constrained Pair Ordering Problem (CPOP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{R}^{+},$
+The Constrained Pair Ordering Problem (CPOP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
 	\begin{equation}
@@
 	\end{equation}
-	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple.	
+	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the vicinal sum constraint.
 \end{definition}
@@
 For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,5\}, \{2,4\}, \{3,4\}, \{4,5\}\}$ and $\tau = 7$, one possible feasible solution is $\mathcal{T} = \langle(1,2), (5,4), (3,4), (4,2), (5,1) \rangle$.
+
+One prominent application of the CPOP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004.
+A set $\mathcal{I}$ of rectangular items of equal height $h$ made from cardboard are to be packed onto a strip from left to right.
+Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places.
+A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure ref{}).
+However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry).
+The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$.
+Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively.
+Clearly, for two items to be placed alongside one another feasibly the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
+Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
+Specifically, as the items are packed from left to right, this involved checking the sum of the right-hand score width of each item $i$ and the left-hand score width of the next item $i+1$ on the strip.
+The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.
+
+It can be seen that this problem is in fact analogous to the CPOP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance.
+Thus, a set $\mathcal{I}$ of items has a feasible arrangement if the equivalent CPOP has a feasible solution $\mathcal{T}$.
 
@@
 During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner, the preceeding vertex $v_{i-1}$ can be rematched, provided that $v_i$ is not the first vertex (i.e $i \neq 1$), $v_{i-1}$ is incident to an edge in $Q$, (i.e.
-$v_{i-1}$ has been matched) and $v_{i-1}$ is adjacne to $v_i$'s partner via an edge in $E$.
-Thenm, $v_{i-1}$ is matched with $v_i$'s partner, and $v_i$ is matched with $v_{i-1}$'s previous match.
+$v_{i-1}$ has been matched) and $v_{i-1}$ is adjacent to $v_i$'s partner via an edge in $E$.
+Then, $v_{i-1}$ is matched with $v_i$'s partner, and $v_i$ is matched with $v_{i-1}$'s previous match.
 It is guaranteed that this algorithm will produce a maximum cardinality matching $Q \subset E$ (\citealp{becker2010}).
@@
 Let $\mathcal{C}$ be a set that will contain all the sets $C_i$ needed to merge all components of $G'$ together, and let $\Lambda$ be a set that records the components covered by the sets in $\mathcal{C}$.
-For the set $C_1$, append the componnents $A_i$ that each edge in $C_1$ is a member of to $\Lambda$, and then add $C_1$ to $\mathcal{C}$.
+For the set $C_1$, append the components $A_i$ that each edge in $C_1$ is a member of to $\Lambda$, and then add $C_1$ to $\mathcal{C}$.
 At this stage, $|\Lambda| = |\mathcal{C}|$.
-Proceeding throug the sets $C_i, i = 2, ..., k$, find a set $C_i$ that contains at least one edge that is a member of a component recorded in $\Lambda$, and at least one edge that is a member of a component not yet recorded in $\Lambda$.
+Proceeding through the sets $C_i, i = 2, ..., k$, find a set $C_i$ that contains at least one edge that is a member of a component recorded in $\Lambda$, and at least one edge that is a member of a component not yet recorded in $\Lambda$.
 Append the component that each edge in this set $C_i$ is a member of to $\Lambda$, provided the component is not already a member of $\Lambda$, and add $C_i$ to $\mathcal{C}$.
@@
 \textcolor{OrangeRed}{Complexity of the CPOP algorithm, ability to find a solution, complete recognition.}
-
-One prominent application of the CPOP is in a cutting stock problem \textcolor{OrangeRed}{(or strip packing problem)} brought to light as an open-combinatorial problem by \cite{goulimis2004} in 2004.
-A set $\mathcal{I}$ of rectangular items of equal height $h$ made from cardboard are to be packed onto  strip from left to right.
-Each item $i \in \mathcal{I}$ has a width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined placed.
-A pair of knives mounted on a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure ref{}).
-However, by desgn, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry).
-Thus, the distance between two score lines on adjacent items must be greater than or equal to the minimum scoring distance in order for the knives to be able to cut the items correctly.
-The distance between a score line and the nearest edge on an item is called a score width.
-Each item $i \in \mathcal{I}$ thus has two score widths, $a_i, b_i \in \mathbb{Z}^{+}$, with $a_i \leq b_i$.
-Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, where the smaller score $a_i$ is on the left-hand side of the item, or ``rotated'', denoted $(b_i, a_i)$, where the item has been rotated by $180^{\circ}$ so that the smaller score $a_i$ is on the right-hand side of the item.
-Then, for two items to be feasibly placed alongside one another, the sum of the adjacent score widths must be greater than or equal to the minimum scoring distance.
-Thus, the problem consists of finding a suitable ordering and orientation of the items on a strip $\mathcal{S}$ that fulfils the \textit{minimum total score width constraint},
-
-\begin{equation}
-\label{eqn:mtswc}
-\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., |\mathcal{S}|-1\},
-\end{equation}
-
-where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th item on the strip $\mathcal{S}$, and $\tau \in \mathbb{R}^{+}$ is the minimum scoring distance.
-
-It can be seen that this problem is analogous to the CPOP, where the pairs of score widths on each item are expressed as an unordered pair in a multiset $\mathcal{M}$, and therefore the problem can be solved in the same manner.
 

### 2018-02-05 paper/main.tex
added figure boxes annotated, added link from single to multistock problem in intro, added paper description at end of intro, added description of ffd approx heuristic

@@
 Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places.
-A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure ref{}).
+A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:boxknife}).
 However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry).
@@
 
+\begin{figure}[h!]	
+	\centering
+	\includestandalone[width=0.8\textwidth]{figures/boxesknifeannotate}
+	\caption{\textcolor{red}{Individual boxes.}}	
+	\label{fig:boxknife}
+\end{figure}
+
 It can be seen that this problem is in fact analogous to the CPOP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance.
-Thus, a set $\mathcal{I}$ of items has a feasible arrangement if the equivalent CPOP has a feasible solution $\mathcal{T}$.
+Thus, a set $\mathcal{I}$ of items has a feasible arrangement if the equivalent CPOP has a solution $\mathcal{T}$.
 
-\textcolor{OrangeRed}{Model the problem using a graph.}
+Observe that, in this particular strip-packing problem, the widths of the individual items are not taken into account, since the aim is to arrage the items onto a strip of seemingly infinite length.
+In reality, strips of material are provided in fixed lengths.
+Given a large problem instance, multiple strips may be required to feasibly accommodate all of the items.
+For this reason, we define a new problem to be investigated.
+
+\begin{definition}
+	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ with equal fixed length $l$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the minimum total score width constraint is met between every pair of adjacent items on every strip.
+\end{definition}
+
+The remainder of this article will firstly, in Section 2, detail a polynomial-time algorithm that is able to produce a solution to any instance of the CPOP, if a solution exists.
+Section 3 describes the heuristics that will be used to find feasible solutions to the SCSPP, and discusses the associated advantages and disadvantages.
+A comparison of these heuristics and an analysis of the results will be provided in Section 4, and finally Section 5 concludes the paper and proposes some potential directions for future work.
+
+\section{Solving the CPOP}
+
+\textcolor{OrangeRed}{Model the problem using a graph. partner function}
 
@@
 
-In the problem detailed by Goulimis, the aim is to align all of the items onto a single strip.
-So, when an instance of this problem is expressed as an instance of the CPOP, the widths of the individual items are not taken into account.
-In reality, strips of material are provided in fixed lengths.
-Given a large problem instance, multiple strips may be required to feasibly accommodate all of the items.
-For this reasons, we define a new problem to be investigated.
-
-\begin{definition}
-	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ with equal fixed length $l$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the minimum total score width constraint is met between every pair of adjacent items on every strip.
-\end{definition}
-
 Indeed, the SCSPP is a generalisation of the classical one-dimensional bin-packing problem (BPP), where in the latter problem, the minimum scoring distance $\tau$ can be said to be equal to zero.
@@
 Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$.
+
+\section{Heuristics}
+
+The first heuristic to be discussed is the Score-Constrainted First-Fit Decreasing (SCFFD) heuristic, which is an extension of the original FFD.
+The items in $\mathcal{I}$ are, as usual, sorted in non-increasing order of widths, with ties broken by selecting the item with the smallest score width.
+Then, for each item $i \in \mathcal{I}$, SCFFD finds the lowest-indexed strip $S_j$ that can accommodate $i$ without being overfilled.
+If this strip $S_j$ is empty, place $i$ onto $S_j$ in a regular orientation, and add $S_j$ to the solution set $\mathcal{S}$.
+However, if $S_j$ is not empty, i.e.
+$S_j \in \mathcal{S}$, the algorithm checked if the vicinal sum constraint is met between the right-most score width on $S_j$ and one of the two score widths on $i$, assessing the smaller score width $a_i$ first.
+In either case, if the constraint is met, $i$ is placed accordingly onto $S_j$.
+Indeed, an item $i$ may not fulfil the vicinal sum constraint in any orientation, in which case SCFFD finds the next lowest-indexed strip and attempts to pack $i$ again.
+This process continues until every item $i \in \mathcal{I}$ has been placed onto a strip $S_j \in \mathcal{S}$.
 

### 2018-02-06 paper/ffdexact/packingexact.cpp
added smallest score width first packing algorithm

@@ -31,9 +31,11 @@ void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth
     int feasible;
     vector<int> boxDecrease;
     vector<int> checked(numScores, 0);
+    int count = 0;
 
 
-    while(boxDecrease.size() < numBox) {
+
+    /*while(boxDecrease.size() < numBox) {
         for (i = 0; i < numScores; ++i) {
             if(checked[i] == 1){
                 continue;
@@ -48,7 +50,7 @@ void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth
         checked[mates[mini]] = 1;
         max = min;
         min = 0;
-    }
+    }*/
 
     /*cout << "Box decrease:\n";
     for(i = 0; i < boxDecrease.size(); ++i){
@@ -56,9 +58,9 @@ void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth
     }
     cout << endl << endl;*/
 
-    strip[0].push_back(boxDecrease[0]);
+    /*strip[0].push_back(boxDecrease[0]);
     strip[0].push_back(mates[boxDecrease[0]]);
-    stripSum[0] += boxWidths[boxDecrease[0]][mates[boxDecrease[0]]];
+    stripSum[0] += boxWidths[boxDecrease[0]][mates[boxDecrease[0]]];*/
 
 
     /*for(j = 1; j < boxDecrease.size(); ++j){
@@ -82,7 +84,7 @@ void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth
     }*/
 
 
-    for(j = 1; j < boxDecrease.size(); ++j){
+    /*for(j = 1; j < boxDecrease.size(); ++j){
         for(i = 0; i < strip.size(); ++i){
             if(!strip[i].empty()){
                 if(stripSum[i] + boxWidths[boxDecrease[j]][mates[boxDecrease[j]]] <= maxStripWidth){
@@ -98,13 +100,13 @@ void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth
                         stripSum[i] += boxWidths[boxDecrease[j]][mates[boxDecrease[j]]];
                         break;
                     }
-                    /*else{
+                    *//*else{
                         feasible = 0;
                         MBAHRA(i, j, feasible, allScores, mates, adjMatrix, boxWidths, boxDecrease, stripSum, strip);
                         if(feasible == 1){
                             break;
                         }
-                    }*/
[…]

### 2018-02-07 paper/main.tex
added explanation of the three heuristics, started making changed to the cpop alg

@@
 
-\textcolor{OrangeRed}{Model the problem using a graph. partner function}
+We shall now present an algorithm for solving the CPOP, which operates by expressing the problem instance graphically.
 
-Let $\mathcal{M}$ be a multiset as described in Definition \ref{defn:cpop}, with an additional unordered pair consisting of ``dominating'' values equal to $\tau$.
-Two values that make up a pair in $\mathcal{M}$ are referred to as ``partners''.
-Then, $G(V, P \cup E)$ is an undirected graph defined by a vertex set $V = \{v_1, v_2, ...v_{2n+2}\}$, where each vertex is assigned a value from $\mathcal{M}$ such that $v_1 \leq v_2 \leq ...
+Let $\mathcal{M}$ be an instance of the CPOP of cardinality $n$ as described in Definition \ref{defn:cpop}.
+Then, the graph $G$ is defined by a vertex set $V = \{v_1, v_2, ...v_{2n+2}\}$, where each vertex is assigned a value from $\mathcal{M}$ such that $v_1 \leq v_2 \leq ...
 \leq v_{2n+2}$.
-$G$ comprises two distinct edge sets: $P$, which contains edges between vertices that are partners, and $E$, which consists of edges between vertices that fulfil the \textit{joint sum constraint}.
+Note that there are two extra ``dominating'' vertices, $v_{2n+1}$ and $v_{2n+2}$, which have values equivalent to $\tau$.
+In $\mathcal{M}$, the values that make up a pair are referred to as ``partners''.
+Thus, let $p: V \to V$ be a bijective function that associates each vertex $v_i \in V$ on $G$ with its partner, $v_j = p(v_i)$.
+$G$ comprises two distinct edge sets: $P$, which contains edges between vertices that are partners, and $E$, which consists of edges between vertices whose corresponding values in $\mathcal{M}$ can be arranged alongside one another.
 That is, for two distinct vertices $v_i, v_j$,
@@
 
-provided $\{v_i, v_j\} \notin P$. Observe that $P$ is in fact a perfect matching, with $|P| = |\mathcal{M}| = n+1$, and that $P \cap E = \emptyset$.
+provided $p(v_i) \neq v_j$.
+Hence, $G(V, P \cup E)$ is an undirected graph with $2n + 2$ vertices and edge sets $P$ and $E$, such that $P \cap E = \emptyset$.
+Observe that $P$ is in fact a perfect matching, with $|P|= n+1$.
 
-If $G(V, P\cup E)$ features an alternating Hamiltonian cycle, then a feasible solution $\mathcal{T}$ exists.
+The following definition describes a variant of the classical Hamiltonian cycle on a graph $G$.
 
@@
 $G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such successive edges alternate between sets $P$ and $E$.
-For example, if $\{v_{i-1}, v_i\} \in P$, then $\{v_i, v_{i+1}\} \in E$, or vice versa.
+For example, if $(v_{i-1}, v_i) \in P$, then $(v_i, v_{i+1}) \in E$, or vice versa.
 \end{definition}
@@
 
+\section{Solving the SCSPP/Heuristics}
+
 Indeed, the SCSPP is a generalisation of the classical one-dimensional bin-packing problem (BPP), where in the latter problem, the minimum scoring distance $\tau$ can be said to be equal to zero.
@@
 
+\subsection{FFD Approx}
 The first heuristic to be discussed is the Score-Constrainted First-Fit Decreasing (SCFFD) heuristic, which is an extension of the original FFD.
@@
 However, if $S_j$ is not empty, i.e.
-$S_j \in \mathcal{S}$, the algorithm checked if the vicinal sum constraint is met between the right-most score width on $S_j$ and one of the two score widths on $i$, assessing the smaller score width $a_i$ first.
+$S_j \in \mathcal{S}$, the algorithm checks if the vicinal sum constraint is met between the right-most score width on $S_j$ and one of the two score widths on $i$, assessing the smaller score width $a_i$ first.
 In either case, if the constraint is met, $i$ is placed accordingly onto $S_j$.
@@
 This process continues until every item $i \in \mathcal{I}$ has been placed onto a strip $S_j \in \mathcal{S}$.
+
+\subsection{Smallest First}
+This next heuristic focusses on packing each strip in turn, rather than each item as in the previous heuristic.
+Each new strip $S_j$ is initialised by placing the item $i \in \mathcal{I}'$ with the smallest score width onto $S_j$ in a regular position, where $\mathcal{I}'$ is the set of items that have not yet been packed onto a strip.
+The heuristic then continues to pack items onto $S_j$, by choosing an item in $\mathcal{I}'$ with the smallest score width that fulfils the vicinal sum constraint when placed alongside the right-most score width on $S_j$, and that does not exceed $S_j$'s capacity.
+Once there are no more items in $\mathcal{I}'$ that can be feasibly packed onto $S_j$, the heuristic adds $S_j$ to the solution set $\mathcal{S}$, and the next new strip $S_{j+1}$ is initialised.
+When $|\mathcal{I}'| = 0$, all items have been packed onto a strip, and the process terminates.
+
+\subsection{FFD Exact} 
+The last heuristic in this paper is formed by integrating the Alternating Hamiltonian Construction Algorithm (AHCA) detailed in Section ref{} with the classical FFD heuristic.
+Again, all items in $\mathcal{I}$ are sorted into non-increasing order of widths, with ties broken by choosing the item with the smallest score width.
+For each item $i \in \mathcal{I}$, the heuristic finds the lowest-indexed feasible strip $S_j$.
+As in the first heuristic, if $S_j$ is empty, $i$ is placed in a regular orientation onto $S_j$, and $S_j$ is then added to the solution set $\mathcal{S}$.
+Unlike the first heuristic, however, if $S_j$ is not empty ($S_j \in \mathcal{S}$), AHCA is applied on all items in $S_j$ and the current item $i$.
+If AHCA is successful, the items currently on $S_j$ are replaced by the new arrangement, which of course includes $i$.
+In the event that AHCA is unable to produce a solution, $S_j$ remains intact, and the heuristic attempts to pack $i$ onto the next lowest-indexed feasible strip.
 

### 2018-02-07 paper/main.tex
edited the CPOP algorithm

@@
 
-The values in each unordered pair in $\mathcal{M}$ cannot be altered, and so every edge in $P$ must be present in the alternating Hamiltonian cycle.
-Thus, the task involves finding a matching $Q \subset E$ of cardinality $n+1$, such that the edge sets $P$ and $Q$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.
-If no suitable matching $Q$ can be found, then, in accordance with Theorem \ref{thm:cpopsolnalt}, no feasible solution exists for the given instance $\mathcal{M}$.
+Therefore, the aim of this algorithm is to construct an alternating Hamiltonian cycle on $G$.
+Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, every edge in $P$ must be present in the alternating Hamiltonian cycle.
+Consequently, the task now involves finding a matching $Q \subset E$ of cardinality $n+1$, such that the edge sets $P$ and $Q$ form an alternating Hamiltonian cycle as described in Definition $\ref{defn:althamcycle}$.
 
-To find a matching $Q \subset E$, the following modified maximum cardinality matching algorithm is executed (\citealp{mahadev1994, becker2010}): for each vertex $v_i, i = 1, 2,...,2n+2$, find the largest vertex in $v_i$'s neighbourhood, excluding partners, that is not incident to any edge in $Q$.
+To find a matching $Q \subset E$, the following modified maximum cardinality matching algorithm is executed (\citealp{mahadev1994, becker2010}): for each vertex $v_i$, $i = 1, 2,...,2n+2$, find the largest vertex $v_j \in \Gamma(v_i)\backslash p(v_i)$ (i.e.
+the largest vertex $v_j$ in $v_i$'s neighbourhood that is not $v_i$'s partner) that is not incident to any edge in $Q$.
 Add the edge connecting these two vertices to $Q$, and proceed to the next vertex until all vertices have been assessed.
@@
 
-During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner, the preceeding vertex $v_{i-1}$ can be rematched, provided that $v_i$ is not the first vertex (i.e $i \neq 1$), $v_{i-1}$ is incident to an edge in $Q$, (i.e.
-$v_{i-1}$ has been matched) and $v_{i-1}$ is adjacent to $v_i$'s partner via an edge in $E$.
-Then, $v_{i-1}$ is matched with $v_i$'s partner, and $v_i$ is matched with $v_{i-1}$'s previous match.
-It is guaranteed that this algorithm will produce a maximum cardinality matching $Q \subset E$ (\citealp{becker2010}).
+During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided $v_i$ is not the first vertex (i.e $i \neq 1$), $v_{i-1}$ has been matched, and $(v_{i-1}, p(v_i)) \in E$.
+Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$.
+It is guaranteed that this algorithm will produce a maximum cardinality matching $Q \subset E$.
+This algorithm is able to create a matching set $Q$ in at most $O(n \log n)$ time.
 
-If $|Q| < n+1$, clearly there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $P$, and hence there is no feasible solution to this particular instance of the CPOP.
-However, if $|Q| = n+1$, then the spanning subgraph $G'(V, P \cup Q)$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $P$, and its match via an edge in $Q$.
-$G'$ thus consists of a collection of alternating Hamiltonian cycles $A_1, A_2, ..., A_{\lambda}$.
-If there is only one alternating Hamiltonian cycle on $G'$, i.e.
-$\lambda = 1$, then a feasible solution has been found \textcolor{OrangeRed}{remove dominating vertices}.
-If $\lambda > 1$, then the components of $G'$ need to be combined into one single alternating Hamiltonian cycle, by removing some matching edges from $Q$, and adding new edges from $E$.
-The following algorithm finds edges that are able to merge the components of $G'$ together.
+Clearly, if $|Q| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $P$, and hence in accordance with Theorem $\ref{thm:cpopsolnalt}$ no feasible solution exists for the given instance $\mathcal{M}$ of the CPOP.
+Otherwise, if $Q$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'(V, P \cup Q)$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $P$, and its match via an edge in $Q$.
+$G'$ thus consists of a collection of alternating cycles $A_1, A_2, ..., A_{\lambda}$.
+If there is only one component on $G'$, i.e.
+$\lambda = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists.
+For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle.
+The algorithm thus executes a procedure that selects suitable edges in $E$ to replace specific edges in $Q$, such that the components of $G'$ are merged together.
 
-For each edge $(v_i, v_j) \in Q$, with $i < j$, $v_i$ is referred to as the ``smaller'' vertex, and $v_j$ as the ``larger'' vertex, since the value associated with $v_i$ is less than or equal to the value associated with $v_j$.
-Initially, the edges in $Q$ are sorted in a list such that the smaller vertices of the edges are in lexicographical order, and therefore in non-decreasing order of values.
-\textcolor{OrangeRed}{remove edges from list that are a result of rematching}.
-Starting from the first edge, search through the list to find an edge that meets the following conditions:
+For each edge $(v_i, v_j) \in Q$, where $i < j$, $v_i$ is referred to as the ``smaller'' vertex, and $v_j$ as the ``larger'' vertex, since the value associated with $v_i$ is less than or equal to the value associated with $v_j$.
+The procedure initially sorts the edges in $Q$ into a list such that the smaller vertices of the edges are in lexicographical order, and therefore in non-decreasing order of values.
+Any edges that are a result of rematching are then removed from this list.
+Starting from the first edge, the procedure searches through the list to find an edge that meets the following conditions:
 \begin{enumerate}
-	\item The smaller vertex of the current edge is adjacent to the larger vertex of the succeeding edge in the list via an edge in $E$,
-	\item The current edge and the succeeding edge are members of different alternating Hamiltonian cycles on $G$.
+	\item The smaller vertex of the current edge and the larger vertex of the succeeding edge are connected by an edge in $E$.
+	\item The current edge and the succeeding edge are members of different components on $G'$.
 \end{enumerate}
 
-If such an edge is found, add it to a set $C_i$, and continue to add all succeeding edges in the list to $C_i$, provided that for each edge conditions 1 and 2 hold, and the succeeding edge does not belong to a component on $G$ that is already represented by an edge in $C_i$.
-Once there are no more valid edges to add to $C_i$, continue to search through the remaining edges in the list to find an edge that meets conditions 1 and 2, and can therefore start a new set $C_{i+1}$.
-If the final edge in the list has been reached, the process is terminated.
+If such an edge is found, the procedure adds this edge to a set $C_i$, and continues to add all succeeding edges in the list to $C_i$, provided that for each edge conditions 1 and 2 hold, and the succeeding edge is not a member of a component on $G'$ that already has an edge in $C_i$.
+Once there are no more valid edges to add to $C_i$, the procedure resumes its search through the remaining edges in the list to find a new edge that meets conditions 1 and 2, and can therefore start a new set $C_{i+1}$.
+The procedure ends when the penultimate edge in the list has been examined.
 
-The sets $C_i, i = 1, ..., k$ that have been created during this process are then analysed.
-In the case where not a single set $C$ has been produced, then the cycles $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
-If there exists a set $C_i$ such that $|C_i| = \lambda$, then all components on $G'$ can be combined as follows:
+The sets $C_1, C_2, ..., C_k$ created during this process are then analysed.
+In the event that the procedure has been unable to produce a single set $C$, the components $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
+If there exists a set $C_i$ such that $|C_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':
 
-Starting from the first edge in $C_i$, add the edge from $E$ connecting the smaller vertex of each edge to the larger vertex of the succeeding edge to the matching $Q$.
+Starting from the first edge in $C_i$, add the edge from $E$ connecting the smaller vertex of each edge to the larger vertex of the succeeding edge to $Q$.
 For the final edge in $C_i$, add the edge from $E$ that connects its smaller vertex to the larger vertex of the first edge in $C_i$ to $Q$.
-Then, edges that appear in both $C_i$ and $Q$ are removed from $Q$, such that $C_i \cap Q = \emptyset$.
-\textcolor{OrangeRed}{Then components have been merged, remove dominating vertices etc}.
+Finally, any edges that appear in both $C_i$ and $Q$ are removed from $Q$, such that $C_i \cap Q = \emptyset$, and $Q$ returns to being a perfect matching.
+$G'$ then comprises a single alternating Hamiltonian cycle, and thus the algorithm has found a solution to the problem instance.
 
-If there is no set $C_i$ such that $|C_i| = \lambda$, and $k > 1$ (i.e.
-there are multiple sets $C_i, i = 1,..., k$), it may be that multiple sets are required to combine the components of $G'$.
-Let $\mathcal{C}$ be a set that will contain all the sets $C_i$ needed to merge all components of $G'$ together, and let $\Lambda$ be a set that records the components covered by the sets in $\mathcal{C}$.
-For the set $C_1$, append the components $A_i$ that each edge in $C_1$ is a member of to $\Lambda$, and then add $C_1$ to $\mathcal{C}$.
+Else, if $k > 1$, it may be that multiple sets are required to combine the components of $G'$.
+Let $\mathcal{C}$ be a set that contains the sets $C_i$ needed to connect the components of $G'$ together, and let $\Lambda$ be a set that records the components covered by the sets in $\mathcal{C}$.
+Start by adding the components $A_i$ that each edge in $C_1$ is a member of to $\Lambda$, and then add $C_1$ to $\mathcal{C}$.
 At this stage, $|\Lambda| = |\mathcal{C}|$.
-Proceeding through the sets $C_i, i = 2, ..., k$, find a set $C_i$ that contains at least one edge that is a member of a component recorded in $\Lambda$, and at least one edge that is a member of a component not yet recorded in $\Lambda$.
-Append the component that each edge in this set $C_i$ is a member of to $\Lambda$, provided the component is not already a member of $\Lambda$, and add $C_i$ to $\mathcal{C}$.
+Proceeding through the remaining sets $C_2, C_3, ..., C_k$, find a set $C_i$ that contains at least one edge that is a member of a component in $\Lambda$, and at least one edge that is a member of a component not yet recorded in $\Lambda$.
+Append the component that each edge in this set $C_i$ is a member of to $\Lambda$, provided the component is not already an element of $\Lambda$, then add $C_i$ to $\mathcal{C}$.
 Continue in this manner until the final set $C_k$ has been assessed.
-If $|\Lambda| = \lambda$, then the sets in $\mathcal{C}$ are able to merge the components of $G'$ together.
-This is done by repeating the connecting process for a single set $C_i$ on every set in $\mathcal{C}$.
+If $|\Lambda| = \lambda$, i.e.
+all components of $G'$ are elements of $\Lambda$, then the sets in $\mathcal{C}$ are able to combine the components of $G'$ to form a single alternating Hamiltonian cycle.
+This is achieved by repeating the connecting method described previously on every set $C_i \in \mathcal{C}$.
 
-\textcolor{OrangeRed}{Complexity of the CPOP algorithm, ability to find a solution, complete recognition.}
+This algorithm, which will be referred to as the Alternating Hamiltonian Construction Algorithm (AHCA) is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the CPOP.
+If a solution does indeed exist, AHCA can produce this solution in at most $O(n^2)$ time.
 
@@
 Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$.
-
-\section{Heuristics}
 

### 2018-02-08 paper/SCSPP/main.cpp
changed name of packStripsFFD to packstripsFFDExact in for loop

@@ -115,17 +115,13 @@ int main(int argc, char **argv){
         createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates,
                        adjMatrix, boxWidths);
 
-        packStripsFFD(numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix,
+        packStripsFFDExact(numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix,
                       boxWidths, stripSum, strip);
 
         resetVectors(numScores, numBox, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
         cout << endl;
     }
-
-
-
-
-
+    
 
     endTime = clock();
     double totalTime = (((endTime - startTime) / double(CLOCKS_PER_SEC)) * 1000);

### 2018-02-08 paper/SCSPP/packing.cpp
added two new functions

@@ -22,20 +22,18 @@ int lowerBound(int maxStripWidth, double totalBoxWidth){
     return lBound;
 }
 
-void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
-                   vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip){
+void packStripsFFDApprox(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
+        vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip){
 
     int i, j, mini, k, l;
     int min = 0;
     int max = maxBoxWidth;
-    int feasible;
     vector<int> boxDecrease;
     vector<int> checked(numScores, 0);
-    int count = 0;
 
 
 
-    /*while(boxDecrease.size() < numBox) {
+    while(boxDecrease.size() < numBox) {
         for (i = 0; i < numScores; ++i) {
             if(checked[i] == 1){
                 continue;
@@ -50,7 +48,7 @@ void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth
         checked[mates[mini]] = 1;
         max = min;
         min = 0;
-    }*/
+    }
 
     /*cout << "Box decrease:\n";
     for(i = 0; i < boxDecrease.size(); ++i){
@@ -58,33 +56,12 @@ void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth
     }
     cout << endl << endl;*/
 
-    /*strip[0].push_back(boxDecrease[0]);
+    strip[0].push_back(boxDecrease[0]);
     strip[0].push_back(mates[boxDecrease[0]]);
-    stripSum[0] += boxWidths[boxDecrease[0]][mates[boxDecrease[0]]];*/
+    stripSum[0] += boxWidths[boxDecrease[0]][mates[boxDecrease[0]]];
 
 
-    /*for(j = 1; j < boxDecrease.size(); ++j){
-        for(i = 0; i < strip.size(); ++i){
-            if(!strip[i].empty()){
-                if(stripSum[i] + boxWidths[boxDecrease[j]][mates[boxDecrease[j]]] <= maxStripWidth){
-                    feasible = 0;
[…]

### 2018-02-08 paper/SCSPP/packing.h
added two new functions

@@ -14,7 +14,13 @@ void swap(int &a, int &b);
 
 int lowerBound(int maxStripWidth, double totalBoxWidth);
 
-void packStripsFFD(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
+void packStripsFFDApprox(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
+                         vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+
+void packStripsFFDSmallest(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
+                         vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+
+void packStripsFFDExact(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
                    vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 void MBAHRA(int i1, int j1, int &feasible, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,

### 2018-02-08 paper/SCSPP/base.cpp
changed all includes to remove exact

@@ -5,7 +5,7 @@ base.cpp
 /--------------*/
 #include <algorithm>
 #include <iomanip>
-#include "baseexact.h"
+#include "base.h"
 using namespace std;
 
 void resetVectors(int numScores, int numBox, vector<int> &allScores, vector<int> &mates,

### 2018-02-08 paper/SCSPP/main.cpp

@@ -8,8 +8,8 @@ mainexact.cpp
 #include <ctime>
 using namespace std;
 
-#include "baseexact.h"
-#include "packingexact.h"
+#include "base.h"
+#include "packing.h"
 
 int main(int argc, char **argv){
     //region USAGE - ARGUMENTS REQUIRED

### 2018-02-08 paper/SCSPP/packing.cpp

@@ -6,7 +6,7 @@ packing.cpp
 #include <algorithm>
 #include <cmath>
 #include <iomanip>
-#include "packingexact.h"
+#include "packing.h"
 using namespace std;
 
 void swap(int &a, int &b){

### 2018-02-08 paper/SCSPP/main.cpp
added switch statement for selecting which type of packing to use

@@ -13,7 +13,7 @@ using namespace std;
 
 int main(int argc, char **argv){
     //region USAGE - ARGUMENTS REQUIRED
-    if(argc < 8){
+    if(argc < 9){
         cout << "Minimum Score Separation Problem: MBAHRA.\n";
         cout << "Arguments are the following:\n";
         cout << "- Number of instances (integer)\n";
@@ -25,6 +25,7 @@ int main(int argc, char **argv){
         cout << "- Maximum width of strips (millimeters)\n";
         cout << "- Random Seed (integer)\n";
         cout << "- Name of input file (must have .txt extension)\n";
+        cout << "- packType: 1 = Approx, 2 = Smallest, 3 = Exact\n";
         exit(1);
     }
     //endregion
@@ -38,6 +39,7 @@ int main(int argc, char **argv){
     int maxBoxWidth = atoi(argv[5]); //max box width (mm)
     int maxStripWidth = atoi(argv[6]);
     int randomSeed = atoi(argv[7]); //random seed
+    int packType = atoi(argv[8]);
 
     int i, j;
     int instance; //counter for instances loop
@@ -109,18 +111,40 @@ int main(int argc, char **argv){
 
         //endregion
 
-    for(i = 0; i < 1; ++i) {
-        cout << "Instance: " << i << endl;
-
-        createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates,
+    createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates,
                        adjMatrix, boxWidths);
 
-        packStripsFFDExact(numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix,
-                      boxWidths, stripSum, strip);
+    switch(packType){
+        case 1:
+            cout << "FFD Approx:\n\n";
+            packStripsFFDApprox(numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
+            break;
 
-        resetVectors(numScores, numBox, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
-        cout << endl;
+        case 2:
+            cout << "FFD Smallest:\n\n";
[…]

### 2018-02-08 paper/SCSPP/base.cpp
output of allscores

@@ -62,10 +62,10 @@ void createInstance(int numScores, int numBox, int minWidth, int maxWidth, int m
     sort(allScores.begin(), allScores.end()); //sorts elements of vector in ascending order
 
     //cout << "All scores:\n";
-    /*for(i = 0; i < allScores.size(); ++i){
+    for(i = 0; i < allScores.size(); ++i){
         cout << allScores[i] << " ";
     }
-    cout << endl;*/
+    cout << endl;
     //Filling in adjacency matrix - if sum of two scores >= threshold (70), then insert 1 into the matrix, else leave as 0
     for (i = 0; i < allScores.size() - 1; ++i) {
         for (j = i + 1; j < allScores.size(); ++j) {

### 2018-02-08 paper/SCSPP/main.cpp
changed spacing between cout statements in switch

@@ -116,17 +116,17 @@ int main(int argc, char **argv){
 
     switch(packType){
         case 1:
-            cout << "FFD Approx:\n\n";
+            cout << "FFD Approx:\n";
             packStripsFFDApprox(numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
             break;
 
         case 2:
-            cout << "FFD Smallest:\n\n";
+            cout << "FFD Smallest:\n";
             packStripsFFDSmallest(numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
             break;
 
         case 3:
-            cout << "FFD Exact:\n\n";
+            cout << "FFD Exact:\n";
             packStripsFFDExact(numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
             break;
 
@@ -149,7 +149,7 @@ int main(int argc, char **argv){
 
     endTime = clock();
     double totalTime = (((endTime - startTime) / double(CLOCKS_PER_SEC)) * 1000);
-    cout << "\nCPU Time = " << totalTime << " milliseconds.\nEND.\n";
+    cout << "CPU Time = " << totalTime << " milliseconds.\nEND.\n";
 
 
 

### 2018-02-08 paper/SCSPP/packing.cpp
changed packstripssmallest so that score widths with larger opposite score widths come first

@@ -128,31 +128,56 @@ void packStripsFFDSmallest(int numScores, int numBox, int maxBoxWidth, int maxSt
 
     int i, j, k, l;
     int count = 0;
+    vector<int> scoreInc;
     vector<int> checked(numScores, 0);
+
+    for(i = 0; i < numScores; ++i){
+        scoreInc.push_back(i);
+    }
+
+    for(i = 0; i < scoreInc.size() - 1; ++i){
+        for(j = i+1; j < scoreInc.size(); ++j){
+            if(allScores[scoreInc[i]] == allScores[scoreInc[j]]){
+                if(allScores[mates[scoreInc[i]]] < allScores[mates[scoreInc[j]]]){
+                    swap(scoreInc[i], scoreInc[j]);
+                }
+            }
+            else{
+                break;
+            }
+        }
+    }
+
+    /*cout << "Scores Increase:\n";
+    for(auto number : scoreInc){
+        cout << number << " ";
+    }
+    cout << endl;*/
+
 
     j = 0;
     while (count < numScores){
-        for(i = 0; i < numScores; ++i){
-            if(checked[i] == 1){
+        for(i = 0; i < scoreInc.size(); ++i){
+            if(checked[scoreInc[i]] == 1){
                 continue;
             }
             if(strip[j].empty()){
-                strip[j].push_back(i);
-                strip[j].push_back(mates[i]);
-                stripSum[j] += boxWidths[i][mates[i]];
-                checked[i] = 1;
-                checked[mates[i]] = 1;
+                strip[j].push_back(scoreInc[i]);
+                strip[j].push_back(mates[scoreInc[i]]);
+                stripSum[j] += boxWidths[scoreInc[i]][mates[scoreInc[i]]];
+                checked[scoreInc[i]] = 1;
+                checked[mates[scoreInc[i]]] = 1;
                 count += 2;
                 i = -1;
                 continue;
             }
             else if(!strip[j].empty()){
-                if(adjMatrix[strip[j].back()][i] == 1 && stripSum[j] + boxWidths[i][mates[i]] <= maxStripWidth){
-                    strip[j].push_back(i);
-                    strip[j].push_back(mates[i]);
-                    stripSum[j] += boxWidths[i][mates[i]];
-                    checked[i] = 1;
-                    checked[mates[i]] = 1;
[…]

### 2018-02-08 paper/main.tex
added labels to all environments

@@
 \begin{definition}
+	\label{defn:scspp}
 	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ with equal fixed length $l$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the minimum total score width constraint is met between every pair of adjacent items on every strip.
@@
 \section{Solving the CPOP}
+\label{sec:ahca}
 
@@
 \begin{theorem}
-	\label{thm:cpopsolnalt}
+	\label{thm:cpopsoln}
 	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the CPOP if and only if its corresponding graph $G(V, P\cup E)$ contains an alternating Hamiltonian cycle.
@@
 
-Clearly, if $|Q| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $P$, and hence in accordance with Theorem $\ref{thm:cpopsolnalt}$ no feasible solution exists for the given instance $\mathcal{M}$ of the CPOP.
+Clearly, if $|Q| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $P$, and hence in accordance with Theorem $\ref{thm:cpopsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the CPOP.
 Otherwise, if $Q$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'(V, P \cup Q)$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $P$, and its match via an edge in $Q$.
@@
 \section{Solving the SCSPP/Heuristics}
+\label{sec:scsppsoln}
 
@@
 \begin{equation}
+	\label{eqn:lowerbound}
 	k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{l}}
@@
 \subsection{FFD Approx}
+\label{sec:ffdapprox}
 The first heuristic to be discussed is the Score-Constrainted First-Fit Decreasing (SCFFD) heuristic, which is an extension of the original FFD.
@@
 \subsection{Smallest First}
+\label{sec:ffdsmall}
 This next heuristic focusses on packing each strip in turn, rather than each item as in the previous heuristic.
@@
 \subsection{FFD Exact}
+\label{sec:ffdexact}
 The last heuristic in this paper is formed by integrating the Alternating Hamiltonian Construction Algorithm (AHCA) detailed in Section ref{} with the classical FFD heuristic.
@@
 
-%========================================================================%
-
-\begin{comment}
-The PSP can be seen in a problem related to the cutting-stock problem, first described by \cite{goulimis2004}.
-Let $\mathcal{I}$ be a set of rectangular items of equal heights, made from corrugated cardboard.
-Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$ and possess two vertical score lines.
-A pair of knives mounted on a bar will cut along these score lines to allow the items to be folded with ease.
-The distances between each edge of an item and the nearest score line are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$.
-As illustrated in Figure \ref{fig:boxesknife}, the knives cut along score lines from two adjacent items simultaneously.
-By design, the knives cannot be placed too close to one another - the distance between the knives must exceed a fixed minimum $\tau \in \mathbb{R}^{+}$ (around 70mm in industry).
-In order for the knives to be able to cut the items in the correct locations, two adajcent score widths, for example $a_i$ and $b_{i+1}$, must fulfil the \textit{minimum total score width constraint}
-
-\begin{equation*}
-a_i + b_{i+1} \geq \tau.
-\end{equation*}
-
-That is, the sum of two adjacent score widths must exceed the \textit{minimum total score width} $\tau$.
-Therefore, the problem involves finding a feasible arrangement of the items such that between each pair of items the minimum total score width constraint is met.
-
-\begin{figure}[H]	
-\centering
-\includestandalone[width=0.4\textwidth]{figures/boxesknifeannotate}
-\caption{\textcolor{red}{Individual boxes.}}	
-\label{fig:boxesknife}
-\end{figure}
-
-Since the score widths on each item $i \in \mathcal{I}$ are not necessarily equal, they can be aligned in two distinct orientations: ``regular'', denoted by $(a_i, b_i)$, and ``rotated'', denoted by $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right-hand side of the item respectively.
-
-This can be seen as a PSP, where the values $x_i$ and $y_i$ are the score widths, and a feasible solution $\mathcal{X}$ consists of an arrangement of items in some order such that $\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \forall  i \in \{1,2,..., |\mathcal{I}|-1\}$.
-
-There exists a polynomial-time algorithm that is able to recognise whether a particular instance of this problem is feasible (\citealp{becker2010}).
-
-\end{comment}
-
 \bibliographystyle{dcu}

### 2018-02-08 paper/SCSPP/main.cpp
changed statements to inlclude opt parameters

@@ -31,7 +31,7 @@ int main(int argc, char **argv){
     //endregion
 
     //region VARIABLES
-    //int numInstances = atoi(argv[1]); //number of instances of mssp, use in main for loop
+    int numInstances = 20; //number of instances of mssp, use in main for loop
     int numBox = atoi(argv[1]); //number of boxes in mssp plus 1 extra box (scores on either side of extra box will be dominating vertices, score widths = 71)
     int minWidth = atoi(argv[2]); //minimum width of scores (millimeters)
     int maxWidth = atoi(argv[3]); //maximum width of scores (millimeters)
@@ -56,6 +56,14 @@ int main(int argc, char **argv){
     double totalBoxWidth = 0.0;
     vector<int> stripSum(numBox, 0);
     vector<vector<int> > strip(numBox);
+    int opt = 0;
+    int opt90 = 0;
+    int opt80 = 0;
+    int opt70 = 0;
+    int opt60 = 0;
+    int opt50 = 0;
+    int optLow = 0;
+
     //endregion
 
 
@@ -111,32 +119,39 @@ int main(int argc, char **argv){
 
         //endregion
 
-    createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates,
-                       adjMatrix, boxWidths);
+    //createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths);
 
     switch(packType){
         case 1:
             cout << "FFD Approx:\n";
-            packStripsFFDApprox(numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
+            for(i = 0; i < numInstances; ++i){
+                createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths);
+                packStripsFFDApprox(opt, opt90, opt80, opt70, opt60, opt50, optLow, numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
+                resetVectors(numScores, numBox, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
+            }
             break;
 
[…]

### 2018-02-08 paper/SCSPP/packing.cpp
added optimality function

@@ -22,8 +22,38 @@ int lowerBound(int maxStripWidth, double totalBoxWidth){
     return lBound;
 }
 
-void packStripsFFDApprox(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
-        vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip){
+void optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB){
+
+    double c = static_cast<double>(LB) / stripSize;
+
+    if(stripSize == LB){
+        ++opt;
+    }
+    else if(c >= 0.9){
+        ++opt90;
+    }
+    else if(c >= 0.8){
+        ++opt80;
+    }
+    else if(c >= 0.7){
+        ++opt70;
+    }
+    else if(c >= 0.6){
+        ++opt60;
+    }
+    else if(c >= 0.5){
+        ++opt50;
+    }
+    else{
+        ++optLow;
+    }
+
+}
+
+
+void packStripsFFDApprox(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numBox, int maxBoxWidth,
+                         int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
+                         vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip){
 
     int i, j, mini, k, l;
     int min = 0;
@@ -99,11 +129,17 @@ void packStripsFFDApprox(int numScores, int numBox, int maxBoxWidth, int maxStri
         stripSum.pop_back();
         --l;
     }
-    cout << "After FFD: " << strip.size()<< " strips\n";
 
-    cout << "Lower Bound: " << lowerBound(maxStripWidth, totalBoxWidth) << " strips\n";
+    int stripSize = strip.size();
+    int LB = lowerBound(maxStripWidth, totalBoxWidth);
 
+    /*cout << "After FFD: " << stripSize << " strips\n";
 
+    cout << "Lower Bound: " << LB << " strips\n";*/
+
+    optimality(opt, opt90, opt80, opt70,opt60, opt50, optLow, stripSize, LB);
+
+/*
     cout << "Strips FFD (scores):\n";
[…]

### 2018-02-08 paper/SCSPP/packing.h

@@ -14,14 +14,19 @@ void swap(int &a, int &b);
 
 int lowerBound(int maxStripWidth, double totalBoxWidth);
 
-void packStripsFFDApprox(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
-                         vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB);
 
-void packStripsFFDSmallest(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
-                         vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void packStripsFFDApprox(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numBox, int maxBoxWidth,
+                         int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
+                         vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
-void packStripsFFDExact(int numScores, int numBox, int maxBoxWidth, int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates,
-                   vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void packStripsFFDSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numBox, int maxBoxWidth,
+                           int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
+                           vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+
+void packStripsFFDExact(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numBox, int maxBoxWidth,
[…]

### 2018-02-08 paper/SCSPP/base.cpp
added output function

@@ -41,6 +41,19 @@ void resetVectors(int numScores, int numBox, vector<int> &allScores, vector<int>
 
 }
 
+void output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int optLow, int numInstances){
+
+    cout << setprecision(2) << fixed;
+    cout << "Number of Instances: " << numInstances << endl;
+    cout << "#        opt of LB: " << opt << "\t\tPercentage: "<< static_cast<double>(opt)/numInstances << "\t\t# 100%: " << opt << endl;
+    cout << "# 90% - <opt of LB: " << opt90 << "\t\tPercentage: "<< static_cast<double>(opt90)/numInstances << "\t\t# >= 90%: " << opt + opt90 << endl;
+    cout << "# 80% - <90% of LB: " << opt80 << "\t\tPercentage: "<< static_cast<double>(opt80)/numInstances << "\t\t# >= 80%: " << opt + opt90 + opt80 << endl;
+    cout << "# 70% - <80% of LB: " << opt70 << "\t\tPercentage: "<< static_cast<double>(opt70)/numInstances << "\t\t# >= 70%: " << opt + opt90 + opt80 + opt70 << endl;
+    cout << "# 60% - <70% of LB: " << opt60 << "\t\tPercentage: "<< static_cast<double>(opt60)/numInstances << "\t\t# >= 60%: " << opt + opt90 + opt80 + opt70 + opt60 << endl;
+    cout << "# 50% - <60% of LB: " << opt50 << "\t\tPercentage: "<< static_cast<double>(opt50)/numInstances << "\t\t# >= 50%: " << opt + opt90 + opt80 + opt70 + opt60 + opt50 << endl;
+    cout << "#       <50% of LB: " << optLow << "\t\tPercentage: "<< static_cast<double>(optLow)/numInstances << endl;
+
+}
 
 void createInstance(int numScores, int numBox, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, double &totalBoxWidth,
                     vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths){
@@ -62,10 +75,10 @@ void createInstance(int numScores, int numBox, int minWidth, int maxWidth, int m
     sort(allScores.begin(), allScores.end()); //sorts elements of vector in ascending order
 
     //cout << "All scores:\n";
-    for(i = 0; i < allScores.size(); ++i){
[…]

### 2018-02-08 paper/SCSPP/base.h

@@ -14,6 +14,8 @@ using namespace std;
 void resetVectors(int numScores, int numBox, vector<int> &allScores, vector<int> &mates,
                   vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
+void output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int optLow, int numInstances);
+
 void createInstance(int numScores, int numBox, int minWidth, int maxWidth, int minBoxWidth, int maxBoxWidth, double &totalBoxWidth,
                     vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix, vector<vector<int> > &boxWidths);
 

### 2018-02-08 paper/SCSPP/base.cpp
cout statement all scores

@@ -74,11 +74,11 @@ void createInstance(int numScores, int numBox, int minWidth, int maxWidth, int m
     //Sort all of the scores in the allScores vector in ascending order
     sort(allScores.begin(), allScores.end()); //sorts elements of vector in ascending order
 
-    //cout << "All scores:\n";
-    /*for(i = 0; i < allScores.size(); ++i){
+    cout << "All scores:\n";
+    for(i = 0; i < allScores.size(); ++i){
         cout << allScores[i] << " ";
     }
-    cout << endl;*/
+    cout << endl;
     //Filling in adjacency matrix - if sum of two scores >= threshold (70), then insert 1 into the matrix, else leave as 0
     for (i = 0; i < allScores.size() - 1; ++i) {
         for (j = i + 1; j < allScores.size(); ++j) {

### 2018-02-08 paper/SCSPP/main.cpp
used int instance as counter for loop, added instance as parameter in ffdexact

@@ -31,7 +31,7 @@ int main(int argc, char **argv){
     //endregion
 
     //region VARIABLES
-    int numInstances = 20; //number of instances of mssp, use in main for loop
+    int numInstances = 21; //number of instances of mssp, use in main for loop
     int numBox = atoi(argv[1]); //number of boxes in mssp plus 1 extra box (scores on either side of extra box will be dominating vertices, score widths = 71)
     int minWidth = atoi(argv[2]); //minimum width of scores (millimeters)
     int maxWidth = atoi(argv[3]); //maximum width of scores (millimeters)
@@ -124,7 +124,7 @@ int main(int argc, char **argv){
     switch(packType){
         case 1:
             cout << "FFD Approx:\n";
-            for(i = 0; i < numInstances; ++i){
+            for(instance = 0; instance < numInstances; ++instance){
                 createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths);
                 packStripsFFDApprox(opt, opt90, opt80, opt70, opt60, opt50, optLow, numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
                 resetVectors(numScores, numBox, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
@@ -133,7 +133,7 @@ int main(int argc, char **argv){
 
         case 2:
             cout << "FFD Smallest:\n";
-            for(i = 0; i < numInstances; ++i){
+            for(instance = 0; instance < numInstances; ++instance){
                 createInstance(numScores, numBox, minWidth, maxWidth, minBoxWidth, maxBoxWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths);
                 packStripsFFDSmallest(opt, opt90, opt80, opt70, opt60, opt50, optLow, numScores, numBox, maxBoxWidth, maxStripWidth, totalBoxWidth, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
                 resetVectors(numScores, numBox, allScores, mates, adjMatrix, boxWidths, stripSum, strip);
@@ -142,9 +142,9 @@ int main(int argc, char **argv){
 
         case 3:
             cout << "FFD Exact:\n";
-            for(i = 0; i < numInstances; ++i){
[…]

### 2018-02-08 paper/SCSPP/packing.cpp
added instances as paramter in ffdexact, used if statements to output strips when instances == 20

@@ -267,7 +267,7 @@ void packStripsFFDSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &op
 
 }
 
-void packStripsFFDExact(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numBox, int maxBoxWidth,
+void packStripsFFDExact(int instance, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numBox, int maxBoxWidth,
                         int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
                         vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip){
 
@@ -296,6 +296,13 @@ void packStripsFFDExact(int &opt, int &opt90, int &opt80, int &opt70, int &opt60
         min = 0;
     }
 
+    if(instance == 20){
+        cout << "Box decrease:\n";
+        for(i = 0; i < boxDecrease.size(); ++i){
+        cout << boxDecrease[i] << " ";
+        }
+        cout << endl << endl;
+    }
     /*cout << "Box decrease:\n";
     for(i = 0; i < boxDecrease.size(); ++i){
         cout << boxDecrease[i] << " ";
@@ -314,6 +321,16 @@ void packStripsFFDExact(int &opt, int &opt90, int &opt80, int &opt70, int &opt60
                     feasible = 0;
                     MBAHRA(i, j, feasible, allScores, mates, adjMatrix, boxWidths, boxDecrease, stripSum, strip);
                     if(feasible == 1){
+                        if(instance == 20) {
+                            for (i = 0; i < strip.size(); ++i) {
+                                cout << "Strip " << i << ": ";
+                                for (j = 0; j < strip[i].size(); ++j) {
+                                    cout << strip[i][j] << " ";
+                                }
+                                cout << endl;
+                            }
+                            cout << endl;
+                        }
                         break;
                     }
                 }
@@ -322,6 +339,16 @@ void packStripsFFDExact(int &opt, int &opt90, int &opt80, int &opt70, int &opt60
                 strip[i].push_back(boxDecrease[j]);
                 strip[i].push_back(mates[boxDecrease[j]]);
                 stripSum[i] += boxWidths[boxDecrease[j]][mates[boxDecrease[j]]];
+                if(instance == 20) {
+                    for (i = 0; i < strip.size(); ++i) {
[…]

### 2018-02-08 paper/SCSPP/packing.h

@@ -24,7 +24,7 @@ void packStripsFFDSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &op
                            int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
                            vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
-void packStripsFFDExact(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numBox, int maxBoxWidth,
+void packStripsFFDExact(int instance, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numBox, int maxBoxWidth,
                         int maxStripWidth, double totalBoxWidth, vector<int> &allScores, vector<int> &mates, vector<vector<int> > &adjMatrix,
                         vector<vector<int> > &boxWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 

### 2018-02-08 paper/main.tex
added abbreviations for the modified maximum cardinality matching algrithm (MMCM) and bridge recognition (BR)

@@
 
-To find a matching $Q \subset E$, the following modified maximum cardinality matching algorithm is executed (\citealp{mahadev1994, becker2010}): for each vertex $v_i$, $i = 1, 2,...,2n+2$, find the largest vertex $v_j \in \Gamma(v_i)\backslash p(v_i)$ (i.e.
+To find a matching $Q \subset E$, the following modified maximum cardinality matching (MMCM) algorithm is executed (\citealp{mahadev1994, becker2010}): for each vertex $v_i$, $i = 1, 2,...,2n+2$, find the largest vertex $v_j \in \Gamma(v_i)\backslash p(v_i)$ (i.e.
 the largest vertex $v_j$ in $v_i$'s neighbourhood that is not $v_i$'s partner) that is not incident to any edge in $Q$.
@@
 Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$.
-It is guaranteed that this algorithm will produce a maximum cardinality matching $Q \subset E$.
-This algorithm is able to create a matching set $Q$ in at most $O(n \log n)$ time.
+It is guaranteed that MMCM will produce a maximum cardinality matching $Q \subset E$, and is able to do so in at most $O(n \log n)$ time.
 
@@
 For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle.
-The algorithm thus executes a procedure that selects suitable edges in $E$ to replace specific edges in $Q$, such that the components of $G'$ are merged together.
+The algorithm thus executes a Bridge Recognition (BR) procedure that selects suitable edges in $E$ to be used as bridges between the components of $G'$, and will replace certain edges in $Q$.
 
@@
 Any edges that are a result of rematching are then removed from this list.
-Starting from the first edge, the procedure searches through the list to find an edge that meets the following conditions:
+Starting from the first edge, BR searches through the list to find an edge that meets the following conditions:
 \begin{enumerate}
@@
 If such an edge is found, the procedure adds this edge to a set $C_i$, and continues to add all succeeding edges in the list to $C_i$, provided that for each edge conditions 1 and 2 hold, and the succeeding edge is not a member of a component on $G'$ that already has an edge in $C_i$.
-Once there are no more valid edges to add to $C_i$, the procedure resumes its search through the remaining edges in the list to find a new edge that meets conditions 1 and 2, and can therefore start a new set $C_{i+1}$.
+Once there are no more valid edges to add to $C_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets conditions 1 and 2, and can therefore start a new set $C_{i+1}$.
 The procedure ends when the penultimate edge in the list has been examined.
@@
 The sets $C_1, C_2, ..., C_k$ created during this process are then analysed.
-In the event that the procedure has been unable to produce a single set $C$, the components $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
+In the event that BR has been unable to produce a single set $C$, the components $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
 If there exists a set $C_i$ such that $|C_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':

### 2018-03-05 paper/SCSPP/base.cpp
added instance to createInstance parameters

@@ -43,18 +43,18 @@ void output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int 
 
     cout << setprecision(2) << fixed;
     cout << "Number of Instances: " << numInstances << endl;
-    cout << "#        opt of LB: " << opt << "\t\tPercentage: "<< static_cast<double>(opt)/numInstances << "\t\t# 100%: " << opt << endl;
-    cout << "# 90% - <opt of LB: " << opt90 << "\t\tPercentage: "<< static_cast<double>(opt90)/numInstances << "\t\t# >= 90%: " << opt + opt90 << endl;
-    cout << "# 80% - <90% of LB: " << opt80 << "\t\tPercentage: "<< static_cast<double>(opt80)/numInstances << "\t\t# >= 80%: " << opt + opt90 + opt80 << endl;
-    cout << "# 70% - <80% of LB: " << opt70 << "\t\tPercentage: "<< static_cast<double>(opt70)/numInstances << "\t\t# >= 70%: " << opt + opt90 + opt80 + opt70 << endl;
-    cout << "# 60% - <70% of LB: " << opt60 << "\t\tPercentage: "<< static_cast<double>(opt60)/numInstances << "\t\t# >= 60%: " << opt + opt90 + opt80 + opt70 + opt60 << endl;
-    cout << "# 50% - <60% of LB: " << opt50 << "\t\tPercentage: "<< static_cast<double>(opt50)/numInstances << "\t\t# >= 50%: " << opt + opt90 + opt80 + opt70 + opt60 + opt50 << endl;
-    cout << "#       <50% of LB: " << optLow << "\t\tPercentage: "<< static_cast<double>(optLow)/numInstances << endl;
+    cout << "#        opt of LB: " << opt << "\t\tPercentage: "<< (static_cast<double>(opt)/numInstances) * 100 << "\t\t# 100%: " << opt << endl;
+    cout << "# 90% - <opt of LB: " << opt90 << "\t\tPercentage: "<< (static_cast<double>(opt90)/numInstances) * 100 << "\t\t# >= 90%: " << opt + opt90 << endl;
+    cout << "# 80% - <90% of LB: " << opt80 << "\t\tPercentage: "<< (static_cast<double>(opt80)/numInstances) * 100 << "\t\t# >= 80%: " << opt + opt90 + opt80 << endl;
[…]

### 2018-03-05 paper/SCSPP/base.h

@@ -16,7 +16,7 @@ void resetVectors(int numScores, int numItem, vector<int> &allScores, vector<int
 
 void output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int optLow, int numInstances);
 
-void createInstance(int tau, int numScores, int numItem, int minWidth, int maxWidth, int minItemWidth, int maxItemWidth, double &totalItemWidth,
+void createInstance(int instance, int tau, int numScores, int numItem, int minWidth, int maxWidth, int minItemWidth, int maxItemWidth, double &totalItemWidth,
                     vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths);
 
 

### 2018-03-05 paper/SCSPP/main.cpp
added output for users choice of input, time output in seconds

@@ -7,6 +7,7 @@ mainexact.cpp
 #include <fstream>
 #include <cstring>
 #include <ctime>
+#include <iomanip>
 using namespace std;
 
 #include "base.h"
@@ -24,13 +25,19 @@ void programInfo(){
          << "       -w <int>    [Minimum item width. Default = 150.]\n"
          << "       -W <int>    [Maximum item width. Default = 1000.]\n"
          << "       -l <int>    [Length of strips. Default = 5000.]\n"
-         << "       -A          [Basic approximate FFD.]\n"
-         << "       -B          [Pack strips in turn, choosing smallest feasible score width.]\n"
-         << "       -C          [FFD combined with AHCA (exact algorithm). Default.]\n"
-         << "       -s <int>    [Random seed. Default = 1.]";
+         << "       -s <int>    [Random seed. Default = 1.]\n"
+         << "---------------\n"
+         << "HEURISTICS:\n"
+         << "       -p <int>    [Type of heuristic to be used.]\n"
+         << "                   [1 = Basic approximate FFD.]\n"
+         << "                   [2 = Pack strips in turn, choosing smallest feasible score width.]\n"
+         << "                   [3 = FFD combined with AHCA (exact algorithm).]\n"
+         << "---------------\n\n";
 }
 
-void argumentCheck(int tau, int minWidth, int maxWidth, int minItemWidth, int maxItemWidth, int maxStripWidth){
+void argumentCheck(int numInstances, int tau, int numItem, int minWidth, int maxWidth, int minItemWidth, int maxItemWidth,
+                   int maxStripWidth, int packType, int randomSeed){
+    cout << "SCSSP\n------------------------------\n";
     if(tau == 0){
         cout << "[ERROR]: Constraint value cannot be zero.\n";
         exit(1);
@@ -60,14 +67,37 @@ void argumentCheck(int tau, int minWidth, int maxWidth, int minItemWidth, int ma
         cout << "[ERROR]: Maximum item width is larger than length of strip.\n";
         exit(1);
     }
+    if(packType == 0){
+        cout << "[ERROR]: No heuristic specified.\n";
+        exit(1);
+    }
+
+    cout << std::left << setw(20) << "Number of instances:" << std::right << setw(10) << numInstances << endl
[…]

### 2018-03-05 paper/SCSPP/packing.cpp
changed type 2 multiple cycles in CP function, changed creation of altHam cycle

@@ -118,7 +118,7 @@ void basicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void pairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int maxStripWidth,
+void pairSmallest(int instance, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int maxStripWidth,
                   double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths,
                   vector<int> &stripSum, vector<vector<int> > &strip){
     int i, j;
@@ -141,6 +141,14 @@ void pairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int 
             }
         }
     }
+
+    /*if(instance == 1){
+        cout << "\nScore increase:\n";
+        for(i = 0; i < scoreIncrease.size(); ++i){
+            cout << scoreIncrease[i] << " ";
+        }
+        cout << endl << endl;
+    }*/
 
     j = 0;
     while (count < numScores){
@@ -188,14 +196,33 @@ void pairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int 
 
     int stripSize = strip.size();
     int LB = lowerBound(maxStripWidth, totalItemWidth);
+    //double c = static_cast<double>(LB) / stripSize;
 
-    optimality(opt, opt90, opt80, opt70,opt60, opt50, optLow, stripSize, LB);
+    /*if(instance == 2){
+        cout << "\nstrips:\n";
+        for(i = 0; i < strip.size(); ++i){
+            cout << "strip " << i << ":\t";
+            for(j = 0; j < strip[i].size(); ++j){
+                cout << strip[i][j] << " ";
+            }
+            cout << endl;
+        }
+        cout << endl;
+    }
+
+    if(instance < 5){
+        //cout << "INSTANCE = " << instance << endl;
+        cout << "LB = " << LB << "\tstripSize = " << stripSize << "\tOPT = " << c << endl;
+        cout << "END INSTANCE = " << instance << endl << endl;
+    }*/
+
+    optimality(opt, opt90, opt80, opt70, opt60, opt50, optLow, stripSize, LB);
 
 } //End pairSmallest
 
 
[…]

### 2018-03-05 paper/SCSPP/packing.h
added parameters to functions

@@ -22,15 +22,16 @@ void basicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void pairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores,
+void pairSmallest(int instance, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores,
                            int maxStripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
                            vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // FFD including AHCA, instead of attempting to place item on end of strip, run AHCA to find feasible solution.
-void FFDincAHCA(int &cp, int &na, int &type0, int &type1, int &type2, int &type3, int instance, int tau, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
-                        int maxStripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-                        vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void FFDincAHCA(int instance, int tau, int &opt, int &opt90, int &opt80, int &opt70,
+                int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth, int maxStripWidth, double totalItemWidth,
+                vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum,
+                vector<vector<int> > &strip);
 
 
 // Initializing instance for AHCA using items on the strip from FFDincAHCA and the item to be packed.
@@ -51,12 +52,12 @@ void BR(int &qstar, int matchSize, vector<vector<int> > adjMat, vector<int> &mat
 
 
 // Connecting Procedure (CP).
[…]

### 2018-03-05 PAPER/draft.tex
renamed folders

--- 2018-01-15 paper/paper.tex
@@
 
-\title{DRAFT}
+\title{Heuristics for the Score-Constrained Bin-Packing Problem}
 \author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
@@
 \begin{abstract}
-	This version finished: 13/01/2018
+
 \end{abstract}
@@
 \section{Introduction}
-\label{sec:intro}
-The one-dimensional bin packing problem (BPP) is a combinatorial optimisation problem that has been widely researched and discussed due to its ability to model a variety of real-life sitations.
+%\label{sec:intro}
+
+The one-dimensional bin-packing problem (BPP) is a combinatorial optimisation problem that has been widely researched and discussed due to its ability to model a variety of real-life situations.
 The BPP can be described as follows: given a set of $n$ items of varying sizes $w$, and a finite number of bins with equal capacity $c$, find the minimum number of bins required to contain all of the items.
-As shown by \cite{garey1979}, this problem is NP-hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP.
-Instead, heursitics can be used to find a near-optimal solution in a shorter amount of time.
-One example is the greedy heuristic known as first-fit, an online algorithm that places each item (in some arbitrary order) into the lowest-indexed bin.
-If there are no bins that can feasibly accommodate the item, the algorithm places the item into a new bin.
-A modified version of first-fit yields the well-known first-fit decreasing (FFD) algorithm (\citealp{eilon1971}), which initially sorts the items into non-decreasing order of size before allocating them into bins.
-As proven by \cite{dosa2007} \textcolor{RoyalBlue}{(proved bound is tight)}, the worst case for FFD is $\frac{11}{9}k + \frac{6}{9}$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ \textcolor{RoyalBlue}{(..if the solution has this many bins then it is optimal,} (\citealp{korf2002})).
+In 2004, \citeauthor{goulimis2004} brought to light an open-combinatorial problem related to the bin-packing problem.
+Corrugated boxes are formed in two stages: firstly, they are produced flat, then a device consisting of knives mounted of a bar creates scores along specific lines on the flat boxes.
+These scores allow the boxes to be folded in predetermined locations.
+The first stage of this process is a cutting stock problem, and involves finding a feasible pattern of the flat boxes that minimises the amount of waste.
+This problem has been researched extensively, and can be solved using delayed column-generation (\citealp{gilmore1961, gilmore1963}).
+However, the second strip of this process requires an additional constraint.
 
-In 2004, \citeauthor{goulimis2004} brought to light an open-combinatorial problem related to the bin-packing problem.
-Corrugated boxes are formed in two stages: firstly, they are produced flat, then a device consistsing of knives mounted on a bar creates ``scores'' along specific lines on the flat boxes.
-These scores allow the boxes to be folded in predetermined places.
-The first stage of this process involves finding a feasible pattern of the flat boxes that minimises the amount of waste, and has been researched extensively.
-\textcolor{Plum}{It is classically solved by delayed column-generation} (\citealp{gilmore1961, gilmore1963}).
-However, the second step of this process requires an additional constraint.
+The scoring knives are arranged in pairs, and cut along score lines from two adjacent boxes simultaneously.
+By design, the knives cannot be placed too close to one another, and so the distance between the scoring knives must exceed a fixed minimum value $\tau \in \mathbb{R}^{+}$ (around 70mm in industry).
+The problem therefore consists of finding a feasible arrangement of boxes such that the distance between two score lines is greater than or equal to $\tau$.
 
-The scoring knives, by design, cannot be placed too close together (around 70mm in industry), and as such have a ``minimum knife distance''.
-The problem then becomes a bin-packing problem with an additional constraint: find a feasible arrangement of boxes such that the sum of two adjacent score widths from different boxes is greater than or equal to the minimum knife distance.
-\textcolor{RoyalBlue}{We will call this constraint the minimum total score width constraint.}
+There exists a polynomial-time algorithm that is able to recognise whether a particular instance of this problem is feasible (\citealp{becker2010}).
+However, this algorithm does not consider the widths of each individual box, and only attempts to place the boxes onto a single strip.
+In industry, strips of material are provided in fixed lengths, and so given a large problem instance multiple strips may be required to feasibly accommodate all of the boxes without exceeding the capacity of the strips.
 
-\textcolor{OrangeRed}{Insert figure, two boxes annotated with score widths, score lines, box widths, knives mounted on bar showing minimum total score width constraint}
+This leads us to our main problem: given a collection of boxes of varying widths and a finite number of strips of fixed lengths, find the minimum number of strips required to feasibly pack all of the boxes such that the distance between two adjacent score lines on every pair of boxes is greater than or equal to some fixed value $\tau$ on all strips.
 
-\textcolor{RoyalBlue}{Figure showing two boxes with score widths and the scoring knives mounted on a bar.
-Since the sum of the two adjacent score widths from different boxes is greater than or equal to 70mm, the minimum total width constraint has been met - this is a feasible alignment of these two boxes}
+The remainder of this article will firstly, in Section \ref{sec:scbpp}, state the notation that will be used throughout, and formally define the problem.
+Section \ref{sec:ffdapprox} will introduce a modified first-fit decreasing heuristic and describe the changes made to consider the new constraint.
+In Section \ref{sec:ffdexact}, we will present a new algorithm which consists of the modified heuristic detailed in the previous section combine with a polynomial-time algorithm which will be used to find feasible sub-solutions.
+A comparison of the two heuristics and an analysis of the results will be provided in Section \ref{sec:comparison}, and finally Section \ref{sec:conclusion} concludes the paper and proposes some potential directions for future work.
 
-There exists a polynomial time algorithm that is able to recognise whether a particular instance of the problem is feasible or infeasible (\citealp{becker2010}) \textcolor{RoyalBlue}{(i.e.
-whether all boxes can be arranged in one line)}.
-However, the algorithm does not consider the lengths of each individual box, or the total length of the final arrangement of boxes.
-In industry, strips of materials are provided in fixed lengths, so, given a large number of boxes to pack, it may not be feasible to pack all of the boxes onto one strip.
+\section{Formulating the Score-Constrained Bin-Packing Problem}
+%\label{sec:scbpp}
 
-This leads us to our main problem, the score-constrained bin-packing problem: given a collection of boxes with varying widths and score widths on either side, and strips of a fixed length, find the minimum number of strips required to accommodate all of the boxes, such that the minimum total width constraint is met between all boxes on all strips.
+Despite the simplicity of the bin-packing problem statement, it has in fact been shown to be an NP-hard optimisation problem (\citealp{garey1979}).
+Thus, under the assumption that $P \neq NP$, there is no known algorithm that is able to find an optimal solution for every instance of the BPP in polynomial time.
+Instead, heuristics can be used to find near-optimal solutions in a shorter amount of time.
+One example is the greedy heuristic known as first-fit (FF), an online algorithm that places each item (in some arbitrary order) into the lowest-indexed bin such that the bin capacity is not exceeded.
+It has been shown that by arranging the items in decreasing order of size, a bin-packing heuristic will produce a solution that is closer to the optimal than if the items are arranged in any other order (\citealp{johnson1974fast}).
+Applying FF onto items sorted in this manner yields the well-known first-fit decreasing (FFD) heuristic.
 
-The remainder of this report will firstly, in Section \ref{sec:ffdapprox}, introduce the first-fit decreasing approximate algorithm and describe the modifications made to consider the minimum score width constraint.
-In Section \ref{sec:ffdexact}, we will present a new algorithm which consists of the modified first-fit decreasing algorithm detailed in the previous section combined with a polynomial-time algorithm which will be used to find feasible sub-solutions.
-A comparison of the two algorithms and an analysis of the results will be provided in Section \ref{sec:compresult}, and finally Section \ref{sec:conclusion} concludes the paper and proposes some potential directions for furture work.
+An optimal solution of an instance of the BPP is a solution that consists of the fewest number of bins, $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
 
-\section{Formulating the problem}
-We are given $n$ boxes that need to be packed onto strips.
-Each of these boxes have a positive width, and two score widths, one on either side of the box.
-Since these score widths are not necessarily equal, the boxes can be aligned in two ways: either in a ``regular'' alignment, where the smaller of the two score widths is on the left hand side of the box, or in a ``rotated'' alignment, where the box has been rotated by $180^{\circ}$ so that the larger score width is on the left-hand side of the box.
-Strips are packed left to right.
-We also have a finite number of strips of equal fixed lengths.
-Once a box has been placed onto a strip, the rightmost score on the strip is referred to as the ``free'' score.
-A box can only be placed onto a strip if it can fit onto the strip, i.e.
-the addition of the box to the strip doesn't exceed the length of the strip, and if the free score and one of the scores on the box meet the minimum total score width constraint, i.e.
-the sum of the free score width and one of the scores on the box is greater than or equal to the minimum total score width.
-Assume that no box has a width that is greater than the fixed length of the strips.
-\textcolor{RoyalBlue}{need to explain minimum total score width constraint with equation and example, used in the definition for SCBPP below.}
+\begin{equation*}
+	k \geq \ceil*{\frac{\sum_{i=1}^{n}w(i)}{c}}
+\end{equation*}
+
+where $n$ is the number of items to be packed, $w(i)$ the size of each item $i$, and $c$ the maximum capacity of the bins (\citealp{martello1990b}).
+In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ bins.
+More recently, \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight.
+Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time compelexity of FFD is $O(n\log n)$.
+
+---------------------------------
+
+Let each box $i$ of a set of $n$ boxes have a positive width $w(i)$.
+A ``score width'' is the distance between a score line and the nearest edge of the box.
+Each box $i$ has two score lines, $i_1, i_2$, with score widths $w(i_1), w(i_2)$ such that $w(i_1) \leq w(i_2)$.
+Since these score widths are not necessarily equal, each box can be aligned in two distinct ways: in a ``regular'' position, where the smaller score width $w(i_1)$ is on the left-hand side of the box, or in a ``rotated'' position, with the smaller score width on the right-hand side of the box.
+The boxes can be expressed using their score lines, where $\{i_1, i_2\}$ represents a regular position, and $\{i_2, i_1\}$ a rotated position.
+
+Given the minimum fixed value $\tau$, two boxes can only be placed next to one another if the adjacent score lines $\alpha$ and $\beta$ fulfil the \textit{minimum total score width constraint},
+
+\begin{equation*}
+	%\label{eqn:mtswc}
+	w(\alpha) + w(\beta) \geq \tau,
+\end{equation*}
+
+that is, the sum of the adjacent score widths must exceed the \textit{minimum total score width} $\tau$.
+
+There are a finite number of strips $S_j, j = 1, 2, ...$, with equal fixed lengths $l > 0$, that are to be packed from left to right.
+Assume that, for all boxes $i = 1, 2, ..., n$, $w(i) \leq l$, and $0 < w(i_1) \leq w(i_2) \leq \tau$.
+We are now able to present a formal definition of the problem.
 
 \begin{definition}
-	\label{defn:scbpp}
-	Given $n$ boxes of varying widths $w(i)$ and score widths $w(i_1), w(i_2)$, and a finite number of strips $S_j$ with equal fixed lengths $l$, the Score-Constrained Bin-Packing Problem (SCBPP) consists of finding the minimum number of strips required to pack all of the boxes such that the minimum total score width constraint is met between every pair of boxes.
-\textcolor{RoyalBlue}{or: such that for every pair of boxes the sum of the adjacent score widths is greater than or equal to some fixed value $t$.}
+%	\label{defn:scbpp}
+	Given $n$ boxes of varying widths $w(i)$ and score widths $w(i_1), w(i_2)$, $i = 1, 2, ..., n$, a finite number of strips $S_j$ with equal fixed lengths $l$, and a minimum total score width $\tau$, the Score-Constrained Bin-Packing Problem (SCBPP) consists of finding the minimum number of strips required to pack the boxes such that the minimum total score width constraint is met between every pair of adjacent boxes.
 \end{definition}
 
-\section{FFD Using Approximate Algorithm}
-\label{sec:ffdapprox}
+\section{FFD Approx}
+%\label{sec:ffdapprox}
+
+The first heuristic to be dicussed is a first-fit decreasing heuristic, modified to account for the minimum total score width constraint.
+The strips are initially empty, thus we define a residual length $r(j)$ for each strip $S_j, j = 1, 2, ...$.
+The residual lengths are set equal to the strip lengths $l$, and reduce as boxes are added to the strips.
+Each strip $S_j$ that is packed with at least one box has a ``free'' score $f_j$, the score on the right-hand side of the last box on the strip.
+A box can only be placed onto $S_j$ if the box can feasibly fit onto the strip, i.e.
+the width of th box is less than or equal to the residual length of the strip, and if $f_j$ and the left-hand socre of the box meet the minimum total score width constraint.
+Since each box has two position, regular and rotated, the heuristic checks if the constraint is met in both positions, favouring the regular position.
+If a box is only able to fit onto a strip that is empty, then the box is placed onto the strip in a regular position.
 
@@
 	\caption{\textcolor{OliveGreen}{Approximate First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
-	\label{alg:ffdapprox}
+%	\label{alg:ffdapprox}
 	\begin{algorithmic}[1]
-	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, minimum total score width $t$, and a set $\mathcal{S} = \emptyset$.
+	\Require A list of boxes $\{i_1, i_2\}$ with widths $w(i), i = 1, 2, ..., n$, strips $S_j = \emptyset$ of fixed lengths $l$ and residual lengths $r(j) = l$, $j = 1, 2, ...,n$, minimum total score width $\tau$, and a set $\mathcal{S} = \emptyset$.
 	\Ensure A feasible packing of all boxes onto a set of strips $\mathcal{S}$.
@@
 			\ElsIf{$S_j \neq \emptyset \land w(i) \leq r(j)$}
-				\If{$w(f_j) + w(i_1) \geq t$}
+				\If{$w(f_j) + w(i_1) \geq \tau$}
 					\State $S_j \gets S_j \cup \{i_1, i_2\}$
@@
 					\Break
-				\ElsIf{$w(f_j) + w(i_2) \geq t$}
+				\ElsIf{$w(f_j) + w(i_2) \geq \tau$}
 					\State $S_j \gets S_j \cup \{i_2, i_1\}$
@@
 
-\textbf{\textcolor{Rhodamine}{DESCRIPTION OF FFDAPPROX}}
-
 Initially, the algorithm arranges the boxes in non-increasing order of widths, breaking ties by choosing the box with the smallest score width.
@@
 
-\section{FFD Using Exact Algorithm}
-\label{sec:ffdexact}
-Introduction
+\section{FFD Exact}
+%\label{sec:ffdexact}
 
-Explanation: Initialise
+Insert introduction to FFD Exact.
 
-Let each box be represented by two vertices on a graph $G$, one vertex for each side of the box.
-We also introduce a ``dummy'' box that has two ``dominating scores'' with widths equal to the minimum total score width, $t$.
-This dummy box will be discarded at the end of the algorithm, and will not be included in the final feasible alignment.
-We now have $n$ boxes including the dummy box, and so $G$ will have $2n$ vertices.
+Let each box be represented by two vertices on a graph $G$, one vertex for each side of a box.
+A ``dummy'' box is introduced, with two ``dominating'' score widths equal to the minimum total score width $\tau$.
+This dummy box will be discarded at the end of the algorihtm, and will not be included in the final solution.
+Thus, there are $n$ boxes, including the dummy box, and so $G$ will consist of $2n$ vertices.
 
-We will refer two two vertices that represent either side of the same box as ``partners''.
-The boxes cannot be altered in any way, and so partners must be adjacent to one another.
-We therefore create a set of edges, $P$, consisting of edges between partners on $G$.
-\textcolor{RoyalBlue}{weighted edges $P$}.
+Two vertices $v_i, v_j$ $(i \neq j)$ that represent either side of the same box are referred to as ``partners''.
+The boxes cannot be altered in any way, and so partners must always be adjacent to one another.
+Therefore, a set $P$ is created, consisting of edges between partners on $G$.
+These edges are weighted, with values corresponding to the width of the box that the partners are associated with.
 
-Each vertex $v_i$ for $i = 1, 2, ..., 2n$ has a positive value $w(v)$ corresponding to the score width it represents.
-There is an edge between two vertices $u$ and $v$ on $G$ if and only if the vertices fulfil the \textit{minimum total score width constraint},
+Each vertex $v_i, i = 1, 2, ..., 2n$ has a postive value $w(v_i)$ corresponding to the score width it represents.
+There is an edge between two vertices $v_i, v_j$ $(i \neq j)$ on $G$ if and only if the vertices fulfil the minimum total score width constraint,
 
 \begin{equation*}
-	\label{eqn:mtswcg}
-	w(u) + w(v) \geq t,
+	%\label{eqn:mtswcg}
+	w(v_i) + w(v_j) \geq \tau,
 \end{equation*}
 
-and $u$ and $v$ are not partners, i.e.
-$\{u, v\} \notin P$.
-The vertices $u$ and $v$ are referred to as \textcolor{OliveGreen}{``matched''}, and so their corresponding score widths can be feasibly aligned next to one another.
-We now have another set of edges, $Q$, consisting of edges between \textcolor{OliveGreen}{``matched''} vertices.
+and $v_i, v_j$ are not partners, i.e.
+$\{v_i, v_j\} \notin P$.
+The vertices $v_i, v_j$ are then referred to as ``matched'', and so their corresponding score widths can be feasibly placed next to one another.
+Hence there is another set of edges $Q$, which contains edges between matched vertices.
 
-In order to find a feasible alignment of the boxes, we must find an alternating Hamiltonian cycle on $G$. \textcolor{RoyalBlue}{turns into path when we remove dummy box.}
+Thus, $G(V, P\cup Q)$ is an undirected graph with vertex set $V = \{v_1, v_2, ..., v_{2n}\}$, and two edge sets $P$ and $Q$, with $P \cap Q = \emptyset$.
+In order to find a feasible alignment of the boxes, $G$ must contain an alternating Hamiltonian cycle.
 
 \begin{definition}
-	\label{defn:althamcycle}
+	%\label{defn:althamcycle}
 	Let $G(V, P\cup Q)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $Q$.
 $G$ has an \textit{alternating Hamiltonian cycle} if there exists a Hamiltonian cycle on $G$ such that the successive edges alternate between sets $P$ and $Q$.
-For example, if vertex $v_k$ in the Hamiltonian cycle is adjacent to vertex $v_{k-1}$ via an edge from $P$, then $v_k$ must be adjacent to vertex $v_{k+1}$ via an edge from $Q$, or vice versa.
+For example, if vertex $v_i$ in the Hamiltonian cycle is adjacent to vertex $v_{i-1}$ via an edge from $P$, then $v_i$ must be adjacent to vertex $v_{i+1}$ via an edge from $Q$, or vice versa.
 \end{definition}
 
-\textcolor{OrangeRed}{Figure of graph $G$ with boxes, figure of aligned boxes with alternating Hamiltonian path underneath.}
+If $G$ does contain an alternating Hamiltonian cycle, the algorithm simply removes the dominating vertices and any associated edges to obtain an alternating Hamiltonian path, which portrays the order of the score widths that gives rise to a feasible alignment of the boxes.
+Thus, the aim of the algorithm is to find an alternating Hamiltonian cycle on $G$, if one exists.
 
-\textcolor{RoyalBlue}{we now need to find a way of producing the alternating hamiltonian cycle on the graph $G$, if one exists.}
+The next step of the algorithm attemps to obtain a set of matching edges $M \subset Q$ of cardinality $n$, such that the edges from $M$ and $P$ form an alternating Hamiltonain cycle as described in Definition \ref{defn:althamcycle}.
+There is a modified matching algorithm (\citealp{mahadev1994, becker2010}) that is able to choose a suitable set of edges for $M$.
 
-MTGMA/MIS
+Initially, the vertices are sorted in order of non-decreasing values $w(v_i), i = 1,2, .., 2n$, with ties broken arbitrarily.
+For each vertex in the list, find the largest adjacent vertex in $Q$ that has not yet been added to the matching set $M$.
+This pair of vertices is then added to $M$, and the algorithm proceeds on to the next vertex in the sorted list.
+This process continues until all of the vertices have been assessed.
 
-We need to obtain a set of matching edges $M \subset Q$ of cardinality $n$, such that the matching edges from $M$ and the edges from $P$ form an alternating Hamiltonain cycle as described in Definition \ref{defn:althamcycle}.
-We use a modified matching algorithm (\citealp{mahadev1994, becker2010}) that produces a suitable set of matching edges $M$.
+If a vertex $v_i$ is not adjacent to any other vertex except its partner, the previous vertex can be rematched, provided $v_i$ is not the first vertex in the sorted list, the previous vertex $v_{i-1}$ is matched under $M$ (i.e.
+$v_{i-1} \in M$), and $v_{i-1}$ is adajcent to $v_i$'s partner.
+Then, $v_{i-1}$ is matched with $v_i$'s partner, and $v_i$ is matched with $v_{i-1}$'s previous match under $M$.
+It is guaranteed that this algorithm will produce a maximum cardinality matching $M \subset Q$ (\citealp{becker2010}).
 
-Initially, the vertices are sorted in order of non-decreasing values, and ties are broken arbitrarily.
-Starting from the smallest vertex, find the largest adjacent vertex (under $Q$?
-in the set $Q$?
-)that is not the current vertex's partner, and that has not yet been matched.
-Add this pair of vertices to the set $M$ that keeps a record of the matching edges, and proceed to the next vertex in the list.
-Continue until all vertices have been assessed.
+If $|M| < n$, there are not enough matching edges to form an alternating Hamiltonian cycle with the edges in $P$, and therefore there is no feasible arrangement of the boxes such that the minimum total score width constraint is not violated.
+However, if $|M| = n$, then the graph $G(V, P \cup M)$ is a 2-regular graph where each vertex is adjacent to one vertex (its partner) via an edge in $P$, and another vertex (its match) via an edge in $M$.
+If $G$ consists of one alternating Hamiltonian cycle, the dominating vertices are removed to obtain a feasible alignment of the boxes.
+If there are two or more cycles on $G(V, P \cup M)$, a solution to the problem has not yet been found.
+These cycles need to be combined into one single alternating Hamiltonian cycle.
 
-If a vertex $v_i$ is not adjacent to any other vertex except its partner, we can rematch previous vertices to provide $v_i$ with a feasible match, provided $v_i$ is not the first vertex in the sorted list, the previous vertex $v_{i-1}$ has a match (i.e.
-$v_{i-1} \in M$), and $v_{i-1}$ is adajcent to $v_i$'s partner.
-We then simply match $v_{i-1}$ with $v_i$'s partner, and match $v_i$ with $v_{i-1}$'s previous match.
-\textcolor{RoyalBlue}{max cardinality.}
+To merge the multiple cycles on $G$, we need to connect vertices from different cycles by removing some matching edges and adding new edges from $Q$.
+The following algorithm finds the matching edges on the graph $G(V, P \cup M)$ that allow the cycles to be combined.
 
-If $|M| < n$, then there are not enough matching edges to form an alternating Hamiltonian cycle with the edges in $P$, and therefore there is no feasible arrangement of the boxes such that the minimum total score width constraint is not violated.
-However, if $|M| = n$, then the graph $G(V, P \cup M)$ is a 2-regular graph, where each vertex is adjacent to one vertex via an edge in $P$, (i.e.
-its partner), and another vertex via an edge in $M$ (i.e.
-its match).
-If $G$ consists of one alternating Hamiltonian cycle, then we simply remove the dominating vertices to obtain a feasible alignment of the boxes/feasible solution.
-If there are more than two cycles on $G$, we need to combine them into one alternating Hamiltonian cycle.
-\textcolor{RoyalBlue}{notation number of cycles.}
-
-\textcolor{OrangeRed}{figure of graph $G$ showing edges between partners ($P$), edges in the set $M$, and faint lines to represent the rest of the edges $Q$.}
-
-FCA/Patch
-
-In order to combine multiple cycles into one, we need to replace some matching edges with feasible edges from the set $Q$ that connect vertices from different cycles.
-\textcolor{RoyalBlue}{The following algorithm is used to find these feasible edges}.
-
-The algorithm initially creates a list of all matching edges in $M$, sorted in order of non-decreasing vertex values \textcolor{RoyalBlue}{(i.e.
-the edge which connects the smallest vertex to its match is first in the list) (do not include edges from partner swap)}.
-Starting from the first edge in the list, the algorithm searches through the list of edges until it finds an edge whose smaller vertex is adjacent via an edge in $Q$ to the larger vertex of the succeeding edge in the list, such that both edges are from different cycles on the graph $G$.
-If such a pair of edges has been found, the algorithm adds the first edge of the pair to a set $C_k$.
+The algorithm initially creates a list of all matching edges in $M$, sorted in order of non-decreasing vertex values.
+Starting from the first edge, the algorithm searches through the list of edges until it finds an edge whose smaller vertex is adjacent via an edge in $Q$ to the larger vertex of the succeeding edge in the list, such that both edges are from different cycles on the graph $G$.
+If such a pair of edges is found, the first edge of the pair is added to a set $C_k$.
 The algorithm then continues to add all succeeding edges to $C_k$, provided that the smaller vertex of the current edge is adjacent to the larger vertex of the succeeding edge via an edge in $Q$, the succeeding edge does not belong to a cycle that is already represented by an edge in $C_k$, and the algorithm has not reached the final edge in the list.
 Once there are no more valid edges to add to $C_k$, the algorithm proceeds to the next edge in the list, and checks whether this edge is suitable for beginning a new set $C_{k+1}$.
-If the algorithm has already reached the penultimate or final edge in the list, the algorithm terminates.
+If the penultimate or final edge in the list is reached, the algorithm terminates.
 
@@
 	\caption{\textcolor{OliveGreen}{Exact First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
-	\label{alg:ffdexact}
+%	\label{alg:ffdexact}
 	\begin{algorithmic}[1]
@@
 				\State \textcolor{RoyalBlue}{Run} \textcolor{OrangeRed}{``MBAHRA''} \textcolor{RoyalBlue}{on boxes in $S_j$ and box $i$}
-				%\Return \textcolor{OrangeRed}{found}
 				\If{feasible alignment found}
-				%\If{found}
 					\State $S_j \gets$ \textcolor{RoyalBlue}{new alignment found by} \textcolor{OrangeRed}{``MBAHRA''}
@@
 \end{algorithm}
-
-\textbf{\textcolor{ProcessBlue}{DESCRIPTION OF FFDEXACT}}
 
@@
 
-\section{Comparison and Results}
-\label{sec:compresult}
+\section{Comparison and results}
+%\label{sec:comparison}
 
 \section{Conclusion}
-\label{sec:conclusion}
-
-\section{References}
-\cite{becker2010}, \cite{becker2015}, \cite{coffman1978}, \cite{dosa2007}, \cite{eilon1971}, \cite{garey1979}, \cite{gilmore1961}, \cite{gilmore1963}, \cite{goulimis2004}, \cite{johnson1974}, \cite{karp1972}, \cite{korf2002}, \cite{lewis2009}, \cite{lewis2017}, \cite{lewis2011}, \cite{mahadev1994}, \cite{mahadev1995}, \cite{martello1990a}, \cite{martello1990b}
+%\label{sec:conclusion}
 
@@
 	\item Exact methods - \cite{martello1990a} branch and bound based exact algorithm MTP, Carvalho 1999 column generation and branch-and-bound, \cite{eilon1971} depth-first search enumerative algorithm, only solve small size problem instances.
-	\item \cite{garey1979} \textcolor{RoyalBlue}{NP-Hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP.}
-	\item \textcolor{RoyalBlue}{Instead, heuristics can be used to find a near optimal solution in a shorter amount of time}.
+	\item \cite{garey1979} NP-Hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP.
+	\item Instead, heuristics can be used to find a near optimal solution in a shorter amount of time.
 	\item discuss heuristics.
@@
 	\item The minimum total score width constraint must be fulfilled in order for the scoring knives to be able to score the boxes correctly.
-	\item The \textit{minimum total score width} is denoted by $t, t > 0$ \textcolor{RoyalBlue}{usually 70mm in industry}.
-\textcolor{RoyalBlue}{The \textit{minimum total score width constraint} is $w(u_p) + w(v_q) \geq t$, $u \neq v, p, q = 1 or 2$.}
+	\item The \textit{minimum total score width} is denoted by $\tau, \tau > 0$ (usually 70mm in industry).
 	\item Strips packed from left to right.
@@
 
-Comparison/Results
-
-Conclusion
+\section{References}
+\cite{becker2010}, \cite{becker2015}, \cite{coffman1978}, \cite{dosa2007}, \cite{eilon1971}, \cite{garey1979}, \cite{gilmore1961}, \cite{gilmore1963}, \cite{goulimis2004}, \cite{johnson1974worst}, \cite{johnson1974fast}, \cite{hung1978}, \cite{garey1972}, \cite{johnson1973}, \cite{karp1972}, \cite{korf2002}, \cite{lewis2009}, \cite{lewis2017}, \cite{lewis2011}, \cite{mahadev1994}, \cite{mahadev1995}, \cite{martello1990a}, \cite{martello1990b}
 

### 2018-03-05 PAPER/main.tex
renamed folders

--- 2018-02-08 paper/main.tex
@@
 \begin{proof}
-	To be completed. \qed
+	Let $\mathcal{A} = \{v_1, v_2, ..., v_{2n+1}, v_{2n+2}\}$ be an alternating Hamiltonian cycle on $G$, where $v_{2n+1}$ and $v_{2n+2}$ are the dominating vertices.
+By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $P$.
+Thus, there exists a set of $n+1$ edges from $E$ that, together with the edges in $P$, form the alternating Hamiltonian cycle.
+Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $P$.
+The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple.
+\textcolor{OrangeRed}{edges E vicinal sum constraint equation 2}.
+\qed
 \end{proof}

### 2018-03-05 PAPER/notespaper.tex
renamed folders

\documentclass{llncs}

\input{includes/preamble.tex}

\title{Notes for IWOCA Paper}
\author{Asyl L. Hawa}

\begin{document}
\maketitle

\begin{abstract}
	Abstract
\end{abstract}

\section{Introduction}

\begin{itemize}
	\item \textcolor{red}{original BPP}
	\item Definition of problem: packing items of different sizes into a finite number of bins/containers that have a fixed size such that the number of bins/containers required is minimised.
	\item Combinatorial NP-hard problem (computational complexity) Gary and Johnson 1979
	\item NP-Complete (decision problem)
	\item Heuristics
	\item FF and FFD
	\item FF can produce a feasible solution quickly, but the solution may not be optimal O(nln n), n is the number of items that need to be packed.
	\item ``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki) Rhyd Lewis 2009
	\item ``bound for FFD is tight'' (wiki)
	\item 2015 Hoberg and Rothvoss proposed and proofed a new complexity for the algorithm FF (wiki)
	\item Exact algorithms, Martello and Toth (MTP), Bin Completion algorithm Korf 2002, Schreiber and Korf (2013) (wiki)
	\item \textcolor{blue}{Although there are exact solutions available for the BPP} (martello knapsack MTP 1989 (1990b) ``is based on a first-fit decreasing'' branching strategy and is the best existing algorithm for optimal packing (KOrf2002)'', hung and brown 1978 ``a branch-and-bound algorithm'' paper title:``an algorithm for a class of loading problems'', eilon christofides 1971 ``a depth-first numerative algorithm'' paper title: ``the loadings problem'', schreiber and korf 2002 bin completion algorithm) \textcolor{blue}{they are only able to find solutions to problems that have a small input size.}
	\item ``Hence, exact solution techniques are bound to work well for small to medium sized problem instances only, and real world sized problems including up to thousands of items have to be solved heuristically.''

	\item \textcolor{red}{Score constraints}	
	\item Goulimis 2004, score constraints for packing and folding
	\item Explain knives for scoring
	\item Picture of box with score widths, score lines
	\item All boxes have same height, different widths, different score widths
	\item ``Threshold'' ``minimum knife distance'' ``minimum score separation constraint'' ``minimum score line distance'', ``minimum score line constraint'' ``minimum total width constraint'' 70mm industry
	\item Becker alg exact, P, but without packing, all boxes on one strip
	\item \textcolor{red}{Multiple strips}
	\item Material may not come in long sizes, instead short sizes of fixed length
	\item find optimal arrangement of boxes on strips while mimimising waste and number of strips required

	\item Formal statement of BPP with score constraint called the Score Constrained Bin packing problem: given ...

	\item layout of paper
\end{itemize}

\begin{enumerate}
	\item Goulimis (2004)
	\item boxes are scored in specfici places to make folding easier 
	\item only consider outermost scores, although box may have many 
	\item machine explanation, scoring knives cannot be placed too close together
	\item therefore we have a score constraint/minimum knife distance
	\item strips of material of a fixed length
	\item minimise waste whilst adhering to the score constraints
	\item feasible arrangement of boxes
	\item boxes have same heights, different widths
	\item therefore have a strip packing/bpp with an additional constraint
	\item explain rest of paper
\end{enumerate}

\begin{itemize}
	\item FF if online, FFD is offline
	\item FF and FFD can produce a feasible solution quickly, but the solution may not be optimal O(nln n), where n is the number of items that need to be packed
	\item Exact algorithms, Martello and Toth (MTP), Bin Completion algorithm Korf 2002, Schreiber and Korf (2013) (wiki)
	\item \textcolor{RoyalBlue}{Although there are exact solutions available for the BPP} (martello knapsack MTP 1989 (1990b) \textcolor{Plum}{``is based on a first-fit decreasing'' branching strategy and is the best existing algorithm for optimal packing (Korf2002)'', hung and brown 1978 ``a branch-and-bound algorithm'' paper title:``an algorithm for a class of loading problems'', eilon christofides 1971 ``a depth-first numerative algorithm'' paper title: ``the loadings problem'', schreiber and korf 2002 bin completion algorithm)} \textcolor{RoyalBlue}{they are only able to find solutions to problems that have a small input size.}
	\item \textcolor{Plum}{``Hence, exact solution techniques are bound to work well for small to medium sized problem instances only, and real world sized problems including up to thousands of items have to be solved heuristically.''}
	\item \textcolor{Plum}{``There exists at least one ordering of items that allows FF to produce an optimal solution'' (wiki) Rhyd Lewis 2009}
	\item All boxes have same height, different widths, different score widths
	\item Recognition algorithm Becker
	\item \textcolor{RoyalBlue}{Formal statement of BPP with score constraint called the Score Constrained Bin packing problem (SCBPP): given}
	\item dicuss other paper/articles with this problem, i.e. rhyd 2017	
\end{itemize}

\begin{itemize}
	\item $n$ boxes need to be packed, all have same height but different widths $w(i)$.
	\item Each box $i$ has two scores $i_1, i_2$, one on either side of the box.
	\item Each of these scores has a width $w(i_1) \leq w(i_2)$.
	\item Score widths not necessarily equal, therefore box has two different positions.
	\item Regular position, smaller score on LHS, denoted $\{i_1, i_2\}$.
	\item Rotated position, smaller score on RHS, denoted $\{i_2, i_1\}$ (rotated $180^{\circ}$).
	\item Boxes will be placed side by side.
	\item The sum of two adjacent score widths must fulfil the minimum total score width constraint ... $t$ is the minimum total score width.
	\item The minimum total score width constraint must be fulfilled in order for the scoring knives to be able to score the boxes correctly.
	\item There are a finite number of strips $S_j$, with equal fixed lengths $l$.
	\item Need to pack the boxes onto the strips so mtswc is met and least number of strips used.
	\item $l > 0, w(i) > 0, w(i) \leq l$
\end{itemize}

Notation
\begin{itemize}
	\item $n$ boxes, $i = 1, 2, ..., n$.
	\item Each box $i$ has a total width $w(i)$.
	\item Each box $i$ has two scores, $i_1$ (the smaller score), and $i_2$ (the larger score), and widths $w(i_1), w(i_2)$, such that $w(i_1) \leq w(i_2)$.
	\item $\{i_1, i_2\}$ represents ``regular'' box $i$: $i_1$ on LHS of box.
	\item $\{i_2, i_1\}$ represents ``rotated'' box $i$: $i_2$ on LHS of box (box rotated by $180^{\circ}$).
	\item All box widths $w(i) > 0$ and all score widths $w(i_1), w(i_2) > 0$ $\forall$ $i = 1, 2, ..., n$.
	\item Finite number of strips $S_j$, $j = 1, 2, ...$.
	\item All strips $S_j$ have equal fixed length $l > 0$ $\forall$ $j = 1, 2, ...$.
	\item All strips $S_j$ have a residual length $r(j)$, initially $r(j) = l$ $\forall$ $j = 1,2, ...$, which reduces as boxes are added to each strip.
	\item Assumption: all box widths $w(i) \leq l, i = 1, 2, ..., n$
	\item Initially, $S_j = \emptyset$ $\forall$ $j = 1, 2, ...$.
	\item For all strips $S_j \neq \emptyset$, the score on the right hand side of the last box in the strip is called the ``free score'', denoted $f_j$, with width $w(f_j)$.
	\item The \textit{minimum total score width} is denoted by $t, t > 0$ \textcolor{RoyalBlue}{usually 70mm in industry}. \textcolor{RoyalBlue}{The \textit{minimum total score width constraint} is $w(u_p) + w(v_q) \geq t$, $u \neq v, p, q = 1 or 2$.}
	\item Strips packed from left to right.

	\item -------------------------

	\item Notation for Exact algorithm
	\item $n$ boxes including dummy box.
	\item $2n$ vertices including dominating vertices.
	\item Graph $G$ is an undirected graph with $2n$ vertices $v_i, i = 1, 2, ...,2n$.
	\item Vertices are weighted, $w(v_i)$.
	\item Vertices that represent either side of same box referred to as ``partners''
	\item $P$ contains the set of edges between partners, fixed, $|P| = n$.
	\item Edges in $P$ are weighted, corresponding to box width.
	\item $Q$ contains the set of edges between vertices that meet the minimum total score width constraint, excluding partners (these edges are not weighted).
	\item $G(V, P \cup Q)$ - each edge on $G$ is either in $P$ or $Q$, not both.
	\item $t$ still represents the minimum total score width.
	\item $M$ is the set of matching edges, $M \subset Q$, edges chosen using the matching algorithm (need $|M| = n$).
	\item number of cycles on $G$ after MTGMA =  ?
	\item $C_k$: sets of edges for connecting cycles.

\end{itemize}

\section{FFD with approximate heuristic}
\begin{enumerate}
	\item background on FF/FFD
	\item explain how FFD operates without score constraints (simple)
	\item complexity/lower bound
	\item explain FFD with score constraint (algorithm)
	\item pros and cons: speed, however there may be a solution that exists that cannot be found due to boxes being fixed in place
\end{enumerate}

\begin{itemize}
	\item discuss heuristics
	\item \textcolor{Plum}{``Heuristics are approximate solution techniques that typically provide solutions in the least amount of time to the detriment of the solutions quality''}
	\item \textcolor{Plum}{``Exact methods find a best possible packing, but are slow and may be unable to provide solutions to large or reastically sized problem instances within reasonable time''}
	\item \textcolor{Plum}{``Consider a set of $n$ items. In the context of bin packing problems, heuristics consider these items one-by-one and attempt to pack them into a bin so as to achieve a near-optimal solution without the guarantee that a solution is optimal.''}
	\item \textcolor{Plum}{``Exact packing methods are often called deterministic methods and are guarantees to find an optimal solution to a problem (given sufficient time and a feasible region) while heuristics attempt to find optimal solutions, but are not guaranteed to do so.''}
	\item \textcolor{Plum}{``Exact methods may often be too slow to solve large problem instances, but may typically be used to solve smaller ones.''}
	\item \textcolor{Plum}{``Packing heuristics follow a fixed set of rules to pack items in such a manner as to find good, feasible (but not necessarily optimal) solutions to the bin packing problem within as short a time span as possible.''}
	\item offline algorithm, whole problem data is provided/required at the start.
	\item online, doesn't consider future events/items, data is processed in the order that it is input into the algorithm, entire input is not required to be available from the start
	\item \textcolor{Plum}{``first-fit decreasing (FFD) algorithm for one-dimensional bin packing by johnson et al (1974, worst-case performance bounds for simple one-dimensional packing algorithms)''}
	\item FF is online, FFD is offline
	\item FF and FFD can produce a feasible solution quickly, but the solution may not be optimal, O(nln n), where n is the number of items that need to be packed
	\item \textcolor{Plum}{who stated that ffd is O(nlog n)?}
	\item \textcolor{Plum}{Coffman et al 1984 heuristics survey}
	\item \textcolor{RoyalBlue}{Describe how the ffdapprox algorithm works}
	\item \textcolor{OrangeRed}{figure of packed boxes on strips}
	\item previously placed boxes are fixed, cannot be rearranged
	\item complexity of modified FFD for SCBPP
	\item background information on FFD
	\item works in the same way as FFD, but with an additional step - each box must meet the minimum total score width constraint, so if a box fits onto a strip, we start by checking if the smallest of the two score widths on the box, and the free score width on the end of the current strip, meet the mtswc. If not, then we rotate the box $180^{\circ}$ and check again if the mtswc is met. If neither score width on the box meets the mtswc with the free score width, then we move onto the next strip and try again.
	\item pack from left to right
	\item boxes can be aligned in two ways, with smaller score on LHS, or rotated $180^{\circ}$ so the smaller score is on the LHS
	\item Karp complexity
	\item \textcolor{OrangeRed}{figure of one packed strip indicating free score end $f_j$}
	\item pros and cons: speed, however there may be a solution that exists that cannot be found due to boxes being fixed in place
	\item In this algorithm, the boxes are sorted by non-increasing widths prior to packing.
	\item If a box does not fit onto any existing strips, a new strip is initialised.
	\item Initially, pack the largest (widest/box with the largest width/first box in the sorted list of boxes) box into the first strip.
	\item \textcolor{Plum}{``Simchi-Levi (1994, ``New worst-case results for the bpp'') has shown that the FFD and the BFD heuristics have an absolute performance ratio of 1.5, and that this value is the best possible for the BPP, unless $P = NP$.''}
	\item We use $\{i_1, i_2\}$ or $\{i_2, i_1\}$ to represent the box, rather than just $i$, because the feasibility of the alignment of boxes on the strip depends on which way the box is placed, regularly or rotated.
\end{itemize}

\section{FFD with exact algorithm}
\begin{enumerate}
	\item extension of the above, however we include an algorithm that can find a feasible alignment of boxes with score constraints if one exists
	\item if a box can fit onto a strip, instead of attempting to place on the end, we apply this algorithm
	\item therefore unlike the heuristic above, boxes are not fixed in place, all boxes can be reordered
	\item then go on to explain mbahra + output of solution
	\item pros and cons? polynomial time, however it means that it cannot be done continuously, i.e. the heuristic can be applied during scoring, but with the exact alg, a full solution must be found before any scoring can occur, as boxes can be moved around
\end{enumerate}

Introduction
\begin{itemize}
	\item This alg will be combining a well known heuristic with an exact algorithm to find a feasible solution to the SCBPP
	\item Becker 2010 recognicity algorithm in polynomial time
	\item doesn't take into account individual widths of boxes
	\item only one strip/align all boxes into one row
	\item in industry, strips have a finite length
	\item algorithm also doesn't output a full solution, only whether there exists a feasible solution or not
	\item ffd but including an algorithm that can find a feasible aligment of boxes with score constraints if one exists
	\item unlike ffd, where boxes are placed onto the end of each strip, the boxes are not fixed in place, all boxes can be reordered.
	\item Can find a solution for a set of boxes on a strip when it may not have been possible to find one in ffdapprox due to only the last box being checked.
	\item try to find a hamiltonian path 
	\item complexity $O(n^2), O(n)$ to construct a solution
	\item if the algorithm cannot find a feasible alignment of the boxes including the current box, move onto next strip and try again.
\end{itemize}

\begin{definition}
	% Alternating Hamiltonian Path/cycle
	Let $G(V,P\cup E)$ be an undirected graph, where $P \cap E = \emptyset$. Then $G$ has an alternating Hamiltonian path (or cycle) if there exists a Hamiltonian path (or cycle) on $G$ such that the successive edges are members of different edge sets, *i.e. if vertex $v_k$ is adjacent to vertex $v_{k-1}$ via an edge from $P$, then $v_k$ must be adjacent to vertex $v_{k+1}$ via an edge from $E$, or vice versa. $G$ is said to be alternating Hamiltonian if and only if there exists an alternating Hamiltonian cycle on $G$. (OR *i.e. if $\{v_{k-1}, v_k\} \in P$, then $\{v_k, v_{k+1}\} \in E$, or vice versa.)
\end{definition}

\subsection{Intro}
\begin{enumerate}
	\item Notation
	\item Creating two sets of edges
	\item Alternating Hamiltonian Path/cycle
\end{enumerate}
\begin{itemize}
	\item $n$ boxes, each box has two score lines, one on each side (mates)
	\item Score width - distance between edge of box and score line
	\item scores come in pairs
	\item let each box be represented by two vertices, one vertex for each score
	\item vertex weight equivalent to score width (mm)
	\item if two scores are part of the same box, join corresponding vertices together with an edge
	\item call this set of edges $P$, where $|P| = n$.
	\item edges in $P$ are weighted, equivalent to box width
	\item threshold graph: if sum of two vertices $\geq$ threshold, and vertices are not connected via an edge from $P$, i.e. $\{u, v\} \notin P$, then join vertices together via an edge
	\item call this set of edges $T$
	\item two sets of edges, $P$ and $T$
	\item add dominating vertices
	\item we want to find an alternating hamiltonian path, edges alternating between set $P$ and set $T$.
	\item -----------------------
	\item each box has same height, varying width (introduction?)
	\item vertices have values corresponding to the score width
	\item two vertices that represent either side of the same box are called ``mates''
	\item add dominating vertices that are mates with value = mkd, removed at the end
	\item so graph has $2n + 2$ vertices
	\item mates must be adjacent to one another, so we have a set of edges $P$ that consists of edges between mates
	\item each of these edges are weighted, value corresponds to boxwidth
	\item seconds set of edges $T$: if the sum of two score widths from different boxes is greater than or equal to the mkd, the corresponding vertices will be connected with an edge 
	\item called these matched
	\item or if the sum of two vertices that are not adjacent via an edge from $P$ is $\geq$ mkd, connect via an edge
	\item picture threshold graph colours or dots?	
\end{itemize}

--------------------------------\\
Let each box be represented by two vertices on a graph $G$, one vertex for each side of the box. Each vertex is assigned a value corresponding to the width of the score it represents. We refer to two vertices that represent either side of the same box as ``mates''. The boxes cannot be altered in anyway, and so vertices that are mates must be adjacent to one another. Thus, we have a set of edges $P$ that consists of edges between mates.

As described in the introduction, let $\tau \in \mathbb{R}_{+}$ be the minimum scoring distance. If the sum of the values of two vertices $\{u, v\}$ is greater than or equal to $\tau$, and $\{u,v\} \notin P$, then we can connect these two vertices with an edge. Hence we have another set of edges $T$ consisting of edges between vertices that could ?

\subsection{MTGMA}
\begin{enumerate}
	\item explain max cardinality matching algorithm excluding edges from $P$
	\item swap of mates
	\item if $|M| = n$, continue, else fail, no feasible arrangement of the boxes exists
\end{enumerate}
\begin{itemize}
	\item need a suitable matching $M\subset E$ s.t. $|M| = n-1$ CHECK THIS NOW WE HAVE DOMINATING VERTICES
	\item maximum cardinality matching algorithm for threshold graphs (Mahadev and Peled 1994)
	\item modify algorithm so that duplicate edges from mates are deleted, only consider edges from matching
	\item explain swap of mates??
\end{itemize}

There is a simple maximum cardinality matching algorithm (Mahadev and Peled, 1994) that produced a matching ?? containing suitable edges from $T$.

Initially, the vertices are sorted in order of non-decreasing weights, with ties broken arbitrarily. Starting from the vertex with the smallest weight, attempt to match it with any vertex in its neighbourhood that has not yet been matched. If such a vertex is available, add the current vertex and its match to a set $I$ that keeps track of the matched vertices. Succesively proceed to the next largest vertex until all vertices have been assessed.

\subsection{MIS}
\begin{enumerate}
	\item new graph, each vertex has degree 2 (connected to one vertex via edge from $P$ and one vertex via edge from $M$)
	\item either one cycle, remove dominating vertices
	\item 2+ cycles, need to connect all cycles together
\end{enumerate}

\subsection{FCA}
\begin{enumerate}
	\item find pairs of vertices in each cycle connected via a matching edge that can be broken and rematched
	\item lower vertex adj to higher vertex of other cycle's edge
	\item connect cycles together, remove dominating vertices
	\item if cycles cannot be connected, then no feasible arrangement of all boxes exists
\end{enumerate}

\subsection{Other}
\begin{enumerate}
	\item benefits of this alg wrt FFD/BPP?
\end{enumerate}

DESCRIPTION OF FFD EXACT
\begin{itemize}
	\item Start with boxes sorted in order of non-increasing widths, breaking ties by choosing the box with the smallest score width.
	\item Place the first box onto the first strip, such that the smaller of the two score widths is on the leftmost side of the strip.
	\item Attempt to fit each box $i, i = 2,..., n$ onto the lowest-indexed strip possible that already contains a box, i.e. the strip is not empty.
	\item If a box is able to feasibly fit onto a strip, apply the \textcolor{OliveGreen}{algorithm} on all of the boxes on the strip plus the current box $i$.
	\item If a feasible alignment of the boxes has been found, replace the current alignment of boxes on the strip with the new alignment, which includes box $i$ (and move onto the next box).
	\item If no feasible alignment of the boxes is found, we move onto the next lowest-indexed strip and repeat.
	\item If a box cannot fit into any of the used strips, i.e. any of the strips that already contain a box/any of the open strips, we then place the box onto a new, unused strip, such that the smaller of the two score widths on the box is on the leftmost side of the strip, then move onto the next box.
	\item Continue untill all boxes have been placed onto a strip/until all boxes have been packed.
\end{itemize}

\section{Experiments/Comparison}
\begin{itemize}
	\item \textcolor{Plum}{``Dowsland and Dowsland (1992, ``Packing Problems'') comment that while average or worst-case performance bounds are useful guidelines, it is best to determine an algorithm's usefuless by testing it on data sets typical to the intended problem. Repositories are available on the internet where benchamrk data sets for packing problems are stored for the purpose of evaluating algorithms.''}
\end{itemize}

\section{Conclusion}

\section{Layout}
Introduction:
\begin{itemize}
	\item One-dimensional BPP, NP-Hard.
	\item Goulimis packing boxes onto \textit{one} strip, where boxes have score constraints.
	\item Describe boxes, scores, score widths, minimum total score width constraint, scoring knives on bar etc. (include figure(s)).
	\item Becker has created a polynomial time algorithm for this problem (again, only on \textit{one} strip).
	\item How we adapt this problem: we take into account the width of each individual box (added widths to the boxes, not included by Becker), multiple strips, fixed lengths, if there was an instance with many boxes it's unlikely they would all fit onto one strip, strips come in fixed lengths that cannot be changed.
	\item Our problem: pack the boxes onto multiple strips of fixed lengths while meeting the minimum total score width constraint, not exceeding the capacity of the strips, and trying to minimise the number of strips used (perhaps mention minimising waste per strip?).
	\item Are there any similar problems? Who has researched this problem/similar problem, and using what methods? \cite{lewis2017} trapezoids paper. 
	\item Explain \textit{why this problem is important} (see above, strips come in fixed lengths, becker's algorithm is rendered useless if the total width of all boxes exceeds the length of one strip).
	\item Outline rest of paper.	
\end{itemize}

Lit Review
\begin{itemize}
	\item Solving the one-dimensional bpp using exact methods and heuristics.
	\item Exact methods - \cite{martello1990a} branch and bound based exact algorithm MTP, Carvalho 1999 column generation and branch-and-bound, \cite{eilon1971} depth-first search enumerative algorithm, only solve small size problem instances.
	\item \cite{garey1979} \textcolor{RoyalBlue}{NP-Hard, and therefore (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution in polynomial time for every instance of the BPP.}
	\item \textcolor{RoyalBlue}{Instead, heuristics can be used to find a near optimal solution in a shorter amount of time}.
	\item discuss heuristics.
	\item Explain FF and FFD, online/offline \cite{eilon1971}, \cite{dosa2007} tight bound, optimal number of bins $k$ \cite{korf2002}, complexity $O(n \log n)$ \cite{coffman1984} (where n is the number of items to be packed).
	\item quickly produce a feasible solution, but may not be optimal.
	\item Use heuristics in this paper to find feasible solutions for the problem, why?
\end{itemize}

Notation and Formulating the problem
\begin{itemize}
	\item $n$ boxes, $i = 1, 2, ..., n$, same height, different widths.
	\item Each box $i$ has a total width $w(i)$.
	\item Each box $i$ has two scores, $i_1$ (the smaller score), and $i_2$ (the larger score), and widths $w(i_1), w(i_2)$, such that $w(i_1) \leq w(i_2)$.
	\item Score widths not necessarily equal, therefore box has two different positions.
	\item $\{i_1, i_2\}$ represents ``regular'' box $i$: $i_1$ on LHS of box.
	\item $\{i_2, i_1\}$ represents ``rotated'' box $i$: $i_2$ on LHS of box (box rotated by $180^{\circ}$).
	\item Boxes will be placed side by side.
	\item All box widths $w(i) > 0$ and all score widths $w(i_1), w(i_2) > 0$ $\forall$ $i = 1, 2, ..., n$.
	\item Finite number of strips $S_j$, $j = 1, 2, ...$.
	\item All strips $S_j$ have equal fixed length $l > 0$ $\forall$ $j = 1, 2, ...$.
	\item All strips $S_j$ have a residual length $r(j)$, initially $r(j) = l$ $\forall$ $j = 1,2, ...$, which reduces as boxes are added to each strip.
	\item Assumption: all box widths $w(i) \leq l, i = 1, 2, ..., n$
	\item Initially, $S_j = \emptyset$ $\forall$ $j = 1, 2, ...$.
	\item For all strips $S_j \neq \emptyset$, the score on the right hand side of the last box in the strip is called the ``free score'', denoted $f_j$, with width $w(f_j)$.
	\item The sum of two adjacent score widths must fulfil the minimum total score width constraint ... $t$ is the minimum total score width.
	\item The minimum total score width constraint must be fulfilled in order for the scoring knives to be able to score the boxes correctly.
	\item The \textit{minimum total score width} is denoted by $t, t > 0$ \textcolor{RoyalBlue}{usually 70mm in industry}. \textcolor{RoyalBlue}{The \textit{minimum total score width constraint} is $w(u_p) + w(v_q) \geq t$, $u \neq v, p, q = 1 or 2$.}
	\item Strips packed from left to right.
	\item $l > 0, w(i) > 0, w(i) \leq l$
	\item Need to pack the boxes onto the strips so mtswc is met and least number of strips used.
	\item Formal definition of Score-Constrained Bin Packing Problem
\end{itemize}

FFD Approx
\begin{itemize}
	\item Explain FFD modified for scored boxes (basic).
	\item Free score $f_j$, residual length $r(j)$.
	\item Figure: partially packed strip showing first box in regular position, free score, minimum total score width constraint met between boxes, residual length.
	\item Pseudocode
	\item Description of algorithm
	\item Complexity, discuss how algorithm only checks if current box meets constraint with free score on final box, boxes are not able to be rearranged, even though there may be another arrangement of the boxes that is feasible (lead on to next algorithm FFD using exact algorithm).	
\end{itemize}

FFD Using Exact Algorithm
\begin{itemize}
	\item Combine FFD with exact algorithm to find a feasible solution to the SCBPP
	\item Unlike FFD approx, where attempts are made to place each box at the end of a strip, this algorithm is able to rearrange the order of the boxes in a strip to find a feasible arrangement.
	\item Can find a solution for a set of boxes on a strip when it may not have possible to find one in ffdapprox
	\item Describe Becker algorithm, using graph theory, Hamiltonian path/cycle
	\item Notation for Exact algorithm:
	\item $n$ boxes including dummy box.
	\item $2n$ vertices including dominating vertices.
	\item Graph $G$ is an undirected graph with $2n$ vertices $v_i, i = 1, 2, ...,2n$.
	\item Vertices are weighted, $w(v_i)$.
	\item Vertices that represent either side of same box referred to as ``partners''
	\item $P$ contains the set of edges between partners, fixed, $|P| = n$.
	\item Edges in $P$ are weighted, corresponding to box width.
	\item $Q$ contains the set of edges between vertices that meet the minimum total score width constraint, excluding partners (these edges are not weighted).
	\item $G(V, P \cup Q)$ - each edge on $G$ is either in $P$ or $Q$, not both.
	\item $t$ still represents the minimum total score width.
	\item $M$ is the set of matching edges, $M \subset Q$, edges chosen using the matching algorithm (need $|M| = n$).
	\item number of cycles on $G$ after MTGMA =  ?
	\item $C_k$: sets of edges for connecting cycles.
	\item Section: Becker algorithm
	\item Combine alg with ffd
	\item Pseudocode
	\item Description of algorithm
	\item Complexity
\end{itemize}

Comparison/Results

Conclusion
\section{References}
\cite{becker2010}, \cite{becker2015}, \cite{coffman1978}, \cite{dosa2007}, \cite{eilon1971}, \cite{garey1979}, \cite{gilmore1961}, \cite{gilmore1963}, \cite{goulimis2004}, \cite{johnson1974}, \cite{karp1972}, \cite{korf2002}, \cite{lewis2009}, \cite{lewis2017}, \cite{lewis2011}, \cite{mahadev1994}, \cite{mahadev1995}, \cite{martello1990a}, \cite{martello1990b}

\cite{becker2010}: Twin Constrainted Hamiltonain Paths on Threshold Graphs

\cite{becker2015}: A Heuristics for the MSSP

\cite{coffman1978}: An Application of Bin-Packing to Multiprocessor Scheduling

\cite{coffman1984}: Approximation Algorithms for Bin-Packing - An Updated Survey.
\begin{itemize}
	\item \textcolor{Plum}{``first fit and first fit decreasing algorithms have equivalent worst-case time complexities of O(n ln n) (cite coffman1984)''}
	\item \textcolor{Plum}{``we refer the interested reader to the excellent survery by (cite coffman1984), which includes a bibliography of more than one hundred titles''}
	\item \textcolor{Plum}{``A comprehensive review of various heuristic algorithms is provided in a recent survery by (cite coffman1984)''}
	\item \textcolor{Plum}{``(cite coffman1984) did an excellent survey on this problem, particularly on approximation algorithms and their asymptotic performance ratios''}
\end{itemize}

\cite{dosa2007}: The tight bound of first fit decreasing bin packing algorithm

\cite{eilon1971}: The loading problem. 
\begin{itemize}
	\item \textcolor{Plum}{``(cite eilon1971) presented a depth-first enumerative algorithm''}
	\item \textcolor{Plum}{``(cite eilon1971) discuss its(the BPP) application to the loading of vehicles (or other containers) with consignment''}
	\item \textcolor{Plum}{``the most well-known heuristics are the FFD and the BFD (cite eilon1971)''}
\end{itemize}

\cite{garey1979}: Computers and Intractibility - A Guide to the Theory of NP-Completeness. 
\begin{itemize}
	\item \textcolor{Plum}{``(cite garey1979) cite simple heuristics which can be shown to be noworse(but also no better) than a rather small multiplying factor above the optimal number of bins.''}
	\item \textcolor{Plum}{``the bpp problem is NP-Hard''}
\end{itemize}

\cite{gilmore1961}: A LP Approach to the CSP Part 1

\cite{gilmore1963}: A LP Approach to the CSP Part 2

\cite{goulimis2004}: Minimum Score Separation

\cite{johnson1974}: Worst case performance bounds for simple one-dimensional packing algorithms
\begin{itemize}
	\item \textcolor{Plum}{ ``(cite johnson1974) discuss three practical applications in computer science, which are table formatting, prepaging, and file allocation''}
\end{itemize}

\cite{karp1972}: Reducibility among combinatorial problems

\cite{korf2002}: A new algorithm for optimal bin packing. \textcolor{Plum}{``If the number of bins in a solution is equivalent to the expression (sum of all weights/ capacity) then that solution is an optimal solution to the problem instance (cite Korf2002)''}

\cite{lewis2009}: A general-purpose hill-climbing method for order independent minimum grouping problems

\cite{lewis2017}: How to pack trapezoids

\cite{lewis2011}: An investigation into two bpp with ordering and orientation implications

\cite{mahadev1994}: Longest cycle in threshold graphs

\cite{mahadev1995}: Threshold graphs and related topics

\cite{martello1990a}: Knapsack problems.\textcolor{Plum}{ ``(cite martello1990) proposed a branch-and-bound based exact algorithm MTP for the BPP.''}

\cite{martello1990b}: Lower bounds and reduction procedures for the bin packing problem

\section{Other}
\begin{itemize}
	\item complexity
\end{itemize}

\bibliographystyle{dcu}
\bibliography{includes/bibliography}

\end{document}

### 2018-03-05 PAPER/paper.tex
renamed folders

--- 2018-01-15 paper/paper.tex
@@
 \section{Introduction}
-\label{sec:intro}
+
 The one-dimensional bin packing problem (BPP) is a combinatorial optimisation problem that has been widely researched and discussed due to its ability to model a variety of real-life sitations.
@@
 If there are no bins that can feasibly accommodate the item, the algorithm places the item into a new bin.
-A modified version of first-fit yields the well-known first-fit decreasing (FFD) algorithm (\citealp{eilon1971}), which initially sorts the items into non-decreasing order of size before allocating them into bins.
+A modified version of first-fit yields the well-known first-fit decreasing (FFD) algorithm (\citealp{eilon1971}), which initially sorts the items into non-increasing order of size before allocating them into bins.
 As proven by \cite{dosa2007} \textcolor{RoyalBlue}{(proved bound is tight)}, the worst case for FFD is $\frac{11}{9}k + \frac{6}{9}$ bins, where $k$ is the optimal number of bins given by $\ceil{\frac{\sum_{i=1}^{n} w_{i}}{c}}$ \textcolor{RoyalBlue}{(..if the solution has this many bins then it is optimal,} (\citealp{korf2002})).
@@
 \begin{definition}
-	\label{defn:scbpp}
+
 	Given $n$ boxes of varying widths $w(i)$ and score widths $w(i_1), w(i_2)$, and a finite number of strips $S_j$ with equal fixed lengths $l$, the Score-Constrained Bin-Packing Problem (SCBPP) consists of finding the minimum number of strips required to pack all of the boxes such that the minimum total score width constraint is met between every pair of boxes.
@@
 \section{FFD Using Approximate Algorithm}
-\label{sec:ffdapprox}
 
@@
 	\caption{\textcolor{OliveGreen}{Approximate First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
-	\label{alg:ffdapprox}
 	\begin{algorithmic}[1]
@@
 \section{FFD Using Exact Algorithm}
-\label{sec:ffdexact}
+
 Introduction
@@
 \begin{equation*}
-	\label{eqn:mtswcg}
 	w(u) + w(v) \geq t,
@@
 \begin{definition}
-	\label{defn:althamcycle}
+
 	Let $G(V, P\cup Q)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $Q$.
@@
 	\caption{\textcolor{OliveGreen}{Exact First-Fit Decreasing Algorithm for the Score-Constrained Bin-Packing Problem}}
-	\label{alg:ffdexact}
+
 	\begin{algorithmic}[1]
@@
 \section{Comparison and Results}
-\label{sec:compresult}
 
 \section{Conclusion}
-\label{sec:conclusion}
 
 \section{References}
-\cite{becker2010}, \cite{becker2015}, \cite{coffman1978}, \cite{dosa2007}, \cite{eilon1971}, \cite{garey1979}, \cite{gilmore1961}, \cite{gilmore1963}, \cite{goulimis2004}, \cite{johnson1974}, \cite{karp1972}, \cite{korf2002}, \cite{lewis2009}, \cite{lewis2017}, \cite{lewis2011}, \cite{mahadev1994}, \cite{mahadev1995}, \cite{martello1990a}, \cite{martello1990b}
+\cite{becker2010}, \cite{becker2015}, \cite{coffman1978}, \cite{dosa2007}, \cite{eilon1971}, \cite{garey1979}, \cite{gilmore1961}, \cite{gilmore1963}, \cite{goulimis2004}, \cite{johnson1974worst}, \cite{johnson1974fast}, \cite{hung1978}, \cite{garey1972}, \cite{johnson1973}, \cite{karp1972}, \cite{korf2002}, \cite{lewis2009}, \cite{lewis2017}, \cite{lewis2011}, \cite{mahadev1994}, \cite{mahadev1995}, \cite{martello1990a}, \cite{martello1990b}
 

### 2018-03-19 SCSPP/COMBINED/main.cpp
added output statements to heuristics

@@ -112,11 +112,11 @@ void ArgumentCheck(int numInstances, int tau, int numItem, int minWidth, int max
         cout << std::left << setw(18) << "Algorithm:" << std::right << setw(13) << "FFDincAHCA\n";
     }
     else if(algType == 4  && xOver == 1){
-        cout << std::left << setw(20) << "Algorithm: " << std::right << setw(6) << "EA with GGA" << endl;
+        cout << std::left << setw(19) << "Algorithm: " << std::right << setw(6) << "EA with GGA" << endl;
         cout << std::left << setw(20) << "Population size:" << std::right << setw(10) << numPop << endl;
     }
     else if(algType == 4 && xOver == 2){
-        cout << std::left << setw(20) << "Algorithm: " << std::right << setw(6) << "EA with GPX'" << endl;
+        cout << std::left << setw(18) << "Algorithm: " << std::right << setw(6) << "EA with GPX'" << endl;
         cout << std::left << setw(20) << "Population size:" << std::right << setw(10) << numPop << endl;
     }
     cout << std::left << setw(20) << "Random seed:" << std::right << setw(10) << randomSeed << endl;
@@ -212,27 +212,36 @@ int main(int argc, char **argv){
     switch(algType){
         case 1:
             for(instance = 0; instance < numInstances; ++instance){
+                //srand(1);
+                //cout << "Tau: " << tau << endl;
                 CreateInstance(tau, numScores, numItem, minWidth, maxWidth, minItemWidth, maxItemWidth, totalItemWidth, allScores, partners, adjMatrix, itemWidths);
                 BasicFFD(opt, opt90, opt80, opt70, opt60, opt50, optLow, numScores, numItem, maxItemWidth, stripLength, totalItemWidth, allScores, partners, adjMatrix, itemWidths, stripSum, strip);
                 ResetVar(numScores, numItem, allScores, partners, adjMatrix, itemWidths, stripSum, strip);
+                //tau += 10;
             }
             Output(opt, opt90, opt80, opt70, opt60, opt50, optLow, numInstances);
             break;
 
         case 2:
             for(instance = 0; instance < numInstances; ++instance){
+                //srand(1);
+                //cout << "Tau: " << tau << endl;
                 CreateInstance(tau, numScores, numItem, minWidth, maxWidth, minItemWidth, maxItemWidth, totalItemWidth, allScores, partners, adjMatrix, itemWidths);
[…]

### 2018-03-19 SCSPP/COMBINED/packing.cpp

@@ -23,6 +23,23 @@ int LowerBound(int stripLength, double totalItemWidth){
     return lBound;
 }
 
+double Fitness(int stripLength, vector<int> &stripSum, vector<vector<int> > &strip){
+
+    int i;
+    double total = 0.0;
+    double final;
+
+    for(i = 0; i < strip.size(); ++i){
+        double a = static_cast<double>(stripSum[i]) / static_cast<double>(stripLength);
+        total += pow(a, 2);
+    }
+
+    final = total / static_cast<double>(strip.size());
+
+    return final;
+
+}
+
 void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB){
 
     double c = static_cast<double>(LB) / stripSize;
@@ -107,20 +124,19 @@ void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
         }
     }
 
-    int k = strip.size() - 1;
-    while(strip[k].empty()){
-        strip.pop_back();
-        --k;
-    }
-
-    int l = stripSum.size() -1;
-    while(stripSum[l] == 0){
+    while(stripSum.back() == 0){
         stripSum.pop_back();
-        --l;
+        strip.pop_back();
     }
 
     int stripSize = strip.size();
     int LB = LowerBound(stripLength, totalItemWidth);
+
+    /*double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
+
+    cout << "Lower Bound: " << LB << endl;
+    cout << "# strips BasicFFD: " << stripSize << endl;
+    cout << "Avg # items/strip: " << avg << endl << endl;*/
 
     Optimality(opt, opt90, opt80, opt70, opt60, opt50, optLow, stripSize, LB);
 
@@ -128,7 +144,7 @@ void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int stripLength,
+void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int stripLength,
[…]

### 2018-03-19 SCSPP/COMBINED/packing.h

@@ -16,6 +16,8 @@ void Swap(int &a, int &b);
 
 int LowerBound(int stripLength, double totalItemWidth);
 
+double Fitness(int stripLength, vector<int> &stripSum, vector<vector<int> > &strip);
+
 void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize,
                 int LB);
 
@@ -25,7 +27,7 @@ void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores,
+void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
                   int stripLength, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
                   vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
@@ -36,8 +38,6 @@ void FFDincAHCA(int tau, int &opt, int &opt90, int &opt80, int &opt70,
                 vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum,
                 vector<vector<int> > &strip);
 
-
-double Fitness(int stripLength, vector<int> &stripSum, vector<vector<int> > &strip);
 
 void FFD(int numScores, int numItem, int maxItemWidth, vector<int> &partners, vector<vector<int> > &itemWidths, vector<int> &itemOrder);
 
@@ -80,8 +80,10 @@ void GPX(int tau, int numScores, int maxItemWidth, int stripLength, vector<int> 
          vector<vector<int> > &itemWidths, vector<int> &offspringSum, vector<vector<int> > &offspring, vector<int> &stripSumX, vector<vector<int> > &stripX,
          vector<int> &stripSumY, vector<vector<int> > &stripY);
 
-void AHCA(int tau, int i1, int j1, int &feasible, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
[…]

### 2018-03-20 SCSPP/COMBINED/main.cpp
added vectors for values of tau that increment alpha by 0.1, added output statements to obtain data for analysis

@@ -47,23 +47,23 @@ void ArgumentCheck(int numInstances, int tau, int numItem, int minWidth, int max
     bool error = false;
 
     cout << "SCSPP\n------------------------------\n";
-    if(tau == 0){
+    /*if(tau == 0){
         cout << "[ERROR]: Constraint value cannot be zero.\n";
         error = true;
-    }
+    }*/
     if(stripLength == 0){
         cout << "[ERROR]: Strip cannot have length zero.\n";
         error = true;
     }
-    if(2*minWidth >= tau){
+    /*if(2*minWidth >= tau){
         cout << "[ERROR]: Constraint value is less than or equal to twice the minimum score width, vicinal sum constraint always valid.\n";
         cout << "         Problem instance is therefore classical strip-packing problem without score constraint (i.e. tau = 0).\n";
         error = true;
-    }
-    if(2*maxWidth < tau){
+    }*/
+    /*if(2*maxWidth < tau){
         cout << "[ERROR]: Constraint value is greater than double maximum score width, vicinal sum constraint never valid.\n";
         error = true;
-    }
+    }*/
     if(2*maxWidth >= minItemWidth){
         cout << "[ERROR]: Minimum item width is less than double maximum score width, scores may overlap.\n";
         error = true;
@@ -106,7 +106,7 @@ void ArgumentCheck(int numInstances, int tau, int numItem, int minWidth, int max
         cout << std::left << setw(18) << "Algorithm:" << std::right << setw(13) << "BasicFFD\n";
     }
     else if(algType == 2){
-        cout << std::left << setw(18) << "Algorithm:" << std::right << setw(13) << "PackSmallest\n";
+        cout << std::left << setw(18) << "Algorithm:" << std::right << setw(13) << "PairSmallest\n";
     }
     else if(algType == 3){
         cout << std::left << setw(18) << "Algorithm:" << std::right << setw(13) << "FFDincAHCA\n";
@@ -131,7 +131,7 @@ int main(int argc, char **argv){
 
     int x;
     int numInstances = 1000;
-    int tau = 70;
+    int tau = 0;
     int numItem = 500;
     int minWidth = 1;
     int maxWidth = 70;
@@ -204,6 +204,11 @@ int main(int argc, char **argv){
     double bestFitness = 0.0;
     double tempFitness;
 
+    //values of tau for alpha = 0.0 to 1.0 in 0.1 incremenents, for n = 100, 500, and 1000. for srand(1) only.
[…]

### 2018-03-20 SCSPP/COMBINED/packing.cpp

@@ -132,11 +132,14 @@ void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
     int stripSize = strip.size();
     int LB = LowerBound(stripLength, totalItemWidth);
 
-    /*double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
+    double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
 
-    cout << "Lower Bound: " << LB << endl;
+    /*cout << "Lower Bound: " << LB << endl;
     cout << "# strips BasicFFD: " << stripSize << endl;
-    cout << "Avg # items/strip: " << avg << endl << endl;*/
+    cout << "Avg # items per strip: " << avg << endl << endl;*/
+
+    //cout << stripSize << endl;
+    //cout << avg << endl;
 
     Optimality(opt, opt90, opt80, opt70, opt60, opt50, optLow, stripSize, LB);
 
@@ -208,11 +211,14 @@ void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int 
     int stripSize = strip.size();
     int LB = LowerBound(stripLength, totalItemWidth);
 
-    /*double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
+    double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
 
-    cout << "Lower Bound: " << LB << endl;
+    /*cout << "Lower Bound: " << LB << endl;
     cout << "# strips PairSmallest: " << stripSize << endl;
     cout << "Avg # items per strip: " << avg << endl << endl;*/
+
+    //cout << stripSize << endl;
+    //cout << avg << endl;
 
     Optimality(opt, opt90, opt80, opt70, opt60, opt50, optLow, stripSize, LB);
 
@@ -281,11 +287,14 @@ void FFDincAHCA(int tau, int &opt, int &opt90, int &opt80, int &opt70, int &opt6
     int stripSize = strip.size();
     int LB = LowerBound(stripLength, totalItemWidth);
 
-    /*double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
+    double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
 
-    cout << "Lower Bound: " << LB << endl;
+    /*cout << "Lower Bound: " << LB << endl;
     cout << "# strips FFDincAHCA: " << stripSize << endl;
[…]

### 2018-03-21 PAPER/main.tex
changed to use elsarticle class
added spaces between definitions

@@
-\documentclass[oribibl]{llncs}
+\documentclass[preprint]{elsarticle}
 
@@
 
+\begin{document}
+
+\begin{frontmatter}
 \title{Heuristics for the Score-Constrained Strip-Packing Problem}
-\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
-\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
+\author{Asyl L. Hawa}
+\author{Rhyd Lewis}
+\author{Jonathan M. Thompson}
+\address{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
 \date{\today}
 
-\begin{document}
-\maketitle
+%\maketitle
 
@@
 
+\end{frontmatter}
+
 \section{Introduction}
@@
 
-Firstly, let us introduce the Constrained Pair-Ordering Problem:
+Firstly, let us introduce the Constrained Pair-Ordering Problem:\\
 
@@
 	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple.
-The Constrained Pair Ordering Problem (CPOP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
+The Constrained Pair-Ordering Problem (CPOP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
 	\begin{equation}
@@
 For this reason, we define a new problem to be investigated.
+\\
 
@@
 
-The following definition describes a variant of the classical Hamiltonian cycle on a graph $G$.
+The following definition describes a variant of the classical Hamiltonian cycle on a graph $G$.\\
 
@@
 $G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such successive edges alternate between sets $P$ and $E$.
-For example, if $(v_{i-1}, v_i) \in P$, then $(v_i, v_{i+1}) \in E$, or vice versa.
+For example, if $(v_{i-1}, v_i) \in P$, then $(v_i, v_{i+1}) \in E$, or vice versa.\\
 \end{definition}
@@
 \textcolor{OrangeRed}{edges E vicinal sum constraint equation 2}.
-\qed
 \end{proof}
@@
 
+\section*{References}
+
 \bibliographystyle{dcu}

### 2018-03-22 SCSPP/COMBINED/main.cpp
reset switch statements back to original, removed alpha vectors

@@ -47,23 +47,23 @@ void ArgumentCheck(int numInstances, int tau, int numItem, int minWidth, int max
     bool error = false;
 
     cout << "SCSPP\n------------------------------\n";
-    /*if(tau == 0){
+    if(tau == 0){
         cout << "[ERROR]: Constraint value cannot be zero.\n";
         error = true;
-    }*/
+    }
     if(stripLength == 0){
         cout << "[ERROR]: Strip cannot have length zero.\n";
         error = true;
     }
-    /*if(2*minWidth >= tau){
+    if(2*minWidth >= tau){
         cout << "[ERROR]: Constraint value is less than or equal to twice the minimum score width, vicinal sum constraint always valid.\n";
         cout << "         Problem instance is therefore classical strip-packing problem without score constraint (i.e. tau = 0).\n";
         error = true;
-    }*/
-    /*if(2*maxWidth < tau){
+    }
+    if(2*maxWidth < tau){
         cout << "[ERROR]: Constraint value is greater than double maximum score width, vicinal sum constraint never valid.\n";
         error = true;
-    }*/
+    }
     if(2*maxWidth >= minItemWidth){
         cout << "[ERROR]: Minimum item width is less than double maximum score width, scores may overlap.\n";
         error = true;
@@ -131,7 +131,7 @@ int main(int argc, char **argv){
 
     int x;
     int numInstances = 1000;
-    int tau = 0;
+    int tau = 70;
     int numItem = 500;
     int minWidth = 1;
     int maxWidth = 70;
@@ -203,12 +203,6 @@ int main(int argc, char **argv){
     vector<int> bestSolnStartSum;
     double bestFitness = 0.0;
     double tempFitness;
-
-    //values of tau for alpha = 0.0 to 1.0 in 0.1 incremenents, for n = 100, 500, and 1000. for srand(1) only.
-    vector<int> alpha100 = { 150, 105, 93, 84, 75, 68, 61, 53, 44, 32, 0 };
-    vector<int> alpha500 = { 150, 110, 97, 88, 79, 72, 64, 56, 46, 34, 0 };
-    vector<int> alpha1000 = { 150, 111, 98, 89, 80, 73, 65, 57, 47, 34, 0 };
-    double alpha = 0.0;
     srand(randomSeed);
 
     time_t startTime, endTime;
@@ -216,68 +210,30 @@ int main(int argc, char **argv){
 
     switch(algType){
         case 1:
[…]

### 2018-03-22 SCSPP/COMBINED/packing.cpp
commented out all output statements used for collecting data from the three heuristics, in CP function, removed copy(edgeCopy...) and added edgeCopy = edge (used vector assignment operator to copy edge vector rather than back_inserter and copy function)

@@ -132,7 +132,7 @@ void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
     int stripSize = strip.size();
     int LB = LowerBound(stripLength, totalItemWidth);
 
-    double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
+    //double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
 
     /*cout << "Lower Bound: " << LB << endl;
     cout << "# strips BasicFFD: " << stripSize << endl;
@@ -211,7 +211,7 @@ void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int 
     int stripSize = strip.size();
     int LB = LowerBound(stripLength, totalItemWidth);
 
-    double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
+    //double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
 
     /*cout << "Lower Bound: " << LB << endl;
     cout << "# strips PairSmallest: " << stripSize << endl;
@@ -287,7 +287,7 @@ void FFDincAHCA(int tau, int &opt, int &opt90, int &opt80, int &opt70, int &opt6
     int stripSize = strip.size();
     int LB = LowerBound(stripLength, totalItemWidth);
 
-    double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
+    //double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
 
     /*cout << "Lower Bound: " << LB << endl;
     cout << "# strips FFDincAHCA: " << stripSize << endl;
@@ -1608,7 +1608,7 @@ void AHCAH(int tau, int i1, int j1, int &feasible, vector<int> &allScores, vecto
     vector<int> original;
     feasible = 0;
 
-    int dom = 140; /****/
+    int dom = 140; /****/ //dominating score widths
 
     //Creating scores vector
     for(k = 0; k < strip[i1].size(); ++k){
@@ -2025,7 +2025,7 @@ void CP(int nScores, int nComp, int &feasible, int qstar, int nCycles, vector<in
         if(type == 0){
             temp.clear();
             SSum = 0;
-            copy(edge.begin(), edge.end(), back_inserter(edgeCopy));
+            edgeCopy = edge;
             for(i = 0; i < C.size(); ++i){
                 if(C[i].size() > maxRowSize){
                     maxRowSize = C[i].size();

### 2018-03-22 PAPER/main.tex
minor typos, added strips figure

--- 2018-03-05 PAPER/main.tex
@@
 \input{includes/preamble.tex}
+
+\begin{document}
 
@@
 
-\begin{document}
 \maketitle
@@
 	\end{equation}
-	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the vicinal sum constraint.
+	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the \textup{vicinal sum constraint}.
 \end{definition}
@@
 It can be seen that this problem is in fact analogous to the CPOP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance.
-Thus, a set $\mathcal{I}$ of items has a feasible arrangement if the equivalent CPOP has a solution $\mathcal{T}$.
+Thus, a set $\mathcal{I}$ of items has a feasible arrangement if the equivalent CPOP has a solution $\mathcal{T}$ that meets the vicinal sum constraint.
 
-Observe that, in this particular strip-packing problem, the widths of the individual items are not taken into account, since the aim is to arrage the items onto a strip of seemingly infinite length.
+Observe that, in this particular strip-packing problem, the widths of the individual items are not taken into account, since the aim is to arrange the items onto a strip of seemingly infinite length.
 In reality, strips of material are provided in fixed lengths.
@@
 	\label{defn:scspp}
-	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ with equal fixed length $l$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the minimum total score width constraint is met between every pair of adjacent items on every strip.
+	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ with equal fixed length $l$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the \textcolor{OrangeRed}{minimum total score width constraint}(this term is never mentioned, rephrase) is met between every pair of adjacent items on every strip.
 \end{definition}
@@
 \label{sec:ffdapprox}
-The first heuristic to be discussed is the Score-Constrainted First-Fit Decreasing (SCFFD) heuristic, which is an extension of the original FFD.
+The first heuristic to be discussed is the Score-Constrained First-Fit Decreasing (SCFFD) heuristic, which is an extension of the original FFD.
 The items in $\mathcal{I}$ are, as usual, sorted in non-increasing order of widths, with ties broken by selecting the item with the smallest score width.
@@
 Each new strip $S_j$ is initialised by placing the item $i \in \mathcal{I}'$ with the smallest score width onto $S_j$ in a regular position, where $\mathcal{I}'$ is the set of items that have not yet been packed onto a strip.
-The heuristic then continues to pack items onto $S_j$, by choosing an item in $\mathcal{I}'$ with the smallest score width that fulfils the vicinal sum constraint when placed alongside the right-most score width on $S_j$, and that does not exceed $S_j$'s capacity.
+The heuristic then continues to pack items onto $S_j$, by choosing an item in $\mathcal{I}'$ with the smallest score width that fulfils the vicinal sum constraint when placed alongside the right-most score width on $S_j$, and that does not exceed the capacity of $S_j$.
 Once there are no more items in $\mathcal{I}'$ that can be feasibly packed onto $S_j$, the heuristic adds $S_j$ to the solution set $\mathcal{S}$, and the next new strip $S_{j+1}$ is initialised.
@@
 
+\begin{figure}[h!]	
+	\centering
+	\includestandalone[width=\textwidth]{figures/strips}
+	\caption{\textcolor{red}{BasicFFD vs. FFDincAHCA}}	
+	\label{fig:ffdvsffdincahca}
+\end{figure}
+
 \bibliographystyle{dcu}

### 2018-03-22 PAPER/main.tex
minor changes

@@
 
-Observe that, in this particular strip-packing problem, the widths of the individual items are not taken into account, since the aim is to arrange the items onto a strip of seemingly infinite length.
+Observe that, in this particular strip-packing problem, the widths of the individual items are disregarded entirely, since the aim is to arrange the items onto a strip of seemingly infinite length.
 In reality, strips of material are provided in fixed lengths.
@@
 	\label{defn:scspp}
-	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ with equal fixed length $l$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the \textcolor{OrangeRed}{minimum total score width constraint}(this term is never mentioned, rephrase) is met between every pair of adjacent items on every strip.
+	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ with equal fixed length $l$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
 \end{definition}
@@
 The procedure initially sorts the edges in $Q$ into a list such that the smaller vertices of the edges are in lexicographical order, and therefore in non-decreasing order of values.
-Any edges that are a result of rematching are then removed from this list.
-Starting from the first edge, BR searches through the list to find an edge that meets the following conditions:
+Any edges whose smaller vertices, during MMCM, were unable to be matched with the largest possible vertex available due to being partners are then removed from this list.
+Any edges that do not connect the smaller vertex to the largest possible vertex, due to the largest vertex being its partner, are also removed.
+the Starting from the first edge, BR searches through the list to find an edge that meets the following conditions:
 \begin{enumerate}

### 2018-03-23 PAPER/main.tex
added pros and cons to heuristics

@@
 This process continues until every item $i \in \mathcal{I}$ has been placed onto a strip $S_j \in \mathcal{S}$.
+The additional check of the vicinal sum constraints and rotation of the items can be performed in constant time, and as such this heuristic has the same time complexity as FFD, $O(n \log n)$.
+This heuristic only checks the current items score widths against the right-most score width on a strip, and if the vicinal sum constraint is not met, the item cannot be placed on the strip.
+However, there may be another location on the strip that the item could be placed in feasibly, or a rearrangement of all items on the strip that produce a feasible alignment.
 
@@
 \label{sec:ffdsmall}
-This next heuristic focusses on packing each strip in turn, rather than each item as in the previous heuristic.
+This next heuristic focuses on packing each strip in turn, rather than each item as in the previous heuristic.
 Each new strip $S_j$ is initialised by placing the item $i \in \mathcal{I}'$ with the smallest score width onto $S_j$ in a regular position, where $\mathcal{I}'$ is the set of items that have not yet been packed onto a strip.
@@
 When $|\mathcal{I}'| = 0$, all items have been packed onto a strip, and the process terminates.
+This heuristic is designed to align score widths such that their sum is as close to the minimum scoring distance as possible, which eliminates the possibility of aligning larger score widths unecessarily.
+The larger score widths are then available to be aligned next to smaller score widths.
+Heuristic prioritises vicinal sum constraint over item widths.
 
@@
 In the event that AHCA is unable to produce a solution, $S_j$ remains intact, and the heuristic attempts to pack $i$ onto the next lowest-indexed feasible strip.
+Due to the inclusion of AHCA, this heuristic is slower than the previous heuristics, with complexity $O(n^2)$.
+This heuristic has a significant advantage, however, as it is able to rearrange items entirely in order to find a feasible solution.
+In addition, we know that if a feasible alignment for a given set of items exists, AHCA is guaranteed to find and produce this solution.
+Thus, every subproblem in this heuristic, i.e.
+every time an item needs to be placed on a strip, can be solved exactly.
+For example, Figure \ref{fig:comparestrips} illustrates an instance of the SCSPP in which an item can feasibly fit onto a strip, i.e.
+the addition of the item onto the strip does not cause the strip's capacity to be exceed.
+In the original version of FFD, the items on the strip are, as expected, in non-increasing order, and the right-most score width has a value of 3.
+Regardless of orientation, the current item cannot meet the vicinal sum constraint.
+The heuristic will therefore attempt to place the item onto another strip, or, if there are no other open strips, a new strip will be required to accommodate the item, thus increasing the total number of strips.
+However, by using FFDincAHCA, a feasible alignment of the items including the current item exists, and hence the item does not need to be placed elsewhere, minimising the risk of potentially adding a new strip to the solution.
 
@@
 	\includestandalone[width=\textwidth]{figures/strips}
-	\caption{\textcolor{red}{BasicFFD vs. FFDincAHCA}}	
-	\label{fig:ffdvsffdincahca}
+	\caption{Comparison of two heuristics, maximum strip length is 18, $\tau = 70$.}	
+	\label{fig:comparestrips}
 \end{figure}
+
+\section{Comparison}
+In order to provide a complete overview of the heuristics, sets of 100, 500, and 1000 items were used on strips of lengths 1500, 2500, and 5000.
+Item widths were randomly selected between 150 and 1000, and score widths between 1 and 70.
+This ensures that each item has two score lines.
 

### 2018-03-27 SCSPP/COMBINED/base.cpp
added line at end of CreateInstance which outputs totalItemWidth (commented out)

@@ -121,4 +121,6 @@ void CreateInstance(int tau, int numScores, int numItem, int minWidth, int maxWi
 
     }
 
+    //cout << "TotalItemWidth: " << totalItemWidth << endl;
+
 } //End CreateInstance

### 2018-03-27 SCSPP/COMBINED/packing.cpp
added double &totalOpt to calculate total optimality for each heuristic

@@ -67,7 +67,7 @@ void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &o
 } //End Optimality
 
 // FFD checking vicinal sum constraint for both sides of each item.
-void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
+void BasicFFD(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
               int stripLength, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
               vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
     int i, j, mini;
@@ -132,11 +132,16 @@ void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
     int stripSize = strip.size();
     int LB = LowerBound(stripLength, totalItemWidth);
 
+    double c = static_cast<double>(LB) / stripSize;
+    totalOpt += c;
+
+
     //double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
 
-    /*cout << "Lower Bound: " << LB << endl;
-    cout << "# strips BasicFFD: " << stripSize << endl;
-    cout << "Avg # items per strip: " << avg << endl << endl;*/
+    //cout << "Lower Bound: " << LB << endl;
+    //cout << "# strips BasicFFD: " << stripSize << endl;
+    //cout << "Avg # items per strip: " << avg << endl << endl;
+    //cout << endl;
 
     //cout << stripSize << endl;
     //cout << avg << endl;
@@ -147,7 +152,7 @@ void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int stripLength,
+void PairSmallest(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int stripLength,
[…]

### 2018-03-27 SCSPP/COMBINED/packing.h

@@ -18,22 +18,21 @@ int LowerBound(int stripLength, double totalItemWidth);
 
 double Fitness(int stripLength, vector<int> &stripSum, vector<vector<int> > &strip);
 
-void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize,
-                int LB);
+void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB);
 
-void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
+void BasicFFD(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
               int stripLength, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
               vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
+void PairSmallest(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
                   int stripLength, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
                   vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // FFD including AHCA, instead of attempting to place item on end of strip, run AHCA to find feasible solution.
-void FFDincAHCA(int tau, int &opt, int &opt90, int &opt80, int &opt70,
+void FFDincAHCA(double &totalOpt, int tau, int &opt, int &opt90, int &opt80, int &opt70,
                 int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth, int stripLength, double totalItemWidth,
                 vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum,
                 vector<vector<int> > &strip);

### 2018-03-27 SCSPP/COMBINED/main.cpp
changed for loops to run instances 1000 times for each value of tau (which correspond to increments of alpha), added struct for time, changed some output statements to WARNING instead of ERROR in ArgumentCheck, added alpha vector, removed old time statements and #include <ctime>, added #include <chrono>

@@ -7,14 +7,33 @@ Combined Program with Heuristics and EA
 
 #include <iostream>
 #include <fstream>
-#include <ctime>
-#include <cstring>
-#include <iomanip>
 #include <cmath>
+#include <cstring>
+#include <ctime>
+#include <chrono>
+#include <iomanip>
 using namespace std;
 
 #include "base.h"
 #include "packing.h"
+
+struct Timer{
+
+    std::chrono::high_resolution_clock::time_point startTime, endTime;
+    std::chrono::duration<float> totalTime;
+
+    Timer(){
+        startTime = std::chrono::high_resolution_clock::now();
+    }
+
+    ~Timer(){
+        endTime = std::chrono::high_resolution_clock::now();
+        totalTime = endTime - startTime;
+
+        float totalTimems = totalTime.count() * 1000.0f;
+        cout << "\nCPU Time: " << totalTimems << "ms (" << totalTime.count() << "s)\n[END OF PROGRAM]\n" << endl;
+    }
+};
 
 void ProgramInfo(){
 
@@ -48,21 +67,25 @@ void ArgumentCheck(int numInstances, int tau, int numItem, int minWidth, int max
 
     cout << "SCSPP\n------------------------------\n";
     if(tau == 0){
-        cout << "[ERROR]: Constraint value cannot be zero.\n";
-        error = true;
+        //cout << "[ERROR]: Constraint value cannot be zero.\n";
+        cout << "[WARNING]: Constraint value is zero, problem instances are equivalent to classical SPP without score constraints.\n";
+        //error = true;
     }
     if(stripLength == 0){
         cout << "[ERROR]: Strip cannot have length zero.\n";
         error = true;
     }
     if(2*minWidth >= tau){
-        cout << "[ERROR]: Constraint value is less than or equal to twice the minimum score width, vicinal sum constraint always valid.\n";
+        //cout << "[ERROR]: Constraint value is less than or equal to twice the minimum score width, vicinal sum constraint always valid.\n";
+        cout << "[WARNING]: Constraint value is less than or equal to twice the minimum score width, vicinal sum constraint always valid.\n";
         cout << "         Problem instance is therefore classical strip-packing problem without score constraint (i.e. tau = 0).\n";
-        error = true;
+        //error = true;
     }
     if(2*maxWidth < tau){
[…]

### 2018-03-28 PAPER/main.tex
added tables

@@
 For example, Figure \ref{fig:comparestrips} illustrates an instance of the SCSPP in which an item can feasibly fit onto a strip, i.e.
-the addition of the item onto the strip does not cause the strip's capacity to be exceed.
+the addition of the item onto the strip does not cause the strip's capacity to be exceeded.
 In the original version of FFD, the items on the strip are, as expected, in non-increasing order, and the right-most score width has a value of 3.
@@
 \section{Comparison}
-In order to provide a complete overview of the heuristics, sets of 100, 500, and 1000 items were used on strips of lengths 1500, 2500, and 5000.
+In order to provide a complete overview of the heuristics, sets of 100, 500, and 1000 items were used on strips of lengths 1250, 2500, and 5000.
 Item widths were randomly selected between 150 and 1000, and score widths between 1 and 70.
 This ensures that each item has two score lines.
+Changing the strip lengths changes the average number of items per strip.
+
+\begin{table}[!htb]
+\centering
+\caption{$n = 100$}
+\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
+	\noalign{\smallskip}
+	& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
+	\hline\noalign{\smallskip}
+	$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
+	\noalign{\smallskip}
+	\hline 
+	\noalign{\smallskip}
+	0.0 & 0.119930 & 0.119930 & 0.119930 & 0.234780 & 0.234780 & 0.234780 & 0.464660 & 0.464660 & 0.464660 \\
+	0.1 & 0.190373 & \textbf{0.209209} & 0.195007 & \textbf{0.368315} & 0.403484 & 0.372649 & 0.653776 & 0.662649 & 0.654527 \\
+	0.2 & 0.241823 & \textbf{0.291742} & 0.252201 & \textbf{0.455307} & 0.537355 & 0.464804 & 0.740613 & 0.743163 & 0.74212 \\
+	0.3 & 0.308598 & \textbf{0.423971} & 0.330489 & \textbf{0.552257} & 0.700541 & 0.573676 & 0.817858 & 0.801526 & 0.820929 \\
+	0.4 & 0.387256 & \textbf{0.634770} & 0.435353 & \textbf{0.648313} & 0.860270 & 0.688716 & 0.874070 & 0.835449 & 0.878158 \\
+	0.5 & 0.491093 & \textbf{0.900872} & 0.586398 & \textbf{0.747025} & 0.953757 & 0.806812 & 0.915534 & 0.854677 & 0.920727 \\
+	0.6	& 0.612443 & \textbf{0.982422} & 0.753466 & \textbf{0.834971} & 0.962939 & 0.896095 & 0.939964 & 0.864190 & 0.945036 \\
+	0.7 & 0.773879 & \textbf{0.986985} & 0.909705 & \textbf{0.916026} & 0.965898 & 0.959666 & 0.957970 & 0.873854 & 0.961036 \\
+	0.8	& 0.904347 & \textbf{0.987407} & 0.980250 & 0.966750 & 0.967486 & \textbf{0.984634} & 0.964117 & 0.885786 & 0.965271 \\
+	0.9	& 0.978801 & 0.984535 &	\textbf{0.991745} & 0.987382 & 0.967989 & \textbf{0.990479} & 0.968735 & 0.897915 & 0.968928 \\
+	1.0 & \textbf{0.995493} & 0.988851 & \textbf{0.995493} & \textbf{0.992539} & 0.969239 & \textbf{0.992539} & 0.967834 & 0.904161 & 0.967834 \\
+	\hline
+\end{tabular}
+\label{table:n100}
+\end{table}
+
+\begin{table}[!htb]
+	\centering
+	\caption{$n = 500$}
+	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
+		\noalign{\smallskip}
+		& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
+		\hline\noalign{\smallskip}
+		$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
+		\noalign{\smallskip}
+		\hline
+		\noalign{\smallskip}
+		0.0 & 0.116078 & 0.116078 &	0.116078 & 0.231142 & 0.231142 & 0.231142 & 0.461296 & 0.461296 & 0.461296 \\
+		0.1 & 0.191817 & 0.206796 &	0.193715 & 0.375914 & 0.403863 & 0.376151 & 0.65971 & 0.67634 & 0.659638 \\
+		0.2	& 0.247985 & 0.289553 &	0.251505 & 0.471136 & 0.541779 & 0.471511 & 0.753568 & 0.757848 & 0.753592 \\
+		0.3	& 0.321577 & 0.426852 &	0.329629 & 0.578598 & 0.717203 & 0.585497 & 0.836553 & 0.813063 & 0.837042 \\
+		0.4	& 0.411209 & 0.660488 &	0.436567 & 0.686034 & 0.886587 & 0.709649 & 0.900865 & 0.846469 & 0.902393 \\
+		0.5	& 0.526376 & 0.967058 &	0.597456 & 0.793717 & 0.968396 & 0.838188 & 0.946179 & 0.867053 & 0.950434 \\
+		0.6	& 0.672678 & 0.987213 &	0.805681 & 0.890082 & 0.971239 & 0.935295 & 0.97161 & 0.881001 & 0.976682 \\
+		0.7	& 0.839117 & 0.987909 &	0.959455 & 0.953589 & 0.973028 & 0.981477 & 0.983071 & 0.898796 & 0.986087 \\
+		0.8	& 0.954183 & 0.987787 &	0.991791 & 0.984277 & 0.97413 & 0.992152 & 0.987373 & 0.917181 & 0.988403 \\
+		0.9	& 0.99056 &	0.988561 & 0.995444 & 0.992356 & 0.974811 & 0.993584 & 0.988397 & 0.931674 & 0.988545 \\
+		1.0	& 0.99555 &	0.987811 & 0.99555 & 0.993626 & 0.974892 & 0.993626 & 0.988883 & 0.938649 & 0.988883 \\
+		\hline
+	\end{tabular}
+	\label{table:n500}
+\end{table}
+
+\begin{table}[!htb]
+	\centering
+	\caption{$n = 1000$}
+	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
+		\noalign{\smallskip}
+		& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
+		\hline\noalign{\smallskip}
+		$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
+		\noalign{\smallskip}
+		\hline
+		\noalign{\smallskip}
+		0.0	&0.115534&	0.115534&	0.115534&	0.230563&	0.230563&	0.230563&	0.460623&	0.460623&	0.460623 \\
+		0.1	&0.193119&	0.206222&	0.194298&	0.379134&	0.402463&	0.378162&	0.6614&	0.681008&	0.661144 \\
+		0.2	&0.251658&	0.289114&	0.253138&	0.478121&	0.538655&	0.475984&	0.758956&	0.763423&	0.758428 \\
+		0.3	&0.328699&	0.427652&	0.332872&	0.590141&	0.711773&	0.593915&	0.84551&	0.818874&	0.845116 \\
+		0.4	&0.420561&	0.65769&	0.44084&	0.701106&	0.8834&	0.722513&	0.909988&	0.854863&	0.910882 \\
+		0.5	&0.542993&	0.976737&	0.611842&	0.814597&	0.970731&	0.856799&	0.957862&	0.874602&	0.961627 \\
+		0.6	&0.703725&	0.987923&	0.839692&	0.911433&	0.973308&	0.95286&	0.980911&	0.889836&	0.985533 \\
+		0.7	&0.866696&	0.98822	& 0.974979&	0.966382&	0.974971&	0.987669&	0.98836&	0.907816&	0.990632 \\
+		0.8	&0.968441&	0.988482&	0.993951&	0.989124&	0.976005&	0.993392&	0.991248&	0.927659&	0.991882 \\
+		0.9	&0.99348&	0.988613&	0.995965&	0.993528&	0.97652&	0.994038&	0.992179&	0.944748&	0.992259 \\
+		1.0	&0.995915&	0.988288&	0.995915&	0.994067&	0.976631&	0.994067&	0.992197&	0.948814&	0.992197 \\
+		\hline
+	\end{tabular}
+	\label{table:n1000}
+\end{table}
 
@@
 \end{document}
+
+\begin{comment}
+\begin{table}[!htb]
+\centering
+\caption{n = 100 l = 5000}
+\begin{tabular}{c@{\hspace{20pt}}c@{\hspace{20pt}}c@{\hspace{10pt}}c}
+\hline\noalign{\smallskip}
+$\delta$ & BasicFFD & PairSmallest & FFDincAHCA \\ 
+\noalign{\smallskip}
+\hline
+\noalign{\smallskip}
+0.0 & 0.11993 & 0.11993 & 0.11993 \\ 
+0.1 & 0.190373 & 0.209209 & 0.195007 \\ 
+0.2 & 0.241823 & 0.291742 & 0.252201 \\ 
+0.3 & 0.308598 & 0.423971 & 0.330489 \\ 
+0.4 & 0.387256 & 0.634770 & 0.435353 \\ 
+0.5 & 0.491093 & 0.900872 & 0.586398 \\ 
+0.6 & 0.612443 & 0.982422 & 0.753466 \\
+0.7 & 0.773879 & 0.986985 & 0.909705 \\
+0.8 & 0.904347 & 0.987407 &	0.980250 \\
+0.9 & 0.978801 & 0.984535 &	0.991745 \\
+1.0 & 0.995493 & 0.988851 &	0.995493 \\
+\hline
+\end{tabular}
+%\label{table:100/5000}
+\end{table}	
+\end{comment}

### 2018-03-28 PAPER/main.tex
bold values in table for best optimality

--- 2018-03-23 PAPER/main.tex
@@
 \section{Comparison}
-In order to provide a complete overview of the heuristics, sets of 100, 500, and 1000 items were used on strips of lengths 1500, 2500, and 5000.
+In order to provide a complete overview of the heuristics, sets of 100, 500, and 1000 items were used on strips of lengths 1250, 2500, and 5000.
 Item widths were randomly selected between 150 and 1000, and score widths between 1 and 70.
 This ensures that each item has two score lines.
+Changing the strip lengths changes the average number of items per strip.
+
+\begin{table}[!htb]
+\centering
+\caption{$n = 100$}
+\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
+	\noalign{\smallskip}
+	& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
+	\hline\noalign{\smallskip}
+	$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
+	\noalign{\smallskip}
+	\hline 
+	\noalign{\smallskip}
+	0.0 & 0.119930 & 0.119930 & 0.119930 & 0.234780 & 0.234780 & 0.234780 & 0.464660 & 0.464660 & 0.464660 \\
+	0.1 & 0.190373 & \textbf{0.209209} & 0.195007 & 0.368315 & \textbf{0.403484} & 0.372649 & 0.653776 & \textbf{0.662649} & 0.654527 \\
+	0.2 & 0.241823 & \textbf{0.291742} & 0.252201 & 0.455307 & \textbf{0.537355} & 0.464804 & 0.740613 & \textbf{0.743163} & 0.74212 \\
+	0.3 & 0.308598 & \textbf{0.423971} & 0.330489 & 0.552257 & \textbf{0.700541} & 0.573676 & 0.817858 & 0.801526 & \textbf{0.820929} \\
+	0.4 & 0.387256 & \textbf{0.634770} & 0.435353 & 0.648313 & \textbf{0.860270} & 0.688716 & 0.874070 & 0.835449 & \textbf{0.878158} \\
+	0.5 & 0.491093 & \textbf{0.900872} & 0.586398 & 0.747025 & \textbf{0.953757} & 0.806812 & 0.915534 & 0.854677 & \textbf{0.920727} \\
+	0.6	& 0.612443 & \textbf{0.982422} & 0.753466 & 0.834971 & \textbf{0.962939} & 0.896095 & 0.939964 & 0.864190 & \textbf{0.945036} \\
+	0.7 & 0.773879 & \textbf{0.986985} & 0.909705 & 0.916026 & \textbf{0.965898} & 0.959666 & 0.957970 & 0.873854 & \textbf{0.961036} \\
+	0.8	& 0.904347 & \textbf{0.987407} & 0.980250 & 0.966750 & 0.967486 & \textbf{0.984634} & 0.964117 & 0.885786 & \textbf{0.965271} \\
+	0.9	& 0.978801 & 0.984535 &	\textbf{0.991745} & 0.987382 & 0.967989 & \textbf{0.990479} & 0.968735 & 0.897915 & \textbf{0.968928} \\
+	1.0 & \textbf{0.995493} & 0.988851 & \textbf{0.995493} & \textbf{0.992539} & 0.969239 & \textbf{0.992539} & \textbf{0.967834} & 0.904161 & \textbf{0.967834} \\
+	\hline
+\end{tabular}
+\label{table:n100}
+\end{table}
+
+\begin{table}[!htb]
+	\centering
+	\caption{$n = 500$}
+	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
+		\noalign{\smallskip}
+		& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
+		\hline\noalign{\smallskip}
+		$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
+		\noalign{\smallskip}
+		\hline
+		\noalign{\smallskip}
+		0.0 & 0.116078 & 0.116078 &	0.116078 & 0.231142 & 0.231142 & 0.231142 & 0.461296 & 0.461296 & 0.461296 \\
+		0.1 & 0.191817 & \textbf{0.206796} & 0.193715 & 0.375914 & \textbf{0.403863} & 0.376151 & 0.65971 & \textbf{0.67634} & 0.659638 \\
+		0.2	& 0.247985 & \textbf{0.289553} & 0.251505 & 0.471136 & \textbf{0.541779} & 0.471511 & 0.753568 & \textbf{0.757848} & 0.753592 \\
+		0.3	& 0.321577 & \textbf{0.426852} & 0.329629 & 0.578598 & \textbf{0.717203} & 0.585497 & 0.836553 & 0.813063 & \textbf{0.837042} \\
+		0.4	& 0.411209 & \textbf{0.660488} & 0.436567 & 0.686034 & \textbf{0.886587} & 0.709649 & 0.900865 & 0.846469 & \textbf{0.902393} \\
+		0.5	& 0.526376 & \textbf{0.967058} & 0.597456 & 0.793717 & \textbf{0.968396} & 0.838188 & 0.946179 & 0.867053 & \textbf{0.950434} \\
+		0.6	& 0.672678 & \textbf{0.987213} & 0.805681 & 0.890082 & \textbf{0.971239} & 0.935295 & 0.97161 & 0.881001 & \textbf{0.976682} \\
+		0.7	& 0.839117 & \textbf{0.987909} & 0.959455 & 0.953589 & 0.973028 & \textbf{0.981477} & 0.983071 & 0.898796 & \textbf{0.986087} \\
+		0.8	& 0.954183 & 0.987787 &	\textbf{0.991791} & 0.984277 & 0.97413 & \textbf{0.992152} & 0.987373 & 0.917181 & \textbf{0.988403} \\
+		0.9	& 0.99056 &	0.988561 & \textbf{0.995444} & 0.992356 & 0.974811 & \textbf{0.993584} & 0.988397 & 0.931674 & \textbf{0.988545} \\
+		1.0	& \textbf{0.99555} & 0.987811 & \textbf{0.99555} & \textbf{0.993626} & 0.974892 & \textbf{0.993626} & \textbf{0.988883} & 0.938649 & \textbf{0.988883} \\
+		\hline
+	\end{tabular}
+	\label{table:n500}
+\end{table}
+
+\begin{table}[!htb]
+	\centering
+	\caption{$n = 1000$}
+	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
+		\noalign{\smallskip}
+		& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
+		\hline\noalign{\smallskip}
+		$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
+		\noalign{\smallskip}
+		\hline
+		\noalign{\smallskip}
+		0.0	&0.115534&	0.115534&	0.115534&	0.230563&	0.230563&	0.230563&	0.460623&	0.460623&	0.460623 \\
+		0.1	&0.193119&	\textbf{0.206222} &	0.194298&	0.379134&	\textbf{0.402463}&	0.378162&	0.6614&	\textbf{0.681008}&	0.661144 \\
+		0.2	&0.251658&	\textbf{0.289114} &	0.253138&	0.478121&	\textbf{0.538655}&	0.475984&	0.758956&	\textbf{0.763423}&	0.758428 \\
+		0.3	&0.328699&	\textbf{0.427652} &	0.332872&	0.590141&	\textbf{0.711773}&	0.593915&	\textbf{0.84551}&	0.818874&	0.845116 \\
+		0.4	&0.420561&	\textbf{0.65769} &	0.44084&	0.701106&	\textbf{0.8834}&	0.722513&	0.909988&	0.854863&	\textbf{0.910882} \\
+		0.5	&0.542993&	\textbf{0.976737} &	0.611842&	0.814597&	\textbf{0.970731}&	0.856799&	0.957862&	0.874602&	\textbf{0.961627} \\
+		0.6	&0.703725&	\textbf{0.987923} &	0.839692&	0.911433&	\textbf{0.973308}&	0.95286&	0.980911&	0.889836&	\textbf{0.985533} \\
+		0.7	&0.866696&	\textbf{0.98822} 	& 0.974979&	0.966382&	0.974971&	\textbf{0.987669}&	0.98836&	0.907816&	\textbf{0.990632} \\
+		0.8	&0.968441&	0.988482& \textbf{0.993951} &	0.989124&	0.976005&	\textbf{0.993392}&	0.991248&	0.927659&	\textbf{0.991882} \\
+		0.9	&0.99348&	0.988613& \textbf{0.995965} &	0.993528&	0.97652&	\textbf{0.994038}&	0.992179&	0.944748&	\textbf{0.992259} \\
+		1.0	& \textbf{0.995915} & 0.988288&	\textbf{0.995915} &	\textbf{0.994067}&	0.976631&	\textbf{0.994067}&	\textbf{0.992197}&	0.948814&	\textbf{0.992197} \\
+		\hline
+	\end{tabular}
+	\label{table:n1000}
+\end{table}
 

### 2018-03-28 SCSPP/COMBINED/main.cpp
added Timer to each case

@@ -31,7 +31,9 @@ struct Timer{
         totalTime = endTime - startTime;
 
         float totalTimems = totalTime.count() * 1000.0f;
-        cout << "\nCPU Time: " << totalTimems << "ms (" << totalTime.count() << "s)\n[END OF PROGRAM]\n" << endl;
+        //cout << "\nCPU Time: " << totalTimems << "ms (" << totalTime.count() << "s)" << endl;
+        cout << totalTime.count() << endl;
+        //cout << totalTimems << endl;
     }
 };
 
@@ -225,57 +227,63 @@ int main(int argc, char **argv){
     vector<int> bestSolnStartSum;
     double bestFitness = 0.0;
     double tempFitness;
-    double totalOpt = 0.0;
-    double avgOpt;
     vector<int> alpha = { 145, 109, 97, 87, 79, 72, 65, 57, 47, 34, 0 };
 
     srand(randomSeed);
 
-    Timer timer;
+    //Timer timer;
 
     switch(algType){
         case 1:
             for(a = 0; a < alpha.size(); ++a) {
                 tau = alpha[a];
-                for (instance = 0; instance < numInstances; ++instance) {
-                    CreateInstance(tau, numScores, numItem, minWidth, maxWidth, minItemWidth, maxItemWidth, totalItemWidth, allScores, partners, adjMatrix, itemWidths);
-                    BasicFFD(totalOpt, opt, opt90, opt80, opt70, opt60, opt50, optLow, numScores, numItem, maxItemWidth, stripLength, totalItemWidth, allScores, partners, adjMatrix, itemWidths, stripSum, strip);
-                    ResetVar(numScores, numItem, allScores, partners, adjMatrix, itemWidths, stripSum, strip);
+                {
+                    Timer timer;
+                    for (instance = 0; instance < numInstances; ++instance) {
+                        CreateInstance(tau, numScores, numItem, minWidth, maxWidth, minItemWidth, maxItemWidth,
+                                       totalItemWidth, allScores, partners, adjMatrix, itemWidths);
+                        BasicFFD(opt, opt90, opt80, opt70, opt60, opt50, optLow, numScores, numItem, maxItemWidth,
+                                 stripLength, totalItemWidth, allScores, partners, adjMatrix, itemWidths, stripSum,
+                                 strip);
+                        ResetVar(numScores, numItem, allScores, partners, adjMatrix, itemWidths, stripSum, strip);
+                    }
                 }
[…]

### 2018-03-28 SCSPP/COMBINED/packing.cpp
removed totalOpt variable

@@ -67,7 +67,7 @@ void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &o
 } //End Optimality
 
 // FFD checking vicinal sum constraint for both sides of each item.
-void BasicFFD(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
+void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
               int stripLength, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
               vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
     int i, j, mini;
@@ -132,10 +132,6 @@ void BasicFFD(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70, in
     int stripSize = strip.size();
     int LB = LowerBound(stripLength, totalItemWidth);
 
-    double c = static_cast<double>(LB) / stripSize;
-    totalOpt += c;
-
-
     //double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
 
     //cout << "Lower Bound: " << LB << endl;
@@ -152,7 +148,7 @@ void BasicFFD(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70, in
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void PairSmallest(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int stripLength,
+void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int stripLength,
                   double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
                   vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
     int i, j;
@@ -216,9 +212,6 @@ void PairSmallest(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70
     int stripSize = strip.size();
     int LB = LowerBound(stripLength, totalItemWidth);
 
[…]

### 2018-03-28 SCSPP/COMBINED/packing.h

@@ -20,19 +20,19 @@ double Fitness(int stripLength, vector<int> &stripSum, vector<vector<int> > &str
 
 void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB);
 
-void BasicFFD(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
+void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
               int stripLength, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
               vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void PairSmallest(double &totalOpt, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
+void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
                   int stripLength, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
                   vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // FFD including AHCA, instead of attempting to place item on end of strip, run AHCA to find feasible solution.
-void FFDincAHCA(double &totalOpt, int tau, int &opt, int &opt90, int &opt80, int &opt70,
+void FFDincAHCA(int tau, int &opt, int &opt90, int &opt80, int &opt70,
                 int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth, int stripLength, double totalItemWidth,
                 vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum,
                 vector<vector<int> > &strip);

### 2018-03-29 PAPER/main.tex
added bullet points comparison

@@
 		0.2	&0.251658&	\textbf{0.289114} &	0.253138&	0.478121&	\textbf{0.538655}&	0.475984&	0.758956&	\textbf{0.763423}&	0.758428 \\
-		0.3	&0.328699&	\textbf{0.427652} &	0.332872&	0.590141&	\textbf{0.711773}&	0.593915&	\textbf{0.84551}&	0.818874&	0.845116 \\
+		0.3	&0.328699&	\textbf{0.427652} &	0.332872&	0.590141&	\textbf{0.711773}&	0.593915&	0.84501&	0.818874&	\textbf{0.845116} \\
 		0.4	&0.420561&	\textbf{0.65769} &	0.44084&	0.701106&	\textbf{0.8834}&	0.722513&	0.909988&	0.854863&	\textbf{0.910882} \\
@@
 \end{table}
+
+\begin{itemize}
+	\item Uniform distribution
+	\item only $n = 500$, the other two show the exact same trend, no need for unecessary data. 
+	\item $n = 500$, avg total item widths per instance (sum of all item widths) = 287684
+	\item $l = 5000$, avg lower bound = 58.039, avg items/strip = 8.62069
+	\item $l = 2500$, avg lower bound = 115.571, avg items/strip = 4.31034
+	\item $l = 1250$, avg lower bound = 230.648, avg items/strip = 2.16450
+	\item all items have height $h = 1$, strips have height $h = 1$
+	\item changing the value of $\tau$ changes the proportion of the number of score widths that meet the vicinal sum constraint, excluding itself and its partner
+	\item parameter $\delta$ defines the proportion, in 0.1 increments
+	\item if $\delta = 0.0$, then no score widths can be aligned, no matchings exist, each item requires its own strip, number of strips = $n$
+	\item if $\delta = 1.0$, then all score widths can be aligned with any other score width, problem becomes analogous to the classical one-dimensional BPP.
+	\item \cite{lewis2011}
+	\item As the strip length is decreased, ffd+ improves, number of items/strip decreases
+	\item basicffd never excels over the other two heuristics, only equals ffd+, since when $\delta = 1.0$, the problem is the same as a normal bpp, and so basicffd and ffd+ will perform in the same manner (standard ffd)
+	\item Pairsmallest does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
+\end{itemize}
 

### 2018-03-30 SCSPP/COMBINED/main.cpp
changed vector alpha to delta

@@ -6,7 +6,6 @@ Combined Program with Heuristics and EA
 /--------------*/
 
 #include <iostream>
-#include <fstream>
 #include <cmath>
 #include <cstring>
 #include <ctime>
@@ -227,7 +226,7 @@ int main(int argc, char **argv){
     vector<int> bestSolnStartSum;
     double bestFitness = 0.0;
     double tempFitness;
-    vector<int> alpha = { 145, 109, 97, 87, 79, 72, 65, 57, 47, 34, 0 };
+    vector<int> delta = { 145, 109, 97, 87, 79, 72, 65, 57, 47, 34, 0 };
 
     srand(randomSeed);
 
@@ -235,8 +234,8 @@ int main(int argc, char **argv){
 
     switch(algType){
         case 1:
-            for(a = 0; a < alpha.size(); ++a) {
-                tau = alpha[a];
+            for (a = 0; a < delta.size(); ++a) {
+                tau = delta[a];
                 {
                     Timer timer;
                     for (instance = 0; instance < numInstances; ++instance) {
@@ -248,13 +247,14 @@ int main(int argc, char **argv){
                         ResetVar(numScores, numItem, allScores, partners, adjMatrix, itemWidths, stripSum, strip);
                     }
                 }
+
                 //Output(opt, opt90, opt80, opt70, opt60, opt50, optLow, numInstances);
             }
             break;
 
         case 2:
-            for(a = 0; a < alpha.size(); ++a) {
-                tau = alpha[a];
+            for (a = 0; a < delta.size(); ++a) {
+                tau = delta[a];
                 {
                     Timer timer;
                     for (instance = 0; instance < numInstances; ++instance) {
@@ -270,8 +270,8 @@ int main(int argc, char **argv){
             break;
 
         case 3:
-            for(a = 0; a < alpha.size(); ++a) {
-                tau = alpha[a];
+            for (a = 0; a < delta.size(); ++a) {
+                tau = delta[a];
                 {
                     Timer timer;
                     for (instance = 0; instance < numInstances; ++instance) {
@@ -289,7 +289,7 @@ int main(int argc, char **argv){
 
         case 4:
             CreateInstance(tau, numScores, numItem, minWidth, maxWidth, minItemWidth, maxItemWidth, totalItemWidth, allScores, partners, adjMatrix, itemWidths);
-            int LB = LowerBound(stripLength, totalItemWidth);
+            int LB = LowerBound(totalItemWidth, stripLength);
[…]

### 2018-03-30 SCSPP/COMBINED/packing.cpp
changed order of parameters in LowerBound function

@@ -16,7 +16,7 @@ void Swap(int &a, int &b){
     b = temp;
 }
 
-int LowerBound(int stripLength, double totalItemWidth){
+int LowerBound(double totalItemWidth, int stripLength){
     int lBound;
 
     lBound = ceil(totalItemWidth/stripLength);
@@ -129,8 +129,8 @@ void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
         strip.pop_back();
     }
 
-    int stripSize = strip.size();
-    int LB = LowerBound(stripLength, totalItemWidth);
+    //int stripSize = strip.size();
+    //int LB = LowerBound(totalItemWidth, stripLength);
 
     //double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
 
@@ -142,7 +142,7 @@ void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
     //cout << stripSize << endl;
     //cout << avg << endl;
 
-    Optimality(opt, opt90, opt80, opt70, opt60, opt50, optLow, stripSize, LB);
+    //Optimality(opt, opt90, opt80, opt70, opt60, opt50, optLow, stripSize, LB);
 
 } //End BasicFFD
 
@@ -209,8 +209,8 @@ void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int 
         strip.pop_back();
     }
 
-    int stripSize = strip.size();
-    int LB = LowerBound(stripLength, totalItemWidth);
+    //int stripSize = strip.size();
+    //int LB = LowerBound(totalItemWidth, stripLength);
 
     //double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
 
@@ -222,7 +222,7 @@ void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int 
     //cout << stripSize << endl;
     //cout << avg << endl;
 
-    Optimality(opt, opt90, opt80, opt70, opt60, opt50, optLow, stripSize, LB);
+    //Optimality(opt, opt90, opt80, opt70, opt60, opt50, optLow, stripSize, LB);
 
 } //End PairSmallest
 
@@ -286,8 +286,9 @@ void FFDincAHCA(int tau, int &opt, int &opt90, int &opt80, int &opt70, int &opt6
         stripSum.pop_back();
         strip.pop_back();
     }
[…]

### 2018-03-30 SCSPP/COMBINED/packing.h

@@ -14,7 +14,7 @@ using namespace std;
 
 void Swap(int &a, int &b);
 
-int LowerBound(int stripLength, double totalItemWidth);
+int LowerBound(double totalItemWidth, int stripLength);
 
 double Fitness(int stripLength, vector<int> &stripSum, vector<vector<int> > &strip);
 

### 2018-03-30 PAPER/main.tex
changed values in example of CPOP

@@
 
-For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,5\}, \{2,4\}, \{3,4\}, \{4,5\}\}$ and $\tau = 7$, one possible feasible solution is $\mathcal{T} = \langle(1,2), (5,4), (3,4), (4,2), (5,1) \rangle$.
+For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,6\}, \{2,3\}, \{3,5\}, \{4,4\}, \{4,5\}\}$ and $\tau = 7$, one possible feasible solution is $\mathcal{T} = \langle(1,2), (5,4), (4,4), (3,5), (3,2), (6,1) \rangle$.
 

### 2018-04-02 SCSPP/COMBINED/main.cpp
added lines for outputting results to txt file (commented out)

@@ -6,6 +6,7 @@ Combined Program with Heuristics and EA
 /--------------*/
 
 #include <iostream>
+#include <fstream>
 #include <cmath>
 #include <cstring>
 #include <ctime>
@@ -227,15 +228,20 @@ int main(int argc, char **argv){
     double bestFitness = 0.0;
     double tempFitness;
     vector<int> delta = { 145, 109, 97, 87, 79, 72, 65, 57, 47, 34, 0 };
+    //double Delta = 0.0;
 
-    srand(randomSeed);
+    //srand(randomSeed);
 
     //Timer timer;
 
     switch(algType){
-        case 1:
+        case 1: {
+            /*ofstream results("1k1kbf.txt");
+            results << numItem << "\t" << stripLength << "\tBasic" << endl;
+            results.close();*/
             for (a = 0; a < delta.size(); ++a) {
                 tau = delta[a];
+                srand(randomSeed);
                 {
                     Timer timer;
                     for (instance = 0; instance < numInstances; ++instance) {
@@ -244,17 +250,32 @@ int main(int argc, char **argv){
                         BasicFFD(opt, opt90, opt80, opt70, opt60, opt50, optLow, numScores, numItem, maxItemWidth,
                                  stripLength, totalItemWidth, allScores, partners, adjMatrix, itemWidths, stripSum,
                                  strip);
+                        /*int lb = LowerBound(totalItemWidth, stripLength);
+                        double opt = static_cast<double>(strip.size()) / static_cast<double>(lb);
+                        double itemPerStrip = static_cast<double>(numItem) / static_cast<double>(strip.size());
+                        results.open("1k1kbf.txt", ios::app);
+                        results << Delta << "\t" << totalItemWidth << "\t" << lb << "\t" << strip.size() << "\t" << itemPerStrip << "\t" << opt << endl;
+                        results.close();*/
                         ResetVar(numScores, numItem, allScores, partners, adjMatrix, itemWidths, stripSum, strip);
                     }
                 }
-
+                /*results.open("1k1kbf.txt", ios::app);
+                results << endl << endl << endl;
+                results.close();
+                Delta += 0.1;*/
                 //Output(opt, opt90, opt80, opt70, opt60, opt50, optLow, numInstances);
             }
+        }
             break;
 
-        case 2:
+        case 2: {
+            /*ofstream results("1k1kps.txt");
[…]

### 2018-04-04 PAPER/main.tex
added figures
changed example, changed figure sizes

--- 2018-03-29 PAPER/main.tex
@@
 \institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
-\date{\today}
 
@@
 
-For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,5\}, \{2,4\}, \{3,4\}, \{4,5\}\}$ and $\tau = 7$, one possible feasible solution is $\mathcal{T} = \langle(1,2), (5,4), (3,4), (4,2), (5,1) \rangle$.
+For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, one possible feasible solution is $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.
 
@@
 
+\begin{figure}	
+\centering
+\begin{subfigure}[h]{0.45\textwidth}
+	\includestandalone[width=\textwidth]{figures/partners}
+	\caption{\textcolor{red}{partners.}}	
+	\label{fig:partners}
+\end{subfigure} \hspace{40pt}
+\begin{subfigure}[h]{0.45\textwidth}
+	\includestandalone[width=\textwidth]{figures/threshold}
+	\caption{\textcolor{red}{threshold.}}	
+	\label{fig:threshold}
+\end{subfigure}
+\caption{$v_0 = 1, v_1 = 1, v_2 = 2, v_3 = 2, v_4 = 3, v_5 = 3, v_6 = 4, v_7 = 4, v_8 = 4, v_9 = 5, v_{10} = 6, v_{11} = 7, v_{12} = 7, v_{13} = 7$}
+\end{figure}
+
 The following definition describes a variant of the classical Hamiltonian cycle on a graph $G$.
@@
 
+\begin{figure}	
+	\centering
+	\begin{subfigure}[h]{0.4\textwidth}
+		\includestandalone[width=\textwidth]{figures/matching}
+		\caption{\textcolor{red}{matching.}}	
+		\label{fig:matching}
+	\end{subfigure} \quad
+	\begin{subfigure}[h]{0.5\textwidth}
+		\includestandalone[width=\textwidth]{figures/mps}
+		\caption{\textcolor{red}{mps}}	
+		\label{fig:mps}
+	\end{subfigure}
+	\caption{main caption}
+\end{figure}
+
 Clearly, if $|Q| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $P$, and hence in accordance with Theorem $\ref{thm:cpopsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the CPOP.
@@
 Any edges that do not connect the smaller vertex to the largest possible vertex, due to the largest vertex being its partner, are also removed.
-the Starting from the first edge, BR searches through the list to find an edge that meets the following conditions:
+Then, starting from the first edge, BR searches through the list to find an edge that meets the following conditions:
 \begin{enumerate}

### 2018-04-06 PAPER/main.tex
changed intro to section 2

@@
 
-Firstly, let us introduce the Constrained Pair-Ordering Problem:
+Firstly, let us introduce the Constrained Ordering Problem:
 
@@
 	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple.
-The Constrained Pair-Ordering Problem (CPOP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
+The Constrained Ordering Problem (COP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
 	\begin{equation}
@@
 
-One prominent application of the CPOP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004.
-A set $\mathcal{I}$ of rectangular items of equal height $h$ made from cardboard are to be packed onto a strip from left to right.
+One prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004.
+A set $\mathcal{I}$ of rectangular items of equal height $h$ made from cardboard are to be packed onto a strip of heigh $h$ from left to right.
 Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places.
@@
 Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively.
-Clearly, for two items to be placed alongside one another feasibly the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
+Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
 Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
-Specifically, as the items are packed from left to right, this involved checking the sum of the right-hand score width of each item $i$ and the left-hand score width of the next item $i+1$ on the strip.
+Specifically, as the items are packed from left to right, this involves checking the sum of the right-hand score width of each item $i$ and the left-hand score width of the next item $i+1$ on the strip.
 The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.
@@
 
-It can be seen that this problem is in fact analogous to the CPOP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance.
-Thus, a set $\mathcal{I}$ of items has a feasible arrangement if the equivalent CPOP has a solution $\mathcal{T}$ that meets the vicinal sum constraint.
+It can be seen that this problem is in fact analogous to the COP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance.
+Thus, a set $\mathcal{I}$ of items has a feasible arrangement if the equivalent COP has a solution $\mathcal{T}$ that meets the vicinal sum constraint.
 
 Observe that, in this particular strip-packing problem, the widths of the individual items are disregarded entirely, since the aim is to arrange the items onto a strip of seemingly infinite length.
-In reality, strips of material are provided in fixed lengths.
-Given a large problem instance, multiple strips may be required to feasibly accommodate all of the items.
+In practical applications, strips of material are often provided in fixed lengths.
+Given a large problem instance, multiple strips may therefore be required to feasibly accommodate all of the items.
 For this reason, we define a new problem to be investigated.
@@
 
-The remainder of this article will firstly, in Section 2, detail a polynomial-time algorithm that is able to produce a solution to any instance of the CPOP, if a solution exists.
+The remainder of this article will firstly, in Section 2, detail a polynomial-time algorithm that is able to produce a solution to any instance of the COP, if a solution exists.
 Section 3 describes the heuristics that will be used to find feasible solutions to the SCSPP, and discusses the associated advantages and disadvantages.
@@
 
-We shall now present an algorithm for solving the CPOP, which operates by expressing the problem instance graphically.
+%We shall now present an algorithm for solving the COP, which operates by expressing the problem instance graphically. 
+We shall now present an algorithm for solving the COP in polynomial time.
+The original(underlying) algorithm was created by \cite{becker2010}, and determines whether or not a solution exists for a given instance.
+We have extended this algorithm so that, if a solution does indeed exist, the algorithm is able to formulate and present us with this final solution.
+This is especially useful for problems such as the previously mentioned strip-packing problem, where a tangible solution is required in order to place the items in the correct order and orientation.
 
-Let $\mathcal{M}$ be an instance of the CPOP of cardinality $n$ as described in Definition \ref{defn:cpop}.
-Then, the graph $G$ is defined by a vertex set $V = \{v_1, v_2, ...v_{2n+2}\}$, where each vertex is assigned a value from $\mathcal{M}$ such that $v_1 \leq v_2 \leq ...
+Let $\mathcal{M}$ be an instance of the COP of cardinality $n$ as described in Definition \ref{defn:cpop}.
+Then, a graph $G$ is defined by a vertex set $V = \{v_1, v_2, ...v_{2n+2}\}$, where each vertex is assigned a value from $\mathcal{M}$ such that $v_1 \leq v_2 \leq ...
 \leq v_{2n+2}$.
@@
 Thus, let $p: V \to V$ be a bijective function that associates each vertex $v_i \in V$ on $G$ with its partner, $v_j = p(v_i)$.
-$G$ comprises two distinct edge sets: $P$, which contains edges between vertices that are partners, and $E$, which consists of edges between vertices whose corresponding values in $\mathcal{M}$ can be arranged alongside one another.
+$G$ comprises two distinct edge sets: $B$, which contains edges between vertices that are partners, and $R$, which consists of edges between vertices whose corresponding values in $\mathcal{M}$ can be arranged alongside one another.
 That is, for two distinct vertices $v_i, v_j$,
@@
 provided $p(v_i) \neq v_j$.
-Hence, $G(V, P \cup E)$ is an undirected graph with $2n + 2$ vertices and edge sets $P$ and $E$, such that $P \cap E = \emptyset$.
-Observe that $P$ is in fact a perfect matching, with $|P|= n+1$.
+Hence, $G=(V, B \cup R)$ is an undirected graph with $2n + 2$ vertices and edge sets $B$ and $R$, such that $B \cap R = \emptyset$.
+Observe that $B$ is in fact a perfect matching, with $|B|= n+1$.
 
@@
 
-The following definition describes a variant of the classical Hamiltonian cycle on a graph $G$.
+The following definition now describes a variant of the classical Hamiltonian cycle on a graph $G$.
 
@@
 	\label{defn:althamcycle}
-	Let $G(V, P\cup E)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $E$.
-$G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such successive edges alternate between sets $P$ and $E$.
-For example, if $(v_{i-1}, v_i) \in P$, then $(v_i, v_{i+1}) \in E$, or vice versa.
+	Let $G(V, B\cup R)$ be an undirected graph, where each edge is a member of one of two sets, $B$ or $R$.
+$G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such that successive edges alternate between sets $B$ and $R$.
+For example, if $(v_{i-1}, v_i) \in B$, then $(v_i, v_{i+1}) \in R$, or vice versa.
 \end{definition}
@@
 	\label{thm:cpopsoln}
-	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the CPOP if and only if its corresponding graph $G(V, P\cup E)$ contains an alternating Hamiltonian cycle.
+	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the COP if and only if its corresponding graph $G(V, B\cup R)$ contains an alternating Hamiltonian cycle.
 \end{theorem}
@@
 	Let $\mathcal{A} = \{v_1, v_2, ..., v_{2n+1}, v_{2n+2}\}$ be an alternating Hamiltonian cycle on $G$, where $v_{2n+1}$ and $v_{2n+2}$ are the dominating vertices.
-By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $P$.
-Thus, there exists a set of $n+1$ edges from $E$ that, together with the edges in $P$, form the alternating Hamiltonian cycle.
-Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $P$.
+By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $B$.
+Thus, there exists a set of $n+1$ edges from $R$ that, together with the edges in $B$, form the alternating Hamiltonian cycle.
+Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $B$.
 The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple.
-\textcolor{OrangeRed}{edges E vicinal sum constraint equation 2}.
+\textcolor{OrangeRed}{edges R vicinal sum constraint equation 2}.
 \qed
@@
 Therefore, the aim of this algorithm is to construct an alternating Hamiltonian cycle on $G$.
-Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, every edge in $P$ must be present in the alternating Hamiltonian cycle.
-Consequently, the task now involves finding a matching $Q \subset E$ of cardinality $n+1$, such that the edge sets $P$ and $Q$ form an alternating Hamiltonian cycle as described in Definition $\ref{defn:althamcycle}$.
+Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, every edge in $B$ must be present in the alternating Hamiltonian cycle.
+Consequently, the task now involves finding a matching $R' \subseteq R$ of cardinality $n+1$, such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition $\ref{defn:althamcycle}$.
 
-To find a matching $Q \subset E$, the following modified maximum cardinality matching (MMCM) algorithm is executed (\citealp{mahadev1994, becker2010}): for each vertex $v_i$, $i = 1, 2,...,2n+2$, find the largest vertex $v_j \in \Gamma(v_i)\backslash p(v_i)$ (i.e.
-the largest vertex $v_j$ in $v_i$'s neighbourhood that is not $v_i$'s partner) that is not incident to any edge in $Q$.
-Add the edge connecting these two vertices to $Q$, and proceed to the next vertex until all vertices have been assessed.
-The pair of vertices incident to each edge in $Q$ are referred to as being ``matched'', and are connected by a ``matching'' edge.
+To find a matching $R' \subseteq R$, the following modified maximum cardinality matching (MMCM) algorithm is executed (\citealp{mahadev1994, becker2010}): for each vertex $v_i$, $i = 1, 2,...,2n+2$, find the largest vertex $v_j \in \Gamma(v_i)\backslash p(v_i)$ (i.e.
+the largest vertex $v_j$ in $v_i$'s neighbourhood that is not $v_i$'s partner) that is not incident to any edge in $R'$.
+Add the edge connecting these two vertices to $R'$, and proceed to the next vertex until all vertices have been assessed.
+The pair of vertices incident to each edge in $R'$ are referred to as being ``matched'', and are connected by a ``matching'' edge.
 
-During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided $v_i$ is not the first vertex (i.e $i \neq 1$), $v_{i-1}$ has been matched, and $(v_{i-1}, p(v_i)) \in E$.
+During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided $v_i$ is not the first vertex (i.e $i \neq 1$), $v_{i-1}$ has been matched, and $(v_{i-1}, p(v_i)) \in R$.
 Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$.
-It is guaranteed that MMCM will produce a maximum cardinality matching $Q \subset E$, and is able to do so in at most $O(n \log n)$ time.
+It is guaranteed that MMCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time.
 
@@
 
-Clearly, if $|Q| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $P$, and hence in accordance with Theorem $\ref{thm:cpopsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the CPOP.
-Otherwise, if $Q$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'(V, P \cup Q)$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $P$, and its match via an edge in $Q$.
+Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence in accordance with Theorem $\ref{thm:cpopsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
+Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$.
 $G'$ thus consists of a collection of alternating cycles $A_1, A_2, ..., A_{\lambda}$.
@@
 For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle.
-The algorithm thus executes a Bridge Recognition (BR) procedure that selects suitable edges in $E$ to be used as bridges between the components of $G'$, and will replace certain edges in $Q$.
+The algorithm thus executes a Bridge Recognition (BR) procedure that selects suitable edges in $R$ to be used as bridges between the components of $G'$, and will replace certain edges in $R'$.
 
-For each edge $(v_i, v_j) \in Q$, where $i < j$, $v_i$ is referred to as the ``smaller'' vertex, and $v_j$ as the ``larger'' vertex, since the value associated with $v_i$ is less than or equal to the value associated with $v_j$.
-The procedure initially sorts the edges in $Q$ into a list such that the smaller vertices of the edges are in lexicographical order, and therefore in non-decreasing order of values.
+For each edge $(v_i, v_j) \in R'$, where $i < j$, $v_i$ is referred to as the ``smaller'' vertex, and $v_j$ as the ``larger'' vertex, since the value associated with $v_i$ is less than or equal to the value associated with $v_j$.
+The procedure initially sorts the edges in $R'$ into a list such that the smaller vertices of the edges are in lexicographical order, and therefore in non-decreasing order of values.
 Any edges whose smaller vertices, during MMCM, were unable to be matched with the largest possible vertex available due to being partners are then removed from this list.
@@
 \begin{enumerate}
-	\item The smaller vertex of the current edge and the larger vertex of the succeeding edge are connected by an edge in $E$.
+	\item The smaller vertex of the current edge and the larger vertex of the succeeding edge are connected by an edge in $R$.
 	\item The current edge and the succeeding edge are members of different components on $G'$.
@@
 
-If such an edge is found, the procedure adds this edge to a set $C_i$, and continues to add all succeeding edges in the list to $C_i$, provided that for each edge conditions 1 and 2 hold, and the succeeding edge is not a member of a component on $G'$ that already has an edge in $C_i$.
-Once there are no more valid edges to add to $C_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets conditions 1 and 2, and can therefore start a new set $C_{i+1}$.
+If such an edge is found, the procedure adds this edge to a set $R_i$, and continues to add all succeeding edges in the list to $R_i$, provided that for each edge conditions 1 and 2 hold, and the succeeding edge is not a member of a component on $G'$ that already has an edge in $R_i$.
+Once there are no more valid edges to add to $R_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets conditions 1 and 2, and can therefore start a new set $R_{i+1}$.
 The procedure ends when the penultimate edge in the list has been examined.
 
-The sets $C_1, C_2, ..., C_k$ created during this process are then analysed.
-In the event that BR has been unable to produce a single set $C$, the components $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
-If there exists a set $C_i$ such that $|C_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':
+The sets $R_1, R_2, ..., R_k \subseteq R$ created during this process are then analysed.
+In the event that BR has been unable to produce a single set $R_1$, the components $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
+If there exists a set $R_i$ such that $|R_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':
 
-Starting from the first edge in $C_i$, add the edge from $E$ connecting the smaller vertex of each edge to the larger vertex of the succeeding edge to $Q$.
-For the final edge in $C_i$, add the edge from $E$ that connects its smaller vertex to the larger vertex of the first edge in $C_i$ to $Q$.
-Finally, any edges that appear in both $C_i$ and $Q$ are removed from $Q$, such that $C_i \cap Q = \emptyset$, and $Q$ returns to being a perfect matching.
+Starting from the first edge in $R_i$, add the edge from $R$ connecting the smaller vertex of each edge to the larger vertex of the succeeding edge to $R'$.
+For the final edge in $R_i$, add the edge from $R$ that connects its smaller vertex to the larger vertex of the first edge in $R_i$ to $R$.
+Finally, any edges that appear in both $R_i$ and $R'$ are removed from $R'$, such that $R_i \cap R' = \emptyset$, and $R'$ returns to being a perfect matching.
 $G'$ then comprises a single alternating Hamiltonian cycle, and thus the algorithm has found a solution to the problem instance.
@@
 Else, if $k > 1$, it may be that multiple sets are required to combine the components of $G'$.
-Let $\mathcal{C}$ be a set that contains the sets $C_i$ needed to connect the components of $G'$ together, and let $\Lambda$ be a set that records the components covered by the sets in $\mathcal{C}$.
-Start by adding the components $A_i$ that each edge in $C_1$ is a member of to $\Lambda$, and then add $C_1$ to $\mathcal{C}$.
-At this stage, $|\Lambda| = |\mathcal{C}|$.
-Proceeding through the remaining sets $C_2, C_3, ..., C_k$, find a set $C_i$ that contains at least one edge that is a member of a component in $\Lambda$, and at least one edge that is a member of a component not yet recorded in $\Lambda$.
-Append the component that each edge in this set $C_i$ is a member of to $\Lambda$, provided the component is not already an element of $\Lambda$, then add $C_i$ to $\mathcal{C}$.
-Continue in this manner until the final set $C_k$ has been assessed.
+Let $\mathcal{R}$ be a set that contains the sets $R_i$ needed to connect the components of $G'$ together, and let $\Lambda$ be a set that records the components covered by the sets in $\mathcal{R}$.
+Start by adding the components $A_i$ that each edge in $R_1$ is a member of to $\Lambda$, and then add $R_1$ to $\mathcal{R}$.
+At this stage, $|\Lambda| = |\mathcal{R}|$.
+Proceeding through the remaining sets $R_2, R_3, ..., R_k$, find a set $R_i$ that contains at least one edge that is a member of a component in $\Lambda$, and at least one edge that is a member of a component not yet recorded in $\Lambda$.
+Append the component that each edge in this set $R_i$ is a member of to $\Lambda$, provided the component is not already an element of $\Lambda$, then add $R_i$ to $\mathcal{R}$.
+Continue in this manner until the final set $R_k$ has been assessed.
 If $|\Lambda| = \lambda$, i.e.
-all components of $G'$ are elements of $\Lambda$, then the sets in $\mathcal{C}$ are able to combine the components of $G'$ to form a single alternating Hamiltonian cycle.
-This is achieved by repeating the connecting method described previously on every set $C_i \in \mathcal{C}$.
+all components of $G'$ are elements of $\Lambda$, then the sets in $\mathcal{R}$ are able to combine the components of $G'$ to form a single alternating Hamiltonian cycle.
+This is achieved by repeating the connecting method described previously on every set $R_i \in \mathcal{R}$.
 
-This algorithm, which will be referred to as the Alternating Hamiltonian Construction Algorithm (AHCA) is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the CPOP.
+This algorithm, which will be referred to as the Alternating Hamiltonian Construction Algorithm (AHCA) is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP.
 If a solution does indeed exist, AHCA can produce this solution in at most $O(n^2)$ time.
+%put theorem here
+%explanation removing dominating vertices
+%why is this different from becker
 
@@
 \label{sec:scsppsoln}
-
-Indeed, the SCSPP is a generalisation of the classical one-dimensional bin-packing problem (BPP), where in the latter problem, the minimum scoring distance $\tau$ can be said to be equal to zero.
+%move this to beginning
+The SCSPP is a generalisation of the classical one-dimensional bin-packing problem (BPP), where in the latter problem, the minimum scoring distance $\tau$ can be said to be equal to zero.
 It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}), and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.

### 2018-04-18 PAPER/main.tex
minor changes

@@
 One prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004.
-A set $\mathcal{I}$ of rectangular items of equal height $h$ made from cardboard are to be packed onto a strip of heigh $h$ from left to right.
+A set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of heigh $H$ from left to right.
 Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places.
@@
 
-Observe that, in this particular strip-packing problem, the widths of the individual items are disregarded entirely, since the aim is to arrange the items onto a strip of seemingly infinite length.
-In practical applications, strips of material are often provided in fixed lengths.
+Observe that, in this particular strip-packing problem, the widths of the individual items are disregarded entirely, since the aim is to arrange the items onto a strip of seemingly infinite width.
+In practical applications, strips of material are often provided in fixed widths.
 Given a large problem instance, multiple strips may therefore be required to feasibly accommodate all of the items.
@@
 	\label{defn:scspp}
-	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ with equal fixed length $l$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
+	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ of equal fixed width $W$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
 \end{definition}

### 2018-04-19 PAPER/main.tex
changed notation and SCSPP definition

@@
 One prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004.
-A set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of heigh $H$ from left to right.
+A set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right.
 Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places.
@@
 	\label{defn:scspp}
-	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ of equal fixed width $W$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
+	Let $\mathcal{S} = S_1, S_2, ..., S_k$ be a set of strips of height $H$ and width $W$, and let $\mathcal{I}$ be a set of rectangular items of height $H$ and varying widths $w_i \in \mathbb{Z}^+ < W$ and score widths $a_i, b_i \in \mathbb{Z}^+$ such that $a_i \leq b_i$ and $a_i + b_i < w_i$ for each item $i \in \mathcal{I}$.
+Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips $k$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
 \end{definition}
@@
 Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$.
-$G'$ thus consists of a collection of alternating cycles $A_1, A_2, ..., A_{\lambda}$.
+$G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_{\lambda}$.
 If there is only one component on $G'$, i.e.
@@
 The sets $R_1, R_2, ..., R_k \subseteq R$ created during this process are then analysed.
-In the event that BR has been unable to produce a single set $R_1$, the components $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
+In the event that BR has been unable to produce a single set $R_1$, the components $C_1,..., C_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
 If there exists a set $R_i$ such that $|R_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':
@@
 Let $\mathcal{R}$ be a set that contains the sets $R_i$ needed to connect the components of $G'$ together, and let $\Lambda$ be a set that records the components covered by the sets in $\mathcal{R}$.
-Start by adding the components $A_i$ that each edge in $R_1$ is a member of to $\Lambda$, and then add $R_1$ to $\mathcal{R}$.
+Start by adding the components $C_i$ that each edge in $R_1$ is a member of to $\Lambda$, and then add $R_1$ to $\mathcal{R}$.
 At this stage, $|\Lambda| = |\mathcal{R}|$.
@@
 	\label{eqn:lowerbound}
-	k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{l}}
+	k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{W}}
 \end{equation}

### 2018-04-19 PAPER/main.tex
changed notation

@@
 
-where $n$ is the number of items in the set $\mathcal{I}$, $w_i$ the width of each item $i \in \mathcal{I}$, and $l$ is the length of the strips (\citealp{martello1990b}).
+where $n$ is the number of items in the set $\mathcal{I}$, $w_i$ the width of each item $i \in \mathcal{I}$, and $W$ is the width of the strips (\citealp{martello1990b}).
 In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ strips.

### 2018-04-24 PAPER/main.tex
moved theorem to end, list for rematching criteria, BPP NP-hard after SCSPP definition

@@
 \begin{definition}
-	\label{defn:cpop}
+	\label{defn:cop}
 	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple.
@@
 	\begin{equation}
-		\label{eqn:cpop}
+		\label{eqn:cop}
 		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
@@
 
+The SCSPP is a generalisation of the classical one-dimensional bin-packing problem (BPP), where in the latter problem the minimum scoring distance $\tau$ can be said to be equal to zero.
+It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}), and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.
+Instead, heuristics can be used to find near-optimal solutions in a shorter amount of time.
+
 The remainder of this article will firstly, in Section 2, detail a polynomial-time algorithm that is able to produce a solution to any instance of the COP, if a solution exists.
-Section 3 describes the heuristics that will be used to find feasible solutions to the SCSPP, and discusses the associated advantages and disadvantages.
+Section 3 describes three heuristics that will be used to find feasible solutions to the SCSPP, and discusses the associated advantages and disadvantages.
 A comparison of these heuristics and an analysis of the results will be provided in Section 4, and finally Section 5 concludes the paper and proposes some potential directions for future work.
 
-\section{Solving the CPOP}
+\section{Solving the COP}
 \label{sec:ahca}
@@
 This is especially useful for problems such as the previously mentioned strip-packing problem, where a tangible solution is required in order to place the items in the correct order and orientation.
+\textcolor{OrangeRed}{USING GRAPH.}
 
-Let $\mathcal{M}$ be an instance of the COP of cardinality $n$ as described in Definition \ref{defn:cpop}.
+\begin{itemize}
+	\item Figure \ref{fig:partners} shows the graph with the values from the example above
+	\item Model each of the values of all pairs in $\mathcal{M}$ as a vertex on a graph $G$
+	\item Each vertex is assigned a value from $\mathcal{M}$
+	\item Add an extra pair of vertices, dominating vertices, that are assigned values equal to $\tau$
+	\item The values in $\mathcal{M}$, and thus the vertices on the graph, are arranged in pairs.
+	\item This is represented on the graph by adding a set of ``blue'' edge, $B$, that are a perfect matching of all vertices on the graph
+	\item Under such a matching, each vertex (each value in $\mathcal{M}$) has a partner that represents the other value in the pair.
+	\item Then, we add to $G$ another set of ``red'' edges, $R$, that consists of edges between vertices whose corresponding values in $\mathcal{M}$ can be arrange alongside one another
+	\item That is, for two distinct vertices, EQUATION, provided $p(v_i) \neq v_j$ i.e. not partners
+	\item Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
+	\item $G$ has $2n + 2$ vertices, edge sets $B$ and $R$ such that $B \cap R = \emptyset$
+	\item $B = |n+1|$
+	\item Dominating vertices are partners
+	\item Dominating vertices will be removed at end, are not part of final solution
+	\item Vertex set $V = \{v_1,...,v_{2n+2}\}$
+	\item Each vertex assigned value from $\mathcal{M}$ s.t. $V-1 \leq ... \leq v_{2n+2}$
+\end{itemize}
+
+Let $\mathcal{M}$ be an instance of the COP of cardinality $n$ as described in Definition \ref{defn:cop}.
 Then, a graph $G$ is defined by a vertex set $V = \{v_1, v_2, ...v_{2n+2}\}$, where each vertex is assigned a value from $\mathcal{M}$ such that $v_1 \leq v_2 \leq ...
@@
 Hence, $G=(V, B \cup R)$ is an undirected graph with $2n + 2$ vertices and edge sets $B$ and $R$, such that $B \cap R = \emptyset$.
-Observe that $B$ is in fact a perfect matching, with $|B|= n+1$.
+Observe that $B$ is also a perfect matching, with $|B|= n+1$.
 
@@
 \end{subfigure}
-\caption{$v_0 = 1, v_1 = 1, v_2 = 2, v_3 = 2, v_4 = 3, v_5 = 3, v_6 = 4, v_7 = 4, v_8 = 4, v_9 = 5, v_{10} = 6, v_{11} = 7, v_{12} = 7, v_{13} = 7$}
+\caption{$v_1 = 1, v_2 = 1, v_3 = 2, v_4 = 2, v_5 = 3, v_6 = 3, v_7 = 4, v_8 = 4, v_9 = 4, v_{10} = 5, v_{11} = 6, v_{12} = 7, v_{13} = 7, v_{14} = 7$}
 \end{figure}
@@
 
-\begin{theorem}
-	\label{thm:cpopsoln}
-	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the COP if and only if its corresponding graph $G(V, B\cup R)$ contains an alternating Hamiltonian cycle.
-\end{theorem}
-\begin{proof}
-	Let $\mathcal{A} = \{v_1, v_2, ..., v_{2n+1}, v_{2n+2}\}$ be an alternating Hamiltonian cycle on $G$, where $v_{2n+1}$ and $v_{2n+2}$ are the dominating vertices.
-By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $B$.
-Thus, there exists a set of $n+1$ edges from $R$ that, together with the edges in $B$, form the alternating Hamiltonian cycle.
-Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $B$.
-The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple.
-\textcolor{OrangeRed}{edges R vicinal sum constraint equation 2}.
-\qed
-\end{proof}
-
 Therefore, the aim of this algorithm is to construct an alternating Hamiltonian cycle on $G$.
@@
 
-During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided $v_i$ is not the first vertex (i.e $i \neq 1$), $v_{i-1}$ has been matched, and $(v_{i-1}, p(v_i)) \in R$.
+During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided that 
+\begin{enumerate*}[label={(\alph*)}]
+	\item $v_i$ is not the first vertex (i.e $i \neq 1$); 
+	\item $v_{i-1}$ has been matched; and
+	\item $(v_{i-1}, p(v_i)) \in R$.
+\end{enumerate*}
 Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$.
 It is guaranteed that MMCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time.
+\textcolor{OrangeRed}{CITE.}
 
@@
 If a solution does indeed exist, AHCA can produce this solution in at most $O(n^2)$ time.
+
+\begin{theorem}
+	\label{thm:copsoln}
+	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the COP if and only if its corresponding graph $G(V, B\cup R)$ contains an alternating Hamiltonian cycle.
+\end{theorem}
+\begin{proof}
+	Let $\mathcal{A} = \{v_1, v_2, ..., v_{2n+1}, v_{2n+2}\}$ be an alternating Hamiltonian cycle on $G$, where $v_{2n+1}$ and $v_{2n+2}$ are the dominating vertices.
+By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $B$.
+Thus, there exists a set of $n+1$ edges from $R$ that, together with the edges in $B$, form the alternating Hamiltonian cycle.
+Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $B$.
+The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple.
+\textcolor{OrangeRed}{edges R vicinal sum constraint equation 2}.
+\qed
+\end{proof}
 %put theorem here

### 2018-04-25 PAPER/main.tex
changed explanation of construction of graph G in section 2, changed captions on figures

@@
 	\includestandalone[width=0.8\textwidth]{figures/boxesknifeannotate}
-	\caption{\textcolor{red}{Individual boxes.}}	
+	\caption{Width and score widths on an item $i \in \mathcal{I}$, and knives mounted on a bar score two items simultaneously}	
 	\label{fig:boxknife}
@@
 
-\begin{itemize}
-	\item Figure \ref{fig:partners} shows the graph with the values from the example above
-	\item Model each of the values of all pairs in $\mathcal{M}$ as a vertex on a graph $G$
-	\item Each vertex is assigned a value from $\mathcal{M}$
-	\item Add an extra pair of vertices, dominating vertices, that are assigned values equal to $\tau$
-	\item The values in $\mathcal{M}$, and thus the vertices on the graph, are arranged in pairs.
-	\item This is represented on the graph by adding a set of ``blue'' edge, $B$, that are a perfect matching of all vertices on the graph
-	\item Under such a matching, each vertex (each value in $\mathcal{M}$) has a partner that represents the other value in the pair.
-	\item Then, we add to $G$ another set of ``red'' edges, $R$, that consists of edges between vertices whose corresponding values in $\mathcal{M}$ can be arrange alongside one another
-	\item That is, for two distinct vertices, EQUATION, provided $p(v_i) \neq v_j$ i.e. not partners
-	\item Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
-	\item $G$ has $2n + 2$ vertices, edge sets $B$ and $R$ such that $B \cap R = \emptyset$
-	\item $B = |n+1|$
-	\item Dominating vertices are partners
-	\item Dominating vertices will be removed at end, are not part of final solution
-	\item Vertex set $V = \{v_1,...,v_{2n+2}\}$
-	\item Each vertex assigned value from $\mathcal{M}$ s.t. $V-1 \leq ... \leq v_{2n+2}$
-\end{itemize}
+% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
+% Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
+% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..
 
-Let $\mathcal{M}$ be an instance of the COP of cardinality $n$ as described in Definition \ref{defn:cop}.
-Then, a graph $G$ is defined by a vertex set $V = \{v_1, v_2, ...v_{2n+2}\}$, where each vertex is assigned a value from $\mathcal{M}$ such that $v_1 \leq v_2 \leq ...
-\leq v_{2n+2}$.
-Note that there are two extra ``dominating'' vertices, $v_{2n+1}$ and $v_{2n+2}$, which have values equivalent to $\tau$.
-In $\mathcal{M}$, the values that make up a pair are referred to as ``partners''.
-Thus, let $p: V \to V$ be a bijective function that associates each vertex $v_i \in V$ on $G$ with its partner, $v_j = p(v_i)$.
-$G$ comprises two distinct edge sets: $B$, which contains edges between vertices that are partners, and $R$, which consists of edges between vertices whose corresponding values in $\mathcal{M}$ can be arranged alongside one another.
-That is, for two distinct vertices $v_i, v_j$,
+Let $\mathcal{M}$ be an instance of the COP of cardinality $n$.
+We model each of the values of all elements in $\mathcal{M}$ as a vertex on a graph $G$, and assign each vertex a value from $\mathcal{M}$ in non-decreasing order.
+A pair of vertices, called ``dominating vertices'' are then added to the graph, both of which are assigned values equal to $\tau$.
+These dominating vertices aid the solution process, and are removed at the end.
+Thus, the graph $G$ has $2n+2$ vertices.
 
-\begin{equation}
-	\label{eqn:jointsum}
-	v_i + v_j \geq \tau,
-\end{equation}
+The values in $\mathcal{M}$, and thus the vertices on $G$, are arranged in pairs.
+This is represented on $G$ by adding a set of ``blue'' edges, $B$, that contains edges between vertices that are ``partners'', i.e.
+whose values make up a pair in $\mathcal{M}$.
+It can be seen that $B$ is a perfect matching, with $|B|= n+1$.
 
-provided $p(v_i) \neq v_j$.
-Hence, $G=(V, B \cup R)$ is an undirected graph with $2n + 2$ vertices and edge sets $B$ and $R$, such that $B \cap R = \emptyset$.
-Observe that $B$ is also a perfect matching, with $|B|= n+1$.
+Now, we add to $G$ a set of ``red'' edges, $R$, that consists of edges between vertices whose values equal or exceed $\tau$, provided they are not partners.
+This corresponds to the vicinal sum constraint in Defintion \ref{defn:cop}.
+
+Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$, and two distinct edge sets $B$ and $R$, such that $B \cap R = \emptyset$.
+Figure \ref{fig:partners/threshold} illustrates the construction of $G$ using the instance $\mathcal{M}$ from the example above.
 
@@
 	\includestandalone[width=\textwidth]{figures/partners}
-	\caption{\textcolor{red}{partners.}}	
+	\caption{$G = (V, B)$}	
 	\label{fig:partners}
@@
 	\includestandalone[width=\textwidth]{figures/threshold}
-	\caption{\textcolor{red}{threshold.}}	
+	\caption{$G=(V, B \cup R)$}	
 	\label{fig:threshold}
 \end{subfigure}
-\caption{$v_1 = 1, v_2 = 1, v_3 = 2, v_4 = 2, v_5 = 3, v_6 = 3, v_7 = 4, v_8 = 4, v_9 = 4, v_{10} = 5, v_{11} = 6, v_{12} = 7, v_{13} = 7, v_{14} = 7$}
+\caption{Example construction of $G$ using instance $\mathcal{M}$ from the example above.}
+\label{fig:partners/threshold}
 \end{figure}
@@
 		\includestandalone[width=\textwidth]{figures/matching}
-		\caption{\textcolor{red}{matching.}}	
+		\caption{$G' = (V, B \cup R')$}	
 		\label{fig:matching}
@@
 		\includestandalone[width=\textwidth]{figures/mps}
-		\caption{\textcolor{red}{mps}}	
+		\caption{$G' =(V, B \cup R')$ planar}	
 		\label{fig:mps}
 	\end{subfigure}
-	\caption{main caption}
+	\caption{Subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MMCM algorithm. Planar graph, can see that $G'$ is made up of two components.}
 \end{figure}
 
-Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence in accordance with Theorem $\ref{thm:cpopsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
+Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence in accordance with Theorem $\ref{thm:copsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
 Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$.

### 2018-04-25 PAPER/main.tex
changed MMCM

@@
 
-To find a matching $R' \subseteq R$, the following modified maximum cardinality matching (MMCM) algorithm is executed (\citealp{mahadev1994, becker2010}): for each vertex $v_i$, $i = 1, 2,...,2n+2$, find the largest vertex $v_j \in \Gamma(v_i)\backslash p(v_i)$ (i.e.
-the largest vertex $v_j$ in $v_i$'s neighbourhood that is not $v_i$'s partner) that is not incident to any edge in $R'$.
-Add the edge connecting these two vertices to $R'$, and proceed to the next vertex until all vertices have been assessed.
-The pair of vertices incident to each edge in $R'$ are referred to as being ``matched'', and are connected by a ``matching'' edge.
+To find a matching $R' \subseteq R$, the following modified maximum cardinality matching (MMCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}: For each vertex $v_i, i=1,2,...,2n+2$, select the edge in $R$ connecting $v_i$ to the highest indexed vertex $v_j$ that is not already incident to an edge in $R'$.
+Add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed.
+The two vertices incident to each matching edge in $R'$ are now referred to as being ``matched''.
 
@@
 \begin{enumerate*}[label={(\alph*)}]
-	\item $v_i$ is not the first vertex (i.e $i \neq 1$); 
-	\item $v_{i-1}$ has been matched; and
+	\item $v_i$ is not the first vertex; 
+	\item $v_{i-1} \in R'$; and
 	\item $(v_{i-1}, p(v_i)) \in R$.
@@
 Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$.
-It is guaranteed that MMCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time.
-\textcolor{OrangeRed}{CITE.}
+It is guaranteed that MMCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time (\citealp{mahadev1994}).
 

### 2018-04-27 PAPER/main.tex
changed table, changed various sections

@@
 	\label{defn:scspp}
-	Let $\mathcal{S} = S_1, S_2, ..., S_k$ be a set of strips of height $H$ and width $W$, and let $\mathcal{I}$ be a set of rectangular items of height $H$ and varying widths $w_i \in \mathbb{Z}^+ < W$ and score widths $a_i, b_i \in \mathbb{Z}^+$ such that $a_i \leq b_i$ and $a_i + b_i < w_i$ for each item $i \in \mathcal{I}$.
+	Let $\mathcal{S} = \{S_1, S_2, ..., S_k\}$ be a set of strips of height $H$ and width $W$, and let $\mathcal{I}$ be a set of rectangular items of height $H$ and varying widths $w_i \in \mathbb{Z}^+ < W$ and score widths $a_i, b_i \in \mathbb{Z}^+$ such that $a_i \leq b_i$ and $a_i + b_i < w_i$ for each item $i \in \mathcal{I}$.
 Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips $k$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
@@
 % Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..
-
 Let $\mathcal{M}$ be an instance of the COP of cardinality $n$.
@@
 
-Now, we add to $G$ a set of ``red'' edges, $R$, that consists of edges between vertices whose values equal or exceed $\tau$, provided they are not partners.
+Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose values equal or exceed $\tau$, provided they are not partners.
 This corresponds to the vicinal sum constraint in Defintion \ref{defn:cop}.
@@
 \end{subfigure}
-\caption{Example construction of $G$ using instance $\mathcal{M}$ from the example above.}
+\caption{Example construction of $G$ using instance $\mathcal{M}  = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$}
 \label{fig:partners/threshold}
@@
 
-The following definition now describes a variant of the classical Hamiltonian cycle on a graph $G$.
+Consider the following definition describing a variant of the classical Hamiltonian cycle on a graph $G$.
 
@@
 
-Therefore, the aim of this algorithm is to construct an alternating Hamiltonian cycle on $G$.
-Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, every edge in $B$ must be present in the alternating Hamiltonian cycle.
-Consequently, the task now involves finding a matching $R' \subseteq R$ of cardinality $n+1$, such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition $\ref{defn:althamcycle}$.
+An alternating Hamiltonian cycle on $G$ would correpsond to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ shows values that can be placed alongside one another feasibly.
+Thus, by removing the dominating vertices and any incident edges, the remaining alternating Hamiltonian path illustrates the order in which the elements should be placed to produce a feasible solution $\mathcal{T}$.
+
+Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, i.e.
+the values cannot be changed, and the values in each element cannot be separated, every edge in $B$ must be present in the alternating Hamiltonian cycle.
+Consequently, the task now involves finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.
 
@@
 	\end{subfigure}
-	\caption{Subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MMCM algorithm. Planar graph, can see that $G'$ is made up of two components.}
+	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MMCM algorithm. Planar graph, can see that $G'$ is made up of two components, $q = 2$}
+	\label{fig:matching/mps}
 \end{figure}
 
-Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence in accordance with Theorem $\ref{thm:copsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
-Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$.
-$G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_{\lambda}$.
-If there is only one component on $G'$, i.e.
-$\lambda = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists.
-For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle.
-The algorithm thus executes a Bridge Recognition (BR) procedure that selects suitable edges in $R$ to be used as bridges between the components of $G'$, and will replace certain edges in $R'$.
+Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence no feasible solution can be found for the given instance $\mathcal{M}$ of the COP.
+Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$ (see Figure \ref{fig:matching/mps}).
+$G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_q$.
+In the case where $G'$ comprises one component, i.e.
+$q = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists.
+However, if $q > 1$, the components of $G'$ must be combined to form an alternating Hamiltonian cycle.
+To do this, a Bridge Recognition (BR) algorithm can be executed that selects suitable edges from $R$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.
+
+\begin{itemize}
+	\item smaller vertices lexicographical increasing, $v_1,..., v_{n+1}$
+	\item larger vertices lexicographical decreasing, $v_{2n+2},..., v_{n+2}$
+	\item any edge that doesn't abide by this order should be removed
+	\item caused during MMCM, highest indexed vertex could not be matched with current vertex due to being partners, so current vertex is matched with next highest indexed vertex available.
+	\item thus list of edges should be $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$.
+\end{itemize}
 
@@
 In the event that BR has been unable to produce a single set $R_1$, the components $C_1,..., C_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
-If there exists a set $R_i$ such that $|R_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':
+If there exists a set $R_i$ such that $|R_i| = \lambda$, then all components on $G'$ can be combined using the following `
+`connecting method'':
 
@@
 		\noalign{\smallskip}
-	0.0 & 0.119930 & 0.119930 & 0.119930 & 0.234780 & 0.234780 & 0.234780 & 0.464660 & 0.464660 & 0.464660 \\
-	0.1 & 0.190373 & \textbf{0.209209} & 0.195007 & 0.368315 & \textbf{0.403484} & 0.372649 & 0.653776 & \textbf{0.662649} & 0.654527 \\
-	0.2 & 0.241823 & \textbf{0.291742} & 0.252201 & 0.455307 & \textbf{0.537355} & 0.464804 & 0.740613 & \textbf{0.743163} & 0.74212 \\
-	0.3 & 0.308598 & \textbf{0.423971} & 0.330489 & 0.552257 & \textbf{0.700541} & 0.573676 & 0.817858 & 0.801526 & \textbf{0.820929} \\
-	0.4 & 0.387256 & \textbf{0.634770} & 0.435353 & 0.648313 & \textbf{0.860270} & 0.688716 & 0.874070 & 0.835449 & \textbf{0.878158} \\
-	0.5 & 0.491093 & \textbf{0.900872} & 0.586398 & 0.747025 & \textbf{0.953757} & 0.806812 & 0.915534 & 0.854677 & \textbf{0.920727} \\
-	0.6	& 0.612443 & \textbf{0.982422} & 0.753466 & 0.834971 & \textbf{0.962939} & 0.896095 & 0.939964 & 0.864190 & \textbf{0.945036} \\
-	0.7 & 0.773879 & \textbf{0.986985} & 0.909705 & 0.916026 & \textbf{0.965898} & 0.959666 & 0.957970 & 0.873854 & \textbf{0.961036} \\
-	0.8	& 0.904347 & \textbf{0.987407} & 0.980250 & 0.966750 & 0.967486 & \textbf{0.984634} & 0.964117 & 0.885786 & \textbf{0.965271} \\
-	0.9	& 0.978801 & 0.984535 &	\textbf{0.991745} & 0.987382 & 0.967989 & \textbf{0.990479} & 0.968735 & 0.897915 & \textbf{0.968928} \\
-	1.0 & \textbf{0.995493} & 0.988851 & \textbf{0.995493} & \textbf{0.992539} & 0.969239 & \textbf{0.992539} & \textbf{0.967834} & 0.904161 & \textbf{0.967834} \\
+		0.0	& 8.35709 & 8.35709 & 8.35709 & 4.26800 & 4.26800 & 4.26800 & 2.15624 & 2.15624 & 2.15624 \\
+		0.1	& 5.27284 & \textbf{4.89963} & 5.14404 & 2.72299 & \textbf{2.48800} & 2.69191 & 1.53147 & \textbf{1.51049} & 1.52968 \\
+		0.2	& 4.16155 & \textbf{3.46467} & 3.98645 & 2.21096 & \textbf{1.87449} & 2.16338 & 1.34812 & \textbf{1.34499} & 1.34593 \\
+		0.3	& 3.27805 & \textbf{2.40153} & 3.05546 & 1.82199 & \textbf{1.43724} & 1.75610 & 1.22453 & 1.24810 & \textbf{1.21994} \\
+		0.4	& 2.61641 & \textbf{1.63390} & 2.33662 & 1.54989 & \textbf{1.16887} & 1.46534 & 1.14507 & 1.19631 & \textbf{1.13979} \\
+		0.5	& 2.08260 & \textbf{1.13827} & 1.77494 & 1.35101 & \textbf{1.04978} & 1.25567 & 1.09274 & 1.17069 & \textbf{1.08661} \\
+		0.6	& 1.65897 & \textbf{1.02027} & 1.36093 & 1.20040 & \textbf{1.03720} & 1.11964 & 1.06255 & 1.15766 & \textbf{1.05701} \\
+		0.7	& 1.32002 & \textbf{1.01350} & 1.11348 & 1.09659 & \textbf{1.03556} & 1.04569 & 1.04546 & 1.14416 & \textbf{1.04150} \\
+		0.8	& 1.10725 & \textbf{1.01384} & 1.02188 & 1.03577 & 1.03439 & \textbf{1.01696} & 1.03711 & 1.12951 & \textbf{1.03565} \\
+		0.9	& 1.02134 & 1.01315 & \textbf{1.00646} & 1.01364 & 1.03285 & \textbf{1.01029} & 1.03434 & 1.11631 & \textbf{1.03416} \\
+		1.0 & \textbf{1.00480} & 1.01302 & \textbf{1.00480} & \textbf{1.00919} & 1.03261 & \textbf{1.00919} & \textbf{1.03393} & 1.10807 & \textbf{1.03393} \\	
 		\hline

### 2018-04-28 PAPER/main.tex
edited section BR

@@
 \end{itemize}
+
+The edges in $R'$ are sorted into a list such that the lower-indexed vertices of each edge are in increasing order of indices, and the higher-indexed vertices are in decreasing order of indices, i.e.
+$(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$.
+Any edges that cannot be placed in such an order are then removed from this list.
+For instance, in the example illustrated in Figure \ref{fig:matching/mps}, $(v_5, v_9)$ would be removed from the list, since the next edge in the list is $(v_6, v_{10})$, and so the higher-indexed vertices are not in decreasing order.
+This is due to $v_5$ not being matched with the highest-indexed vertex available, $v_{10}$, during MMCM, as $(v_5, v_{10}) \in B$.
+
+Starting from the first edge, BR searches through the list to find an edge that meets the following conditions: 
+\begin{enumerate*}[label={(\alph*)}]
+	\item The lower-indexed vertex of the current edge, and the higher-indexed vertex of the succeeding edge in the list are adjacent via an edge in $R$, and;
+	\item The current edge and the succeeding edge are members of different components on $G'$.
+\end{enumerate*}
+
+If these conditions are met, BR adds the edge from $R$ connecting the lower-indexed vertex of the current edge to the higher-indexed vertex of the succeeding edge to a set $R_i$ that records edges to be used as potential bridges.
+BR then continues to add
 

### 2018-04-30 PAPER/main.tex
edited BR, bullet points for connecting procedure after BR, added figures

@@
 
-\begin{itemize}
-	\item smaller vertices lexicographical increasing, $v_1,..., v_{n+1}$
-	\item larger vertices lexicographical decreasing, $v_{2n+2},..., v_{n+2}$
-	\item any edge that doesn't abide by this order should be removed
-	\item caused during MMCM, highest indexed vertex could not be matched with current vertex due to being partners, so current vertex is matched with next highest indexed vertex available.
-	\item thus list of edges should be $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$.
-\end{itemize}
-
 The edges in $R'$ are sorted into a list such that the lower-indexed vertices of each edge are in increasing order of indices, and the higher-indexed vertices are in decreasing order of indices, i.e.
@@
 \begin{enumerate*}[label={(\alph*)}]
-	\item The lower-indexed vertex of the current edge, and the higher-indexed vertex of the succeeding edge in the list are adjacent via an edge in $R$, and;
-	\item The current edge and the succeeding edge are members of different components on $G'$.
+	\item The lower-indexed vertex of the current edge, and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
+	\item The current edge and the next edge are members of different components on $G'$.
 \end{enumerate*}
 
-If these conditions are met, BR adds the edge from $R$ connecting the lower-indexed vertex of the current edge to the higher-indexed vertex of the succeeding edge to a set $R_i$ that records edges to be used as potential bridges.
-BR then continues to add
+If the conditions are met, BR adds the current edge to a set $R_i$, and continues to add all succeeding edges in the list to $R_i$, provided that for each edge both conditions hold, and the succeeding edge is not a member of a component of $G'$ that has an edge in $R_i$.
+Once there are no more valid edges available to add to $R_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets the conditions, and can begin a new set $R_{i+1}$.
+The procedure terminates once the penultimate edge in the list has been assessed.
 
-For each edge $(v_i, v_j) \in R'$, where $i < j$, $v_i$ is referred to as the ``smaller'' vertex, and $v_j$ as the ``larger'' vertex, since the value associated with $v_i$ is less than or equal to the value associated with $v_j$.
-The procedure initially sorts the edges in $R'$ into a list such that the smaller vertices of the edges are in lexicographical order, and therefore in non-decreasing order of values.
-Any edges whose smaller vertices, during MMCM, were unable to be matched with the largest possible vertex available due to being partners are then removed from this list.
-Any edges that do not connect the smaller vertex to the largest possible vertex, due to the largest vertex being its partner, are also removed.
-Then, starting from the first edge, BR searches through the list to find an edge that meets the following conditions:
-\begin{enumerate}
-	\item The smaller vertex of the current edge and the larger vertex of the succeeding edge are connected by an edge in $R$.
-	\item The current edge and the succeeding edge are members of different components on $G'$.
-\end{enumerate}
-
-If such an edge is found, the procedure adds this edge to a set $R_i$, and continues to add all succeeding edges in the list to $R_i$, provided that for each edge conditions 1 and 2 hold, and the succeeding edge is not a member of a component on $G'$ that already has an edge in $R_i$.
-Once there are no more valid edges to add to $R_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets conditions 1 and 2, and can therefore start a new set $R_{i+1}$.
-The procedure ends when the penultimate edge in the list has been examined.
-
-The sets $R_1, R_2, ..., R_k \subseteq R$ created during this process are then analysed.
-In the event that BR has been unable to produce a single set $R_1$, the components $C_1,..., C_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists.
-If there exists a set $R_i$ such that $|R_i| = \lambda$, then all components on $G'$ can be combined using the following `
-`connecting method'':
-
-Starting from the first edge in $R_i$, add the edge from $R$ connecting the smaller vertex of each edge to the larger vertex of the succeeding edge to $R'$.
-For the final edge in $R_i$, add the edge from $R$ that connects its smaller vertex to the larger vertex of the first edge in $R_i$ to $R$.
-Finally, any edges that appear in both $R_i$ and $R'$ are removed from $R'$, such that $R_i \cap R' = \emptyset$, and $R'$ returns to being a perfect matching.
-$G'$ then comprises a single alternating Hamiltonian cycle, and thus the algorithm has found a solution to the problem instance.
-
-Else, if $k > 1$, it may be that multiple sets are required to combine the components of $G'$.
-Let $\mathcal{R}$ be a set that contains the sets $R_i$ needed to connect the components of $G'$ together, and let $\Lambda$ be a set that records the components covered by the sets in $\mathcal{R}$.
-Start by adding the components $C_i$ that each edge in $R_1$ is a member of to $\Lambda$, and then add $R_1$ to $\mathcal{R}$.
-At this stage, $|\Lambda| = |\mathcal{R}|$.
-Proceeding through the remaining sets $R_2, R_3, ..., R_k$, find a set $R_i$ that contains at least one edge that is a member of a component in $\Lambda$, and at least one edge that is a member of a component not yet recorded in $\Lambda$.
-Append the component that each edge in this set $R_i$ is a member of to $\Lambda$, provided the component is not already an element of $\Lambda$, then add $R_i$ to $\mathcal{R}$.
-Continue in this manner until the final set $R_k$ has been assessed.
-If $|\Lambda| = \lambda$, i.e.
-all components of $G'$ are elements of $\Lambda$, then the sets in $\mathcal{R}$ are able to combine the components of $G'$ to form a single alternating Hamiltonian cycle.
-This is achieved by repeating the connecting method described previously on every set $R_i \in \mathcal{R}$.
+\begin{itemize}
+	\item sets $R_1, R_2, ..., R_k \in R'$ are produced during BR
+	\item Connecting procedure detects collection of sets that combine all components of $G'$ together
+	\item only overlap once
+	\item If $k = 0$, i.e. not a single set $R_i$ created during BR, then no edges exist that can combine the components together - infeasible, cannot create alt ham cycle (no solution)
+	\item If $\exists$ set $R_i$ such that $|R_i| = q$, i.e. number of edges in $R_i$ equals number of components, then solution exists, need to connect components using connecting method/procedure
+	\item this is because there is an edge in each component that can be removed, and replaced with a new edge that bridges the components together 
+	\item otherwise, more than one set $R_i$ needed
+	\item second method - find two sets $R_i, R_j$ such that there is one red edge from each component of $G'$ in EITHER $R_i$ OR $R_j$, and there is one component of $G'$ that has one red edge in $R_i$ and another (different) red edge in $R_j$
+	\item that is, $R_i$ and $R_j$ each have an edge from the same components, and all the other edges are from different components
+	\item Example of set $R_1$ BR procedure Figures
+	\item different edge from same component means components can be joined together to make single alt ham cycle
+	\item e.g. if $q = 4$, then $R_i$ has edges from $C_1, C_2$, and $R_j$ has edges from $C_2, C_3, C_4$, then there is an overlap (each set has an edge from $C_2$)
+	\item if there aren't two sets that cover all components and overlap only once, another method
+	\item third method - find set $R_i$ with largest cardinality, then run modified BR, where edges from the largest set $R_i$ are removed from the initial sorted list of edges, and then find a new set $R_j$ that contains an edge from a component that isn't covered by $R_i$, and an edge from a component that is covered by $R_i$ (the overlap)
+	\item continue to add succeeding edges as long as they aren't a member of a component already covered in $R_i$ or $R_j$
+	\item if end of list is reached, and not all components covered, delete edges that are in $R_j$ from the list of edges, and start again from the beginning
+	\item continue until no new sets can be made, then check to see if the sets cover all components, if not, infeasible, else feasible
+	\item connecting method/procedure - connect smaller-indexed vertex of each edge to higher-indexed vertex of next edge, except last edge, connect smallest of last edge to highest of first edge
+	\item then add these edges to $R'$ and remove the edges in $R_i$ from $R'$, so the cardinality of $R'$ should still be $n+1$ (perfect matching), and $R_i \cap R' = \emptyset$.
+\end{itemize}
 
@@
 If a solution does indeed exist, AHCA can produce this solution in at most $O(n^2)$ time.
+
+\begin{figure}	
+	\centering
+	\begin{subfigure}[h]{0.7\textwidth}
+		\includestandalone[width=\textwidth]{figures/mpsconnect}
+		\caption{connect}	
+		\label{fig:mpsconnect}
+	\end{subfigure} \quad
+	\begin{subfigure}[h]{0.7\textwidth}
+		\includestandalone[width=\textwidth]{figures/mpscycle}
+		\caption{cycle}	
+		\label{fig:mpscycle}
+	\end{subfigure}
+	\caption{connect and cycle}
+	\label{fig:connect/cycle}
+\end{figure}
 

### 2018-04-30 PAPER/main.tex
bullet points for solving SCSPP/heuristics

@@
 Once there are no more valid edges available to add to $R_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets the conditions, and can begin a new set $R_{i+1}$.
-The procedure terminates once the penultimate edge in the list has been assessed.
+The procedure terminates once the penultimate edge in the list has been assessed, having generated the sets $R_1, R_2, ..., R_k \subseteq R'$.
+
+In the event that BR has been unable to produce a single set, i.e.
+$k = 0$, there are no suitable edges that can combine the components $C_1, C_2, ..., C_k$ of $G'$, and therefore an alternating Hamiltonian cycle cannot be created.
+Thus, no feasible solution exists for the given instance of the COP.
+
+If there exists a set $R_i$ such that $|R_i| = q$, then the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle.
+This is achieved by adding the red edge connecting the lower-indexed vertex of each edge in $R_i$ to the higher-indexed vertex of the next edge to $R'$ (for the final edge in $R_i$, add the red edge connecting its lower-indexed vertex to the higher-indexed vertex of the first edge).
+Any edges that appear in both $R_i$ and $R'$ are then removed from $R'$, so that $R'$ remains a perfect matching, and $R_i \cap R' = \emptyset$.
+$G'$ then consists of a single alternating Hamiltonian cycle, and hence a solution has been found.
+
+Otherwise, if $k > 1$, it may be that multiple sets are required to connect all components of $G'$.
+For two sets $R_i$ and $R_j$ to ``overlap'', each set must have one edge from the same component on $G'$, and the other edges in each set must be from different components.
+For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, and the other edges in the sets are from different components.
+Hence, a selection of sets from $R_1, R_2, ..., R_k$ need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets.
+If such a collection of sets exists, then the components of $G$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.
 
 \begin{itemize}
-	\item sets $R_1, R_2, ..., R_k \in R'$ are produced during BR
-	\item Connecting procedure detects collection of sets that combine all components of $G'$ together
-	\item only overlap once
-	\item If $k = 0$, i.e. not a single set $R_i$ created during BR, then no edges exist that can combine the components together - infeasible, cannot create alt ham cycle (no solution)
-	\item If $\exists$ set $R_i$ such that $|R_i| = q$, i.e. number of edges in $R_i$ equals number of components, then solution exists, need to connect components using connecting method/procedure
-	\item this is because there is an edge in each component that can be removed, and replaced with a new edge that bridges the components together 
-	\item otherwise, more than one set $R_i$ needed
-	\item second method - find two sets $R_i, R_j$ such that there is one red edge from each component of $G'$ in EITHER $R_i$ OR $R_j$, and there is one component of $G'$ that has one red edge in $R_i$ and another (different) red edge in $R_j$
-	\item that is, $R_i$ and $R_j$ each have an edge from the same components, and all the other edges are from different components
-	\item Example of set $R_1$ BR procedure Figures
-	\item different edge from same component means components can be joined together to make single alt ham cycle
-	\item e.g. if $q = 4$, then $R_i$ has edges from $C_1, C_2$, and $R_j$ has edges from $C_2, C_3, C_4$, then there is an overlap (each set has an edge from $C_2$)
-	\item if there aren't two sets that cover all components and overlap only once, another method
-	\item third method - find set $R_i$ with largest cardinality, then run modified BR, where edges from the largest set $R_i$ are removed from the initial sorted list of edges, and then find a new set $R_j$ that contains an edge from a component that isn't covered by $R_i$, and an edge from a component that is covered by $R_i$ (the overlap)
-	\item continue to add succeeding edges as long as they aren't a member of a component already covered in $R_i$ or $R_j$
-	\item if end of list is reached, and not all components covered, delete edges that are in $R_j$ from the list of edges, and start again from the beginning
-	\item continue until no new sets can be made, then check to see if the sets cover all components, if not, infeasible, else feasible
-	\item connecting method/procedure - connect smaller-indexed vertex of each edge to higher-indexed vertex of next edge, except last edge, connect smallest of last edge to highest of first edge
-	\item then add these edges to $R'$ and remove the edges in $R_i$ from $R'$, so the cardinality of $R'$ should still be $n+1$ (perfect matching), and $R_i \cap R' = \emptyset$.
+	\item figures explain
 \end{itemize}
@@
 	\centering
-	\begin{subfigure}[h]{0.7\textwidth}
+	\begin{subfigure}[H]{0.5\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpsconnect}
@@
 	\end{subfigure} \quad
-	\begin{subfigure}[h]{0.7\textwidth}
+	\begin{subfigure}[H]{0.5\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpscycle}
@@
 \label{sec:scsppsoln}
-%move this to beginning
-The SCSPP is a generalisation of the classical one-dimensional bin-packing problem (BPP), where in the latter problem, the minimum scoring distance $\tau$ can be said to be equal to zero.
-It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}), and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.
-Instead, heuristics can be used to find near-optimal solutions in a shorter amount of time.
-One example is the greedy heuristic known as first-fit (FF), an online algorithm that places each item (in some arbitrary order) onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
-It has been shown that by arranging the items in decreasing order of size, a packing heuristic will produce a solution that is closer to the optimal than if the items are arranged in any other order (\citealp{johnson1974fast}).
-Applying FF onto items sorted in this manner yields the well-known first-fit decreasing (FFD) heuristic.
 
-An optimal solution of an instance of the SCSPP is a solution that consists of the fewest number of strips, $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
-
+\begin{itemize}
+	\item As mentioned in the introduction, SCSPP is an NP-hard problem, therefore heuristics used
+	\item Perhaps the simplest and most well-known heuristics for packing problems is First-Fit (FF), a greedy heuristic/online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip whose capacity will not be exceeded/such that the capacity of the strip is not exceeded.
+	\item It has been shown that there always exists at least one ordering of items such that FF produces an optimal solution (Lewis 2009, General-Purpose HC Method for OIMGP)
+	\item A simple modification yields the First-Fit Decreasing (FFD) heuristic, which sorts the items in non-increasing order of size prior to performing FF.
+	\item An optimal solution of an instance of the SCSPP is a solution that consists of the fewest number of strips, $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
 	\begin{equation}
@@
 	\end{equation}
-
 	where $n$ is the number of items in the set $\mathcal{I}$, $w_i$ the width of each item $i \in \mathcal{I}$, and $W$ is the width of the strips (\citealp{martello1990b}).
@@
 Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$.
+	\item However, this bound does not hold for our current problem, as, for example, if $\tau = \infty$, we would require $n$ strips.
+The value of $\tau$ is not taken into account in the original time complexity.
+	\item Difference between BPP and SCSPP: In BPP, an item can be removed from a bin, and feasibility will be retained, however in SCSPP it may not, as the vicinal sum constraint may no longer hold.
+	\item Therefore modifications must be made to maintain feasibility.
+	\item comparing three heuristics, a basic ffd (basic modification of original FFD), smallest first (Lewis2011) and a heuristic combining FFD and AHCA.
+	\item lower bound is also inaccurate, doesn't take into account score widths or $\tau$, very basic lower bound.
+	\item feasible candidate solution $\mathcal{S} = \{S_1, S_2,...,S_k\}$ such that
+	\item (a) $\bigcup S_i = \mathcal{I}$ (all items in $\mathcal{I}$ packed onto strips)
+	\item (b) $S_i \cap S_j = \emptyset$ $\forall i\neq j$ (each item packed onto exactly one strip)
+	\item (c) $\forall S_i \in \mathcal{S}$ the items on $S_i$ can be feasibly packed onto a single strip (vicinal sum constraint holds on every strip)
+	\item Aim is to minimise $k$.
+\end{itemize}
 
@@
 \end{comment}
+
+\begin{comment}
+\begin{itemize}
+	\item need to name this connecting algorithm/method/procedure
+	\item sets $R_1, R_2, ..., R_k \in R'$ are produced during BR
+	\item Connecting procedure detects collection of sets that combine all components of $G'$ together
+	\item only overlap once
+	\item If $k = 0$, i.e. not a single set $R_i$ created during BR, then no edges exist that can combine the components together - infeasible, cannot create alt ham cycle (no solution)
+	\item If $\exists$ set $R_i$ such that $|R_i| = q$, i.e. number of edges in $R_i$ equals number of components, then solution exists, need to connect components using connecting method/procedure
+	\item this is because there is an edge in each component that can be removed, and replaced with a new edge that bridges the components together 
+	\item otherwise, more than one set $R_i$ needed
+	\item second method - find two sets $R_i, R_j$ such that there is one red edge from each component of $G'$ in EITHER $R_i$ OR $R_j$, and there is one component of $G'$ that has one red edge in $R_i$ and another (different) red edge in $R_j$
+	\item that is, $R_i$ and $R_j$ each have an edge from the same components, and all the other edges are from different components
+	\item Example of set $R_1$ BR procedure Figures
+	\item different edge from same component means components can be joined together to make single alt ham cycle
+	\item e.g. if $q = 4$, then $R_i$ has edges from $C_1, C_2$, and $R_j$ has edges from $C_2, C_3, C_4$, then there is an overlap (each set has an edge from $C_2$)
+	\item if there aren't two sets that cover all components and overlap only once, another method
+	\item should have $|R_i| + |R_j| = q+1$, two edges from one component, one edge from all other components.
+	\item third method - find set $R_i$ with largest cardinality, then run modified BR, where edges from the largest set $R_i$ are removed from the initial sorted list of edges, and then find a new set $R_j$ that contains an edge from a component that isn't covered by $R_i$, and an edge from a component that is covered by $R_i$ (the overlap)
+	\item continue to add succeeding edges as long as they aren't a member of a component already covered in $R_i$ or $R_j$
+	\item if end of list is reached, and not all components covered, delete edges that are in $R_j$ from the list of edges, and start again from the beginning
+	\item continue until no new sets can be made, then check to see if the sets cover all components, if not, infeasible, else feasible
+	\item connecting method/procedure - connect smaller-indexed vertex of each edge to higher-indexed vertex of next edge, except last edge, connect smallest of last edge to highest of first edge
+	\item then add these edges to $R'$ and remove the edges in $R_i$ from $R'$, so the cardinality of $R'$ should still be $n+1$ (perfect matching), and $R_i \cap R' = \emptyset$.
+	\item multiple sets, cover all components, i.e. combining all edges from sets should mean that each component has at least one edge in the set
+	\item each set overlaps with at least one other set, and overlaps with that set only once (not all sets have to overlap with one another)
+	\item if such sets found, perform connecting method from above	
+\end{itemize}
+\end{comment}

### 2018-05-04 PAPER/main.tex
major changes

@@
 \documentclass[oribibl]{llncs}
-
 \input{includes/preamble.tex}
@@
 \institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
-
 \maketitle
@@
 \begin{abstract}
-
 \end{abstract}
@@
 \label{sec:intro}
-
 Firstly, let us introduce the Constrained Ordering Problem:
@@
 	\begin{equation}
-		\label{eqn:cop}
+		\label{eqn:vsc}
 		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
@@
 Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places.
-A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:boxknife}).
+A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:itemsknife}).
 However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry).
@@
 	\centering
-	\includestandalone[width=0.8\textwidth]{figures/boxesknifeannotate}
-	\caption{Width and score widths on an item $i \in \mathcal{I}$, and knives mounted on a bar score two items simultaneously}	
-	\label{fig:boxknife}
+	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
+	\caption{Dimensions of an item $i \in \mathcal{I}$, and knives mounted on a bar score two items simultaneously.}	
+	\label{fig:itemsknife}
 \end{figure}
@@
 \label{sec:ahca}
-
-%We shall now present an algorithm for solving the COP, which operates by expressing the problem instance graphically. 
 We shall now present an algorithm for solving the COP in polynomial time.
@@
 This is especially useful for problems such as the previously mentioned strip-packing problem, where a tangible solution is required in order to place the items in the correct order and orientation.
-\textcolor{OrangeRed}{USING GRAPH.}
+% We shall now present an algorithm for solving the COP, which operates by expressing the problem instance graphically.
 
-% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
-% Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
-% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..
 Let $\mathcal{M}$ be an instance of the COP of cardinality $n$.
@@
 
-Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$, and two distinct edge sets $B$ and $R$, such that $B \cap R = \emptyset$.
+Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$, and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$.
 Figure \ref{fig:partners/threshold} illustrates the construction of $G$ using the instance $\mathcal{M}$ from the example above.
+% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
+% Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
+% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..
 
@@
 \end{subfigure}
-\caption{Example construction of $G$ using instance $\mathcal{M}  = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$}
+\caption{Example construction of $G$ using instance $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$.}
 \label{fig:partners/threshold}
@@
 Consider the following definition describing a variant of the classical Hamiltonian cycle on a graph $G$.
-
 \begin{definition}
@@
 
-To find a matching $R' \subseteq R$, the following modified maximum cardinality matching (MMCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}: For each vertex $v_i, i=1,2,...,2n+2$, select the edge in $R$ connecting $v_i$ to the highest indexed vertex $v_j$ that is not already incident to an edge in $R'$.
+To find a matching $R' \subseteq R$, the following \textsc{Maximum Cardinality Matching} (MCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}: For each vertex $v_i, i=1,2,...,2n+2$, select the edge in $R$ connecting $v_i$ to the highest indexed vertex $v_j$ that is not already incident to an edge in $R'$.
 Add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed.
@@
 
-During this algorithm, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided that 
+During MCM, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided that 
 \begin{enumerate*}[label={(\alph*)}]
@@
 Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$.
-It is guaranteed that MMCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time (\citealp{mahadev1994}).
+It is guaranteed that MCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time (\citealp{mahadev1994}).
 
@@
 		\includestandalone[width=\textwidth]{figures/mps}
-		\caption{$G' =(V, B \cup R')$ planar}	
+		\caption{Planar representation of $G' =(V, B \cup R')$}	
 		\label{fig:mps}
 	\end{subfigure}
-	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MMCM algorithm. Planar graph, can see that $G'$ is made up of two components, $q = 2$}
+	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MCM. The planar representation shows $G'$ comprises $q = 2$ components.}
 	\label{fig:matching/mps}
@@
 However, if $q > 1$, the components of $G'$ must be combined to form an alternating Hamiltonian cycle.
-To do this, a Bridge Recognition (BR) algorithm can be executed that selects suitable edges from $R$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.
+To do this, a \textsc{Bridge Recognition} (BR) algorithm can be executed that selects suitable edges from $R$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.
 
@@
 For instance, in the example illustrated in Figure \ref{fig:matching/mps}, $(v_5, v_9)$ would be removed from the list, since the next edge in the list is $(v_6, v_{10})$, and so the higher-indexed vertices are not in decreasing order.
-This is due to $v_5$ not being matched with the highest-indexed vertex available, $v_{10}$, during MMCM, as $(v_5, v_{10}) \in B$.
+This is due to $v_5$ not being matched with the highest-indexed vertex available, $v_{10}$, during MCM, as $(v_5, v_{10}) \in B$.
 
@@
 If such a collection of sets exists, then the components of $G$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.
+% Refer to figures
 
-\begin{itemize}
-	\item figures explain
-\end{itemize}
-
-This algorithm, which will be referred to as the Alternating Hamiltonian Construction Algorithm (AHCA) is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP.
+This algorithm, which will be referred to as the \textsc{Alternating Hamiltonian Construction Algorithm} (AHCA) is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP.
 If a solution does indeed exist, AHCA can produce this solution in at most $O(n^2)$ time.
+% Cite Becker
 
@@
 		\includestandalone[width=\textwidth]{figures/mpsconnect}
-		\caption{connect}	
+		\caption{Edges from $R\backslash R'$ can connect vertices from different cycles.}	
 		\label{fig:mpsconnect}
-	\end{subfigure} \quad
+	\end{subfigure}
 	\begin{subfigure}[H]{0.5\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpscycle}
-		\caption{cycle}	
+		\caption{Replacing edges connects the components and forms an alternating Hamiltonian cycle.}	
 		\label{fig:mpscycle}
 	\end{subfigure}
-	\caption{connect and cycle}
+	\caption{Selected edges found using BR can be used to merge the components of $G'$ together, thus forming an alternating Hamiltonian cycle which corresponds to a feasible solution.}
 	\label{fig:connect/cycle}
@@
 	\label{thm:copsoln}
-	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the COP if and only if its corresponding graph $G(V, B\cup R)$ contains an alternating Hamiltonian cycle.
+	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the COP if and only if its corresponding graph $G=(V, B\cup R)$ contains an alternating Hamiltonian cycle.
 \end{theorem}
@@
 Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $B$.
-The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple.
-\textcolor{OrangeRed}{edges R vicinal sum constraint equation 2}.
-\qed
+The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple.\qed
 \end{proof}
-%put theorem here
-%explanation removing dominating vertices
-%why is this different from becker
 
-\section{Solving the SCSPP/Heuristics}
+\section{Solving the SCSPP}
 \label{sec:scsppsoln}
 
-\begin{itemize}
-	\item As mentioned in the introduction, SCSPP is an NP-hard problem, therefore heuristics used
-	\item Perhaps the simplest and most well-known heuristics for packing problems is First-Fit (FF), a greedy heuristic/online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip whose capacity will not be exceeded/such that the capacity of the strip is not exceeded.
-	\item It has been shown that there always exists at least one ordering of items such that FF produces an optimal solution (Lewis 2009, General-Purpose HC Method for OIMGP)
-	\item A simple modification yields the First-Fit Decreasing (FFD) heuristic, which sorts the items in non-increasing order of size prior to performing FF.
-	\item An optimal solution of an instance of the SCSPP is a solution that consists of the fewest number of strips, $k$. A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
+\begin{definition}
+	Let $\mathcal{I}' \subseteq \mathcal{I}$ be a set of items whose total width is less than or equal to the capacity of a strip, (i.e.
+$\sum_{i=1}^{|\mathcal{I}'|}w_i \leq W$).
+Given a minimum scoring distance $\tau$, the Score-Constrained Packing Sub-Problem (SCPSP) involves finding an arrangement of the items in $\mathcal{I}'$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
+\end{definition}
+
+(Why heuristics, using AHCA for SCSPP, explain) Perhaps the simplest and most well-known heuristic for packing problems is \textsc{First-Fit} (FF), a greedy online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
+It is known that there always exists at least one ordering of the items such that FF produces an optimal solution (\citealp{lewis2009}).
+A minor modification to FF yields the \textsc{First-Fit Decreasing} (FFD) heuristic, which sorts the items in non-increasing order of size prior to performing FF.
+
+For an instance of the SCSPP, a feasible solution is represented by the set $\mathcal{S} = \{S_1, S_2, ..., S_k\}$ such that
+\begin{subequations}
+	\begin{align}
+		\bigcup\nolimits_{j=1}^{|\mathcal{S}|} S_j &= \mathcal{I}, \label{eqn:packall}\\[3pt]
+		S_j \cap S_l &= \emptyset \hspace{5mm} \forall \hspace{1mm} j, l \in \{1, 2, ..., |\mathcal{S}|\}, \hspace{2mm} j \neq l, \label{eqn:nooverlap} \\[3pt]
+		\sum\nolimits_{i=1}^{|S_j|}w_i & \leq W \hspace{3mm} \forall \hspace{1mm} S_j \in \mathcal{S}, \label{eqn:capacity} \\[3pt]
+		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) &\geq \tau \hspace {5mm} \forall \hspace{1mm} i \in \{1, 2, ..., |S_j|-1\}, \hspace{2mm} \forall \hspace{1mm} S_j \in \mathcal{S}.
+\label{eqn:vscstrip}
+\end{align}
+\end{subequations}
+
+That is, all items must be packed onto a strip, each item can only be placed on one strip, the strips cannot be overpacked, and the items on each strip $S_j$ in the solution must be arranged such that the sum of two adjacent score widths is greater than or equal to the minimum scoring distance $\tau$.
+
+An optimal solution $\mathcal{S}$ of an instance of the SCSPP is a solution that consists of the fewest number of strips $k$.
+A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
 \begin{equation}
 \label{eqn:lowerbound}
-	k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{W}}
+k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{W}},
 \end{equation}
-	where $n$ is the number of items in the set $\mathcal{I}$, $w_i$ the width of each item $i \in \mathcal{I}$, and $W$ is the width of the strips (\citealp{martello1990b}).
+where $n$ is the number of items ($|\mathcal{I}|$), $w_i$ the width of each item $i \in \mathcal{I}$, and $W$ is the width of the strips (\citealp{martello1990b}).
 In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ strips.
@@
 Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$.
-	\item However, this bound does not hold for our current problem, as, for example, if $\tau = \infty$, we would require $n$ strips.
-The value of $\tau$ is not taken into account in the original time complexity.
-	\item Difference between BPP and SCSPP: In BPP, an item can be removed from a bin, and feasibility will be retained, however in SCSPP it may not, as the vicinal sum constraint may no longer hold.
-	\item Therefore modifications must be made to maintain feasibility.
-	\item comparing three heuristics, a basic ffd (basic modification of original FFD), smallest first (Lewis2011) and a heuristic combining FFD and AHCA.
-	\item lower bound is also inaccurate, doesn't take into account score widths or $\tau$, very basic lower bound.
-	\item feasible candidate solution $\mathcal{S} = \{S_1, S_2,...,S_k\}$ such that
-	\item (a) $\bigcup S_i = \mathcal{I}$ (all items in $\mathcal{I}$ packed onto strips)
-	\item (b) $S_i \cap S_j = \emptyset$ $\forall i\neq j$ (each item packed onto exactly one strip)
-	\item (c) $\forall S_i \in \mathcal{S}$ the items on $S_i$ can be feasibly packed onto a single strip (vicinal sum constraint holds on every strip)
-	\item Aim is to minimise $k$.
+
+As mentioned in the introduction, the SCSPP shares many similarities with the BPP, however the addition of constraint (\ref{eqn:vscstrip}) induces complications that must be taken into consideration.
+One obvious difference is the order in which the items must appear on the strips.
+In the BPP, removing an item retains feasibility, whereas in the SCSPP this is not guaranteed, as the constraint may not be fulfilled between the two score widths either side of the item removed.
+Furthermore, lower bound for $k$ (Equation (\ref{eqn:lowerbound})) does not hold for the SCSPP, as the minimum scoring distance $\tau$ is not included in the calculation.
+For example, if $\tau > 2 \max(b_i)$ (that is, the minimum scoring distance is greater than twice the largest score width), then it is clear that $n$ strips will be required, regardless of the items' widths.
+% Time complexity for FFD also inaccurate
+
+Three heuristics for the SCSPP have been developed: a basic FFD heuristic with a simple modification; a heuristic that packs strips individually and prioritises score widths; and a powerful version of FFD that incorporates the polynomial-time AHCA algorithm.
+
+\subsection{Modified First-Fit Decreasing Heuristic (MFFD)}
+\label{sec:mffd}
+The \textsc{Modified First-Fit Decreasing} (MFFD) heuristic performs in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip.
+If an item is able to be packed onto a strip without exceeding the strip's capacity, MFFD then checks to see if the vicinal sum constraint is met between the right-most score on the strip and one of the score widths on the current item.
+If the constraint is met, MFFD places the item on the end of the strip in the appropriate orientation, else the heuristic attempts to pack the item onto the next lowest-indexed strip.
+For example, in Figure \ref{fig:comparestrips}, the strip is able to accommodate the current item, however the vicinal sum constraint is not fulfilled regardless of the orientation of the item, and therefore the item cannot be feasibly packed onto the strip.
+
+Despite the additional step, MFFD is a very fast heuristic, as checking the vicinal sum constraint can be performed in constant time.
+The most prominent issue with this heuristic, however, is due to the items being placed on the end of the strips.
+Although an item may not meet the constraint when placed on the end of a strip, there may be another location on the strip where the item can be placed feasibly.
+MFFD is incapable of placing items anywhere other than on the end of the strips, and so an item that could potentially be packed must be placed on another strip, or perhaps even begin a new strip, thus increasing the number of strips in the final solution.
+
+\subsection{Pair-Smallest Heuristic (PS)}
+\label{sec:ps}
+
+The \textsc{Pair-Smallest} (PS) heuristic is an extension of a procedure defined by \cite{lewis2011}.
+Unlike MFFD, which packs each item in turn, PS focusses on packing one strip at a time, only starting a new strip once the current strip is unable to accommodate any more items feasibly.
+Each strip is initialised by choosing the item from $\mathcal{I}$ with the smallest score width, and packing it in a regular orientation.
+PS then continues to fill the strip by selecting the item with the smallest score width that meets the vicinal sum constraint with the right-most score width on the strip, and whose width will not cause the strip to be overfilled.
+This heuristic aligns the smallest score widths with the largest ones, eliminating the possibility of placing larger score widths together unecessarily.
+Note that PS prioritises the vicinal sum constraint over the item widths, choosing to fulfil the constraint first before considering whether the item can be accommodated.
+% Break ties by choosing item whose second score width is larger.
+
+\begin{itemize}
+	\item \cite{lewis2011}
+	\item Pack each strip one by one
+	\item choose item with smallest score width that meets VSC with right-most score width on the strip, then check if the item can fit onto the strip
+	\item if not, then choose item with second smallest score width that meets VSC, etc.
+	\item when no more items can fit onto strip/no item can meet VSC with right-most score width on the strip, close the strip (no more items canbe placed on it) and start new strip
+	\item If two items have equal score width, break ties by choosing item whose second score width is larger
+	\item this method aligns smallest score widths with larger ones, eliminates possibility of aligning larger score widths together unecessarily.
+	\item Heuristic prioritises VSC over item widths, chooses item with smallest possible score width that meets VSC first before checking item width.
 \end{itemize}
 
-\subsection{FFD Approx}
-\label{sec:ffdapprox}
-The first heuristic to be discussed is the Score-Constrained First-Fit Decreasing (SCFFD) heuristic, which is an extension of the original FFD.
-The items in $\mathcal{I}$ are, as usual, sorted in non-increasing order of widths, with ties broken by selecting the item with the smallest score width.
-Then, for each item $i \in \mathcal{I}$, SCFFD finds the lowest-indexed strip $S_j$ that can accommodate $i$ without being overfilled.
-If this strip $S_j$ is empty, place $i$ onto $S_j$ in a regular orientation, and add $S_j$ to the solution set $\mathcal{S}$.
-However, if $S_j$ is not empty, i.e.
-$S_j \in \mathcal{S}$, the algorithm checks if the vicinal sum constraint is met between the right-most score width on $S_j$ and one of the two score widths on $i$, assessing the smaller score width $a_i$ first.
-In either case, if the constraint is met, $i$ is placed accordingly onto $S_j$.
-Indeed, an item $i$ may not fulfil the vicinal sum constraint in any orientation, in which case SCFFD finds the next lowest-indexed strip and attempts to pack $i$ again.
-This process continues until every item $i \in \mathcal{I}$ has been placed onto a strip $S_j \in \mathcal{S}$.
-The additional check of the vicinal sum constraints and rotation of the items can be performed in constant time, and as such this heuristic has the same time complexity as FFD, $O(n \log n)$.
-This heuristic only checks the current items score widths against the right-most score width on a strip, and if the vicinal sum constraint is not met, the item cannot be placed on the strip.
-However, there may be another location on the strip that the item could be placed in feasibly, or a rearrangement of all items on the strip that produce a feasible alignment.
-
-\subsection{Smallest First}
-\label{sec:ffdsmall}
-This next heuristic focuses on packing each strip in turn, rather than each item as in the previous heuristic.
-Each new strip $S_j$ is initialised by placing the item $i \in \mathcal{I}'$ with the smallest score width onto $S_j$ in a regular position, where $\mathcal{I}'$ is the set of items that have not yet been packed onto a strip.
-The heuristic then continues to pack items onto $S_j$, by choosing an item in $\mathcal{I}'$ with the smallest score width that fulfils the vicinal sum constraint when placed alongside the right-most score width on $S_j$, and that does not exceed the capacity of $S_j$.
-Once there are no more items in $\mathcal{I}'$ that can be feasibly packed onto $S_j$, the heuristic adds $S_j$ to the solution set $\mathcal{S}$, and the next new strip $S_{j+1}$ is initialised.
-When $|\mathcal{I}'| = 0$, all items have been packed onto a strip, and the process terminates.
-This heuristic is designed to align score widths such that their sum is as close to the minimum scoring distance as possible, which eliminates the possibility of aligning larger score widths unecessarily.
-The larger score widths are then available to be aligned next to smaller score widths.
-Heuristic prioritises vicinal sum constraint over item widths.
-
-\subsection{FFD Exact}
-\label{sec:ffdexact}
-The last heuristic in this paper is formed by integrating the Alternating Hamiltonian Construction Algorithm (AHCA) detailed in Section ref{} with the classical FFD heuristic.
-Again, all items in $\mathcal{I}$ are sorted into non-increasing order of widths, with ties broken by choosing the item with the smallest score width.
-For each item $i \in \mathcal{I}$, the heuristic finds the lowest-indexed feasible strip $S_j$.
-As in the first heuristic, if $S_j$ is empty, $i$ is placed in a regular orientation onto $S_j$, and $S_j$ is then added to the solution set $\mathcal{S}$.
-Unlike the first heuristic, however, if $S_j$ is not empty ($S_j \in \mathcal{S}$), AHCA is applied on all items in $S_j$ and the current item $i$.
-If AHCA is successful, the items currently on $S_j$ are replaced by the new arrangement, which of course includes $i$.
-In the event that AHCA is unable to produce a solution, $S_j$ remains intact, and the heuristic attempts to pack $i$ onto the next lowest-indexed feasible strip.
-Due to the inclusion of AHCA, this heuristic is slower than the previous heuristics, with complexity $O(n^2)$.
-This heuristic has a significant advantage, however, as it is able to rearrange items entirely in order to find a feasible solution.
-In addition, we know that if a feasible alignment for a given set of items exists, AHCA is guaranteed to find and produce this solution.
-Thus, every subproblem in this heuristic, i.e.
-every time an item needs to be placed on a strip, can be solved exactly.
-For example, Figure \ref{fig:comparestrips} illustrates an instance of the SCSPP in which an item can feasibly fit onto a strip, i.e.
-the addition of the item onto the strip does not cause the strip's capacity to be exceeded.
-In the original version of FFD, the items on the strip are, as expected, in non-increasing order, and the right-most score width has a value of 3.
-Regardless of orientation, the current item cannot meet the vicinal sum constraint.
-The heuristic will therefore attempt to place the item onto another strip, or, if there are no other open strips, a new strip will be required to accommodate the item, thus increasing the total number of strips.
-However, by using FFDincAHCA, a feasible alignment of the items including the current item exists, and hence the item does not need to be placed elsewhere, minimising the risk of potentially adding a new strip to the solution.
+\subsection{Modified First-Fit Decreasing with AHCA (MFFD$^+$)}
+\label{sec:mffd+}
+\begin{itemize}
+	\item Like original FFD, sort items in non-increasing order, and attempt to pack each item into first strip that can feasibly accommodate the item without exceeding capacity
+	\item if item can fit onto strip, apply AHCA on all items on the strip and the current item to find a feasible alignment of the items
+	\item if solution found, place the items on the strip in the order of the solution
+	\item if no solution found, no feasible alignment exists, attempt to place current item on next strip
+	\item Using AHCA means if a feasible alignment of items inc current items exists (i.e. VSC is met between all items on strip), it will be found
+	\item Unlike in Basic FFD where an item cannot be placed on the end because VSC is not met, here we can find a solution
+	\item items may potentially be entirely rearranged, not in non-decreasing order on each strip as in Basic FFD
+	\item Slower as AHCA must be run for each item that can fit on a strip
+	\item see Figure \ref{fig:comparestrips}, item cannot be placed onto strip in Basic FFD heuristic as VSC is not met in either orientation of the item, whereas by using FFD+ a feasible solution can be found, item can be placed, no need to try another strip or start a new strip
+\end{itemize}
 
@@
 	\includestandalone[width=\textwidth]{figures/strips}
-	\caption{Comparison of two heuristics, maximum strip length is 18, $\tau = 70$.}	
+	\caption{Comparison of MFFD and MFFD$^+$, $W = 20$, $\tau = 70$.}	
 	\label{fig:comparestrips}
@@
 \section{Comparison}
-In order to provide a complete overview of the heuristics, sets of 100, 500, and 1000 items were used on strips of lengths 1250, 2500, and 5000.
-Item widths were randomly selected between 150 and 1000, and score widths between 1 and 70.
-This ensures that each item has two score lines.
-Changing the strip lengths changes the average number of items per strip.
+\begin{itemize}
+	\item $n$ = 100, 500, and 1000, number of items in $\mathcal{I}$, $W$ = 5000, 2500, 1250, item widths uniform dist [150, 1000], score widths uniform dist [1,70] (ensures each item has two score widths that do not overlap), all items and strips have height H ( = 1)
+	\item Changing strip length changes the average number of items per strip (why is this important?) Harder problems have fewer items per strip
+	\item run each instance 1000 times (per value of $\delta$), same instances each time.
+	\item table shows optimality, which is the number of strips in the final solution generated by the heuristic divided by the number of strips in the optimal solution (which is calculated using the lower bound for $k$ above), =1 then optimal
+	\item Goulimis stated n= 10, this is able to find solutions for n=1000
+	\item graph showing time or optimality of all three heuristics
+	\item changing the value of $\tau$ changes the proportion of the number of score widths
+	\item if $\delta = 0.0$, then no score widths can be aligned number of strips = $n$, $\delta = 1.0$, then all score widths can be aligned with any other score width, BPP.
+	\item As the strip length is decreased, ffd+ improves, number of items/strip decreases
+	\item when $\delta = 1.0$ basicffd and ffd+ will perform in the same manner (standard ffd)
+	\item Pairsmallest does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
+\end{itemize}
 
@@
 		\noalign{\smallskip}
-		& \multicolumn{3}{c}{$l = 5000$} & \multicolumn{3}{c}{$l = 2500$} & \multicolumn{3}{c}{$l = 1250$} \\
+		& \multicolumn{3}{c}{$W = 5000$} & \multicolumn{3}{c}{$W = 2500$} & \multicolumn{3}{c}{$W = 1250$} \\
 		\hline\noalign{\smallskip}
-		$\delta$ & Basic & Pair & FFD+ & Basic & Pair & FFD+ & Basic & Pair & FFD+ \\
+		$\delta$ & MFFD & PS & MFFD$^+$ & MFFD & PS & MFFD$^+$ & MFFD & PS & MFFD$^+$ \\
 		\noalign{\smallskip}
@@
 		\noalign{\smallskip}
-		0.0 & 0.116078 & 0.116078 &	0.116078 & 0.231142 & 0.231142 & 0.231142 & 0.461296 & 0.461296 & 0.461296 \\
-		0.1 & 0.191817 & \textbf{0.206796} & 0.193715 & 0.375914 & \textbf{0.403863} & 0.376151 & 0.65971 & \textbf{0.67634} & 0.659638 \\
-		0.2	& 0.247985 & \textbf{0.289553} & 0.251505 & 0.471136 & \textbf{0.541779} & 0.471511 & 0.753568 & \textbf{0.757848} & 0.753592 \\
-		0.3	& 0.321577 & \textbf{0.426852} & 0.329629 & 0.578598 & \textbf{0.717203} & 0.585497 & 0.836553 & 0.813063 & \textbf{0.837042} \\
-		0.4	& 0.411209 & \textbf{0.660488} & 0.436567 & 0.686034 & \textbf{0.886587} & 0.709649 & 0.900865 & 0.846469 & \textbf{0.902393} \\
-		0.5	& 0.526376 & \textbf{0.967058} & 0.597456 & 0.793717 & \textbf{0.968396} & 0.838188 & 0.946179 & 0.867053 & \textbf{0.950434} \\
-		0.6	& 0.672678 & \textbf{0.987213} & 0.805681 & 0.890082 & \textbf{0.971239} & 0.935295 & 0.97161 & 0.881001 & \textbf{0.976682} \\
-		0.7	& 0.839117 & \textbf{0.987909} & 0.959455 & 0.953589 & 0.973028 & \textbf{0.981477} & 0.983071 & 0.898796 & \textbf{0.986087} \\
-		0.8	& 0.954183 & 0.987787 &	\textbf{0.991791} & 0.984277 & 0.97413 & \textbf{0.992152} & 0.987373 & 0.917181 & \textbf{0.988403} \\
-		0.9	& 0.99056 &	0.988561 & \textbf{0.995444} & 0.992356 & 0.974811 & \textbf{0.993584} & 0.988397 & 0.931674 & \textbf{0.988545} \\
-		1.0	& \textbf{0.99555} & 0.987811 & \textbf{0.99555} & \textbf{0.993626} & 0.974892 & \textbf{0.993626} & \textbf{0.988883} & 0.938649 & \textbf{0.988883} \\
+		0.0 & 8.61813 & 8.61813 & 8.61813 & 4.32789 & 4.32789 & 4.32789 & 2.16858 & 2.16858 & 2.16858 \\
+		0.1 & 5.21367 & \textbf{4.84177} & 5.16085 & 2.65934 & \textbf{2.47735} & 2.65679 & 1.51486 & \textbf{1.47896} & 1.51486 \\
+		0.2 & 4.03055 & \textbf{3.45946} & 3.97645 & 2.12099 & \textbf{1.84737} & 2.11788 & 1.32613 & \textbf{1.31781} & 1.32610 \\
+		0.3 & 3.11091 & \textbf{2.34803} & 3.03816 & 1.72955 & \textbf{1.39676} & 1.70772 & 1.19451 & 1.22922 & \textbf{1.19381} \\
+		0.4 & 2.43605 & \textbf{1.52907} & 2.29713 & 1.45976 & \textbf{1.12798} & 1.40951 & 1.11037 & 1.18065 & \textbf{1.10819} \\
+		0.5 & 1.91057 & \textbf{1.04130} & 1.69129 & 1.26343 & \textbf{1.03341} & 1.19575 & 1.05771 & 1.15415 & \textbf{1.05319} \\
+		0.6 & 1.49086 & \textbf{1.01263} & 1.24645 & 1.12448 & \textbf{1.02957} & 1.06874 & 1.02932 & 1.13470 & \textbf{1.02398} \\
+		0.7 & 1.19571 & \textbf{1.01257} & 1.04468 & 1.04933 & 1.02774 & \textbf{1.01918} & 1.01741 & 1.11368 & \textbf{1.01444} \\
+		0.8 & 1.04977 & 1.01203 & \textbf{1.00815} & 1.01595 & 1.02661 & \textbf{1.00790} & 1.01297 & 1.09136 & \textbf{1.01197} \\
+		0.9 & 1.00929 & 1.01197 & \textbf{1.00463} & 1.00734 & 1.02586 & \textbf{1.00641} & 1.01159 & 1.07283 & \textbf{1.01139} \\
+		1.0 & \textbf{1.00423} & 1.01171 & \textbf{1.00423} & \textbf{1.00626} & 1.02561 & \textbf{1.00626} & \textbf{1.01130} & 1.06549 & \textbf{1.01130} \\		
 		\hline
@@
 		\noalign{\smallskip}
-		0.0	&0.115534&	0.115534&	0.115534&	0.230563&	0.230563&	0.230563&	0.460623&	0.460623&	0.460623 \\
-		0.1	&0.193119&	\textbf{0.206222} &	0.194298&	0.379134&	\textbf{0.402463}&	0.378162&	0.6614&	\textbf{0.681008}&	0.661144 \\
-		0.2	&0.251658&	\textbf{0.289114} &	0.253138&	0.478121&	\textbf{0.538655}&	0.475984&	0.758956&	\textbf{0.763423}&	0.758428 \\
-		0.3	&0.328699&	\textbf{0.427652} &	0.332872&	0.590141&	\textbf{0.711773}&	0.593915&	0.84501&	0.818874&	\textbf{0.845116} \\
-		0.4	&0.420561&	\textbf{0.65769} &	0.44084&	0.701106&	\textbf{0.8834}&	0.722513&	0.909988&	0.854863&	\textbf{0.910882} \\
-		0.5	&0.542993&	\textbf{0.976737} &	0.611842&	0.814597&	\textbf{0.970731}&	0.856799&	0.957862&	0.874602&	\textbf{0.961627} \\
-		0.6	&0.703725&	\textbf{0.987923} &	0.839692&	0.911433&	\textbf{0.973308}&	0.95286&	0.980911&	0.889836&	\textbf{0.985533} \\
-		0.7	&0.866696&	\textbf{0.98822} 	& 0.974979&	0.966382&	0.974971&	\textbf{0.987669}&	0.98836&	0.907816&	\textbf{0.990632} \\
-		0.8	&0.968441&	0.988482& \textbf{0.993951} &	0.989124&	0.976005&	\textbf{0.993392}&	0.991248&	0.927659&	\textbf{0.991882} \\
-		0.9	&0.99348&	0.988613& \textbf{0.995965} &	0.993528&	0.97652&	\textbf{0.994038}&	0.992179&	0.944748&	\textbf{0.992259} \\
-		1.0	& \textbf{0.995915} & 0.988288&	\textbf{0.995915} &	\textbf{0.994067}&	0.976631&	\textbf{0.994067}&	\textbf{0.992197}&	0.948814&	\textbf{0.992197} \\
+		0.0 & 8.65711 & 8.65711 & 8.65711 & 4.33803 & 4.33803 & 4.33803 & 2.17138 & 2.17138 & 2.17138 \\
+		0.1 & 5.17263 & \textbf{4.84248} & 5.14027 & 2.63606 & \textbf{2.48111} & 2.64271 & 1.51056 & \textbf{1.46744} & 1.51121 \\
+		0.2 & 3.97565 & \textbf{3.46163} & 3.95164 & 2.09301 & \textbf{1.85824} & 2.10161 & 1.31785 & \textbf{1.31090} & 1.31876 \\
+		0.3 & 3.04866 & \textbf{2.35023} & 3.01260 & 1.69777 & \textbf{1.40862} & 1.68776 & \textbf{1.18304} & 1.22111 & 1.18344 \\
+		0.4 & 2.37436 & \textbf{1.52046} & 2.26560 & 1.42646 & \textbf{1.13101} & 1.38430 & 1.09722 & 1.17063 & \textbf{1.09614} \\
+		0.5 & 1.84748 & \textbf{1.02600} & 1.64169 & 1.22960 & \textbf{1.03017} & 1.16950 & 1.04411 & 1.14430 & \textbf{1.03986} \\
+		0.6 & 1.43331 & \textbf{1.01212} & 1.20264 & 1.09935 & \textbf{1.02738} & 1.05010 & 1.01971 & 1.12392 & \textbf{1.01480} \\
+		0.7 & 1.15500 & \textbf{1.01198} & 1.02574 & 1.03421 & 1.02569 & \textbf{1.01224} & 1.01150 & 1.10164 & \textbf{1.00926} \\
+		0.8 & 1.03182 & 1.01182 & \textbf{1.00587} & 1.01111 & 1.02454 & \textbf{1.00682} & 1.00861 & 1.07791 & \textbf{1.00804} \\
+		0.9 & 1.00707 & 1.01165 & \textbf{1.00419} & 1.00663 & 1.02406 & \textbf{1.00608} & 1.00784 & 1.05885 & \textbf{1.00774} \\
+		1.0 & \textbf{1.00399} & 1.01169 & \textbf{1.00399} & \textbf{1.00603} & 1.02400 & \textbf{1.00603} & \textbf{1.00770} & 1.05406 & \textbf{1.00770} \\
 		\hline
@@
 
+\textbf{$n$ = 100}
 \begin{itemize}
-	\item Uniform distribution
-	\item only $n = 500$, the other two show the exact same trend, no need for unecessary data. 
-	\item $n = 500$, avg total item widths per instance (sum of all item widths) = 287684
-	\item $l = 5000$, avg lower bound = 58.039, avg items/strip = 8.62069
-	\item $l = 2500$, avg lower bound = 115.571, avg items/strip = 4.31034
-	\item $l = 1250$, avg lower bound = 230.648, avg items/strip = 2.16450
-	\item all items have height $h = 1$, strips have height $h = 1$
-	\item changing the value of $\tau$ changes the proportion of the number of score widths that meet the vicinal sum constraint, excluding itself and its partner
-	\item parameter $\delta$ defines the proportion, in 0.1 increments
-	\item if $\delta = 0.0$, then no score widths can be aligned, no matchings exist, each item requires its own strip, number of strips = $n$
-	\item if $\delta = 1.0$, then all score widths can be aligned with any other score width, problem becomes analogous to the classical one-dimensional BPP.
-	\item \cite{lewis2011}
-	\item As the strip length is decreased, ffd+ improves, number of items/strip decreases
-	\item basicffd never excels over the other two heuristics, only equals ffd+, since when $\delta = 1.0$, the problem is the same as a normal bpp, and so basicffd and ffd+ will perform in the same manner (standard ffd)
-	\item Pairsmallest does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
+	\item Average total item width = 57466.776, $\sigma$ = 2499.06092
+	\item $W = 5000$, Average LB = 11.993, $\sigma$ = 0.56829
+	\item $W = 2500$, Average LB = 23.478, $\sigma$ = 1.05618
+	\item $W = 1250$, Average LB = 46.466, $\sigma$ = 2.02703 
+\end{itemize}
+
+\textbf{$n$ = 500}
+\begin{itemize}
+	\item Average total item width = 287683.855, $\sigma$ = 5434.63046
+	\item $W = 5000$, Average LB = 58.039, $\sigma$ = 1.12227
+	\item $W = 2500$, Average LB = 115.571, $\sigma$ = 2.18150
+	\item $W = 1250$, Average LB = 230.648, $\sigma$ = 4.35041 
+\end{itemize}
+
+\textbf{$n$ = 1000}
+\begin{itemize}
+	\item Average total item width = 575163.174, $\sigma$ = 7880.93401
+	\item $W = 5000$, Average LB = 115.534, $\sigma$ = 1.59463
+	\item $W = 2500$, Average LB = 230.563, $\sigma$ = 3.16734
+	\item $W = 1250$, Average LB = 460.623, $\sigma$ = 6.30895 
 \end{itemize}
@@
 \end{document}
-
-\begin{comment}
-\begin{table}[!htb]
-\centering
-\caption{n = 100 l = 5000}
-\begin{tabular}{c@{\hspace{20pt}}c@{\hspace{20pt}}c@{\hspace{10pt}}c}
-\hline\noalign{\smallskip}
-$\delta$ & BasicFFD & PairSmallest & FFDincAHCA \\ 
-\noalign{\smallskip}
-\hline
-\noalign{\smallskip}
-0.0 & 0.11993 & 0.11993 & 0.11993 \\ 
-0.1 & 0.190373 & 0.209209 & 0.195007 \\ 
-0.2 & 0.241823 & 0.291742 & 0.252201 \\ 
-0.3 & 0.308598 & 0.423971 & 0.330489 \\ 
-0.4 & 0.387256 & 0.634770 & 0.435353 \\ 
-0.5 & 0.491093 & 0.900872 & 0.586398 \\ 
-0.6 & 0.612443 & 0.982422 & 0.753466 \\
-0.7 & 0.773879 & 0.986985 & 0.909705 \\
-0.8 & 0.904347 & 0.987407 &	0.980250 \\
-0.9 & 0.978801 & 0.984535 &	0.991745 \\
-1.0 & 0.995493 & 0.988851 &	0.995493 \\
-\hline
-\end{tabular}
-%\label{table:100/5000}
-\end{table}	
-\end{comment}
-
-\begin{comment}
-\begin{itemize}
-	\item need to name this connecting algorithm/method/procedure
-	\item sets $R_1, R_2, ..., R_k \in R'$ are produced during BR
-	\item Connecting procedure detects collection of sets that combine all components of $G'$ together
-	\item only overlap once
-	\item If $k = 0$, i.e. not a single set $R_i$ created during BR, then no edges exist that can combine the components together - infeasible, cannot create alt ham cycle (no solution)
-	\item If $\exists$ set $R_i$ such that $|R_i| = q$, i.e. number of edges in $R_i$ equals number of components, then solution exists, need to connect components using connecting method/procedure
-	\item this is because there is an edge in each component that can be removed, and replaced with a new edge that bridges the components together 
-	\item otherwise, more than one set $R_i$ needed
-	\item second method - find two sets $R_i, R_j$ such that there is one red edge from each component of $G'$ in EITHER $R_i$ OR $R_j$, and there is one component of $G'$ that has one red edge in $R_i$ and another (different) red edge in $R_j$
-	\item that is, $R_i$ and $R_j$ each have an edge from the same components, and all the other edges are from different components
-	\item Example of set $R_1$ BR procedure Figures
-	\item different edge from same component means components can be joined together to make single alt ham cycle
-	\item e.g. if $q = 4$, then $R_i$ has edges from $C_1, C_2$, and $R_j$ has edges from $C_2, C_3, C_4$, then there is an overlap (each set has an edge from $C_2$)
-	\item if there aren't two sets that cover all components and overlap only once, another method
-	\item should have $|R_i| + |R_j| = q+1$, two edges from one component, one edge from all other components.
-	\item third method - find set $R_i$ with largest cardinality, then run modified BR, where edges from the largest set $R_i$ are removed from the initial sorted list of edges, and then find a new set $R_j$ that contains an edge from a component that isn't covered by $R_i$, and an edge from a component that is covered by $R_i$ (the overlap)
-	\item continue to add succeeding edges as long as they aren't a member of a component already covered in $R_i$ or $R_j$
-	\item if end of list is reached, and not all components covered, delete edges that are in $R_j$ from the list of edges, and start again from the beginning
-	\item continue until no new sets can be made, then check to see if the sets cover all components, if not, infeasible, else feasible
-	\item connecting method/procedure - connect smaller-indexed vertex of each edge to higher-indexed vertex of next edge, except last edge, connect smallest of last edge to highest of first edge
-	\item then add these edges to $R'$ and remove the edges in $R_i$ from $R'$, so the cardinality of $R'$ should still be $n+1$ (perfect matching), and $R_i \cap R' = \emptyset$.
-	\item multiple sets, cover all components, i.e. combining all edges from sets should mean that each component has at least one edge in the set
-	\item each set overlaps with at least one other set, and overlaps with that set only once (not all sets have to overlap with one another)
-	\item if such sets found, perform connecting method from above	
-\end{itemize}
-\end{comment}

### 2018-05-04 PAPER/main.tex
minor changes section 3

@@
 Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, i.e.
-the values cannot be changed, and the values in each element cannot be separated, every edge in $B$ must be present in the alternating Hamiltonian cycle.
+the values cannot be changed and the values in each element cannot be separated, every edge in $B$ must be present in the alternating Hamiltonian cycle.
 Consequently, the task now involves finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.
@@
 
-The edges in $R'$ are sorted into a list such that the lower-indexed vertices of each edge are in increasing order of indices, and the higher-indexed vertices are in decreasing order of indices, i.e.
+The edges in $R'$ are sorted into a list such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order, i.e.
 $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$.
@@
 For instance, in the example illustrated in Figure \ref{fig:matching/mps}, $(v_5, v_9)$ would be removed from the list, since the next edge in the list is $(v_6, v_{10})$, and so the higher-indexed vertices are not in decreasing order.
-This is due to $v_5$ not being matched with the highest-indexed vertex available, $v_{10}$, during MCM, as $(v_5, v_{10}) \in B$.
+This is due to $v_5$ not being matched with the highest-indexed vertex available $v_{10}$ during MCM, as $(v_5, v_{10}) \in B$.
 
@@
 \begin{enumerate*}[label={(\alph*)}]
-	\item The lower-indexed vertex of the current edge, and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
+	\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
 	\item The current edge and the next edge are members of different components on $G'$.
@@
 	\end{subfigure}
-	\caption{Selected edges found using BR can be used to merge the components of $G'$ together, thus forming an alternating Hamiltonian cycle which corresponds to a feasible solution.}
+	\caption{Selected edges found using BR merge the components of $G'$ together, forming an alternating Hamiltonian cycle which corresponds to a feasible solution $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.}
 	\label{fig:connect/cycle}
@@
 If the constraint is met, MFFD places the item on the end of the strip in the appropriate orientation, else the heuristic attempts to pack the item onto the next lowest-indexed strip.
-For example, in Figure \ref{fig:comparestrips}, the strip is able to accommodate the current item, however the vicinal sum constraint is not fulfilled regardless of the orientation of the item, and therefore the item cannot be feasibly packed onto the strip.
+For example, in Figure \ref{fig:comparestrips}, the strip is able to accommodate the current item, however the vicinal sum constraint is not fulfilled in either orientation of the item, and therefore it cannot be feasibly packed onto the strip.
 
@@
 Note that PS prioritises the vicinal sum constraint over the item widths, choosing to fulfil the constraint first before considering whether the item can be accommodated.
+If there are multiple items with equal score widths, break ties by choosing the item whose second score width is the largest.
 % Break ties by choosing item whose second score width is larger.
-
-\begin{itemize}
-	\item \cite{lewis2011}
-	\item Pack each strip one by one
-	\item choose item with smallest score width that meets VSC with right-most score width on the strip, then check if the item can fit onto the strip
-	\item if not, then choose item with second smallest score width that meets VSC, etc.
-	\item when no more items can fit onto strip/no item can meet VSC with right-most score width on the strip, close the strip (no more items canbe placed on it) and start new strip
-	\item If two items have equal score width, break ties by choosing item whose second score width is larger
-	\item this method aligns smallest score widths with larger ones, eliminates possibility of aligning larger score widths together unecessarily.
-	\item Heuristic prioritises VSC over item widths, chooses item with smallest possible score width that meets VSC first before checking item width.
-\end{itemize}
+% If item with smallest feasible score width does not fit onto the strip, choose item with next smallest score width and repeat.
 

### 2018-05-05 SCSPP/COMBINED/base.h
changed layout of ResetVar function, parameters now on 2 lines instead of 3

@@ -12,9 +12,8 @@ Combined Program with Heuristics and EA
 #include <vector>
 using namespace std;
 
-void ResetVar(int numScores, int numItem, vector<int> &allScores, vector<int> &partners,
-              vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum,
-              vector<vector<int> > &strip);
+void ResetVar(int numScores, int numItem, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
+              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 void Output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int optLow, int numInstances);
 

### 2018-05-05 SCSPP/COMBINED/main.cpp
stripLength->stripWidth, BasicFFD->MFFD, FFDincAHCA->MFFDPlus, MMCM->MCM - minItemWidth w->m, max itemWidth W->M, stripWidth l->W in parameter arguments user input

@@ -46,9 +46,9 @@ void ProgramInfo(){
          << "       -n <int>    [Number of items. Default = 500.]\n"
          << "       -a <int>    [Minimum score width. Default = 1.]\n"
          << "       -b <int>    [Maximum score width. Default = 70.]\n"
-         << "       -w <int>    [Minimum item width. Default = 150.]\n"
-         << "       -W <int>    [Maximum item width. Default = 1000.]\n"
-         << "       -l <int>    [Length of strips. Default = 5000.]\n"
+         << "       -m <int>    [Minimum item width. Default = 150.]\n"
+         << "       -M <int>    [Maximum item width. Default = 1000.]\n"
+         << "       -W <int>    [Width of strips. Default = 5000.]\n"
          << "       -s <int>    [Random seed. Default = 1.]\n"
          << "---------------\n"
          << "ALGORITHM:\n"
@@ -63,7 +63,7 @@ void ProgramInfo(){
 }
 
 void ArgumentCheck(int numInstances, int tau, int numItem, int minWidth, int maxWidth, int minItemWidth, int maxItemWidth,
-                   int stripLength, int algType, int numPop, int xOver, int randomSeed){
+                   int stripWidth, int algType, int numPop, int xOver, int randomSeed){
 
     bool error = false;
 
@@ -73,8 +73,8 @@ void ArgumentCheck(int numInstances, int tau, int numItem, int minWidth, int max
         cout << "[WARNING]: Constraint value is zero, problem instances are equivalent to classical SPP without score constraints.\n";
         //error = true;
     }
-    if(stripLength == 0){
-        cout << "[ERROR]: Strip cannot have length zero.\n";
+    if(stripWidth == 0){
+        cout << "[ERROR]: Strip cannot have width zero.\n";
         error = true;
     }
     if(2*minWidth >= tau){
@@ -97,8 +97,8 @@ void ArgumentCheck(int numInstances, int tau, int numItem, int minWidth, int max
         cout << "[ERROR]: Minimum score width is greater than maximum score width.\n";
         error = true;
     }
-    if(maxItemWidth > stripLength){
-        cout << "[ERROR]: Maximum item width is larger than length of strip.\n";
+    if(maxItemWidth > stripWidth){
+        cout << "[ERROR]: Maximum item width is larger than width of strip.\n";
         error = true;
     }
     if(algType == 4 && numPop < 5){
@@ -125,15 +125,15 @@ void ArgumentCheck(int numInstances, int tau, int numItem, int minWidth, int max
[…]

### 2018-05-05 SCSPP/COMBINED/packing.cpp

@@ -16,21 +16,21 @@ void Swap(int &a, int &b){
     b = temp;
 }
 
-int LowerBound(double totalItemWidth, int stripLength){
+int LowerBound(double totalItemWidth, int stripWidth){
     int lBound;
 
-    lBound = ceil(totalItemWidth/stripLength);
+    lBound = ceil(totalItemWidth/stripWidth);
     return lBound;
 }
 
-double Fitness(int stripLength, vector<int> &stripSum, vector<vector<int> > &strip){
+double Fitness(int stripWidth, vector<int> &stripSum, vector<vector<int> > &strip){
 
     int i;
     double total = 0.0;
     double final;
 
     for(i = 0; i < strip.size(); ++i){
-        double a = static_cast<double>(stripSum[i]) / static_cast<double>(stripLength);
+        double a = static_cast<double>(stripSum[i]) / static_cast<double>(stripWidth);
         total += pow(a, 2);
     }
 
@@ -67,9 +67,9 @@ void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &o
 } //End Optimality
 
 // FFD checking vicinal sum constraint for both sides of each item.
-void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
-              int stripLength, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
+void MFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
+          int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners,
+          vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
     int i, j, mini;
     int min = 0;
     int max = maxItemWidth;
@@ -100,7 +100,7 @@ void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt
     for(j = 1; j < itemDecrease.size(); ++j){
         for(i = 0; i < strip.size(); ++i){
             if(!strip[i].empty()){
[…]

### 2018-05-05 SCSPP/COMBINED/packing.h

@@ -14,52 +14,52 @@ using namespace std;
 
 void Swap(int &a, int &b);
 
-int LowerBound(double totalItemWidth, int stripLength);
+int LowerBound(double totalItemWidth, int stripWidth);
 
-double Fitness(int stripLength, vector<int> &stripSum, vector<vector<int> > &strip);
+double Fitness(int stripWidth, vector<int> &stripSum, vector<vector<int> > &strip);
 
 void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB);
 
-void BasicFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
-              int stripLength, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void MFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
+          int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners,
+          vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
 void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
-                  int stripLength, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
+                  int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
                   vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // FFD including AHCA, instead of attempting to place item on end of strip, run AHCA to find feasible solution.
-void FFDincAHCA(int tau, int &opt, int &opt90, int &opt80, int &opt70,
-                int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth, int stripLength, double totalItemWidth,
[…]

### 2018-05-05 PAPER/main.tex
started MFFD+ section, added average speeds to comparison, changed figure 1

@@
 	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
-	\caption{Dimensions of an item $i \in \mathcal{I}$, and knives mounted on a bar score two items simultaneously.}	
+	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation, and a feasible alignment of two items that can be scored simultaneously.}	
 	\label{fig:itemsknife}
@@
 
-\section{Solving the SCSPP}
+\section{Heuristics for the SCSPP}
 \label{sec:scsppsoln}
@@
 \begin{definition}
+	\label{defn:subprob}
 	Let $\mathcal{I}' \subseteq \mathcal{I}$ be a set of items whose total width is less than or equal to the capacity of a strip, (i.e.
@@
 \label{sec:mffd+}
+
+The last heuristic incorporates AHCA as described in Section \ref{sec:ahca}.
+The \textsc{Modified First-Fit Decreasing with AHCA} (MFFD$^+$) heuristic operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.
+However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ then executes AHCA on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$.
+If AHCA finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip.
+
 \begin{itemize}
@@
 	\item if no solution found, no feasible alignment exists, attempt to place current item on next strip
-	\item Using AHCA means if a feasible alignment of items inc current items exists (i.e. VSC is met between all items on strip), it will be found
-	\item Unlike in Basic FFD where an item cannot be placed on the end because VSC is not met, here we can find a solution
-	\item items may potentially be entirely rearranged, not in non-decreasing order on each strip as in Basic FFD
+	\item Using AHCA means if a feasible alignment of items inc current items exists (i.e. VSC is met between all items on strip), it will be found (guaranteed)
+	\item Unlike in MFFD where an item cannot be placed on the end because VSC is not met, here we can find a solution
+	\item items may potentially be entirely rearranged, not in non-decreasing order on each strip as in MFFD (refer to Figure \ref{fig:comparestrips})
 	\item Slower as AHCA must be run for each item that can fit on a strip
-	\item see Figure \ref{fig:comparestrips}, item cannot be placed onto strip in Basic FFD heuristic as VSC is not met in either orientation of the item, whereas by using FFD+ a feasible solution can be found, item can be placed, no need to try another strip or start a new strip
+	\item see Figure \ref{fig:comparestrips}, item cannot be placed onto strip in MFFD heuristic as VSC is not met in either orientation of the item, whereas by using MFFD$^+$ a feasible solution can be found, item can be placed, no need to try another strip or start a new strip
+	\item each iteration when an item can fit onto the strip, we have an instance of the sub problem, where the items on the strip and the current items are in the subset $\mathcal{I}' \subseteq \mathcal{I}$ Refer to definition \ref{defn:subprob}.
+	\item Then run AHCA on the subproblem, ignore all other strips.
+	\item worst case is AHCA is performed for each item on every strip in $\mathcal{S}$ so far (except when new strip needs to be started, AHCA isn't performed, item is simply placed in regular orientation at beginning of the strip).
+	\item reduces chances of needing to start a new strip, therefore reducing possibility of increasing number of strips in final solution.
+
 \end{itemize}
@@
 \begin{itemize}
+	\item Heuristics implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
 	\item $n$ = 100, 500, and 1000, number of items in $\mathcal{I}$, $W$ = 5000, 2500, 1250, item widths uniform dist [150, 1000], score widths uniform dist [1,70] (ensures each item has two score widths that do not overlap), all items and strips have height H ( = 1)
@@
 	\item graph showing time or optimality of all three heuristics
+	\item $\delta$ is proportion of score widths that meet VSC (excluding partners and itself), 0.1 increments.
 	\item changing the value of $\tau$ changes the proportion of the number of score widths
 	\item if $\delta = 0.0$, then no score widths can be aligned number of strips = $n$, $\delta = 1.0$, then all score widths can be aligned with any other score width, BPP.
-	\item As the strip length is decreased, ffd+ improves, number of items/strip decreases
-	\item when $\delta = 1.0$ basicffd and ffd+ will perform in the same manner (standard ffd)
-	\item Pairsmallest does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
+	\item As the strip length is decreased, MFFD+ improves, number of items/strip decreases
+	\item when $\delta = 1.0$ MFFD and MFFD+ will perform in the same manner (like original FFD)
+	\item PS does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
+	\item as avg number of items per strip decreases, PS is less efficient, MFFD+ is better
+	\item note anomaly in $n = 1000, W = 1250, \delta = 0.3$, MFFD performs the best.
 \end{itemize}
@@
 	\item Average total item width = 57466.776, $\sigma$ = 2499.06092
-	\item $W = 5000$, Average LB = 11.993, $\sigma$ = 0.56829
-	\item $W = 2500$, Average LB = 23.478, $\sigma$ = 1.05618
-	\item $W = 1250$, Average LB = 46.466, $\sigma$ = 2.02703 
+	\item $W = 5000$, Average LB = 11.993, $\sigma$ = 0.56829, Average speed = 38.88504ms/instance
+	\item $W = 2500$, Average LB = 23.478, $\sigma$ = 1.05618, Average speed = 38.55795ms/instance
+	\item $W = 1250$, Average LB = 46.466, $\sigma$ = 2.02703, Average speed = 37.98091ms/instance
 \end{itemize}
@@
 	\item Average total item width = 287683.855, $\sigma$ = 5434.63046
-	\item $W = 5000$, Average LB = 58.039, $\sigma$ = 1.12227
-	\item $W = 2500$, Average LB = 115.571, $\sigma$ = 2.18150
-	\item $W = 1250$, Average LB = 230.648, $\sigma$ = 4.35041 
+	\item $W = 5000$, Average LB = 58.039, $\sigma$ = 1.12227, Average speed = 42.11938ms/instance
+	\item $W = 2500$, Average LB = 115.571, $\sigma$ = 2.18150, Average speed = 44.24521ms/instance
+	\item $W = 1250$, Average LB = 230.648, $\sigma$ = 4.35041, Average speed = 49.66614ms/instance
 \end{itemize}
@@
 	\item Average total item width = 575163.174, $\sigma$ = 7880.93401
-	\item $W = 5000$, Average LB = 115.534, $\sigma$ = 1.59463
-	\item $W = 2500$, Average LB = 230.563, $\sigma$ = 3.16734
-	\item $W = 1250$, Average LB = 460.623, $\sigma$ = 6.30895 
+	\item $W = 5000$, Average LB = 115.534, $\sigma$ = 1.59463, Average speed = 214.04479ms/instance
+	\item $W = 2500$, Average LB = 230.563, $\sigma$ = 3.16734, Average speed = 190.36579ms/instance
+	\item $W = 1250$, Average LB = 460.623, $\sigma$ = 6.30895, Average speed = 214.78729ms/instance
 \end{itemize}

### 2018-05-07 PAPER/main.tex
added ham cycle defn, moved sub problem defn, finished draft MFFD+

--- 2018-05-04 PAPER/main.tex
@@
 	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
-	\caption{Dimensions of an item $i \in \mathcal{I}$, and knives mounted on a bar score two items simultaneously.}	
+	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation $(a_i, b_i)$, and a feasible alignment of two items that can be scored simultaneously.}	
 	\label{fig:itemsknife}
@@
 
+\begin{definition}
+	\label{defn:subprob}
+	Let $\mathcal{I}' \subseteq \mathcal{I}$ be a set of items whose total width is less than or equal to the capacity of a strip, (i.e.
+$\sum_{i=1}^{|\mathcal{I}'|}w_i \leq W$).
+Given a minimum scoring distance $\tau$, the Score-Constrained Packing Sub-Problem (SCPSP) involves finding an arrangement of the items in $\mathcal{I}'$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
+\end{definition}
+
 The remainder of this article will firstly, in Section 2, detail a polynomial-time algorithm that is able to produce a solution to any instance of the COP, if a solution exists.
-Section 3 describes three heuristics that will be used to find feasible solutions to the SCSPP, and discusses the associated advantages and disadvantages.
+Section 3 describes three heuristics that can be used to find feasible solutions to the SCSPP, and discusses the associated advantages and disadvantages.
 A comparison of these heuristics and an analysis of the results will be provided in Section 4, and finally Section 5 concludes the paper and proposes some potential directions for future work.
@@
 It can be seen that $B$ is a perfect matching, with $|B|= n+1$.
+Let the bijective function $p: V \to V$ associate each vertex with its partner, $p(v_i) = v_j$.
+Hence $B = \{(v_i, p(v_i)) : v_i \in V\}$
 
@@
 
-Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$, and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$.
+Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$ and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$.
 Figure \ref{fig:partners/threshold} illustrates the construction of $G$ using the instance $\mathcal{M}$ from the example above.
 % Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
-% Bijective function $p: V \to V$ assoc each vertex with its partner, $v_j = p(v_i)$
 % Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..
@@
 \end{subfigure}
-\caption{Example construction of $G$ using instance $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$.}
+\caption{Construction of $G$ using instance $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, where $v_{13}$ and $v_{14}$ are the dominating vertices.}
 \label{fig:partners/threshold}
@@
 
-Consider the following definition describing a variant of the classical Hamiltonian cycle on a graph $G$.
+Recall that a Hamiltonian cycle on a graph $G$ is a cycle that visits every vertex exactly once.
+Now, consider the following definition describing a variant of the classical Hamiltonian cycle involving multiple edge sets.
 \begin{definition}
@@
 The two vertices incident to each matching edge in $R'$ are now referred to as being ``matched''.
+Similarly to partners, let $m : V \to V$ be a bijective function that assigns each vertex with its match, $m(v_i) = v_j$.
+Then, $R' =\{(v_i, m(v_i)) : v_i \in V\}$.
 
@@
 	\item $v_i$ is not the first vertex; 
-	\item $v_{i-1} \in R'$; and
+	%\item $v_{i-1} \in R'$; and
+	\item $(v_{i-1}, m(v_{i-1})) \in R'$; and
 	\item $(v_{i-1}, p(v_i)) \in R$.
 \end{enumerate*}
-Then, $v_{i-1}$ is matched with $p(v_i)$, and $v_i$ is matched with the vertex that was previously matched with $v_{i-1}$.
+Then, $v_i$ is matched with the vertex that is currently matched with $v_{i-1}$, i.e $m(v_i) = m(v_{i-1})$, and $v_{i-1}$ is rematched with $p(v_i)$, i.e.
+$m(v_{i-1}) = p(v_i)$.
 It is guaranteed that MCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time (\citealp{mahadev1994}).
@@
 
-\section{Solving the SCSPP}
+\section{Heuristics for the SCSPP}
 \label{sec:scsppsoln}
-
-\begin{definition}
-	Let $\mathcal{I}' \subseteq \mathcal{I}$ be a set of items whose total width is less than or equal to the capacity of a strip, (i.e.
-$\sum_{i=1}^{|\mathcal{I}'|}w_i \leq W$).
-Given a minimum scoring distance $\tau$, the Score-Constrained Packing Sub-Problem (SCPSP) involves finding an arrangement of the items in $\mathcal{I}'$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
-\end{definition}
 
@@
 \label{sec:mffd+}
-\begin{itemize}
-	\item Like original FFD, sort items in non-increasing order, and attempt to pack each item into first strip that can feasibly accommodate the item without exceeding capacity
-	\item if item can fit onto strip, apply AHCA on all items on the strip and the current item to find a feasible alignment of the items
-	\item if solution found, place the items on the strip in the order of the solution
-	\item if no solution found, no feasible alignment exists, attempt to place current item on next strip
-	\item Using AHCA means if a feasible alignment of items inc current items exists (i.e. VSC is met between all items on strip), it will be found
-	\item Unlike in Basic FFD where an item cannot be placed on the end because VSC is not met, here we can find a solution
-	\item items may potentially be entirely rearranged, not in non-decreasing order on each strip as in Basic FFD
-	\item Slower as AHCA must be run for each item that can fit on a strip
-	\item see Figure \ref{fig:comparestrips}, item cannot be placed onto strip in Basic FFD heuristic as VSC is not met in either orientation of the item, whereas by using FFD+ a feasible solution can be found, item can be placed, no need to try another strip or start a new strip
-\end{itemize}
+
+The last heuristic incorporates AHCA as described in Section \ref{sec:ahca}.
+The \textsc{Modified First-Fit Decreasing with AHCA} (MFFD$^+$) heuristic operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.
+However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ then executes AHCA on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}).
+If AHCA finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip.
+Using AHCA means that if a feasible alignment of the items exists, there is a guarantee that it will be found.
+Unlike MFFD, where the current item can only be placed on the end of the strip, MFFD$^+$ allows the items to be entirely rearranged (see Figure \ref{fig:comparestrips}).
+This reduces the possibility of having to start a new strip for an item, thus preventing increasing the number of strips in the final solution.
 
@@
 
+\textbf{Speed $n$ = 500}
+\begin{itemize}
+	\item MFFD $W = 5000$ Average speed = 38.88504ms/instance
+	\item MFFD $W = 2500$ Average speed = 38.55795ms/instance
+	\item MFFD $W = 1250$ Average speed = 37.98091ms/instance
+	\item PS $W = 5000$ Average speed = 42.11938ms/instance
+	\item PS $W = 2500$ Average speed = 44.24521ms/instance
+	\item PS $W = 1250$ Average speed = 49.66614ms/instance
+	\item MFFD$^+$ $W = 5000$ Average speed = 214.04479ms/instance
+	\item MFFD$^+$ $W = 2500$ Average speed = 190.36579ms/instance
+	\item MFFD$^+$ $W = 1250$ Average speed = 214.78729ms/instance
+\end{itemize}
+
+\textbf{Speed $n$ = 1000}
+\begin{itemize}
+	\item MFFD $W = 5000$ Average speed = 159.68755ms/instance
+	\item MFFD $W = 2500$ Average speed = 
+	\item MFFD $W = 1250$ Average speed = 
+	\item PS $W = 5000$ Average speed = 
+	\item PS $W = 2500$ Average speed = 
+	\item PS $W = 1250$ Average speed = 
+	\item MFFD$^+$ $W = 5000$ Average speed = 
+	\item MFFD$^+$ $W = 2500$ Average speed = 
+	\item MFFD$^+$ $W = 1250$ Average speed = 
+\end{itemize}
+
 \bibliographystyle{dcu}

### 2018-05-08 PAPER/main.tex
made changes suggested by Rhyd

@@
 \label{sec:intro}
-Firstly, let us introduce the Constrained Ordering Problem:
+Firstly, let us introduce the Constrained Ordering Problem (COP):
 
@@
 
-One prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004.
-A set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right.
+A prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \cite{goulimis2004}.
+Here, a set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right.
 Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places.
@@
 Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
-Specifically, as the items are packed from left to right, this involves checking the sum of the right-hand score width of each item $i$ and the left-hand score width of the next item $i+1$ on the strip.
 The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.
@@
 
-It can be seen that this problem is in fact analogous to the COP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance.
-Thus, a set $\mathcal{I}$ of items has a feasible arrangement if the equivalent COP has a solution $\mathcal{T}$ that meets the vicinal sum constraint.
+It can be seen that this problem is in fact equal to the COP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance.
 
-Observe that, in this particular strip-packing problem, the widths of the individual items are disregarded entirely, since the aim is to arrange the items onto a strip of seemingly infinite width.
-In practical applications, strips of material are often provided in fixed widths.
+Observe that in this particular strip-packing problem the widths of the individual items are disregarded, since the aim is to arrange the items onto a strip of seemingly infinite width.
+However, in industrail applications, strips of material are often provided in fixed widths.
 Given a large problem instance, multiple strips may therefore be required to feasibly accommodate all of the items.
-For this reason, we define a new problem to be investigated.
+For this reason, a more generalised problem can also be formulated.
 
@@
 	\label{defn:scspp}
-	Let $\mathcal{S} = \{S_1, S_2, ..., S_k\}$ be a set of strips of height $H$ and width $W$, and let $\mathcal{I}$ be a set of rectangular items of height $H$ and varying widths $w_i \in \mathbb{Z}^+ < W$ and score widths $a_i, b_i \in \mathbb{Z}^+$ such that $a_i \leq b_i$ and $a_i + b_i < w_i$ for each item $i \in \mathcal{I}$.
+	Let $\mathcal{S} = \{S_1, S_2, ..., S_k\}$ be a set of strips of height $H$ and width $W$, and let $\mathcal{I}$ be a set of rectangular items of height $H$ and varying widths $w_i \in \mathbb{Z}^+ \leq W$ and score widths $a_i, b_i \in \mathbb{Z}^+$ such that $a_i \leq b_i$ and $a_i + b_i < w_i$ for each item $i \in \mathcal{I}$.
 Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips $k$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
@@
 
-The SCSPP is a generalisation of the classical one-dimensional bin-packing problem (BPP), where in the latter problem the minimum scoring distance $\tau$ can be said to be equal to zero.
+Note that in the special case of $\tau = 0$, the SCSPP is equivalent to the classical one-dimensional bin-packing problem (BPP).
 It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}), and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.
@@
 
-The remainder of this article will firstly, in Section 2, detail a polynomial-time algorithm that is able to produce a solution to any instance of the COP, if a solution exists.
-Section 3 describes three heuristics that can be used to find feasible solutions to the SCSPP, and discusses the associated advantages and disadvantages.
+The remainder of this article is structured as follows: In Section 2, we will detail an exact polynomial-time algorithm for the COP, if a solution exists.
+Section 3 then describes three heuristics that can be used to find feasible solutions to the SCSPP and the associated advantages and disadvantages.
 A comparison of these heuristics and an analysis of the results will be provided in Section 4, and finally Section 5 concludes the paper and proposes some potential directions for future work.
@@
 \label{sec:ahca}
-We shall now present an algorithm for solving the COP in polynomial time.
-The original(underlying) algorithm was created by \cite{becker2010}, and determines whether or not a solution exists for a given instance.
-We have extended this algorithm so that, if a solution does indeed exist, the algorithm is able to formulate and present us with this final solution.
-This is especially useful for problems such as the previously mentioned strip-packing problem, where a tangible solution is required in order to place the items in the correct order and orientation.
+We shall now present an exact polynomial-time algorithm for the COP.
+The underlying algorithm was originally created by \cite{becker2010}, and is used to determine whether or not a solution exists for a given instance.
+In our case, we have extended this algorithm so that, if a solution does indeed exist, the algorithm is able to formulate and present us with this final solution.
+This is especially useful for problems such as the previously mentioned strip-packing problem, where a solution is required in order to place the items in the correct order and orientation.
 % We shall now present an algorithm for solving the COP, which operates by expressing the problem instance graphically.
@@
 Let $\mathcal{M}$ be an instance of the COP of cardinality $n$.
-We model each of the values of all elements in $\mathcal{M}$ as a vertex on a graph $G$, and assign each vertex a value from $\mathcal{M}$ in non-decreasing order.
-A pair of vertices, called ``dominating vertices'' are then added to the graph, both of which are assigned values equal to $\tau$.
+It is now useful to model $\mathcal{M}$ a a graph $G$ in which each vertex is associated with a single value in $\mathcal{M}$ in non-decreasing order.
+A pair of vertices, called ``dominating vertices'' are also added to the graph, both of which are assigned values equal to $\tau$.
 These dominating vertices aid the solution process, and are removed at the end.
@@
 
-The values in $\mathcal{M}$, and thus the vertices on $G$, are arranged in pairs.
-This is represented on $G$ by adding a set of ``blue'' edges, $B$, that contains edges between vertices that are ``partners'', i.e.
-whose values make up a pair in $\mathcal{M}$.
-It can be seen that $B$ is a perfect matching, with $|B|= n+1$.
+As we have seen, the values in $\mathcal{M}$ are arranged in pairs.
+This is represented in $G$ by adding a set of ``blue'' edges, $B$, that contains edges between vertices that are ``partners'', i.e.
+whose values make up a pair in $\mathcal{M}$, as shown in Figure \ref{fig:partners}.
+It can be seen that $B$ is a perfect matching in $G$, with $|B|= n+1$.
 Let the bijective function $p: V \to V$ associate each vertex with its partner, $p(v_i) = v_j$.
-Hence $B = \{(v_i, p(v_i)) : v_i \in V\}$
+Hence $B = \{(v_i, p(v_i)) : v_i \in V\}$.
 
-Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose values equal or exceed $\tau$, provided they are not partners.
+Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose sum equal or exceed $\tau$, provided they are not partners.
 This corresponds to the vicinal sum constraint in Defintion \ref{defn:cop}.
-
 Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$ and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$.
-Figure \ref{fig:partners/threshold} illustrates the construction of $G$ using the instance $\mathcal{M}$ from the example above.
+Figure \ref{fig:partners/threshold} illustrates and example construction of $G$.
 % Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
@@
 $G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such that successive edges alternate between sets $B$ and $R$.
-For example, if $(v_{i-1}, v_i) \in B$, then $(v_i, v_{i+1}) \in R$, or vice versa.
 \end{definition}
 
-An alternating Hamiltonian cycle on $G$ would correpsond to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ shows values that can be placed alongside one another feasibly.
-Thus, by removing the dominating vertices and any incident edges, the remaining alternating Hamiltonian path illustrates the order in which the elements should be placed to produce a feasible solution $\mathcal{T}$.
+An alternating Hamiltonian cycle on $G$ correpsonds to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ shows values that can be placed alongside one another feasibly.
+Thus, by removing the dominating vertices and any incident edges, the remaining alternating Hamiltonian path gives the order in which the elements should be placed to produce a feasible solution $\mathcal{T}$, if indeed one exists.
 
-Since the values in each unordered pair in $\mathcal{M}$ cannot be altered, i.e.
-the values cannot be changed and the values in each element cannot be separated, every edge in $B$ must be present in the alternating Hamiltonian cycle.
-Consequently, the task now involves finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.
+Also, note that every edge in $B$ must be present in the alternating Hamiltonian cycle.
+Consequently, the task can be seen as finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.
 
-To find a matching $R' \subseteq R$, the following \textsc{Maximum Cardinality Matching} (MCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}: For each vertex $v_i, i=1,2,...,2n+2$, select the edge in $R$ connecting $v_i$ to the highest indexed vertex $v_j$ that is not already incident to an edge in $R'$.
-Add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed.
+To find a matching $R' \subseteq R$, the following \textsc{Maximum Cardinality Matching} (MCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}.
+Take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest indexed vertex $v_j$ that is not already incident to an edge in $R'$.
+Now add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed.
 The two vertices incident to each matching edge in $R'$ are now referred to as being ``matched''.
@@
 	\end{subfigure}
-	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MCM. The planar representation shows $G'$ comprises $q = 2$ components.}
+	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MCM. The same solution is shown in planar form in (b).}
 	\label{fig:matching/mps}
@@
 
-Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence no feasible solution can be found for the given instance $\mathcal{M}$ of the COP.
-Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$ (see Figure \ref{fig:matching/mps}).
-$G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_q$.
+Clearly, if $|R'| < n+1$ after MCM are completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and hence no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
+Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$ (see Figure \ref{fig:matching/mps}).
+$G'$ therefore consists of a collection of cyclic components $C_1, C_2, ..., C_q$.
 In the case where $G'$ comprises one component, i.e.
-$q = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists.
-However, if $q > 1$, the components of $G'$ must be combined to form an alternating Hamiltonian cycle.
+$q = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP.
+However, if $q > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle.
 To do this, a \textsc{Bridge Recognition} (BR) algorithm can be executed that selects suitable edges from $R$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.
 
-The edges in $R'$ are sorted into a list such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order, i.e.
+BR operates by first ordering the edges in $R'$ such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order, i.e.
 $(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$.
 Any edges that cannot be placed in such an order are then removed from this list.
-For instance, in the example illustrated in Figure \ref{fig:matching/mps}, $(v_5, v_9)$ would be removed from the list, since the next edge in the list is $(v_6, v_{10})$, and so the higher-indexed vertices are not in decreasing order.
-This is due to $v_5$ not being matched with the highest-indexed vertex available $v_{10}$ during MCM, as $(v_5, v_{10}) \in B$.
+For instance, in the example illustrated in Figure \ref{fig:matching/mps}, the edges would be sorted as follows: $(v_1, v_{14}), (v_2, v_{13}),(v_3, v_{12}),(v_4, v_{11}),(v_6, v_{10}),(v_7, v_8).$
 
-Starting from the first edge, BR searches through the list to find an edge that meets the following conditions: 
+Starting from the first edge in the list, BR then searches through the list to find an edge that meets the following conditions: 
 \begin{enumerate*}[label={(\alph*)}]
@@
 \end{enumerate*}
+If these conditions are met, BR adds the current edge to a set $R_i$, and continues to add all succeeding edges in the list to $R_i$ provided that, for each edge, both conditions hold and the succeeding edge is not a member of a component of $G'$ that has an edge in $R_i$.
+Once there are no more valid edges available to add to $R_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets the conditions, and can begin a new set $R_{i+1}$.
+The procedure terminates once the penultimate edge in the list has been assessed.
 
-If the conditions are met, BR adds the current edge to a set $R_i$, and continues to add all succeeding edges in the list to $R_i$, provided that for each edge both conditions hold, and the succeeding edge is not a member of a component of $G'$ that has an edge in $R_i$.
-Once there are no more valid edges available to add to $R_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets the conditions, and can begin a new set $R_{i+1}$.
-The procedure terminates once the penultimate edge in the list has been assessed, having generated the sets $R_1, R_2, ..., R_k \subseteq R'$.
+Now, one of the following three conditions holds.
+\begin{enumerate}
+\item In the event that BR has been unable to produce a single setthere are no suitable edges that can combine the components $C_1, C_2, ..., C_q$ of $G'$, and therefore an alternating Hamiltonian cycle for $G$ cannot be created.
+Thus, no feasible solution exists for the corresponding COP.
 
-In the event that BR has been unable to produce a single set, i.e.
-$k = 0$, there are no suitable edges that can combine the components $C_1, C_2, ..., C_k$ of $G'$, and therefore an alternating Hamiltonian cycle cannot be created.
-Thus, no feasible solution exists for the given instance of the COP.
-
-If there exists a set $R_i$ such that $|R_i| = q$, then the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle.
+\item On the other hand, if there exists a set $R_i$ such that $|R_i| = q$, then the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle.
 This is achieved by adding the red edge connecting the lower-indexed vertex of each edge in $R_i$ to the higher-indexed vertex of the next edge to $R'$ (for the final edge in $R_i$, add the red edge connecting its lower-indexed vertex to the higher-indexed vertex of the first edge).
@@
 
-Otherwise, if $k > 1$, it may be that multiple sets are required to connect all components of $G'$.
-For two sets $R_i$ and $R_j$ to ``overlap'', each set must have one edge from the same component on $G'$, and the other edges in each set must be from different components.
-For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, and the other edges in the sets are from different components.
+\item Otherwise, it may be that multiple sets are required to connect the components of $G'$.
+For two sets $R_i$ and $R_j$ to ``overlap'', each set must have one edge from the same component in $G'$, with the other edges in each set being from different components.
+For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, but the other edges in the sets are from different components.
 Hence, a selection of sets from $R_1, R_2, ..., R_k$ need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets.
@@
 % Refer to figures
+\end{enumerate}
+Using the instance illustrated in the figures as an example, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are in the set $R_1$ formed by $BR$, as they are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$ as seen in Figure \ref{fig:mps}), and $(v_3, v_{11}) \in R$.
+Note that since $v_4$ and $v_{11}$ are adjacent, $v_4$ must also be adjacent to $v_{12}$, i.e.
+$(v_4, v_{12}) \in R$, since the value associated with $v_12$ is greater than or equal to the value associated with $v_{11}$.
+Then, as $|R_1| = q$, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are removed from $R'$ and replaced by the edges $(v_3, v_{11})$ and $(v_4, v_{12})$ from $R$, as shown in Figure \ref{fig:connect/cycle}.
+Removing the dominating vertices and any incident edges results in an alternating Hamiltonian path, which corresponds to a feasible solution $\mathcal{T}$.
 
-This algorithm, which will be referred to as the \textsc{Alternating Hamiltonian Construction Algorithm} (AHCA) is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP.
-If a solution does indeed exist, AHCA can produce this solution in at most $O(n^2)$ time.
+This algorithm, which will be referred to as the \textsc{Alternating Hamiltonian Construction} (AHC) algorithm is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP.
+If a solution does indeed exist, AHC can produce this solution in at most $O(n^2)$ time.
 % Cite Becker
@@
 
-(Why heuristics, using AHCA for SCSPP, explain) Perhaps the simplest and most well-known heuristic for packing problems is \textsc{First-Fit} (FF), a greedy online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
-It is known that there always exists at least one ordering of the items such that FF produces an optimal solution (\citealp{lewis2009}).
-A minor modification to FF yields the \textsc{First-Fit Decreasing} (FFD) heuristic, which sorts the items in non-increasing order of size prior to performing FF.
+In this section, we now turn our attention to the multi-strip version of the problem.
+As mentioned in the introduction this problem is a generalisation of the BPP in that we also require the sum of every pair of adjacent score widths to be greater than or equal to a minimum scoring distance $\tau$.
 
@@
 
-That is, all items must be packed onto a strip, each item can only be placed on one strip, the strips cannot be overpacked, and the items on each strip $S_j$ in the solution must be arranged such that the sum of two adjacent score widths is greater than or equal to the minimum scoring distance $\tau$.
+That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the sum of two adjacent score widths is greater than or equal to the minimum scoring distance $\tau$ (\ref{eqn:vscstrip}).
 
@@
 where $n$ is the number of items ($|\mathcal{I}|$), $w_i$ the width of each item $i \in \mathcal{I}$, and $W$ is the width of the strips (\citealp{martello1990b}).
+Perhaps the simplest and most well-known heuristic for packing problems is \textsc{First-Fit} (FF), a greedy online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
+It is known that there always exists at least one ordering of the items such that FF produces an optimal solution (\citealp{lewis2009}).
+A minor modification to FF yields the \textsc{First-Fit Decreasing} (FFD) heuristic, which sorts the items in non-increasing order of size prior to performing FF.
 In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ strips.
@@
 One obvious difference is the order in which the items must appear on the strips.
-In the BPP, removing an item retains feasibility, whereas in the SCSPP this is not guaranteed, as the constraint may not be fulfilled between the two score widths either side of the item removed.
-Furthermore, lower bound for $k$ (Equation (\ref{eqn:lowerbound})) does not hold for the SCSPP, as the minimum scoring distance $\tau$ is not included in the calculation.
-For example, if $\tau > 2 \max(b_i)$ (that is, the minimum scoring distance is greater than twice the largest score width), then it is clear that $n$ strips will be required, regardless of the items' widths.
+The order of the items in the BPP is unimportant, as there are no conditions regarding which items can be placed together, however in the SCSPP the items must be ordered in a way that meets the vicinal sum constraint.
+In addition, removing an item in the BPP retains feasibility, whereas in the SCSPP this is not guaranteed, as it may leave a subset of items for which the vicinal sum constraint is not satisfied.
+Furthermore, the lower bound for $k$ (Equation (\ref{eqn:lowerbound})) has the potential to be less accurate for the SCSPP, as the minimum scoring distance $\tau$ is not considered.
+For example, if the minimum scoring distance is greater than twice the largest score width, then it is clear that $n$ strips will be required, regardless of the items' widths.
 % Time complexity for FFD also inaccurate
 
-Three heuristics for the SCSPP have been developed: a basic FFD heuristic with a simple modification; a heuristic that packs strips individually and prioritises score widths; and a powerful version of FFD that incorporates the polynomial-time AHCA algorithm.
+Three heuristics for the SCSPP have been developed: a basic FFD heuristic with a simple modification; a heuristic that packs strips individually and prioritises score widths; and a powerful version of FFD that incorporates the polynomial-time AHC algorithm.
 
@@
 
-\subsection{Modified First-Fit Decreasing with AHCA (MFFD$^+$)}
+\subsection{Modified First-Fit Decreasing with AHC (MFFD$^+$)}
 \label{sec:mffd+}
 
-The last heuristic incorporates AHCA as described in Section \ref{sec:ahca}.
-The \textsc{Modified First-Fit Decreasing with AHCA} (MFFD$^+$) heuristic operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.
-However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ then executes AHCA on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}).
-If AHCA finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip.
-Using AHCA means that if a feasible alignment of the items exists, there is a guarantee that it will be found.
+The last heuristic incorporates AHC as described in Section \ref{sec:ahca}.
+The \textsc{Modified First-Fit Decreasing with AHC} (MFFD$^+$) heuristic operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.
+However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ then executes AHC on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}).
+If AHC finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip.
+Using AHC means that if a feasible alignment of the items exists, there is a guarantee that it will be found.
 Unlike MFFD, where the current item can only be placed on the end of the strip, MFFD$^+$ allows the items to be entirely rearranged (see Figure \ref{fig:comparestrips}).
@@
 	\item MFFD $W = 5000$ Average speed = 159.68755ms/instance
-	\item MFFD $W = 2500$ Average speed = 
-	\item MFFD $W = 1250$ Average speed = 
-	\item PS $W = 5000$ Average speed = 
-	\item PS $W = 2500$ Average speed = 
-	\item PS $W = 1250$ Average speed = 
-	\item MFFD$^+$ $W = 5000$ Average speed = 
+	\item MFFD $W = 2500$ Average speed = 157.92673ms/instance
+	\item MFFD $W = 1250$ Average speed = 154.45345ms/instance
+	\item PS $W = 5000$ Average speed = 168.77291ms/instance
+	\item PS $W = 2500$ Average speed = 176.81209ms/instance
+	\item PS $W = 1250$ Average speed = 201.522ms/instance
+	\item MFFD$^+$ $W = 5000$ Average speed = 825.59964ms/instance
 	\item MFFD$^+$ $W = 2500$ Average speed = 

### 2018-05-09 PAPER/main.tex
algorithm pseudocode for mffd+

@@
 However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry).
-The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$.
+The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$ where $a_i + b_i < w_i$, assigned such that $a_i \leq b_i$.
 Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively.
-Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
-Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
-The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.
 
-\begin{figure}[h!]	
+\begin{figure}[H]	
 	\centering
@@
 
+Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
+Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
+The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.
+
 It can be seen that this problem is in fact equal to the COP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance.
+Figure \ref{fig:items/aligned} shows the example instance $\mathcal{M}$ of the COP from above as a packing problem.
+% vsc = sum of every adj pair of score widths \geq \tau.
+
+\begin{figure}	
+	\centering
+	\begin{subfigure}[h]{0.44\textwidth}
+		\includestandalone[width=\textwidth]{figures/items}
+		\label{fig:items}\vspace{10pt}
+	\end{subfigure} 
+	\begin{subfigure}[h]{0.7\textwidth}
+		\includestandalone[width=\textwidth]{figures/itemsaligned}
+		\label{fig:itemsaligned}
+	\end{subfigure}
+	\caption{Example of the strip-packing problem, where the sum of each pair of adjacent score widths must be greater than or equal to $\tau = 7$. From instance $\mathcal{M}$ above.}
+	\label{fig:items/aligned}
+\end{figure}
 
@@
 \begin{definition}
-	\label{defn:scspp}
-	Let $\mathcal{S} = \{S_1, S_2, ..., S_k\}$ be a set of strips of height $H$ and width $W$, and let $\mathcal{I}$ be a set of rectangular items of height $H$ and varying widths $w_i \in \mathbb{Z}^+ \leq W$ and score widths $a_i, b_i \in \mathbb{Z}^+$ such that $a_i \leq b_i$ and $a_i + b_i < w_i$ for each item $i \in \mathcal{I}$.
-Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips $k$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
+	Let $\mathcal{I}$ be a set of rectangular items of height $H$ with varying widths $w_i \in \mathbb{Z}^+$ and score widths $a_i, b_i \in \mathbb{Z}^+$ for each item $i \in \mathcal{I}$.
+Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consist of finding the minimum number of strips of height $H$ and width $W$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
+%and that no strip is overfilled.
 \end{definition}
@@
 This is especially useful for problems such as the previously mentioned strip-packing problem, where a solution is required in order to place the items in the correct order and orientation.
-% We shall now present an algorithm for solving the COP, which operates by expressing the problem instance graphically.
 
@@
 whose values make up a pair in $\mathcal{M}$, as shown in Figure \ref{fig:partners}.
-It can be seen that $B$ is a perfect matching in $G$, with $|B|= n+1$.
-Let the bijective function $p: V \to V$ associate each vertex with its partner, $p(v_i) = v_j$.
-Hence $B = \{(v_i, p(v_i)) : v_i \in V\}$.
+By introducing a bijective function $p: V \to V$ that associates each vertex with its partner, $p(v_i) = v_j$, we can denote this set of edges as $B = \{(v_i, p(v_i)) : v_i \in V\}$.
+It can be seen that $B$ is a perfect matching in $G$, with $|B| = n+1$.
 
@@
 % Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..
+% "This corresponds to the vsc in Defn 1" - values that can be aligned alongside one another that are not part of the same unordered pair in M, hence why they cannot be partners on the graph G, must be from different unordered pairs.
 
@@
 To find a matching $R' \subseteq R$, the following \textsc{Maximum Cardinality Matching} (MCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}.
-Take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest indexed vertex $v_j$ that is not already incident to an edge in $R'$.
+Take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest-indexed vertex $v_j$ that is not already incident to an edge in $R'$.
 Now add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed.
@@
 Similarly to partners, let $m : V \to V$ be a bijective function that assigns each vertex with its match, $m(v_i) = v_j$.
-Then, $R' =\{(v_i, m(v_i)) : v_i \in V\}$.
+Then, we can denote this matchin set as $R' =\{(v_i, m(v_i)) : v_i \in V\}$.
 
@@
 
-Clearly, if $|R'| < n+1$ after MCM are completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and hence no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
-Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$ (see Figure \ref{fig:matching/mps}).
+Clearly, if $|R'| < n+1$ after MCM has completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and hence no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
+Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex $v_i \in V$ is adjacent to its partner $p(v_i)$ via a blue edge in $B$, and its match $m(v_i)$ via a red edge in $R'$ (see Figure \ref{fig:matching/mps}).
 $G'$ therefore consists of a collection of cyclic components $C_1, C_2, ..., C_q$.
@@
 Any edges that cannot be placed in such an order are then removed from this list.
-For instance, in the example illustrated in Figure \ref{fig:matching/mps}, the edges would be sorted as follows: $(v_1, v_{14}), (v_2, v_{13}),(v_3, v_{12}),(v_4, v_{11}),(v_6, v_{10}),(v_7, v_8).$
+For instance, in the example illustrated in Figure \ref{fig:matching/mps}, the edges would be sorted as follows: $(v_1, v_{14}), (v_2, v_{13}),(v_3, v_{12}),(v_4, v_{11}),(v_6, v_{10}),(v_7, v_8)$.
+% (v5, v9) removed from list, not matched with highest-indexed vertex in MCM since it was v10 and v10 is v5's partner.
 
@@
 The procedure terminates once the penultimate edge in the list has been assessed.
+% (a) (v_i,m(v_{i+1})) \in R
+% (b) (v_i, m(v_i)) \in C_k, (v_{i+1}, m(v_{i+1})) \in C_l, k \neq l
 
@@
 \begin{enumerate}
-\item In the event that BR has been unable to produce a single setthere are no suitable edges that can combine the components $C_1, C_2, ..., C_q$ of $G'$, and therefore an alternating Hamiltonian cycle for $G$ cannot be created.
+\item In the event that BR has been unable to produce a single set, there are no suitable edges that can combine the components $C_1, C_2, ..., C_q$ of $G'$, and therefore an alternating Hamiltonian cycle for $G$ cannot be created.
 Thus, no feasible solution exists for the corresponding COP.
@@
 This is achieved by adding the red edge connecting the lower-indexed vertex of each edge in $R_i$ to the higher-indexed vertex of the next edge to $R'$ (for the final edge in $R_i$, add the red edge connecting its lower-indexed vertex to the higher-indexed vertex of the first edge).
-Any edges that appear in both $R_i$ and $R'$ are then removed from $R'$, so that $R'$ remains a perfect matching, and $R_i \cap R' = \emptyset$.
+Any edges that appear in both $R_i$ and $R'$ are then removed from $R'$, so that $R'$ remains a perfect matching and $R_i \cap R' = \emptyset$.
 $G'$ then consists of a single alternating Hamiltonian cycle, and hence a solution has been found.
+% add edges (v_i, m(v_{i+1})) for i \in {1, 2, ..., |R_i| -1} from R to R', and then the edge (v_{|R_i|}, m(v_1)) from R to R'
 
@@
 For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, but the other edges in the sets are from different components.
-Hence, a selection of sets from $R_1, R_2, ..., R_k$ need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets.
+Hence, a selection of sets need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets.
 If such a collection of sets exists, then the components of $G$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.
@@
 \end{enumerate}
-Using the instance illustrated in the figures as an example, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are in the set $R_1$ formed by $BR$, as they are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$ as seen in Figure \ref{fig:mps}), and $(v_3, v_{11}) \in R$.
+Using the instance illustrated in the figures as an example, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are in the set $R_1$ formed by BR, as they are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$ as seen in Figure \ref{fig:mps}), and $(v_3, v_{11}) \in R$.
 Note that since $v_4$ and $v_{11}$ are adjacent, $v_4$ must also be adjacent to $v_{12}$, i.e.
-$(v_4, v_{12}) \in R$, since the value associated with $v_12$ is greater than or equal to the value associated with $v_{11}$.
+$(v_4, v_{12}) \in R$, since the value associated with $v_{12}$ is greater than or equal to the value associated with $v_{11}$.
 Then, as $|R_1| = q$, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are removed from $R'$ and replaced by the edges $(v_3, v_{11})$ and $(v_4, v_{12})$ from $R$, as shown in Figure \ref{fig:connect/cycle}.
@@
 \end{figure}
+
+\begin{algorithm}[H]
+	\caption{MFFD$^+$}
+	\label{alg:mffd+}
+	\begin{algorithmic}[1]
+		\State Sort items in $\mathcal{I}$ in order of non-increasing widths $w_i$.
+		\For{$i \gets 1 \To |\mathcal{I}|$}
+			\State $j \gets 1$, packed $\gets \False$
+			\While{not packed}
+				\If{$S_j \in \mathcal{S}$ and $\sum_{i=1}^{|S_j|}w_i + w_i \leq W$}
+					\State Run AHC
+					\If{AHC returns feasible solution}
+						\State $S_j \gets S_j \cup i$ in order of feasible solution
+						\State packed $\gets \True$
+					\Else \hspace{0.2mm} $j \gets j + 1$					 
+					\EndIf
+				\ElsIf{$S_j \notin \mathcal{S}$}
+					\State $S_j \gets S_j \cup i$ in regular orientation
+					\State $\mathcal{S} \gets \mathcal{S} \cup S_j$	
+					\State packed $\gets \True$
+				\EndIf
+			\EndWhile	
+		\EndFor
+		\Return $\mathcal{S}$
+	\end{algorithmic}	
+\end{algorithm}
 
@@
 	\item MFFD$^+$ $W = 5000$ Average speed = 825.59964ms/instance
-	\item MFFD$^+$ $W = 2500$ Average speed = 
-	\item MFFD$^+$ $W = 1250$ Average speed = 
+	\item MFFD$^+$ $W = 2500$ Average speed = 744.73509ms/instance
+	\item MFFD$^+$ $W = 1250$ Average speed = 434.67655ms/instance
 \end{itemize}

### 2018-05-10 PAPER/main.tex
changed word 'packed' in algorithm to italics
added pseudocode for mffd algorithm

@@
 	\label{thm:copsoln}
-	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the COP if and only if its corresponding graph $G=(V, B\cup R)$ contains an alternating Hamiltonian cycle.
+	If there exists an alternating Hamiltonian cycle on a graph $G$ created from an instance $\mathcal{M}$ of the COP, then AHC is able to find the cycle in $O(n^2)$ time.
 \end{theorem}
 \begin{proof}
-	Let $\mathcal{A} = \{v_1, v_2, ..., v_{2n+1}, v_{2n+2}\}$ be an alternating Hamiltonian cycle on $G$, where $v_{2n+1}$ and $v_{2n+2}$ are the dominating vertices.
-By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $B$.
-Thus, there exists a set of $n+1$ edges from $R$ that, together with the edges in $B$, form the alternating Hamiltonian cycle.
-Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $B$.
-The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple.\qed
+	\qed
 \end{proof}
@@
 \begin{algorithm}[H]
+\caption{MFFD}
+\label{alg:mffd}
+\begin{algorithmic}[1]
+	\State Sort items in $\mathcal{I}$ in order of non-increasing widths $w_i$.
+	\State Let $r_j$ denote the right-most score width on strip $S_j$.
+		\For{$i \gets 1 \To |\mathcal{I}|$}
+			\State $j \gets 1$, packed $\gets \False$
+			\While{\textbf{not} packed}
+				\If{$S_j \in \mathcal{S}$ and $\sum_{i=1}^{|S_j|}w_i + w_i \leq W$}
+					\If{$r_j + a_i \geq \tau$}
+						\State $S_j \gets S_j \cup (a_i, b_i)$
+						\State packed $\gets \True$
+					\ElsIf{$r_j + b_i \geq \tau$}
+						\State $S_j \gets S_j \cup (b_i, a_i)$
+						\State packed $\gets \True$
+					\Else \hspace{0.2mm} $j \gets j + 1$		
+					\EndIf
+				\ElsIf{$S_j \notin \mathcal{S}$}
+					\State $S_j \gets S_j \cup (a_i, b_i)$
+					\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
+					\State packed $\gets \True$	
+				\EndIf
+			\EndWhile	
+		\EndFor
+	\Return $\mathcal{S}$
+\end{algorithmic}	
+\end{algorithm}
+
+\begin{algorithm}[H]
 \caption{MFFD$^+$}
@@
 		\State $j \gets 1$, packed $\gets \False$
-			\While{not packed}
+		\While{\textbf{not} packed}
 			\If{$S_j \in \mathcal{S}$ and $\sum_{i=1}^{|S_j|}w_i + w_i \leq W$}
@@
 \section{Comparison}
+\subsection{Problem Instances}
+\begin{itemize}
+	\item sets of items $\mathcal{I}$ of sizes 100, 500, and 100
+	\item 1000 different problem instances for each size, so 1000 problem instances for $|\mathcal{I}| = 100$, $|\mathcal{I}| = 500$, and $|\mathcal{I}| = 1000$
+	\item use the same 1000 instances in every run for each size, fair
+	\item For all problem instances, the items have equal height $H = 1$.
+	\item For each problem instance, the items have varying widths randomly selected from a uniform distribution between 150 and 1000, and score widths also randomly selected from a uniform distribution between 1 and 70, preventing the score widths from overlapping, and ensuring that each item has exactly two score widths.
+	\item The strips also have equal height $H = 1$, and three different widths, $W = 5000$, $W = 2500$, and $W = 1250$. 
+	\item As the strip width decreases, the number of items per strip decreases, making the problem more difficult.
+	\item We introduce a parameter $\delta$ that gives the proportion of pairs of score widths whose total sum is greater than or equal to $\tau$. 
+	\item Values for $\delta$ from 0.0 to 1.0 in increments of 0.1 are calculated by changing the value of $\tau$. 
+	\item Thus, if $\delta  = 0.0$, then there are no score widths that can feasibly be aligned together, and hence $|\mathcal{I}|$ strips are required (one for each item), whereas if $\delta = 1.0$, then all pairs of score widths meet the vicinal sum constraint (i.e.
+sum of all pairs of score widths $\geq \tau$), and the problem is therefore analogous to the BPP.
+\end{itemize}
+
 \begin{itemize}

### 2018-05-10 PAPER/main.tex
added some bullet points for further work

@@
 		\includestandalone[width=\textwidth]{figures/items}
-		\label{fig:items}\vspace{10pt}
+		\label{fig:items} \vspace{5pt}
 	\end{subfigure} 
@@
 
-\begin{algorithm}[H]
-\caption{MFFD}
-\label{alg:mffd}
-\begin{algorithmic}[1]
-	\State Sort items in $\mathcal{I}$ in order of non-increasing widths $w_i$.
-	\State Let $r_j$ denote the right-most score width on strip $S_j$.
-		\For{$i \gets 1 \To |\mathcal{I}|$}
-			\State $j \gets 1$, packed $\gets \False$
-			\While{\textbf{not} packed}
-				\If{$S_j \in \mathcal{S}$ and $\sum_{i=1}^{|S_j|}w_i + w_i \leq W$}
-					\If{$r_j + a_i \geq \tau$}
-						\State $S_j \gets S_j \cup (a_i, b_i)$
-						\State packed $\gets \True$
-					\ElsIf{$r_j + b_i \geq \tau$}
-						\State $S_j \gets S_j \cup (b_i, a_i)$
-						\State packed $\gets \True$
-					\Else \hspace{0.2mm} $j \gets j + 1$		
-					\EndIf
-				\ElsIf{$S_j \notin \mathcal{S}$}
-					\State $S_j \gets S_j \cup (a_i, b_i)$
-					\State $\mathcal{S} \gets \mathcal{S} \cup S_j$
-					\State packed $\gets \True$	
-				\EndIf
-			\EndWhile	
-		\EndFor
-	\Return $\mathcal{S}$
-\end{algorithmic}	
-\end{algorithm}
-
-\begin{algorithm}[H]
-\caption{MFFD$^+$}
-\label{alg:mffd+}
-\begin{algorithmic}[1]
-	\State Sort items in $\mathcal{I}$ in order of non-increasing widths $w_i$.
-	\For{$i \gets 1 \To |\mathcal{I}|$}
-		\State $j \gets 1$, packed $\gets \False$
-		\While{\textbf{not} packed}
-			\If{$S_j \in \mathcal{S}$ and $\sum_{i=1}^{|S_j|}w_i + w_i \leq W$}
-				\State Run AHC
-				\If{AHC returns feasible solution}
-					\State $S_j \gets S_j \cup i$ in order of feasible solution
-					\State packed $\gets \True$
-				\Else \hspace{0.2mm} $j \gets j + 1$					 
-				\EndIf
-			\ElsIf{$S_j \notin \mathcal{S}$}
-				\State $S_j \gets S_j \cup i$ in regular orientation
-				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$	
-				\State packed $\gets \True$
-			\EndIf
-		\EndWhile	
-	\EndFor
-	\Return $\mathcal{S}$
-\end{algorithmic}	
-\end{algorithm}
-
 \section{Comparison}
@@
 
+\section{Further Work}
+\begin{itemize}
+	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution.
+	\item include item width in ahc, so add values to the blue edges of the graph, weighted edges, red edges have value = 0.
+	\item Then the problem would be: find the minimum number of alternating cycles on $G$ such that the length of the cycle is less than or equal to some value $W$ (which is the strip width).
+The length of the cycle would be the sum of all the weighted edges, so the sum of all the blue edges, since red = 0.
+	\item then could break and form edges to create new components of different sizes if some are too large, or join together if some are small, thus decreasing the number of cycles
+	\item or if possible, find a single alt Ham cycle, and break up into as few smaller cycles as possible such that the length of each cycle is less than or equal to $W$
+	\item another way, create as few feasible subsets $\mathcal{I}' \subseteq \mathcal{I}$ such that the total width of the items in each subset $\mathcal{I}$ is less than $W$, i.e.
+perform usual FFD alg, ignore score widths
+	\item then perform ahc on each set, try to find feasible solution.
+	\item if sets dont have feasible solution, try swapping items between sets
+	\item initial tests, Becker theorem 6 2015 paper 
+\end{itemize}
+
 \bibliographystyle{dcu}

### 2018-05-14 PAPER/main.tex
started on comparison

@@
 
-For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, one possible feasible solution is $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.
+For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, one possible solution is $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.
 
@@
 	\end{subfigure}
-	\caption{Example of the strip-packing problem, where the sum of each pair of adjacent score widths must be greater than or equal to $\tau = 7$. From instance $\mathcal{M}$ above.}
+	\caption{Example of the strip-packing problem, where the sum of each pair of adjacent score widths is greater than or equal to $\tau = 7$. From instance $\mathcal{M}$ above.}
 	\label{fig:items/aligned}
@@
 Observe that in this particular strip-packing problem the widths of the individual items are disregarded, since the aim is to arrange the items onto a strip of seemingly infinite width.
-However, in industrail applications, strips of material are often provided in fixed widths.
+However, in industrial applications, strips of material are often provided in fixed widths.
 Given a large problem instance, multiple strips may therefore be required to feasibly accommodate all of the items.
@@
 Similarly to partners, let $m : V \to V$ be a bijective function that assigns each vertex with its match, $m(v_i) = v_j$.
-Then, we can denote this matchin set as $R' =\{(v_i, m(v_i)) : v_i \in V\}$.
+Then, we can denote this matching set as $R' =\{(v_i, m(v_i)) : v_i \in V\}$.
 
@@
 For two sets $R_i$ and $R_j$ to ``overlap'', each set must have one edge from the same component in $G'$, with the other edges in each set being from different components.
-For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, but the other edges in the sets are from different components.
+For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of components $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, but the other edges in the sets are from different components.
 Hence, a selection of sets need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets.
@@
 In this section, we now turn our attention to the multi-strip version of the problem.
-As mentioned in the introduction this problem is a generalisation of the BPP in that we also require the sum of every pair of adjacent score widths to be greater than or equal to a minimum scoring distance $\tau$.
+As mentioned in the introduction, this problem is a generalisation of the BPP in that we also require the sum of every pair of adjacent score widths to be greater than or equal to a minimum scoring distance $\tau$.
 
@@
 \end{equation}
-where $n$ is the number of items ($|\mathcal{I}|$), $w_i$ the width of each item $i \in \mathcal{I}$, and $W$ is the width of the strips (\citealp{martello1990b}).
+where $n = |\mathcal{I}|$ is the number of items (\citealp{martello1990b}).
 Perhaps the simplest and most well-known heuristic for packing problems is \textsc{First-Fit} (FF), a greedy online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
@@
 \section{Comparison}
+For our experiments, we used sets $\mathcal{I}$ containing 100, 500, and 1000 items.
+We generated 1000 different problem instances for each size of $\mathcal{I}$.
+For each problem instance, the items have varying widths $w_i$ between 150 and 1000, and score widths $a_i, b_i$ between 1 and 70, all selected randomly from a uniform distribution.
+Three different strip widths $W$ were used, 5000, 2500, and 1250.
+As the width of the strips decrease, the average number of items per strip also decreases, making the problem more difficult.
+Both the items and the strips have equal height of $H = 1$.
+
 \subsection{Problem Instances}
@@
 	\item sets of items $\mathcal{I}$ of sizes 100, 500, and 100
-	\item 1000 different problem instances for each size, so 1000 problem instances for $|\mathcal{I}| = 100$, $|\mathcal{I}| = 500$, and $|\mathcal{I}| = 1000$
-	\item use the same 1000 instances in every run for each size, fair
-	\item For all problem instances, the items have equal height $H = 1$.
+	\item 1000 different problem instances for each size, so 1000 problem instances for $|\mathcal{I}| = 100$, $|\mathcal{I}| = 500$, and $|\mathcal{I}| = 1000$, same 1000 instances for each run
 	\item For each problem instance, the items have varying widths randomly selected from a uniform distribution between 150 and 1000, and score widths also randomly selected from a uniform distribution between 1 and 70, preventing the score widths from overlapping, and ensuring that each item has exactly two score widths.
-	\item The strips also have equal height $H = 1$, and three different widths, $W = 5000$, $W = 2500$, and $W = 1250$. 
-	\item As the strip width decreases, the number of items per strip decreases, making the problem more difficult.
+	\item items and strips have equal height $H = 1$, strips have three different widths, $W = 5000$, $W = 2500$, and $W = 1250$. 
+	\item As the strip width decreases, the number of items/strip decreases, making the problem more difficult, changes the average number of items per strip (why is this important?)
 	\item We introduce a parameter $\delta$ that gives the proportion of pairs of score widths whose total sum is greater than or equal to $\tau$. 
@@
 sum of all pairs of score widths $\geq \tau$), and the problem is therefore analogous to the BPP.
-\end{itemize}
-
-\begin{itemize}
 	\item Heuristics implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
-	\item $n$ = 100, 500, and 1000, number of items in $\mathcal{I}$, $W$ = 5000, 2500, 1250, item widths uniform dist [150, 1000], score widths uniform dist [1,70] (ensures each item has two score widths that do not overlap), all items and strips have height H ( = 1)
-	\item Changing strip length changes the average number of items per strip (why is this important?) Harder problems have fewer items per strip
 	\item run each instance 1000 times (per value of $\delta$), same instances each time.
@@
 	\item graph showing time or optimality of all three heuristics
-	\item $\delta$ is proportion of score widths that meet VSC (excluding partners and itself), 0.1 increments.
-	\item changing the value of $\tau$ changes the proportion of the number of score widths
-	\item if $\delta = 0.0$, then no score widths can be aligned number of strips = $n$, $\delta = 1.0$, then all score widths can be aligned with any other score width, BPP.
 	\item As the strip length is decreased, MFFD+ improves, number of items/strip decreases
-	\item when $\delta = 1.0$ MFFD and MFFD+ will perform in the same manner (like original FFD)
 	\item PS does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
@@
 
+\begin{comment}
 \textbf{$n$ = 100}
@@
 \end{itemize}
-
+\end{comment}
+\begin{comment}
 \section{Further Work}
@@
 \end{itemize}
+\end{comment}
 

### 2018-05-15 PAPER/main.tex
changed mffd+ pseudocode, using F for feasible solution returned by AHC
changed figure caption, comment about MFFD+ speed, minor change to Comparison

@@
 This reduces the possibility of having to start a new strip for an item, thus preventing increasing the number of strips in the final solution.
+Since AHC is executed every time an item can fit onto a strip that already contains items, (up to $|\mathcal{S}|$ times per item, where $|\mathcal{S}|$ is the number of strips containing at least one item so far in the procedure) MFFD$^+$ is slower in comparison to the previous heuristics.
 
@@
 	\includestandalone[width=\textwidth]{figures/strips}
-	\caption{Comparison of MFFD and MFFD$^+$, $W = 20$, $\tau = 70$.}	
+	\caption{Example instance of the sub-problem, with $W = 20$ and $\tau = 70$. In MFFD the constraint is not fulfilled in either orientation, however MFFD$^+$ is able find a feasible arrangement.}	
 	\label{fig:comparestrips}
@@
 \section{Comparison}
-For our experiments, we used sets $\mathcal{I}$ containing 100, 500, and 1000 items.
-We generated 1000 different problem instances for each size of $\mathcal{I}$.
+For our experiments, we generated 1000 problem instances for three different sizes of $\mathcal{I}$, containing 100, 500, and 1000 items.
 For each problem instance, the items have varying widths $w_i$ between 150 and 1000, and score widths $a_i, b_i$ between 1 and 70, all selected randomly from a uniform distribution.
@@
 
-\subsection{Problem Instances}
 \begin{itemize}

### 2018-05-16 PAPER/main.tex
added to comparison

@@
 
-It can be seen that this problem is in fact equal to the COP, where each unordered pair in an instance $\mathcal{M}$ contains values corresponding to the score widths of an item, and $\tau$ is the minimum scoring distance.
-Figure \ref{fig:items/aligned} shows the example instance $\mathcal{M}$ of the COP from above as a packing problem.
-% vsc = sum of every adj pair of score widths \geq \tau.
+It can be seen that this problem is in fact equal to the COP, where each unordered pair in an instance $\mathcal{M}$ contains the score widths of an item, and $\tau$ is the minimum scoring distance.
+It then follows that the vicinal sum constraint corresponds to the requirement for the sum of adjacent score widths to exceed $\tau$.
+Figure \ref{fig:items/aligned} shows the example instance $\mathcal{M}$ of the COP from above depicted as a packing problem.
 
@@
 	Let $\mathcal{I}$ be a set of rectangular items of height $H$ with varying widths $w_i \in \mathbb{Z}^+$ and score widths $a_i, b_i \in \mathbb{Z}^+$ for each item $i \in \mathcal{I}$.
-Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consist of finding the minimum number of strips of height $H$ and width $W$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
-%and that no strip is overfilled.
+Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consist of finding the minimum number of strips of height $H$ and width $W$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$, and that no strip is overfilled.
 \end{definition}
@@
 	Let $\mathcal{I}' \subseteq \mathcal{I}$ be a set of items whose total width is less than or equal to the capacity of a strip, (i.e.
-$\sum_{i=1}^{|\mathcal{I}'|}w_i \leq W$).
+$\sum_{i\in \mathcal{I}'}w_i \leq W$).
 Given a minimum scoring distance $\tau$, the Score-Constrained Packing Sub-Problem (SCPSP) involves finding an arrangement of the items in $\mathcal{I}'$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
@@
 	\end{subfigure} \quad
-	\begin{subfigure}[h]{0.5\textwidth}
+	\begin{subfigure}[h]{0.55\textwidth}
 		\includestandalone[width=\textwidth]{figures/mps}
@@
 	\centering
-	\begin{subfigure}[H]{0.5\textwidth}
+	\begin{subfigure}[H]{0.7\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpsconnect}
 		\caption{Edges from $R\backslash R'$ can connect vertices from different cycles.}	
-		\label{fig:mpsconnect}
+		\label{fig:mpsconnect} \vspace{5mm}
 	\end{subfigure}
-	\begin{subfigure}[H]{0.5\textwidth}
+	\begin{subfigure}[H]{0.7\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpscycle}
@@
 As mentioned in the introduction, this problem is a generalisation of the BPP in that we also require the sum of every pair of adjacent score widths to be greater than or equal to a minimum scoring distance $\tau$.
+It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}), and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.
+Instead, heuristics can be used to find near-optimal solutions in a shorter amount of time.
 
@@
 
-That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the sum of two adjacent score widths is greater than or equal to the minimum scoring distance $\tau$ (\ref{eqn:vscstrip}).
+That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled, that is, the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance $\tau$ (\ref{eqn:vscstrip}).
 
@@
 For each problem instance, the items have varying widths $w_i$ between 150 and 1000, and score widths $a_i, b_i$ between 1 and 70, all selected randomly from a uniform distribution.
-Three different strip widths $W$ were used, 5000, 2500, and 1250.
+Three strip widths $W$ were used, 5000, 2500, and 1250.
 As the width of the strips decrease, the average number of items per strip also decreases, making the problem more difficult.
 Both the items and the strips have equal height of $H = 1$.
+Similarly to experiments performed by \cite{lewis2011}, we also introduced a parameter $\delta$ to denote the proportion of pairs of score widths from different items that meet the vicinal sum constraint, i.e.
+whose sum is greater than or equal to $\tau$.
+Values of $\delta$ from 0.0 to 1.0 were created by changing the value of the minimum scoring distance $\tau$.
+Clearly, when $\delta = 0.0$, there are no score widths that can be packed together feasibly, and so $|\mathcal{I}|$ strips will be required (one for each item), whereas if $\delta = 1.0$ then all pairs of score widths meet the constraint, and the problem is analogous to the BPP.
 
-\begin{itemize}
-	\item sets of items $\mathcal{I}$ of sizes 100, 500, and 100
-	\item 1000 different problem instances for each size, so 1000 problem instances for $|\mathcal{I}| = 100$, $|\mathcal{I}| = 500$, and $|\mathcal{I}| = 1000$, same 1000 instances for each run
-	\item For each problem instance, the items have varying widths randomly selected from a uniform distribution between 150 and 1000, and score widths also randomly selected from a uniform distribution between 1 and 70, preventing the score widths from overlapping, and ensuring that each item has exactly two score widths.
-	\item items and strips have equal height $H = 1$, strips have three different widths, $W = 5000$, $W = 2500$, and $W = 1250$. 
-	\item As the strip width decreases, the number of items/strip decreases, making the problem more difficult, changes the average number of items per strip (why is this important?)
-	\item We introduce a parameter $\delta$ that gives the proportion of pairs of score widths whose total sum is greater than or equal to $\tau$. 
-	\item Values for $\delta$ from 0.0 to 1.0 in increments of 0.1 are calculated by changing the value of $\tau$. 
-	\item Thus, if $\delta  = 0.0$, then there are no score widths that can feasibly be aligned together, and hence $|\mathcal{I}|$ strips are required (one for each item), whereas if $\delta = 1.0$, then all pairs of score widths meet the vicinal sum constraint (i.e.
-sum of all pairs of score widths $\geq \tau$), and the problem is therefore analogous to the BPP.
-	\item Heuristics implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
-	\item run each instance 1000 times (per value of $\delta$), same instances each time.
-	\item table shows optimality, which is the number of strips in the final solution generated by the heuristic divided by the number of strips in the optimal solution (which is calculated using the lower bound for $k$ above), =1 then optimal
-	\item Goulimis stated n= 10, this is able to find solutions for n=1000
-	\item graph showing time or optimality of all three heuristics
-	\item As the strip length is decreased, MFFD+ improves, number of items/strip decreases
-	\item PS does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
-	\item as avg number of items per strip decreases, PS is less efficient, MFFD+ is better
-	\item note anomaly in $n = 1000, W = 1250, \delta = 0.3$, MFFD performs the best.
-\end{itemize}
+The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
+The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the number of strips $k$ in the optimal solution, which was calculated using Equation \ref{eqn:lowerbound}.
+
+Firstly, it is apparent that the heuristics perform comparitively in the same manner regardless of the input size.
 

### 2018-05-17 SCSPP/COMBINED/base.cpp
deleted files moved to arc

@@ -1,126 +1,0 @@
-/*--------------/
-ALH
-base.cpp
-Combined Program with Heuristics and EA
-17/03/18
-/--------------*/
-
-#include <algorithm>
-#include <iomanip>
-#include "base.h"
-using namespace std;
-
-void ResetVar(int numScores, int numItem, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
-    int i, j;
-
-    for(i = 0; i < numScores; ++i){
-        partners[i] = 0;
-        for(j = 0; j < numScores; ++j){
-            adjMatrix[i][j] = 0;
-            itemWidths[i][j] = 0;
-        }
-    }
-
-    strip.clear();
-    strip.resize(numItem);
-    stripSum.clear();
-    stripSum.resize(numItem, 0);
-    allScores.clear();
-
-} //End ResetVar
-
-
-void Output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int optLow, int numInstances){
-
-    cout << setprecision(2) << fixed;
-    cout << "Number of Instances: " << numInstances << endl;
-    cout << "#        opt of LB: " << opt << "\t\tPercentage: "<< (static_cast<double>(opt)/numInstances) * 100 << "\t\t# 100%: " << opt << endl;
-    cout << "# 90% - <opt of LB: " << opt90 << "\t\tPercentage: "<< (static_cast<double>(opt90)/numInstances) * 100 << "\t\t# >= 90%: " << opt + opt90 << endl;
-    cout << "# 80% - <90% of LB: " << opt80 << "\t\tPercentage: "<< (static_cast<double>(opt80)/numInstances) * 100 << "\t\t# >= 80%: " << opt + opt90 + opt80 << endl;
-    cout << "# 70% - <80% of LB: " << opt70 << "\t\tPercentage: "<< (static_cast<double>(opt70)/numInstances) * 100 << "\t\t# >= 70%: " << opt + opt90 + opt80 + opt70 << endl;
-    cout << "# 60% - <70% of LB: " << opt60 << "\t\tPercentage: "<< (static_cast<double>(opt60)/numInstances) * 100 << "\t\t# >= 60%: " << opt + opt90 + opt80 + opt70 + opt60 << endl;
[…]

### 2018-05-17 SCSPP/COMBINED/base.h

@@ -1,23 +1,0 @@
-/*--------------/
-ALH
-base.h
-Combined Program with Heuristics and EA
-17/03/18
-/--------------*/
-
-#ifndef COMBINED_BASE_H
-#define COMBINED_BASE_H
-
-#include <iostream>
-#include <vector>
-using namespace std;
-
-void ResetVar(int numScores, int numItem, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
-
-void Output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int optLow, int numInstances);
-
-void CreateInstance(int tau, int numScores, int numItem, int minWidth, int maxWidth, int minItemWidth, int maxItemWidth, double &totalItemWidth,
-                    vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths);
-
-#endif

### 2018-05-17 SCSPP/COMBINED/main.cpp

@@ -1,371 +1,0 @@
-/*--------------/
-ALH
-main.cpp
-Combined Program with Heuristics and EA
-17/03/2018
-/--------------*/
-
-#include <iostream>
-#include <fstream>
-#include <cmath>
-#include <cstring>
-#include <ctime>
-#include <chrono>
-#include <iomanip>
-using namespace std;
-
-#include "base.h"
-#include "packing.h"
-
-struct Timer{
-
-    std::chrono::high_resolution_clock::time_point startTime, endTime;
-    std::chrono::duration<float> totalTime;
-
-    Timer(){
-        startTime = std::chrono::high_resolution_clock::now();
-    }
-
-    ~Timer(){
-        endTime = std::chrono::high_resolution_clock::now();
-        totalTime = endTime - startTime;
-
-        float totalTimems = totalTime.count() * 1000.0f;
-        //cout << "\nCPU Time: " << totalTimems << "ms (" << totalTime.count() << "s)" << endl;
-        cout << totalTime.count() << endl;
-        //cout << totalTimems << endl;
-    }
-};
-
-void ProgramInfo(){
-
-    cout << "SCSPP:\n-------------\n"
-         << "PARAMETERS:\n"
-         << "       -i <int>    [Number of instances. Default = 1000.]\n"
-         << "       -t <int>    [Constraint value. Default = 70.]\n"
-         << "       -n <int>    [Number of items. Default = 500.]\n"
-         << "       -a <int>    [Minimum score width. Default = 1.]\n"
-         << "       -b <int>    [Maximum score width. Default = 70.]\n"
-         << "       -m <int>    [Minimum item width. Default = 150.]\n"
-         << "       -M <int>    [Maximum item width. Default = 1000.]\n"
-         << "       -W <int>    [Width of strips. Default = 5000.]\n"
-         << "       -s <int>    [Random seed. Default = 1.]\n"
-         << "---------------\n"
-         << "ALGORITHM:\n"
-         << "       -x <int>    [1: Basic approximate FFD.]\n"
-         << "                   [2: Pack strips in turn, choosing smallest feasible score width.]\n"
-         << "                   [3: FFD combined with AHCA (exact algorithm).]\n"
-         << "                   [4: Evolutionary Algorithm using Local Search.]\n"
-         << "       -r <int>    [Recombination operator. 1: GGA. 2: GPX'.]\n"
-         << "       -p <int>    [Number of solutions in population.]\n"
-         << "---------------\n\n";
-
-}
-
[…]

### 2018-05-17 SCSPP/COMBINED/packing.cpp

@@ -1,2235 +1,0 @@
-/*--------------/
-ALH
-packing.cpp
-Combined Program with Heuristics and EA
-17/03/18
-/--------------*/
-
-#include <algorithm>
-#include <iomanip>
-#include "packing.h"
-using namespace std;
-
-void Swap(int &a, int &b){
-    int temp = a;
-    a = b;
-    b = temp;
-}
-
-int LowerBound(double totalItemWidth, int stripWidth){
-    int lBound;
-
-    lBound = ceil(totalItemWidth/stripWidth);
-    return lBound;
-}
-
-double Fitness(int stripWidth, vector<int> &stripSum, vector<vector<int> > &strip){
-
-    int i;
-    double total = 0.0;
-    double final;
-
-    for(i = 0; i < strip.size(); ++i){
-        double a = static_cast<double>(stripSum[i]) / static_cast<double>(stripWidth);
-        total += pow(a, 2);
-    }
-
-    final = total / static_cast<double>(strip.size());
-
-    return final;
-
-}
-
-void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB){
-
-    double c = static_cast<double>(LB) / stripSize;
-    if(stripSize == LB){
-        ++opt;
-    }
-    else if(c >= 0.9){
-        ++opt90;
-    }
-    else if(c >= 0.8){
-        ++opt80;
-    }
-    else if(c >= 0.7){
-        ++opt70;
-    }
-    else if(c >= 0.6){
-        ++opt60;
-    }
-    else if(c >= 0.5){
-        ++opt50;
-    }
-    else{
-        ++optLow;
-    }
-} //End Optimality
-
-// FFD checking vicinal sum constraint for both sides of each item.
-void MFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
-          int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners,
-          vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
-    int i, j, mini;
-    int min = 0;
-    int max = maxItemWidth;
-    vector<int> itemDecrease;
-    vector<int> checked(numScores, 0);
-
-    while(itemDecrease.size() < numItem) {
-        for (i = 0; i < numScores; ++i) {
[…]

### 2018-05-17 SCSPP/COMBINED/packing.h

@@ -1,108 +1,0 @@
-/*--------------/
-ALH
-packing.h
-Combined Program with Heuristics and EA
-17/03/18
-/--------------*/
-
-#ifndef COMBINED_PACKING_H
-#define COMBINED_PACKING_H
-
-#include <iostream>
-#include <vector>
-using namespace std;
-
-void Swap(int &a, int &b);
-
-int LowerBound(double totalItemWidth, int stripWidth);
-
-double Fitness(int stripWidth, vector<int> &stripSum, vector<vector<int> > &strip);
-
-void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB);
-
-void MFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
-          int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners,
-          vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
-
-
-// Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
-                  int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-                  vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
-
-
-// FFD including AHCA, instead of attempting to place item on end of strip, run AHCA to find feasible solution.
-void MFFDPlus(int tau, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
-              int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
-
-
-void FFD(int numScores, int numItem, int maxItemWidth, vector<int> &partners, vector<vector<int> > &itemWidths, vector<int> &itemOrder);
-
[…]

### 2018-05-17 SCSPP/COMBINED/base.cpp
recommit

@@ -1,0 +1,126 @@
+/*--------------/
+ALH
+base.cpp
+Combined Program with Heuristics and EA
+17/03/18
+/--------------*/
+
+#include <algorithm>
+#include <iomanip>
+#include "base.h"
+using namespace std;
+
+void ResetVar(int numScores, int numItem, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
+              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
+    int i, j;
+
+    for(i = 0; i < numScores; ++i){
+        partners[i] = 0;
+        for(j = 0; j < numScores; ++j){
+            adjMatrix[i][j] = 0;
+            itemWidths[i][j] = 0;
+        }
+    }
+
+    strip.clear();
+    strip.resize(numItem);
+    stripSum.clear();
+    stripSum.resize(numItem, 0);
+    allScores.clear();
+
+} //End ResetVar
+
+
+void Output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int optLow, int numInstances){
+
+    cout << setprecision(2) << fixed;
+    cout << "Number of Instances: " << numInstances << endl;
+    cout << "#        opt of LB: " << opt << "\t\tPercentage: "<< (static_cast<double>(opt)/numInstances) * 100 << "\t\t# 100%: " << opt << endl;
+    cout << "# 90% - <opt of LB: " << opt90 << "\t\tPercentage: "<< (static_cast<double>(opt90)/numInstances) * 100 << "\t\t# >= 90%: " << opt + opt90 << endl;
+    cout << "# 80% - <90% of LB: " << opt80 << "\t\tPercentage: "<< (static_cast<double>(opt80)/numInstances) * 100 << "\t\t# >= 80%: " << opt + opt90 + opt80 << endl;
+    cout << "# 70% - <80% of LB: " << opt70 << "\t\tPercentage: "<< (static_cast<double>(opt70)/numInstances) * 100 << "\t\t# >= 70%: " << opt + opt90 + opt80 + opt70 << endl;
+    cout << "# 60% - <70% of LB: " << opt60 << "\t\tPercentage: "<< (static_cast<double>(opt60)/numInstances) * 100 << "\t\t# >= 60%: " << opt + opt90 + opt80 + opt70 + opt60 << endl;
[…]

### 2018-05-17 SCSPP/COMBINED/base.h

@@ -1,0 +1,23 @@
+/*--------------/
+ALH
+base.h
+Combined Program with Heuristics and EA
+17/03/18
+/--------------*/
+
+#ifndef COMBINED_BASE_H
+#define COMBINED_BASE_H
+
+#include <iostream>
+#include <vector>
+using namespace std;
+
+void ResetVar(int numScores, int numItem, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
+              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+
+void Output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int optLow, int numInstances);
+
+void CreateInstance(int tau, int numScores, int numItem, int minWidth, int maxWidth, int minItemWidth, int maxItemWidth, double &totalItemWidth,
+                    vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths);
+
+#endif

### 2018-05-17 SCSPP/COMBINED/main.cpp

@@ -1,0 +1,371 @@
+/*--------------/
+ALH
+main.cpp
+Combined Program with Heuristics and EA
+17/03/2018
+/--------------*/
+
+#include <iostream>
+#include <fstream>
+#include <cmath>
+#include <cstring>
+#include <ctime>
+#include <chrono>
+#include <iomanip>
+using namespace std;
+
+#include "base.h"
+#include "packing.h"
+
+struct Timer{
+
+    std::chrono::high_resolution_clock::time_point startTime, endTime;
+    std::chrono::duration<float> totalTime;
+
+    Timer(){
+        startTime = std::chrono::high_resolution_clock::now();
+    }
+
+    ~Timer(){
+        endTime = std::chrono::high_resolution_clock::now();
+        totalTime = endTime - startTime;
+
+        float totalTimems = totalTime.count() * 1000.0f;
+        //cout << "\nCPU Time: " << totalTimems << "ms (" << totalTime.count() << "s)" << endl;
+        cout << totalTime.count() << endl;
+        //cout << totalTimems << endl;
+    }
+};
+
+void ProgramInfo(){
+
+    cout << "SCSPP:\n-------------\n"
+         << "PARAMETERS:\n"
+         << "       -i <int>    [Number of instances. Default = 1000.]\n"
+         << "       -t <int>    [Constraint value. Default = 70.]\n"
+         << "       -n <int>    [Number of items. Default = 500.]\n"
+         << "       -a <int>    [Minimum score width. Default = 1.]\n"
+         << "       -b <int>    [Maximum score width. Default = 70.]\n"
+         << "       -m <int>    [Minimum item width. Default = 150.]\n"
+         << "       -M <int>    [Maximum item width. Default = 1000.]\n"
+         << "       -W <int>    [Width of strips. Default = 5000.]\n"
+         << "       -s <int>    [Random seed. Default = 1.]\n"
+         << "---------------\n"
+         << "ALGORITHM:\n"
+         << "       -x <int>    [1: Basic approximate FFD.]\n"
+         << "                   [2: Pack strips in turn, choosing smallest feasible score width.]\n"
+         << "                   [3: FFD combined with AHCA (exact algorithm).]\n"
+         << "                   [4: Evolutionary Algorithm using Local Search.]\n"
+         << "       -r <int>    [Recombination operator. 1: GGA. 2: GPX'.]\n"
+         << "       -p <int>    [Number of solutions in population.]\n"
+         << "---------------\n\n";
+
+}
+
[…]

### 2018-05-17 SCSPP/COMBINED/packing.cpp

@@ -1,0 +1,2235 @@
+/*--------------/
+ALH
+packing.cpp
+Combined Program with Heuristics and EA
+17/03/18
+/--------------*/
+
+#include <algorithm>
+#include <iomanip>
+#include "packing.h"
+using namespace std;
+
+void Swap(int &a, int &b){
+    int temp = a;
+    a = b;
+    b = temp;
+}
+
+int LowerBound(double totalItemWidth, int stripWidth){
+    int lBound;
+
+    lBound = ceil(totalItemWidth/stripWidth);
+    return lBound;
+}
+
+double Fitness(int stripWidth, vector<int> &stripSum, vector<vector<int> > &strip){
+
+    int i;
+    double total = 0.0;
+    double final;
+
+    for(i = 0; i < strip.size(); ++i){
+        double a = static_cast<double>(stripSum[i]) / static_cast<double>(stripWidth);
+        total += pow(a, 2);
+    }
+
+    final = total / static_cast<double>(strip.size());
+
+    return final;
+
+}
+
+void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB){
+
+    double c = static_cast<double>(LB) / stripSize;
+    if(stripSize == LB){
+        ++opt;
+    }
+    else if(c >= 0.9){
+        ++opt90;
+    }
+    else if(c >= 0.8){
+        ++opt80;
+    }
+    else if(c >= 0.7){
+        ++opt70;
+    }
+    else if(c >= 0.6){
+        ++opt60;
+    }
+    else if(c >= 0.5){
+        ++opt50;
+    }
+    else{
+        ++optLow;
+    }
+} //End Optimality
+
+// FFD checking vicinal sum constraint for both sides of each item.
+void MFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
+          int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners,
+          vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
+    int i, j, mini;
+    int min = 0;
+    int max = maxItemWidth;
+    vector<int> itemDecrease;
+    vector<int> checked(numScores, 0);
+
+    while(itemDecrease.size() < numItem) {
+        for (i = 0; i < numScores; ++i) {
[…]

### 2018-05-17 SCSPP/COMBINED/packing.h

@@ -1,0 +1,108 @@
+/*--------------/
+ALH
+packing.h
+Combined Program with Heuristics and EA
+17/03/18
+/--------------*/
+
+#ifndef COMBINED_PACKING_H
+#define COMBINED_PACKING_H
+
+#include <iostream>
+#include <vector>
+using namespace std;
+
+void Swap(int &a, int &b);
+
+int LowerBound(double totalItemWidth, int stripWidth);
+
+double Fitness(int stripWidth, vector<int> &stripSum, vector<vector<int> > &strip);
+
+void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB);
+
+void MFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
+          int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners,
+          vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+
+
+// Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
+void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
+                  int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
+                  vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+
+
+// FFD including AHCA, instead of attempting to place item on end of strip, run AHCA to find feasible solution.
+void MFFDPlus(int tau, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
+              int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
+              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+
+
+void FFD(int numScores, int numItem, int maxItemWidth, vector<int> &partners, vector<vector<int> > &itemWidths, vector<int> &itemOrder);
+
[…]

### 2018-05-17 PAPER/main.tex
added bullet points to comparison

@@
 
+\begin{algorithm}
+\caption{MFFD$^+$}
+\label{alg:mffd+}
+\begin{algorithmic}[1]
+	\State Sort items in $\mathcal{I}$ in non-increasing order of widths $w_i$
+	\For{$i \gets 1 \To |\mathcal{I}|$}	
+		\State $j \gets 1$, packed $\gets \False$
+		\While{\textbf{not} packed}
+			\If{$S_j \in \mathcal{S}$ and $\sum_{i = 1}^{|S_j|}w_i + w_i \leq W$}
+				\State Run AHC
+				\If{AHC returns solution $\mathcal{F}$}
+					\State $S_j \gets \mathcal{F}$
+					\State packed $\gets \True$
+				\Else \hspace{0.5mm} $j \gets j + 1$	
+				\EndIf
+			\ElsIf{$S_j \notin \mathcal{S}$}
+				\State{$S_j \gets S_j \cup i$ in regular orientation}
+				\State $\mathcal{S} \gets \mathcal{S} \cup S_j$	
+				\State packed $\gets \True$
+			\EndIf
+		\EndWhile
+	\EndFor
+	\Return $\mathcal{S}$
+\end{algorithmic}	
+\end{algorithm}
+
 \begin{figure}[h!]	
@@
 The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
-The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the number of strips $k$ in the optimal solution, which was calculated using Equation \ref{eqn:lowerbound}.
+The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the lower bound for number of strips $k$, which was calculated using Equation \ref{eqn:lowerbound}.
 
 Firstly, it is apparent that the heuristics perform comparitively in the same manner regardless of the input size.
+
+\begin{itemize}
+	\item ``BPP becomes easier to solve when the number of items per bin increases, and problems with two or less items per bin are trivial to solve.
+Triplers are proposed to be `the most difficult bin packing instances''' \cite{falkenauer1996}.
+	\item Fair comparison, running over 1000 instances (average of 1000 instances)
+	\item Note that MFFD and MFFD$^+$ perform identically when $\delta = 1.0$, as they both perform in exactly the same manner as the original FFD heuristic  
+\end{itemize}
 

### 2018-05-17 SCSPP/COMBINED/packing.cpp
added extra segment to MFFDPlus that doesn't perform AHC on strips that only have one item, just checks constraints.

@@ -282,6 +282,54 @@ void MFFDPlus(int tau, int &opt, int &opt90, int &opt80, int &opt70, int &opt60,
         }
     }
 
+    /*
+    for(j = 1; j < itemDecrease.size(); ++j){
+        for(i = 0; i < strip.size(); ++i){
+            if(!strip[i].empty()){
+                if(stripSum[i] + itemWidths[itemDecrease[j]][partners[itemDecrease[j]]] <= stripWidth){
+                    if(strip[i].size() == 2){ //If the strip only contains one item, don't run AHCA, just do checks instead
+                        if(adjMatrix[strip[i].back()][itemDecrease[j]] == 1){
+                            strip[i].push_back(itemDecrease[j]);
+                            strip[i].push_back(partners[itemDecrease[j]]);
+                            stripSum[i] += itemWidths[itemDecrease[j]][partners[itemDecrease[j]]];
+                            break;
+                        }
+                        else if (adjMatrix[strip[i].back()][partners[itemDecrease[j]]] == 1){
+                            strip[i].push_back(partners[itemDecrease[j]]);
+                            strip[i].push_back(itemDecrease[j]);
+                            stripSum[i] += itemWidths[itemDecrease[j]][partners[itemDecrease[j]]];
+                            break;
+                        }
+                        else if(adjMatrix[strip[i].front()][itemDecrease[j]] == 1){
+                            strip[i].insert(strip[i].begin(), itemDecrease[j]);
+                            strip[i].insert(strip[i].begin(), partners[itemDecrease[j]]);
+                            stripSum[i] += itemWidths[itemDecrease[j]][partners[itemDecrease[j]]];
+                        }
+                        else if(adjMatrix[strip[i].front()][partners[itemDecrease[j]]] == 1){
+                            strip[i].insert(strip[i].begin(), partners[itemDecrease[j]]);
+                            strip[i].insert(strip[i].begin(), itemDecrease[j]);
+                            stripSum[i] += itemWidths[itemDecrease[j]][partners[itemDecrease[j]]];
+                        }
+                    }
+                    else {
+                        feasible = 0;
+                        AHCAH(tau, i, j, feasible, allScores, partners, adjMatrix, itemWidths, itemDecrease, stripSum,
+                              strip);
+                        if (feasible == 1) {
+                            break;
+                        }
+                    }
+                }
+            }
+            else if (strip[i].empty()){
[…]

### 2018-05-18 SCSPP/COMBINED/main.cpp
removed comments for writing to file and scope for individual Timer

@@ -212,7 +212,6 @@ int main(int argc, char **argv){
     ArgumentCheck(numInstances, tau, numItem, minWidth, maxWidth, minItemWidth, maxItemWidth, stripWidth, algType, numPop, xOver, randomSeed);
 
     int a, i, j, k, instance, bestStart, bestEnd;
-    int opt = 0, opt90 = 0, opt80= 0, opt70 = 0, opt60 = 0, opt50 = 0, optLow = 0;
     int numScores = numItem * 2;
     double totalItemWidth = 0.0;
     vector<int> allScores;
@@ -229,111 +228,50 @@ int main(int argc, char **argv){
     double tempFitness;
     vector<int> delta = { 145, 109, 97, 87, 79, 72, 65, 57, 47, 34, 0 };
     //double Delta = 0.0;
-
     //srand(randomSeed);
 
-    //Timer timer;
+    Timer timer;
 
     switch(algType){
-        case 1: {
-            /*ofstream results("1k1kbf.txt");
-            results << numItem << "\t" << stripWidth << "\tBasic" << endl;
-            results.close();*/
+        case 1:
             for (a = 0; a < delta.size(); ++a) {
                 tau = delta[a];
                 srand(randomSeed);
-                {
-                    Timer timer;
-                    for (instance = 0; instance < numInstances; ++instance) {
-                        CreateInstance(tau, numScores, numItem, minWidth, maxWidth, minItemWidth, maxItemWidth,
-                                       totalItemWidth, allScores, partners, adjMatrix, itemWidths);
-                        MFFD(opt, opt90, opt80, opt70, opt60, opt50, optLow, numScores, numItem, maxItemWidth,
-                             stripWidth, totalItemWidth, allScores, partners, adjMatrix, itemWidths, stripSum,
-                             strip);
-                        /*int lb = LowerBound(totalItemWidth, stripWidth);
-                        double opt = static_cast<double>(strip.size()) / static_cast<double>(lb);
-                        double itemPerStrip = static_cast<double>(numItem) / static_cast<double>(strip.size());
-                        results.open("1k1kbf.txt", ios::app);
-                        results << Delta << "\t" << totalItemWidth << "\t" << lb << "\t" << strip.size() << "\t" << itemPerStrip << "\t" << opt << endl;
-                        results.close();*/
-                        ResetVar(numScores, numItem, allScores, partners, adjMatrix, itemWidths, stripSum, strip);
-                    }
+                for (instance = 0; instance < numInstances; ++instance) {
[…]

### 2018-05-18 SCSPP/COMBINED/packing.cpp
added extra statements for MFFDPlus reduce times, removed unnecessary parameters in all functions, removed optimality function

@@ -40,35 +40,8 @@ double Fitness(int stripWidth, vector<int> &stripSum, vector<vector<int> > &stri
 
 }
 
-void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB){
-
-    double c = static_cast<double>(LB) / stripSize;
-    if(stripSize == LB){
-        ++opt;
-    }
-    else if(c >= 0.9){
-        ++opt90;
-    }
-    else if(c >= 0.8){
-        ++opt80;
-    }
-    else if(c >= 0.7){
-        ++opt70;
-    }
-    else if(c >= 0.6){
-        ++opt60;
-    }
-    else if(c >= 0.5){
-        ++opt50;
-    }
-    else{
-        ++optLow;
-    }
-} //End Optimality
-
 // FFD checking vicinal sum constraint for both sides of each item.
-void MFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
-          int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners,
+void MFFD(int numScores, int numItem, int maxItemWidth, int stripWidth, vector<int> &allScores, vector<int> &partners,
           vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
     int i, j, mini;
     int min = 0;
@@ -129,27 +102,12 @@ void MFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, 
         strip.pop_back();
     }
 
-    //int stripSize = strip.size();
-    //int LB = LowerBound(totalItemWidth, stripWidth);
-
-    //double avg = static_cast<double>(numItem) / static_cast<double>(stripSize);
-
-    //cout << "Lower Bound: " << LB << endl;
-    //cout << "# strips MFFD: " << stripSize << endl;
-    //cout << "Avg # items per strip: " << avg << endl << endl;
-    //cout << endl;
-
-    //cout << stripSize << endl;
-    //cout << avg << endl;
-
-    //Optimality(opt, opt90, opt80, opt70, opt60, opt50, optLow, stripSize, LB);
 
 } //End MFFD
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
[…]

### 2018-05-18 SCSPP/COMBINED/packing.h
removed optimality function and unnecessary parameters in all functions

@@ -18,23 +18,18 @@ int LowerBound(double totalItemWidth, int stripWidth);
 
 double Fitness(int stripWidth, vector<int> &stripSum, vector<vector<int> > &strip);
 
-void Optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB);
-
-void MFFD(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
-          int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners,
+void MFFD(int numScores, int numItem, int maxItemWidth, int stripWidth, vector<int> &allScores, vector<int> &partners,
           vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void PairSmallest(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
-                  int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
+void PairSmallest(int numScores, int stripWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
                   vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // FFD including AHCA, instead of attempting to place item on end of strip, run AHCA to find feasible solution.
-void MFFDPlus(int tau, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem,
-              int maxItemWidth, int stripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void MFFDPlus(int tau, int numScores, int numItem, int maxItemWidth, int stripWidth, vector<int> &allScores, vector<int> &partners,
+              vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
[…]

### 2018-05-18 PAPER/main.tex
added bullet points to comparison
added bullets to comparison, removed comments end speed times

--- 2018-05-16 PAPER/main.tex
@@
 The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
-The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the number of strips $k$ in the optimal solution, which was calculated using Equation \ref{eqn:lowerbound}.
+The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the lower bound for the number of strips $k$, which was calculated using Equation \ref{eqn:lowerbound}.
 
 Firstly, it is apparent that the heuristics perform comparitively in the same manner regardless of the input size.
+
+\begin{itemize}
+	\item ``BPP becomes easier to solve when the number of items per bin increases, and problems with two or less items per bin are trivial to solve.
+Triplers are proposed to be `the most difficult bin packing instances''' \cite{falkenauer1996}.
+	\item Fair comparison, running over 1000 instances (average of 1000 instances)
+	\item Note that MFFD and MFFD$^+$ perform identically when $\delta = 1.0$, as they both perform in exactly the same manner as the original FFD heuristic  
+	\item All instances completed in less than 160ms
+	\item PS is not able to reach highest optimality in any case from $\delta = 0.8$ onwards.
+\end{itemize}
 
@@
 
-\textbf{Speed $n$ = 500}
-\begin{itemize}
-	\item MFFD $W = 5000$ Average speed = 38.88504ms/instance
-	\item MFFD $W = 2500$ Average speed = 38.55795ms/instance
-	\item MFFD $W = 1250$ Average speed = 37.98091ms/instance
-	\item PS $W = 5000$ Average speed = 42.11938ms/instance
-	\item PS $W = 2500$ Average speed = 44.24521ms/instance
-	\item PS $W = 1250$ Average speed = 49.66614ms/instance
-	\item MFFD$^+$ $W = 5000$ Average speed = 214.04479ms/instance
-	\item MFFD$^+$ $W = 2500$ Average speed = 190.36579ms/instance
-	\item MFFD$^+$ $W = 1250$ Average speed = 214.78729ms/instance
-\end{itemize}
-
-\textbf{Speed $n$ = 1000}
-\begin{itemize}
-	\item MFFD $W = 5000$ Average speed = 159.68755ms/instance
-	\item MFFD $W = 2500$ Average speed = 157.92673ms/instance
-	\item MFFD $W = 1250$ Average speed = 154.45345ms/instance
-	\item PS $W = 5000$ Average speed = 168.77291ms/instance
-	\item PS $W = 2500$ Average speed = 176.81209ms/instance
-	\item PS $W = 1250$ Average speed = 201.522ms/instance
-	\item MFFD$^+$ $W = 5000$ Average speed = 825.59964ms/instance
-	\item MFFD$^+$ $W = 2500$ Average speed = 744.73509ms/instance
-	\item MFFD$^+$ $W = 1250$ Average speed = 434.67655ms/instance
-\end{itemize}
 \end{comment}

### 2018-05-31 PAPER/main.tex
added values for items/strip at end of paper
minor change in sentence explaining optimality ratio

@@
 The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
-The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the lower bound for the number of strips $k$, which was calculated using Equation \ref{eqn:lowerbound}.
+The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the lower bound for the optimal number of strips $k$, which was calculated using Equation \ref{eqn:lowerbound}.
 
@@
 	\item PS is not able to reach highest optimality in any case from $\delta = 0.8$ onwards.
+	\item 
 \end{itemize}
@@
 	\item Average total item width = 57466.776, $\sigma$ = 2499.06092
-	\item $W = 5000$, Average LB = 11.993, $\sigma$ = 0.56829
-	\item $W = 2500$, Average LB = 23.478, $\sigma$ = 1.05618
-	\item $W = 1250$, Average LB = 46.466, $\sigma$ = 2.02703
+	\item $W = 5000$, Average LB = 11.993, $\sigma$ = 0.56829, i/s = 8.3333
+	\item $W = 2500$, Average LB = 23.478, $\sigma$ = 1.05618, i/s = 4.1667
+	\item $W = 1250$, Average LB = 46.466, $\sigma$ = 2.02703, i/s = 2.1277
 \end{itemize}
@@
 	\item Average total item width = 287683.855, $\sigma$ = 5434.63046
-	\item $W = 5000$, Average LB = 58.039, $\sigma$ = 1.12227
-	\item $W = 2500$, Average LB = 115.571, $\sigma$ = 2.18150
-	\item $W = 1250$, Average LB = 230.648, $\sigma$ = 4.35041
+	\item $W = 5000$, Average LB = 58.039, $\sigma$ = 1.12227, i/s = 8.4746
+	\item $W = 2500$, Average LB = 115.571, $\sigma$ = 2.18150, i/s = 4.3103
+	\item $W = 1250$, Average LB = 230.648, $\sigma$ = 4.35041, i/s = 2.1645
 \end{itemize}
@@
 	\item Average total item width = 575163.174, $\sigma$ = 7880.93401
-	\item $W = 5000$, Average LB = 115.534, $\sigma$ = 1.59463
-	\item $W = 2500$, Average LB = 230.563, $\sigma$ = 3.16734
-	\item $W = 1250$, Average LB = 460.623, $\sigma$ = 6.30895
+	\item $W = 5000$, Average LB = 115.534, $\sigma$ = 1.59463, i/s = 8.6207
+	\item $W = 2500$, Average LB = 230.563, $\sigma$ = 3.16734, i/s = 4.3290
+	\item $W = 1250$, Average LB = 460.623, $\sigma$ = 6.30895, i/s = 2.1692
 \end{itemize}

### 2018-06-05 SCSPP/HEURISTICS/base.cpp
full working version of 3 heuristics for paper

@@ -8,8 +8,8 @@ base.cpp
 #include "base.h"
 using namespace std;
 
-void resetVectors(int numScores, int numItem, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-                  vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
+void ResetVar(int numScores, int numItem, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
+              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
     int i, j;
 
     for(i = 0; i < numScores; ++i){
@@ -20,41 +20,17 @@ void resetVectors(int numScores, int numItem, vector<int> &allScores, vector<int
         }
     }
 
-    while(!strip.empty()){
-        strip.pop_back();
-    }
-
-    while(!stripSum.empty()){
-        stripSum.pop_back();
-    }
-
-    vector<int> temp;
-    for(i = 0; i < numItem; ++i){
-        strip.push_back(temp);
-        stripSum.push_back(0);
-    }
-
+    strip.clear();
+    strip.resize(numItem);
+    stripSum.clear();
+    stripSum.resize(numItem, 0);
     allScores.clear();
 
-} //End resetVectors
+} //End ResetVar
 
 
-void output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int optLow, int numInstances){
 
-    cout << setprecision(2) << fixed;
-    cout << "Number of Instances: " << numInstances << endl;
-    cout << "#        opt of LB: " << opt << "\t\tPercentage: "<< (static_cast<double>(opt)/numInstances) * 100 << "\t\t# 100%: " << opt << endl;
-    cout << "# 90% - <opt of LB: " << opt90 << "\t\tPercentage: "<< (static_cast<double>(opt90)/numInstances) * 100 << "\t\t# >= 90%: " << opt + opt90 << endl;
-    cout << "# 80% - <90% of LB: " << opt80 << "\t\tPercentage: "<< (static_cast<double>(opt80)/numInstances) * 100 << "\t\t# >= 80%: " << opt + opt90 + opt80 << endl;
-    cout << "# 70% - <80% of LB: " << opt70 << "\t\tPercentage: "<< (static_cast<double>(opt70)/numInstances) * 100 << "\t\t# >= 70%: " << opt + opt90 + opt80 + opt70 << endl;
[…]

### 2018-06-05 SCSPP/HEURISTICS/base.h

@@ -11,12 +11,10 @@ base.h
 #include <vector>
 using namespace std;
 
-void resetVectors(int numScores, int numItem, vector<int> &allScores, vector<int> &partners,
-                  vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void ResetVar(int numScores, int numItem, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
+              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
-void output(int opt, int opt90, int opt80, int opt70, int opt60, int opt50, int optLow, int numInstances);
-
-void createInstance(int instance, int tau, int numScores, int numItem, int minWidth, int maxWidth, int minItemWidth, int maxItemWidth, double &totalItemWidth,
+void CreateInstance(int tau, int numScores, int numItem, int minWidth, int maxWidth, int minItemWidth, int maxItemWidth, double &totalItemWidth,
                     vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths);
 
 

### 2018-06-05 SCSPP/HEURISTICS/main.cpp

@@ -7,13 +7,34 @@ mainexact.cpp
 #include <fstream>
 #include <cstring>
 #include <ctime>
+#include <chrono>
 #include <iomanip>
 using namespace std;
 
 #include "base.h"
 #include "packing.h"
 
-void programInfo(){
+struct Timer{
+
+    std::chrono::high_resolution_clock::time_point startTime, endTime;
+    std::chrono::duration<float> totalTime;
+
+    Timer(){
+        startTime = std::chrono::high_resolution_clock::now();
+    }
+
+    ~Timer(){
+        endTime = std::chrono::high_resolution_clock::now();
+        totalTime = endTime - startTime;
+
+        float totalTimems = totalTime.count() * 1000.0f;
+        //cout << "\nCPU Time: " << totalTimems << "ms (" << totalTime.count() << "s)" << endl;
+        cout << totalTime.count() << endl;
+        //cout << totalTimems << endl;
+    }
+};
+
+void ProgramInfo(){
 
     cout << "SCSPP:\n-------------\n"
          << "PARAMETERS:\n"
@@ -22,53 +43,64 @@ void programInfo(){
          << "       -n <int>    [Number of items. Default = 500.]\n"
          << "       -a <int>    [Minimum score width. Default = 1.]\n"
          << "       -b <int>    [Maximum score width. Default = 70.]\n"
-         << "       -w <int>    [Minimum item width. Default = 150.]\n"
-         << "       -W <int>    [Maximum item width. Default = 1000.]\n"
-         << "       -l <int>    [Length of strips. Default = 5000.]\n"
+         << "       -m <int>    [Minimum item width. Default = 150.]\n"
+         << "       -M <int>    [Maximum item width. Default = 1000.]\n"
+         << "       -W <int>    [Width of strips. Default = 5000.]\n"
          << "       -s <int>    [Random seed. Default = 1.]\n"
          << "---------------\n"
-         << "HEURISTICS:\n"
-         << "       -p <int>    [Type of heuristic to be used.]\n"
-         << "                   [1 = Basic approximate FFD.]\n"
-         << "                   [2 = Pack strips in turn, choosing smallest feasible score width.]\n"
-         << "                   [3 = FFD combined with AHCA (exact algorithm).]\n"
+         << "ALGORITHM:\n"
+         << "       -x <int>    [1: Basic approximate FFD.]\n"
+         << "                   [2: Pack strips in turn, choosing smallest feasible score width.]\n"
[…]

### 2018-06-05 SCSPP/HEURISTICS/packing.cpp

@@ -7,42 +7,15 @@ packing.cpp
 #include "packing.h"
 using namespace std;
 
-int lowerBound(int maxStripWidth, double totalItemWidth){
+int LowerBound(double totalItemWidth, int stripWidth){
     int lBound;
-    lBound = ceil(totalItemWidth/maxStripWidth);
+
+    lBound = ceil(totalItemWidth/stripWidth);
     return lBound;
-} //End lowerBound
+}
 
-void optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB){
-
-    double c = static_cast<double>(LB) / stripSize;
-    if(stripSize == LB){
-        ++opt;
-    }
-    else if(c >= 0.9){
-        ++opt90;
-    }
-    else if(c >= 0.8){
-        ++opt80;
-    }
-    else if(c >= 0.7){
-        ++opt70;
-    }
-    else if(c >= 0.6){
-        ++opt60;
-    }
-    else if(c >= 0.5){
-        ++opt50;
-    }
-    else{
-        ++optLow;
-    }
-} //End optimality
-
-// FFD checking vicinal sum constraint for both sides of each item.
-void basicFFD(int instance, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
-              int maxStripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-              vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
+void MFFD(int numScores, int numItem, int maxItemWidth, int stripWidth, vector<int> &allScores, vector<int> &partners,
+          vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip){
     int i, j, mini;
     int min = 0;
     int max = maxItemWidth;
@@ -73,7 +46,7 @@ void basicFFD(int instance, int &opt, int &opt90, int &opt80, int &opt70, int &o
     for(j = 1; j < itemDecrease.size(); ++j){
         for(i = 0; i < strip.size(); ++i){
             if(!strip[i].empty()){
-                if(stripSum[i] + itemWidths[itemDecrease[j]][partners[itemDecrease[j]]] <= maxStripWidth){
[…]

### 2018-06-05 SCSPP/HEURISTICS/packing.h

@@ -11,54 +11,42 @@ packing.h
 using namespace std;
 
 
-int lowerBound(int maxStripWidth, double totalItemWidth);
+int LowerBound(double totalItemWidth, int stripWidth);
 
-void optimality(int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int stripSize, int LB);
 
-// FFD checking vicinal sum constraint for both sides of each item.
-void basicFFD(int instance, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth,
-                         int maxStripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-                         vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void MFFD(int numScores, int numItem, int maxItemWidth, int stripWidth, vector<int> &allScores, vector<int> &partners,
+          vector<vector<int> > &adjMatrix, vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // Packing each strip in turn, choosing smallest score width that meets vicinal sum constraint.
-void pairSmallest(int instance, int &opt, int &opt90, int &opt80, int &opt70, int &opt60, int &opt50, int &optLow, int numScores,
-                           int maxStripWidth, double totalItemWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
-                           vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
+void PairSmallest(int numScores, int stripWidth, vector<int> &allScores, vector<int> &partners, vector<vector<int> > &adjMatrix,
+                  vector<vector<int> > &itemWidths, vector<int> &stripSum, vector<vector<int> > &strip);
 
 
 // FFD including AHCA, instead of attempting to place item on end of strip, run AHCA to find feasible solution.
-void FFDincAHCA(int instance, int tau, int &opt, int &opt90, int &opt80, int &opt70,
-                int &opt60, int &opt50, int &optLow, int numScores, int numItem, int maxItemWidth, int maxStripWidth, double totalItemWidth,
[…]

### 2018-06-05 PAPER/main.tex
changed layout of tables, removed n=100 table, added theoretical min

@@
 		\label{eqn:vsc}
-		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
+		\emph{\textbf{rhs}}(i) + \emph{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
 	\end{equation}
-	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the \textup{vicinal sum constraint}.
+	where \emph{\textbf{lhs}($i$)} and \emph{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the \emph{vicinal sum constraint}.
 \end{definition}
@@
 
-An optimal solution $\mathcal{S}$ of an instance of the SCSPP is a solution that consists of the fewest number of strips $k$.
-A simple lower bound for $k$ that can be computed in $O(n)$ time is given by
+An optimal solution $\mathcal{S}$ for the SCSPP is a solution that consists of the fewest number of strips $k$ needed to feasibly contain the $|\mathcal{I}|$ items in the given problem instance.
+A simple lower bound for $k$ is the theoretical minimum
 \begin{equation}
 \label{eqn:lowerbound}
-k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{W}},
+t = \ceil*{\frac{\sum_{i=1}^{|\mathcal{I}|}w_i}{W}},
 \end{equation}
-where $n = |\mathcal{I}|$ is the number of items (\citealp{martello1990b}).
+which can be computed in linear time (\citealp{martello1990b}).
 Perhaps the simplest and most well-known heuristic for packing problems is \textsc{First-Fit} (FF), a greedy online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
@@
 More recently, \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight.
-Due to the initial sorting of the $n$ items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$.
+Due to the initial sorting of the items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$, where $n = |\mathcal{I}|$ is the input size.
 
@@
 In addition, removing an item in the BPP retains feasibility, whereas in the SCSPP this is not guaranteed, as it may leave a subset of items for which the vicinal sum constraint is not satisfied.
-Furthermore, the lower bound for $k$ (Equation (\ref{eqn:lowerbound})) has the potential to be less accurate for the SCSPP, as the minimum scoring distance $\tau$ is not considered.
-For example, if the minimum scoring distance is greater than twice the largest score width, then it is clear that $n$ strips will be required, regardless of the items' widths.
+Furthermore, the theoretical minimum $t$ (Equation (\ref{eqn:lowerbound})) has the potential to be less accurate for the SCSPP, as the minimum scoring distance $\tau$ is not considered.
+For example, if the minimum scoring distance is greater than twice the largest score width, then it is clear that $|\mathcal{I}|$ strips will be required, regardless of the items' widths.
 % Time complexity for FFD also inaccurate
@@
 The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
-The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the lower bound for the optimal number of strips $k$, which was calculated using Equation \ref{eqn:lowerbound}.
+The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the theoretical minimum $t$, which was calculated using Equation \ref{eqn:lowerbound}.
 
@@
 \begin{itemize}
-	\item ``BPP becomes easier to solve when the number of items per bin increases, and problems with two or less items per bin are trivial to solve.
-Triplers are proposed to be `the most difficult bin packing instances''' \cite{falkenauer1996}.
-	\item Fair comparison, running over 1000 instances (average of 1000 instances)
-	\item Note that MFFD and MFFD$^+$ perform identically when $\delta = 1.0$, as they both perform in exactly the same manner as the original FFD heuristic  
-	\item All instances completed in less than 160ms
-	\item PS is not able to reach highest optimality in any case from $\delta = 0.8$ onwards.
+	\item \textbf{PairSmallest:}
+	\item Best average optimality over all three set sizes for $W = 5000$ and $W = 2500$ for $\delta = 0.1 - 0.6$, in some cases up to $\delta = 0.8$.
+	\item However, when $W = 1250$, PS only has best average optimality for $\delta = 0.1$ and $\delta = 0.2$. 
+	\item PS is able to obtain solution that are on average within 10\% of the lower bound for the optimal solution for $\delta = 0.6$ onwards when $W=5000$ and $W = 2500$.
+	\item When $W = 1250$, PS only obtains solutions within 10\% of the lowerbound for $\delta = 0.8$ onwards with set sizes 500 and 1000.
+For $|\mathcal{I}| = 100$, PS is not able to (on average) obtain solutions within 10\% of the lower bound for any value of $\delta$.
+	\item Clear pattern across all three set sizes, PS performs better when the strip widths are wider, however PS is still the best of the three heuristics for smaller strip widths and harder problems, i.e.
+when $\delta$ is smaller.
+	\item PS never obtains avg solution within 1\% of lower bound.
+\end{itemize}
+
+\begin{itemize}
+	\item optimality converge toward 1 as $\delta$ increases, i.e. as the problem instances become less difficult.
+	\item When $\delta = 1.0$. MFFD and MFFD$^+$ perform identically, as the problems are equivalent to the original BPP, and so they behave like the original FFD heuristic.
+	\item When $\delta = 0.0$, all optimalities are equal, as each item requires its own strip, and so $|\mathcal{I}|$ strips are needed for all 1000 instances.
+	\item Values in bold represent the best avg optimality of the three heuristics for the given level of $\delta$. 
+	\item Clear pattern across both set sizes, PS performs the best out of the three for $\delta = 0.1$ to 0.7 when $W = 5000$, and for $\delta = 0.1$ to 0.6 when $W = 2500$.
+	\item However, when $W = 1250$, PS is only superior when $\delta = 0.1$ and 0.2. 
+	\item On further inspection, we can see that the difference between the average optimalities for PS and MFFD$^+$ is negligible.
+	\item Using Table 1 as an example, when $\delta = 0.2$, the solutions generated by PS are on average within 31.781\% of $t$, and for MFFD$^+$ within 32.61\%, a difference of 0.829\%. 
+	\item In practical terms, PS produces solutions using 303.95 strips on average, where $t = 230.648$. MFFD$^+$ produces solutions using 305.862 strips, a difference of less than two strips. 
+	\item Another trend is that PS produces average solutions within 10\% of $t$ for $\delta = 0.5$ onwards when $W = 5000$ and 2500, however when $W = 1250$, PS only produces solutions within 10\% of $t$ for $\delta = 0.8$ onwards.
+	\item In contrast, MFFD and MFFD$^+$ can produce solution within 10\% of $t$ when $W = 1250$ for $\delta = 0.5$ onwards for $n = 500$, and $\delta = 0.4$ for $n = 1000$.
+	\item MFFD$^+$ can also find solutions within 1\% of $t$ for $\delta = 0.8$ onwards for all strip widths in both set sizes.
+	\item Number of items per strip smaller, problem is harder, falkenauer 1996, martello and toth 1990b
 	\item 
@@
 	\centering
-	\caption{$n = 100$}
-	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
-		\noalign{\smallskip}
-		& \multicolumn{3}{c}{$W = 5000$} & \multicolumn{3}{c}{$W = 2500$} & \multicolumn{3}{c}{$W = 1250$} \\
-		\hline\noalign{\smallskip}
-		$\delta$ & MFFD & PS & MFFD$^+$ & MFFD & PS & MFFD$^+$ & MFFD & PS & MFFD$^+$ \\
-		\noalign{\smallskip}
-		\hline 
-		\noalign{\smallskip}
-		0.0	& 8.35709 & 8.35709 & 8.35709 & 4.26800 & 4.26800 & 4.26800 & 2.15624 & 2.15624 & 2.15624 \\
-		0.1	& 5.27284 & \textbf{4.89963} & 5.14404 & 2.72299 & \textbf{2.48800} & 2.69191 & 1.53147 & \textbf{1.51049} & 1.52968 \\
-		0.2	& 4.16155 & \textbf{3.46467} & 3.98645 & 2.21096 & \textbf{1.87449} & 2.16338 & 1.34812 & \textbf{1.34499} & 1.34593 \\
-		0.3	& 3.27805 & \textbf{2.40153} & 3.05546 & 1.82199 & \textbf{1.43724} & 1.75610 & 1.22453 & 1.24810 & \textbf{1.21994} \\
-		0.4	& 2.61641 & \textbf{1.63390} & 2.33662 & 1.54989 & \textbf{1.16887} & 1.46534 & 1.14507 & 1.19631 & \textbf{1.13979} \\
-		0.5	& 2.08260 & \textbf{1.13827} & 1.77494 & 1.35101 & \textbf{1.04978} & 1.25567 & 1.09274 & 1.17069 & \textbf{1.08661} \\
-		0.6	& 1.65897 & \textbf{1.02027} & 1.36093 & 1.20040 & \textbf{1.03720} & 1.11964 & 1.06255 & 1.15766 & \textbf{1.05701} \\
-		0.7	& 1.32002 & \textbf{1.01350} & 1.11348 & 1.09659 & \textbf{1.03556} & 1.04569 & 1.04546 & 1.14416 & \textbf{1.04150} \\
-		0.8	& 1.10725 & \textbf{1.01384} & 1.02188 & 1.03577 & 1.03439 & \textbf{1.01696} & 1.03711 & 1.12951 & \textbf{1.03565} \\
-		0.9	& 1.02134 & 1.01315 & \textbf{1.00646} & 1.01364 & 1.03285 & \textbf{1.01029} & 1.03434 & 1.11631 & \textbf{1.03416} \\
-		1.0 & \textbf{1.00480} & 1.01302 & \textbf{1.00480} & \textbf{1.00919} & 1.03261 & \textbf{1.00919} & \textbf{1.03393} & 1.10807 & \textbf{1.03393} \\	
-		\hline
+	\ra{1.3}
+	\caption{Average optimality ratios for $|\mathcal{I}| = 500$.}
+	\begin{tabular}{@{}c@{\hspace{25pt}}c@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}c@{}}\toprule
+		& \multicolumn{3}{c}{$W = 5000$, $t = 58.039$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 2500$, $t = 115.571$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 1250$, $t = 230.648$} \\
+		\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
+		$\delta$ & MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$\\ \midrule
+		0.0 & 8.61813 & 8.61813 & 8.61813 && 4.32789 & 4.32789 & 4.32789 && 2.16858 & 2.16858 & 2.16858 \\
+		0.1 & 5.21367 & \textbf{4.84177} & 5.16085 && 2.65934 & \textbf{2.47735} & 2.65679 && 1.51486 & \textbf{1.47896} & 1.51486 \\
+		0.2 & 4.03055 & \textbf{3.45946} & 3.97645 && 2.12099 & \textbf{1.84737} & 2.11788 && 1.32613 & \textbf{1.31781} & 1.32610 \\
+		0.3 & 3.11091 & \textbf{2.34803} & 3.03816 && 1.72955 & \textbf{1.39676} & 1.70772 && 1.19451 & 1.22922 & \textbf{1.19381} \\
+		0.4 & 2.43605 & \textbf{1.52907} & 2.29713 && 1.45976 & \textbf{1.12798} & 1.40951 && 1.11037 & 1.18065 & \textbf{1.10819} \\
+		0.5 & 1.91057 & \textbf{1.04130} & 1.69129 && 1.26343 & \textbf{1.03341} & 1.19575 && 1.05771 & 1.15415 & \textbf{1.05319} \\
+		0.6 & 1.49086 & \textbf{1.01263} & 1.24645 && 1.12448 & \textbf{1.02957} & 1.06874 && 1.02932 & 1.13470 & \textbf{1.02398} \\
+		0.7 & 1.19571 & \textbf{1.01257} & 1.04468 && 1.04933 & 1.02774 & \textbf{1.01918} && 1.01741 & 1.11368 & \textbf{1.01444} \\
+		0.8 & 1.04977 & 1.01203 & \textbf{1.00815} && 1.01595 & 1.02661 & \textbf{1.00790} && 1.01297 & 1.09136 & \textbf{1.01197} \\
+		0.9 & 1.00929 & 1.01197 & \textbf{1.00463} && 1.00734 & 1.02586 & \textbf{1.00641} && 1.01159 & 1.07283 & \textbf{1.01139} \\
+		1.0 & \textbf{1.00423} & 1.01171 & \textbf{1.00423} && \textbf{1.00626} & 1.02561 & \textbf{1.00626} && \textbf{1.01130} & 1.06549 & \textbf{1.01130} \\
+		\bottomrule
 	\end{tabular}	
-	\label{table:n100}
+	\label{table:n=500}
 \end{table}
@@
 	\centering
-	\caption{$n = 500$}
-	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
-		\noalign{\smallskip}
-		& \multicolumn{3}{c}{$W = 5000$} & \multicolumn{3}{c}{$W = 2500$} & \multicolumn{3}{c}{$W = 1250$} \\
-		\hline\noalign{\smallskip}
-		$\delta$ & MFFD & PS & MFFD$^+$ & MFFD & PS & MFFD$^+$ & MFFD & PS & MFFD$^+$ \\
-		\noalign{\smallskip}
-		\hline
-		\noalign{\smallskip}
-		0.0 & 8.61813 & 8.61813 & 8.61813 & 4.32789 & 4.32789 & 4.32789 & 2.16858 & 2.16858 & 2.16858 \\
-		0.1 & 5.21367 & \textbf{4.84177} & 5.16085 & 2.65934 & \textbf{2.47735} & 2.65679 & 1.51486 & \textbf{1.47896} & 1.51486 \\
-		0.2 & 4.03055 & \textbf{3.45946} & 3.97645 & 2.12099 & \textbf{1.84737} & 2.11788 & 1.32613 & \textbf{1.31781} & 1.32610 \\
-		0.3 & 3.11091 & \textbf{2.34803} & 3.03816 & 1.72955 & \textbf{1.39676} & 1.70772 & 1.19451 & 1.22922 & \textbf{1.19381} \\
-		0.4 & 2.43605 & \textbf{1.52907} & 2.29713 & 1.45976 & \textbf{1.12798} & 1.40951 & 1.11037 & 1.18065 & \textbf{1.10819} \\
-		0.5 & 1.91057 & \textbf{1.04130} & 1.69129 & 1.26343 & \textbf{1.03341} & 1.19575 & 1.05771 & 1.15415 & \textbf{1.05319} \\
-		0.6 & 1.49086 & \textbf{1.01263} & 1.24645 & 1.12448 & \textbf{1.02957} & 1.06874 & 1.02932 & 1.13470 & \textbf{1.02398} \\
-		0.7 & 1.19571 & \textbf{1.01257} & 1.04468 & 1.04933 & 1.02774 & \textbf{1.01918} & 1.01741 & 1.11368 & \textbf{1.01444} \\
-		0.8 & 1.04977 & 1.01203 & \textbf{1.00815} & 1.01595 & 1.02661 & \textbf{1.00790} & 1.01297 & 1.09136 & \textbf{1.01197} \\
-		0.9 & 1.00929 & 1.01197 & \textbf{1.00463} & 1.00734 & 1.02586 & \textbf{1.00641} & 1.01159 & 1.07283 & \textbf{1.01139} \\
-		1.0 & \textbf{1.00423} & 1.01171 & \textbf{1.00423} & \textbf{1.00626} & 1.02561 & \textbf{1.00626} & \textbf{1.01130} & 1.06549 & \textbf{1.01130} \\		
-		\hline
+	\ra{1.3}
+	\caption{Average optimality ratios for $|\mathcal{I}| = 1000$.}
+	\begin{tabular}{@{}c@{\hspace{25pt}}c@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}c@{}}\toprule
+		& \multicolumn{3}{c}{$W = 5000$, $t = 115.534$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 2500$, $t = 230.563$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 1250$, $t = 460.623$} \\
+		\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
+		$\delta$ & MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$\\ \midrule
+		0.0 & 8.65711 & 8.65711 & 8.65711 && 4.33803 & 4.33803 & 4.33803 && 2.17138 & 2.17138 & 2.17138 \\
+		0.1 & 5.17263 & \textbf{4.84248} & 5.14027 && 2.63606 & \textbf{2.48111} & 2.64271 && 1.51056 & \textbf{1.46744} & 1.51121 \\
+		0.2 & 3.97565 & \textbf{3.46163} & 3.95164 && 2.09301 & \textbf{1.85824} & 2.10161 && 1.31785 & \textbf{1.31090} & 1.31876 \\
+		0.3 & 3.04866 & \textbf{2.35023} & 3.01260 && 1.69777 & \textbf{1.40862} & 1.68776 && \textbf{1.18304} & 1.22111 & 1.18344 \\
+		0.4 & 2.37436 & \textbf{1.52046} & 2.26560 && 1.42646 & \textbf{1.13101} & 1.38430 && 1.09722 & 1.17063 & \textbf{1.09614} \\
+		0.5 & 1.84748 & \textbf{1.02600} & 1.64169 && 1.22960 & \textbf{1.03017} & 1.16950 && 1.04411 & 1.14430 & \textbf{1.03986} \\
+		0.6 & 1.43331 & \textbf{1.01212} & 1.20264 && 1.09935 & \textbf{1.02738} & 1.05010 && 1.01971 & 1.12392 & \textbf{1.01480} \\
+		0.7 & 1.15500 & \textbf{1.01198} & 1.02574 && 1.03421 & 1.02569 & \textbf{1.01224} && 1.01150 & 1.10164 & \textbf{1.00926} \\
+		0.8 & 1.03182 & 1.01182 & \textbf{1.00587} && 1.01111 & 1.02454 & \textbf{1.00682} && 1.00861 & 1.07791 & \textbf{1.00804} \\
+		0.9 & 1.00707 & 1.01165 & \textbf{1.00419} && 1.00663 & 1.02406 & \textbf{1.00608} && 1.00784 & 1.05885 & \textbf{1.00774} \\
+		1.0 & \textbf{1.00399} & 1.01169 & \textbf{1.00399} && \textbf{1.00603} & 1.02400 & \textbf{1.00603} && \textbf{1.00770} & 1.05406 & \textbf{1.00770} \\
+		\bottomrule
 	\end{tabular}
-	\label{table:n500}
+	\label{table:n=1000}	
 \end{table}
 
+\begin{comment}
+\begin{itemize}
+	\item ``BPP becomes easier to solve when the number of items per bin increases, and problems with two or less items per bin are trivial to solve.
+Triplets are proposed to be `the most difficult bin packing instances''' \cite{falkenauer1996}.
+	\item Fair comparison, running over 1000 instances (average of 1000 instances)
+	\item Note that MFFD and MFFD$^+$ perform identically when $\delta = 1.0$, as they both perform in exactly the same manner as the original FFD heuristic  
+	\item All instances completed in less than 160ms
+	\item PS is not able to reach highest optimality in any case from $\delta = 0.8$ onwards.
+	\item If optimality = 1 then lower bound reached
+	\item state that bold is best optimality
+	\item PS never obtains best avg optimality at  $\delta = 1.0$ in any case
+	\item As W decreases, i.e. items/strip decreases, PS becomes less efficient, mffd+ better
+	\item n = 1000 W = 1250 PS doesnt obtain soln $<$ 10\% for any value of $\delta$
+	\item mffd+ $<$ 10\% for $\delta = 0.8$ onwards in all cases
+	\item mffd+ and mffd+ able to get $<$ 10\% for W = 1250 for n = 100 and 500 $\delta = 0.5$, and n = 1000 $\delta = 0.4$ onwards
+	\item PS never obtains avg solns $<$ 1\% in any case
+	\item In a few cases, mffd+ able to get avg opt $<$ 1\% for smaller values of $\delta$ than mffd.
+	\item PS able to get $<$ 10\% for $\delta = 0.6$ onwards in n= 100, 500, 1000, and W=5000,2500, but reduces significantly when W = 1250.
+	\item First row is avg number of items per strip.
+\end{itemize}
+\end{comment}
+
+\begin{comment}
 \begin{table}[!htb]
 	\centering
-	\caption{$n = 1000$}
-	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}}c@{\hspace{10pt}}c@{\hspace{10pt}}c@{\hspace{7pt}}| @{\hspace{7pt}} c@{\hspace{10pt}}c@{\hspace{10pt}}c}
-		\noalign{\smallskip}
-		& \multicolumn{3}{c}{$W = 5000$} & \multicolumn{3}{c}{$W = 2500$} & \multicolumn{3}{c}{$W = 1250$} \\
-		\hline\noalign{\smallskip}
-		$\delta$ & MFFD & PS & MFFD$^+$ & MFFD & PS & MFFD$^+$ & MFFD & PS & MFFD$^+$ \\
-		\noalign{\smallskip}
-		\hline
-		\noalign{\smallskip}
-		0.0 & 8.65711 & 8.65711 & 8.65711 & 4.33803 & 4.33803 & 4.33803 & 2.17138 & 2.17138 & 2.17138 \\
-		0.1 & 5.17263 & \textbf{4.84248} & 5.14027 & 2.63606 & \textbf{2.48111} & 2.64271 & 1.51056 & \textbf{1.46744} & 1.51121 \\
-		0.2 & 3.97565 & \textbf{3.46163} & 3.95164 & 2.09301 & \textbf{1.85824} & 2.10161 & 1.31785 & \textbf{1.31090} & 1.31876 \\
-		0.3 & 3.04866 & \textbf{2.35023} & 3.01260 & 1.69777 & \textbf{1.40862} & 1.68776 & \textbf{1.18304} & 1.22111 & 1.18344 \\
-		0.4 & 2.37436 & \textbf{1.52046} & 2.26560 & 1.42646 & \textbf{1.13101} & 1.38430 & 1.09722 & 1.17063 & \textbf{1.09614} \\
-		0.5 & 1.84748 & \textbf{1.02600} & 1.64169 & 1.22960 & \textbf{1.03017} & 1.16950 & 1.04411 & 1.14430 & \textbf{1.03986} \\
-		0.6 & 1.43331 & \textbf{1.01212} & 1.20264 & 1.09935 & \textbf{1.02738} & 1.05010 & 1.01971 & 1.12392 & \textbf{1.01480} \\
-		0.7 & 1.15500 & \textbf{1.01198} & 1.02574 & 1.03421 & 1.02569 & \textbf{1.01224} & 1.01150 & 1.10164 & \textbf{1.00926} \\
-		0.8 & 1.03182 & 1.01182 & \textbf{1.00587} & 1.01111 & 1.02454 & \textbf{1.00682} & 1.00861 & 1.07791 & \textbf{1.00804} \\
-		0.9 & 1.00707 & 1.01165 & \textbf{1.00419} & 1.00663 & 1.02406 & \textbf{1.00608} & 1.00784 & 1.05885 & \textbf{1.00774} \\
-		1.0 & \textbf{1.00399} & 1.01169 & \textbf{1.00399} & \textbf{1.00603} & 1.02400 & \textbf{1.00603} & \textbf{1.00770} & 1.05406 & \textbf{1.00770} \\
-		\hline
+	\ra{1.2}
+	\caption{Average optimality ratios for $|\mathcal{I}| = 100$. Average $t$ for $W = 5000$, 2500 and 1250 are 11.993, 23.478, and 46.466 respectively.}
+	\begin{tabular}{@{}c@{\hspace{25pt}}c@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}c@{}}\toprule
+		& \multicolumn{3}{c}{$W = 5000$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 2500$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 1250$} \\
+		\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
+		$\delta$ & MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$\\ \midrule
+		0.0	& 8.35709 & 8.35709 & 8.35709 && 4.26800 & 4.26800 & 4.26800 && 2.15624 & 2.15624 & 2.15624 \\
+		0.1	& 5.27284 & \textbf{4.89963} & 5.14404 && 2.72299 & \textbf{2.48800} & 2.69191 && 1.53147 & \textbf{1.51049} & 1.52968 \\
+		0.2	& 4.16155 & \textbf{3.46467} & 3.98645 && 2.21096 & \textbf{1.87449} & 2.16338 && 1.34812 & \textbf{1.34499} & 1.34593 \\
+		0.3	& 3.27805 & \textbf{2.40153} & 3.05546 && 1.82199 & \textbf{1.43724} & 1.75610 && 1.22453 & 1.24810 & \textbf{1.21994} \\
+		0.4	& 2.61641 & \textbf{1.63390} & 2.33662 && 1.54989 & \textbf{1.16887} & 1.46534 && 1.14507 & 1.19631 & \textbf{1.13979} \\
+		0.5	& 2.08260 & \textbf{1.13827} & 1.77494 && 1.35101 & \textbf{1.04978} & 1.25567 && 1.09274 & 1.17069 & \textbf{1.08661} \\
+		0.6 & 1.65897 & \textbf{1.02027} & 1.36093 && 1.20040 & \textbf{1.03720} & 1.11964 && 1.06255 & 1.15766 & \textbf{1.05701} \\
+		0.7	& 1.32002 & \textbf{1.01350} & 1.11348 && 1.09659 & \textbf{1.03556} & 1.04569 && 1.04546 & 1.14416 & \textbf{1.04150} \\
+		0.8	& 1.10725 & \textbf{1.01384} & 1.02188 && 1.03577 & 1.03439 & \textbf{1.01696} && 1.03711 & 1.12951 & \textbf{1.03565} \\
+		0.9	& 1.02134 & 1.01315 & \textbf{1.00646} && 1.01364 & 1.03285 & \textbf{1.01029} && 1.03434 & 1.11631 & \textbf{1.03416} \\
+		1.0 & \textbf{1.00480} & 1.01302 & \textbf{1.00480} && \textbf{1.00919} & 1.03261 & \textbf{1.00919} && \textbf{1.03393} & 1.10807 & \textbf{1.03393} \\
+		\bottomrule
 	\end{tabular}	
-	\label{table:n1000}
+	\label{table:n=100}
 \end{table}
+\end{comment}
 

### 2018-06-05 PAPER/main.tex
more bullet points to comparison/analysis section

@@
 	\item MFFD$^+$ can also find solutions within 1\% of $t$ for $\delta = 0.8$ onwards for all strip widths in both set sizes.
-	\item Number of items per strip smaller, problem is harder, falkenauer 1996, martello and toth 1990b
-	\item 
+	\item Number of items per strip smaller, problem is harder, falkenauer 1996, martello and toth 1990b items per strip roughly 2
+	\item all instances run in less than 160ms
+	\item For each instance where opt $>1$, two cases: either $t$ is incorrect, and there does not exist a solution with $k = t$ strips, and the solution found is actually an optimal solution, or $t$ is correct, and the heuristic cannot find a solution with $t$ strips, not an optimal solution.
+	\item since this is a relatively new problem, no problem instances solved to optimality, and so we have no way of knowing if in fact the heuristics are finding optimal solutions.
+Only able to compare with the theoretical minimum.
 \end{itemize}

### 2018-06-07 SCSPP/HEURISTICS/base.cpp
removed unecessary comments

@@ -45,20 +45,15 @@ void CreateInstance(int tau, int numScores, int numItem, int minWidth, int maxWi
 
     sort(allScores.begin(), allScores.end());
 
-    //int ones = 0;
     for (i = 0; i < allScores.size() - 1; ++i) {
         for (j = i + 1; j < allScores.size(); ++j) {
             if (allScores[i] + allScores[j] >= tau) {
                 adjMatrix[i][j] = 1;
                 adjMatrix[j][i] = 1;
-                //ones += 2;
             }
         }
 
     }
-
-    //ones -= numScores;
-    //cout << tau << ": " << ones << endl;
 
     for (i = 0; i < numScores; ++i) {
         randOrder.push_back(i);
@@ -92,12 +87,10 @@ void CreateInstance(int tau, int numScores, int numItem, int minWidth, int maxWi
     }
 
 
-    //cout << "Box#" << setw(10) << "Mates" << setw(10) << "Scores" << setw(10) << "Width\n";
     for(i = 0; i < numScores; ++i){
         if(checkItem[i] == 1){
             continue;
         }
-        //cout << count << setw(10)  << i << "-" << mates[i] << setw(10) << allScores[i] << "-" << allScores[mates[i]] << setw(8) << itemWidths[i][mates[i]] << endl;
         totalItemWidth += itemWidths[i][partners[i]];
         checkItem[i] = 1;
         checkItem[partners[i]] = 1;

### 2018-06-07 SCSPP/HEURISTICS/main.cpp

@@ -9,6 +9,7 @@ mainexact.cpp
 #include <ctime>
 #include <chrono>
 #include <iomanip>
+#include <cmath>
 using namespace std;
 
 #include "base.h"
@@ -28,9 +29,7 @@ struct Timer{
         totalTime = endTime - startTime;
 
         float totalTimems = totalTime.count() * 1000.0f;
-        //cout << "\nCPU Time: " << totalTimems << "ms (" << totalTime.count() << "s)" << endl;
-        cout << totalTime.count() << endl;
-        //cout << totalTimems << endl;
+        cout << "\nCPU Time: " << totalTimems << "ms (" << totalTime.count() << "s)" << endl;
     }
 };
 
@@ -193,7 +192,6 @@ int main(int argc, char **argv){
     vector<vector<vector<int> > > population;
     vector<vector<int> > populationSum;
     vector<int> delta = { 145, 109, 97, 87, 79, 72, 65, 57, 47, 34, 0 };
-    //double Delta = 0.0;
 
     Timer timer;
 

### 2018-06-07 PAPER/main.tex
added n = |I|

@@
 A prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \cite{goulimis2004}.
-Here, a set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right.
+Here, a set $\mathcal{I}$ of rectangular items (where $|\mathcal{I}| = n$) of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right.
 Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places.
@@
 	Let $\mathcal{I}$ be a set of rectangular items of height $H$ with varying widths $w_i \in \mathbb{Z}^+$ and score widths $a_i, b_i \in \mathbb{Z}^+$ for each item $i \in \mathcal{I}$.
-Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consist of finding the minimum number of strips of height $H$ and width $W$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$, and that no strip is overfilled.
+Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips of height $H$ and width $W$ required to pack all $n$ items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$, and that no strip is overfilled.
 \end{definition}
@@
 
-An optimal solution $\mathcal{S}$ for the SCSPP is a solution that consists of the fewest number of strips $k$ needed to feasibly contain the $|\mathcal{I}|$ items in the given problem instance.
+An optimal solution $\mathcal{S}$ for the SCSPP is a solution that consists of the fewest number of strips $k$ needed to feasibly contain the $n$ items in the given problem instance.
 A simple lower bound for $k$ is the theoretical minimum
@@
 \label{eqn:lowerbound}
-t = \ceil*{\frac{\sum_{i=1}^{|\mathcal{I}|}w_i}{W}},
+t = \ceil*{\frac{\sum_{i=1}^{n}w_i}{W}},
 \end{equation}
-which can be computed in linear time (\citealp{martello1990b}).
+which can be computed in $O(n)$ time (\citealp{martello1990b}).
 Perhaps the simplest and most well-known heuristic for packing problems is \textsc{First-Fit} (FF), a greedy online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
@@
 More recently, \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight.
-Due to the initial sorting of the items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$, where $n = |\mathcal{I}|$ is the input size.
+Due to the initial sorting of the items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$.
 
@@
 Furthermore, the theoretical minimum $t$ (Equation (\ref{eqn:lowerbound})) has the potential to be less accurate for the SCSPP, as the minimum scoring distance $\tau$ is not considered.
-For example, if the minimum scoring distance is greater than twice the largest score width, then it is clear that $|\mathcal{I}|$ strips will be required, regardless of the items' widths.
+For example, if the minimum scoring distance is greater than twice the largest score width, then it is clear that $n$ strips will be required, regardless of the items' widths.
 % Time complexity for FFD also inaccurate
@@
 \section{Comparison}
-For our experiments, we generated 1000 problem instances for three different sizes of $\mathcal{I}$, containing 100, 500, and 1000 items.
-For each problem instance, the items have varying widths $w_i$ between 150 and 1000, and score widths $a_i, b_i$ between 1 and 70, all selected randomly from a uniform distribution.
-Three strip widths $W$ were used, 5000, 2500, and 1250.
-As the width of the strips decrease, the average number of items per strip also decreases, making the problem more difficult.
+For our experiments, we generated 1000 problem instances for two different sizes of $\mathcal{I}$ containing 500 and 1000 items.
+For each problem instance the items have varying widths $w_i$ between 150 and 1000 and score widths $a_i, b_i$ between 1 and 70 to ensure that each item has exactly two score lines, all selected randomly from a uniform distribution.
+Strips of widths $W = 5000$, 2500 and 1250 were used to alter the number of items per strip.
 Both the items and the strips have equal height of $H = 1$.
@@
 Values of $\delta$ from 0.0 to 1.0 were created by changing the value of the minimum scoring distance $\tau$.
-Clearly, when $\delta = 0.0$, there are no score widths that can be packed together feasibly, and so $|\mathcal{I}|$ strips will be required (one for each item), whereas if $\delta = 1.0$ then all pairs of score widths meet the constraint, and the problem is analogous to the BPP.
+Clearly, when $\delta = 0.0$, there are no score widths that can be packed together feasibly, and so $n$ strips will be required (one for each item), whereas if $\delta = 1.0$ all pairs of score widths meet the constraint, and the problem is analogous to the BPP.
+(As the width of the strips decrease, the average number of items per strip also decreases, making the problem more difficult.)
 
 The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
-The tables below show the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the theoretical minimum $t$, which was calculated using Equation \ref{eqn:lowerbound}.
+We calculated the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the theoretical minimum $t$, which was calculated using Equation \ref{eqn:lowerbound}.
+All individual trials were executed in under 160ms.
 
-Firstly, it is apparent that the heuristics perform comparitively in the same manner regardless of the input size.
-
-\begin{itemize}
-	\item \textbf{PairSmallest:}
-	\item Best average optimality over all three set sizes for $W = 5000$ and $W = 2500$ for $\delta = 0.1 - 0.6$, in some cases up to $\delta = 0.8$.
-	\item However, when $W = 1250$, PS only has best average optimality for $\delta = 0.1$ and $\delta = 0.2$. 
-	\item PS is able to obtain solution that are on average within 10\% of the lower bound for the optimal solution for $\delta = 0.6$ onwards when $W=5000$ and $W = 2500$.
-	\item When $W = 1250$, PS only obtains solutions within 10\% of the lowerbound for $\delta = 0.8$ onwards with set sizes 500 and 1000.
-For $|\mathcal{I}| = 100$, PS is not able to (on average) obtain solutions within 10\% of the lower bound for any value of $\delta$.
-	\item Clear pattern across all three set sizes, PS performs better when the strip widths are wider, however PS is still the best of the three heuristics for smaller strip widths and harder problems, i.e.
-when $\delta$ is smaller.
-	\item PS never obtains avg solution within 1\% of lower bound.
-\end{itemize}
+Tables \ref{table:n=500} and \ref{table:n=1000} compare the results obtained from the three heuristics using different values of $\delta$ and $W$ for $n = 500$ and 1000 respectively.
+Figures in bold indicate the best average optimality for the given combination of $\delta$ and $W$.
+Initially, we can see that the optimality ratios tend toward 1 as $\delta$ increases, as the proportion of pairs of score widths that can be packed.
 
@@
 	\item In contrast, MFFD and MFFD$^+$ can produce solution within 10\% of $t$ when $W = 1250$ for $\delta = 0.5$ onwards for $n = 500$, and $\delta = 0.4$ for $n = 1000$.
-	\item MFFD$^+$ can also find solutions within 1\% of $t$ for $\delta = 0.8$ onwards for all strip widths in both set sizes.
-	\item Number of items per strip smaller, problem is harder, falkenauer 1996, martello and toth 1990b items per strip roughly 2
+	\item MFFD$^+$ can also find solutions within 1\% of $t$ for $\delta = 0.8$ onwards for all strip widths when $n = 1000$, and the two larger strip widths when $n = 500$.
+	\item Number of items per strip smaller, problem is harder, falkenauer 1996, martello and toth 1990b items per strip roughly 2, triplets hardest problems
 	\item all instances run in less than 160ms
@@
 Only able to compare with the theoretical minimum.
+	\item $W =5000$ Table 2, $\delta = 0.7$ PS has best optimality, however looking at the number of instance solved to $t$, PS has 0, whereas MFFD$^+$ has 152.
+Therefore there are at least 152 instances where the optimal number of strips = $t$ that PS is not able to solve to optimality.
+	\item We see that PS produces solutions using fewer strips on average of the three algoritihms for a larger range of $\delta$ when the strips are wider, and MFFD$^+$ produces solutions using fewer strips for a wider range of $\delta$ when the strips are shorter.
+	\item We can see that the range of values of $\delta$ in which PS produces solutions using the minimum number of strips on average of the three algorithms reduces as the strip width decreases
+	\item PS never performs best for 0.8 onwards
 \end{itemize}
@@
 	\ra{1.3}
-	\caption{Average optimality ratios for $|\mathcal{I}| = 500$.}
+	\caption{Average optimality ratios for $n = 500$. The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.4746, 4.3103, and 2.1645 respectively.}
 	\begin{tabular}{@{}c@{\hspace{25pt}}c@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}c@{}}\toprule
@@
 	\ra{1.3}
-	\caption{Average optimality ratios for $|\mathcal{I}| = 1000$.}
+	\caption{Average optimality ratios for $n = 1000$. The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.6207, 4.329 and 2.1692 respectively.}
 	\begin{tabular}{@{}c@{\hspace{25pt}}c@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}c@{}}\toprule

### 2018-06-08 PAPER/main.tex
condensed points for comparison, added reference

@@
 The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
-We calculated the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution obtained by the heuristic to the theoretical minimum $t$, which was calculated using Equation \ref{eqn:lowerbound}.
+The source code for these procedures used for our computational experiments is available at \cite{hawa2018}.
+We calculated the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution generated by the heuristic to the theoretical minimum $t$, which was calculated using Equation \ref{eqn:lowerbound}.
 All individual trials were executed in under 160ms.
@@
 Initially, we can see that the optimality ratios tend toward 1 as $\delta$ increases, as the proportion of pairs of score widths that can be packed.
+
+\begin{enumerate}
+	\item Opt ratios tend to 1 as $\delta \to 1$, as the problem instances become easier to solve, more feasible alignments of pairs of items, more items per strip, reducing the need for more strips, closer to BPP.
+	\item $\delta = 0.0$ $n$ strips required, hence all ratios equal.
+	\item $\delta = 1.0$,  MFFD and MFFD$^+$ obtain identical opts, since (described above) instance is equivalent to original BPP, $\tau = 0$, so MFFD and MFFD$^+$ perform in the same fashion as original FFD.
+	\item Pattern, PS best for wider range of $\delta$ when $W$ high, and smaller range (only 0.1-0.2) when $W = 1250$.
+	\item Conversely, MFFD$^+$ best when $W$ small for wider range of $\delta$.
+	\item Note that although PS best for 0.1-0.2, difference is negligible, e.g. $n = 500$, $\delta = 0.2$, difference in opt is 0.00829, translates to less than 2 strips difference on average.
+	\item MFFD and MFFD$^+$ able to obtain opts $\leq 1\%$ of $t$, PS is not.
+	\item PS never best $\delta \geq 0.8$.
+	\item $n = 1000$, $W = 5000$, $\delta = 0.7$, PS is best opt, however PS does not produce a single solution containing $t$ strips, whereas there are 152 instances in which MFFD$^+$ produces solutions containing $t$ strips, i.e.
+there are at least 152 instances out of the 1000 where $k = t$, and PS cannot obtain any.
+Therefore, MFFD$^+$ solutions must vary significantly (i.e.
+some solns that are much worse than optimal), as PS is best opt.
+	\item Significant difference in opt, $n = 1000$, $W = 1250$, $\delta = 0.6$, difference between MFFD$^+$ and PS opts is 0.10912 (MFFD$^+$ better), which amounts to an average difference of over 50 strips in solns produced.
+	\item Noticable drop in opts between $\delta = 0.4$ and $\delta = 0.5$ when $W$ high, as capacity not main concern, more items can now be placed next to one another, so number of strips reduces dramatically, however when $W = 1250$ there is still a capacity issue, regardless of the increased proportion of possible pairings.
+	\item anomaly MFFD $n = 1000$, $W = 1250$, $\delta = 0.3$
+	\item harder problems, \cite{falkenauer1996}, triplets, fewer items per strip.
+	\item cases when opt $\neq 1$: $t$ incorrect, solution produced is not optimal, or both.
+	\item less than 10\% past $\delta = 0.8$
+\end{enumerate}
 
@@
 	\item PS never performs best for 0.8 onwards
+	\item significant drop between $\delta = 0.4$ and 0.5 for all heuristics and both set sizes except when $W = 1250$
 \end{itemize}

### 2018-06-09 PAPER/main.tex
added to Comparison

@@
 The source code for these procedures used for our computational experiments is available at \cite{hawa2018}.
-We calculated the average optimality of the heuristics for each value of $\delta$ from 1000 instances, where the optimality of each instance is the ratio of the number of strips in the final solution generated by the heuristic to the theoretical minimum $t$, which was calculated using Equation \ref{eqn:lowerbound}.
+We calculated the average optimality of each heuristic for every combination of $n$, $\delta$, and $W$ from 1000 instances, where the optimality $r$ of each instance is
+\begin{equation}
+	r = \frac{|\mathcal{S}|}{t},
+\end{equation}
+i.e.
+the ratio of the number of strips in the final solution $\mathcal{S}$ generated by the heuristic to the theoretical minimum $t$, which was calculated using Equation \ref{eqn:lowerbound}.
 All individual trials were executed in under 160ms.
@@
 Tables \ref{table:n=500} and \ref{table:n=1000} compare the results obtained from the three heuristics using different values of $\delta$ and $W$ for $n = 500$ and 1000 respectively.
-Figures in bold indicate the best average optimality for the given combination of $\delta$ and $W$.
-Initially, we can see that the optimality ratios tend toward 1 as $\delta$ increases, as the proportion of pairs of score widths that can be packed.
+Figures in bold indicate the best average optimality for the given combination of parameters.
+Initially, we can see that $r$ tends toward 1 as $\delta$ increases, since the proportion of score widths meet the vicinal sum constraint increases and more items can be packed onto one strip, reducing the number of strips required.
+Note that when $\delta = 1.0$ MFFD and MFFD$^+$ have identical optimality ratios, as the instances are equivalent to the original BPP ($\tau = 0$) and so they operate in the same fashion as the original FFD heuristic.
+
+Looking at results for both $n = 500$ and $n = 1000$, there is a clear pattern with respect to $r$ across all widths and proportion levels.
+PS has the best optimality ratio for a wider range of $\delta$ when the strips are wider, and a much smaller range when the strip width decreases.
+Conversely, MFFD$^+$ obtains better optimality ratios for a wider range of $\delta$ when $W = 1250$.
+Although PS does have the best optimality of the three heuristics for $\delta = 0.1$ and 0.2 using the smallest strip width, we can see that it only marginally superior to MFFD$^+$.
+For example, take $\delta = 0.2$ in Table \ref{table:n=500} for $W = 1250$.
+The difference between $r$ for PS and MFFD$^+$ is 0.00829, which translates to less than 2 strips difference between the average number of strips generated by each heuristic.
+
+One interesting feature is the reduction of $r$ between $\delta = 0.4$ and $\delta = 0.5$, which is much more significant for $W = 5000$ as opposed to $W = 1250$.
+The reduction occurs due to an increase in the number of feasible alignments of the items, as every score width is able to be paired with $n-1$ other score widths when $\delta = 0.5$.
+Thus, when $W = 5000$, more items can be packed onto a strip feasibly, resulting in fewer strips in the final solution.
+However, the difference in $r$ is less noticeable for $W = 1250$, as regardless of the increased proportion in possible pairings, the capacity of the strips is much smaller, preventing the collection of items from multiple strips onto one.
 
 \begin{enumerate}
-	\item Opt ratios tend to 1 as $\delta \to 1$, as the problem instances become easier to solve, more feasible alignments of pairs of items, more items per strip, reducing the need for more strips, closer to BPP.
-	\item $\delta = 0.0$ $n$ strips required, hence all ratios equal.
-	\item $\delta = 1.0$,  MFFD and MFFD$^+$ obtain identical opts, since (described above) instance is equivalent to original BPP, $\tau = 0$, so MFFD and MFFD$^+$ perform in the same fashion as original FFD.
-	\item Pattern, PS best for wider range of $\delta$ when $W$ high, and smaller range (only 0.1-0.2) when $W = 1250$.
-	\item Conversely, MFFD$^+$ best when $W$ small for wider range of $\delta$.
-	\item Note that although PS best for 0.1-0.2, difference is negligible, e.g. $n = 500$, $\delta = 0.2$, difference in opt is 0.00829, translates to less than 2 strips difference on average.
 	\item MFFD and MFFD$^+$ able to obtain opts $\leq 1\%$ of $t$, PS is not.
@@
 \end{enumerate}
-
-\begin{itemize}
-	\item optimality converge toward 1 as $\delta$ increases, i.e. as the problem instances become less difficult.
-	\item When $\delta = 1.0$. MFFD and MFFD$^+$ perform identically, as the problems are equivalent to the original BPP, and so they behave like the original FFD heuristic.
-	\item When $\delta = 0.0$, all optimalities are equal, as each item requires its own strip, and so $|\mathcal{I}|$ strips are needed for all 1000 instances.
-	\item Values in bold represent the best avg optimality of the three heuristics for the given level of $\delta$. 
-	\item Clear pattern across both set sizes, PS performs the best out of the three for $\delta = 0.1$ to 0.7 when $W = 5000$, and for $\delta = 0.1$ to 0.6 when $W = 2500$.
-	\item However, when $W = 1250$, PS is only superior when $\delta = 0.1$ and 0.2. 
-	\item On further inspection, we can see that the difference between the average optimalities for PS and MFFD$^+$ is negligible.
-	\item Using Table 1 as an example, when $\delta = 0.2$, the solutions generated by PS are on average within 31.781\% of $t$, and for MFFD$^+$ within 32.61\%, a difference of 0.829\%. 
-	\item In practical terms, PS produces solutions using 303.95 strips on average, where $t = 230.648$. MFFD$^+$ produces solutions using 305.862 strips, a difference of less than two strips. 
-	\item Another trend is that PS produces average solutions within 10\% of $t$ for $\delta = 0.5$ onwards when $W = 5000$ and 2500, however when $W = 1250$, PS only produces solutions within 10\% of $t$ for $\delta = 0.8$ onwards.
-	\item In contrast, MFFD and MFFD$^+$ can produce solution within 10\% of $t$ when $W = 1250$ for $\delta = 0.5$ onwards for $n = 500$, and $\delta = 0.4$ for $n = 1000$.
-	\item MFFD$^+$ can also find solutions within 1\% of $t$ for $\delta = 0.8$ onwards for all strip widths when $n = 1000$, and the two larger strip widths when $n = 500$.
-	\item Number of items per strip smaller, problem is harder, falkenauer 1996, martello and toth 1990b items per strip roughly 2, triplets hardest problems
-	\item all instances run in less than 160ms
-	\item For each instance where opt $>1$, two cases: either $t$ is incorrect, and there does not exist a solution with $k = t$ strips, and the solution found is actually an optimal solution, or $t$ is correct, and the heuristic cannot find a solution with $t$ strips, not an optimal solution.
-	\item since this is a relatively new problem, no problem instances solved to optimality, and so we have no way of knowing if in fact the heuristics are finding optimal solutions.
-Only able to compare with the theoretical minimum.
-	\item $W =5000$ Table 2, $\delta = 0.7$ PS has best optimality, however looking at the number of instance solved to $t$, PS has 0, whereas MFFD$^+$ has 152.
-Therefore there are at least 152 instances where the optimal number of strips = $t$ that PS is not able to solve to optimality.
-	\item We see that PS produces solutions using fewer strips on average of the three algoritihms for a larger range of $\delta$ when the strips are wider, and MFFD$^+$ produces solutions using fewer strips for a wider range of $\delta$ when the strips are shorter.
-	\item We can see that the range of values of $\delta$ in which PS produces solutions using the minimum number of strips on average of the three algorithms reduces as the strip width decreases
-	\item PS never performs best for 0.8 onwards
-	\item significant drop between $\delta = 0.4$ and 0.5 for all heuristics and both set sizes except when $W = 1250$
-\end{itemize}
 
@@
 
+\begin{comment}
+	\begin{enumerate}
+	\item Opt ratios tend to 1 as $\delta \to 1$, as the problem instances become easier to solve, more feasible alignments of pairs of items, more items per strip, reducing the need for more strips, closer to BPP.
+	\item $\delta = 0.0$ $n$ strips required, hence all ratios equal.
+	\item $\delta = 1.0$,  MFFD and MFFD$^+$ obtain identical opts, since (described above) instance is equivalent to original BPP, $\tau = 0$, so MFFD and MFFD$^+$ perform in the same fashion as original FFD.
+	\item Pattern, PS best for wider range of $\delta$ when $W$ high, and smaller range (only 0.1-0.2) when $W = 1250$.
+	\item Conversely, MFFD$^+$ best when $W$ small for wider range of $\delta$.
+	\item Note that although PS best for 0.1-0.2, difference is negligible, e.g. $n = 500$, $\delta = 0.2$, difference in opt is 0.00829, translates to less than 2 strips difference on average.
+	\item MFFD and MFFD$^+$ able to obtain opts $\leq 1\%$ of $t$, PS is not.
+	\item PS never best $\delta \geq 0.8$.
+	\item $n = 1000$, $W = 5000$, $\delta = 0.7$, PS is best opt, however PS does not produce a single solution containing $t$ strips, whereas there are 152 instances in which MFFD$^+$ produces solutions containing $t$ strips, i.e.
+there are at least 152 instances out of the 1000 where $k = t$, and PS cannot obtain any.
+Therefore, MFFD$^+$ solutions must vary significantly (i.e.
+some solns that are much worse than optimal), as PS is best opt.
+	\item Significant difference in opt, $n = 1000$, $W = 1250$, $\delta = 0.6$, difference between MFFD$^+$ and PS opts is 0.10912 (MFFD$^+$ better), which amounts to an average difference of over 50 strips in solns produced.
+	\item Noticable drop in opts between $\delta = 0.4$ and $\delta = 0.5$ when $W$ high, as capacity not main concern, more items can now be placed next to one another, so number of strips reduces dramatically, however when $W = 1250$ there is still a capacity issue, regardless of the increased proportion of possible pairings.
+	\item anomaly MFFD $n = 1000$, $W = 1250$, $\delta = 0.3$
+	\item harder problems, \cite{falkenauer1996}, triplets, fewer items per strip.
+	\item cases when opt $\neq 1$: $t$ incorrect, solution produced is not optimal, or both.
+	\item less than 10\% past $\delta = 0.8$
+	\end{enumerate}
+\end{comment}
+
 \bibliographystyle{dcu}

### 2018-06-11 PAPER/main.tex
added pseudocode for AHC

@@
 
+\begin{algorithm}[h]
+\caption{\textsc{Alternating Hamiltonian Construction} (AHC) algorithm}
+\label{alg:ahca}
+\begin{algorithmic}[1]
+	\State Create the graph $G = (V, B \cup R)$ from instance $\mathcal{M}$
+	\State Execute \textsc{Maximum Cardinality Matching}
+	\If{$|R'| < n + 1$}
+		\State Infeasible, end
+	\EndIf
+	\State Produce the subgraph $G' = (V, B \cup R')$
+	\If{$q = 1$}
+		\State Remove dominating vertices and incident edges
+		\Return $G'$
+	\Else
+		\State Execute \textsc{Bridge Recognition}
+		\If{$q = 1$}
+			\State Remove dominating vertices and incident edges
+			\Return $G'$
+		\Else
+			\State Infeasible, end	
+		\EndIf	
+	\EndIf
+\end{algorithmic}	
+\end{algorithm}
+
 \begin{theorem}
@@
 
+Although using the average optmality from 1000 instances provides a useful overview of the efficiency of a heuristic, there are other characteristics that we can consider.
+Take, for example, the results obtained with parameters $\delta = 0.7$ and $W = 5000$ in Table \ref{table:n=1000}.
+Clearly PS obtains solutions with the fewest strips on average, however, we noted that out of the 1000 instances, PS did not produce a single solution containing $t$ strips.
+On the other hand, there were 152 instances in which MFFD$^+$ was able to generate a solution $S$ such that $|\mathcal{S}| = t$, thus implying that there are at least 152 solutions that can be solved to optimality.
+Despite this, MFFD$^+$ has a higher average optimality than PS, suggesting that the variance in the number of strips required is higher.
+
 \begin{enumerate}
@@
 	\item PS never best $\delta \geq 0.8$.
-	\item $n = 1000$, $W = 5000$, $\delta = 0.7$, PS is best opt, however PS does not produce a single solution containing $t$ strips, whereas there are 152 instances in which MFFD$^+$ produces solutions containing $t$ strips, i.e.
-there are at least 152 instances out of the 1000 where $k = t$, and PS cannot obtain any.
-Therefore, MFFD$^+$ solutions must vary significantly (i.e.
-some solns that are much worse than optimal), as PS is best opt.
 	\item Significant difference in opt, $n = 1000$, $W = 1250$, $\delta = 0.6$, difference between MFFD$^+$ and PS opts is 0.10912 (MFFD$^+$ better), which amounts to an average difference of over 50 strips in solns produced.
-	\item Noticable drop in opts between $\delta = 0.4$ and $\delta = 0.5$ when $W$ high, as capacity not main concern, more items can now be placed next to one another, so number of strips reduces dramatically, however when $W = 1250$ there is still a capacity issue, regardless of the increased proportion of possible pairings.
 	\item anomaly MFFD $n = 1000$, $W = 1250$, $\delta = 0.3$
-	\item harder problems, \cite{falkenauer1996}, triplets, fewer items per strip.
+	\item harder problems, \cite{falkenauer1996}, triplets, fewer items per strip, further from 1 when shorter strips.
 	\item cases when opt $\neq 1$: $t$ incorrect, solution produced is not optimal, or both.

### 2018-06-12 PAPER/main.tex
changed figure captions, added paragraph before sub-problem definition

@@
 Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively.
-
 \begin{figure}[H]	
 	\centering
-	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
+	\includestandalone[width=0.9\textwidth]{figures/itemsknife}
 	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation $(a_i, b_i)$, and a feasible alignment of two items that can be scored simultaneously.}	
@@
 
-Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
+Clearly, for two items to be placed alongside one another feasibly, the distance between the two score lines from adjacent items must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
 Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
-The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.
+Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.
 
@@
 	\end{subfigure}
-	\caption{Example of the strip-packing problem, where the sum of each pair of adjacent score widths is greater than or equal to $\tau = 7$. From instance $\mathcal{M}$ above.}
+	\caption{Example of the strip-packing problem modelled using the instance $\mathcal{M}$ above.
+The vicinal sum constraint has been met between all items in the alignment, which corresponds to a solution $\mathcal{T}$.}
 	\label{fig:items/aligned}
@@
 \begin{definition}
-	Let $\mathcal{I}$ be a set of rectangular items of height $H$ with varying widths $w_i \in \mathbb{Z}^+$ and score widths $a_i, b_i \in \mathbb{Z}^+$ for each item $i \in \mathcal{I}$.
-Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips of height $H$ and width $W$ required to pack all $n$ items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$, and that no strip is overfilled.
+	Let $\mathcal{I}$ be a set of $n$ rectangular items of height $H$ with varying widths $w_i \in \mathbb{Z}^+$ and score widths $a_i, b_i \in \mathbb{Z}^+$ for each item $i \in \mathcal{I}$.
+Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips of height $H$ and width $W$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$, and that no strip is overfilled.
 \end{definition}
@@
 Note that in the special case of $\tau = 0$, the SCSPP is equivalent to the classical one-dimensional bin-packing problem (BPP).
-It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}), and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.
-Instead, heuristics can be used to find near-optimal solutions in a shorter amount of time.
+Due to the vicinal sum constraint, the SCSPP not only allocates the items to a strip, but must also determine how to pack the items on each strip.
+This involves deciding the order in which the items are packed from left to right, and whether each item should be placed in a regular or rotated orientation.
+Thus, we define the following sub-problem associated with the SCSPP.
 
@@
 
-The remainder of this article is structured as follows: In Section 2, we will detail an exact polynomial-time algorithm for the COP, if a solution exists.
+The remainder of this article is structured as follows: In Section 2, we will detail an exact polynomial-time algorithm for the COP, and thus the SCPSP.
 Section 3 then describes three heuristics that can be used to find feasible solutions to the SCSPP and the associated advantages and disadvantages.
@@
 	\EndIf
-	\State Produce the subgraph $G' = (V, B \cup R')$
+	\State Produce the subgraph $G' = (V, B \cup R')$ consisting of $q$ cycles
 	\If{$q = 1$}
@@
 
+\section{Further Work}
+\begin{itemize}
+	\item \cite{miller1960}
+	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution.
+	\item include item width in ahc, so add values to the blue edges of the graph, weighted edges, red edges have value = 0.
+	\item Then the problem would be: find the minimum number of alternating cycles on $G$ such that the length of the cycle is less than or equal to some value $W$ (which is the strip width).
+The length of the cycle would be the sum of all the weighted edges, so the sum of all the blue edges, since red = 0.
+	\item then could break and form edges to create new components of different sizes if some are too large, or join together if some are small, thus decreasing the number of cycles
+	\item or if possible, find a single alt Ham cycle, and break up into as few smaller cycles as possible such that the length of each cycle is less than or equal to $W$
+	\item another way, create as few feasible subsets $\mathcal{I}' \subseteq \mathcal{I}$ such that the total width of the items in each subset $\mathcal{I}$ is less than $W$, i.e.
+perform usual FFD alg, ignore score widths
+	\item then perform ahc on each set, try to find feasible solution.
+	\item if sets dont have feasible solution, try swapping items between sets
+	\item initial tests, Becker theorem 6 2015 paper 
+\end{itemize}
+
 \begin{comment}
@@
 \end{comment}
-\begin{comment}
-\section{Further Work}
-\begin{itemize}
-	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution.
-	\item include item width in ahc, so add values to the blue edges of the graph, weighted edges, red edges have value = 0.
-	\item Then the problem would be: find the minimum number of alternating cycles on $G$ such that the length of the cycle is less than or equal to some value $W$ (which is the strip width).
-The length of the cycle would be the sum of all the weighted edges, so the sum of all the blue edges, since red = 0.
-	\item then could break and form edges to create new components of different sizes if some are too large, or join together if some are small, thus decreasing the number of cycles
-	\item or if possible, find a single alt Ham cycle, and break up into as few smaller cycles as possible such that the length of each cycle is less than or equal to $W$
-	\item another way, create as few feasible subsets $\mathcal{I}' \subseteq \mathcal{I}$ such that the total width of the items in each subset $\mathcal{I}$ is less than $W$, i.e.
-perform usual FFD alg, ignore score widths
-	\item then perform ahc on each set, try to find feasible solution.
-	\item if sets dont have feasible solution, try swapping items between sets
-	\item initial tests, Becker theorem 6 2015 paper 
-\end{itemize}
-\end{comment}
 

### 2018-06-14 PAPER/main.tex
added explanation alt ham np-hard

@@
 \begin{abstract}
+
 \end{abstract}
@@
 It can be seen that $B$ is a perfect matching in $G$, with $|B| = n+1$.
-
 Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose sum equal or exceed $\tau$, provided they are not partners.
-This corresponds to the vicinal sum constraint in Defintion \ref{defn:cop}.
+It can be seen that the edges in $R$ represent all possible orderings of values from different pairs in an instance $\mathcal{M}$ that fulfil the vicinal sum constraint in Definition \ref{defn:cop}.
 Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$ and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$.
-Figure \ref{fig:partners/threshold} illustrates and example construction of $G$.
-% Equation $v_i + v_j \geq \tau$ provided $p(v_i) \neq v_j$, i.e. not partners
-% Values are assigned from $\mathcal{M}$ in non-decreasing order, i.e. value assoc with v_1 \leq value assoc with v_2 etc..
-% "This corresponds to the vsc in Defn 1" - values that can be aligned alongside one another that are not part of the same unordered pair in M, hence why they cannot be partners on the graph G, must be from different unordered pairs.
-
+Figure \ref{fig:partners/threshold} illustrates an example construction of $G$.
 \begin{figure}	
@@
 Thus, by removing the dominating vertices and any incident edges, the remaining alternating Hamiltonian path gives the order in which the elements should be placed to produce a feasible solution $\mathcal{T}$, if indeed one exists.
-
 Also, note that every edge in $B$ must be present in the alternating Hamiltonian cycle.
 Consequently, the task can be seen as finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.
+
+The problem of finding an alternating Hamiltonian cycle on general graphs is NP-hard as it generalises the classical Hamiltonian cycle problem, as stated in a proposition by \cite{haggkvist1977}.
+However, the special structure of graphs derived from instances of the COP allows them to be solved using the following method.
 
@@
 \begin{comment}
+\begin{abstract}
+\begin{itemize}
+\item ``first, alg for COP and show how used for single strip feasible arrangement''
+\item ``then go on to examine how alg can combine to tackle multi-strip version of problem - closely related to 1DBPP''
+\item discuss problems that arise
+\item variant/generalisation of the 1DBPP ``in which both the ordering and orientation of items in a container influences the validity and quality of a solution''
+\item ``problem that requires the cutting and socring of rectangular pieces of cardboard in the construction of boxes''
+\end{itemize}	
+\end{abstract}
+\end{comment}
+
+\begin{comment}
 \begin{itemize}

### 2018-06-25 PAPER/main.tex
put heuristics into paragraphs

@@
 \end{abstract}
+
+\begin{comment}
+\begin{abstract}
+	\begin{itemize}
+	\item ``first, alg for COP and show how used for single strip feasible arrangement''
+	\item ``then go on to examine how alg can combine to tackle multi-strip version of problem - closely related to 1DBPP''
+	\item discuss problems that arise
+	\item variant/generalisation of the 1DBPP ``in which both the ordering and orientation of items in a container influences the validity and quality of a solution''
+	\item ``problem that requires the cutting and socring of rectangular pieces of cardboard in the construction of boxes''
+	\end{itemize}	
+\end{abstract}
+\end{comment}
 
@@
 
-\subsection{Modified First-Fit Decreasing Heuristic (MFFD)}
-\label{sec:mffd}
-The \textsc{Modified First-Fit Decreasing} (MFFD) heuristic performs in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip.
+The first heuristic we developed is the \textsc{Modified First-Fit Decreasing} (MFFD) heuristic which performs in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip.
 If an item is able to be packed onto a strip without exceeding the strip's capacity, MFFD then checks to see if the vicinal sum constraint is met between the right-most score on the strip and one of the score widths on the current item.
@@
 
-\subsection{Pair-Smallest Heuristic (PS)}
-\label{sec:ps}
-
-The \textsc{Pair-Smallest} (PS) heuristic is an extension of a procedure defined by \cite{lewis2011}.
+The next heuristic is the \textsc{Pair-Smallest} (PS) heuristic, an extension of a procedure defined by \cite{lewis2011}.
 Unlike MFFD, which packs each item in turn, PS focusses on packing one strip at a time, only starting a new strip once the current strip is unable to accommodate any more items feasibly.
@@
 Note that PS prioritises the vicinal sum constraint over the item widths, choosing to fulfil the constraint first before considering whether the item can be accommodated.
-If there are multiple items with equal score widths, break ties by choosing the item whose second score width is the largest.
-% Break ties by choosing item whose second score width is larger.
+%If there are multiple items with equal score widths, break ties by choosing the item whose second score width is the largest.
 % If item with smallest feasible score width does not fit onto the strip, choose item with next smallest score width and repeat.
 
-\subsection{Modified First-Fit Decreasing with AHC (MFFD$^+$)}
-\label{sec:mffd+}
-
-The last heuristic incorporates AHC as described in Section \ref{sec:ahca}.
-The \textsc{Modified First-Fit Decreasing with AHC} (MFFD$^+$) heuristic operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.
-However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ then executes AHC on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}).
+The last heuristic, \textsc{Modified First-Fit Decreasing with AHC} (MFFD$^+$), incorporates AHC as described in Section \ref{sec:ahca}.
+MFFD$^+$ operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.
+However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ executes AHC on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}).
 If AHC finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip.
@@
 This reduces the possibility of having to start a new strip for an item, thus preventing increasing the number of strips in the final solution.
-Since AHC is executed every time an item can fit onto a strip that already contains items, (up to $|\mathcal{S}|$ times per item, where $|\mathcal{S}|$ is the number of strips containing at least one item so far in the procedure) MFFD$^+$ is slower in comparison to the previous heuristics.
+%Since AHC is executed every time an item can fit onto a strip that already contains items, (up to $|\mathcal{S}|$ times per item, where $|\mathcal{S}|$ is the number of strips containing at least one item so far in the procedure) MFFD$^+$ is slower in comparison to the previous heuristics.
 
@@
 \begin{comment}
-\begin{abstract}
-\begin{itemize}
-\item ``first, alg for COP and show how used for single strip feasible arrangement''
-\item ``then go on to examine how alg can combine to tackle multi-strip version of problem - closely related to 1DBPP''
-\item discuss problems that arise
-\item variant/generalisation of the 1DBPP ``in which both the ordering and orientation of items in a container influences the validity and quality of a solution''
-\item ``problem that requires the cutting and socring of rectangular pieces of cardboard in the construction of boxes''
-\end{itemize}	
-\end{abstract}
-\end{comment}
-
-\begin{comment}
 \begin{itemize}

### 2018-06-26 PAPER/main.tex
bullet point abstract

@@
 
-\begin{comment}
-\begin{abstract}
 \begin{itemize}
+	\item This paper addresses a generalisation of the one-dimensional bin-packing problem
+	\item rectangular items scored to create/construct cardboard boxes
+	\item items packed onto strips in order to be scored to aid construction of boxes
+	\item 
 	\item ``first, alg for COP and show how used for single strip feasible arrangement''
@@
 \end{itemize}
-\end{abstract}
-\end{comment}
 
@@
 	\item if sets dont have feasible solution, try swapping items between sets
-	\item initial tests, Becker theorem 6 2015 paper 
+	\item initial tests, Becker theorem 6 2015 paper \cite{garraffa2016}
+	\item minimise waste on each strip, not just number of strips
+	\item tsp return to base
 \end{itemize}

### 2018-06-29 PAPER/main.tex
changed subfigures to be aligned
added abstract and changed end of introduction

@@
 \begin{abstract}
-
+	This paper investigates the Score-Constrained Strip-Packing Problem (SCSPP), a combinatorial optimisation problem that generalises the one-dimensional bin-packing problem.
+In the construction of cardboard boxes, rectangular items are packed onto strips to be scored by knives prior to being folded.
+The order and orientation of the items on the strips determine whether the knives are able to score the items correctly.
+Initially, we detail an exact polynomial-time algorithm for the Constrained Ordering Problem (COP), and illustrate how it can find a feasible alignment of items on a single strip.
+We then integrate this algorithm with a packing heuristic to address the SCSPP and compare with two other greedy heuristics, showing the cases in which each heuristic is superior.
 \end{abstract}
-
-\begin{itemize}
-	\item This paper addresses a generalisation of the one-dimensional bin-packing problem
-	\item rectangular items scored to create/construct cardboard boxes
-	\item items packed onto strips in order to be scored to aid construction of boxes
-	\item 
-	\item ``first, alg for COP and show how used for single strip feasible arrangement''
-	\item ``then go on to examine how alg can combine to tackle multi-strip version of problem - closely related to 1DBPP''
-	\item discuss problems that arise
-	\item variant/generalisation of the 1DBPP ``in which both the ordering and orientation of items in a container influences the validity and quality of a solution''
-	\item ``problem that requires the cutting and socring of rectangular pieces of cardboard in the construction of boxes''
-\end{itemize}
 
@@
 
-The remainder of this article is structured as follows: In Section 2, we will detail an exact polynomial-time algorithm for the COP, and thus the SCPSP.
-Section 3 then describes three heuristics that can be used to find feasible solutions to the SCSPP and the associated advantages and disadvantages.
-A comparison of these heuristics and an analysis of the results will be provided in Section 4, and finally Section 5 concludes the paper and proposes some potential directions for future work.
+The remainder of this article is structured as follows: In Section 2, we will detail an exact polynomial-time algorithm for the COP, and show how it is applicable to the subproblem.
+Section 3 then introduces three heuristics that can be used to find feasible solutions to the SCSPP, one of which makes particular use of the exact algorithm from the previous section, and their associated advantages and disadvantages.
+An analysis of results gained from extensive experiments and a comparison of the heuristics is provided in Section 4, and finally Section 5 concludes the paper and proposes some potential directions for future work.
 
@@
 	\centering
-	\begin{subfigure}[h]{0.4\textwidth}
+	\begin{subfigure}[t]{0.4\textwidth}
 		\includestandalone[width=\textwidth]{figures/matching}
@@
 	\end{subfigure} \quad
-	\begin{subfigure}[h]{0.55\textwidth}
+	\begin{subfigure}[t]{0.55\textwidth}
 		\includestandalone[width=\textwidth]{figures/mps}
@@
 MFFD$^+$ operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.
-However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ executes AHC on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}).
+However, rather than attempting to place the item onto the right-most side of the strip, MFFD$^+$ executes AHC on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}).
 If AHC finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip.
@@
 \begin{itemize}
+\item This paper addresses a generalisation of the one-dimensional bin-packing problem
+\item Paper investigates the SCSPP, a combinatorial optimisation problem that generalises 1dbpp/ problem related to the 1dbpp/with applications in the cutting and packing industries/assoc with the csp.
+\item Rectangular items scored to create/construct cardboard boxes
+\item Items packed onto strips in order to be scored to aid construction of boxes
+\item Feasible alignment/order and orientation of items
+\item Graph theory/networks/hamiltonian cycles
+\item Scored prior to being folded
+\item Feasible alignment prior to being scored
+\item Initially, detail exact p-time alg for COP, illustrate how to use for single strip problem/finding alignment of items on a single strip
+\item Multistrip version, integrate with well known heuristic, compare with other greedy heuristics, show effectiveness/cases in which superior
+\item Related to 1DBPP
+
+\item ``during the process of producing boxes, flat papers are prepared for folding by being scored with knives''
+\item ``min distance between knives can be kept''
+\item ``first, alg for COP and show how used for single strip feasible arrangement''
+\item ``then go on to examine how alg can combine to tackle multi-strip version of problem - closely related to 1DBPP''
+\item discuss problems that arise
+\item variant/generalisation of the 1DBPP ``in which both the ordering and orientation of items in a container influences the validity and quality of a solution''
+\item ``problem that requires the cutting and scoring of rectangular pieces of cardboard in the construction of boxes''
+\item ``highlight the circumstances under which each scheme is advantageous''
+\end{itemize}
+\end{comment}
+
+\begin{comment}
+\begin{itemize}
 	\item ``BPP becomes easier to solve when the number of items per bin increases, and problems with two or less items per bin are trivial to solve.

### 2018-07-04 PAPER/main.tex
added parts to conclusion, introduction, theorem, and extra figure

@@
 	This paper investigates the Score-Constrained Strip-Packing Problem (SCSPP), a combinatorial optimisation problem that generalises the one-dimensional bin-packing problem.
-In the construction of cardboard boxes, rectangular items are packed onto strips to be scored by knives prior to being folded.
+In the construction of cardboard boxes rectangular items are packed onto strips to be scored by knives prior to being folded.
 The order and orientation of the items on the strips determine whether the knives are able to score the items correctly.
-Initially, we detail an exact polynomial-time algorithm for the Constrained Ordering Problem (COP), and illustrate how it can find a feasible alignment of items on a single strip.
-We then integrate this algorithm with a packing heuristic to address the SCSPP and compare with two other greedy heuristics, showing the cases in which each heuristic is superior.
+Initially, we detail an exact polynomial-time algorithm for the Constrained Ordering Problem and illustrate how it can find a feasible alignment of items on a single strip.
+We then integrate this algorithm with a packing heuristic to address the SCSPP and compare with two other greedy heuristics, discussing the circumstances in which each heuristic is superior.
 \end{abstract}
@@
 	\centering
-	\includestandalone[width=0.9\textwidth]{figures/itemsknife}
+	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
 	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation $(a_i, b_i)$, and a feasible alignment of two items that can be scored simultaneously.}	
@@
 Clearly, for two items to be placed alongside one another feasibly, the distance between the two score lines from adjacent items must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
-Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
-Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.
+Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.}.
+It follows that there are $\frac{n!}{2}$ $2^n$ distinct arrangements of items, and so as $n$ increases,
 
@@
 		\caption{Replacing edges connects the components and forms an alternating Hamiltonian cycle.}	
-		\label{fig:mpscycle}
+		\label{fig:mpscycle} \vspace{5mm}
+	\end{subfigure}
+	\begin{subfigure}[H]{0.8\textwidth}
+		\includestandalone[width=\textwidth]{figures/mpspath}
+		\caption{Alternating Hamiltonian Path corresponding to feasible solution $\mathcal{T}$.}	
+		\label{fig:mpspath}
 	\end{subfigure}
@@
 	\If{$|R'| < n + 1$}
-		\State Infeasible, end
+		\State infeasible, end
 	\EndIf
@@
 	\If{$q = 1$}
-		\State Remove dominating vertices and incident edges
+		\State remove dominating vertices and incident edges
 		\Return $G'$
 	\Else
-		\State Execute \textsc{Bridge Recognition}
+		\State execute \textsc{Bridge Recognition}
 		\If{$q = 1$}
-			\State Remove dominating vertices and incident edges
+			\State remove dominating vertices and incident edges
 			\Return $G'$
 		\Else
-			\State Infeasible, end	
+			\State infeasible, end	
 		\EndIf	
@@
 \begin{proof}
+	\begin{itemize}
+		\item Initial creation of $G = (V, B \cup R)$ - $O(n^2)$.
+		\item \textsc{Maximum Cardinality Matching} - $O(n\log n)$ due to initial sorting of vertices.
+		\item \textsc{Bridge Recognition}:
+		\begin{itemize}
+			\item sort edges into list and remove invalid egdes - $O(n \log n)$.
+			\item go through list to put into sets $R_i$, each edge assessed exactly once - $O(n)$.
+			\item check every set $R_i$ to see if $|R_i| = q$, since there must be a minimum of two red/matching edges in a set $R_i$, there can be at most $\frac{n}{2}$ $R_i$ sets created - $O(n)$.
+			\item check overlapping/multiple sets - ?
+		\end{itemize}	
+		\item Connecting Procedure - $n+1$ red edges on $G'$, so maximum every red edge in $R'$ needs to be replaced, $n+1$ edges to replace with edges from sets $R_i$.
+so at most $n+1$ edges need to be added to $G'$ and $n+1$ edges removed (edges added to $R'$ and removed from $R'$) - $O(n)$.
+	\end{itemize}
+	Hence complexity of AHC is $O(n^2)$ time.
 	\qed
@@
 That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled, that is, the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance $\tau$ (\ref{eqn:vscstrip}).
+Note that equations \ref{eqn:packall} - \ref{eqn:capacity} are the necessary conditions for the BPP.
 
@@
 
-\section{Further Work}
+\section{Conclusions and Further Work}
 \begin{itemize}
-	\item \cite{miller1960}
+	\item This paper introduced a SPP with score constraints, where the order and orientation of the items is crucial to the feasibility of the solution (for example).
+	\item We showed that a solution can be found for the single strip version of the problem (subproblem) in p-time/ we showed an exact p-time alg for the single strip version of the problem. 
+	\item exact p-time alg for COP used to solve subproblem
+	\item Thus the main problem was finding solutions for the multistrip version
+	\item Created 3 heuristics, one which included the p-time alg. 
+	\item shown how AHC can be combined with well known heuristic to produce a method for tackling multistrip version of the problem, the SCSPP.
+	\item Experimental results show that ...
+	\item Further work.
+	\item items closer to practical applications, multiple items having same width and score widths
+	\item Genetic algorithm/EA
+	\item Operating theatre cleaning/scheduling
+	\item lower bound for the optimal number of strips SCSPP
+	\item \cite{miller1960} TSP returning to base
 	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution.

### 2018-07-05 PAPER/main.tex
added statement about combinatorial explosion, changed figure size

@@
 Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.}.
-It follows that there are $\frac{n!}{2}$ $2^n$ distinct arrangements of items, and so as $n$ increases,
+It follows that there are $\frac{n!}{2}2^n$ distinct arrangements of items, and so complete enumeration can cause a combinatorial explosion.
 
@@
 	\end{subfigure} \quad
-	\begin{subfigure}[t]{0.55\textwidth}
+	\begin{subfigure}[t]{0.57\textwidth}
 		\includestandalone[width=\textwidth]{figures/mps}
@@
 	\label{thm:copsoln}
-	If there exists an alternating Hamiltonian cycle on a graph $G$ created from an instance $\mathcal{M}$ of the COP, then AHC is able to find the cycle in $O(n^2)$ time.
+	If there exists an alternating Hamiltonian cycle on a graph $G$ created from an instance $\mathcal{M}$ of the COP, then AHC is able to find the cycle in at most $O(n^2)$ time.
 \end{theorem}
@@
 That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled, that is, the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance $\tau$ (\ref{eqn:vscstrip}).
-Note that equations \ref{eqn:packall} - \ref{eqn:capacity} are the necessary conditions for the BPP.
+Note that equations (\ref{eqn:packall}) - (\ref{eqn:capacity}) are the necessary conditions for the BPP.
 
@@
 	\item minimise waste on each strip, not just number of strips
-	\item tsp return to base
 \end{itemize}

### 2018-07-05 PAPER/main.tex
minor changes

@@
 \label{sec:intro}
-Firstly, let us introduce the Constrained Ordering Problem (COP):
+The Constrained Ordering Problem (COP) is defined as follows:
 
@@
 	\centering
-	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
+	\includestandalone[width=0.7\textwidth]{figures/itemsknife}
 	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation $(a_i, b_i)$, and a feasible alignment of two items that can be scored simultaneously.}	
@@
 Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose sum equal or exceed $\tau$, provided they are not partners.
-It can be seen that the edges in $R$ represent all possible orderings of values from different pairs in an instance $\mathcal{M}$ that fulfil the vicinal sum constraint in Definition \ref{defn:cop}.
+It can be seen that the edges in $R$ represent all possible orderings of values from different pairs in $\mathcal{M}$ that fulfil the vicinal sum constraint in Definition \ref{defn:cop}.
 Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$ and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$.
@@
 \end{subfigure}
-\caption{Construction of $G$ using instance $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, where $v_{13}$ and $v_{14}$ are the dominating vertices.}
+\caption{Construction of $G$ using instance $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$.}
 \label{fig:partners/threshold}
@@
 
-An alternating Hamiltonian cycle on $G$ correpsonds to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ shows values that can be placed alongside one another feasibly.
+An alternating Hamiltonian cycle on $G$ correpsonds to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ indicates the values that can be placed alongside one another feasibly.
 Thus, by removing the dominating vertices and any incident edges, the remaining alternating Hamiltonian path gives the order in which the elements should be placed to produce a feasible solution $\mathcal{T}$, if indeed one exists.
@@
 
-During MCM, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided that 
+During MCM, if a vertex $v_i$ is not adjacent to any other unmatched vertex except its partner $p(v_i)$ via a blue edge, the preceeding vertex $v_{i-1}$ can be ``rematched'', provided that 
 \begin{enumerate*}[label={(\alph*)}]
@@
 	%\item $v_{i-1} \in R'$; and
-	\item $(v_{i-1}, m(v_{i-1})) \in R'$; and
-	\item $(v_{i-1}, p(v_i)) \in R$.
+	%\item $(v_{i-1}, m(v_{i-1})) \in R'$; and
+	\item the previous vertex $v_{i-1}$ has been matched; and
+	%\item $(v_{i-1}, p(v_i)) \in R$.
+	\item $v_{i-1}$ and $p(v_i)$ are adjacent via a red edge in $R$.
 \end{enumerate*}
-Then, $v_i$ is matched with the vertex that is currently matched with $v_{i-1}$, i.e $m(v_i) = m(v_{i-1})$, and $v_{i-1}$ is rematched with $p(v_i)$, i.e.
-$m(v_{i-1}) = p(v_i)$.
+Then, $v_i$ is matched with the vertex that is currently matched with $v_{i-1}$, and $v_{i-1}$ is rematched with $p(v_i)$.
 It is guaranteed that MCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time (\citealp{mahadev1994}).
@@
 	\end{subfigure}
-	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MCM. The same solution is shown in planar form in (b).}
+	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MCM. When in planar form, it is clear that $q = 2$.}
 	\label{fig:matching/mps}
@@
 However, if $q > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle.
-To do this, a \textsc{Bridge Recognition} (BR) algorithm can be executed that selects suitable edges from $R$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.
+To do this, a \textsc{Bridge Recognition} (BR) algorithm can be executed that selects suitable edges from $R\backslash R'$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.
 
@@
 For instance, in the example illustrated in Figure \ref{fig:matching/mps}, the edges would be sorted as follows: $(v_1, v_{14}), (v_2, v_{13}),(v_3, v_{12}),(v_4, v_{11}),(v_6, v_{10}),(v_7, v_8)$.
+Note that, since $v_5$ was not matched with the highest-indexed vertex possible during MCM, the edge $(v_5, v_9)$ does not adhere to the required structure of the list and is therefore omitted.
 % (v5, v9) removed from list, not matched with highest-indexed vertex in MCM since it was v10 and v10 is v5's partner.
@@
 \begin{enumerate*}[label={(\alph*)}]
-	\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
-	\item The current edge and the next edge are members of different components on $G'$.
+	\item the lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
+	\item the current edge and the next edge are members of different components on $G'$.
 \end{enumerate*}
@@
 \item On the other hand, if there exists a set $R_i$ such that $|R_i| = q$, then the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle.
-This is achieved by adding the red edge connecting the lower-indexed vertex of each edge in $R_i$ to the higher-indexed vertex of the next edge to $R'$ (for the final edge in $R_i$, add the red edge connecting its lower-indexed vertex to the higher-indexed vertex of the first edge).
+This is achieved by adding the red edge from $R\backslash R'$ connecting the lower-indexed vertex of each edge in $R_i$ to the higher-indexed vertex of the next edge to $R'$ (for the final edge in $R_i$, add the red edge connecting its lower-indexed vertex to the higher-indexed vertex of the first edge).
 Any edges that appear in both $R_i$ and $R'$ are then removed from $R'$, so that $R'$ remains a perfect matching and $R_i \cap R' = \emptyset$.
-$G'$ then consists of a single alternating Hamiltonian cycle, and hence a solution has been found.
+$G'$ then consists of a single alternating Hamiltonian cycle.
 % add edges (v_i, m(v_{i+1})) for i \in {1, 2, ..., |R_i| -1} from R to R', and then the edge (v_{|R_i|}, m(v_1)) from R to R'
@@
 \end{enumerate}
-Using the instance illustrated in the figures as an example, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are in the set $R_1$ formed by BR, as they are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$ as seen in Figure \ref{fig:mps}), and $(v_3, v_{11}) \in R$.
+Using the instance illustrated in the figures as an example, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are in the set $R_1$ formed by BR, as \begin{enumerate*}[label={(\alph*)}]
+	\item $(v_3, v_{11}) \in R$, i.e. the lower-indexed vertex of the first edge is adjacent to the higher-indexed vertex of the next edge; and
+	\item the edges are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$ as seen in Figure \ref{fig:mps}).
+\end{enumerate*}
 Note that since $v_4$ and $v_{11}$ are adjacent, $v_4$ must also be adjacent to $v_{12}$, i.e.
@@
 	\centering
-	\begin{subfigure}[H]{0.7\textwidth}
+	\begin{subfigure}[H]{0.57\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpsconnect}
@@
 	\end{subfigure}
-	\begin{subfigure}[H]{0.7\textwidth}
+	\begin{subfigure}[H]{0.57\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpscycle}
@@
 	\end{subfigure}
-	\begin{subfigure}[H]{0.8\textwidth}
+	\begin{subfigure}[H]{0.7\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpspath}
@@
 
+\begin{comment}
 \begin{algorithm}[h]
@@
 \end{algorithm}
+\end{comment}
 
@@
 	\label{thm:copsoln}
-	If there exists an alternating Hamiltonian cycle on a graph $G$ created from an instance $\mathcal{M}$ of the COP, then AHC is able to find the cycle in at most $O(n^2)$ time.
+	If there exists an alternating Hamiltonian cycle on a graph $G$ created from an instance $\mathcal{M}$ of the COP, AHC is able to find the cycle in at most $O(n^2)$ time.
 \end{theorem}

### 2018-07-06 PAPER/main.tex
rearranged locations of figures and tables, minor changes

@@
 	\item $v_i$ is not the first vertex; 
-	%\item $v_{i-1} \in R'$; and
-	%\item $(v_{i-1}, m(v_{i-1})) \in R'$; and
 	\item the previous vertex $v_{i-1}$ has been matched; and
-	%\item $(v_{i-1}, p(v_i)) \in R$.
 	\item $v_{i-1}$ and $p(v_i)$ are adjacent via a red edge in $R$.
@@
 Note that, since $v_5$ was not matched with the highest-indexed vertex possible during MCM, the edge $(v_5, v_9)$ does not adhere to the required structure of the list and is therefore omitted.
-% (v5, v9) removed from list, not matched with highest-indexed vertex in MCM since it was v10 and v10 is v5's partner.
 
@@
 The procedure terminates once the penultimate edge in the list has been assessed.
-% (a) (v_i,m(v_{i+1})) \in R
-% (b) (v_i, m(v_i)) \in C_k, (v_{i+1}, m(v_{i+1})) \in C_l, k \neq l
 
@@
 If such a collection of sets exists, then the components of $G$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.
-% Refer to figures
 \end{enumerate}
+
 Using the instance illustrated in the figures as an example, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are in the set $R_1$ formed by BR, as \begin{enumerate*}[label={(\alph*)}]
@@
 
-This algorithm, which will be referred to as the \textsc{Alternating Hamiltonian Construction} (AHC) algorithm is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP.
-If a solution does indeed exist, AHC can produce this solution in at most $O(n^2)$ time.
-% Cite Becker
-
 \begin{figure}	
@@
 		\includestandalone[width=\textwidth]{figures/mpsconnect}
-		\caption{Edges from $R\backslash R'$ can connect vertices from different cycles.}	
-		\label{fig:mpsconnect} \vspace{5mm}
+		%\caption{Edges from $R\backslash R'$ can connect vertices from different cycles.}	
+		\label{fig:mpsconnect}
 	\end{subfigure}
@@
 		\includestandalone[width=\textwidth]{figures/mpscycle}
-		\caption{Replacing edges connects the components and forms an alternating Hamiltonian cycle.}	
-		\label{fig:mpscycle} \vspace{5mm}
+		%\caption{Replacing edges connects the components and forms an alternating Hamiltonian cycle.}	
+		\label{fig:mpscycle}
 	\end{subfigure}
-	\begin{subfigure}[H]{0.7\textwidth}
+	\begin{subfigure}[H]{0.6\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpspath}
-		\caption{Alternating Hamiltonian Path corresponding to feasible solution $\mathcal{T}$.}	
+		%\caption{Alternating Hamiltonian Path corresponding to feasible solution $\mathcal{T}$.}	
 		\label{fig:mpspath}
@@
 
-\begin{comment}
-\begin{algorithm}[h]
-\caption{\textsc{Alternating Hamiltonian Construction} (AHC) algorithm}
-\label{alg:ahca}
-\begin{algorithmic}[1]
-	\State Create the graph $G = (V, B \cup R)$ from instance $\mathcal{M}$
-	\State Execute \textsc{Maximum Cardinality Matching}
-	\If{$|R'| < n + 1$}
-		\State infeasible, end
-	\EndIf
-	\State Produce the subgraph $G' = (V, B \cup R')$ consisting of $q$ cycles
-	\If{$q = 1$}
-		\State remove dominating vertices and incident edges
-		\Return $G'$
-	\Else
-		\State execute \textsc{Bridge Recognition}
-		\If{$q = 1$}
-			\State remove dominating vertices and incident edges
-			\Return $G'$
-		\Else
-			\State infeasible, end	
-		\EndIf	
-	\EndIf
-\end{algorithmic}	
-\end{algorithm}
-\end{comment}
+This algorithm, which will be referred to as the \textsc{Alternating Hamiltonian Construction} (AHC) algorithm is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP.
+If a solution does indeed exist, AHC can produce this solution in at most $O(n^2)$ time.
+% Cite Becker
 
@@
 In this section, we now turn our attention to the multi-strip version of the problem.
-As mentioned in the introduction, this problem is a generalisation of the BPP in that we also require the sum of every pair of adjacent score widths to be greater than or equal to a minimum scoring distance $\tau$.
+As mentioned in the introduction, the SCSPP is a generalisation of the BPP in that we also require the sum of every pair of adjacent score widths to be greater than or equal to a minimum scoring distance $\tau$.
 It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}), and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.
@@
 
-\begin{figure}[h!]	
+\begin{figure}[H]	
 	\centering
@@
 All individual trials were executed in under 160ms.
-
-Tables \ref{table:n=500} and \ref{table:n=1000} compare the results obtained from the three heuristics using different values of $\delta$ and $W$ for $n = 500$ and 1000 respectively.
-Figures in bold indicate the best average optimality for the given combination of parameters.
-Initially, we can see that $r$ tends toward 1 as $\delta$ increases, since the proportion of score widths meet the vicinal sum constraint increases and more items can be packed onto one strip, reducing the number of strips required.
-Note that when $\delta = 1.0$ MFFD and MFFD$^+$ have identical optimality ratios, as the instances are equivalent to the original BPP ($\tau = 0$) and so they operate in the same fashion as the original FFD heuristic.
-
-Looking at results for both $n = 500$ and $n = 1000$, there is a clear pattern with respect to $r$ across all widths and proportion levels.
-PS has the best optimality ratio for a wider range of $\delta$ when the strips are wider, and a much smaller range when the strip width decreases.
-Conversely, MFFD$^+$ obtains better optimality ratios for a wider range of $\delta$ when $W = 1250$.
-Although PS does have the best optimality of the three heuristics for $\delta = 0.1$ and 0.2 using the smallest strip width, we can see that it only marginally superior to MFFD$^+$.
-For example, take $\delta = 0.2$ in Table \ref{table:n=500} for $W = 1250$.
-The difference between $r$ for PS and MFFD$^+$ is 0.00829, which translates to less than 2 strips difference between the average number of strips generated by each heuristic.
-
-One interesting feature is the reduction of $r$ between $\delta = 0.4$ and $\delta = 0.5$, which is much more significant for $W = 5000$ as opposed to $W = 1250$.
-The reduction occurs due to an increase in the number of feasible alignments of the items, as every score width is able to be paired with $n-1$ other score widths when $\delta = 0.5$.
-Thus, when $W = 5000$, more items can be packed onto a strip feasibly, resulting in fewer strips in the final solution.
-However, the difference in $r$ is less noticeable for $W = 1250$, as regardless of the increased proportion in possible pairings, the capacity of the strips is much smaller, preventing the collection of items from multiple strips onto one.
-
-Although using the average optmality from 1000 instances provides a useful overview of the efficiency of a heuristic, there are other characteristics that we can consider.
-Take, for example, the results obtained with parameters $\delta = 0.7$ and $W = 5000$ in Table \ref{table:n=1000}.
-Clearly PS obtains solutions with the fewest strips on average, however, we noted that out of the 1000 instances, PS did not produce a single solution containing $t$ strips.
-On the other hand, there were 152 instances in which MFFD$^+$ was able to generate a solution $S$ such that $|\mathcal{S}| = t$, thus implying that there are at least 152 solutions that can be solved to optimality.
-Despite this, MFFD$^+$ has a higher average optimality than PS, suggesting that the variance in the number of strips required is higher.
-
-\begin{enumerate}
-	\item MFFD and MFFD$^+$ able to obtain opts $\leq 1\%$ of $t$, PS is not.
-	\item PS never best $\delta \geq 0.8$.
-	\item Significant difference in opt, $n = 1000$, $W = 1250$, $\delta = 0.6$, difference between MFFD$^+$ and PS opts is 0.10912 (MFFD$^+$ better), which amounts to an average difference of over 50 strips in solns produced.
-	\item anomaly MFFD $n = 1000$, $W = 1250$, $\delta = 0.3$
-	\item harder problems, \cite{falkenauer1996}, triplets, fewer items per strip, further from 1 when shorter strips.
-	\item cases when opt $\neq 1$: $t$ incorrect, solution produced is not optimal, or both.
-	\item less than 10\% past $\delta = 0.8$
-\end{enumerate}
 
@@
 \end{table}
+
+Tables \ref{table:n=500} and \ref{table:n=1000} compare the results obtained from the three heuristics using different values of $\delta$ and $W$ for $n = 500$ and 1000 respectively.
+Figures in bold indicate the best average optimality for the given combination of parameters.
+Initially, we can see that $r$ tends toward 1 as $\delta$ increases, since the proportion of score widths meet the vicinal sum constraint increases and more items can be packed onto one strip, reducing the number of strips required.
+Note that when $\delta = 1.0$ MFFD and MFFD$^+$ have identical optimality ratios, as the instances are equivalent to the original BPP ($\tau = 0$) and so they operate in the same fashion as the original FFD heuristic.
+
+Looking at results for both $n = 500$ and $n = 1000$, there is a clear pattern with respect to $r$ across all widths and proportion levels.
+PS has the best optimality ratio for a wider range of $\delta$ when the strips are wider, and a much smaller range when the strip width decreases.
+Conversely, MFFD$^+$ obtains better optimality ratios for a wider range of $\delta$ when $W = 1250$.
+Although PS does have the best optimality of the three heuristics for $\delta = 0.1$ and 0.2 using the smallest strip width, we can see that it only marginally superior to MFFD$^+$.
+For example, take $\delta = 0.2$ in Table \ref{table:n=500} for $W = 1250$.
+The difference between $r$ for PS and MFFD$^+$ is 0.00829, which translates to less than 2 strips difference between the average number of strips generated by each heuristic.
+
+One interesting feature is the reduction of $r$ between $\delta = 0.4$ and $\delta = 0.5$, which is much more significant for $W = 5000$ as opposed to $W = 1250$.
+The reduction occurs due to an increase in the number of feasible alignments of the items, as every score width is able to be paired with $n-1$ other score widths when $\delta = 0.5$.
+Thus, when $W = 5000$, more items can be packed onto a strip feasibly, resulting in fewer strips in the final solution.
+However, the difference in $r$ is less noticeable for $W = 1250$, as regardless of the increased proportion in possible pairings, the capacity of the strips is much smaller, preventing the collection of items from multiple strips onto one.
+
+Although using the average optmality from 1000 instances provides a useful overview of the efficiency of a heuristic, there are other characteristics that we can consider.
+Take, for example, the results obtained with parameters $\delta = 0.7$ and $W = 5000$ in Table \ref{table:n=1000}.
+Clearly PS obtains solutions with the fewest strips on average, however, we noted that out of the 1000 instances, PS did not produce a single solution containing $t$ strips.
+On the other hand, there were 152 instances in which MFFD$^+$ was able to generate a solution $S$ such that $|\mathcal{S}| = t$, thus implying that there are at least 152 solutions that can be solved to optimality.
+Despite this, MFFD$^+$ has a higher average optimality than PS, suggesting that the variance in the number of strips required is higher.
+
+\begin{enumerate}
+	\item MFFD and MFFD$^+$ able to obtain opts $\leq 1\%$ of $t$, PS is not.
+	\item PS never best $\delta \geq 0.8$.
+	\item Significant difference in opt, $n = 1000$, $W = 1250$, $\delta = 0.6$, difference between MFFD$^+$ and PS opts is 0.10912 (MFFD$^+$ better), which amounts to an average difference of over 50 strips in solns produced.
+	\item anomaly MFFD $n = 1000$, $W = 1250$, $\delta = 0.3$
+	\item harder problems, \cite{falkenauer1996}, triplets, fewer items per strip, further from 1 when shorter strips.
+	\item cases when opt $\neq 1$: $t$ incorrect, solution produced is not optimal, or both.
+	\item less than 10\% past $\delta = 0.8$
+\end{enumerate}
 

### 2018-07-09 PAPER/main.tex
added authorrunning

@@
-\documentclass[oribibl]{llncs}
+\documentclass[oribibl, runningheads]{llncs}
 \input{includes/preamble.tex}
@@
 \author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
+\authorrunning{A. L. Hawa et al.}
 \institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
@@
 Clearly, for two items to be placed alongside one another feasibly, the distance between the two score lines from adjacent items must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
-Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.}.
-It follows that there are $\frac{n!}{2}2^n$ distinct arrangements of items, and so complete enumeration can cause a combinatorial explosion.
+Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.} It follows that there are $\frac{n!}{2}2^n$ distinct arrangements of items, and so complete enumeration can cause a combinatorial explosion.
 

### 2018-07-09 PAPER/main.tex
removed oribibl
changed layout of paper (not full page), running heads, all of rhyd's changes, table 3dp, removed figure, bullet point procedure overlapping sets

@@
-\documentclass[oribibl, runningheads]{llncs}
+\documentclass[runningheads]{llncs}
 \input{includes/preamble.tex}
@@
 \title{Heuristics for the Score-Constrained Strip-Packing Problem}
-\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
+\author{Asyl L. Hawa\orcidID{0000-0002-2270-1057} \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
 \authorrunning{A. L. Hawa et al.}
-\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
+\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK
+\email{hawaa@cardiff.ac.uk}}
 \maketitle
@@
 The order and orientation of the items on the strips determine whether the knives are able to score the items correctly.
-Initially, we detail an exact polynomial-time algorithm for the Constrained Ordering Problem and illustrate how it can find a feasible alignment of items on a single strip.
-We then integrate this algorithm with a packing heuristic to address the SCSPP and compare with two other greedy heuristics, discussing the circumstances in which each heuristic is superior.
+Initially, we detail an exact polynomial-time algorithm for finding a feasible alignment of items on a single strip.
+We then integrate this algorithm with a packing heuristic to address the multi-strip problem and compare with two other greedy heuristics, discussing the circumstances in which each method is superior.
 \end{abstract}
@@
 	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple.
-The Constrained Ordering Problem (COP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
+The \emph{Constrained Ordering Problem (COP)} consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
 	\begin{equation}
@@
 
-For example, given the multiset $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, one possible solution is $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.
+For example, given $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, one possible solution is $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.
 
-A prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \cite{goulimis2004}.
+A prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by Goulimis \cite{goulimis2004}.
 Here, a set $\mathcal{I}$ of rectangular items (where $|\mathcal{I}| = n$) of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right.
@@
 A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:itemsknife}).
-However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry).
+However, by design, the scoring knives cannot be placed too close to one another and, as such, have a ``minimum scoring distance'' (around 70mm in industry).
 The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$ where $a_i + b_i < w_i$, assigned such that $a_i \leq b_i$.
@@
 \end{figure}
+Clearly, for two items to be feasibly placed alongside one another on a strip, the distance between the two score lines must be equal to or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
+Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and can therefore be ignored.} It follows that there are $\frac{n!}{2}2^n$ distinct arrangements, making complete enumeration infeasible for non-trivial values of $n$.
 
-Clearly, for two items to be placed alongside one another feasibly, the distance between the two score lines from adjacent items must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
-Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.} It follows that there are $\frac{n!}{2}2^n$ distinct arrangements of items, and so complete enumeration can cause a combinatorial explosion.
-
-It can be seen that this problem is in fact equal to the COP, where each unordered pair in an instance $\mathcal{M}$ contains the score widths of an item, and $\tau$ is the minimum scoring distance.
+It can be seen that, when using just one strip, this strip-packing problem is equivalent to the COP, where each unordered pair in an instance $\mathcal{M}$ contains the score widths of an item, and $\tau$ is the minimum scoring distance.
 It then follows that the vicinal sum constraint corresponds to the requirement for the sum of adjacent score widths to exceed $\tau$.
-Figure \ref{fig:items/aligned} shows the example instance $\mathcal{M}$ of the COP from above depicted as a packing problem.
+Figure \ref{fig:items/aligned} shows the same instance $\mathcal{M}$ used above depicted as a packing problem.
 
@@
 		\includestandalone[width=\textwidth]{figures/items}
-		\label{fig:items} \vspace{5pt}
+		\label{fig:items}
 	\end{subfigure} 
@@
 	\end{subfigure}
-	\caption{Example of the strip-packing problem modelled using the instance $\mathcal{M}$ above.
-The vicinal sum constraint has been met between all items in the alignment, which corresponds to a solution $\mathcal{T}$.}
+	\caption{Example of the strip-packing problem and a corresponding solution using $\tau = 7$.}
 	\label{fig:items/aligned}
@@
 
-Observe that in this particular strip-packing problem the widths of the individual items are disregarded, since the aim is to arrange the items onto a strip of seemingly infinite width.
-However, in industrial applications, strips of material are often provided in fixed widths.
+Observe that in this particular strip-packing problem the widths of the individual items are disregarded, since the aim is to arrange the items onto a single strip of seemingly infinite width.
+However, in industrial applications, strips of material will often be provided in fixed widths.
 Given a large problem instance, multiple strips may therefore be required to feasibly accommodate all of the items.
-For this reason, a more generalised problem can also be formulated.
+For this reason, a more generalised problem can also be formulated:
 
@@
 We shall now present an exact polynomial-time algorithm for the COP.
-The underlying algorithm was originally created by \cite{becker2010}, and is used to determine whether or not a solution exists for a given instance.
-In our case, we have extended this algorithm so that, if a solution does indeed exist, the algorithm is able to formulate and present us with this final solution.
-This is especially useful for problems such as the previously mentioned strip-packing problem, where a solution is required in order to place the items in the correct order and orientation.
+The underlying algorithm was originally proposed by \cite{becker2010}, and is used to determine whether or not a solution exists for a given instance.
+Here, we extend this algorithm so that, if a solution does indeed exist, it is also able to formulate and present us with this final solution.
+This is especially useful for problems such as the strip-packing problem, where a solution is required in order to show how the items should be arranged on a strip.
 
-Let $\mathcal{M}$ be an instance of the COP of cardinality $n$.
-It is now useful to model $\mathcal{M}$ a a graph $G$ in which each vertex is associated with a single value in $\mathcal{M}$ in non-decreasing order.
+Let $\mathcal{M}$ be an instance of the COP with cardinality $n$.
+It is now useful to model $\mathcal{M}$ as a graph $G$ in which each vertex is associated with a single value in $\mathcal{M}$ in non-decreasing order.
 A pair of vertices, called ``dominating vertices'' are also added to the graph, both of which are assigned values equal to $\tau$.
@@
 This is represented in $G$ by adding a set of ``blue'' edges, $B$, that contains edges between vertices that are ``partners'', i.e.
-whose values make up a pair in $\mathcal{M}$, as shown in Figure \ref{fig:partners}.
+whose values make up a pair in $\mathcal{M}$.
 By introducing a bijective function $p: V \to V$ that associates each vertex with its partner, $p(v_i) = v_j$, we can denote this set of edges as $B = \{(v_i, p(v_i)) : v_i \in V\}$.
 It can be seen that $B$ is a perfect matching in $G$, with $|B| = n+1$.
-Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose sum equal or exceed $\tau$, provided they are not partners.
+Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose sum equals or exceeds $\tau$, provided they are not partners.
 It can be seen that the edges in $R$ represent all possible orderings of values from different pairs in $\mathcal{M}$ that fulfil the vicinal sum constraint in Definition \ref{defn:cop}.
 Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$ and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$.
-Figure \ref{fig:partners/threshold} illustrates an example construction of $G$.
-\begin{figure}	
+Figure \ref{fig:threshold} illustrates an example construction of $G$.
+\begin{figure}[h!]	
 \centering
-\begin{subfigure}[h]{0.45\textwidth}
-	\includestandalone[width=\textwidth]{figures/partners}
-	\caption{$G = (V, B)$}	
-	\label{fig:partners}
-\end{subfigure} \hspace{40pt}
-\begin{subfigure}[h]{0.45\textwidth}
-	\includestandalone[width=\textwidth]{figures/threshold}
-	\caption{$G=(V, B \cup R)$}	
+	\includestandalone[width=0.6\textwidth]{figures/threshold}
+	\caption{$G = (V, B \cup R)$ using $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$. The corresponding values of each vertex are show in parentheses.}
 	\label{fig:threshold}
-\end{subfigure}
-\caption{Construction of $G$ using instance $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$.}
-\label{fig:partners/threshold}
 \end{figure}
@@
 Recall that a Hamiltonian cycle on a graph $G$ is a cycle that visits every vertex exactly once.
-Now, consider the following definition describing a variant of the classical Hamiltonian cycle involving multiple edge sets.
+Now, consider the following definition describing a variant of the Hamiltonian cycle problem involving multiple edge sets.
 \begin{definition}
@@
 
-An alternating Hamiltonian cycle on $G$ correpsonds to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ indicates the values that can be placed alongside one another feasibly.
-Thus, by removing the dominating vertices and any incident edges, the remaining alternating Hamiltonian path gives the order in which the elements should be placed to produce a feasible solution $\mathcal{T}$, if indeed one exists.
+It is clear than an alternating Hamiltonian cycle on $G$, if one exists, correpsonds to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ indicates the values that can be placed alongside one another feasibly.
 Also, note that every edge in $B$ must be present in the alternating Hamiltonian cycle.
-Consequently, the task can be seen as finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.
+Consequently, the task can also be seen as finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.
+The problem of finding an alternating Hamiltonian cycle on general graphs is NP-hard as it generalises the classical Hamiltonian cycle problem \cite{haggkvist1977}.
+However, the special structure of graphs derived from instances of the COP allows them to be solved in polynomial-time using the following method.
 
-The problem of finding an alternating Hamiltonian cycle on general graphs is NP-hard as it generalises the classical Hamiltonian cycle problem, as stated in a proposition by \cite{haggkvist1977}.
-However, the special structure of graphs derived from instances of the COP allows them to be solved using the following method.
-
-To find a matching $R' \subseteq R$, the following \textsc{Maximum Cardinality Matching} (MCM) algorithm can be executed, as suggested by \cite{mahadev1994} and \cite{becker2010}.
-Take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest-indexed vertex $v_j$ that is not already incident to an edge in $R'$.
+To find a matching $R' \subseteq R$, the \textsc{Maximum Cardinality Matching} (MCM) algorithm is executed \cite{mahadev1994, becker2010}.
+First, take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest-indexed vertex $v_j$ that is not already incident to an edge in $R'$.
 Now add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed.
@@
 \end{enumerate*}
-Then, $v_i$ is matched with the vertex that is currently matched with $v_{i-1}$, and $v_{i-1}$ is rematched with $p(v_i)$.
-It is guaranteed that MCM will produce a maximum cardinality matching $R' \subseteq R$, and is able to do so in at most $O(n \log n)$ time (\citealp{mahadev1994}).
+Then, $v_i$ is matched with the vertex that is currently matched with $v_{i-1}$, and $v_{i-1}$ is rematched with $p(v_i)$. The complexity of MCM is $O(n \lg n)$ time \cite{mahadev1994}.
 
@@
 	\centering
-	\begin{subfigure}[t]{0.4\textwidth}
+	\begin{subfigure}[h]{0.4\textwidth}
 		\includestandalone[width=\textwidth]{figures/matching}
-		\caption{$G' = (V, B \cup R')$}	
-		\label{fig:matching}
 	\end{subfigure} \quad
-	\begin{subfigure}[t]{0.57\textwidth}
+	\begin{subfigure}[h]{0.56\textwidth}
 		\includestandalone[width=\textwidth]{figures/mps}
-		\caption{Planar representation of $G' =(V, B \cup R')$}	
+	\end{subfigure}
+	\caption{Subgraph $G'= (V, B \cup R')$. When in planar form, it is clear that $l = 2$.}
 	\label{fig:mps}
-	\end{subfigure}
-	\caption{Spanning subgraph $G'$ consisting of a matching set $R' \subseteq R$ derived using MCM. When in planar form, it is clear that $q = 2$.}
-	\label{fig:matching/mps}
 \end{figure}
 
-Clearly, if $|R'| < n+1$ after MCM has completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and hence no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
-Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex $v_i \in V$ is adjacent to its partner $p(v_i)$ via a blue edge in $B$, and its match $m(v_i)$ via a red edge in $R'$ (see Figure \ref{fig:matching/mps}).
-$G'$ therefore consists of a collection of cyclic components $C_1, C_2, ..., C_q$.
+Clearly, if $|R'| < n+1$ after MCM has completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and so no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
+Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex $v_i \in V$ is incident to one blue edge and one red edge (see Figure \ref{fig:mps}).
+$G'$ therefore consists of a collection of cyclic components $C_1, C_2, ..., C_l$.
 In the case where $G'$ comprises one component, i.e.
-$q = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP.
-However, if $q > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle.
-To do this, a \textsc{Bridge Recognition} (BR) algorithm can be executed that selects suitable edges from $R\backslash R'$ that will replace certain edges in $R'$ in order to function as bridges and connect the components of $G'$.
+$l = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP.
+However, if $l > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle.
+To do this, a \textsc{Bridge Recognition} (BR) algorithm can now be executed.
+This operates by selecting suitable edges in $R\backslash R'$ that replace edges in $R'$ in order to connect the components of $G'$.
 
-BR operates by first ordering the edges in $R'$ such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order, i.e.
-$(v_1, v_{2n+2}), (v_2, v_{2n+1}), ..., (v_{n+1}, v_{n+2})$.
+BR operates by first ordering the edges in $R'$ such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order.
 Any edges that cannot be placed in such an order are then removed from this list.
-For instance, in the example illustrated in Figure \ref{fig:matching/mps}, the edges would be sorted as follows: $(v_1, v_{14}), (v_2, v_{13}),(v_3, v_{12}),(v_4, v_{11}),(v_6, v_{10}),(v_7, v_8)$.
+For instance, in the example illustrated in Figure \ref{fig:mps}, the edges would be sorted as follows: $(v_1, v_{14}), (v_2, v_{13}),(v_3, v_{12}),(v_4, v_{11}),(v_6, v_{10}),(v_7, v_8)$.
 Note that, since $v_5$ was not matched with the highest-indexed vertex possible during MCM, the edge $(v_5, v_9)$ does not adhere to the required structure of the list and is therefore omitted.
@@
 \begin{enumerate*}[label={(\alph*)}]
-	\item the lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
+	\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
 	\item the current edge and the next edge are members of different components on $G'$.
 \end{enumerate*}
-If these conditions are met, BR adds the current edge to a set $R_i$, and continues to add all succeeding edges in the list to $R_i$ provided that, for each edge, both conditions hold and the succeeding edge is not a member of a component of $G'$ that has an edge in $R_i$.
-Once there are no more valid edges available to add to $R_i$, BR resumes its search through the remaining edges in the list to find a new edge that meets the conditions, and can begin a new set $R_{i+1}$.
+If these conditions are met, BR adds the current edge to a set $R_1$, and continues to add all succeeding edges in the list to $R_1$ provided that, for each edge, both conditions hold and the succeeding edge is not a member of a component of $G'$ that has an edge in $R_1$.
+Once there are no more valid edges available to add to $R_1$, BR resumes its search through the remaining edges in the list to find a new edge that meets the conditions, and can begin a new set $R_2$.
 The procedure terminates once the penultimate edge in the list has been assessed.
@@
 \begin{enumerate}
-\item In the event that BR has been unable to produce a single set, there are no suitable edges that can combine the components $C_1, C_2, ..., C_q$ of $G'$, and therefore an alternating Hamiltonian cycle for $G$ cannot be created.
+\item In the event that BR has produced no sets, there are no suitable edges that can combine the components $C_1, C_2, ..., C_l$ of $G'$, and therefore an alternating Hamiltonian cycle for $G$ cannot be created.
 Thus, no feasible solution exists for the corresponding COP.
 
-\item On the other hand, if there exists a set $R_i$ such that $|R_i| = q$, then the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle.
+\item On the other hand, if there exists a set $R_i$ such that $|R_i| = l$, then all the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle.
 This is achieved by adding the red edge from $R\backslash R'$ connecting the lower-indexed vertex of each edge in $R_i$ to the higher-indexed vertex of the next edge to $R'$ (for the final edge in $R_i$, add the red edge connecting its lower-indexed vertex to the higher-indexed vertex of the first edge).
 Any edges that appear in both $R_i$ and $R'$ are then removed from $R'$, so that $R'$ remains a perfect matching and $R_i \cap R' = \emptyset$.
-$G'$ then consists of a single alternating Hamiltonian cycle.
+$G'$ then consists of a single alternating Hamiltonian cycle; hence a solution has been found.
 % add edges (v_i, m(v_{i+1})) for i \in {1, 2, ..., |R_i| -1} from R to R', and then the edge (v_{|R_i|}, m(v_1)) from R to R'
 
-\item Otherwise, it may be that multiple sets are required to connect the components of $G'$.
-For two sets $R_i$ and $R_j$ to ``overlap'', each set must have one edge from the same component in $G'$, with the other edges in each set being from different components.
-For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of components $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$, but the other edges in the sets are from different components.
-Hence, a selection of sets need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets.
-If such a collection of sets exists, then the components of $G$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.
+\item Otherwise, it may be that multiple sets need to be used to connect the components of $G'$.
+For two sets $R_i$ and $R_j$ to ``overlap'', each set must have exactly one edge from the same component in $G'$, with the other edges in each set being from different components.
+For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of components $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$ but the other edges in the sets are from different components.
+Therefore, a selection of sets need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets.
+If such a collection of sets exists, then the components of $G'$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.
 \end{enumerate}
 
-Using the instance illustrated in the figures as an example, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are in the set $R_1$ formed by BR, as \begin{enumerate*}[label={(\alph*)}]
+\begin{itemize}
+	\item Choose set $R_i$ with the highest cardinality. Call this set $R^{*}_1$. Add this set to $\mathcal{R}$.
+	\item Take original sorted list from beginning of BR, remove edges from list that are in $\mathcal{R}$.
+	\item Go through list again, perform modified BR:
+	\begin{itemize}
+		\item (a) lower-indexed vertex of current edge and higher-indexed vertex of next edge in list are adj via red edge;
+		\item (b) The current edge and an edge in $\mathcal{R}$ are members of the same component, and the next edge is in a component that does not have an edge in $\mathcal{R}$, or vice versa.
+	\end{itemize}	
+	\item If found, add these two edges to set $R^{*}_2$ and add this set to $\mathcal{R}$.
+Continue to add succeeding edges in list to $R^{*}_2$, provided condition (a) holds, and the succeeding edge is a member of a component that does not have an edge in $\mathcal{R}$.
+	\item If no more valid edges, check to see if at least one edge from every component of $G'$ is in $\mathcal{R}$.
+	\item If not, remove edges from $R^{*}_2$ from sorted list, and start again.
+Continue until $\mathcal{R}$ contains sets that overlap and have an edge from every component, or until every edge in the list is assessed and no new set has been created.
+	\item If not all components covered, infeasible, else apply connecting procedure to every individual set in $\mathcal{R}$.
+\end{itemize}
+
+Using the instance illustrated in Figure \ref{fig:connect/cycle} as an example, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are in the set $R_1$ formed by BR, as \begin{enumerate*}[label={(\alph*)}]
 	\item $(v_3, v_{11}) \in R$, i.e. the lower-indexed vertex of the first edge is adjacent to the higher-indexed vertex of the next edge; and
@@
 $(v_4, v_{12}) \in R$, since the value associated with $v_{12}$ is greater than or equal to the value associated with $v_{11}$.
-Then, as $|R_1| = q$, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are removed from $R'$ and replaced by the edges $(v_3, v_{11})$ and $(v_4, v_{12})$ from $R$, as shown in Figure \ref{fig:connect/cycle}.
+Then, because $|R_1| = l$, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are removed from $R'$ and replaced by the edges $(v_3, v_{11})$ and $(v_4, v_{12})$ from $R_1$, as shown in Figure \ref{fig:connect/cycle}.
 Removing the dominating vertices and any incident edges results in an alternating Hamiltonian path, which corresponds to a feasible solution $\mathcal{T}$.
@@
 	\begin{itemize}
-		\item Initial creation of $G = (V, B \cup R)$ - $O(n^2)$.
 		\item \textsc{Maximum Cardinality Matching} - $O(n\log n)$ due to initial sorting of vertices.
@@
 			\item go through list to put into sets $R_i$, each edge assessed exactly once - $O(n)$.
-			\item check every set $R_i$ to see if $|R_i| = q$, since there must be a minimum of two red/matching edges in a set $R_i$, there can be at most $\frac{n}{2}$ $R_i$ sets created - $O(n)$.
+			\item check every set $R_i$ to see if $|R_i| = l$, since there must be a minimum of two red/matching edges in a set $R_i$, there can be at most $\frac{n}{2}$ $R_i$ sets created - $O(n)$.
 			\item check overlapping/multiple sets - ?
@@
 As mentioned in the introduction, the SCSPP is a generalisation of the BPP in that we also require the sum of every pair of adjacent score widths to be greater than or equal to a minimum scoring distance $\tau$.
-It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard (\citealp{garey1979}), and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.
+It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard \cite{garey1979}, and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.
 Instead, heuristics can be used to find near-optimal solutions in a shorter amount of time.
@@
 	\begin{align}
-		\bigcup\nolimits_{j=1}^{|\mathcal{S}|} S_j &= \mathcal{I}, \label{eqn:packall}\\[3pt]
-		S_j \cap S_l &= \emptyset \hspace{5mm} \forall \hspace{1mm} j, l \in \{1, 2, ..., |\mathcal{S}|\}, \hspace{2mm} j \neq l, \label{eqn:nooverlap} \\[3pt]
+		\bigcup\nolimits_{i=1}^{|\mathcal{S}|} S_i &= \mathcal{I}, \label{eqn:packall}\\[3pt]
+		S_i \cap S_j &= \emptyset \hspace{5mm} \forall \hspace{1mm} i, j \in \{1, 2, ..., |\mathcal{S}|\}, \hspace{2mm} i \neq j, \label{eqn:nooverlap} \\[3pt]
 		\sum\nolimits_{i=1}^{|S_j|}w_i & \leq W \hspace{3mm} \forall \hspace{1mm} S_j \in \mathcal{S}, \label{eqn:capacity} \\[3pt]
@@
 
-That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled, that is, the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance $\tau$ (\ref{eqn:vscstrip}).
-Note that equations (\ref{eqn:packall}) - (\ref{eqn:capacity}) are the necessary conditions for the BPP.
-
+That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled (\ref{eqn:vscstrip}).
+Note that constraints (\ref{eqn:packall}) - (\ref{eqn:capacity}) are the necessary conditions for the BPP.
 An optimal solution $\mathcal{S}$ for the SCSPP is a solution that consists of the fewest number of strips $k$ needed to feasibly contain the $n$ items in the given problem instance.
 A simple lower bound for $k$ is the theoretical minimum
-\begin{equation}
-\label{eqn:lowerbound}
-t = \ceil*{\frac{\sum_{i=1}^{n}w_i}{W}},
-\end{equation}
-which can be computed in $O(n)$ time (\citealp{martello1990b}).
+$t = \ceil*{\sum_{i=1}^{n}w_i / W}$ which can be computed in $O(n)$ time \cite{martello1990b}.
 Perhaps the simplest and most well-known heuristic for packing problems is \textsc{First-Fit} (FF), a greedy online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
-It is known that there always exists at least one ordering of the items such that FF produces an optimal solution (\citealp{lewis2009}).
+It is known that there always exists at least one ordering of the items such that FF produces an optimal solution \cite{lewis2009}.
 A minor modification to FF yields the \textsc{First-Fit Decreasing} (FFD) heuristic, which sorts the items in non-increasing order of size prior to performing FF.
-In 1973, \citeauthor{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ strips.
-More recently, \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight.
+In 1973, Johnson \cite{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ strips.
+More recently, Dosa \cite{dosa2007} has proven that the worst case for FFD is in fact $\frac{11}{9}k + \frac{6}{9}$, and that this bound is tight.
 Due to the initial sorting of the items in non-increasing order of sizes, the time complexity of FFD is $O(n\log n)$.
 
-As mentioned in the introduction, the SCSPP shares many similarities with the BPP, however the addition of constraint (\ref{eqn:vscstrip}) induces complications that must be taken into consideration.
-One obvious difference is the order in which the items must appear on the strips.
-The order of the items in the BPP is unimportant, as there are no conditions regarding which items can be placed together, however in the SCSPP the items must be ordered in a way that meets the vicinal sum constraint.
-In addition, removing an item in the BPP retains feasibility, whereas in the SCSPP this is not guaranteed, as it may leave a subset of items for which the vicinal sum constraint is not satisfied.
-Furthermore, the theoretical minimum $t$ (Equation (\ref{eqn:lowerbound})) has the potential to be less accurate for the SCSPP, as the minimum scoring distance $\tau$ is not considered.
+As mentioned in the introduction, the SCSPP shares many similarities with the BPP, however the addition of constraint (\ref{eqn:vscstrip}) brings complications.
+One obvious difference is the order in which the items appear on the strips.
+The order of the items in the BPP is unimportant, however in the SCSPP the items must be ordered in a way that meets the vicinal sum constraint.
+In addition, removing an item from a binin the BPP retains the feasibility of the bin, whereas in the SCSPP this is not guaranteed, as it may leave a subset of items for which the vicinal sum constraint is not satisfied.
+Furthermore, the theoretical minimum $t$ has the potential to be less accurate for the SCSPP, as the minimum scoring distance $\tau$ is not considered.
 For example, if the minimum scoring distance is greater than twice the largest score width, then it is clear that $n$ strips will be required, regardless of the items' widths.
@@
 
-Three heuristics for the SCSPP have been developed: a basic FFD heuristic with a simple modification; a heuristic that packs strips individually and prioritises score widths; and a powerful version of FFD that incorporates the polynomial-time AHC algorithm.
+To gain an understanding of this problem, three heuristics for the SCSPP have been developed for our tests: a basic FFD heuristic with a simple modification; a heuristic that packs strips individually and prioritises score widths; and a powerful version of FFD that incorporates the polynomial-time AHC algorithm.
 
-The first heuristic we developed is the \textsc{Modified First-Fit Decreasing} (MFFD) heuristic which performs in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip.
+The first heuristic is the \textsc{Modified First-Fit Decreasing} (MFFD) heuristic which acts in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip.
 If an item is able to be packed onto a strip without exceeding the strip's capacity, MFFD then checks to see if the vicinal sum constraint is met between the right-most score on the strip and one of the score widths on the current item.
-If the constraint is met, MFFD places the item on the end of the strip in the appropriate orientation, else the heuristic attempts to pack the item onto the next lowest-indexed strip.
-For example, in Figure \ref{fig:comparestrips}, the strip is able to accommodate the current item, however the vicinal sum constraint is not fulfilled in either orientation of the item, and therefore it cannot be feasibly packed onto the strip.
+If the constraint is met, MFFD places the item on the end of the strip in the appropriate orientation, otherwise the next strip is considered.
 
-Despite the additional step, MFFD is a very fast heuristic, as checking the vicinal sum constraint can be performed in constant time.
+Despite the additional step, MFFD is a very fast heuristic, as checking the vicinal sum constraint in this way can be performed in constant time.
 The most prominent issue with this heuristic, however, is due to the items being placed on the end of the strips.
@@
 
-The next heuristic is the \textsc{Pair-Smallest} (PS) heuristic, an extension of a procedure defined by \cite{lewis2011}.
-Unlike MFFD, which packs each item in turn, PS focusses on packing one strip at a time, only starting a new strip once the current strip is unable to accommodate any more items feasibly.
+The next heuristic is the \textsc{Pair-Smallest} (PS) heuristic, which is an extension of an inexact procedure defined by \cite{lewis2011}.
+Unlike MFFD, which packs each item in turn, PS focusses on packing one strip at a time, only starting a new strip once the current strip is unable to accommodate any further items.
 Each strip is initialised by choosing the item from $\mathcal{I}$ with the smallest score width, and packing it in a regular orientation.
@@
 
-The last heuristic, \textsc{Modified First-Fit Decreasing with AHC} (MFFD$^+$), incorporates AHC as described in Section \ref{sec:ahca}.
-MFFD$^+$ operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.
-However, rather than attempting to place the item onto the right-most side of the strip, MFFD$^+$ executes AHC on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$ (see Definition \ref{defn:subprob}).
-If AHC finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip.
+The last heuristic, \textsc{Modified First-Fit Decreasing with AHC} (MFFD$^+$), incorporates the AHC algorithm from Section \ref{sec:ahca}.
+It operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.
+However, rather than attempting to place the item onto the right-most side of the strip, MFFD$^+$ executes AHC on the items.
+If AHC finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next strip.
 Using AHC means that if a feasible alignment of the items exists, there is a guarantee that it will be found.
@@
 
-\section{Comparison}
-For our experiments, we generated 1000 problem instances for two different sizes of $\mathcal{I}$ containing 500 and 1000 items.
+\section{Experimental Results}
+For our experiments, we generated 1000 problem instances for $|\mathcal{I}| \in \{500, 100\}$.
 For each problem instance the items have varying widths $w_i$ between 150 and 1000 and score widths $a_i, b_i$ between 1 and 70 to ensure that each item has exactly two score lines, all selected randomly from a uniform distribution.
-Strips of widths $W = 5000$, 2500 and 1250 were used to alter the number of items per strip.
+Strips of widths $W = 5000$, 2500 and 1250 were used to influence the number of items per strip.
 Both the items and the strips have equal height of $H = 1$.
@@
 Values of $\delta$ from 0.0 to 1.0 were created by changing the value of the minimum scoring distance $\tau$.
-Clearly, when $\delta = 0.0$, there are no score widths that can be packed together feasibly, and so $n$ strips will be required (one for each item), whereas if $\delta = 1.0$ all pairs of score widths meet the constraint, and the problem is analogous to the BPP.
-(As the width of the strips decrease, the average number of items per strip also decreases, making the problem more difficult.)
+Clearly, when $\delta = 0.0$, there are no score widths that can be packed together feasibly, and so $n$ strips will be required (one for each item), whereas if $\delta = 1.0$ all pairs of score widths meet the constraint, and the problem is equivalent to the BPP.
+(As the width of the strips decrease, the average number of items per strip also decreases, making the problem more constrained.)
 
-The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
-The source code for these procedures used for our computational experiments is available at \cite{hawa2018}.
-We calculated the average optimality of each heuristic for every combination of $n$, $\delta$, and $W$ from 1000 instances, where the optimality $r$ of each instance is
-\begin{equation}
-	r = \frac{|\mathcal{S}|}{t},
-\end{equation}
-i.e.
-the ratio of the number of strips in the final solution $\mathcal{S}$ generated by the heuristic to the theoretical minimum $t$, which was calculated using Equation \ref{eqn:lowerbound}.
+The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 3.30GHz processor.
+Our source code and all data is available at \cite{hawa2018}.
+Since optimal solutions are not available, the solution quality $q$ is estimated by comparing to the theoretical minimum $t$, i.e.
+$q = |\mathcal{S}| / t$.
+We calculated the average solution quality of each heuristic for every combination of $n$, $\delta$, and $W$ from 1000 instances.
 All individual trials were executed in under 160ms.
@@
 	\centering
-	\ra{1.3}
-	\caption{Average optimality ratios for $n = 500$. The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.4746, 4.3103, and 2.1645 respectively.}
-	\begin{tabular}{@{}c@{\hspace{25pt}}c@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}c@{}}\toprule
-		& \multicolumn{3}{c}{$W = 5000$, $t = 58.039$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 2500$, $t = 115.571$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 1250$, $t = 230.648$} \\
+	\caption{Average solution quality for $n = 500$. The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.475, 4.310, and 2.165 respectively.}
+	\begin{tabular}{@{}c@{\hspace{15pt}}c@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}c@{}}\toprule
+		& \multicolumn{3}{c}{$W = 5000$, $t = 58.039$} && \multicolumn{3}{c}{$W = 2500$, $t = 115.571$} && \multicolumn{3}{c}{$W = 1250$, $t = 230.648$} \\
 		\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
 		$\delta$ & MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$\\ \midrule
-		0.0 & 8.61813 & 8.61813 & 8.61813 && 4.32789 & 4.32789 & 4.32789 && 2.16858 & 2.16858 & 2.16858 \\
-		0.1 & 5.21367 & \textbf{4.84177} & 5.16085 && 2.65934 & \textbf{2.47735} & 2.65679 && 1.51486 & \textbf{1.47896} & 1.51486 \\
-		0.2 & 4.03055 & \textbf{3.45946} & 3.97645 && 2.12099 & \textbf{1.84737} & 2.11788 && 1.32613 & \textbf{1.31781} & 1.32610 \\
-		0.3 & 3.11091 & \textbf{2.34803} & 3.03816 && 1.72955 & \textbf{1.39676} & 1.70772 && 1.19451 & 1.22922 & \textbf{1.19381} \\
-		0.4 & 2.43605 & \textbf{1.52907} & 2.29713 && 1.45976 & \textbf{1.12798} & 1.40951 && 1.11037 & 1.18065 & \textbf{1.10819} \\
-		0.5 & 1.91057 & \textbf{1.04130} & 1.69129 && 1.26343 & \textbf{1.03341} & 1.19575 && 1.05771 & 1.15415 & \textbf{1.05319} \\
-		0.6 & 1.49086 & \textbf{1.01263} & 1.24645 && 1.12448 & \textbf{1.02957} & 1.06874 && 1.02932 & 1.13470 & \textbf{1.02398} \\
-		0.7 & 1.19571 & \textbf{1.01257} & 1.04468 && 1.04933 & 1.02774 & \textbf{1.01918} && 1.01741 & 1.11368 & \textbf{1.01444} \\
-		0.8 & 1.04977 & 1.01203 & \textbf{1.00815} && 1.01595 & 1.02661 & \textbf{1.00790} && 1.01297 & 1.09136 & \textbf{1.01197} \\
-		0.9 & 1.00929 & 1.01197 & \textbf{1.00463} && 1.00734 & 1.02586 & \textbf{1.00641} && 1.01159 & 1.07283 & \textbf{1.01139} \\
-		1.0 & \textbf{1.00423} & 1.01171 & \textbf{1.00423} && \textbf{1.00626} & 1.02561 & \textbf{1.00626} && \textbf{1.01130} & 1.06549 & \textbf{1.01130} \\
+		0.0 & 8.618 & 8.618 & 8.618 && 4.328 & 4.328 & 4.327 && 2.169 & 2.169 & 2.169 \\
+		0.1 & 5.214 & \textbf{4.842} & 5.161 && 2.659 & \textbf{2.477} & 2.657 && 1.515 & \textbf{1.479} & 1.515 \\
+		0.2 & 4.031 & \textbf{3.459} & 3.976 && 2.121 & \textbf{1.847} & 2.118 && 1.326 & \textbf{1.318} & 1.326 \\
+		0.3 & 3.111 & \textbf{2.348} & 3.038 && 1.730 & \textbf{1.397} & 1.708 && 1.195 & 1.229 & \textbf{1.194} \\
+		0.4 & 2.436 & \textbf{1.529} & 2.297 && 1.460 & \textbf{1.128} & 1.410 && 1.110 & 1.181 & \textbf{1.108} \\
+		0.5 & 1.911 & \textbf{1.041} & 1.691 && 1.263 & \textbf{1.033} & 1.196 && 1.058 & 1.154 & \textbf{1.053} \\
+		0.6 & 1.491 & \textbf{1.013} & 1.246 && 1.124 & \textbf{1.030} & 1.069 && 1.029 & 1.135 & \textbf{1.024} \\
+		0.7 & 1.196 & \textbf{1.013} & 1.045 && 1.049 & 1.028 & \textbf{1.019} && 1.017 & 1.114 & \textbf{1.014} \\
+		0.8 & 1.050 & 1.012 & \textbf{1.008} && 1.016 & 1.027 & \textbf{1.008} && 1.013 & 1.091 & \textbf{1.012} \\
+		0.9 & 1.009 & 1.012 & \textbf{1.005} && 1.007 & 1.026 & \textbf{1.006} && 1.012 & 1.073 & \textbf{1.011} \\
+		1.0 & \textbf{1.004} & 1.012 & \textbf{1.004} && \textbf{1.006} & 1.026 & \textbf{1.006} && \textbf{1.011} & 1.065 & \textbf{1.011} \\
 		\bottomrule
@@
 	\centering
-	\ra{1.3}
-	\caption{Average optimality ratios for $n = 1000$. The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.6207, 4.329 and 2.1692 respectively.}
-	\begin{tabular}{@{}c@{\hspace{25pt}}c@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}c@{}}\toprule
-		& \multicolumn{3}{c}{$W = 5000$, $t = 115.534$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 2500$, $t = 230.563$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 1250$, $t = 460.623$} \\
+	\caption{Average solution quality for $n = 1000$. The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.621, 4.329 and 2.169 respectively.}
+	\begin{tabular}{@{}c@{\hspace{15pt}}c@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}c@{}}\toprule
+		& \multicolumn{3}{c}{$W = 5000$, $t = 115.534$} && \multicolumn{3}{c}{$W = 2500$, $t = 230.563$} && \multicolumn{3}{c}{$W = 1250$, $t = 460.623$} \\
 		\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
 		$\delta$ & MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$\\ \midrule
-		0.0 & 8.65711 & 8.65711 & 8.65711 && 4.33803 & 4.33803 & 4.33803 && 2.17138 & 2.17138 & 2.17138 \\
-		0.1 & 5.17263 & \textbf{4.84248} & 5.14027 && 2.63606 & \textbf{2.48111} & 2.64271 && 1.51056 & \textbf{1.46744} & 1.51121 \\
-		0.2 & 3.97565 & \textbf{3.46163} & 3.95164 && 2.09301 & \textbf{1.85824} & 2.10161 && 1.31785 & \textbf{1.31090} & 1.31876 \\
-		0.3 & 3.04866 & \textbf{2.35023} & 3.01260 && 1.69777 & \textbf{1.40862} & 1.68776 && \textbf{1.18304} & 1.22111 & 1.18344 \\
-		0.4 & 2.37436 & \textbf{1.52046} & 2.26560 && 1.42646 & \textbf{1.13101} & 1.38430 && 1.09722 & 1.17063 & \textbf{1.09614} \\
-		0.5 & 1.84748 & \textbf{1.02600} & 1.64169 && 1.22960 & \textbf{1.03017} & 1.16950 && 1.04411 & 1.14430 & \textbf{1.03986} \\
-		0.6 & 1.43331 & \textbf{1.01212} & 1.20264 && 1.09935 & \textbf{1.02738} & 1.05010 && 1.01971 & 1.12392 & \textbf{1.01480} \\
-		0.7 & 1.15500 & \textbf{1.01198} & 1.02574 && 1.03421 & 1.02569 & \textbf{1.01224} && 1.01150 & 1.10164 & \textbf{1.00926} \\
-		0.8 & 1.03182 & 1.01182 & \textbf{1.00587} && 1.01111 & 1.02454 & \textbf{1.00682} && 1.00861 & 1.07791 & \textbf{1.00804} \\
-		0.9 & 1.00707 & 1.01165 & \textbf{1.00419} && 1.00663 & 1.02406 & \textbf{1.00608} && 1.00784 & 1.05885 & \textbf{1.00774} \\
-		1.0 & \textbf{1.00399} & 1.01169 & \textbf{1.00399} && \textbf{1.00603} & 1.02400 & \textbf{1.00603} && \textbf{1.00770} & 1.05406 & \textbf{1.00770} \\
+		0.0 & 8.657 & 8.657 & 8.657 && 4.338 & 4.338 & 4.338 && 2.171 & 2.171 & 2.171 \\
+		0.1 & 5.173 & \textbf{4.842} & 5.140 && 2.636 & \textbf{2.481} & 2.643 && 1.511 & \textbf{1.467} & 1.511 \\
+		0.2 & 3.976 & \textbf{3.462} & 3.952 && 2.093 & \textbf{1.858} & 2.102 && 1.318 & \textbf{1.311} & 1.319 \\
+		0.3 & 3.047 & \textbf{2.350} & 3.013 && 1.698 & \textbf{1.409} & 1.688 && \textbf{1.183} & 1.221 & \textbf{1.183} \\
+		0.4 & 2.374 & \textbf{1.520} & 2.266 && 1.426 & \textbf{1.131} & 1.384 && 1.097 & 1.171 & \textbf{1.096} \\
+		0.5 & 1.847 & \textbf{1.026} & 1.642 && 1.230 & \textbf{1.030} & 1.170 && 1.044 & 1.144 & \textbf{1.040} \\
+		0.6 & 1.433 & \textbf{1.012} & 1.203 && 1.099 & \textbf{1.027} & 1.050 && 1.020 & 1.124 & \textbf{1.015} \\
+		0.7 & 1.155 & \textbf{1.012} & 1.026 && 1.034 & 1.026 & \textbf{1.012} && 1.012 & 1.102 & \textbf{1.009} \\
+		0.8 & 1.032 & 1.012 & \textbf{1.006} && 1.011 & 1.025 & \textbf{1.007} && 1.009 & 1.078 & \textbf{1.008} \\
+		0.9 & 1.007 & 1.012 & \textbf{1.004} && 1.007 & 1.024 & \textbf{1.006} && \textbf{1.008} & 1.059 & \textbf{1.008} \\
+		1.0 & \textbf{1.004} & 1.012 & \textbf{1.004} && \textbf{1.006} & 1.024 & \textbf{1.006} && \textbf{1.008} & 1.054 & \textbf{1.008} \\
 		\bottomrule
@@
 
-Tables \ref{table:n=500} and \ref{table:n=1000} compare the results obtained from the three heuristics using different values of $\delta$ and $W$ for $n = 500$ and 1000 respectively.
-Figures in bold indicate the best average optimality for the given combination of parameters.
-Initially, we can see that $r$ tends toward 1 as $\delta$ increases, since the proportion of score widths meet the vicinal sum constraint increases and more items can be packed onto one strip, reducing the number of strips required.
-Note that when $\delta = 1.0$ MFFD and MFFD$^+$ have identical optimality ratios, as the instances are equivalent to the original BPP ($\tau = 0$) and so they operate in the same fashion as the original FFD heuristic.
+Tables \ref{table:n=500} and \ref{table:n=1000} compare the results obtained from the three heuristics using the different values of $\delta$ and $W$ for $n = 500$ and 1000 respectively.
+Figures in bold indicate the best average solution quality for the given combination of parameters.
+We see that $q$ tends toward 1 as $\delta$ increases since the proportion of score widths meeting the vicinal sum constraint increases, allowing more items per strip and reducing the number of strips required.
+Note that when $\delta = 1.0$ MFFD and MFFD$^+$ have identical solution qualities, as the instances are equivalent to the original BPP ($\tau = 0$) and so they operate in the same fashion as the original FFD heuristic.
 
-Looking at results for both $n = 500$ and $n = 1000$, there is a clear pattern with respect to $r$ across all widths and proportion levels.
-PS has the best optimality ratio for a wider range of $\delta$ when the strips are wider, and a much smaller range when the strip width decreases.
-Conversely, MFFD$^+$ obtains better optimality ratios for a wider range of $\delta$ when $W = 1250$.
-Although PS does have the best optimality of the three heuristics for $\delta = 0.1$ and 0.2 using the smallest strip width, we can see that it only marginally superior to MFFD$^+$.
+Looking at results for both $n = 500$ and 1000, there is a clear pattern with respect to $q$ across all widths and proportion levels.
+PS has the best solution quality for a wider range of $\delta$ when the strips are wider, and a much smaller range when the strip width decreases.
+Conversely, MFFD$^+$ obtains better solution qualities for a wider range of $\delta$ when $W = 1250$.
+Although PS does have the best solution quality of the three heuristics for $\delta = 0.1$ and 0.2 using the smallest strip width, we can see that it only marginally superior to MFFD$^+$.
 For example, take $\delta = 0.2$ in Table \ref{table:n=500} for $W = 1250$.
-The difference between $r$ for PS and MFFD$^+$ is 0.00829, which translates to less than 2 strips difference between the average number of strips generated by each heuristic.
+The difference between $q$ for PS and MFFD$^+$ is 0.00829, which translates to less than 2 strips difference between the average number of strips generated by each heuristic.
 
-One interesting feature is the reduction of $r$ between $\delta = 0.4$ and $\delta = 0.5$, which is much more significant for $W = 5000$ as opposed to $W = 1250$.
+One interesting feature is the reduction of $q$ between $\delta = 0.4$ and $\delta = 0.5$, which is much more significant for $W = 5000$ as opposed to $W = 1250$.
 The reduction occurs due to an increase in the number of feasible alignments of the items, as every score width is able to be paired with $n-1$ other score widths when $\delta = 0.5$.
 Thus, when $W = 5000$, more items can be packed onto a strip feasibly, resulting in fewer strips in the final solution.
-However, the difference in $r$ is less noticeable for $W = 1250$, as regardless of the increased proportion in possible pairings, the capacity of the strips is much smaller, preventing the collection of items from multiple strips onto one.
+However, the difference in $q$ is less noticeable for $W = 1250$, as regardless of the increased proportion in possible pairings, the capacity of the strips is much smaller, preventing the collection of items from multiple strips onto one.
 
-Although using the average optmality from 1000 instances provides a useful overview of the efficiency of a heuristic, there are other characteristics that we can consider.
+Although using the average solution quality from 1000 instances provides a useful overview of the efficiency of a heuristic, there are other characteristics that we can consider.
 Take, for example, the results obtained with parameters $\delta = 0.7$ and $W = 5000$ in Table \ref{table:n=1000}.
@@
 On the other hand, there were 152 instances in which MFFD$^+$ was able to generate a solution $S$ such that $|\mathcal{S}| = t$, thus implying that there are at least 152 solutions that can be solved to optimality.
-Despite this, MFFD$^+$ has a higher average optimality than PS, suggesting that the variance in the number of strips required is higher.
+Despite this, MFFD$^+$ has a higher average solution quality than PS, suggesting that the variance in the number of strips required is higher.
 
@@
 
-\bibliographystyle{dcu}
+\bibliographystyle{splncs04}
 \bibliography{includes/bibliography}

### 2018-07-10 PAPER/main.tex
started writing procedure for overlapping sets

@@
 	This paper investigates the Score-Constrained Strip-Packing Problem (SCSPP), a combinatorial optimisation problem that generalises the one-dimensional bin-packing problem.
-In the construction of cardboard boxes rectangular items are packed onto strips to be scored by knives prior to being folded.
+In the construction of cardboard boxes, rectangular items are packed onto strips to be scored by knives prior to being folded.
 The order and orientation of the items on the strips determine whether the knives are able to score the items correctly.
@@
 
-Now, one of the following three conditions holds.
+Now, one of the following three cases occurs:
 \begin{enumerate}
@@
 \item Otherwise, it may be that multiple sets need to be used to connect the components of $G'$.
-For two sets $R_i$ and $R_j$ to ``overlap'', each set must have exactly one edge from the same component in $G'$, with the other edges in each set being from different components.
-For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of components $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$ but the other edges in the sets are from different components.
-Therefore, a selection of sets need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the selected sets.
-If such a collection of sets exists, then the components of $G'$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in the collection.
+For two edge sets $R_i$ and $R_j$ to ``overlap'', each set must have exactly one edge from the same component in $G'$, with the other edges in each set being from different components.
+A collection of sets $\mathcal{R}^{*}$ need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the sets.
+If such a collection of sets exists, then the components of $G'$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in $\mathcal{R}^{*}$.
+%For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of components $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$ but the other edges in the sets are from different components.
 \end{enumerate}
 
-\begin{itemize}
-	\item Choose set $R_i$ with the highest cardinality. Call this set $R^{*}_1$. Add this set to $\mathcal{R}$.
-	\item Take original sorted list from beginning of BR, remove edges from list that are in $\mathcal{R}$.
-	\item Go through list again, perform modified BR:
-	\begin{itemize}
-		\item (a) lower-indexed vertex of current edge and higher-indexed vertex of next edge in list are adj via red edge;
-		\item (b) The current edge and an edge in $\mathcal{R}$ are members of the same component, and the next edge is in a component that does not have an edge in $\mathcal{R}$, or vice versa.
-	\end{itemize}	
-	\item If found, add these two edges to set $R^{*}_2$ and add this set to $\mathcal{R}$.
-Continue to add succeeding edges in list to $R^{*}_2$, provided condition (a) holds, and the succeeding edge is a member of a component that does not have an edge in $\mathcal{R}$.
-	\item If no more valid edges, check to see if at least one edge from every component of $G'$ is in $\mathcal{R}$.
-	\item If not, remove edges from $R^{*}_2$ from sorted list, and start again.
-Continue until $\mathcal{R}$ contains sets that overlap and have an edge from every component, or until every edge in the list is assessed and no new set has been created.
-	\item If not all components covered, infeasible, else apply connecting procedure to every individual set in $\mathcal{R}$.
-\end{itemize}
+To find these overlapping sets, the \textsc{Modified Bridge Recognition} (MBR) algorithm is used, which is based on BR.
+Firstly, a copy of the set $R_i$ with the highest cardinality generated by BR is created, called $R^{*}_1$, and is added to $\mathcal{R}^{*}$.
+Then, MBR takes the original sorted list used in BR and removes edges from the list that are already in $\mathcal{R}^{*}$.
+Similarly to BR, MBR proceeds through the list to find an edge that meets the following conditions:
+\begin{enumerate*}[label={(\alph*)}]
+	\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
+	\item the current edge and an edge in $\mathcal{R}^{*}$ are members of the same component of $G'$, and the next edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, or vice versa.
+\end{enumerate*}
+If both conditions hold, the current edge is added to a new set $R^{*}_2$ which is then added to $\mathcal{R}^{*}$.
+MBR continues to add suceeding edges to $R^{*}_2$, provided condition (a) holds and the suceeding edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$.
 
@@
 For example, take $\delta = 0.2$ in Table \ref{table:n=500} for $W = 1250$.
-The difference between $q$ for PS and MFFD$^+$ is 0.00829, which translates to less than 2 strips difference between the average number of strips generated by each heuristic.
+The difference between $q$ for PS and MFFD$^+$ is 0.008, which translates to less than 2 strips difference between the average number of strips generated by each heuristic.
 
@@
 	\item ``BPP becomes easier to solve when the number of items per bin increases, and problems with two or less items per bin are trivial to solve.
-Triplets are proposed to be `the most difficult bin packing instances''' \cite{falkenauer1996}.
+Triplets are proposed to be `the most difficult bin packing instances''' Falkenauer
 	\item Fair comparison, running over 1000 instances (average of 1000 instances)
@@
 	\item anomaly MFFD $n = 1000$, $W = 1250$, $\delta = 0.3$
-	\item harder problems, \cite{falkenauer1996}, triplets, fewer items per strip.
+	\item harder problems, falkenauer, triplets, fewer items per strip.
 	\item cases when opt $\neq 1$: $t$ incorrect, solution produced is not optimal, or both.

### 2018-07-11 PAPER/main.tex
completed MBR explanation and proof of theorem

@@
 \institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK
-\email{hawaa@cardiff.ac.uk}}
+\email{hawaa|lewisr9|thompsonjm1@cardiff.ac.uk}}
 \maketitle
@@
 We then integrate this algorithm with a packing heuristic to address the multi-strip problem and compare with two other greedy heuristics, discussing the circumstances in which each method is superior.
+	\keywords{Strip-Packing \and Heuristics \and Graphs and Networks}
 \end{abstract}
@@
 \end{definition}
-
 For example, given $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, one possible solution is $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.
@@
 	\centering
-	\includestandalone[width=0.7\textwidth]{figures/itemsknife}
+	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
 	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation $(a_i, b_i)$, and a feasible alignment of two items that can be scored simultaneously.}	
@@
 \end{figure}
-Clearly, for two items to be feasibly placed alongside one another on a strip, the distance between the two score lines must be equal to or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
+\noindent Clearly, for two items to be feasibly placed alongside one another on a strip, the distance between the two score lines must be equal to or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations.
 Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.\footnote{Note that the left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and can therefore be ignored.} It follows that there are $\frac{n!}{2}2^n$ distinct arrangements, making complete enumeration infeasible for non-trivial values of $n$.
@@
 Figure \ref{fig:items/aligned} shows the same instance $\mathcal{M}$ used above depicted as a packing problem.
+\textcolor{OrangeRed}{FIGURE 2 HERE.}
 
@@
 
-Observe that in this particular strip-packing problem the widths of the individual items are disregarded, since the aim is to arrange the items onto a single strip of seemingly infinite width.
+\noindent Observe that in this particular strip-packing problem the widths of the individual items are disregarded, since the aim is to arrange the items onto a single strip of seemingly infinite width.
 However, in industrial applications, strips of material will often be provided in fixed widths.
@@
 
-Note that in the special case of $\tau = 0$, the SCSPP is equivalent to the classical one-dimensional bin-packing problem (BPP).
+\noindent Note that in the special case of $\tau = 0$, the SCSPP is equivalent to the classical one-dimensional bin-packing problem (BPP).
 Due to the vicinal sum constraint, the SCSPP not only allocates the items to a strip, but must also determine how to pack the items on each strip.
@@
 
-The remainder of this article is structured as follows: In Section 2, we will detail an exact polynomial-time algorithm for the COP, and show how it is applicable to the subproblem.
+\noindent The remainder of this article is structured as follows: In Section 2, we will detail an exact polynomial-time algorithm for the COP, and show how it is applicable to the subproblem.
 Section 3 then introduces three heuristics that can be used to find feasible solutions to the SCSPP, one of which makes particular use of the exact algorithm from the previous section, and their associated advantages and disadvantages.
@@
 Figure \ref{fig:threshold} illustrates an example construction of $G$.
+\textcolor{OrangeRed}{FIGURE 3 HERE.}
 \begin{figure}[h!]	
@@
 
-Recall that a Hamiltonian cycle on a graph $G$ is a cycle that visits every vertex exactly once.
+\noindent Recall that a Hamiltonian cycle on a graph $G$ is a cycle that visits every vertex exactly once.
 Now, consider the following definition describing a variant of the Hamiltonian cycle problem involving multiple edge sets.
+
 \begin{definition}
@@
 
-It is clear than an alternating Hamiltonian cycle on $G$, if one exists, correpsonds to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ indicates the values that can be placed alongside one another feasibly.
+\noindent It is clear than an alternating Hamiltonian cycle on $G$, if one exists, correpsonds to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ indicates the values that can be placed alongside one another feasibly.
 Also, note that every edge in $B$ must be present in the alternating Hamiltonian cycle.
@@
 
-To find a matching $R' \subseteq R$, the \textsc{Maximum Cardinality Matching} (MCM) algorithm is executed \cite{mahadev1994, becker2010}.
+To find a matching $R' \subseteq R$, the \textsc{Maximum Cardinality Matching} (MCM) algorithm is executed \cite{becker2010,mahadev1994}.
 First, take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest-indexed vertex $v_j$ that is not already incident to an edge in $R'$.
@@
 
+Clearly, if $|R'| < n+1$ after MCM has completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and so no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
+Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex $v_i \in V$ is incident to one blue edge and one red edge, as can be seen in Figure \ref{fig:mps}).
+$G'$ therefore consists of a collection of cyclic components $C_1, C_2, ..., C_l$.
 \begin{figure}	
@@
 
-Clearly, if $|R'| < n+1$ after MCM has completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and so no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
-Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex $v_i \in V$ is incident to one blue edge and one red edge (see Figure \ref{fig:mps}).
-$G'$ therefore consists of a collection of cyclic components $C_1, C_2, ..., C_l$.
-In the case where $G'$ comprises one component, i.e.
+\noindent In the case where $G'$ comprises one component, i.e.
 $l = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP.
 However, if $l > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle.
-To do this, a \textsc{Bridge Recognition} (BR) algorithm can now be executed.
-This operates by selecting suitable edges in $R\backslash R'$ that replace edges in $R'$ in order to connect the components of $G'$.
+To do this, a \textsc{Bridge Recognition} (BR) algorithm is executed that selects suitable edges in $R\backslash R'$ to replace edges in $R'$, in order to connect the components of $G'$.
 
@@
 A collection of sets $\mathcal{R}^{*}$ need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the sets.
-If such a collection of sets exists, then the components of $G'$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in $\mathcal{R}^{*}$.
 %For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of components $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$ but the other edges in the sets are from different components.
@@
 To find these overlapping sets, the \textsc{Modified Bridge Recognition} (MBR) algorithm is used, which is based on BR.
-Firstly, a copy of the set $R_i$ with the highest cardinality generated by BR is created, called $R^{*}_1$, and is added to $\mathcal{R}^{*}$.
+Firstly, a copy of the set $R_i$ with the highest cardinality\footnote{In the event of a tie, MBR selects the set with the lowest index.} generated by BR is created, called $R^{*}_1$, and is added to $\mathcal{R}^{*}$.
 Then, MBR takes the original sorted list used in BR and removes edges from the list that are already in $\mathcal{R}^{*}$.
@@
 If both conditions hold, the current edge is added to a new set $R^{*}_2$ which is then added to $\mathcal{R}^{*}$.
-MBR continues to add suceeding edges to $R^{*}_2$, provided condition (a) holds and the suceeding edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$.
+MBR continues to add suceeding edges to $R^{*}_2$, provided condition (a) holds and the suceeding edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, stopping when an edge that does not meet these conditions is reached.
+Then, if every component of $G'$ has an edge in one of the sets in $\mathcal{R}^{*}$, these sets are able to connect all the components of $G'$ together, and so MBR terminates.
+Otherwise, the edges in $R^{*}_2$ are removed from the sorted list, and MBR repeats the search for suitable edges to start a new set $R^{*}_3$.
+This procedure continues until either $\mathcal{R}^{*}$ contains overlapping sets that cover all components of $G'$, or until there are no more suitable edges in the list to start a new set.
+If MBR has produced a feasible collection of sets then the components of $G'$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in $\mathcal{R}^{*}$.
 
@@
 	\end{subfigure}
-	\caption{Selected edges found using BR merge the components of $G'$ together, forming an alternating Hamiltonian cycle which corresponds to a feasible solution $\mathcal{T} = \langle(1,2), (6,3), (5,3), (4,4), (4,2), (7,1) \rangle$.}
+	\caption{Selected edges found using BR merge the components of $G'$ together, forming an alternating Hamiltonian cycle which corresponds to a solution $\mathcal{T}$.}
 	\label{fig:connect/cycle}
@@
 
-This algorithm, which will be referred to as the \textsc{Alternating Hamiltonian Construction} (AHC) algorithm is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP.
+\noindent This algorithm, which will be referred to as the \textsc{Alternating Hamiltonian Construction} (AHC) algorithm is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP.
 If a solution does indeed exist, AHC can produce this solution in at most $O(n^2)$ time.
@@
 \end{theorem}
+
 \begin{proof}
-	\begin{itemize}
-		\item \textsc{Maximum Cardinality Matching} - $O(n\log n)$ due to initial sorting of vertices.
-		\item \textsc{Bridge Recognition}:
-		\begin{itemize}
-			\item sort edges into list and remove invalid egdes - $O(n \log n)$.
-			\item go through list to put into sets $R_i$, each edge assessed exactly once - $O(n)$.
-			\item check every set $R_i$ to see if $|R_i| = l$, since there must be a minimum of two red/matching edges in a set $R_i$, there can be at most $\frac{n}{2}$ $R_i$ sets created - $O(n)$.
-			\item check overlapping/multiple sets - ?
-		\end{itemize}	
-		\item Connecting Procedure - $n+1$ red edges on $G'$, so maximum every red edge in $R'$ needs to be replaced, $n+1$ edges to replace with edges from sets $R_i$.
-so at most $n+1$ edges need to be added to $G'$ and $n+1$ edges removed (edges added to $R'$ and removed from $R'$) - $O(n)$.
-	\end{itemize}
-	Hence complexity of AHC is $O(n^2)$ time.
+	We shall assess each subprocedure of AHC in turn.
+Firstly, MCM produces a matching set $R' \subseteq R$ in at most $O(n \lg n)$ time due to the sorting of the vertices in lexicographical order.
+In BR, sorting the $n+1$ edges of $R'$ and removing unsuitable edges also requires $O(n \lg n)$ time.
+The sets $R_i$ can be created in $O(n)$ time, as each edge in the list is considered once.
+As each set $R_i$ contains at least two edges, BR can produce up to $\frac{n+1}{2}$ sets.
+Thus, examining each set to find one such that $|R_i| = l$ takes at most $O(n)$ time.
+The same method is used to find the set with the highest cardinality in MBR.
+Since $G'$ comprises a maximum of $\frac{n+1}{2}$ components, it follows that the number of edge sets in $\mathcal{R}^{*}$ needed to connect all the components is bounded by $\frac{n+1}{2}-1$.
+The initial sorted list consists of at most $n-1$ edges, and therefore MBR is of quadratic complexity $O(n^2)$.
+Finally, the connecting procedure replaces up to $n+1$ edges, and so can be executed in $O(n)$ time.
+Consequently, AHC had an overall worst case complexity of $O(n^2)$.
 \qed
@@
 
-That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled (\ref{eqn:vscstrip}).
+\noindent That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled (\ref{eqn:vscstrip}).
 Note that constraints (\ref{eqn:packall}) - (\ref{eqn:capacity}) are the necessary conditions for the BPP.
@@
 
-Tables \ref{table:n=500} and \ref{table:n=1000} compare the results obtained from the three heuristics using the different values of $\delta$ and $W$ for $n = 500$ and 1000 respectively.
+\noindent Tables \ref{table:n=500} and \ref{table:n=1000} compare the results obtained from the three heuristics using the different values of $\delta$ and $W$ for $n = 500$ and 1000 respectively.
 Figures in bold indicate the best average solution quality for the given combination of parameters.

### 2018-07-12 PAPER/main.tex
started conclusion, sorted format, made changes Rhyd suggestions

@@
 \title{Heuristics for the Score-Constrained Strip-Packing Problem}
-\author{Asyl L. Hawa\orcidID{0000-0002-2270-1057} \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
+\author{Asyl L. Hawa \and Rhyd Lewis \and Jonathan M. Thompson}
 \authorrunning{A. L. Hawa et al.}
@@
 The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$ where $a_i + b_i < w_i$, assigned such that $a_i \leq b_i$.
-Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively.
+Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side respectively.
 \begin{figure}[H]	
 	\centering
-	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
+	\includestandalone[width=0.85\textwidth]{figures/itemsknife}
 	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation $(a_i, b_i)$, and a feasible alignment of two items that can be scored simultaneously.}	
@@
 It then follows that the vicinal sum constraint corresponds to the requirement for the sum of adjacent score widths to exceed $\tau$.
-Figure \ref{fig:items/aligned} shows the same instance $\mathcal{M}$ used above depicted as a packing problem.
-\textcolor{OrangeRed}{FIGURE 2 HERE.}
+Figure \ref{fig:items/aligned} shows the same instance $\mathcal{M}$ mentioned earlier depicted as a packing problem.
+
+Observe that in this particular strip-packing problem the widths of the individual items are disregarded, since the aim is to arrange the items onto a single strip of seemingly infinite width.
+However, in industrial applications, strips of material will often be provided in fixed finite widths.
+Given a large problem instance, multiple strips may therefore be required to feasibly accommodate all of the items.
+For this reason, a more generalised problem can also be formulated as follows:
 
@@
 	\centering
-	\begin{subfigure}[h]{0.44\textwidth}
+	\begin{subfigure}[h]{0.5\textwidth}
 		\includestandalone[width=\textwidth]{figures/items}
@@
 	\end{subfigure} 
-	\begin{subfigure}[h]{0.7\textwidth}
+	\begin{subfigure}[h]{0.8\textwidth}
 		\includestandalone[width=\textwidth]{figures/itemsaligned}
@@
 
-\noindent Observe that in this particular strip-packing problem the widths of the individual items are disregarded, since the aim is to arrange the items onto a single strip of seemingly infinite width.
-However, in industrial applications, strips of material will often be provided in fixed widths.
-Given a large problem instance, multiple strips may therefore be required to feasibly accommodate all of the items.
-For this reason, a more generalised problem can also be formulated:
-
 \begin{definition}
@@
 \noindent Note that in the special case of $\tau = 0$, the SCSPP is equivalent to the classical one-dimensional bin-packing problem (BPP).
-Due to the vicinal sum constraint, the SCSPP not only allocates the items to a strip, but must also determine how to pack the items on each strip.
-This involves deciding the order in which the items are packed from left to right, and whether each item should be placed in a regular or rotated orientation.
+When $\tau > 0$, the problem also involves deciding the order in which the items are packed from left to right, and whether each item should be placed in a regular or rotated orientation.
 Thus, we define the following sub-problem associated with the SCSPP.
@@
 
-\noindent The remainder of this article is structured as follows: In Section 2, we will detail an exact polynomial-time algorithm for the COP, and show how it is applicable to the subproblem.
+\noindent The remainder of this article is structured as follows: In Section 2, we will detail an exact polynomial-time algorithm for the COP, and show how it is applicable to the SCPSP.
 Section 3 then introduces three heuristics that can be used to find feasible solutions to the SCSPP, one of which makes particular use of the exact algorithm from the previous section, and their associated advantages and disadvantages.
@@
 \label{sec:ahca}
-We shall now present an exact polynomial-time algorithm for the COP.
-The underlying algorithm was originally proposed by \cite{becker2010}, and is used to determine whether or not a solution exists for a given instance.
+We now present an exact polynomial-time algorithm for the COP.
+The underlying algorithm was originally proposed by Becker in \cite{becker2010}, and is used to determine whether or not a solution exists for a given instance.
 Here, we extend this algorithm so that, if a solution does indeed exist, it is also able to formulate and present us with this final solution.
-This is especially useful for problems such as the strip-packing problem, where a solution is required in order to show how the items should be arranged on a strip.
+This is especially useful for problems such as the strip-packing problem.
 
 Let $\mathcal{M}$ be an instance of the COP with cardinality $n$.
-It is now useful to model $\mathcal{M}$ as a graph $G$ in which each vertex is associated with a single value in $\mathcal{M}$ in non-decreasing order.
+It is useful to model $\mathcal{M}$ as a graph $G$ in which each vertex is associated with a single value in $\mathcal{M}$ in non-decreasing order.
 A pair of vertices, called ``dominating vertices'' are also added to the graph, both of which are assigned values equal to $\tau$.
@@
 As we have seen, the values in $\mathcal{M}$ are arranged in pairs.
-This is represented in $G$ by adding a set of ``blue'' edges, $B$, that contains edges between vertices that are ``partners'', i.e.
+This is represented in $G$ by adding a set of ``blue'' edges, $B$, between vertices that are ``partners'', i.e.
 whose values make up a pair in $\mathcal{M}$.
@@
 Figure \ref{fig:threshold} illustrates an example construction of $G$.
-\textcolor{OrangeRed}{FIGURE 3 HERE.}
 \begin{figure}[h!]	
@@
 	\includestandalone[width=0.6\textwidth]{figures/threshold}
-	\caption{$G = (V, B \cup R)$ using $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$. The corresponding values of each vertex are show in parentheses.}
+	\caption{$G = (V, B \cup R)$ using $\mathcal{M} = \{\{1,2\}, \{1,7\}, \{2,4\}, \{3,5\}, \{3,6\}, \{4,4\}\}$ and $\tau = 7$, where the thinner red edges are in $R$, and the thicker blue edges are in $B$.
+The corresponding values of each vertex are show in parentheses.}
 	\label{fig:threshold}
@@
 \noindent Recall that a Hamiltonian cycle on a graph $G$ is a cycle that visits every vertex exactly once.
-Now, consider the following definition describing a variant of the Hamiltonian cycle problem involving multiple edge sets.
+Now, consider the following definition describing a variant of the Hamiltonian cycle problem involving two edge sets.
 
@@
 
-To find a matching $R' \subseteq R$, the \textsc{Maximum Cardinality Matching} (MCM) algorithm is executed \cite{becker2010,mahadev1994}.
+To find a matching $R' \subseteq R$, the Maximum Cardinality Matching (MCM) algorithm is executed, which is based on \cite{becker2010} and also the earlier work of Mahadev and Peled \cite{mahadev1994}.
 First, take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest-indexed vertex $v_j$ that is not already incident to an edge in $R'$.
@@
 
-Clearly, if $|R'| < n+1$ after MCM has completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and so no feasible solution exists for the given instance $\mathcal{M}$ of the COP.
-Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex $v_i \in V$ is incident to one blue edge and one red edge, as can be seen in Figure \ref{fig:mps}).
-$G'$ therefore consists of a collection of cyclic components $C_1, C_2, ..., C_l$.
+Clearly, if $|R'| < n+1$ after MCM has completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and so no feasible solution exists for the given instance $\mathcal{M}$.
+Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex $v_i \in V$ is incident to one blue edge and one red edge, as can be seen in Figure \ref{fig:mps}.
+$G'$ therefore consists of one or more cyclic components $C_1, C_2, ..., C_l$.
+In the case where $G'$ comprises one component, i.e.
+$l = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP.
+However, if $l > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle.
+To do this, an additional procedure called Bridge Recognition (BR) is executed that selects suitable edges in $R\backslash R'$ to replace edges in $R'$ to connect the components of $G'$.
+
 \begin{figure}	
@@
 	\end{subfigure}
-	\caption{Subgraph $G'= (V, B \cup R')$. When in planar form, it is clear that $l = 2$.}
+	\caption{Subgraph $G'= (V, B \cup R')$ created after MCM. When in planar form, it is clear that $l = 2$.}
 	\label{fig:mps}
@@
 
-\noindent In the case where $G'$ comprises one component, i.e.
-$l = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP.
-However, if $l > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle.
-To do this, a \textsc{Bridge Recognition} (BR) algorithm is executed that selects suitable edges in $R\backslash R'$ to replace edges in $R'$, in order to connect the components of $G'$.
-
-BR operates by first ordering the edges in $R'$ such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order.
+\noindent BR operates by first ordering the edges in $R'$ such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order.
 Any edges that cannot be placed in such an order are then removed from this list.
-For instance, in the example illustrated in Figure \ref{fig:mps}, the edges would be sorted as follows: $(v_1, v_{14}), (v_2, v_{13}),(v_3, v_{12}),(v_4, v_{11}),(v_6, v_{10}),(v_7, v_8)$.
+For instance, in the example in Figure \ref{fig:mps}, the edges would be sorted as follows: $(v_1, v_{14}), (v_2, v_{13}),(v_3, v_{12}),(v_4, v_{11}),(v_6, v_{10}),(v_7, v_8)$.
 Note that, since $v_5$ was not matched with the highest-indexed vertex possible during MCM, the edge $(v_5, v_9)$ does not adhere to the required structure of the list and is therefore omitted.
@@
 \begin{enumerate*}[label={(\alph*)}]
-	\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
+	\item the lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
 	\item the current edge and the next edge are members of different components on $G'$.
@@
 If these conditions are met, BR adds the current edge to a set $R_1$, and continues to add all succeeding edges in the list to $R_1$ provided that, for each edge, both conditions hold and the succeeding edge is not a member of a component of $G'$ that has an edge in $R_1$.
-Once there are no more valid edges available to add to $R_1$, BR resumes its search through the remaining edges in the list to find a new edge that meets the conditions, and can begin a new set $R_2$.
+Once there are no more valid edges available to add to $R_1$, BR resumes its search through the remaining edges in the list to find another edge that meets the conditions, and can begin a new set $R_2$.
 The procedure terminates once the penultimate edge in the list has been assessed.
@@
 $G'$ then consists of a single alternating Hamiltonian cycle; hence a solution has been found.
-% add edges (v_i, m(v_{i+1})) for i \in {1, 2, ..., |R_i| -1} from R to R', and then the edge (v_{|R_i|}, m(v_1)) from R to R'
 
@@
 For two edge sets $R_i$ and $R_j$ to ``overlap'', each set must have exactly one edge from the same component in $G'$, with the other edges in each set being from different components.
-A collection of sets $\mathcal{R}^{*}$ need to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the sets.
-%For example, if $R_1$ has two edges, one from component $C_1$ and one from component $C_2$, and $R_2$ has three edges that are members of components $C_2$, $C_3$ and $C_4$, then $R_1$ and $R_2$ are said to overlap, since they each possess an edge $C_2$ but the other edges in the sets are from different components.
+A collection of sets $\mathcal{R}^{*}$ therefore needs to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the sets.
 \end{enumerate}
 
-To find these overlapping sets, the \textsc{Modified Bridge Recognition} (MBR) algorithm is used, which is based on BR.
+To find these overlapping sets, a Modified Bridge Recognition (MBR) algorithm is used, which is based on BR.
 Firstly, a copy of the set $R_i$ with the highest cardinality\footnote{In the event of a tie, MBR selects the set with the lowest index.} generated by BR is created, called $R^{*}_1$, and is added to $\mathcal{R}^{*}$.
@@
 	\item $(v_3, v_{11}) \in R$, i.e. the lower-indexed vertex of the first edge is adjacent to the higher-indexed vertex of the next edge; and
-	\item the edges are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$ as seen in Figure \ref{fig:mps}).
+	\item the edges are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$ as shown previously in Figure \ref{fig:mps}).
 \end{enumerate*}
@@
 $(v_4, v_{12}) \in R$, since the value associated with $v_{12}$ is greater than or equal to the value associated with $v_{11}$.
-Then, because $|R_1| = l$, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are removed from $R'$ and replaced by the edges $(v_3, v_{11})$ and $(v_4, v_{12})$ from $R_1$, as shown in Figure \ref{fig:connect/cycle}.
+Then, because $|R_1| = l$, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are removed from $R'$ and replaced by the edges $(v_3, v_{11})$ and $(v_4, v_{12})$ from $R_1$, as illustrated in Figure \ref{fig:connect/cycle}.
 Removing the dominating vertices and any incident edges results in an alternating Hamiltonian path, which corresponds to a feasible solution $\mathcal{T}$.
@@
 	\centering
-	\begin{subfigure}[H]{0.57\textwidth}
+	\begin{subfigure}[H]{0.65\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpsconnect}
@@
 	\end{subfigure}
-	\begin{subfigure}[H]{0.57\textwidth}
+	\begin{subfigure}[H]{0.65\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpscycle}
@@
 	\end{subfigure}
-	\begin{subfigure}[H]{0.6\textwidth}
+	\begin{subfigure}[H]{0.75\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpspath}
@@
 
-\noindent This algorithm, which will be referred to as the \textsc{Alternating Hamiltonian Construction} (AHC) algorithm is able to deduce whether a feasible solution $\mathcal{T}$ exists for any given instance $\mathcal{M}$ of the COP.
-If a solution does indeed exist, AHC can produce this solution in at most $O(n^2)$ time.
-% Cite Becker
+\noindent The entire algorithm that has been described will be referred to as the Alternating Hamiltonian Construction (AHC) algorithm.
+The time complexity of AHC is quadratic, as stated in the following theorem:
 
@@
 	\label{thm:copsoln}
-	If there exists an alternating Hamiltonian cycle on a graph $G$ created from an instance $\mathcal{M}$ of the COP, AHC is able to find the cycle in at most $O(n^2)$ time.
+	Let $G=(V, B \cup R)$ be a graph created from an instance $\mathcal{M}$ of cardinality $n$ of the COP. Then, AHC terminates in at most $O(n^2)$ time.
 \end{theorem}
@@
 \begin{proof}
-	We shall assess each subprocedure of AHC in turn.
+	We assess each subprocedure of AHC in turn.
 Firstly, MCM produces a matching set $R' \subseteq R$ in at most $O(n \lg n)$ time due to the sorting of the vertices in lexicographical order.
@@
 The sets $R_i$ can be created in $O(n)$ time, as each edge in the list is considered once.
-As each set $R_i$ contains at least two edges, BR can produce up to $\frac{n+1}{2}$ sets.
+As each set $R_i$ contains at least two edges, BR will produce up to $\frac{n+1}{2}$ sets.
 Thus, examining each set to find one such that $|R_i| = l$ takes at most $O(n)$ time.
-The same method is used to find the set with the highest cardinality in MBR.
+The same method is also used to find the set with the highest cardinality in MBR.
 Since $G'$ comprises a maximum of $\frac{n+1}{2}$ components, it follows that the number of edge sets in $\mathcal{R}^{*}$ needed to connect all the components is bounded by $\frac{n+1}{2}-1$.
@@
 In this section, we now turn our attention to the multi-strip version of the problem.
-As mentioned in the introduction, the SCSPP is a generalisation of the BPP in that we also require the sum of every pair of adjacent score widths to be greater than or equal to a minimum scoring distance $\tau$.
+As mentioned in the introduction, the SCSPP is a generalisation of the one-dimensional BPP in that we also require the sum of every pair of adjacent score widths to be greater than or equal to a minimum scoring distance $\tau$.
 It follows that the SCSPP is at least as hard as the BPP, which is known to be NP-hard \cite{garey1979}, and so (under the assumption that $P \neq NP$) there is no known algorithm that is able to find an optimal solution for every instance of the SCSPP in polynomial time.
@@
 \noindent That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled (\ref{eqn:vscstrip}).
-Note that constraints (\ref{eqn:packall}) - (\ref{eqn:capacity}) are the necessary conditions for the BPP.
+Note that constraints (\ref{eqn:packall})--(\ref{eqn:capacity}) are the necessary conditions for the BPP.
 An optimal solution $\mathcal{S}$ for the SCSPP is a solution that consists of the fewest number of strips $k$ needed to feasibly contain the $n$ items in the given problem instance.
@@
 $t = \ceil*{\sum_{i=1}^{n}w_i / W}$ which can be computed in $O(n)$ time \cite{martello1990b}.
-Perhaps the simplest and most well-known heuristic for packing problems is \textsc{First-Fit} (FF), a greedy online algorithm that places each item presented in some arbitrary order onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
+
+Perhaps the simplest and most well-known heuristic for one-dimensional bin packing problems is First-Fit (FF), a greedy online algorithm that places each item, presented in some arbitrary order, onto the lowest-indexed strip such that the capacity of the strip is not exceeded.
 It is known that there always exists at least one ordering of the items such that FF produces an optimal solution \cite{lewis2009}.
-A minor modification to FF yields the \textsc{First-Fit Decreasing} (FFD) heuristic, which sorts the items in non-increasing order of size prior to performing FF.
+A minor modification to FF yields the First-Fit Decreasing (FFD) heuristic, which sorts the items in non-increasing order of size prior to performing FF.
 In 1973, Johnson \cite{johnson1973} showed that FFD is guaranteed to return a solution that uses no more than $\frac{11}{9}k + 4$ strips.
@@
 One obvious difference is the order in which the items appear on the strips.
-The order of the items in the BPP is unimportant, however in the SCSPP the items must be ordered in a way that meets the vicinal sum constraint.
-In addition, removing an item from a binin the BPP retains the feasibility of the bin, whereas in the SCSPP this is not guaranteed, as it may leave a subset of items for which the vicinal sum constraint is not satisfied.
+The order of the items in the BPP is unimportant; however in the SCSPP the items must be ordered in a way that meets the vicinal sum constraint.
+In addition, removing an item from a bin in the BPP retains the feasibility of the bin, whereas in the SCSPP this is not guaranteed, as it may leave a subset of items for which the vicinal sum constraint is not satisfied.
 Furthermore, the theoretical minimum $t$ has the potential to be less accurate for the SCSPP, as the minimum scoring distance $\tau$ is not considered.
 For example, if the minimum scoring distance is greater than twice the largest score width, then it is clear that $n$ strips will be required, regardless of the items' widths.
-% Time complexity for FFD also inaccurate
 
-To gain an understanding of this problem, three heuristics for the SCSPP have been developed for our tests: a basic FFD heuristic with a simple modification; a heuristic that packs strips individually and prioritises score widths; and a powerful version of FFD that incorporates the polynomial-time AHC algorithm.
+To gain an understanding of this problem, three heuristics for the SCSPP have been developed: a basic FFD heuristic with a simple modification; a heuristic that packs strips individually and prioritises score widths; and a more advanced version of FFD that incorporates the polynomial-time AHC algorithm.
 
-The first heuristic is the \textsc{Modified First-Fit Decreasing} (MFFD) heuristic which acts in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip.
+The first heuristic is the Modified First-Fit Decreasing (MFFD) heuristic which acts in the same manner as the original FFD, attempting to place each item onto the end of the lowest-indexed strip.
 If an item is able to be packed onto a strip without exceeding the strip's capacity, MFFD then checks to see if the vicinal sum constraint is met between the right-most score on the strip and one of the score widths on the current item.
 If the constraint is met, MFFD places the item on the end of the strip in the appropriate orientation, otherwise the next strip is considered.
+The most prominent issue with this heuristic is due to the items being placed on the end of the strips.
+Although an item could potentially be packed in a different location on the strip other than the end, it may end up being placed on another strip, or perhaps even begin a new strip, thus increasing the number of strips in the final solution.
 
-Despite the additional step, MFFD is a very fast heuristic, as checking the vicinal sum constraint in this way can be performed in constant time.
-The most prominent issue with this heuristic, however, is due to the items being placed on the end of the strips.
-Although an item may not meet the constraint when placed on the end of a strip, there may be another location on the strip where the item can be placed feasibly.
-MFFD is incapable of placing items anywhere other than on the end of the strips, and so an item that could potentially be packed must be placed on another strip, or perhaps even begin a new strip, thus increasing the number of strips in the final solution.
-
-The next heuristic is the \textsc{Pair-Smallest} (PS) heuristic, which is an extension of an inexact procedure defined by \cite{lewis2011}.
+The next heuristic is the Pair-Smallest (PS) heuristic, which is an extension of an inexact procedure defined by Lewis et al.
+\cite{lewis2011}.
 Unlike MFFD, which packs each item in turn, PS focusses on packing one strip at a time, only starting a new strip once the current strip is unable to accommodate any further items.
@@
 This heuristic aligns the smallest score widths with the largest ones, eliminating the possibility of placing larger score widths together unecessarily.
-Note that PS prioritises the vicinal sum constraint over the item widths, choosing to fulfil the constraint first before considering whether the item can be accommodated.
-%If there are multiple items with equal score widths, break ties by choosing the item whose second score width is the largest.
-% If item with smallest feasible score width does not fit onto the strip, choose item with next smallest score width and repeat.
+Note that PS therefore prioritises the vicinal sum constraint over the item widths, choosing to fulfil this constraint first before considering whether the item can actually be accommodated.
+Consequently, there is no use for a procedure such as AHC to find a feasible arrangement of the items.
 
-The last heuristic, \textsc{Modified First-Fit Decreasing with AHC} (MFFD$^+$), incorporates the AHC algorithm from Section \ref{sec:ahca}.
+The last heuristic, Modified First-Fit Decreasing with AHC (MFFD$^+$), incorporates the AHC algorithm from Section \ref{sec:ahca}.
 It operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.
-However, rather than attempting to place the item onto the right-most side of the strip, MFFD$^+$ executes AHC on the items.
+However, rather than attempting to place the item onto the right-most side of the strip, MFFD$^+$ executes AHC on all items on the strip.
 If AHC finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next strip.
@@
 Strips of widths $W = 5000$, 2500 and 1250 were used to influence the number of items per strip.
+As the width of the strips decrease, the average number of items per strip also decreases, making the problem more constrained.
 Both the items and the strips have equal height of $H = 1$.
-Similarly to experiments performed by \cite{lewis2011}, we also introduced a parameter $\delta$ to denote the proportion of pairs of score widths from different items that meet the vicinal sum constraint, i.e.
+Similarly to experiments performed in \cite{lewis2011}, we also introduced a parameter $\delta$ to denote the proportion of pairs of score widths from different items that meet the vicinal sum constraint, i.e.
 whose sum is greater than or equal to $\tau$.
-Values of $\delta$ from 0.0 to 1.0 were created by changing the value of the minimum scoring distance $\tau$.
-Clearly, when $\delta = 0.0$, there are no score widths that can be packed together feasibly, and so $n$ strips will be required (one for each item), whereas if $\delta = 1.0$ all pairs of score widths meet the constraint, and the problem is equivalent to the BPP.
-(As the width of the strips decrease, the average number of items per strip also decreases, making the problem more constrained.)
+Values of $\delta$ from 0.0 to 1.0 were created by changing the value of $\tau$.
+Clearly, when $\delta = 0.0$, there are no items that can be packed together feasibly, and so $n$ strips will be required (one for each item), whereas if $\delta = 1.0$ all pairs of score widths meet the constraint, and the problem is equivalent to the BPP.
 
-The heuristics were implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 3.30GHz processor.
-Our source code and all data is available at \cite{hawa2018}.
-Since optimal solutions are not available, the solution quality $q$ is estimated by comparing to the theoretical minimum $t$, i.e.
-$q = |\mathcal{S}| / t$.
-We calculated the average solution quality of each heuristic for every combination of $n$, $\delta$, and $W$ from 1000 instances.
-All individual trials were executed in under 160ms.
+The heuristics were implemented in C++ and executed on a computer with an Intel Core i3-2120 3.30GHz processor.
+Our source code and all data is provided at \cite{hawa2018}.
+Since optimal solutions are not available, in our case solution quality $q$ is estimated by comparing to the theoretical minimum, $q = |\mathcal{S}| / t$.
+For each heuristics, we calculated the average solution quality for every combination of $n$, $\delta$, and $W$ from 1000 instances.
+All individual trials were seen to complete in under 160ms.
 
-\begin{table}[!htb]
+\begin{table}[h!]
 	\centering
-	\caption{Average solution quality for $n = 500$. The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.475, 4.310, and 2.165 respectively.}
+	\caption{Average solution quality $q$ for $n = 500$.}
 	\begin{tabular}{@{}c@{\hspace{15pt}}c@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}c@{}}\toprule
@@
 \end{table}
+%The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.475, 4.310, and 2.165 respectively.
 
-\begin{table}[!htb]
+\begin{table}[h!]
 	\centering
-	\caption{Average solution quality for $n = 1000$. The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.621, 4.329 and 2.169 respectively.}
+	\caption{Average solution quality $q$ for $n = 1000$.}
 	\begin{tabular}{@{}c@{\hspace{15pt}}c@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}c@{}}\toprule
@@
 \end{table}
+% The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.621, 4.329 and 2.169 respectively.
 
-\noindent Tables \ref{table:n=500} and \ref{table:n=1000} compare the results obtained from the three heuristics using the different values of $\delta$ and $W$ for $n = 500$ and 1000 respectively.
+\noindent Tables \ref{table:n=500} and \ref{table:n=1000} compare the results obtained from the three heuristics using the different values of $\delta$ and $W$, for $n = 500$ and 1000 respectively.
 Figures in bold indicate the best average solution quality for the given combination of parameters.
-We see that $q$ tends toward 1 as $\delta$ increases since the proportion of score widths meeting the vicinal sum constraint increases, allowing more items per strip and reducing the number of strips required.
-Note that when $\delta = 1.0$ MFFD and MFFD$^+$ have identical solution qualities, as the instances are equivalent to the original BPP ($\tau = 0$) and so they operate in the same fashion as the original FFD heuristic.
+We see that $q$ tends toward 1 as $\delta$ increases since the proportion of score widths meeting the vicinal sum constraint increases, allowing more items per strip\footnote{The average number of items per strip when $n = 500$ for $W = 5000$, 2500 and 1250 are 8.475, 4.310, and 2.165 respectively, and the average number of items per strip when $n = 1000$ for $W = 5000$, 2500 and 1250 are 8.621, 4.329, and 2.169 respectively.} and reducing the number of strips required.
+Note that when $\delta = 1.0$ MFFD and MFFD$^+$ have identical solution qualities, as the instances are equivalent to the original BPP ($\tau = 0$); hence they operate in the same fashion as the original FFD heuristic.
 
-Looking at results for both $n = 500$ and 1000, there is a clear pattern with respect to $q$ across all widths and proportion levels.
+Looking at results for both $n = 500$ and 1000, we see there is a clear pattern with respect to $q$ across all widths and proportion levels.
 PS has the best solution quality for a wider range of $\delta$ when the strips are wider, and a much smaller range when the strip width decreases.
@@
 For example, take $\delta = 0.2$ in Table \ref{table:n=500} for $W = 1250$.
-The difference between $q$ for PS and MFFD$^+$ is 0.008, which translates to less than 2 strips difference between the average number of strips generated by each heuristic.
-
-One interesting feature is the reduction of $q$ between $\delta = 0.4$ and $\delta = 0.5$, which is much more significant for $W = 5000$ as opposed to $W = 1250$.
-The reduction occurs due to an increase in the number of feasible alignments of the items, as every score width is able to be paired with $n-1$ other score widths when $\delta = 0.5$.
-Thus, when $W = 5000$, more items can be packed onto a strip feasibly, resulting in fewer strips in the final solution.
-However, the difference in $q$ is less noticeable for $W = 1250$, as regardless of the increased proportion in possible pairings, the capacity of the strips is much smaller, preventing the collection of items from multiple strips onto one.
+The difference between $q$ for PS and MFFD$^+$ is 0.008, which translates to fewer than 2 strips difference between the average number of strips generated by each heuristic.
+In this particular instance, PS and MFFD$^+$ produced 303 and 305 strips on average, respectively.
 
@@
 Clearly PS obtains solutions with the fewest strips on average, however, we noted that out of the 1000 instances, PS did not produce a single solution containing $t$ strips.
-On the other hand, there were 152 instances in which MFFD$^+$ was able to generate a solution $S$ such that $|\mathcal{S}| = t$, thus implying that there are at least 152 solutions that can be solved to optimality.
+On the other hand, there were 152 instances in which MFFD$^+$ was able to generate a solution $S$ such that $|\mathcal{S}| = t$, thus implying that there are at least 152 instances that can be solved to optimality.
 Despite this, MFFD$^+$ has a higher average solution quality than PS, suggesting that the variance in the number of strips required is higher.
 
-\begin{enumerate}
-	\item MFFD and MFFD$^+$ able to obtain opts $\leq 1\%$ of $t$, PS is not.
-	\item PS never best $\delta \geq 0.8$.
-	\item Significant difference in opt, $n = 1000$, $W = 1250$, $\delta = 0.6$, difference between MFFD$^+$ and PS opts is 0.10912 (MFFD$^+$ better), which amounts to an average difference of over 50 strips in solns produced.
-	\item anomaly MFFD $n = 1000$, $W = 1250$, $\delta = 0.3$
-	\item harder problems, \cite{falkenauer1996}, triplets, fewer items per strip, further from 1 when shorter strips.
-	\item cases when opt $\neq 1$: $t$ incorrect, solution produced is not optimal, or both.
-	\item less than 10\% past $\delta = 0.8$
-\end{enumerate}
+\section{Conclusions and Further Work}
+This paper introduced a strip-packing problem with score constraints, where the order and orientation of the items is crucial to the feasibility of the solution.
+We shown that a solution can be found for the single-strip version of the problem in polynomial-time by modelling the problem graphically and using the concept of Hamiltonian cycles.
+Thus, our main problem was to tackle the multi-strip problem.
+Three heuristics, one of which included the exact algorithm for the single-strip problem, were described, and thorough experiments using a variety of parameters were executed.
 
-\section{Conclusions and Further Work}
+\begin{comment}
 \begin{itemize}
@@
 	\item lower bound for the optimal number of strips SCSPP
-	\item \cite{miller1960} TSP returning to base
+	\item cite miller1960 TSP returning to base
 	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution.
@@
 	\item if sets dont have feasible solution, try swapping items between sets
-	\item initial tests, Becker theorem 6 2015 paper \cite{garraffa2016}
+	\item initial tests, Becker theorem 6 2015 paper cite garraffa2016
 	\item minimise waste on each strip, not just number of strips
 \end{itemize}
-
-\begin{comment}
-\begin{itemize}
-\item This paper addresses a generalisation of the one-dimensional bin-packing problem
-\item Paper investigates the SCSPP, a combinatorial optimisation problem that generalises 1dbpp/ problem related to the 1dbpp/with applications in the cutting and packing industries/assoc with the csp.
-\item Rectangular items scored to create/construct cardboard boxes
-\item Items packed onto strips in order to be scored to aid construction of boxes
-\item Feasible alignment/order and orientation of items
-\item Graph theory/networks/hamiltonian cycles
-\item Scored prior to being folded
-\item Feasible alignment prior to being scored
-\item Initially, detail exact p-time alg for COP, illustrate how to use for single strip problem/finding alignment of items on a single strip
-\item Multistrip version, integrate with well known heuristic, compare with other greedy heuristics, show effectiveness/cases in which superior
-\item Related to 1DBPP
-
-\item ``during the process of producing boxes, flat papers are prepared for folding by being scored with knives''
-\item ``min distance between knives can be kept''
-\item ``first, alg for COP and show how used for single strip feasible arrangement''
-\item ``then go on to examine how alg can combine to tackle multi-strip version of problem - closely related to 1DBPP''
-\item discuss problems that arise
-\item variant/generalisation of the 1DBPP ``in which both the ordering and orientation of items in a container influences the validity and quality of a solution''
-\item ``problem that requires the cutting and scoring of rectangular pieces of cardboard in the construction of boxes''
-\item ``highlight the circumstances under which each scheme is advantageous''
-\end{itemize}
-\end{comment}
-
-\begin{comment}
-\begin{itemize}
-	\item ``BPP becomes easier to solve when the number of items per bin increases, and problems with two or less items per bin are trivial to solve.
-Triplets are proposed to be `the most difficult bin packing instances''' Falkenauer
-	\item Fair comparison, running over 1000 instances (average of 1000 instances)
-	\item Note that MFFD and MFFD$^+$ perform identically when $\delta = 1.0$, as they both perform in exactly the same manner as the original FFD heuristic  
-	\item All instances completed in less than 160ms
-	\item PS is not able to reach highest optimality in any case from $\delta = 0.8$ onwards.
-	\item If optimality = 1 then lower bound reached
-	\item state that bold is best optimality
-	\item PS never obtains best avg optimality at  $\delta = 1.0$ in any case
-	\item As W decreases, i.e. items/strip decreases, PS becomes less efficient, mffd+ better
-	\item n = 1000 W = 1250 PS doesnt obtain soln $<$ 10\% for any value of $\delta$
-	\item mffd+ $<$ 10\% for $\delta = 0.8$ onwards in all cases
-	\item mffd+ and mffd+ able to get $<$ 10\% for W = 1250 for n = 100 and 500 $\delta = 0.5$, and n = 1000 $\delta = 0.4$ onwards
-	\item PS never obtains avg solns $<$ 1\% in any case
-	\item In a few cases, mffd+ able to get avg opt $<$ 1\% for smaller values of $\delta$ than mffd.
-	\item PS able to get $<$ 10\% for $\delta = 0.6$ onwards in n= 100, 500, 1000, and W=5000,2500, but reduces significantly when W = 1250.
-	\item First row is avg number of items per strip.
-\end{itemize}
-\end{comment}
-
-\begin{comment}
-\begin{table}[!htb]
-	\centering
-	\ra{1.2}
-	\caption{Average optimality ratios for $|\mathcal{I}| = 100$. Average $t$ for $W = 5000$, 2500 and 1250 are 11.993, 23.478, and 46.466 respectively.}
-	\begin{tabular}{@{}c@{\hspace{25pt}}c@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}ccc@{\hspace{8pt}}c@{\hspace{8pt}}c@{}}\toprule
-		& \multicolumn{3}{c}{$W = 5000$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 2500$} & \phantom{abcd} & \multicolumn{3}{c}{$W = 1250$} \\
-		\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
-		$\delta$ & MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$ && MFFD & PS & MFFD$^+$\\ \midrule
-		0.0	& 8.35709 & 8.35709 & 8.35709 && 4.26800 & 4.26800 & 4.26800 && 2.15624 & 2.15624 & 2.15624 \\
-		0.1	& 5.27284 & \textbf{4.89963} & 5.14404 && 2.72299 & \textbf{2.48800} & 2.69191 && 1.53147 & \textbf{1.51049} & 1.52968 \\
-		0.2	& 4.16155 & \textbf{3.46467} & 3.98645 && 2.21096 & \textbf{1.87449} & 2.16338 && 1.34812 & \textbf{1.34499} & 1.34593 \\
-		0.3	& 3.27805 & \textbf{2.40153} & 3.05546 && 1.82199 & \textbf{1.43724} & 1.75610 && 1.22453 & 1.24810 & \textbf{1.21994} \\
-		0.4	& 2.61641 & \textbf{1.63390} & 2.33662 && 1.54989 & \textbf{1.16887} & 1.46534 && 1.14507 & 1.19631 & \textbf{1.13979} \\
-		0.5	& 2.08260 & \textbf{1.13827} & 1.77494 && 1.35101 & \textbf{1.04978} & 1.25567 && 1.09274 & 1.17069 & \textbf{1.08661} \\
-		0.6 & 1.65897 & \textbf{1.02027} & 1.36093 && 1.20040 & \textbf{1.03720} & 1.11964 && 1.06255 & 1.15766 & \textbf{1.05701} \\
-		0.7	& 1.32002 & \textbf{1.01350} & 1.11348 && 1.09659 & \textbf{1.03556} & 1.04569 && 1.04546 & 1.14416 & \textbf{1.04150} \\
-		0.8	& 1.10725 & \textbf{1.01384} & 1.02188 && 1.03577 & 1.03439 & \textbf{1.01696} && 1.03711 & 1.12951 & \textbf{1.03565} \\
-		0.9	& 1.02134 & 1.01315 & \textbf{1.00646} && 1.01364 & 1.03285 & \textbf{1.01029} && 1.03434 & 1.11631 & \textbf{1.03416} \\
-		1.0 & \textbf{1.00480} & 1.01302 & \textbf{1.00480} && \textbf{1.00919} & 1.03261 & \textbf{1.00919} && \textbf{1.03393} & 1.10807 & \textbf{1.03393} \\
-		\bottomrule
-	\end{tabular}	
-	\label{table:n=100}
-\end{table}
-\end{comment}
-
-\begin{comment}
-\textbf{$n$ = 100}
-\begin{itemize}
-	\item Average total item width = 57466.776, $\sigma$ = 2499.06092
-	\item $W = 5000$, Average LB = 11.993, $\sigma$ = 0.56829, i/s = 8.3333
-	\item $W = 2500$, Average LB = 23.478, $\sigma$ = 1.05618, i/s = 4.1667
-	\item $W = 1250$, Average LB = 46.466, $\sigma$ = 2.02703, i/s = 2.1277
-\end{itemize}
-
-\textbf{$n$ = 500}
-\begin{itemize}
-	\item Average total item width = 287683.855, $\sigma$ = 5434.63046
-	\item $W = 5000$, Average LB = 58.039, $\sigma$ = 1.12227, i/s = 8.4746
-	\item $W = 2500$, Average LB = 115.571, $\sigma$ = 2.18150, i/s = 4.3103
-	\item $W = 1250$, Average LB = 230.648, $\sigma$ = 4.35041, i/s = 2.1645
-\end{itemize}
-
-\textbf{$n$ = 1000}
-\begin{itemize}
-	\item Average total item width = 575163.174, $\sigma$ = 7880.93401
-	\item $W = 5000$, Average LB = 115.534, $\sigma$ = 1.59463, i/s = 8.6207
-	\item $W = 2500$, Average LB = 230.563, $\sigma$ = 3.16734, i/s = 4.3290
-	\item $W = 1250$, Average LB = 460.623, $\sigma$ = 6.30895, i/s = 2.1692
-\end{itemize}
-
-\end{comment}
-
-\begin{comment}
-	\begin{enumerate}
-	\item Opt ratios tend to 1 as $\delta \to 1$, as the problem instances become easier to solve, more feasible alignments of pairs of items, more items per strip, reducing the need for more strips, closer to BPP.
-	\item $\delta = 0.0$ $n$ strips required, hence all ratios equal.
-	\item $\delta = 1.0$,  MFFD and MFFD$^+$ obtain identical opts, since (described above) instance is equivalent to original BPP, $\tau = 0$, so MFFD and MFFD$^+$ perform in the same fashion as original FFD.
-	\item Pattern, PS best for wider range of $\delta$ when $W$ high, and smaller range (only 0.1-0.2) when $W = 1250$.
-	\item Conversely, MFFD$^+$ best when $W$ small for wider range of $\delta$.
-	\item Note that although PS best for 0.1-0.2, difference is negligible, e.g. $n = 500$, $\delta = 0.2$, difference in opt is 0.00829, translates to less than 2 strips difference on average.
-	\item MFFD and MFFD$^+$ able to obtain opts $\leq 1\%$ of $t$, PS is not.
-	\item PS never best $\delta \geq 0.8$.
-	\item $n = 1000$, $W = 5000$, $\delta = 0.7$, PS is best opt, however PS does not produce a single solution containing $t$ strips, whereas there are 152 instances in which MFFD$^+$ produces solutions containing $t$ strips, i.e.
-there are at least 152 instances out of the 1000 where $k = t$, and PS cannot obtain any.
-Therefore, MFFD$^+$ solutions must vary significantly (i.e.
-some solns that are much worse than optimal), as PS is best opt.
-	\item Significant difference in opt, $n = 1000$, $W = 1250$, $\delta = 0.6$, difference between MFFD$^+$ and PS opts is 0.10912 (MFFD$^+$ better), which amounts to an average difference of over 50 strips in solns produced.
-	\item Noticable drop in opts between $\delta = 0.4$ and $\delta = 0.5$ when $W$ high, as capacity not main concern, more items can now be placed next to one another, so number of strips reduces dramatically, however when $W = 1250$ there is still a capacity issue, regardless of the increased proportion of possible pairings.
-	\item anomaly MFFD $n = 1000$, $W = 1250$, $\delta = 0.3$
-	\item harder problems, falkenauer, triplets, fewer items per strip.
-	\item cases when opt $\neq 1$: $t$ incorrect, solution produced is not optimal, or both.
-	\item less than 10\% past $\delta = 0.8$
-	\end{enumerate}
 \end{comment}

### 2018-07-13 PAPER/main.tex
made changes to section 2, table

@@
 	\label{defn:althamcycle}
-	Let $G(V, B\cup R)$ be an undirected graph, where each edge is a member of one of two sets, $B$ or $R$.
+	Let $G(V, B\cup R)$ be a simple, undirected graph where each edge is a member of one of two sets, $B$ or $R$.
 $G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such that successive edges alternate between sets $B$ and $R$.
@@
 
-\noindent It is clear than an alternating Hamiltonian cycle on $G$, if one exists, correpsonds to a feasible solution, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ indicates the values that can be placed alongside one another feasibly.
+\noindent It is clear that an alternating Hamiltonian cycle on $G$, if one exists, correpsonds to a feasible solution $\mathcal{T}$, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ indicates the values that meet the vicinal sum constraint, and thus can be placed alongside one another feasibly.
 Also, note that every edge in $B$ must be present in the alternating Hamiltonian cycle.
 Consequently, the task can also be seen as finding a matching $R' \subseteq R$ of cardinality $n+1$ such that the edge sets $B$ and $R'$ form an alternating Hamiltonian cycle as described in Definition \ref{defn:althamcycle}.
+
 The problem of finding an alternating Hamiltonian cycle on general graphs is NP-hard as it generalises the classical Hamiltonian cycle problem \cite{haggkvist1977}.
@@
 
-To find a matching $R' \subseteq R$, the Maximum Cardinality Matching (MCM) algorithm is executed, which is based on \cite{becker2010} and also the earlier work of Mahadev and Peled \cite{mahadev1994}.
+To find a suitable matching $R' \subseteq R$, the Maximum Cardinality Matching (MCM) algorithm is executed, which is based on \cite{becker2010} and also the earlier work of Mahadev and Peled \cite{mahadev1994}.
 First, take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest-indexed vertex $v_j$ that is not already incident to an edge in $R'$.
-Now add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed.
+Now, add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed.
 The two vertices incident to each matching edge in $R'$ are now referred to as being ``matched''.
@@
 \end{enumerate*}
-Then, $v_i$ is matched with the vertex that is currently matched with $v_{i-1}$, and $v_{i-1}$ is rematched with $p(v_i)$. The complexity of MCM is $O(n \lg n)$ time \cite{mahadev1994}.
+Then, $v_i$ is matched with the vertex that is currently matched with $v_{i-1}$, and $v_{i-1}$ is rematched with $p(v_i)$.
+Due to the initial order of the vertices, MCM is guaranteed to produce a maximum cardinality matching.
 
-Clearly, if $|R'| < n+1$ after MCM has completed, there are insufficient red edges to form an alternating Hamiltonian cycle, and so no feasible solution exists for the given instance $\mathcal{M}$.
+Clearly, if $|R'| < n+1$ after MCM has completed, there are an insufficient number of red edges to form an alternating Hamiltonian cycle, and therefore no feasible solution exists for the given instance $\mathcal{M}$.
 Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex $v_i \in V$ is incident to one blue edge and one red edge, as can be seen in Figure \ref{fig:mps}.
 $G'$ therefore consists of one or more cyclic components $C_1, C_2, ..., C_l$.
-In the case where $G'$ comprises one component, i.e.
-$l = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP.
-However, if $l > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle.
-To do this, an additional procedure called Bridge Recognition (BR) is executed that selects suitable edges in $R\backslash R'$ to replace edges in $R'$ to connect the components of $G'$.
 
@@
 
-\noindent BR operates by first ordering the edges in $R'$ such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order.
+\noindent In the case where $G'$ comprises one component, i.e.
+$l = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP.
+However, if $l > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle.
+To do this, an additional procedure called Bridge Recognition (BR) is executed that selects suitable edges in $R\backslash R'$ to replace edges in $R'$ to connect the components of $G'$.
+
+BR operates by first ordering the edges in $R'$ such that the lower-indexed vertices of each edge are in increasing order and the higher-indexed vertices are in decreasing order.
 Any edges that cannot be placed in such an order are then removed from this list.
@@
 
-To find these overlapping sets, a Modified Bridge Recognition (MBR) algorithm is used, which is based on BR.
+\noindent To find these overlapping sets, a Modified Bridge Recognition (MBR) algorithm is used, which is based on BR.
 Firstly, a copy of the set $R_i$ with the highest cardinality\footnote{In the event of a tie, MBR selects the set with the lowest index.} generated by BR is created, called $R^{*}_1$, and is added to $\mathcal{R}^{*}$.
@@
 $(v_4, v_{12}) \in R$, since the value associated with $v_{12}$ is greater than or equal to the value associated with $v_{11}$.
-Then, because $|R_1| = l$, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are removed from $R'$ and replaced by the edges $(v_3, v_{11})$ and $(v_4, v_{12})$ from $R_1$, as illustrated in Figure \ref{fig:connect/cycle}.
+Then, because $|R_1| = l$, the edges $(v_3, v_{12})$ and $(v_4, v_{11})$ are removed from $R'$ and replaced by the edges $(v_3, v_{11})$ and $(v_4, v_{12})$ from $R_1$.
 Removing the dominating vertices and any incident edges results in an alternating Hamiltonian path, which corresponds to a feasible solution $\mathcal{T}$.
@@
 \section{Experimental Results}
+Benchmark instances currently do not exist for the SCSPP, and so artificial problem instances were produced to compare the performance of the three heuristics.
 For our experiments, we generated 1000 problem instances for $|\mathcal{I}| \in \{500, 100\}$.
-For each problem instance the items have varying widths $w_i$ between 150 and 1000 and score widths $a_i, b_i$ between 1 and 70 to ensure that each item has exactly two score lines, all selected randomly from a uniform distribution.
+In each problem instance the items have varying widths $w_i \in [150,1000]$ and score widths $a_i, b_i \in [1, 70]$ to ensure that each item has exactly two score lines, all selected randomly from a uniform distribution.
 Strips of widths $W = 5000$, 2500 and 1250 were used to influence the number of items per strip.
@@
 Our source code and all data is provided at \cite{hawa2018}.
-Since optimal solutions are not available, in our case solution quality $q$ is estimated by comparing to the theoretical minimum, $q = |\mathcal{S}| / t$.
-For each heuristics, we calculated the average solution quality for every combination of $n$, $\delta$, and $W$ from 1000 instances.
+Since optimal solutions are not available, in our case solution quality $q$ is estimated by comparing each solution to the theoretical minimum, $q = |\mathcal{S}| / t$.
+For each heuristic, we calculated the average solution quality for every combination of $n$, $\delta$, and $W$ from 1000 instances.
 All individual trials were seen to complete in under 160ms.
@@
 	\caption{Average solution quality $q$ for $n = 500$.}
-	\begin{tabular}{@{}c@{\hspace{15pt}}c@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}c@{}}\toprule
-		& \multicolumn{3}{c}{$W = 5000$, $t = 58.039$} && \multicolumn{3}{c}{$W = 2500$, $t = 115.571$} && \multicolumn{3}{c}{$W = 1250$, $t = 230.648$} \\
+	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{7pt}}c@{\hspace{4pt}}ccc@{\hspace{7pt}}c@{\hspace{4pt}}ccc@{\hspace{7pt}}c@{\hspace{4pt}}c}\toprule
+		& \multicolumn{3}{c}{$W = 5000$, $t = 58.039$} & \phantom{a} & \multicolumn{3}{c}{$W = 2500$, $t = 115.571$} & \phantom{a} & \multicolumn{3}{c}{$W = 1250$, $t = 230.648$} \\
 		\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
@@
 \end{table}
-%The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.475, 4.310, and 2.165 respectively.
 
@@
 	\caption{Average solution quality $q$ for $n = 1000$.}
-	\begin{tabular}{@{}c@{\hspace{15pt}}c@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}ccc@{\hspace{7pt}}c@{\hspace{5pt}}c@{}}\toprule
-		& \multicolumn{3}{c}{$W = 5000$, $t = 115.534$} && \multicolumn{3}{c}{$W = 2500$, $t = 230.563$} && \multicolumn{3}{c}{$W = 1250$, $t = 460.623$} \\
+	\begin{tabular}{c@{\hspace{15pt}}c@{\hspace{7pt}}c@{\hspace{4pt}}ccc@{\hspace{7pt}}c@{\hspace{4pt}}ccc@{\hspace{7pt}}c@{\hspace{4pt}}c}\toprule
+		& \multicolumn{3}{c}{$W = 5000$, $t = 115.534$} & \phantom{a} & \multicolumn{3}{c}{$W = 2500$, $t = 230.563$} & \phantom{a} & \multicolumn{3}{c}{$W = 1250$, $t = 460.623$} \\
 		\cmidrule{2-4} \cmidrule{6-8} \cmidrule{10-12}
@@
 \end{table}
-% The average number of items per strip for $W = 5000$, 2500 and 1250 are 8.621, 4.329 and 2.169 respectively.
 
@@
 Figures in bold indicate the best average solution quality for the given combination of parameters.
-We see that $q$ tends toward 1 as $\delta$ increases since the proportion of score widths meeting the vicinal sum constraint increases, allowing more items per strip\footnote{The average number of items per strip when $n = 500$ for $W = 5000$, 2500 and 1250 are 8.475, 4.310, and 2.165 respectively, and the average number of items per strip when $n = 1000$ for $W = 5000$, 2500 and 1250 are 8.621, 4.329, and 2.169 respectively.} and reducing the number of strips required.
+We see that $q$ tends towards 1 as $\delta$ increases since the proportion of score widths meeting the vicinal sum constraint increases, consequently permissing more items to be packed on each individual strip\footnote{The average number of items per strip when $n = 500$ for $W = 5000$, 2500 and 1250 are 8.475, 4.310, and 2.165 respectively, and the average number of items per strip when $n = 1000$ for $W = 5000$, 2500 and 1250 are 8.621, 4.329, and 2.169 respectively.}, thus reducing the number of strips required.
 Note that when $\delta = 1.0$ MFFD and MFFD$^+$ have identical solution qualities, as the instances are equivalent to the original BPP ($\tau = 0$); hence they operate in the same fashion as the original FFD heuristic.

### 2018-07-22 PAPER/main.tex
finished draft conclusion and further work

@@
 
-\noindent The remainder of this article is structured as follows: In Section 2, we will detail an exact polynomial-time algorithm for the COP, and show how it is applicable to the SCPSP.
-Section 3 then introduces three heuristics that can be used to find feasible solutions to the SCSPP, one of which makes particular use of the exact algorithm from the previous section, and their associated advantages and disadvantages.
-An analysis of results gained from extensive experiments and a comparison of the heuristics is provided in Section 4, and finally Section 5 concludes the paper and proposes some potential directions for future work.
+\noindent The remainder of this article is structured as follows: In Section \ref{sec:ahc}, we will detail an exact polynomial-time algorithm for the COP, and show how it is applicable to the SCPSP.
+Section \ref{sec:scsppsoln} then introduces three heuristics that can be used to find feasible solutions to the SCSPP, one of which makes particular use of the exact algorithm from the previous section, and their associated advantages and disadvantages.
+An analysis of results gained from extensive experiments and a comparison of the heuristics is provided in Section \ref{sec:expresults}, and finally Section \ref{sec:conclusion} concludes the paper and proposes some potential directions for future work.
 
 \section{Solving the COP}
-\label{sec:ahca}
+\label{sec:ahc}
 We now present an exact polynomial-time algorithm for the COP.
@@
 \section{Experimental Results}
+\label{sec:expresults}
 Benchmark instances currently do not exist for the SCSPP, and so artificial problem instances were produced to compare the performance of the three heuristics.
@@
 \section{Conclusions and Further Work}
-This paper introduced a strip-packing problem with score constraints, where the order and orientation of the items is crucial to the feasibility of the solution.
-We shown that a solution can be found for the single-strip version of the problem in polynomial-time by modelling the problem graphically and using the concept of Hamiltonian cycles.
-Thus, our main problem was to tackle the multi-strip problem.
-Three heuristics, one of which included the exact algorithm for the single-strip problem, were described, and thorough experiments using a variety of parameters were executed.
+\label{sec:conclusion}
+This paper has investigated the Score-Constrained Strip-Packing Problem (SCSPP), a packing problem in which the order and orientation of the items is crucial to the feasibility of the solution.
+We begun by introducing the Constrained Ordering Problem (COP), and described the Alternating Hamiltonian Construction (AHC) algorithm, an exact polynomial-time algorithm that operates by modelling the problem graphically and using the concept of Hamiltonian cycles.
+We then showed how AHC can be used to find a solution for the Score-Constrained Packing Sub-Problem (SCPSP), the single-strip version of the SCSPP.
+Thus, the main problem was to tackle the multi-strip problem.
+Three heuristics, one of which included the exact AHC algorithm, were described, and thorough experiments using a variety of parameters were executed.
+
+A potential avenue for further research would be to adapt AHC in order to find feasible solutions for the SCSPP, rather than the single-strip sub-problem.
+One possible approach would be to introduce weighted edges on the graph $G$ formed during AHC, where blue edges between partners have a value corresponding to the item's width, and all red edges have a value of zero.
+Then, the problem involves producing the fewest number of alternating cycles such that the length of each cycle is less than some fixed value.
+It is clear that this problem is equivalent to the SCSPP, where the total width of items on each strip is less than or equal to $W$, and the number of strips is minimised.
+This can be seen as a variation of a generalisation of the TSP defined by Miller et al.
+\cite{miller1960}.
+
+\begin{comment}
+\begin{enumerate}
+	\item Paper investigated SCSPP, SPP with score-constraints, where order and orientation of items on strips is crucial to the feasibility of the solution.
+	\item We introduced the COP and described AHC, an exact p-time alg to solve it, which models problem graphically and uses concept of Hamiltonian cycles. 
+	\item Then showed that AHC can be used to find solution for single-strip version of SCSPP.
+	\item Thus main problem is multi-strip problem
+	\item Three heuristics, one which includes exact alg AHC for single-strip problem, were detailed/defined, and thorough experiments using a variety of parameters were executed. 
+	\item Showed that all heuristics able to find feasible solutions for large sets of items in very small amount of time
+	\item lower bound.
+	\item AHC can be used in conjucntion with other well known heuristics, ie NF, BF and decreasing versions
+	\item Extend concept of AHC to solve multi-strip problem, graph G has weighted edges, where blue edges between partners have value corresponding to item width and red edges = 0.
+	\item Then the problem involves producing the fewest number of alt cycles s.t.
+the length of each cycle is less than W, i.e.
+the total width of items on each strip is less than W and the number of strips is minimised.
+	\item Can be seen as a variation of a generalization of the TSP defined by miller where the salesman is required to visit each city exactly once, return to a base city a fixed number of times, given that they must visit no more than a fixed number of cities in each subtour.
+\end{enumerate}	
+\end{comment}
 
@@
 \begin{itemize}
+	\item Showed that all heuristics able to find feasible solutions for large sets of items in very small amount of time
+	\item lower bound.
+	\item AHC can be used in conjucntion with other well known heuristics, ie NF, BF and decreasing versions
 	\item This paper introduced a SPP with score constraints, where the order and orientation of the items is crucial to the feasibility of the solution (for example).
@@
 	\item minimise waste on each strip, not just number of strips
+	\item in conjunction with
 \end{itemize}

### 2018-07-23 PAPER/main.tex
minor changes

@@
 	\label{defn:althamcycle}
-	Let $G(V, B\cup R)$ be a simple, undirected graph where each edge is a member of one of two sets, $B$ or $R$.
+	Let $G = (V, B \cup R)$ be a simple, undirected graph where each edge is a member of one of two sets, $B$ or $R$.
 $G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such that successive edges alternate between sets $B$ and $R$.
@@
 
-To find a suitable matching $R' \subseteq R$, the Maximum Cardinality Matching (MCM) algorithm is executed, which is based on \cite{becker2010} and also the earlier work of Mahadev and Peled \cite{mahadev1994}.
+To find a suitable matching $R' \subseteq R$, a Maximum Cardinality Matching (MCM) algorithm is executed, which is based on \cite{becker2010} and also the earlier work of Mahadev and Peled \cite{mahadev1994}.
 First, take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest-indexed vertex $v_j$ that is not already incident to an edge in $R'$.
@@
 
-\begin{figure}	
+\begin{figure}[H]	
 	\centering
@@
 
-\begin{figure}	
+\begin{figure}[H]	
 	\centering
-	\begin{subfigure}[H]{0.65\textwidth}
+	\begin{subfigure}[h]{0.65\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpsconnect}
@@
 	\end{subfigure}
-	\begin{subfigure}[H]{0.65\textwidth}
+	\begin{subfigure}[h]{0.65\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpscycle}
@@
 	\end{subfigure}
-	\begin{subfigure}[H]{0.75\textwidth}
+	\begin{subfigure}[h]{0.75\textwidth}
 		\includestandalone[width=\textwidth]{figures/mpspath}
@@
 
-The last heuristic, Modified First-Fit Decreasing with AHC (MFFD$^+$), incorporates the AHC algorithm from Section \ref{sec:ahca}.
+The last heuristic, Modified First-Fit Decreasing with AHC (MFFD$^+$), incorporates the AHC algorithm from Section \ref{sec:ahc}.
 It operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip.

### 2018-08-01 PAPER/main.tex
added bullet point for MBR (commented out), minor changes

@@
 \item In the event that BR has produced no sets, there are no suitable edges that can combine the components $C_1, C_2, ..., C_l$ of $G'$, and therefore an alternating Hamiltonian cycle for $G$ cannot be created.
-Thus, no feasible solution exists for the corresponding COP.
+Consequently, no feasible solution exists for the corresponding COP.
 
-\item On the other hand, if there exists a set $R_i$ such that $|R_i| = l$, then all the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle.
+\item If there exists a set $R_i$ such that $|R_i| = l$, then all the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle.
 This is achieved by adding the red edge from $R\backslash R'$ connecting the lower-indexed vertex of each edge in $R_i$ to the higher-indexed vertex of the next edge to $R'$ (for the final edge in $R_i$, add the red edge connecting its lower-indexed vertex to the higher-indexed vertex of the first edge).
@@
 
-\item Otherwise, it may be that multiple sets need to be used to connect the components of $G'$.
+\item It may be that multiple sets need to be used to connect the components of $G'$.
 For two edge sets $R_i$ and $R_j$ to ``overlap'', each set must have exactly one edge from the same component in $G'$, with the other edges in each set being from different components.
@@
 
-\noindent To find these overlapping sets, a Modified Bridge Recognition (MBR) algorithm is used, which is based on BR.
+\noindent  In the final case above, a Modified Bridge Recognition (MBR) algorithm is used to find suitable overlapping sets.
 Firstly, a copy of the set $R_i$ with the highest cardinality\footnote{In the event of a tie, MBR selects the set with the lowest index.} generated by BR is created, called $R^{*}_1$, and is added to $\mathcal{R}^{*}$.
@@
 If both conditions hold, the current edge is added to a new set $R^{*}_2$ which is then added to $\mathcal{R}^{*}$.
-MBR continues to add suceeding edges to $R^{*}_2$, provided condition (a) holds and the suceeding edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, stopping when an edge that does not meet these conditions is reached.
+MBR continues to add succeeding edges to $R^{*}_2$, provided condition (a) holds and the succeeding edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, stopping when an edge that does not meet these conditions is reached.
 Then, if every component of $G'$ has an edge in one of the sets in $\mathcal{R}^{*}$, these sets are able to connect all the components of $G'$ together, and so MBR terminates.
@@
 If MBR has produced a feasible collection of sets then the components of $G'$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in $\mathcal{R}^{*}$.
+
+\begin{comment}
+\begin{enumerate}[noitemsep]
+	\item copy of set $R_i$ with highest cardinality generated by BR is created called $R^{*}_1$ and added to $\mathcal{R}^*$
+	\item remove edges from sorted list used in BR that are in $\mathcal{R}^*$
+	\item go through list to find edge that meets following conditions:
+	\begin{enumerate}[label={(\alph*)}]
+		\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
+		\item the current edge and an edge in $\mathcal{R}^{*}$ are members of the same component of $G'$, and the next edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, or vice versa.
+	\end{enumerate}
+	\item if suitable edge found add current edge to new set $R^{*}_2$, add this set to $\mathcal{R}^*$
+	\item continue to add succeeding edges to $R^{*}_2$ provided (a) holds and succeeding edge is member of component that does not have an edge in $\mathcal{R}^*$.
+	\item If every component of $G'$ has an edge in one of the sets in $\mathcal{R}^*$, stop (the sets can connect all components together, MBR terminates)
+	\item Else, edges in $R^{*}_2$ are removed from sorted list, MBR repeats search from beginning of list for suitable edges to start new set $R^{*}_3$
+	\item (Outside bullet points) Procedure continues until either $\mathcal{R}^*$ contains overlapping sets that cover all components of $G'$ or until there are no more suitable edges in list to start a new set (or until no more sets can be made).
+If MBR has produced a feasible collection of overlapping sets then the components of $G'$ can be merged to create an alt Ham cycle by applying the connecting procedure described above to every set in $\mathcal{R}^*$.
+\end{enumerate}	
+\end{comment}
 

### 2018-08-03 PAPER/main.tex
minor changes to MBR

@@
 	\label{defn:cop}
-	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple.
+	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers\\ $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple.
 The \emph{Constrained Ordering Problem (COP)} consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
@@
 \end{enumerate*}
-If these conditions are met, BR adds the current edge to a set $R_1$, and continues to add all succeeding edges in the list to $R_1$ provided that, for each edge, both conditions hold and the succeeding edge is not a member of a component of $G'$ that has an edge in $R_1$.
+If these conditions are met, BR adds the current edge to a set $R_1$, and continues to add all succeeding edges in the list to $R_1$ provided that, for each edge, both conditions hold and the succeeding edge is not a member of a component of $G'$ that already has an edge in $R_1$.
 Once there are no more valid edges available to add to $R_1$, BR resumes its search through the remaining edges in the list to find another edge that meets the conditions, and can begin a new set $R_2$.
@@
 Firstly, a copy of the set $R_i$ with the highest cardinality\footnote{In the event of a tie, MBR selects the set with the lowest index.} generated by BR is created, called $R^{*}_1$, and is added to $\mathcal{R}^{*}$.
-Then, MBR takes the original sorted list used in BR and removes edges from the list that are already in $\mathcal{R}^{*}$.
+Then, MBR takes the sorted list used in BR and removes edges from the list that are in $\mathcal{R}^{*}$.
 Similarly to BR, MBR proceeds through the list to find an edge that meets the following conditions:
 \begin{enumerate*}[label={(\alph*)}]
-	\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
+	\item the lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
 	\item the current edge and an edge in $\mathcal{R}^{*}$ are members of the same component of $G'$, and the next edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, or vice versa.
@@
 If both conditions hold, the current edge is added to a new set $R^{*}_2$ which is then added to $\mathcal{R}^{*}$.
-MBR continues to add succeeding edges to $R^{*}_2$, provided condition (a) holds and the succeeding edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, stopping when an edge that does not meet these conditions is reached.
+MBR continues to add succeeding edges to $R^{*}_2$, provided (a) holds and the succeeding edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$.
 Then, if every component of $G'$ has an edge in one of the sets in $\mathcal{R}^{*}$, these sets are able to connect all the components of $G'$ together, and so MBR terminates.
@@
 If MBR has produced a feasible collection of sets then the components of $G'$ can be merged to create an alternating Hamiltonian cycle by applying the connecting procedure above to every set in $\mathcal{R}^{*}$.
-
-\begin{comment}
-\begin{enumerate}[noitemsep]
-	\item copy of set $R_i$ with highest cardinality generated by BR is created called $R^{*}_1$ and added to $\mathcal{R}^*$
-	\item remove edges from sorted list used in BR that are in $\mathcal{R}^*$
-	\item go through list to find edge that meets following conditions:
-	\begin{enumerate}[label={(\alph*)}]
-		\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
-		\item the current edge and an edge in $\mathcal{R}^{*}$ are members of the same component of $G'$, and the next edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, or vice versa.
-	\end{enumerate}
-	\item if suitable edge found add current edge to new set $R^{*}_2$, add this set to $\mathcal{R}^*$
-	\item continue to add succeeding edges to $R^{*}_2$ provided (a) holds and succeeding edge is member of component that does not have an edge in $\mathcal{R}^*$.
-	\item If every component of $G'$ has an edge in one of the sets in $\mathcal{R}^*$, stop (the sets can connect all components together, MBR terminates)
-	\item Else, edges in $R^{*}_2$ are removed from sorted list, MBR repeats search from beginning of list for suitable edges to start new set $R^{*}_3$
-	\item (Outside bullet points) Procedure continues until either $\mathcal{R}^*$ contains overlapping sets that cover all components of $G'$ or until there are no more suitable edges in list to start a new set (or until no more sets can be made).
-If MBR has produced a feasible collection of overlapping sets then the components of $G'$ can be merged to create an alt Ham cycle by applying the connecting procedure described above to every set in $\mathcal{R}^*$.
-\end{enumerate}	
-\end{comment}
 
@@
 
+\begin{comment}
+\begin{enumerate}[noitemsep]
+\item copy of set $R_i$ with highest cardinality generated by BR is created called $R^{*}_1$ and added to $\mathcal{R}^*$
+\item remove edges from sorted list used in BR that are in $\mathcal{R}^*$
+\item go through list to find edge that meets following conditions:
+\begin{enumerate}[label={(\alph*)}]
+\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
+\item the current edge and an edge in $\mathcal{R}^{*}$ are members of the same component of $G'$, and the next edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, or vice versa.
+\end{enumerate}
+\item if suitable edge found add current edge to new set $R^{*}_2$, add this set to $\mathcal{R}^*$
+\item continue to add succeeding edges to $R^{*}_2$ provided (a) holds and succeeding edge is member of component that does not have an edge in $\mathcal{R}^*$.
+\item If every component of $G'$ has an edge in one of the sets in $\mathcal{R}^*$, stop (the sets can connect all components together, MBR terminates)
+\item Else, edges in $R^{*}_2$ are removed from sorted list, MBR repeats search from beginning of list for suitable edges to start new set $R^{*}_3$
+\item (Outside bullet points) Procedure continues until either $\mathcal{R}^*$ contains overlapping sets that cover all components of $G'$ or until there are no more suitable edges in list to start a new set (or until no more sets can be made).
+If MBR has produced a feasible collection of overlapping sets then the components of $G'$ can be merged to create an alt Ham cycle by applying the connecting procedure described above to every set in $\mathcal{R}^*$.
+\end{enumerate}	
+\end{comment}
+
 \bibliographystyle{splncs04}

### 2018-08-07 PAPER/main.tex
final copy to submit

@@
 Here, a set $\mathcal{I}$ of rectangular items (where $|\mathcal{I}| = n$) of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right.
-Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places.
+Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$ and possesses two vertical score lines, marked in predetermined places.
 A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:itemsknife}).
@@
 	\includestandalone[width=0.85\textwidth]{figures/itemsknife}
-	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation $(a_i, b_i)$, and a feasible alignment of two items that can be scored simultaneously.}	
+	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation $(a_i, b_i)$, and a feasible alignment of two items whose adjacent score lines can be scored simultaneously.}	
 	\label{fig:itemsknife}
@@
 
-It can be seen that, when using just one strip, this strip-packing problem is equivalent to the COP, where each unordered pair in an instance $\mathcal{M}$ contains the score widths of an item, and $\tau$ is the minimum scoring distance.
-It then follows that the vicinal sum constraint corresponds to the requirement for the sum of adjacent score widths to exceed $\tau$.
+It can be seen that, when using a single strip, this packing problem is equivalent to the COP, where each unordered pair in an instance $\mathcal{M}$ contains the score widths of an item and $\tau$ is the minimum scoring distance.
+It then follows that the vicinal sum constraint \eqref{eqn:vsc} corresponds to the requirement for the sum of adjacent score widths to exceed $\tau$.
 Figure \ref{fig:items/aligned} shows the same instance $\mathcal{M}$ mentioned earlier depicted as a packing problem.
@@
 	\end{subfigure}
-	\caption{Example of the strip-packing problem and a corresponding solution using $\tau = 7$.}
+	\caption{Example of a single strip-packing problem and a corresponding solution with $\tau = 7$.}
 	\label{fig:items/aligned}
@@
 	Let $\mathcal{I}$ be a set of $n$ rectangular items of height $H$ with varying widths $w_i \in \mathbb{Z}^+$ and score widths $a_i, b_i \in \mathbb{Z}^+$ for each item $i \in \mathcal{I}$.
-Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips of height $H$ and width $W$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$, and that no strip is overfilled.
+Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips of height $H$ and width $W$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$ and no strip is overfilled.
 \end{definition}
@@
 
-\noindent The remainder of this article is structured as follows: In Section \ref{sec:ahc}, we will detail an exact polynomial-time algorithm for the COP, and show how it is applicable to the SCPSP.
+\noindent The remainder of this article is structured as follows: In Section \ref{sec:ahc}, we will detail an exact polynomial-time algorithm for the COP and show how it is applicable to the SCPSP.
 Section \ref{sec:scsppsoln} then introduces three heuristics that can be used to find feasible solutions to the SCSPP, one of which makes particular use of the exact algorithm from the previous section, and their associated advantages and disadvantages.
@@
 
-Let $\mathcal{M}$ be an instance of the COP with cardinality $n$.
+Let $\mathcal{M}$ be an instance of the COP of cardinality $n$.
 It is useful to model $\mathcal{M}$ as a graph $G$ in which each vertex is associated with a single value in $\mathcal{M}$ in non-decreasing order.
 A pair of vertices, called ``dominating vertices'' are also added to the graph, both of which are assigned values equal to $\tau$.
-These dominating vertices aid the solution process, and are removed at the end.
+These dominating vertices aid the solution process and are removed at the end.
 Thus, the graph $G$ has $2n+2$ vertices.
 
-As we have seen, the values in $\mathcal{M}$ are arranged in pairs.
+As seen in Definition \ref{defn:cop}, the values in $\mathcal{M}$ are arranged in pairs.
 This is represented in $G$ by adding a set of ``blue'' edges, $B$, between vertices that are ``partners'', i.e.
@@
 By introducing a bijective function $p: V \to V$ that associates each vertex with its partner, $p(v_i) = v_j$, we can denote this set of edges as $B = \{(v_i, p(v_i)) : v_i \in V\}$.
-It can be seen that $B$ is a perfect matching in $G$, with $|B| = n+1$.
+Note that $B$ is a perfect matching in $G$, with $|B| = n+1$.
 Next, a set of ``red'' edges $R$ is added to $G$ that consists of edges between vertices whose sum equals or exceeds $\tau$, provided they are not partners.
-It can be seen that the edges in $R$ represent all possible orderings of values from different pairs in $\mathcal{M}$ that fulfil the vicinal sum constraint in Definition \ref{defn:cop}.
-Thus, we have an undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$ and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$.
+It can be seen that the edges in $R$ represent all possible orderings of values from different pairs in $\mathcal{M}$ that fulfil the vicinal sum constraint \eqref{eqn:vsc}.
+Thus, we have a simple, undirected graph $G$ with vertex set $V = \{v_1, ..., v_{2n+2}\}$ and two distinct edge sets $B$ and $R$ such that $B \cap R = \emptyset$.
 Figure \ref{fig:threshold} illustrates an example construction of $G$.
@@
 
-\noindent Recall that a Hamiltonian cycle on a graph $G$ is a cycle that visits every vertex exactly once.
+\noindent Recall that a Hamiltonian cycle in a graph $G$ is a cycle that visits every vertex exactly once.
 Now, consider the following definition describing a variant of the Hamiltonian cycle problem involving two edge sets.
@@
 
-\noindent It is clear that an alternating Hamiltonian cycle on $G$, if one exists, correpsonds to a feasible solution $\mathcal{T}$, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ indicates the values that meet the vicinal sum constraint, and thus can be placed alongside one another feasibly.
+\noindent It is clear that an alternating Hamiltonian cycle in $G$, if one exists, correpsonds to a feasible solution $\mathcal{T}$, as each ``blue'' edge from $B$ represents a pair of values in $\mathcal{M}$, and each ``red'' edge from $R$ indicates the values that meet the vicinal sum constraint, and thus can be placed alongside one another feasibly.
 Also, note that every edge in $B$ must be present in the alternating Hamiltonian cycle.
@@
 
-The problem of finding an alternating Hamiltonian cycle on general graphs is NP-hard as it generalises the classical Hamiltonian cycle problem \cite{haggkvist1977}.
+The problem of finding an alternating Hamiltonian cycle in general graphs is NP-hard as it generalises the classical Hamiltonian cycle problem \cite{haggkvist1977}.
 However, the special structure of graphs derived from instances of the COP allows them to be solved in polynomial-time using the following method.
@@
 To find a suitable matching $R' \subseteq R$, a Maximum Cardinality Matching (MCM) algorithm is executed, which is based on \cite{becker2010} and also the earlier work of Mahadev and Peled \cite{mahadev1994}.
-First, take each vertex $v_1, v_2,..., v_{2n+2}$ in turn, and select the edge in $R$ connecting $v_i$ to the highest-indexed vertex $v_j$ that is not already incident to an edge in $R'$.
-Now, add this edge $(v_i, v_j)$ to $R'$, and proceed to the next vertex until all the vertices have been assessed.
+First, take each vertex $v_1, v_2,..., v_{2n+2}$ in turn and select the edge in $R$ connecting $v_i$ to the highest-indexed vertex $v_j$ that is not already incident to an edge in $R'$.
+Now, add this edge $(v_i, v_j)$ to $R'$ and proceed to the next vertex until all the vertices have been assessed.
 The two vertices incident to each matching edge in $R'$ are now referred to as being ``matched''.
@@
 Clearly, if $|R'| < n+1$ after MCM has completed, there are an insufficient number of red edges to form an alternating Hamiltonian cycle, and therefore no feasible solution exists for the given instance $\mathcal{M}$.
-Otherwise, $R'$ is a perfect matching of cardinality $n+1$ and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex $v_i \in V$ is incident to one blue edge and one red edge, as can be seen in Figure \ref{fig:mps}.
+Otherwise, $R'$ is a perfect matching of cardinality $n+1$, and the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph where each vertex $v_i \in V$ is incident to one blue edge and one red edge, as can be seen in Figure \ref{fig:mps}.
 $G'$ therefore consists of one or more cyclic components $C_1, C_2, ..., C_l$.
@@
 \noindent In the case where $G'$ comprises one component, i.e.
-$l = 1$, then this alternating cycle is in fact Hamiltonian, and therefore specifies a solution to the COP.
+$l = 1$, then this alternating cycle is in fact Hamiltonian and therefore specifies a solution to the COP.
 However, if $l > 1$, the components of $G'$ must be combined to form a single alternating Hamiltonian cycle.
-To do this, an additional procedure called Bridge Recognition (BR) is executed that selects suitable edges in $R\backslash R'$ to replace edges in $R'$ to connect the components of $G'$.
+To do this, a Bridge Recognition (BR) procedure is executed that selects suitable edges from $R\backslash R'$ to replace edges in $R'$ to connect the components of $G'$.
 
@@
 	\item the lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
-	\item the current edge and the next edge are members of different components on $G'$.
+	\item the current edge and the next edge are members of different components of $G'$.
 \end{enumerate*}
@@
 \begin{enumerate}
-\item In the event that BR has produced no sets, there are no suitable edges that can combine the components $C_1, C_2, ..., C_l$ of $G'$, and therefore an alternating Hamiltonian cycle for $G$ cannot be created.
+\item In the event that BR has produced no sets, there are no suitable edges that can combine the components of $G'$, and therefore an alternating Hamiltonian cycle in $G$ cannot be created.
 Consequently, no feasible solution exists for the corresponding COP.
 
-\item If there exists a set $R_i$ such that $|R_i| = l$, then all the components of $G'$ can be merged together to form a single alternating Hamiltonian cycle.
+\item If there exists a set $R_i$ such that $|R_i| = l$, then all components of $G'$ can be merged together to form a single alternating Hamiltonian cycle.
 This is achieved by adding the red edge from $R\backslash R'$ connecting the lower-indexed vertex of each edge in $R_i$ to the higher-indexed vertex of the next edge to $R'$ (for the final edge in $R_i$, add the red edge connecting its lower-indexed vertex to the higher-indexed vertex of the first edge).
-Any edges that appear in both $R_i$ and $R'$ are then removed from $R'$, so that $R'$ remains a perfect matching and $R_i \cap R' = \emptyset$.
+Edges that appear in both $R_i$ and $R'$ are then removed from $R'$ so that $R'$ remains a perfect matching and $R_i \cap R' = \emptyset$.
 $G'$ then consists of a single alternating Hamiltonian cycle; hence a solution has been found.
@@
 For two edge sets $R_i$ and $R_j$ to ``overlap'', each set must have exactly one edge from the same component in $G'$, with the other edges in each set being from different components.
-A collection of sets $\mathcal{R}^{*}$ therefore needs to be found such that each set overlaps with at least one other set, and each component has at least one edge in one of the sets.
+A collection of sets $\mathcal{R}^{*}$ therefore needs to be found such that each set in $\mathcal{R}^*$ overlaps with at least one other set, and each component of $G'$ has at least one edge in one of the sets.
 \end{enumerate}
@@
 \noindent  In the final case above, a Modified Bridge Recognition (MBR) algorithm is used to find suitable overlapping sets.
-Firstly, a copy of the set $R_i$ with the highest cardinality\footnote{In the event of a tie, MBR selects the set with the lowest index.} generated by BR is created, called $R^{*}_1$, and is added to $\mathcal{R}^{*}$.
+Firstly, a copy of the set $R_i$ with the highest cardinality\footnote{In the event of a tie, MBR selects the set with the lowest index.} generated by BR is created, called $R^{*}_1$, and added to $\mathcal{R}^{*}$.
 Then, MBR takes the sorted list used in BR and removes edges from the list that are in $\mathcal{R}^{*}$.
@@
 	\item the lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
-	\item the current edge and an edge in $\mathcal{R}^{*}$ are members of the same component of $G'$, and the next edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, or vice versa.
+	\item the current edge and an edge in $\mathcal{R}^{*}$ are members of the same component of $G'$ and the next edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, or vice versa.
 \end{enumerate*}
@@
 	\item $(v_3, v_{11}) \in R$, i.e. the lower-indexed vertex of the first edge is adjacent to the higher-indexed vertex of the next edge; and
-	\item the edges are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$ as shown previously in Figure \ref{fig:mps}).
+	\item the edges are members of different components ($(v_3, v_{12}) \in C_1$ and $(v_4, v_{11}) \in C_2$).
 \end{enumerate*}
@@
 	\end{subfigure}
-	\caption{Selected edges found using BR merge the components of $G'$ together, forming an alternating Hamiltonian cycle which corresponds to a solution $\mathcal{T}$.}
+	\caption{Specific edges found using BR merge the components of $G'$ together, forming an alternating Hamiltonian cycle which corresponds to a solution.}
 	\label{fig:connect/cycle}
@@
 
-\noindent The entire algorithm that has been described will be referred to as the Alternating Hamiltonian Construction (AHC) algorithm.
+\noindent This entire algorithm that has been described will be referred to as the Alternating Hamiltonian Construction (AHC) algorithm.
 The time complexity of AHC is quadratic, as stated in the following theorem:
@@
 The sets $R_i$ can be created in $O(n)$ time, as each edge in the list is considered once.
-As each set $R_i$ contains at least two edges, BR will produce up to $\frac{n+1}{2}$ sets.
+As each set $R_i$ contains at least two edges, BR can produce up to $\frac{n+1}{2}$ sets.
 Thus, examining each set to find one such that $|R_i| = l$ takes at most $O(n)$ time.
@@
 Finally, the connecting procedure replaces up to $n+1$ edges, and so can be executed in $O(n)$ time.
-Consequently, AHC had an overall worst case complexity of $O(n^2)$.
+Consequently, AHC has an overall worst case complexity of $O(n^2)$.
 \qed
@@
 
-\noindent That is, all items must be packed onto a strip (\ref{eqn:packall}), each item can only be placed on one strip (\ref{eqn:nooverlap}), the strips cannot be overfilled (\ref{eqn:capacity}), and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled (\ref{eqn:vscstrip}).
-Note that constraints (\ref{eqn:packall})--(\ref{eqn:capacity}) are the necessary conditions for the BPP.
+\noindent That is, all items must be packed onto a strip \eqref{eqn:packall}, each item can only be placed on one strip \eqref{eqn:nooverlap}, the strips cannot be overfilled \eqref{eqn:capacity}, and the items on each strip $S_j$ in the solution must be arranged such that the vicinal sum constraint is fulfilled \eqref{eqn:vscstrip}.
+Note that constraints \eqref{eqn:packall}--\eqref{eqn:capacity} are the necessary conditions for the BPP.
 An optimal solution $\mathcal{S}$ for the SCSPP is a solution that consists of the fewest number of strips $k$ needed to feasibly contain the $n$ items in the given problem instance.
@@
 
-As mentioned in the introduction, the SCSPP shares many similarities with the BPP, however the addition of constraint (\ref{eqn:vscstrip}) brings complications.
+As mentioned in the introduction, the SCSPP shares many similarities with the BPP, however the addition of \eqref{eqn:vscstrip} brings complications.
 One obvious difference is the order in which the items appear on the strips.
@@
 Then, the problem involves producing the fewest number of alternating cycles such that the length of each cycle is less than some fixed value.
-It is clear that this problem is equivalent to the SCSPP, where the total width of items on each strip is less than or equal to $W$, and the number of strips is minimised.
 This can be seen as a variation of a generalisation of the TSP defined by Miller et al.
-\cite{miller1960}.
+\cite{miller1960}.It is clear that this problem is equivalent to the SCSPP, where the total width of items on each strip is less than or equal to $W$, and the number of strips is minimised.
 

### 2018-10-01 PAPER/main.tex
made changes to conclusion

@@
 		\includestandalone[width=\textwidth]{figures/mpsconnect}	
-		%\caption{Edges from $R\backslash R'$ can connect vertices from different cycles.}	
 		\label{fig:mpsconnect}
@@
 		\includestandalone[width=\textwidth]{figures/mpscycle}
-		%\caption{Replacing edges connects the components and forms an alternating Hamiltonian cycle.}	
 		\label{fig:mpscycle}
@@
 		\includestandalone[width=\textwidth]{figures/mpspath}
-		%\caption{Alternating Hamiltonian Path corresponding to feasible solution $\mathcal{T}$.}	
 		\label{fig:mpspath}
@@
 This reduces the possibility of having to start a new strip for an item, thus preventing increasing the number of strips in the final solution.
-%Since AHC is executed every time an item can fit onto a strip that already contains items, (up to $|\mathcal{S}|$ times per item, where $|\mathcal{S}|$ is the number of strips containing at least one item so far in the procedure) MFFD$^+$ is slower in comparison to the previous heuristics.
 
@@
 Benchmark instances currently do not exist for the SCSPP, and so artificial problem instances were produced to compare the performance of the three heuristics.
-For our experiments, we generated 1000 problem instances for $|\mathcal{I}| \in \{500, 100\}$.
+For our experiments, we generated 1000 problem instances for $|\mathcal{I}| \in \{500, 1000\}$.
 In each problem instance the items have varying widths $w_i \in [150,1000]$ and score widths $a_i, b_i \in [1, 70]$ to ensure that each item has exactly two score lines, all selected randomly from a uniform distribution.
@@
 
-A potential avenue for further research would be to adapt AHC in order to find feasible solutions for the SCSPP, rather than the single-strip sub-problem.
-One possible approach would be to introduce weighted edges on the graph $G$ formed during AHC, where blue edges between partners have a value corresponding to the item's width, and all red edges have a value of zero.
-Then, the problem involves producing the fewest number of alternating cycles such that the length of each cycle is less than some fixed value.
-This can be seen as a variation of a generalisation of the TSP defined by Miller et al.
-\cite{miller1960}.It is clear that this problem is equivalent to the SCSPP, where the total width of items on each strip is less than or equal to $W$, and the number of strips is minimised.
-
-\begin{comment}
-\begin{enumerate}
-	\item Paper investigated SCSPP, SPP with score-constraints, where order and orientation of items on strips is crucial to the feasibility of the solution.
-	\item We introduced the COP and described AHC, an exact p-time alg to solve it, which models problem graphically and uses concept of Hamiltonian cycles. 
-	\item Then showed that AHC can be used to find solution for single-strip version of SCSPP.
-	\item Thus main problem is multi-strip problem
-	\item Three heuristics, one which includes exact alg AHC for single-strip problem, were detailed/defined, and thorough experiments using a variety of parameters were executed. 
-	\item Showed that all heuristics able to find feasible solutions for large sets of items in very small amount of time
-	\item lower bound.
-	\item AHC can be used in conjucntion with other well known heuristics, ie NF, BF and decreasing versions
-	\item Extend concept of AHC to solve multi-strip problem, graph G has weighted edges, where blue edges between partners have value corresponding to item width and red edges = 0.
-	\item Then the problem involves producing the fewest number of alt cycles s.t.
-the length of each cycle is less than W, i.e.
-the total width of items on each strip is less than W and the number of strips is minimised.
-	\item Can be seen as a variation of a generalization of the TSP defined by miller where the salesman is required to visit each city exactly once, return to a base city a fixed number of times, given that they must visit no more than a fixed number of cities in each subtour.
-\end{enumerate}	
-\end{comment}
-
-\begin{comment}
-\begin{itemize}
-	\item Showed that all heuristics able to find feasible solutions for large sets of items in very small amount of time
-	\item lower bound.
-	\item AHC can be used in conjucntion with other well known heuristics, ie NF, BF and decreasing versions
-	\item This paper introduced a SPP with score constraints, where the order and orientation of the items is crucial to the feasibility of the solution (for example).
-	\item We showed that a solution can be found for the single strip version of the problem (subproblem) in p-time/ we showed an exact p-time alg for the single strip version of the problem. 
-	\item exact p-time alg for COP used to solve subproblem
-	\item Thus the main problem was finding solutions for the multistrip version
-	\item Created 3 heuristics, one which included the p-time alg. 
-	\item shown how AHC can be combined with well known heuristic to produce a method for tackling multistrip version of the problem, the SCSPP.
-	\item Experimental results show that ...
-	\item Further work.
-	\item items closer to practical applications, multiple items having same width and score widths
-	\item Genetic algorithm/EA
-	\item Operating theatre cleaning/scheduling
-	\item lower bound for the optimal number of strips SCSPP
-	\item cite miller1960 TSP returning to base
-	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution.
-	\item include item width in ahc, so add values to the blue edges of the graph, weighted edges, red edges have value = 0.
-	\item Then the problem would be: find the minimum number of alternating cycles on $G$ such that the length of the cycle is less than or equal to some value $W$ (which is the strip width).
-The length of the cycle would be the sum of all the weighted edges, so the sum of all the blue edges, since red = 0.
-	\item then could break and form edges to create new components of different sizes if some are too large, or join together if some are small, thus decreasing the number of cycles
-	\item or if possible, find a single alt Ham cycle, and break up into as few smaller cycles as possible such that the length of each cycle is less than or equal to $W$
-	\item another way, create as few feasible subsets $\mathcal{I}' \subseteq \mathcal{I}$ such that the total width of the items in each subset $\mathcal{I}$ is less than $W$, i.e.
-perform usual FFD alg, ignore score widths
-	\item then perform ahc on each set, try to find feasible solution.
-	\item if sets dont have feasible solution, try swapping items between sets
-	\item initial tests, Becker theorem 6 2015 paper cite garraffa2016
-	\item minimise waste on each strip, not just number of strips
-	\item in conjunction with
-\end{itemize}
-\end{comment}
-
-\begin{comment}
-\begin{enumerate}[noitemsep]
-\item copy of set $R_i$ with highest cardinality generated by BR is created called $R^{*}_1$ and added to $\mathcal{R}^*$
-\item remove edges from sorted list used in BR that are in $\mathcal{R}^*$
-\item go through list to find edge that meets following conditions:
-\begin{enumerate}[label={(\alph*)}]
-\item The lower-indexed vertex of the current edge and the higher-indexed vertex of the next edge in the list are adjacent via an edge in $R$; and
-\item the current edge and an edge in $\mathcal{R}^{*}$ are members of the same component of $G'$, and the next edge is a member of a component that does not have an edge in $\mathcal{R}^{*}$, or vice versa.
-\end{enumerate}
-\item if suitable edge found add current edge to new set $R^{*}_2$, add this set to $\mathcal{R}^*$
-\item continue to add succeeding edges to $R^{*}_2$ provided (a) holds and succeeding edge is member of component that does not have an edge in $\mathcal{R}^*$.
-\item If every component of $G'$ has an edge in one of the sets in $\mathcal{R}^*$, stop (the sets can connect all components together, MBR terminates)
-\item Else, edges in $R^{*}_2$ are removed from sorted list, MBR repeats search from beginning of list for suitable edges to start new set $R^{*}_3$
-\item (Outside bullet points) Procedure continues until either $\mathcal{R}^*$ contains overlapping sets that cover all components of $G'$ or until there are no more suitable edges in list to start a new set (or until no more sets can be made).
-If MBR has produced a feasible collection of overlapping sets then the components of $G'$ can be merged to create an alt Ham cycle by applying the connecting procedure described above to every set in $\mathcal{R}^*$.
-\end{enumerate}	
-\end{comment}
+A potential avenue for further research would be to produce an evolutionary algorithm (EA) for the SCSPP which incorporates AHC during local search.
+One possible addition would be to introduce an approach similar to one used in \cite{malaguti2008}.
+During each iteration of the evolutionary algorithm, high quality strips are chosen from each offspring solution and stored in separate set.
+On completion of the EA, a postoptimisation procedure based on the exact cover problem is executed.
+The procedure aims to find the fewest number of strips from the set of high quality strips that contains every item exactly once.
 
